### 2010-10-12 papers/pldi2011/sigplanconf-template.tex

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

\documentclass[preprint]{sigplanconf}

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}

\begin{document}

\conferenceinfo{PLDI'11}{June 4-8, San Jose, California.} 
\copyrightyear{2011} 
\copyrightdata{[to be supplied]}

\titlebanner{preprint}        % These are ignored unless
\preprintfooter{}   % 'preprint' option specified.

\title{Debugging by \textit{lastChange}}
\subtitle{}

\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
           {Ecole Polytechnique F\'ed\'erale de Lausanne}
           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}

\authorinfo{John J. Barton}
           {IBM Research - Almaden}
           {johnjbarton@johnjbarton.com}

\maketitle

\begin{abstract}
Backward search from bug symptoms to defects-which cause the bug-is a natural way to debugging. However, due to the lack of support for easily bakward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy demands a lot of effort from developers. A fundumental step in this process is tracking origins to wrong values and any aid in this regard can greatly reduce the complexity of debugging for developers.

In this paper we present a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the point. The only prerequisite for \textit{lastChange} functionality is bug reproduciblity (i.e., there is a test case which reproduces the bug). We explain the algorithms behind this functionality. As a proof of concept we developed a javascript prototype which adds this feature to a well-known javascript debugger, Firebug.

% how we buil it on breakpoint technology
\end{abstract}

\category{D.2.5}{Testing and Debugging}{Debugging aids}
\category{D.2.6}{Programming Environments}{Integrated environments}

\terms
Algorithms, Human Factors, Languages

\keywords
LastChange, Locating Defects, Breakpoint, Watchpoint, Logging

%---------------------------------------------------------------------------------------------------
\section{Introduction}
Debugging is an inevitable part of programming, still hard and time-consuming. To fix a bug, developers have to reproduce and monitor the buggy execution several times to understand the program's unexpected behavior. Trial and error, guess-work and analyzing huge collected data are the inseparable parts of this process. According to \cite{LaToza}, developers spend about fifty percent of their time debugging. Therefore, every improvement to debugging techniques and tools can considerably save developers' time and improve programs' quiality.

Locating defects cause the bug is the main part of debugging. A common strategy for locating defects is starting from bug symptoms and backward movement by following the origings to wrong values. While this strategy seems straight-forward and effective, applying this strategy using traditional methods is complicated. There are two traditional approaches to debugging, breakpoint-based and log-based debugging. None of these approaches assist developer in finding origings to a wrong value. It is due to developer to search source files, find the list of possible origings to a wrong value and set breakpoints or insert log statements in a way that covers all possible origins.
The next dilemma is data collection. In breakpoint debugging, developer has to memorize values or collect data manually at every breakpoint hit and in cases that there are many breakpoint hits, this becomes a tedious task. In log-based debugging, developer has to decide about data should be collected when inserts the log statement. In this approach developer ends up in dealing with long log files and analyzing huge collected data.

Our proposal is a new functionality in debuggers which locates the origin of a wrong value, call it \textit{lastChange}. The only prerequisite for \textit{lastChange} functionality is bug reproduciblity (i.e., there is a test case which reproduces the bug). Assume that the program execution is paused on a breakpoint and the developer is suspicious about the value of an object property or variable. The developer selects \textit{lastChange} on the value and it is due to debugger to locate and shows the last change of object property or variable. Debugger reproduces the buggy execution and collects limited data and once the execution reaches the same place (i.e., the same breakpoint hit), call it \textit{reproduction point}, it pauses the execution, analyzes the collected data and shows the location of the last change to the developer. Developer can also examine the program state at the located point of execution, and asks for a new \textit{lastChange} at this point.

Our contritution in this paper is the algorightm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point. The algorithm builds on existing breakpoint debugger technology. We demonstrate the feasibiltily of the algorithm with an implementation extending the Firebug Javascript debugger.

%\begin{enumerate}
%/\item The evaluation of \textit{lastChange} implementation.

%\end{enumerate}

%---------------------------------------------------------------------------------------------------
\section{Introductory example}
We illustrate the \textit{lastChange} functionality by a simple example. The example demonstrates a buggy javascript code in a html page (Figure ~\ref{fig:js-code}). The page contains a button (line 40) which shows the \texttt{myObject.myProperty} value. Whenever user clicks on the button \texttt{onClick} function is called. This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value. Once the page is loaded for the first time the button shows \texttt{1} as the initial value of \texttt{myObject.myProperty}. The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears on the button.

\begin{figure}[htp]
\begin{verbatim}
1 <html>
...
5   <script type="text/javascript">
6    myObject = {myProperty : 1};
7    myCondition = {value : 1};
...
13   function onClick(){
14     foo();
15     myObject.myProperty++;
16     bar();
17     ...
18     updateButton();
19   }
20   function updateButton(){
21     var myParagraph =
          document.getElementById("myButton");
22     myButton.innerHTML = myObject.myProperty;
23   }   
24   function foo(){
25  	 myCondition.value = oldValue;
26   }  
27   function bar(){ 
28     if (!myCondition.value)
29         myObject.myProperty = 0;
30   }
31  </script> 
...
40  <button id="myButton" onclick="onClick()">
41  	1 
42  </button>
43 </html>
\end{verbatim}
\caption{The buggy javascript code.}
\label{fig:js-code}
\end{figure}

To start debugging, the developer sets a abreakpoint on line 22 which is the place button's text is updated. Once the button is clicked execution is paused at line 22. (Figure ~\ref{fig:example1}) shows the debugger while the execution is paused. The developer can examine the program state at the right panel and as it shows the \texttt{myObject.myProperty} value at this point is zero. This value is wrong and the developer seeks the last place this value is changed. By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}). Debugger considers the paused point at the breakpoint as the \textit{reproduction point}, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}). The program state debugger shows on the right panel belongs to the past. Therefore the right panel just shows the partially collected data. If the developer needs some values which are not available in the right panel, debuggers re-executes another time and collects and shows the requested data.

Looking at line 29, it seems that something is wrong with \texttt{myCondition.value} which causes line 29 execution. The developer examines \texttt{myCondition.value} and it is \texttt{undefined}. The next step is to know when this property got this value. To do so, the developer runs \textit{lastChange} command on \texttt{myCondition.value} at this point. Debugger re-executes the execution and pauses at the reproduction point and shows line 25-the place \texttt{undefined} value is assigned to \texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is clear that the bug occures because \texttt{oldValue} is \texttt{undefined} once execution reaches line 25.

\begin{figure}[htp]
\includegraphics{5-example-points.jpg}
\caption{The examinated points.}
\label{fig:example-points}
\end{figure}

As demonstrated in Figure ~\ref{fig:example-points}, the developer examinated three points of execution. These points-the history of the search for the defect-are available through the debugger's interface. On the top of the left panel in Figure ~\ref{fig:example3} there is an opened list which shows all three examinated points. The first one is the breakpoint on line 22, the second one is the point which is the last change of \texttt{myObject.myProperty} before the reaching the breakpoint and finally the last one is the point of execution in which \texttt{myCondition.value} gets the \texttt{undefined} value. Moreover, the source lines related to these points are tagged with red-cycle icons.

\begin{figure*}[htp]

\subfigure[The execution is paused at line 22 by an ordinary breakpoint.]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.19\textheight]{1-bp22.jpg}}

\subfigure[\textit{lastChange} command.]{\label{fig:example2}\includegraphics[width=1.0\textwidth, height=.19\textheight]{2-bp22-lastChange.jpg}}

\subfigure[The result of \textit{lastChange} call on \texttt{myObject.myProperty}.]{\label{fig:example3}\includegraphics[width=1.0\textwidth, height=.23\textheight]{3-lastChange.jpg}}

\subfigure[The result of \textit{lastChange} call on \texttt{myCondition.value}.]{\label{fig:example4}\includegraphics[width=1.0\textwidth, height=.23\textheight]{4-lastChange2.jpg}}

\caption{The stages of locating the defect using \textit{lastChange} feature.}
\label{fig:lastChange}
\end{figure*}

Notice that in our example, \textit{lastChange} combines some aspects of breakpoint and of log-based debugging. Like breakpoint debugging, the developer re-executes a live runtime without changing the source and without a special execution environment beyond the debugger. The state of the program memory and the call stack are available at the lastChange point. Like log-based debugging, the program state and the call stack are recorded during program execution. We can't halt the program at \textit{lastChange} because we don't know which is the last one until we return to the original breakpoint.

%---------------------------------------------------------------------------------------------------
\section{\textit{lastChange} implementation}
\textit{lastChange} can be called on two different types of values: An object property or a variable value. We explain each case separately.

\subsection{\textit{lastChange} on object propery}
At the beginning, we assume that every object has a unique id. Moreover, we assume that there is a special watchpoint, \textit{property watchpoint}, that can be set on a property name \texttt{foo} and whenever property \texttt{foo} in any object changes this watchpoint hits. We know that none of these assumptions is true in javascript. We discuss this issue later in traking object creation.

Once developer asks for the last change of \texttt{bar.foo} at a reproduction point, debugger sets a property watchpoint on \texttt{foo} and  re-executes the program. Whenever the property watchpoint hits, debugger keeps the object id and stack frame locations. Whenever the execution reaches the same reproduction point it looks at the list of all changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).

\begin{figure}[htp]
\includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
\caption{The list of \texttt{foo} changes and \texttt{bar} id which identifies the last change of \texttt{bar.foo} in the history of events.}
\label{fig:foo-changes1}
\end{figure}

\subsection{\textit{lastChange} on variable} 
Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first finds the scope the variable comes from. Consider that in javascript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible. The outer scopes are regualr javascript objects or closure scopes. The first group are usually created by calling \texttt{with()} function. The second group are created once a function is called. Therefore, there are theree cases for the escope of a variable, the current scope, an outer scope regular object or an outer scope clousure scope.

If the variable belongs to an outer scope regular object, debugger treats the case like \textit{lastChange} on an object property. In the other two cases, debugger sets breakpoints on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions). For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var2} is requested by the developer, two breakpoints on lines 22 and 23 will be set, but if the execution is paused at line 19, four breakpoints on lines 11, 12, 16, and 18.

%%% we need a short explanation about scopes
%%% important: think about it: we also need to set a special variable (id) to let us to identify the related functional scope
\begin{figure}[htp]
\begin{verbatim}
10  function parent(var1){
11    var var2;
12    var2 = 1;
13    function myfun(var3){
14      var var4;
15      var4 = {...}
16      var2 = var4;
17      function firstChild(var5){
18        var2 = 5;
19        var4 = 5;
20      }  
21      function secondChild(var6){
22       	var var2;
23        var2 = 5			      
24        var4 = 5;	
25      }
26    }  
23  }    
\end{verbatim}
\caption{Sample javascript code demonstrating closure variables.}
\label{fig:js-closure}
\end{figure}

Everytime one of the breakpoints hit a new event is inserted to the list of events. To separate irrelvant event from each other, we use a special variable \texttt{\_scopeId}. If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created in the scope. This is specially needed in case of recursive calls. Figure Figure ~\ref{fig:recursive} shows changes to a the same variable \texttt{x} but in different scopes. alling \textit{lastChange(x)} at point B should return point A.

\begin{figure}[htp]
\begin{verbatim}

Recursive function: 
 f(){
   var x;
   x++;
   f();
   x; 
   ...
 }

The trace of recursive calls:

  f was called.
    x changes; // A
      f was called;
        x changes;
        f was called
          x changes;
    //B

\end{verbatim}
\caption{Recursive calls.}
\label{fig:recursive}
\end{figure}

\subsection{\textit{lastChange} on \textit{lastChange}}
Once the developer asks for the first \textit{lastChange} all program state is available to the debugger. But the next \textit{lastChange} calls are asked over collected data. For example, debugger needs object id for the second \textit{lastChange} and this data should be collected. To do so, debugger does a data dependency analysis between points which gives a list of items should be collected at every point.

%---------------------------------------------------------------------------------------------------
\section{Javascript implementation}
The javascript prototype is implemented as an extension to Firebug[] javasrcipt debugger.

\subsection{Execution reproduction}
Altough execution reproduction is basicly should be provided by the developer, we tried to devise some automatic way which reproduces the execution. In the prototype, develooper can choose among three reproduction options. The first one is using a test case which provided by developer. The second one is by record and replay and the third one is local-reproduction.

Two parts should be carefully considered in execution reproduction. First, the initial state should be the same as previous execution. Second, the similar actions and events should be applied to the program during the execution. In the record and replay approach, debugger stores the initial page url and user actions and during replay phase, opens the same url and emulates user actions. 
In the local reproduction approach, debugger calls the funtion on the bottom of stack with the same parameters.

\subsection{Tracking object creation}
Now we discuss two mentioned assumptions. In the standard javascript every object has a \texttt{watch()} function which receives two parameters, a property name and another function as a hook. Whenever the property with the given name changes the hook function is called. The issue with using this function is that it can only be applied to available objects. However, at the beginning of re-execution there is no object available. To solve this issue we use a feature in Firefox javascript engine, setting a flag gives us the place the object created (e.g., myFile.js, line 24). Though this is a limited data it can help us to get a reference to the object once it is created. Therefore, at the reproduction point, debugger gets the creation location of \texttt{bar} and once the execution reaches to that location it gets a reference to the created object and sets a unique id for it.

\subsection{Data collection}

\subsection{User interface}

\section{Converting \textit{lastChange} result to a conditional breakpoint}
We believe that in many cases it is possible to convert the \textit{lastChange} result to a conditional breakpoint and therefore debugger is able to pause at the point
 instead of showing collected data to the developer. Here, we present an example which shows a case this transformation is not possible.

Figure ~\ref{fig:counter-example} shows a function with processes an array. The array contains numbers except one itme which is \texttt{undefined} and it causes a bug in line 30. There is a call to \texttt{randomPermutation} function in line 11 which randomly permutates the array item. So at every execution the \texttt{undefined} item will be in a new place. Calling \textit{lastChange} on \texttt{x} at the place bug happens, gives a point which shows line 14. Although this point exists at every re-execution but it can not be identified by a conditional breakpoint.

\begin{figure}[htp]
\begin{verbatim}
10 function randomProcess(array){
11   randomPermutation(array);
12   var x, y;
13   for (var i=0 ; i<array.length ; i++){
14      x = array[i]
...
30      y = x+1;
31   }
32 }
\end{verbatim}
\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
\label{fig:counter-example}
\end{figure}

%\section{}
%---------------------------------------------------------------------------------------------------
\section{Reproducible Non-deterministic Execution}
Thus far we have not discussed problems caused by mul-tiple threads or other sources of non-deterministic execu-tions. We want to explain why we believe \textit{lastChange} is robust in the practically important case where a bug is reproducible even though the execution may not be deterministic. 
Because \textit{lastChange} require re-execution, we rely on reproducible but not necessarily deterministic execution. A bug is reproducible for a developer when the developer can start from a determined initial state, operate on the program with a list of actions, and reproduce the symptoms of the bug. The details of the execution can change each time we re-execute the buggy program, but the buggy result is the same. The entire query chain reapplies during each execution so the data we show the developer will be internally consistent. The reproducibility of the bug means that the defect is very unlikely to depend on the order of events during the execution.

In this important case of reproducible bugs, \textit{lastChange} are more effective than breakpoints. In the case of logically deterministic program execution, we can use the result from a \textit{lastChange} operation to set a conditional breakpoint then re-execute the program to position the execution trace backwards from our first breakpoint. %(This may be a useful adjunct for Querypoint debuggers to implement, but this backwards motion in the execution logic is not required for Querypoint debugging.) Thus in this case Querypoint debugging can do the same kinds of things as conventional breakpoints just more automatically.

In the case of a non-deterministic program, a \textit{lastChange} is not equivalent to any series of conventional watchpoints or breakpoints. Each time we re-execute a non-deterministic program, the details of execution in-struction order may change. For example, if we record the source code lines every time a conventional watchpoint hits, the record may differ each time we re-execute. Sup-pose we consult one such record and set a breakpoint on the last entry, the apparent lastChange source line. When we re-execute, the breakpoint will hit, but the information we gain may be incorrect: this may not be the lastChange for this particular re-execution. The \textit{lastChange} method records the values we need and the sequence of source lines from all of the watchpoints, then analyzes the record to select the correct lastChange point. The data shown to the developer will be internally consistent, but of course it may change from a previous re-execution, surprising the developer. This is just a signal that the execution is not deterministic. In future we hope to compare queries from successive executions as a tool for learning about non-deterministic executions.

\section{Evaluation}

\section{Related Work}

\textit{lastChange} functionality supports obtaining information about the execution state logically earlier in the control flow. This support resembles a mixture of replay-based and logging-based debugging. Replay-based approaches capture limited data during execution and replay the bug-gy execution to reach past points. In contrast, logging-based approaches collect enough data during execution to relieve developer from re-execution. Replay-based approaches impose much less runtime overhead (about two orders of magnitudes) comparing to logging-based appproches. However, developer has to re-execute the buggy execution several times. \textit{lastChange} functionality collects data on re-execution but this data is limited to the current queries of developer.

Among replay-based debuggers we compare to bdb \cite{Boothe} and reverse watchpoint \cite{Maruyama}.  A bidirectional C debugger, bdb employs a step counter to locate the requested point from the beginning of execution. It relies on deterministic execution replay (i.e., the same sequence of instructions in re-execution) and records the results of non-deterministic system calls and re-injects them into the program when it is replayed. It makes use of checkpoints to reduce the time needed for re-execution.  Reverse watchpoint, is proposed by Maruyama et al., analyses the execution and moves the debugger to the last write access of a selected variable by re-executing the program from the \cite{Maruyama}.  Similar to bdb it relies on deterministic replay and uses a counter to correctly locate a point in the next execution. The main disadvantage of these appraoches is requiring the exactly the same executions. Even one instruction difference between in two executions leads to wrong results. This requirement is that much restricting that after ten years from bdb paper publication, there is no newer implementation of this idea. On the other hand, \textit{lastChange} doesn't require any special feature in the re-rexecution and it is fit to everyday's developers' debugging practice.

Among logging-based approaches are "omniscient" debuggers ODB\cite{Lewis} and Unstuck[]. Omniscient debuggers have been proposed as a solution for the problems of breakpoint-debugging. Both approaches keep the log history in memory and hence can only record and store the complete history for a short period of time. These debuggers record all the events that occur during the buggy execution and later let the developer to navigate through the obtained execution log. In this approach there is no execution to resume: moving backwards in the log can be similar to moving forwards. Omniscient debuggers suffer from a different set of issues. First, the recording step is time expensive and it should be repeated in case of changes in program. Second, the execution log cannot fully replace the live execution. There are other aspects of execution (e.g., program user interface, file system, database tables, etc.) which are also important in debugging and are not available to the developer in omniscient debuggers. Third, querying collected data (e.g., to restore the program state at a certain point) may not be efficient enough for debugging of realistic programs.

A more scalable approach has been proposed by Pothier et al. \cite{Pothier}. Their back-in-time debugger, TOD, addresses the space problem by storing execution events in a distributed database. Comparing to Omniscient debuggers our approach is lightweight and more flexible. Developer can start debugging just after reproducing bug without a capturing step.  Changing inputs or environment settings and re-executing to investigate the bug works as in conventional breakpoint debuggers.

Two new directions in logging debuggers explore more detailed use of the log and more effective logging approaches. WhyLine\cite{Ko} provides visual interface to collected runtime information and let developer to move  on execution log using queries expressed in terms of the programming objects. WhyLine stores the program user in-terface in addition to program trace and provides answers to why and why not questions to the user. Jive\cite{Czyz} depicts the history of execution by a sequence diagram and lets user to query on events database. Both tools suffer from similar issues with omniscient debuggers; 
%both provide models for extending Querypoint debugging to obtain a better user interface while retaining the flexible conven-tional replay model of debugging.

A recent work by Lienhard et al.\cite{Lienhard} suggests virtual machine level support for keeping the object flow. It rep-laces every object reference with an alias object which keeps the history of changes to the object reference. In this way, when an object is collected by garbage collector, its track of changes (if it is not referenced by other alias-es) will be also collected. Though this approach incurs less runtime overhead (7 times to 115 times) in comparison to omniscient debuggers, it adds memory overhead. Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program. Moreover, the Lienhard et al. debugger significantly changes the virtual machine, while our approach is a generalization to conditional breakpoints and available debugger infrastructure can be adapted to support it.

\textit{lastChange} functionality does rely on a conventional breakpoint to begin queries, a requirement not shared by full logging solutions.  Here we leverage past experience of developers, but there are also new tools [] to help with this problem in the case of graphical and event based systems.

\section{Conclusions and Future Work}

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{10}
\softraggedright

\bibitem[Bond(2007)]{Bond}
M.D. Bond, N. Nethercote, S.W. Kent, S.Z. Guyer, and K.S. McKinley. \newblock Tracking bad apples: reporting the origin of null and undefined value errors.
\newblock In \emph{22nd annual ACM SIGPLAN conference on Object-oriented programming, systems, languages, and applications(OOPSLA)},
October, 2007.

\bibitem[Boothe(2000)]{Boothe}
B. Boothe. \newblock Efficient algorithms for bidirectional debugging.
\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
June, 2000.

\bibitem[Czyz(2007)]{Czyz}
J.K. Czyz, and B. Jayaraman. \newblock Declarative and visual debugging in Eclipse.
\newblock In \emph{OOPSLA workshop on eclipse technology eXchange},
October, 2007.

\bibitem[Ko(2008)]{Ko}
A.J. Ko, and B.A. Myers. \newblock Debugging reinvented: asking and answering why and why not questions about program behavior.
\newblock In \emph{30th international conference on Software engineering(ICSE)},
May, 2008.

\bibitem[LaToza(2006)]{LaToza}
T.D. LaToza, G. Venolia, and R. DeLine. \newblock Maintaining mental models: a study of developer work habits
\newblock In \emph{28th international conference on Software engineering(ICSE)},
May, 2006.

\bibitem[Lewis(2003)]{Lewis}
B. Lewis, and M. Ducasse. \newblock Using events to debug Java programs backwards in time.
\newblock In \emph{Companion of the 18th annual ACM SIGPLAN conference on Object-oriented programming, systems, languages, and applications(OOPSLA)},
2003.

\bibitem[Lienhard(2008)]{Lienhard}
A. Lienhard, T. G\^{\i}rba, and O. Nierstrasz. \newblock Practical Object-Oriented Back-in-Time Debugging.
\newblock In \emph{22nd European conference on Object-Oriented Programming(ECOOP)},
July, 2008.

\bibitem[Maruyama(2003)]{Maruyama}
K. Maruyama, and T. Kazutaka. \newblock Debugging with Reverse Watchpoint.
\newblock In \emph{Proceedings of the Third International Conference on Quality Software},
2003.

\bibitem[Pothier(2007)]{Pothier}
G. Pothier, \'{E}. Tanter, and J. Piquer. \newblock Scalable omniscient debugging.
\newblock In \emph{22nd annual ACM SIGPLAN conference on Object-oriented programming, systems, languages, and applications(OOPSLA)},
October, 2007.

\end{thebibliography}

\end{document}

### 2010-10-12 trunk/papers/pldi2011/sigplanconf-template.tex

--- 2010-10-12 papers/pldi2011/sigplanconf-template.tex
@@
 The page contains a button (line 40) which shows the \texttt{myObject.myProperty} value.
-Whenever user clicks on the button \texttt{onClick} function is called.
-This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value.
+It is supposed that whenever user clicks on the button, the value of \texttt{myObject.myProperty} and therefore button's label is increased by one.
 Once the page is loaded for the first time the button shows \texttt{1} as the initial value of \texttt{myObject.myProperty}.
-The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears on the button.
+The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears.
 
@@
 \end{verbatim}
-\caption{The buggy javascript code.}
+\caption{The buggy javascript code in a html page.}
 \label{fig:js-code}
@@
 
-To start debugging, the developer sets a abreakpoint on line 22 which is the place button's text is updated.
-Once the button is clicked execution is paused at line 22.
+Once user clicks on the button, \texttt{onClick} function is called.
+This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
+To start debugging, the developer sets a abreakpoint on line 22 and once the button is clicked execution is paused at line 22.
 (Figure ~\ref{fig:example1}) shows the debugger while the execution is paused.
-The developer can examine the program state at the right panel and as it shows the \texttt{myObject.myProperty} value at this point is zero.
-This value is wrong and the developer seeks the last place this value is changed.
+The developer can examine the program state at the right panel and as it shows the \texttt{myObject.myProperty} value at this point is zero which is obviously a wrong value.
+
+To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
+To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
+Even if the developer could sucessfully finish this step (There is no simple way to check it), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
+All this work is useless if an origin was missed in the first step or unsufficient data was collected in the scond step.
+
+In contrast, we propose a high-level function in debugger, \textit{lastChange}, which provides the answer.
 By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}).
@@
 Therefore the right panel just shows the partially collected data.
-If the developer needs some values which are not available in the right panel, debuggers re-executes another time and collects and shows the requested data.
+If the developer needs some values which are not available in the right panel, debugger re-executes another time and collects and shows the requested data.
 
@@
 \section{\textit{lastChange} implementation}
-\textit{lastChange} can be called on two different types of values: An object property or a variable value. We explain each case separately.
+\textit{lastChange} can be called on two different types of values: An object property or a variable value. A variable can be a global, local or closure variable. We explain each case separately.
 

### 2010-10-13 papers/pldi2011/sigplanconf-template.tex

@@
 Backward search from bug symptoms to defects-which cause the bug-is a natural way to debugging.
-However, due to the lack of support for easily bakward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy demands a lot of effort from developers.
+However, due to the lack of support for easily bakward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy-if it is not pracatically impossible-demands a lot of effort from developers.
 A fundumental step in this process is tracking origins to wrong values and any aid in this regard can greatly reduce the complexity of debugging for developers.
@@
 We explain the algorithms behind this functionality.
-As a proof of concept we developed a javascript prototype which adds this feature to a well-known javascript debugger, Firebug.
+
+As a proof of concept we developed \textit{RevNav}, a JavaScript prototype, which adds the \textit{lastChange} feature to Firebug JavaScript debugger.
+Moreover, \textit{RevNav} provides mechanism for automated execution reproduction, and a centralized user interface for all collected results.
 
@@
 It is due to developer to search source files, find the list of possible origings to a wrong value and set breakpoints or insert log statements in a way that covers all possible origins.
+
 The next dilemma is data collection.
@@
 In log-based debugging, developer has to decide about data should be collected when inserts the log statement.
-In this approach developer ends up in dealing with long log files and analyzing huge collected data.
+It is very common that the data developer decided to be collected is insufficient.
+Developer has to change the log statements and re-executes the program another time.
+Once the sufficient data is collected, it still requires analysis and understanding.
+Developer usually ends up in dealing with long log files and analyzing huge collected data.
 
@@
 
-Our contritution in this paper is the algorightm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point.
+Our contribution in this paper is the algorightm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point.
 The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibiltily of the algorithm with an implementation extending the Firebug Javascript debugger.
+We demonstrate the feasibiltily of the algorithm with an implementation extending the Firebug JavaScript debugger.
 
@@
 We illustrate the \textit{lastChange} functionality by a simple example.
-The example demonstrates a buggy javascript code in a html page (Figure ~\ref{fig:js-code}).
+The example demonstrates a buggy JavaScript code in a html page (Figure ~\ref{fig:js-code}).
 The page contains a button (line 40) which shows the \texttt{myObject.myProperty} value.
-Whenever user clicks on the button \texttt{onClick} function is called.
-This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value.
+It is supposed that whenever user clicks on the button, the value of \texttt{myObject.myProperty} and therefore button's label is increased by one.
 Once the page is loaded for the first time the button shows \texttt{1} as the initial value of \texttt{myObject.myProperty}.
-The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears on the button.
+The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears.
 
@@
 \end{verbatim}
-\caption{The buggy javascript code.}
+\caption{The buggy JavaScript code in a html page.}
 \label{fig:js-code}
@@
 
-To start debugging, the developer sets a abreakpoint on line 22 which is the place button's text is updated.
-Once the button is clicked execution is paused at line 22.
+Once user clicks on the button, \texttt{onClick} function is called.
+This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
+To start debugging, the developer sets a abreakpoint on line 22 and once the button is clicked execution is paused at line 22.
 (Figure ~\ref{fig:example1}) shows the debugger while the execution is paused.
-The developer can examine the program state at the right panel and as it shows the \texttt{myObject.myProperty} value at this point is zero.
-This value is wrong and the developer seeks the last place this value is changed.
-By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}).
-Debugger considers the paused point at the breakpoint as the \textit{reproduction point}, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}).
-The program state debugger shows on the right panel belongs to the past.
-Therefore the right panel just shows the partially collected data.
-If the developer needs some values which are not available in the right panel, debuggers re-executes another time and collects and shows the requested data.
+The developer can examine the program state at the right panel and as it shows the \texttt{myObject.myProperty} value at this point is zero which is obviously a wrong value.
 
-Looking at line 29, it seems that something is wrong with \texttt{myCondition.value} which causes line 29 execution.
-The developer examines \texttt{myCondition.value} and it is \texttt{undefined}.
-The next step is to know when this property got this value.
-To do so, the developer runs \textit{lastChange} command on \texttt{myCondition.value} at this point.
-Debugger re-executes the execution and pauses at the reproduction point and shows line 25-the place \texttt{undefined} value is assigned to \texttt{myCondition.value} (Figure ~\ref{fig:example3}).
-Now it is clear that the bug occures because \texttt{oldValue} is \texttt{undefined} once execution reaches line 25.
+To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
+To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
+Even if the developer could sucessfully finish this step (There is no simple way to check it), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
+All this work is useless if an origin was missed in the first step or if the data was collected in the second step is insufficient.
 
@@
 
-As demonstrated in Figure ~\ref{fig:example-points}, the developer examinated three points of execution.
-These points-the history of the search for the defect-are available through the debugger's interface.
-On the top of the left panel in Figure ~\ref{fig:example3} there is an opened list which shows all three examinated points.
-The first one is the breakpoint on line 22, the second one is the point which is the last change of \texttt{myObject.myProperty} before the reaching the breakpoint and finally the last one is the point of execution in which \texttt{myCondition.value} gets the \texttt{undefined} value.
-Moreover, the source lines related to these points are tagged with red-cycle icons.
+In contrast, we propose a high-level function in debugger, \textit{lastChange}, which provides the answer without demanding anymore effort from the developer.
+By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}).
+Debugger considers the paused point at the breakpoint as the \textit{reproduction point}, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}).
+The program state debugger shows on the right panel belongs to the past.
+Therefore the right panel just shows the partially collected data.
+If the developer needs some values which are not available in the right panel, debugger re-executes another time and collects and shows the requested data.
 
@@
 
+Looking at line 29, it seems that something is wrong with \texttt{myCondition.value} which causes line 29 execution.
+The developer examines \texttt{myCondition.value} and it is \texttt{undefined}.
+The next step is to know when this property got this value.
+To do so, the developer runs \textit{lastChange} command on \texttt{myCondition.value} at this point.
+Debugger re-executes the execution and pauses at the reproduction point and shows line 25-the place \texttt{undefined} value is assigned to \texttt{myCondition.value} (Figure ~\ref{fig:example3}).
+Now it is clear that the bug occures because \texttt{oldValue} is \texttt{undefined} once execution reaches line 25.
+
+As demonstrated in Figure ~\ref{fig:example-points}, the developer examinated three points of execution.
+These points-the history of the search for the defect-are available through the debugger's interface.
+On the top of the left panel in Figure ~\ref{fig:example3} there is an opened list which shows all three examinated points.
+The first one is the breakpoint on line 22, the second one is the point which is the last change of \texttt{myObject.myProperty} before the reaching the breakpoint and finally the last one is the point of execution in which \texttt{myCondition.value} gets the \texttt{undefined} value.
+Moreover, the source lines related to these points are tagged with red-cycle icons.
+
 Notice that in our example, \textit{lastChange} combines some aspects of breakpoint and of log-based debugging.
@@
 %---------------------------------------------------------------------------------------------------
-\section{\textit{lastChange} implementation}
-\textit{lastChange} can be called on two different types of values: An object property or a variable value. We explain each case separately.
+\section{\textit{lastChange} Algorithm}
+\textit{lastChange} can be called on two different types of values: An object property or a variable value. A variable can be a global, local or closure variable. We explain each case separately.
 
 \subsection{\textit{lastChange} on object propery}
+
 At the beginning, we assume that every object has a unique id.
 Moreover, we assume that there is a special watchpoint, \textit{property watchpoint}, that can be set on a property name \texttt{foo} and whenever property \texttt{foo} in any object changes this watchpoint hits.
-We know that none of these assumptions is true in javascript.
-We discuss this issue later in traking object creation.
+We know that none of these assumptions is true in JavaScript.
+We discuss this issue later in tracking object creation.
 
@@
 Whenever the property watchpoint hits, debugger keeps the object id and stack frame locations.
-Whenever the execution reaches the same reproduction point it looks at the list of all changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
+Whenever the execution reaches the reproduction point it looks at the list of all changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
 
@@
 \subsection{\textit{lastChange} on variable} 
-Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first finds the scope the variable comes from.
-Consider that in javascript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible.
-The outer scopes are regualr javascript objects or closure scopes.
+Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first determines the variable's scope as follows:  Consider that in JavaScript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible.
+The outer scopes are regualr JavaScript objects or closure scopes.
 The first group are usually created by calling \texttt{with()} function.
@@
 \end{verbatim}
-\caption{Sample javascript code demonstrating closure variables.}
+\caption{Sample JavaScript code demonstrating closure variables.}
 \label{fig:js-closure}
@@
 %---------------------------------------------------------------------------------------------------
-\section{Javascript implementation}
-The javascript prototype is implemented as an extension to Firebug[] javasrcipt debugger.
+\section{JavaScript implementation}
+The JavaScript prototype is implemented as an extension to Firebug[] javasrcipt debugger.
 
@@
 Now we discuss two mentioned assumptions.
-In the standard javascript every object has a \texttt{watch()} function which receives two parameters, a property name and another function as a hook.
+In the standard JavaScript every object has a \texttt{watch()} function which receives two parameters, a property name and another function as a hook.
 Whenever the property with the given name changes the hook function is called.
@@
 However, at the beginning of re-execution there is no object available.
-To solve this issue we use a feature in Firefox javascript engine, setting a flag gives us the place the object created (e.g., myFile.js, line 24).
+To solve this issue we use a feature in Firefox JavaScript engine, setting a flag gives us the place the object created (e.g., myFile.js, line 24).
 Though this is a limited data it can help us to get a reference to the object once it is created.

### 2010-10-13 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 Backward search from bug symptoms to defects-which cause the bug-is a natural way to debugging.
-However, due to the lack of support for easily bakward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy demands a lot of effort from developers.
-A fundumental step in this process is tracking origins to wrong values and any aid in this regard can greatly reduce the complexity of debugging for developers.
+However, due to the lack of support for easily bakward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy-if it is not pracatically impossible-demands a lot of effort from developers.
+Tracking origins to wrong values is a fundumental step in this process and any aid in this regard can greatly reduce the complexity of debugging for developers.
 
-In this paper we present a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the point.
-The only prerequisite for \textit{lastChange} functionality is bug reproduciblity (i.e., there is a test case which reproduces the bug).
-We explain the algorithms behind this functionality.
-As a proof of concept we developed a javascript prototype which adds this feature to a well-known javascript debugger, Firebug.
+To attack the mentioned problem, we propose a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the located point.
+While \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires \textit{bug reproduciblity} (i.e., a test case is available which reproduces the bug).
+
+As a proof of concept we developed \textit{RevNav}, a JavaScript prototype, which adds the \textit{lastChange} feature to Firebug JavaScript debugger.
+Moreover, \textit{RevNav} provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
 
@@
 According to \cite{LaToza}, developers spend about fifty percent of their time debugging.
-Therefore, every improvement to debugging techniques and tools can considerably save developers' time and improve programs' quiality.
+Therefore, every improvement to debugging techniques and tools can considerably save developers' time and improve programs' quality.
 
@@
 Debugger reproduces the buggy execution and collects limited data and once the execution reaches the same place (i.e., the same breakpoint hit), call it \textit{reproduction point}, it pauses the execution, analyzes the collected data and shows the location of the last change to the developer.
-Developer can also examine the program state at the located point of execution, and asks for a new \textit{lastChange} at this point.
+Developer can also examine the program state at the located point of execution, and ask for a new \textit{lastChange} at this point.
 
-Our contritution in this paper is the algorightm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point.
+Our contribution in this paper is the algorightm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point.
 The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibiltily of the algorithm with an implementation extending the Firebug Javascript debugger.
+We demonstrate the feasibiltily of the algorithm with an implementation extending the Firebug JavaScript debugger.
 
@@
 We illustrate the \textit{lastChange} functionality by a simple example.
-The example demonstrates a buggy javascript code in a html page (Figure ~\ref{fig:js-code}).
+The example demonstrates a buggy JavaScript code in a html page (Figure ~\ref{fig:js-code}).
 The page contains a button (line 40) which shows the \texttt{myObject.myProperty} value.
@@
 \end{verbatim}
-\caption{The buggy javascript code in a html page.}
+\caption{The buggy JavaScript code in a html page.}
 \label{fig:js-code}
@@
 Even if the developer could sucessfully finish this step (There is no simple way to check it), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
-All this work is useless if an origin was missed in the first step or unsufficient data was collected in the scond step.
-
-In contrast, we propose a high-level function in debugger, \textit{lastChange}, which provides the answer.
-By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}).
-Debugger considers the paused point at the breakpoint as the \textit{reproduction point}, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}).
-The program state debugger shows on the right panel belongs to the past.
-Therefore the right panel just shows the partially collected data.
-If the developer needs some values which are not available in the right panel, debugger re-executes another time and collects and shows the requested data.
-
-Looking at line 29, it seems that something is wrong with \texttt{myCondition.value} which causes line 29 execution.
-The developer examines \texttt{myCondition.value} and it is \texttt{undefined}.
-The next step is to know when this property got this value.
-To do so, the developer runs \textit{lastChange} command on \texttt{myCondition.value} at this point.
-Debugger re-executes the execution and pauses at the reproduction point and shows line 25-the place \texttt{undefined} value is assigned to \texttt{myCondition.value} (Figure ~\ref{fig:example3}).
-Now it is clear that the bug occures because \texttt{oldValue} is \texttt{undefined} once execution reaches line 25.
+All this work is useless if an origin was missed in the first step or if the data was collected in the second step is insufficient.
 
@@
 %---------------------------------------------------------------------------------------------------
-\section{\textit{lastChange} implementation}
+\section{\textit{lastChange} Algorithm}
 \textit{lastChange} can be called on two different types of values: An object property or a variable value. A variable can be a global, local or closure variable. We explain each case separately.
@@
 \subsection{\textit{lastChange} on object propery}
+
 At the beginning, we assume that every object has a unique id.
 Moreover, we assume that there is a special watchpoint, \textit{property watchpoint}, that can be set on a property name \texttt{foo} and whenever property \texttt{foo} in any object changes this watchpoint hits.
-We know that none of these assumptions is true in javascript.
-We discuss this issue later in traking object creation.
+We know that none of these assumptions is true in JavaScript.
+We discuss this issue later in tracking object creation.
 

### 2010-10-13 papers/pldi2011/sigplanconf-template.tex

@@
 However, due to the lack of support for easily bakward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy-if it is not pracatically impossible-demands a lot of effort from developers.
-A fundumental step in this process is tracking origins to wrong values and any aid in this regard can greatly reduce the complexity of debugging for developers.
+Tracking origins to wrong values is a fundumental step in this process and any aid in this regard can greatly reduce the complexity of debugging for developers.
 
-In this paper we present a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the point.
-The only prerequisite for \textit{lastChange} functionality is bug reproduciblity (i.e., there is a test case which reproduces the bug).
-We explain the algorithms behind this functionality.
+To attack the mentioned problem, we propose a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the located point.
+While \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires \textit{bug reproduciblity} (i.e., a test case is available which reproduces the bug).
 
 As a proof of concept we developed \textit{RevNav}, a JavaScript prototype, which adds the \textit{lastChange} feature to Firebug JavaScript debugger.
-Moreover, \textit{RevNav} provides mechanism for automated execution reproduction, and a centralized user interface for all collected results.
+Moreover, \textit{RevNav} provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
 
@@
 Debugger reproduces the buggy execution and collects limited data and once the execution reaches the same place (i.e., the same breakpoint hit), call it \textit{reproduction point}, it pauses the execution, analyzes the collected data and shows the location of the last change to the developer.
-Developer can also examine the program state at the located point of execution, and asks for a new \textit{lastChange} at this point.
+Developer can also examine the program state at the located point of execution, and ask for a new \textit{lastChange} at this point.
 
@@
 By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}).
-Debugger considers the paused point at the breakpoint as the \textit{reproduction point}, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}).
+Debugger considers the paused point at the breakpoint as the reproduction point, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}).
 The program state debugger shows on the right panel belongs to the past.
@@
 \section{\textit{lastChange} Algorithm}
-\textit{lastChange} can be called on two different types of values: An object property or a variable value. A variable can be a global, local or closure variable. We explain each case separately.
+
+The \textit{lastChange} algorithm is based on program re-execution.
+\textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld.
+Like the introductory example, it can be specified by a [conditional] breakpoint.
+\textit{lastChange} can be called on two different types of values: An object property or a variable value.
+In JavaScript, every available variable in a frame comes from one of the scopes in the current scope chain.
+There are five different scopes: global, local, with, catch, closure.
+We explain each case separately.
 
 \subsection{\textit{lastChange} on object propery}
+To simplify the algorithm explanation and avoid technical details, we assume two basic operations and postpone implementation details to the next section.
+The first opertion is \texttt{objectId()} which gets an object and returns an integer as its identifier.
+This identifier is unique for every object during one execution.
+The second operation is \texttt{setPropertyChangeHook()} which gets function as the hook and a string as the property name like \texttt{foo}.
+Whenever property \texttt{foo} in any object changes the hook will be called.
+The hook function receives a reference to the owner of \texttt{foo}.
 
-At the beginning, we assume that every object has a unique id.
-Moreover, we assume that there is a special watchpoint, \textit{property watchpoint}, that can be set on a property name \texttt{foo} and whenever property \texttt{foo} in any object changes this watchpoint hits.
-We know that none of these assumptions is true in JavaScript.
-We discuss this issue later in tracking object creation.
-
-Once developer asks for the last change of \texttt{bar.foo} at a reproduction point, debugger sets a property watchpoint on \texttt{foo} and  re-executes the program.
-Whenever the property watchpoint hits, debugger keeps the object id and stack frame locations.
+Once developer asks for the last change of \texttt{bar.foo} at the reproduction point, debugger calls \texttt{setPropertyChangeHook()} with \texttt{foo} as the property name and re-executes the program.
+Whenever \texttt{foo} changes and the hook function is called, debugger first calls \texttt{objectID()} on the \texttt{foo} owner object.
+Then it stores owner id and stack frame locations.
 Whenever the execution reaches the reproduction point it looks at the list of all changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).

### 2010-10-13 papers/pldi2011/sigplanconf-template.tex

@@
 Then it stores owner id and stack frame locations.
-Whenever the execution reaches the reproduction point it looks at the list of all changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
+The reason we keep object id instead of a reference to the object itself is to let garbage collector destroys dead objects.
+Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
 

### 2010-10-13 papers/pldi2011/sigplanconf-template.tex

@@
 In JavaScript, every available variable in a frame comes from one of the scopes in the current scope chain.
-There are five different scopes: global, local, with, catch, closure.
+There are five different scope types: global, local, with, catch, closure.
 We explain each case separately.
@@
 \subsection{\textit{lastChange} on variable} 
-Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first determines the variable's scope as follows:  Consider that in JavaScript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible.
-The outer scopes are regualr JavaScript objects or closure scopes.
-The first group are usually created by calling \texttt{with()} function.
-The second group are created once a function is called.
-Therefore, there are theree cases for the escope of a variable, the current scope, an outer scope regular object or an outer scope clousure scope.
+Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first determines the variable's scope as follows: it iterates over the scopes in the scope chain and the first scope which has a variable with the same name is the variable's scope.
+Consider that in JavaScript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible.
+Among five scope types, global scopes and with scopes-scopes which are created by calling \texttt{with()} function-are regular JavaScript objects.
+Debugger treats the case where variable's scope is global or with, like \textit{lastChange} on an object property.
 
-If the variable belongs to an outer scope regular object, debugger treats the case like \textit{lastChange} on an object property.
-In the other two cases, debugger sets breakpoints on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
+A closure scope is created once a function is called.
+In this case, debugger sets breakpoints on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
 For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var2} is requested by the developer, two breakpoints on lines 22 and 23 will be set, but if the execution is paused at line 19, four breakpoints on lines 11, 12, 16, and 18.

### 2010-10-14 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibiltily of the algorithm with an implementation extending the Firebug JavaScript debugger.
+We demonstrate the feasibiltily of the algorithm with \textit{RevNav}, an implementation extending the Firebug JavaScript debugger.
+\textit{RevNav} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
 
+The rest of the paper is organized as follows.
+First, we demonstrate the \textit{lastChange} usage on a simple example with the comparison to breakpoint debugging.
+Section 3 presents \textit{lastChange} algorithm.
+In section 4, we explain the details of the JavaScript prototype implementation.
 %\begin{enumerate}
@@
 The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears.
+
+Once user clicks on the button, \texttt{onClick} function (line 13) is called.
+This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
+To start debugging, the developer sets a abreakpoint on line 22 and once the button is clicked execution is paused at line 22.
+(Figure ~\ref{fig:example1}) shows the debugger while the execution is paused.
+The developer can examine the program state at the right panel and as it shows, the \texttt{myObject.myProperty} value at this point is zero which is obviously a wrong value.
+
+To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
+To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
+Even if the developer could sucessfully finish this step (There is no simple way to check it), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
+All this work is useless if an origin was missed in the first step or if the data was collected in the second step is insufficient.
 
@@
 
-Once user clicks on the button, \texttt{onClick} function is called.
-This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
-To start debugging, the developer sets a abreakpoint on line 22 and once the button is clicked execution is paused at line 22.
-(Figure ~\ref{fig:example1}) shows the debugger while the execution is paused.
-The developer can examine the program state at the right panel and as it shows the \texttt{myObject.myProperty} value at this point is zero which is obviously a wrong value.
-
-To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
-To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
-Even if the developer could sucessfully finish this step (There is no simple way to check it), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
-All this work is useless if an origin was missed in the first step or if the data was collected in the second step is insufficient.
-
 \begin{figure}[htp]
@@
 As demonstrated in Figure ~\ref{fig:example-points}, the developer examinated three points of execution.
+Excepting the first point which debugger pause execution at that point, the second and third points are in the past and are shown by dotted line.
 These points-the history of the search for the defect-are available through the debugger's interface.
@@
 We can't halt the program at \textit{lastChange} because we don't know which is the last one until we return to the original breakpoint.
+In section 5 we discuss about the possibility of pausing at \textit{lastChange} results.
 
@@
 \section{\textit{lastChange} Algorithm}
-\textit{lastChange} can be called on two different types of values: An object property or a variable value. A variable can be a global, local or closure variable. We explain each case separately.
+
+The \textit{lastChange} algorithm is based on program re-execution.
+Once developer asks for the \textit{lastChange} of a value, debugger re-executes the program, collects limited data and shows the result.
+\textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld.
+Like the introductory example, it can be defined by a [conditional] breakpoint.
+\textit{lastChange} can be called on two different types of values: An object property or a variable value.
+In JavaScript, every available variable in a frame comes from one of the scopes in the current scope chain.
+There are five different scope types: global, local, with, catch, closure.
+We explain each case separately.
 
 \subsection{\textit{lastChange} on object propery}
+To simplify the algorithm explanation and avoid technical details, we assume two basic operations and postpone implementation details to the next section.
+The first opertion is \texttt{objectId()} which gets an object and returns an integer as its identifier.
+This identifier is unique for every object during one execution.
+The second operation is \texttt{setPropertyChangeHook()} which gets function as the hook and a string as the property name like \texttt{foo}.
+Whenever property \texttt{foo} in any object changes the hook will be called.
+The hook function receives a reference to the owner of \texttt{foo}.
 
-At the beginning, we assume that every object has a unique id.
-Moreover, we assume that there is a special watchpoint, \textit{property watchpoint}, that can be set on a property name \texttt{foo} and whenever property \texttt{foo} in any object changes this watchpoint hits.
-We know that none of these assumptions is true in JavaScript.
-We discuss this issue later in tracking object creation.
-
-Once developer asks for the last change of \texttt{bar.foo} at a reproduction point, debugger sets a property watchpoint on \texttt{foo} and  re-executes the program.
-Whenever the property watchpoint hits, debugger keeps the object id and stack frame locations.
-Whenever the execution reaches the reproduction point it looks at the list of all changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
+Once developer asks for the last change of \texttt{bar.foo} at the reproduction point, debugger calls \texttt{setPropertyChangeHook()} with \texttt{foo} as the property name and re-executes the program.
+Whenever \texttt{foo} changes and the hook function is called, debugger first calls \texttt{objectID()} on the \texttt{foo} owner object.
+Then it stores owner id and stack frame locations.
+The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
+Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
 
@@
 \subsection{\textit{lastChange} on variable} 
-Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first determines the variable's scope as follows:  Consider that in JavaScript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible.
-The outer scopes are regualr JavaScript objects or closure scopes.
-The first group are usually created by calling \texttt{with()} function.
-The second group are created once a function is called.
-Therefore, there are theree cases for the escope of a variable, the current scope, an outer scope regular object or an outer scope clousure scope.
+In JavaScript, every frame has a scope chain and every available variable in the frame comes from one of the scopes in the frame's scope chain.
+Once developer asks for the last change of variable \texttt{foo} at the reproduction point, debugger first determines the variable's scope as follows: it iterates over the scopes in the scope chain and the first scope which has a variable with the same name is the variable's scope.
+There are five different scope types: local, global, \texttt{with}, closure, \texttt{catch}.
+We explain each case separately.
 
-If the variable belongs to an outer scope regular object, debugger treats the case like \textit{lastChange} on an object property.
-In the other two cases, debugger sets breakpoints on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
-For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var2} is requested by the developer, two breakpoints on lines 22 and 23 will be set, but if the execution is paused at line 19, four breakpoints on lines 11, 12, 16, and 18.
+\subsubsection{global and \texttt{with} scopes}
+Global scope is the the most outer scope in the scope chain and it also refers as global object.
+This scope is a regular JavaScript object and therefore every global variable is a property of global object.
+Similar to global scope, \texttt{with} scopes are also regular objects.
+A \texttt{with} scope is created by a \texttt{with()} block with an object as the parameter.
+Every property of passed object is available inside the block as a variable.
+Debugger treats the case where variable's scope is global or \texttt{with}, like \textit{lastChange} on an object property.
+
+\subsubsection{local, clousure and \texttt{catch} scopes}
+local scope refers to the top scope in the scope chain.
+Clousure scope refers to the scope which is created once a function is defined.
+Catch scope is the scope created by try-catch blocks and contains the exception variable.
+These objects are not necessarily regular JavaScript objects.
+Therefore to track changes to a variable in these scopes we need a new strategy.
+
+A variables in these scopes can only be changed by the code which is included in the it's definition block.
+Therefore it is only enough to take care only about the lines that a variable is assinged a new value.
+The same fact is also true about \texttt{catch} and local scopes.
+Debugger puts hooks in on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
+For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var1} is requested by the developer, two hooks on lines 22 and 23 will be set, but if the execution is paused at line 19, four hooks on lines 11, 12, 16, and 18.
+The reason is that \texttt{var1} in \texttt{firstChild} is a closure variable but in \texttt{secondChild} is a local variable.
 
@@
 \begin{verbatim}
-10  function parent(var1){
-11    var var2;
-12    var2 = 1;
-13    function myfun(var3){
-14      var var4;
-15      var4 = {...}
-16      var2 = var4;
-17      function firstChild(var5){
-18        var2 = 5;
-19        var4 = 5;
+10  function parent(arg1){
+11    var var1;
+12    var1 = 0;
+13    function myfun(arg2){
+14      var var2;
+15      var2 = {...}
+16      var1 = var2;
+17      function firstChild(arg3){
+18        var1 = 1;
+19        var2 = 1;
 20      }  
-21      function secondChild(var6){
-22       	var var2;
-23        var2 = 5			      
-24        var4 = 5;	
+21      function secondChild(arg4){
+22       	var var1;
+23        var1 = 2			      
+24        var2 = 2;	
 25      }
 26    }  
-23  }    
+27  }    
 \end{verbatim}
@@
 
-Everytime one of the breakpoints hit a new event is inserted to the list of events.
+Everytime one of the hook hit a new event is inserted to the list of events.
 To separate irrelvant event from each other, we use a special variable \texttt{\_scopeId}.
-If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created in the scope.
-This is specially needed in case of recursive calls.
-Figure Figure ~\ref{fig:recursive} shows changes to a the same variable \texttt{x} but in different scopes.
-alling \textit{lastChange(x)} at point B should return point A.
+If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created by \texttt{eval()} function in the scope.
+Figure ~\ref{fig:recursive} demonstrates one case that scope id is necessary for identifying the right answer.
+In thiss case the same variable \texttt{x} is changed several times but in different scopes due to recursive calls.
+Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
 
@@
         f was called 
-          x changes;
-    //B
+          x changes; //C
+    //C
 

### 2010-10-14 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 \includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
-\caption{The list of \texttt{foo} changes and \texttt{bar} id which identifies the last change of \texttt{bar.foo} in the history of events.}
+\caption{The list of property \texttt{foo} changes and \texttt{bar} id which identifies the last change of \texttt{bar.foo} in the history of events.}
 \label{fig:foo-changes1}
@@
 
-\subsubsection{local, clousure and \texttt{catch} scopes}
+\subsubsection{local, closure and \texttt{catch} scopes}
 local scope refers to the top scope in the scope chain.
@@
 Therefore to track changes to a variable in these scopes we need a new strategy.
-
-A variables in these scopes can only be changed by the code which is included in the it's definition block.
-Therefore it is only enough to take care only about the lines that a variable is assinged a new value.
-The same fact is also true about \texttt{catch} and local scopes.
-Debugger puts hooks in on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
-For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var1} is requested by the developer, two hooks on lines 22 and 23 will be set, but if the execution is paused at line 19, four hooks on lines 11, 12, 16, and 18.
-The reason is that \texttt{var1} in \texttt{firstChild} is a closure variable but in \texttt{secondChild} is a local variable.
 
@@
 
-Everytime one of the hook hit a new event is inserted to the list of events.
-To separate irrelvant event from each other, we use a special variable \texttt{\_scopeId}.
-If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created by \texttt{eval()} function in the scope.
-Figure ~\ref{fig:recursive} demonstrates one case that scope id is necessary for identifying the right answer.
-In thiss case the same variable \texttt{x} is changed several times but in different scopes due to recursive calls.
-Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
+A variables in these scopes can only be changed by the code which is included in the it's definition block.
+Therefore it is only enough to take care only about the lines that a variable is assinged a new value.
+The same fact is also true about \texttt{catch} and local scopes.
+Debugger puts hooks in on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
+For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var1} is requested by the developer, two hooks on lines 22 and 23 will be set, but if the execution is paused at line 19, four hooks on lines 11, 12, 16, and 18.
+The reason is that \texttt{var1} in \texttt{firstChild} is a closure variable but in \texttt{secondChild} is a local variable.
 
@@
 
+\begin{figure}[htp]
+\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
+\caption{The list of variable \texttt{foo} changes and the \texttt{foo}'s scope id at the reproduction point which identifies the answer.}
+\label{fig:foo-changes2}
+\end{figure}
+
+Everytime one of the hook hit a new event is inserted to the list of events.
+To separate irrelvant event from each other, we use a special variable \texttt{\_scopeId}.
+If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created by \texttt{eval()} function in the scope.
+For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
+Consider that even in the case of closure scopes, \texttt{\_scopeId} is set when the variable first defined and the variable's scope is still local.
+Figure ~\ref{fig:recursive} demonstrates one case that scope id is necessary for identifying the right answer.
+In thiss case the same variable \texttt{x} is changed several times but in different scopes due to recursive calls.
+Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
+
 \subsection{\textit{lastChange} on \textit{lastChange}}
@@
 
+\begin{figure}[htp]
+\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
+\caption{The list of events stored for locating \textit{lastChange} of \texttt{bar.x} (point B) at the reproduction point and \texttt{baz.y} at point B.}
+\label{fig:lastchange-lastchange}
+\end{figure}
 %---------------------------------------------------------------------------------------------------

### 2010-10-15 papers/pldi2011/sigplanconf-template.tex

@@
 The \textit{lastChange} algorithm is based on program re-execution.
+Once developer asks for the \textit{lastChange} of a value, debugger re-executes the program, collects limited data and shows the result.
 \textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld.
-Like the introductory example, it can be specified by a [conditional] breakpoint.
+Like the introductory example, it can be defined by a [conditional] breakpoint.
 \textit{lastChange} can be called on two different types of values: An object property or a variable value.
@@
 Then it stores owner id and stack frame locations.
-The reason we keep object id instead of a reference to the object itself is to let garbage collector destroys dead objects.
+The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
 Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
@@
 \subsection{\textit{lastChange} on variable} 
-Once developer asks for the last change of variable \texttt{foo} at a reproduction point, debugger first determines the variable's scope as follows: it iterates over the scopes in the scope chain and the first scope which has a variable with the same name is the variable's scope.
-Consider that in JavaScript, available variables are not resricted to local varialbes, but all variables in outer scopes are also accessible.
-Among five scope types, global scopes and with scopes-scopes which are created by calling \texttt{with()} function-are regular JavaScript objects.
-Debugger treats the case where variable's scope is global or with, like \textit{lastChange} on an object property.
+In JavaScript, every frame has a scope chain and every available variable in the frame comes from one of the scopes in the frame's scope chain.
+Once developer asks for the last change of variable \texttt{foo} at the reproduction point, debugger first determines the variable's scope as follows: it iterates over the scopes in the scope chain and the first scope which has a variable with the same name is the variable's scope.
+There are five different scope types: local, global, \texttt{with}, closure, \texttt{catch}.
+We explain each case separately.
 
-A closure scope is created once a function is called.
-In this case, debugger sets breakpoints on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
-For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var2} is requested by the developer, two breakpoints on lines 22 and 23 will be set, but if the execution is paused at line 19, four breakpoints on lines 11, 12, 16, and 18.
+\subsubsection{global and \texttt{with} scopes}
+Global scope is the the most outer scope in the scope chain and it also refers as global object.
+This scope is a regular JavaScript object and therefore every global variable is a property of global object.
+Similar to global scope, \texttt{with} scopes are also regular objects.
+A \texttt{with} scope is created by a \texttt{with()} block with an object as the parameter.
+Every property of passed object is available inside the block as a variable.
+Debugger treats the case where variable's scope is global or \texttt{with}, like \textit{lastChange} on an object property.
+
+\subsubsection{local, closure and \texttt{catch} scopes}
+local scope refers to the top scope in the scope chain.
+Clousure scope refers to the scope which is created once a function is defined.
+Catch scope is the scope created by try-catch blocks and contains the exception variable.
+These objects are not necessarily regular JavaScript objects.
+Therefore to track changes to a variable in these scopes we need a new strategy.
 
@@
 
-Everytime one of the breakpoints hit a new event is inserted to the list of events.
-To separate irrelvant event from each other, we use a special variable \texttt{\_scopeId}.
-If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created in the scope.
-This is specially needed in case of recursive calls.
-Figure Figure ~\ref{fig:recursive} shows changes to a the same variable \texttt{x} but in different scopes.
-alling \textit{lastChange(x)} at point B should return point A.
+A variables in these scopes can only be changed by the code which is included in the it's definition block.
+Therefore it is only enough to take care only about the lines that a variable is assinged a new value.
+The same fact is also true about \texttt{catch} and local scopes.
+Debugger puts hooks in on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
+For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var1} is requested by the developer, two hooks on lines 22 and 23 will be set, but if the execution is paused at line 19, four hooks on lines 11, 12, 16, and 18.
+The reason is that \texttt{var1} in \texttt{firstChild} is a closure variable but in \texttt{secondChild} is a local variable.
 
@@
 
+\begin{figure}[htp]
+\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
+\caption{The list of variable \texttt{foo} changes and the \texttt{foo}'s scope id at the reproduction point which identifies the answer.}
+\label{fig:foo-changes2}
+\end{figure}
+
+Everytime one of the hook hit a new event is inserted to the list of events.
+To separate irrelvant event from each other, we use a special variable \texttt{\_scopeId}.
+If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created by \texttt{eval()} function in the scope.
+For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
+Consider that even in the case of closure scopes, \texttt{\_scopeId} is set when the variable first defined and the variable's scope is still local.
+Figure ~\ref{fig:recursive} demonstrates one case that scope id is necessary for identifying the right answer.
+In thiss case the same variable \texttt{x} is changed several times but in different scopes due to recursive calls.
+Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
+
 \subsection{\textit{lastChange} on \textit{lastChange}}
-Once the developer asks for the first \textit{lastChange} all program state is available to the debugger.
-But the next \textit{lastChange} calls are asked over collected data.
-For example, debugger needs object id for the second \textit{lastChange} and this data should be collected.
-To do so, debugger does a data dependency analysis between points which gives a list of items should be collected at every point.
+The algorithm we explained so far needs an enhancement to support longer sequence of \textit{lastChange}s. We explain first the issue and then the solution. Consider the following points:
+
+\begin{center}
+\textit{
+ point A : the reproduction point \\
+ point B : lastChange(A, bar.x) \\
+ point C : lastChange(B, baz.y) 
+ }
+ \end{center}
+According the algorithm explained in the previous section none of the points B and C can be identified before reaching point A.
+Therefore, all \texttt{x} changes for piont B and all \texttt{y} changes for point C are stored.
+Once the execution reaches point A, and the exact \texttt{bar} id reveals, point B can be identified among the items in the history of \texttt{x} changes.
+The problem arises in recognizing point C.
+To recognize point C, we need \texttt{baz} id at point B, but B is a past program state, and \texttt{baz} id has not been collected at this point.
+
+\begin{figure}[htp]
+\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
+\caption{The list of events stored for locating \textit{lastChange} of \texttt{bar.x} (point B) at the reproduction point and \texttt{baz.y} at point B.}
+\label{fig:lastchange-lastchange}
+\end{figure}
+
+To address this issue, debugger does a dependency analysis between all \textit{lastChange} queries and computes the additional data needs to be collected at each point.
+For example in the mentioned case, \texttt{baz} id- if it is available- should be collected at all points \texttt{x} changes.
+Having this additional data, locating point C, using the \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
 

### 2010-10-15 papers/pldi2011/sigplanconf-template.tex

@@
 
-To attack the mentioned problem, we propose a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the located point.
-While \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires \textit{bug reproduciblity} (i.e., a test case is available which reproduces the bug).
+To address this problem, we propose a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the located point.
+Although \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires bug reproduction by re-executions.
+In other words \textit{bug reproduciblity} (i.e., a test case is available which reproduces the bug) is the only prerequisite for \textit{lastChange} functinality.
 
-As a proof of concept we developed \textit{RevNav}, a JavaScript prototype, which adds the \textit{lastChange} feature to Firebug JavaScript debugger.
-Moreover, \textit{RevNav} provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
+As a proof of concept, we developed \textit{RevNav}, a prototype which enhances Firebug JavaScript debugger with \textit{lastChange} feature.
+Moreover, \textit{RevNav} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
 
-% how we buil it on breakpoint technology
 \end{abstract}
@@
 A common strategy for locating defects is starting from bug symptoms and backward movement by following the origings to wrong values.
-While this strategy seems straight-forward and effective, applying this strategy using traditional methods is complicated.
+While this strategy seems straightforward and effective, applying this strategy using traditional methods is complicated.
 There are two traditional approaches to debugging, breakpoint-based and log-based debugging.
@@
 The next dilemma is data collection.
-In breakpoint debugging, developer has to memorize values or collect data manually at every breakpoint hit and in cases that there are many breakpoint hits, this becomes a tedious task.
-In log-based debugging, developer has to decide about data should be collected when inserts the log statement.
-It is very common that the data developer decided to be collected is insufficient.
-Developer has to change the log statements and re-executes the program another time.
-Once the sufficient data is collected, it still requires analysis and understanding.
-Developer usually ends up in dealing with long log files and analyzing huge collected data.
+In breakpoint debugging, developer has to memorize values or manually collect data at every breakpoint hit.
+As the number of breakpoint hits increases, the process of checking the program state, collecting data and resuming the execution becomes cumbersome.
+While in breakpoint-based debugging, the whole program state is available to developer, in log-based debugging, developer has to decide about data should be collected when inserts the log statement.
+It is very common that developer has to repeat this step several times due to insufficient collected data.
+Once the adequate data is collected, it still requires analysis and understanding.
+Developers usually end up in dealing with long log files and analyzing huge collected data.
 
@@
 The example demonstrates a buggy JavaScript code in a html page (Figure ~\ref{fig:js-code}).
-The page contains a button (line 40) which shows the \texttt{myObject.myProperty} value.
+The page contains a button (line 40) which shows the value of \texttt{myObject.myProperty}.
 It is supposed that whenever user clicks on the button, the value of \texttt{myObject.myProperty} and therefore button's label is increased by one.
@@
 This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
-To start debugging, the developer sets a abreakpoint on line 22 and once the button is clicked execution is paused at line 22.
-(Figure ~\ref{fig:example1}) shows the debugger while the execution is paused.
+To start debugging, the developer sets a breakpoint on line 22 and once the button is clicked execution is paused at line 22.
+Figure ~\ref{fig:example1} shows the debugger while the execution is paused.
 The developer can examine the program state at the right panel and as it shows, the \texttt{myObject.myProperty} value at this point is zero which is obviously a wrong value.
@@
 To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
-Even if the developer could sucessfully finish this step (There is no simple way to check it), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
-All this work is useless if an origin was missed in the first step or if the data was collected in the second step is insufficient.
+Having the fact that an object and property can be accessed and changed through different names and methods, we realize that the difficulty of this task.
+Even if the developer could sucessfully finish this step (There is no simple way to check it!), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
+All this work should be repeated if an origin was missed in the first step or if the data was collected in the second step is insufficient.
 

### 2010-10-18 papers/pldi2011/sigplanconf-template.tex

@@
 
-As a proof of concept, we developed \textit{RevNav}, a prototype which enhances Firebug JavaScript debugger with \textit{lastChange} feature.
-Moreover, \textit{RevNav} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
+As a proof of concept, we developed \textit{Querypoint}, a prototype which enhances Firebug JavaScript debugger with \textit{lastChange} feature.
+Moreover, \textit{Querypoint} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
 
@@
 The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibiltily of the algorithm with \textit{RevNav}, an implementation extending the Firebug JavaScript debugger.
-\textit{RevNav} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
+We demonstrate the feasibiltily of the algorithm with \textit{Querypoint}, an implementation extending the Firebug JavaScript debugger.
+\textit{Querypoint} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
 
@@
 In section 4, we explain the details of the JavaScript prototype implementation.
-%\begin{enumerate}
-%/\item The evaluation of \textit{lastChange} implementation.
-
-%\end{enumerate}
 
@@
 To start debugging, the developer sets a breakpoint on line 22 and once the button is clicked execution is paused at line 22.
-Figure ~\ref{fig:example1} shows the debugger while the execution is paused.
-The developer can examine the program state at the right panel and as it shows, the \texttt{myObject.myProperty} value at this point is zero which is obviously a wrong value.
-
-To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
-To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
-Having the fact that an object and property can be accessed and changed through different names and methods, we realize that the difficulty of this task.
-Even if the developer could sucessfully finish this step (There is no simple way to check it!), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
-All this work should be repeated if an origin was missed in the first step or if the data was collected in the second step is insufficient.
+Figure ~\ref{fig:example1} shows the Firebug debugger while the execution is paused.
+Firebug has several panels (e.g., html, css, script, dom, etc.) that each one demonstrate one aspect of JavaScript execution.
+The script panel contains the list of all loaded source files and regular debugging facilities such as setting breakpoints and stepping.
+The right panel in the script panel shows the program state and developer can examine object and variable values.
+In our case, the \texttt{myObject.myProperty} value at the paused point is zero which is obviously a wrong value.
 
@@
 
+To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
+To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
+Having the fact that an object and property can be accessed and changed through different names and methods, we realize that the difficulty of this task.
+Even if the developer could sucessfully finish this step (There is no simple way to check it!), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
+All this work should be repeated if an origin was missed in the first step or if the data was collected in the second step is insufficient.
+
 \begin{figure}[htp]
 \includegraphics{5-example-points.jpg}
-\caption{The examinated points.}
+\caption{The examinated points before locating the defect.}
 \label{fig:example-points}
@@
 
-\subfigure[The execution is paused at line 22 by an ordinary breakpoint.]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.19\textheight]{1-bp22.jpg}}
+\subfigure[A view of Firebug JavaScript debugger.
+The selected script panel, presents all loaded JavaScript code.
+Developer has access to any loaded source file and can set breakpoints on lines.
+In this figure, the execution is paused at line 22 by a regular breakpoint.
+The panel at the right site shows the program state at the paused point.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.19\textheight]{1-bp22.jpg}}
 
-\subfigure[\textit{lastChange} command.]{\label{fig:example2}\includegraphics[width=1.0\textwidth, height=.19\textheight]{2-bp22-lastChange.jpg}}
+\subfigure[Developer can query \textit{lastChange} on a value by right clicking on the value.]{\label{fig:example2}\includegraphics[width=1.0\textwidth, height=.19\textheight]{2-bp22-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} call on \texttt{myObject.myProperty}.]{\label{fig:example3}\includegraphics[width=1.0\textwidth, height=.23\textheight]{3-lastChange.jpg}}
+\subfigure[The result of \textit{lastChange} query for \texttt{myObject.myProperty}.
+The right panel shows the collected data at the point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth, height=.23\textheight]{3-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} call on \texttt{myCondition.value}.]{\label{fig:example4}\includegraphics[width=1.0\textwidth, height=.23\textheight]{4-lastChange2.jpg}}
+\subfigure[The result of \textit{lastChange} query for \texttt{myCondition.value}.
+The opened list on the top of the left panel shows the visited execution points.
+Clicking on each point in the list shows the corresponding code and data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth, height=.23\textheight]{4-lastChange2.jpg}}
 
@@
 The \textit{lastChange} algorithm is based on program re-execution.
-Once developer asks for the \textit{lastChange} of a value, debugger re-executes the program, collects limited data and shows the result.
+Developer sets a breakpoint and execution is paused once the breakpoint hits.
+The breakpoint hit becomes the \textit{Reproduction point} when developer asks for the \textit{lastChange} of a value.
+Debugger re-executes the program, collects limited data and shows the result.
 \textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld.
@@
 The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
-Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
+Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point.
+Figure ~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change events in a hypothetical execution.
+\texttt{bar} id at the reproduction point is 1010, so the last change of \texttt{bar.foo} is the forth column.
 
@@
 \includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
-\caption{The list of property \texttt{foo} changes and \texttt{bar} id which identifies the last change of \texttt{bar.foo} in the history of events.}
+\caption{The list of property \texttt{foo} change events and \texttt{bar} id at the reproduction point which identifies the last change of \texttt{bar.foo} in the list.
+Column 3 is also a change of the object we want to study, id 1010, but it is not the last change; Column 5 is also a change of a property \texttt{foo} but its not for the object we are interested in.}
 \label{fig:foo-changes1}
@@
 \subsubsection{local, closure and \texttt{catch} scopes}
-local scope refers to the top scope in the scope chain.
+local scope refers to the most nested scope in the scope chain.
 Clousure scope refers to the scope which is created once a function is defined.
@@
 
-A variables in these scopes can only be changed by the code which is included in the it's definition block.
-Therefore it is only enough to take care only about the lines that a variable is assinged a new value.
+A variable in these scopes can only be changed by the code which is included in the its definition block.
+Therefore it is only enough to take care only about the lines that a variable is assigned a new value.
 The same fact is also true about \texttt{catch} and local scopes.
-Debugger puts hooks in on the line the variable is defined and all lines the variable is assigned a new variable (including inner-functions).
-For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 24 and the last change of \texttt{var1} is requested by the developer, two hooks on lines 22 and 23 will be set, but if the execution is paused at line 19, four hooks on lines 11, 12, 16, and 18.
+Debugger puts hooks in on the line the variable is defined and all lines the variable is assigned a new value (including inner-functions).
+For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 19, four hooks on lines 11, 12, 16, and 18, but if the execution is paused at line 24 and the last change of \texttt{var1} is requested by the developer, two hooks on lines 22 and 23 will be set.
 The reason is that \texttt{var1} in \texttt{firstChild} is a closure variable but in \texttt{secondChild} is a local variable.
@@
 \includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
-\caption{The list of variable \texttt{foo} changes and the \texttt{foo}'s scope id at the reproduction point which identifies the answer.}
+\caption{The list of variable \texttt{foo} change events and the \texttt{foo}'s scope id at the reproduction point which identifies the last change.}
 \label{fig:foo-changes2}
@@
 \includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
-\caption{The list of events stored for locating \textit{lastChange} of \texttt{bar.x} (point B) at the reproduction point and \texttt{baz.y} at point B.}
+\caption{The list of change events stored for locating point B, the \textit{lastChange} of \texttt{bar.x} at the reproduction point, and point C, the \textit{lastChange} of  \texttt{baz.y} at point B.}
 \label{fig:lastchange-lastchange}

### 2010-10-19 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 \usepackage{subfigure}
+\usepackage{algorithmic}
+\usepackage{algorithm}
 
@@
 
-To attack the mentioned problem, we propose a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the located point.
-While \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires \textit{bug reproduciblity} (i.e., a test case is available which reproduces the bug).
+To address this problem, we propose a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the located point.
+Although \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires bug reproduction by re-executions.
+In other words \textit{bug reproduciblity} (i.e., a test case is available which reproduces the bug) is the only prerequisite for \textit{lastChange} functinality.
 
-As a proof of concept we developed \textit{RevNav}, a JavaScript prototype, which adds the \textit{lastChange} feature to Firebug JavaScript debugger.
-Moreover, \textit{RevNav} provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
+As a proof of concept, we developed \textit{Querypointer}, a prototype which enhances Firebug JavaScript debugger with \textit{lastChange} feature.
+Moreover, \textit{Querypointer} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
 
-% how we buil it on breakpoint technology
 \end{abstract}
@@
 The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibiltily of the algorithm with \textit{RevNav}, an implementation extending the Firebug JavaScript debugger.
-\textit{RevNav} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
+We demonstrate the feasibiltily of the algorithm with \textit{Querypointer}, an implementation extending the Firebug JavaScript debugger.
+\textit{Querypointer} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
 
@@
 This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
-To start debugging, the developer sets a abreakpoint on line 22 and once the button is clicked execution is paused at line 22.
-(Figure ~\ref{fig:example1}) shows the debugger while the execution is paused.
-The developer can examine the program state at the right panel and as it shows, the \texttt{myObject.myProperty} value at this point is zero which is obviously a wrong value.
-
-To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
-To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
-Even if the developer could sucessfully finish this step (There is no simple way to check it), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
-All this work is useless if an origin was missed in the first step or if the data was collected in the second step is insufficient.
+To start debugging, the developer sets a breakpoint on line 22 and once the button is clicked execution is paused at line 22.
+Figure ~\ref{fig:example1} shows the Firebug debugger while the execution is paused.
+Firebug has several panels (e.g., html, css, script, dom, etc.) that each one demonstrate one aspect of JavaScript execution.
+The script panel contains the list of all loaded source files and regular debugging facilities such as setting breakpoints and stepping.
+The right panel in the script panel shows the program state and developer can examine object and variable values.
+In our case, the \texttt{myObject.myProperty} value at the paused point is zero which is obviously a wrong value.
 
@@
 \includegraphics{5-example-points.jpg}
-\caption{The examinated points.}
+\caption{The examinated points before locating the defect.}
 \label{fig:example-points}
 \end{figure}
+
+To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
+To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
+Having the fact that an object and property can be accessed and changed through different names and methods, we realize that the difficulty of this task.
+Even if the developer could sucessfully finish this step (There is no simple way to check it!), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
+All this work should be repeated if an origin was missed in the first step or if the data was collected in the second step is insufficient.
 
@@
 
-\subfigure[The execution is paused at line 22 by an ordinary breakpoint.]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.19\textheight]{1-bp22.jpg}}
+\subfigure[A view of Firebug JavaScript debugger.
+The selected script panel, presents all loaded JavaScript code.
+Developer has access to all loaded source file and can set breakpoints on lines.
+In this figure, the execution is paused at line 22 by a regular breakpoint.
+The panel at the right site shows the program state at the paused point.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.19\textheight]{1-bp22.jpg}}
 
-\subfigure[\textit{lastChange} command.]{\label{fig:example2}\includegraphics[width=1.0\textwidth, height=.19\textheight]{2-bp22-lastChange.jpg}}
+\subfigure[Developer can query \textit{lastChange} on a value by right clicking on the value.]{\label{fig:example2}\includegraphics[width=1.0\textwidth, height=.19\textheight]{2-bp22-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} call on \texttt{myObject.myProperty}.]{\label{fig:example3}\includegraphics[width=1.0\textwidth, height=.23\textheight]{3-lastChange.jpg}}
+\subfigure[The result of \textit{lastChange} query for \texttt{myObject.myProperty}.
+The right panel shows the collected data at the point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth, height=.23\textheight]{3-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} call on \texttt{myCondition.value}.]{\label{fig:example4}\includegraphics[width=1.0\textwidth, height=.23\textheight]{4-lastChange2.jpg}}
+\subfigure[The result of \textit{lastChange} query for \texttt{myCondition.value}.
+The opened list on the top of the left panel shows the visited execution points.
+Clicking on each point in the list shows the corresponding code and data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth, height=.23\textheight]{4-lastChange2.jpg}}
 
@@
 
+The story starts when developer examines the program state at a breakpoint hit and asks for the \textit{lastChange} of a value.
 The \textit{lastChange} algorithm is based on program re-execution.
-Once developer asks for the \textit{lastChange} of a value, debugger re-executes the program, collects limited data and shows the result.
-\textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld.
-Like the introductory example, it can be defined by a [conditional] breakpoint.
+Therefore it is assumed that the execution can be reproduced automatically (e.g., by a given test case) or with the developer's assistance.
+The breakpoint hit becomes the \textit{reproduction point}.
+Debugger sets hooks on all instructions that might be the result of \textit{lastChange} query, re-executes the program, at every hook hit, \textit{change event}, collects limited data and once the execution reaches the reproduction point, it analyzes the collected data and shows the result.
+The result is a partial snapshot of the program state at the execution point that last change occured.
+
+As we shown in the previous section, a \textit{lastChange} query can be performed on the result of another \textit{lastChange} query.
+If we name the reproduction point \textit{R}, we can write the first \textit{lastChange} in the introductory example in this form: \textit{lastChange(R, myObject.myProperty)}.
+It means that this query is defined at \textit{R}.
+If we name the result of this query \textit{A}, we can write the second \textit{lastChange} in this form: \textit{lastChange(A, myCondition.value)}.
+In this way, a sequence of \textit{lastChange} queries with any length can be defined.
+
 \textit{lastChange} can be called on two different types of values: An object property or a variable value.
-In JavaScript, every available variable in a frame comes from one of the scopes in the current scope chain.
+In JavaScript, every available variable in a frame comes from one of the scopes in the frame's scope chain.
 There are five different scope types: global, local, with, catch, closure.
@@
 \subsection{\textit{lastChange} on object propery}
-To simplify the algorithm explanation and avoid technical details, we assume two basic operations and postpone implementation details to the next section.
-The first opertion is \texttt{objectId()} which gets an object and returns an integer as its identifier.
+To simplify the algorithm explanation and avoid technical details, we assume two basic operations and later we explain the details of this two operations.
+The first opertion is \texttt{objectId()} which gets a JavaScript object and returns an integer as its identifier.
 This identifier is unique for every object during one execution.
-The second operation is \texttt{setPropertyChangeHook()} which gets function as the hook and a string as the property name like \texttt{foo}.
-Whenever property \texttt{foo} in any object changes the hook will be called.
-The hook function receives a reference to the owner of \texttt{foo}.
-
-Once developer asks for the last change of \texttt{bar.foo} at the reproduction point, debugger calls \texttt{setPropertyChangeHook()} with \texttt{foo} as the property name and re-executes the program.
-Whenever \texttt{foo} changes and the hook function is called, debugger first calls \texttt{objectID()} on the \texttt{foo} owner object.
-Then it stores owner id and stack frame locations.
-The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
-Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point(Figure ~\ref{fig:foo-changes1}).
+The second operation is \texttt{setPropertyChangeHook()} which gets function as the callback and a string as the property name like \texttt{foo}.
+Whenever property \texttt{foo} in any object changes the callback will be called.
+The callback function receives a reference to the owner of \texttt{foo}.
 
@@
 \includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
-\caption{The list of property \texttt{foo} changes and \texttt{bar} id which identifies the last change of \texttt{bar.foo} in the history of events.}
+\caption{The list of property \texttt{foo} change events and \texttt{bar} id at the reproduction point which identifies the last change of \texttt{bar.foo} in the list.
+Column 3 is also a change of the object we want to study, id 1010, but it is not the last change; Column 5 is also a change of a property \texttt{foo} but its not for the object we are interested in.}
 \label{fig:foo-changes1}
 \end{figure}
+
+Once developer asks for the last change of \texttt{bar.foo} at the reproduction point, debugger calls \texttt{setPropertyChangeHook()} with \texttt{foo} as the property name and re-executes the program.
+Whenever \texttt{foo} changes and the callback function is called, debugger first calls \texttt{objectId()} on the \texttt{foo} owner object.
+Then it stores owner id and stack frame locations.
+The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
+Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point.
+Figure ~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change events in a hypothetical execution.
+\texttt{bar} id at the reproduction point is 1010, so the last change of \texttt{bar.foo} is the forth column.
+
+\subsubsection{\texttt{objectId()}}
+The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable.
+Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program.
+Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function.
+As a parameter it can be specified that the defined property is not enumerable.
+Then it is enough to assign a new generated id to this property.
+
+\subsubsection{\texttt{setPropertyChangeHook()}}
+To implement this operation, we use two features that are available in Firefox JavaScript engine.
+First, every regular JavaScript object has a \texttt{watch()} function which receives two parameters, a property name and another function as a callback.
+Whenever the property with the given name changes the calleback function is called.
+The hook is set by this function is enabled even if the property is removed and added again [ref].
+The issue with this function is that it can only be applied to available objects.
+However, at the beginning of re-execution there is no object available.
+To solve this issue we use the second feature.
+Enabling a flag gives us the place the object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
+Though this is a limited data, it helps us to get a reference to the object once it is created.
+Then it is enough to set objet id and call \texttt{watch()} with the property name.
+In section 4.1, we explain how we get reference to the created objects.
 
@@
 There are five different scope types: local, global, \texttt{with}, closure, \texttt{catch}.
-We explain each case separately.
+We explain these cases in two groups.
 
@@
 \subsection{\textit{lastChange} on \textit{lastChange}}
-Once the developer asks for the first \textit{lastChange} all program state is available to the debugger.
-But the next \textit{lastChange} calls are asked over collected data.
-For example, debugger needs object id for the second \textit{lastChange} and this data should be collected.
-To do so, debugger does a data dependency analysis between points which gives a list of items should be collected at every point.
+The algorithm we explained so far needs an enhancement to support longer sequence of \textit{lastChange}s. We explain first the issue and then the solution. Consider the following points:
+
+\begin{center}
+\textit{
+ point A : the reproduction point \\
+ point B : lastChange(A, bar.x) \\
+ point C : lastChange(B, baz.y) 
+ }
+ \end{center}
+According the algorithm explained in the previous section none of the points B and C can be identified before reaching point A.
+Therefore, all \texttt{x} changes for piont B and all \texttt{y} changes for point C are stored.
+Once the execution reaches point A, and the exact \texttt{bar} id reveals, point B can be identified among the items in the history of \texttt{x} changes.
+The problem arises in recognizing point C.
+To recognize point C, we need \texttt{baz} id at point B, but B is a past program state, and \texttt{baz} id has not been collected at this point.
+
+\begin{algorithm}
+\caption{\textit{lastChange} queries dependency analysis.}
+\label{dependency-analysis}
+\begin{algorithmic}
+
+%\FORALL{xxx}%q in queries} 
+\FOR{$q$ in $queries$} 
+ \FOR {$p$ defined at the $q$ result}
+   %\STATE \COMMENT{p = lastChange(q, bar.foo)}        	
+   \IF {$p$ is a lastChange on object property}
+
+     \STATE Store $foo$ id at $q$. 
+   \ELSE %\STATE \COMMENT{lastChange on variable}
+    % \STATE \COMMENT{p = lastChange(q, foo)}        	
+     \STATE Store $foo$ scope id at $q$.
+	 \ENDIF 
+ \ENDFOR 
+\ENDFOR
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 \includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
-\caption{The list of events stored for locating \textit{lastChange} of \texttt{bar.x} (point B) at the reproduction point and \texttt{baz.y} at point B.}
+\caption{The list of change events stored for locating point B, the \textit{lastChange} of \texttt{bar.x} at the reproduction point, and point C, the \textit{lastChange} of  \texttt{baz.y} at point B.}
 \label{fig:lastchange-lastchange}
 \end{figure}
+
+To address this issue, debugger does a dependency analysis between all \textit{lastChange} queries and computes the additional data needs to be collected at each point.
+For example in the mentioned case, \texttt{baz} id- if it is available- should be collected at all points \texttt{x} changes.
+Having this additional data, locating point C, using the \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
+
 %---------------------------------------------------------------------------------------------------
@@
 The JavaScript prototype is implemented as an extension to Firebug[] javasrcipt debugger.
+
+\subsection{Tracking object creation}
+Now we discuss two mentioned assumptions.
+In the standard JavaScript every object has a \texttt{watch()} function which receives two parameters, a property name and another function as a hook.
+Whenever the property with the given name changes the hook function is called.
+The issue with using this function is that it can only be applied to available objects.
+However, at the beginning of re-execution there is no object available.
+To solve this issue we use a feature in Firefox JavaScript engine, setting a flag gives us the place the object created (e.g., myFile.js, line 24).
+Though this is a limited data it can help us to get a reference to the object once it is created.
+Therefore, at the reproduction point, debugger gets the creation location of \texttt{bar} and once the execution reaches to that location it gets a reference to the created object and sets a unique id for it.
 
@@
 In the local reproduction approach, debugger calls the funtion on the bottom of stack with the same parameters.
-
-\subsection{Tracking object creation}
-Now we discuss two mentioned assumptions.
-In the standard JavaScript every object has a \texttt{watch()} function which receives two parameters, a property name and another function as a hook.
-Whenever the property with the given name changes the hook function is called.
-The issue with using this function is that it can only be applied to available objects.
-However, at the beginning of re-execution there is no object available.
-To solve this issue we use a feature in Firefox JavaScript engine, setting a flag gives us the place the object created (e.g., myFile.js, line 24).
-Though this is a limited data it can help us to get a reference to the object once it is created.
-Therefore, at the reproduction point, debugger gets the creation location of \texttt{bar} and once the execution reaches to that location it gets a reference to the created object and sets a unique id for it.
 

### 2010-10-19 papers/pldi2011/sigplanconf-template.tex

@@
 
-As a proof of concept, we developed \textit{Querypoint}, a prototype which enhances Firebug JavaScript debugger with \textit{lastChange} feature.
-Moreover, \textit{Querypoint} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
+As a proof of concept, we developed \textit{Querypointer}, a prototype which enhances Firebug JavaScript debugger with \textit{lastChange} feature.
+Moreover, \textit{Querypointer} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
 
@@
 The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibiltily of the algorithm with \textit{Querypoint}, an implementation extending the Firebug JavaScript debugger.
-\textit{Querypoint} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
+We demonstrate the feasibiltily of the algorithm with \textit{Querypointer}, an implementation extending the Firebug JavaScript debugger.
+\textit{Querypointer} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
 
@@
 
+\begin{figure}[htp]
+\includegraphics{5-example-points.jpg}
+\caption{The examinated points before locating the defect.}
+\label{fig:example-points}
+\end{figure}
+
 To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
@@
 All this work should be repeated if an origin was missed in the first step or if the data was collected in the second step is insufficient.
-
-\begin{figure}[htp]
-\includegraphics{5-example-points.jpg}
-\caption{The examinated points before locating the defect.}
-\label{fig:example-points}
-\end{figure}
 
@@
 The selected script panel, presents all loaded JavaScript code.
-Developer has access to any loaded source file and can set breakpoints on lines.
+Developer has access to all loaded source file and can set breakpoints on lines.
 In this figure, the execution is paused at line 22 by a regular breakpoint.
@@
 
+The story starts when developer examines the program state at a breakpoint hit and asks for the \textit{lastChange} of a value.
 The \textit{lastChange} algorithm is based on program re-execution.
-Developer sets a breakpoint and execution is paused once the breakpoint hits.
-The breakpoint hit becomes the \textit{Reproduction point} when developer asks for the \textit{lastChange} of a value.
-Debugger re-executes the program, collects limited data and shows the result.
-\textit{Reproduction point} is the execution point in which first \textit{lastChange} is calld.
-Like the introductory example, it can be defined by a [conditional] breakpoint.
+Therefore it is assumed that the execution can be reproduced automatically (e.g., by a given test case) or with the developer's assistance.
+The breakpoint hit becomes the \textit{reproduction point}.
+Debugger sets hooks on all instructions that might be the result of \textit{lastChange} query, re-executes the program, at every hook hit, \textit{change event}, collects limited data and once the execution reaches the reproduction point, it analyzes the collected data and shows the result.
+The result is a partial snapshot of the program state at the execution point that last change occured.
+
+As we shown in the previous section, a \textit{lastChange} query can be performed on the result of another \textit{lastChange} query.
+If we name the reproduction point \textit{R}, we can write the first \textit{lastChange} in the introductory example in this form: \textit{lastChange(R, myObject.myProperty)}.
+It means that this query is defined at \textit{R}.
+If we name the result of this query \textit{A}, we can write the second \textit{lastChange} in this form: \textit{lastChange(A, myCondition.value)}.
+In this way, a sequence of \textit{lastChange} queries with any length can be defined.
+
 \textit{lastChange} can be called on two different types of values: An object property or a variable value.
-In JavaScript, every available variable in a frame comes from one of the scopes in the current scope chain.
+In JavaScript, every available variable in a frame comes from one of the scopes in the frame's scope chain.
 There are five different scope types: global, local, with, catch, closure.
@@
 \subsection{\textit{lastChange} on object propery}
-To simplify the algorithm explanation and avoid technical details, we assume two basic operations and postpone implementation details to the next section.
-The first opertion is \texttt{objectId()} which gets an object and returns an integer as its identifier.
+To simplify the algorithm explanation and avoid technical details, we assume two basic operations and later we explain the details of this two operations.
+The first opertion is \texttt{objectId()} which gets a JavaScript object and returns an integer as its identifier.
 This identifier is unique for every object during one execution.
-The second operation is \texttt{setPropertyChangeHook()} which gets function as the hook and a string as the property name like \texttt{foo}.
-Whenever property \texttt{foo} in any object changes the hook will be called.
-The hook function receives a reference to the owner of \texttt{foo}.
-
-Once developer asks for the last change of \texttt{bar.foo} at the reproduction point, debugger calls \texttt{setPropertyChangeHook()} with \texttt{foo} as the property name and re-executes the program.
-Whenever \texttt{foo} changes and the hook function is called, debugger first calls \texttt{objectID()} on the \texttt{foo} owner object.
-Then it stores owner id and stack frame locations.
-The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
-Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point.
-Figure ~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change events in a hypothetical execution.
-\texttt{bar} id at the reproduction point is 1010, so the last change of \texttt{bar.foo} is the forth column.
+The second operation is \texttt{setPropertyChangeHook()} which gets function as the callback and a string as the property name like \texttt{foo}.
+Whenever property \texttt{foo} in any object changes the callback will be called.
+The callback function receives a reference to the owner of \texttt{foo}.
 
@@
 
+Once developer asks for the last change of \texttt{bar.foo} at the reproduction point, debugger calls \texttt{setPropertyChangeHook()} with \texttt{foo} as the property name and re-executes the program.
+Whenever \texttt{foo} changes and the callback function is called, debugger first calls \texttt{objectId()} on the \texttt{foo} owner object.
+Then it stores owner id and stack frame locations.
+The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
+Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point.
+Figure ~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change events in a hypothetical execution.
+\texttt{bar} id at the reproduction point is 1010, so the last change of \texttt{bar.foo} is the forth column.
+
+\subsubsection{\texttt{objectId()}}
+The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable.
+Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program.
+Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function.
+As a parameter it can be specified that the defined property is not enumerable.
+Then it is enough to assign a new generated id to this property.
+
+\subsubsection{\texttt{setPropertyChangeHook()}}
+To implement this operation, we use two features that are available in Firefox JavaScript engine.
+First, every regular JavaScript object has a \texttt{watch()} function which receives two parameters, a property name and another function as a callback.
+Whenever the property with the given name changes the calleback function is called.
+The hook is set by this function is enabled even if the property is removed and added again [ref].
+The issue with this function is that it can only be applied to available objects.
+However, at the beginning of re-execution there is no object available.
+To solve this issue we use the second feature.
+Enabling a flag gives us the place the object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
+Though this is a limited data, it helps us to get a reference to the object once it is created.
+Then it is enough to set objet id and call \texttt{watch()} with the property name.
+In section 4.1, we explain how we get reference to the created objects.
+
 \subsection{\textit{lastChange} on variable} 
@@
 There are five different scope types: local, global, \texttt{with}, closure, \texttt{catch}.
-We explain each case separately.
+We explain these cases in two groups.
 
 \subsubsection{global and \texttt{with} scopes}
-Global scope is the the most outer scope in the scope chain and it also refers as global object.
+Global scope is the the most outer scope in the scope chain and it is also refered as global object which is usually \texttt{window} object.
 This scope is a regular JavaScript object and therefore every global variable is a property of global object.
@@
 \subsubsection{local, closure and \texttt{catch} scopes}
-local scope refers to the most nested scope in the scope chain.
-Clousure scope refers to the scope which is created once a function is defined.
-Catch scope is the scope created by try-catch blocks and contains the exception variable.
-These objects are not necessarily regular JavaScript objects.
-Therefore to track changes to a variable in these scopes we need a new strategy.
+Local scope refers to the most nested scope in the scope chain.
+Closure scope refers to the scope which is created once a function is defined.
+Catch scope is the scope created in the catch block of try-catch statements and contains the exception variable.
+These scopes are not necessarily regular JavaScript objects.
+Therefore, to track changes to a variable in these scopes we use a different strategy.
 
-%%% we need a short explanation about scopes
-%%% important: think about it: we also need to set a special variable (id) to let us to identify the related functional scope
 \begin{figure}[htp]
 \begin{verbatim}
-10  function parent(arg1){
+10  function parent(){
 11    var var1;
-12    var1 = 0;
-13    function myfun(arg2){
-14      var var2;
-15      var2 = {...}
-16      var1 = var2;
-17      function firstChild(arg3){
-18        var1 = 1;
-19        var2 = 1;
-20      }  
-21      function secondChild(arg4){
-22       	var var1;
-23        var1 = 2			      
-24        var2 = 2;	
-25      }
-26    }  
-27  }    
+12    var1 = ...;
+13    function myfun(){
+14      var1 = ...;
+15      function firstChild(){
+16       	var var1;
+17        var1 = ...;
+18      }  
+19      function secondChild(){
+20        var1 = ...;			      
+21      }
+22    }  
+23  }    
 \end{verbatim}
-\caption{Sample JavaScript code demonstrating closure variables.}
+\caption{Sample JavaScript code demonstrating local and clousure variables.}
 \label{fig:js-closure}
@@
 
-A variable in these scopes can only be changed by the code which is included in the its definition block.
-Therefore it is only enough to take care only about the lines that a variable is assigned a new value.
-The same fact is also true about \texttt{catch} and local scopes.
-Debugger puts hooks in on the line the variable is defined and all lines the variable is assigned a new value (including inner-functions).
-For example in Figure ~\ref{fig:js-closure}, if the execution is paused at line 19, four hooks on lines 11, 12, 16, and 18, but if the execution is paused at line 24 and the last change of \texttt{var1} is requested by the developer, two hooks on lines 22 and 23 will be set.
-The reason is that \texttt{var1} in \texttt{firstChild} is a closure variable but in \texttt{secondChild} is a local variable.
+A variable in these types of scope can only be changed in the function the variable is defined or the nested fuctions.
+For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be changed in lines 10 to 23.
+Therefore, after locating the function in which the variable is defined, it is enough to parse the code inside the function block and set a hook on all lines where the variable is assigned a new value.% TODO lines or instruction???
+We also set a hook at the first line of the function which is corresponding to the line variable is defined.
+In Figure ~\ref{fig:js-closure}, if the execution is paused at line 17 and the last change of \texttt{var1} is queried, two hooks on lines 16 and 17 will be set, but if the execution is paused at line 20 , four hooks on lines 11, 12, 14, 20 will be set.
+These two cases are different due the fact that \texttt{var1} in \texttt{firstChild} is a local variable but in \texttt{secondChild} is a closure variable.
+
+Everytime one of the hooks hits a new change event is inserted to the list of change events.
+During execution the same variable might be changed several times but in different scopes.
+Figure ~\ref{fig:recursive} demonstrates one case that a scope identifier is necessary for locating the right answer.
+In this case the same variable \texttt{x} is changed several times but in different scopes due to the recursive calls.
+Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
 
@@
 
-Recursive function: 
- f(){
+  function f(){
     var x;
@@
     f();
-   x; 
-   ...
   }
 
-The trace of recursive calls:
+Sample Trace:
 
-  f was called.
-    x changes; // A
-      f was called;
-        x changes;
-        f was called 
-          x changes; //C
-    //C
+   f()
+A  |  x changes; 
+   |  f()
+   |  |  x changes;
+   |  |  f()
+B  |  |  |  x changes; 
+C  |  ?
 
 \end{verbatim}
-\caption{Recursive calls.}
+\caption{A recursive call trace demonstrates the need for scope id. Querying \textit{lastChange} on \texttt{x} at point C should return point A not B.}
 \label{fig:recursive}
@@
 
-Everytime one of the hook hit a new event is inserted to the list of events.
-To separate irrelvant event from each other, we use a special variable \texttt{\_scopeId}.
-If the scope has this variable, the value of this variable is used for the scope id otherwise a new id will be generated and \texttt{\_scopeId} variable is created by \texttt{eval()} function in the scope.
+The scope id is kept as a variable in the scope, \texttt{\_scopeId}.
+As we said, a hook is set on the first instruction of the function defines the variable.
+Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function.
 For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
-Consider that even in the case of closure scopes, \texttt{\_scopeId} is set when the variable first defined and the variable's scope is still local.
-Figure ~\ref{fig:recursive} demonstrates one case that scope id is necessary for identifying the right answer.
-In thiss case the same variable \texttt{x} is changed several times but in different scopes due to recursive calls.
-Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
 
@@
  \end{center}
-According the algorithm explained in the previous section none of the points B and C can be identified before reaching point A.
+According to the algorithm explained in the previous section none of the points B and C can be identified before reaching point A.
 Therefore, all \texttt{x} changes for piont B and all \texttt{y} changes for point C are stored.
-Once the execution reaches point A, and the exact \texttt{bar} id reveals, point B can be identified among the items in the history of \texttt{x} changes.
+Once the execution reaches point A, and the exact \texttt{bar} id reveals, point B can be identified among the change events in the history of \texttt{x} changes.
 The problem arises in recognizing point C.
 To recognize point C, we need \texttt{baz} id at point B, but B is a past program state, and \texttt{baz} id has not been collected at this point.
+
+To address this issue, debugger does a dependency analysis between all \textit{lastChange} queries and computes the additional data required to be collected at each point.
+For example in the mentioned case, \texttt{baz} id- if it is available- should be collected at all points \texttt{x} changes.
+Having this additional data, locating point C, using \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
+
+\begin{algorithm}
+\caption{\textit{lastChange} queries dependency analysis.}
+\label{dependency-analysis}
+\begin{algorithmic}
+
+\FOR{$q$ in $queries$} 
+ \FOR {$p$ was defined at the $q$ result}
+   \IF {$p$ is a lastChange on object property} 
+     \STATE property id should be stored at $q$ change events. 
+   \ELSIF {$p$ is a lastChange on variable} 
+     \STATE variable scope id should be stored at $q$ change events.
+	 \ENDIF 
+ \ENDFOR 
+\ENDFOR
+
+\end{algorithmic}
+\end{algorithm}
 
@@
 
-To address this issue, debugger does a dependency analysis between all \textit{lastChange} queries and computes the additional data needs to be collected at each point.
-For example in the mentioned case, \texttt{baz} id- if it is available- should be collected at all points \texttt{x} changes.
-Having this additional data, locating point C, using the \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
-
 %---------------------------------------------------------------------------------------------------

### 2010-10-20 trunk/papers/pldi2011/sigplanconf-template.tex
only adding newlines to make the paragraphs narrower in my editor

@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
-
 \documentclass[preprint]{sigplanconf}
@@
 \section{Introductory example}
-We illustrate the \textit{lastChange} functionality by a simple example.
-The example demonstrates a buggy JavaScript code in a html page (Figure ~\ref{fig:js-code}).
-The page contains a button (line 40) which shows the value of \texttt{myObject.myProperty}.
-It is supposed that whenever user clicks on the button, the value of \texttt{myObject.myProperty} and therefore button's label is increased by one.
-Once the page is loaded for the first time the button shows \texttt{1} as the initial value of \texttt{myObject.myProperty}.
-The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears.
 
-Once user clicks on the button, \texttt{onClick} function (line 13) is called.
-This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
-To start debugging, the developer sets a breakpoint on line 22 and once the button is clicked execution is paused at line 22.
-Figure ~\ref{fig:example1} shows the Firebug debugger while the execution is paused.
-Firebug has several panels (e.g., html, css, script, dom, etc.) that each one demonstrate one aspect of JavaScript execution.
-The script panel contains the list of all loaded source files and regular debugging facilities such as setting breakpoints and stepping.
-The right panel in the script panel shows the program state and developer can examine object and variable values.
-In our case, the \texttt{myObject.myProperty} value at the paused point is zero which is obviously a wrong value.
+We illustrate the \textit{lastChange} functionality by a simple
+example. The example demonstrates a buggy JavaScript code in a html
+page (Figure ~\ref{fig:js-code}). The page contains a button (line 40)
+which shows the value of \texttt{myObject.myProperty}. It is supposed
+that whenever user clicks on the button, the value of
+\texttt{myObject.myProperty} and therefore button's label is increased
+by one. Once the page is loaded for the first time the button shows
+\texttt{1} as the initial value of \texttt{myObject.myProperty}. The
+bug happens when user clicks on the button and instead of \texttt{2},
+\texttt{0} appears.
+
+Once user clicks on the button, \texttt{onClick} function (line 13) is
+called. This function increases the value of
+\texttt{myObject.myProperty} by one (line 15) and calls
+\texttt{updateButton} function which updates button's text to the new
+value (line 22). To start debugging, the developer sets a breakpoint
+on line 22 and once the button is clicked execution is paused at line
+22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
+execution is paused. Firebug has several panels (e.g., html, css,
+script, dom, etc.) that each one demonstrate one aspect of JavaScript
+execution. The script panel contains the list of all loaded source
+files and regular debugging facilities such as setting breakpoints and
+stepping. The right panel in the script panel shows the program state
+and developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero which
+is obviously a wrong value.
 
@@
 
-To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
-To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
-Having the fact that an object and property can be accessed and changed through different names and methods, we realize that the difficulty of this task.
-Even if the developer could sucessfully finish this step (There is no simple way to check it!), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
-All this work should be repeated if an origin was missed in the first step or if the data was collected in the second step is insufficient.
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin to the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find and
+set breakpoint at all possible places that
+\texttt{myObject.myProperty} might get a new value. Having the fact
+that an object and property can be accessed and changed through
+different names and methods, we realize that the difficulty of this
+task. Even if the developer could sucessfully finish this step (There
+is no simple way to check it!), the next step is monitoring the
+re-execution and collecting data at breakpoint hits before reaching
+line 22. All this work should be repeated if an origin was missed in
+the first step or if the data was collected in the second step is
+insufficient.
 
-In contrast, we propose a high-level function in debugger, \textit{lastChange}, which provides the answer without demanding anymore effort from the developer.
-By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}).
-Debugger considers the paused point at the breakpoint as the reproduction point, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}).
-The program state debugger shows on the right panel belongs to the past.
-Therefore the right panel just shows the partially collected data.
-If the developer needs some values which are not available in the right panel, debugger re-executes another time and collects and shows the requested data.
+In contrast, we propose a high-level function in debugger,
+\textit{lastChange}, which provides the answer without demanding
+anymore effort from the developer. By right clicking on
+\texttt{myObject.myProperty} in the right panel, the developer can run
+\textit{lastChange} command (Figure ~\ref{fig:example2}). Debugger
+considers the paused point at the breakpoint as the reproduction
+point, and re-executes the buggy execution, pauses at the reproduction
+point and shows line 29 in a new panel (Figure
+~\ref{fig:example3}). The program state debugger shows on the right
+panel belongs to the past. Therefore the right panel just shows the
+partially collected data. If the developer needs some values which are
+not available in the right panel, debugger re-executes another time
+and collects and shows the requested data.
 
@@
 
-\subfigure[A view of Firebug JavaScript debugger.
-The selected script panel, presents all loaded JavaScript code.
-Developer has access to all loaded source file and can set breakpoints on lines.
-In this figure, the execution is paused at line 22 by a regular breakpoint.
-The panel at the right site shows the program state at the paused point.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.19\textheight]{1-bp22.jpg}}
+\subfigure[A view of Firebug JavaScript debugger. The selected script
+  panel, presents all loaded JavaScript code. Developer has access to
+  all loaded source file and can set breakpoints on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The panel at the right site shows the program state at
+  the paused
+  point. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth,
+    height=.19\textheight]{1-bp22.jpg}}
 
-\subfigure[Developer can query \textit{lastChange} on a value by right clicking on the value.]{\label{fig:example2}\includegraphics[width=1.0\textwidth, height=.19\textheight]{2-bp22-lastChange.jpg}}
+\subfigure[Developer can query \textit{lastChange} on a value by right
+  clicking on the
+  value.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
+    height=.19\textheight]{2-bp22-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} query for \texttt{myObject.myProperty}.
-The right panel shows the collected data at the point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth, height=.23\textheight]{3-lastChange.jpg}}
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The right panel shows the collected
+  data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,
+    height=.23\textheight]{3-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} query for \texttt{myCondition.value}.
-The opened list on the top of the left panel shows the visited execution points.
-Clicking on each point in the list shows the corresponding code and data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth, height=.23\textheight]{4-lastChange2.jpg}}
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. The opened list on the top of the left
+  panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth,
+    height=.23\textheight]{4-lastChange2.jpg}}
 
@@
 
-Looking at line 29, it seems that something is wrong with \texttt{myCondition.value} which causes line 29 execution.
-The developer examines \texttt{myCondition.value} and it is \texttt{undefined}.
-The next step is to know when this property got this value.
-To do so, the developer runs \textit{lastChange} command on \texttt{myCondition.value} at this point.
-Debugger re-executes the execution and pauses at the reproduction point and shows line 25-the place \texttt{undefined} value is assigned to \texttt{myCondition.value} (Figure ~\ref{fig:example3}).
-Now it is clear that the bug occures because \texttt{oldValue} is \texttt{undefined} once execution reaches line 25.
+Looking at line 29, it seems that something is wrong with
+\texttt{myCondition.value} which causes line 29 execution. The
+developer examines \texttt{myCondition.value} and it is
+\texttt{undefined}. The next step is to know when this property got
+this value. To do so, the developer runs \textit{lastChange} command
+on \texttt{myCondition.value} at this point. Debugger re-executes the
+execution and pauses at the reproduction point and shows line 25-the
+place \texttt{undefined} value is assigned to
+\texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
+clear that the bug occures because \texttt{oldValue} is
+\texttt{undefined} once execution reaches line 25.
 
-As demonstrated in Figure ~\ref{fig:example-points}, the developer examinated three points of execution.
-Excepting the first point which debugger pause execution at that point, the second and third points are in the past and are shown by dotted line.
-These points-the history of the search for the defect-are available through the debugger's interface.
-On the top of the left panel in Figure ~\ref{fig:example3} there is an opened list which shows all three examinated points.
-The first one is the breakpoint on line 22, the second one is the point which is the last change of \texttt{myObject.myProperty} before the reaching the breakpoint and finally the last one is the point of execution in which \texttt{myCondition.value} gets the \texttt{undefined} value.
-Moreover, the source lines related to these points are tagged with red-cycle icons.
+As demonstrated in Figure ~\ref{fig:example-points}, the developer
+examinated three points of execution. Excepting the first point which
+debugger pause execution at that point, the second and third points
+are in the past and are shown by dotted line. These points-the history
+of the search for the defect-are available through the debugger's
+interface. On the top of the left panel in Figure ~\ref{fig:example3}
+there is an opened list which shows all three examinated points. The
+first one is the breakpoint on line 22, the second one is the point
+which is the last change of \texttt{myObject.myProperty} before the
+reaching the breakpoint and finally the last one is the point of
+execution in which \texttt{myCondition.value} gets the
+\texttt{undefined} value. Moreover, the source lines related to these
+points are tagged with red-cycle icons.
 
-Notice that in our example, \textit{lastChange} combines some aspects of breakpoint and of log-based debugging.
-Like breakpoint debugging, the developer re-executes a live runtime without changing the source and without a special execution environment beyond the debugger.
-The state of the program memory and the call stack are available at the lastChange point.
-Like log-based debugging, the program state and the call stack are recorded during program execution.
-We can't halt the program at \textit{lastChange} because we don't know which is the last one until we return to the original breakpoint.
-In section 5 we discuss about the possibility of pausing at \textit{lastChange} results.
+Notice that in our example, \textit{lastChange} combines some aspects
+of breakpoint and of log-based debugging. Like breakpoint debugging,
+the developer re-executes a live runtime without changing the source
+and without a special execution environment beyond the debugger. The
+state of the program memory and the call stack are available at the
+lastChange point. Like log-based debugging, the program state and the
+call stack are recorded during program execution. We can't halt the
+program at \textit{lastChange} because we don't know which is the last
+one until we return to the original breakpoint. In section 5 we
+discuss about the possibility of pausing at \textit{lastChange}
+results.
 
@@
 \subsubsection{global and \texttt{with} scopes}
-Global scope is the the most outer scope in the scope chain and it also refers as global object.
+Global scope is the the most outer scope in the scope chain and it is also refered as global object which is usually \texttt{window} object.
 This scope is a regular JavaScript object and therefore every global variable is a property of global object.
@@
  \end{center}
-According the algorithm explained in the previous section none of the points B and C can be identified before reaching point A.
+According to the algorithm explained in the previous section none of the points B and C can be identified before reaching point A.
 Therefore, all \texttt{x} changes for piont B and all \texttt{y} changes for point C are stored.
-Once the execution reaches point A, and the exact \texttt{bar} id reveals, point B can be identified among the items in the history of \texttt{x} changes.
+Once the execution reaches point A, and the exact \texttt{bar} id reveals, point B can be identified among the change events in the history of \texttt{x} changes.
 The problem arises in recognizing point C.
 To recognize point C, we need \texttt{baz} id at point B, but B is a past program state, and \texttt{baz} id has not been collected at this point.
+
+To address this issue, debugger does a dependency analysis between all \textit{lastChange} queries and computes the additional data required to be collected at each point.
+For example in the mentioned case, \texttt{baz} id- if it is available- should be collected at all points \texttt{x} changes.
+Having this additional data, locating point C, using \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
 
@@
 
-%\FORALL{xxx}%q in queries} 
 \FOR{$q$ in $queries$} 
- \FOR {$p$ defined at the $q$ result}
-   %\STATE \COMMENT{p = lastChange(q, bar.foo)}        	
+ \FOR {$p$ was defined at the $q$ result}
    \IF {$p$ is a lastChange on object property} 
-
-     \STATE Store $foo$ id at $q$. 
-   \ELSE %\STATE \COMMENT{lastChange on variable}
-    % \STATE \COMMENT{p = lastChange(q, foo)}        	
-     \STATE Store $foo$ scope id at $q$.
+     \STATE property id should be stored at $q$ change events. 
+   \ELSIF {$p$ is a lastChange on variable} 
+     \STATE variable scope id should be stored at $q$ change events.
 	 \ENDIF 
@@
 \end{figure}
-
-To address this issue, debugger does a dependency analysis between all \textit{lastChange} queries and computes the additional data needs to be collected at each point.
-For example in the mentioned case, \texttt{baz} id- if it is available- should be collected at all points \texttt{x} changes.
-Having this additional data, locating point C, using the \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
 

### 2010-10-20 trunk/papers/pldi2011/sigplanconf-template.tex
my edits to section 2, without checking that latex is happy

@@
 We illustrate the \textit{lastChange} functionality by a simple
-example. The example demonstrates a buggy JavaScript code in a html
+example. The example demonstrates a buggy JavaScript code in a HTML
 page (Figure ~\ref{fig:js-code}). The page contains a button (line 40)
-which shows the value of \texttt{myObject.myProperty}. It is supposed
-that whenever user clicks on the button, the value of
-\texttt{myObject.myProperty} and therefore button's label is increased
-by one. Once the page is loaded for the first time the button shows
-\texttt{1} as the initial value of \texttt{myObject.myProperty}. The
-bug happens when user clicks on the button and instead of \texttt{2},
-\texttt{0} appears.
-
-Once user clicks on the button, \texttt{onClick} function (line 13) is
+showing the value of \texttt{myObject.myProperty}.  When the user
+clicks on the button, the \texttt{onClick} function (line 13) is
 called. This function increases the value of
@@
 \texttt{updateButton} function which updates button's text to the new
-value (line 22). To start debugging, the developer sets a breakpoint
+value (line 22).  Once the page is loaded for the first time the
+button shows \texttt{1} as the initial value of
+\texttt{myObject.myProperty}.  In practice when the user clicks on the
+button, \texttt{0} appears instead of \texttt{2}: there is a bug.
+
+Two other functions are called in \texttt{onClick()}, \texttt{foo()}
+and \texttt{bar()}. As developers we often encounter function calls
+which seem perpheral to our current concern; they may have been added
+by another developer, or we may have forgotten their exact properties
+or those properties may have changed, and so on. The difference
+between what we expect these functions to do, e.g. nothing
+interesting, and what they do in practice may cause bugs.
+
+To start debugging, the developer sets a breakpoint
 on line 22 and once the button is clicked execution is paused at line
 22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
-execution is paused. Firebug has several panels (e.g., html, css,
-script, dom, etc.) that each one demonstrate one aspect of JavaScript
-execution. The script panel contains the list of all loaded source
+execution is paused. Firebug has several panels (e.g., HTML, CSS,
+Script, DOM, etc.) that each demonstrate one aspect of the Web page.
+The Script panel contains the list of all loaded source
 files and regular debugging facilities such as setting breakpoints and
-stepping. The right panel in the script panel shows the program state
-and developer can examine object and variable values. In our case, the
-\texttt{myObject.myProperty} value at the paused point is zero which
-is obviously a wrong value.
+stepping. To the right of the script panel, the Watch panel shows the program state
+where the developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
 
@@
 \end{verbatim}
-\caption{The buggy JavaScript code in a html page.}
+\caption{A Web page containing JavaScript code. Some lines not related to our paper have been elided.}
 \label{fig:js-code}
@@
 set breakpoint at all possible places that
-\texttt{myObject.myProperty} might get a new value. Having the fact
-that an object and property can be accessed and changed through
-different names and methods, we realize that the difficulty of this
-task. Even if the developer could sucessfully finish this step (There
-is no simple way to check it!), the next step is monitoring the
-re-execution and collecting data at breakpoint hits before reaching
-line 22. All this work should be repeated if an origin was missed in
-the first step or if the data was collected in the second step is
-insufficient.
+\texttt{myObject.myProperty} might get a new value.  However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these alias or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if the some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
 
 In contrast, we propose a high-level function in debugger,
-\textit{lastChange}, which provides the answer without demanding
-anymore effort from the developer. By right clicking on
-\texttt{myObject.myProperty} in the right panel, the developer can run
+\textit{lastChange}, which provides the answer without tedious manual
+effort from the developer. By right clicking on
+\texttt{myObject.myProperty} in the Watch panel, the developer can run
 \textit{lastChange} command (Figure ~\ref{fig:example2}). Debugger
-considers the paused point at the breakpoint as the reproduction
-point, and re-executes the buggy execution, pauses at the reproduction
-point and shows line 29 in a new panel (Figure
-~\ref{fig:example3}). The program state debugger shows on the right
-panel belongs to the past. Therefore the right panel just shows the
-partially collected data. If the developer needs some values which are
-not available in the right panel, debugger re-executes another time
-and collects and shows the requested data.
+re-executes the program and halts again at the breakpoint on line 22.
+However, it shows a new QP panel, centered on the source at line 29
+(Figure ~\ref{fig:example3}), the point of \testit{lastChange}.  To
+the right, the TraceData panels shows values of properties from the
+program state when it passed through line 29.  These two panels
+resemble the Script and Watch panels, but they show data collected by
+the debugger at an execution point which has now past: these are
+'traces' or 'logs' of information collected during the re-execution.
 
@@
 
-\subfigure[A view of Firebug JavaScript debugger. The selected script
-  panel, presents all loaded JavaScript code. Developer has access to
-  all loaded source file and can set breakpoints on lines. In this
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:example2}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
   figure, the execution is paused at line 22 by a regular
-  breakpoint. The panel at the right site shows the program state at
+  breakpoint. The Watch panel at the right shows the program state at
   the paused
@@
 
-\subfigure[Developer can query \textit{lastChange} on a value by right
-  clicking on the
-  value.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
+\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
+on the
+  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
     height=.19\textheight]{2-bp22-lastChange.jpg}}
@@
 \subfigure[The result of \textit{lastChange} query for
-  \texttt{myObject.myProperty}. The right panel shows the collected
-  data at the
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
   point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,
@@
 \texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
-clear that the bug occures because \texttt{oldValue} is
+clear that the bug occurs because \texttt{oldValue} is
 \texttt{undefined} once execution reaches line 25.
@@
 As demonstrated in Figure ~\ref{fig:example-points}, the developer
-examinated three points of execution. Excepting the first point which
-debugger pause execution at that point, the second and third points
-are in the past and are shown by dotted line. These points-the history
+examinated three points of execution. The first point was the breakpoint set by the developer.
+The second and third points preceded the breakpoint in time.
+All three points-the history
 of the search for the defect-are available through the debugger's
@@
 program at \textit{lastChange} because we don't know which is the last
-one until we return to the original breakpoint. In section 5 we
-discuss about the possibility of pausing at \textit{lastChange}
-results.
+one until we return to the original breakpoint. (In section 5 we
+discuss cases were it is possible to pause at lines of \textit{lastChange}).
 

### 2010-10-20 papers/pldi2011/sigplanconf-template.tex

@@
 \section{Introductory example}
-We illustrate the \textit{lastChange} functionality by a simple example.
-The example demonstrates a buggy JavaScript code in a html page (Figure ~\ref{fig:js-code}).
-The page contains a button (line 40) which shows the value of \texttt{myObject.myProperty}.
-It is supposed that whenever user clicks on the button, the value of \texttt{myObject.myProperty} and therefore button's label is increased by one.
-Once the page is loaded for the first time the button shows \texttt{1} as the initial value of \texttt{myObject.myProperty}.
-The bug happens when user clicks on the button and instead of \texttt{2}, \texttt{0} appears.
 
-Once user clicks on the button, \texttt{onClick} function (line 13) is called.
-This function increases the value of \texttt{myObject.myProperty} by one (line 15) and calls \texttt{updateButton} function which updates button's text to the new value (line 22).
-To start debugging, the developer sets a breakpoint on line 22 and once the button is clicked execution is paused at line 22.
-Figure ~\ref{fig:example1} shows the Firebug debugger while the execution is paused.
-Firebug has several panels (e.g., html, css, script, dom, etc.) that each one demonstrate one aspect of JavaScript execution.
-The script panel contains the list of all loaded source files and regular debugging facilities such as setting breakpoints and stepping.
-The right panel in the script panel shows the program state and developer can examine object and variable values.
-In our case, the \texttt{myObject.myProperty} value at the paused point is zero which is obviously a wrong value.
+We illustrate the \textit{lastChange} functionality by a simple
+example. The example demonstrates a buggy JavaScript code in a HTML
+page (Figure ~\ref{fig:js-code}). The page contains a button (line 40)
+showing the value of \texttt{myObject.myProperty}.  When the user
+clicks on the button, the \texttt{onClick} function (line 13) is
+called. This function increases the value of
+\texttt{myObject.myProperty} by one (line 15) and calls
+\texttt{updateButton} function which updates button's text to the new
+value (line 22).  Once the page is loaded for the first time the
+button shows \texttt{1} as the initial value of
+\texttt{myObject.myProperty}.  In practice when the user clicks on the
+button, \texttt{0} appears instead of \texttt{2}: there is a bug.
+
+Two other functions are called in \texttt{onClick()}, \texttt{foo()}
+and \texttt{bar()}. As developers we often encounter function calls
+which seem perpheral to our current concern; they may have been added
+by another developer, or we may have forgotten their exact properties
+or those properties may have changed, and so on. The difference
+between what we expect these functions to do, e.g. nothing
+interesting, and what they do in practice may cause bugs.
+
+To start debugging, the developer sets a breakpoint
+on line 22 and once the button is clicked execution is paused at line
+22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
+execution is paused. Firebug has several panels (e.g., HTML, CSS,
+Script, DOM, etc.) that each demonstrate one aspect of the Web page.
+The Script panel contains the list of all loaded source
+files and regular debugging facilities such as setting breakpoints and
+stepping. To the right of the script panel, the Watch panel shows the program state
+where the developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
 
@@
 
-To apply backward search strategy for locating defects, the developer first needs to know the origin to the wrong value.
-To achieve this goal using breakpoints, the developer should search code to find and set breakpoint at all possible places that \texttt{myObject.myProperty} might get a new value.
-Having the fact that an object and property can be accessed and changed through different names and methods, we realize that the difficulty of this task.
-Even if the developer could sucessfully finish this step (There is no simple way to check it!), the next step is monitoring the re-execution and collecting data at breakpoint hits before reaching line 22.
-All this work should be repeated if an origin was missed in the first step or if the data was collected in the second step is insufficient.
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin to the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find and
+set breakpoint at all possible places that
+\texttt{myObject.myProperty} might get a new value.  However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these alias or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if the some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
 
-In contrast, we propose a high-level function in debugger, \textit{lastChange}, which provides the answer without demanding anymore effort from the developer.
-By right clicking on \texttt{myObject.myProperty} in the right panel, the developer can run \textit{lastChange} command (Figure ~\ref{fig:example2}).
-Debugger considers the paused point at the breakpoint as the reproduction point, and re-executes the buggy execution, pauses at the reproduction point and shows line 29 in a new panel (Figure ~\ref{fig:example3}).
-The program state debugger shows on the right panel belongs to the past.
-Therefore the right panel just shows the partially collected data.
-If the developer needs some values which are not available in the right panel, debugger re-executes another time and collects and shows the requested data.
+In contrast, we propose a high-level function in debugger,
+\textit{lastChange}, which provides the answer without tedious manual
+effort from the developer. By right clicking on
+\texttt{myObject.myProperty} in the Watch panel, the developer can run
+\textit{lastChange} command (Figure ~\ref{fig:example2}). Debugger
+re-executes the program and halts again at the breakpoint on line 22.
+However, it shows a new QP panel, centered on the source at line 29
+(Figure ~\ref{fig:example3}), the point of \textit{lastChange}.  To
+the right, the TraceData panels shows values of properties from the
+program state when it passed through line 29.  These two panels
+resemble the Script and Watch panels, but they show data collected by
+the debugger at an execution point which has now past: these are
+'traces' or 'logs' of information collected during the re-execution.
 
@@
 
-\subfigure[A view of Firebug JavaScript debugger.
-The selected script panel, presents all loaded JavaScript code.
-Developer has access to all loaded source file and can set breakpoints on lines.
-In this figure, the execution is paused at line 22 by a regular breakpoint.
-The panel at the right site shows the program state at the paused point.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.19\textheight]{1-bp22.jpg}}
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:example2}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel at the right shows the program state at
+  the paused
+  point. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth,
+    height=.19\textheight]{1-bp22.jpg}}
 
-\subfigure[Developer can query \textit{lastChange} on a value by right clicking on the value.]{\label{fig:example2}\includegraphics[width=1.0\textwidth, height=.19\textheight]{2-bp22-lastChange.jpg}}
+\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
+on the
+  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
+    height=.19\textheight]{2-bp22-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} query for \texttt{myObject.myProperty}.
-The right panel shows the collected data at the point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth, height=.23\textheight]{3-lastChange.jpg}}
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,
+    height=.23\textheight]{3-lastChange.jpg}}
 
-\subfigure[The result of \textit{lastChange} query for \texttt{myCondition.value}.
-The opened list on the top of the left panel shows the visited execution points.
-Clicking on each point in the list shows the corresponding code and data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth, height=.23\textheight]{4-lastChange2.jpg}}
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. The opened list on the top of the left
+  panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth,
+    height=.23\textheight]{4-lastChange2.jpg}}
 
@@
 
-Looking at line 29, it seems that something is wrong with \texttt{myCondition.value} which causes line 29 execution.
-The developer examines \texttt{myCondition.value} and it is \texttt{undefined}.
-The next step is to know when this property got this value.
-To do so, the developer runs \textit{lastChange} command on \texttt{myCondition.value} at this point.
-Debugger re-executes the execution and pauses at the reproduction point and shows line 25-the place \texttt{undefined} value is assigned to \texttt{myCondition.value} (Figure ~\ref{fig:example3}).
-Now it is clear that the bug occures because \texttt{oldValue} is \texttt{undefined} once execution reaches line 25.
+Looking at line 29, it seems that something is wrong with
+\texttt{myCondition.value} which causes line 29 execution. The
+developer examines \texttt{myCondition.value} and it is
+\texttt{undefined}. The next step is to know when this property got
+this value. To do so, the developer runs \textit{lastChange} command
+on \texttt{myCondition.value} at this point. Debugger re-executes the
+execution and pauses at the reproduction point and shows line 25-the
+place \texttt{undefined} value is assigned to
+\texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
+clear that the bug occurs because \texttt{oldValue} is
+\texttt{undefined} once execution reaches line 25.
 
-As demonstrated in Figure ~\ref{fig:example-points}, the developer examinated three points of execution.
-Excepting the first point which debugger pause execution at that point, the second and third points are in the past and are shown by dotted line.
-These points-the history of the search for the defect-are available through the debugger's interface.
-On the top of the left panel in Figure ~\ref{fig:example3} there is an opened list which shows all three examinated points.
-The first one is the breakpoint on line 22, the second one is the point which is the last change of \texttt{myObject.myProperty} before the reaching the breakpoint and finally the last one is the point of execution in which \texttt{myCondition.value} gets the \texttt{undefined} value.
-Moreover, the source lines related to these points are tagged with red-cycle icons.
+As demonstrated in Figure ~\ref{fig:example-points}, the developer
+examinated three points of execution. The first point was the breakpoint set by the developer.
+The second and third points preceded the breakpoint in time.
+All three points-the history
+of the search for the defect-are available through the debugger's
+interface. On the top of the left panel in Figure ~\ref{fig:example3}
+there is an opened list which shows all three examinated points. The
+first one is the breakpoint on line 22, the second one is the point
+which is the last change of \texttt{myObject.myProperty} before the
+reaching the breakpoint and finally the last one is the point of
+execution in which \texttt{myCondition.value} gets the
+\texttt{undefined} value. Moreover, the source lines related to these
+points are tagged with red-cycle icons.
 
-Notice that in our example, \textit{lastChange} combines some aspects of breakpoint and of log-based debugging.
-Like breakpoint debugging, the developer re-executes a live runtime without changing the source and without a special execution environment beyond the debugger.
-The state of the program memory and the call stack are available at the lastChange point.
-Like log-based debugging, the program state and the call stack are recorded during program execution.
-We can't halt the program at \textit{lastChange} because we don't know which is the last one until we return to the original breakpoint.
-In section 5 we discuss about the possibility of pausing at \textit{lastChange} results.
+Notice that in our example, \textit{lastChange} combines some aspects
+of breakpoint and of log-based debugging. Like breakpoint debugging,
+the developer re-executes a live runtime without changing the source
+and without a special execution environment beyond the debugger. The
+state of the program memory and the call stack are available at the
+lastChange point. Like log-based debugging, the program state and the
+call stack are recorded during program execution. We can't halt the
+program at \textit{lastChange} because we don't know which is the last
+one until we return to the original breakpoint. (In section 5 we
+discuss cases were it is possible to pause at lines of \textit{lastChange}).
 
@@
 \subsection{\textit{lastChange} on object propery}
-To simplify the algorithm explanation and avoid technical details, we assume two basic operations and later we explain the details of this two operations.
+To simplify the algorithm explanation and avoid technical details, we assume two basic operations and later we explain the details of these two operations.
 The first opertion is \texttt{objectId()} which gets a JavaScript object and returns an integer as its identifier.
@@
 Figure ~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change events in a hypothetical execution.
-\texttt{bar} id at the reproduction point is 1010, so the last change of \texttt{bar.foo} is the forth column.
-
-\subsubsection{\texttt{objectId()}}
-The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable.
-Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program.
-Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function.
-As a parameter it can be specified that the defined property is not enumerable.
-Then it is enough to assign a new generated id to this property.
-
-\subsubsection{\texttt{setPropertyChangeHook()}}
-To implement this operation, we use two features that are available in Firefox JavaScript engine.
-First, every regular JavaScript object has a \texttt{watch()} function which receives two parameters, a property name and another function as a callback.
-Whenever the property with the given name changes the calleback function is called.
-The hook is set by this function is enabled even if the property is removed and added again [ref].
-The issue with this function is that it can only be applied to available objects.
-However, at the beginning of re-execution there is no object available.
-To solve this issue we use the second feature.
-Enabling a flag gives us the place the object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
-Though this is a limited data, it helps us to get a reference to the object once it is created.
-Then it is enough to set objet id and call \texttt{watch()} with the property name.
-In section 4.1, we explain how we get reference to the created objects.
+\texttt{bar} id at the reproduction point is 1010, so the last change of \texttt{bar.foo} is the fourth column.
 
@@
 
-The scope id is kept as a variable in the scope, \texttt{\_scopeId}.
-As we said, a hook is set on the first instruction of the function defines the variable.
-Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function.
-For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
-
 \subsection{\textit{lastChange} on \textit{lastChange}}
@@
 
-\subsection{Tracking object creation}
+\subsection{Algorithm technical details}
+\subsubsection{\texttt{objectId()}}
+The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable.
+Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program.
+Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function.
+As a parameter it can be specified that the defined property is not enumerable.
+Then it is enough to assign a new generated id to this property.
+
+\subsubsection{\texttt{scopeId()}}
+The scope id is kept as a variable in the scope, \texttt{\_scopeId}.
+As we said, a hook is set on the first instruction of the function defines the variable.
+Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function.
+For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
+
+\subsubsection{\texttt{setPropertyChangeHook()}}
+To implement this operation, we use two features that are available in Firefox JavaScript engine.
+First, every regular JavaScript object has a \texttt{watch()} function which receives two parameters, a property name and another function as a callback.
+Whenever the property with the given name changes the calleback function is called.
+The hook is set by this function is enabled even if the property is removed and added again [ref].
+The issue with this function is that it can only be applied to available objects.
+However, at the beginning of re-execution there is no object available.
+To solve this issue we use the second feature.
+Enabling a flag gives us the place the object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
+Though this is a limited data, it helps us to get a reference to the object once it is created.
+Then it is enough to set objet id and call \texttt{watch()} with the property name.
+In section 4.1, we explain how we get reference to the created objects.
+
+\subsubsection{Tracking object creation}
 Now we discuss two mentioned assumptions.
@@
 \section{Evaluation}
+\subsection{Execution overhead analysis}
+%If we assume for every change event k additionial instructions should be executed and the number of instructions executed in one execution is n and the number of change %events is m then the total amount of instructions is n+mk.
+The overhead is mk/n.
+for m=10^3, k=10^2 and n=10^10 the overhead is very low about 10^-5.
 

### 2010-10-20 papers/pldi2011/sigplanconf-template.tex

@@
 \section{JavaScript implementation}
-The JavaScript prototype is implemented as an extension to Firebug[] javasrcipt debugger.
+The JavaScript prototype is implemented as an extension to Firebug\cite{Firebug} javasrcipt debugger.
+In this section, first we explain technical details for the \textit{lastChange} implementation skipped in the previous section.
+Then we address other issues, such as re-execution, data collection and presentation.
 
@@
 \subsubsection{Tracking object creation}
-Now we discuss two mentioned assumptions.
-In the standard JavaScript every object has a \texttt{watch()} function which receives two parameters, a property name and another function as a hook.
-Whenever the property with the given name changes the hook function is called.
-The issue with using this function is that it can only be applied to available objects.
-However, at the beginning of re-execution there is no object available.
-To solve this issue we use a feature in Firefox JavaScript engine, setting a flag gives us the place the object created (e.g., myFile.js, line 24).
-Though this is a limited data it can help us to get a reference to the object once it is created.
-Therefore, at the reproduction point, debugger gets the creation location of \texttt{bar} and once the execution reaches to that location it gets a reference to the created object and sets a unique id for it.
+Having the source file url and the line number in wich the object created, we want to get a reference to the created object.
+Due to the fact that more than one object might be created in a line and there is no way to distinguish between them, we get references to all created objects.
+By parsing the source code we can find all statements that create a new object.
+It might be an object constructed by \texttt{\{\}} or \texttt{new ...
+} or spcial objects like function which can be created by \texttt{function()}.
+Every recently created object might be assigned to a variable or property by \texttt{=} or \texttt{:} or be passed to a function as an argument.
+For the first two case we create a list of assignees.
+Having the list of possible assignees we do stepping and after every step we check those assignees values and if the value is changed, we consider the new value
+ as a created object.
+
+ %One solution is to assume that jsd has features that simplify it:first: Setting the flag (object track) returns the exact location of object creation instead of the line number.second: It is possible to set hook on object creation and this returns a reference to the created object.
+ %Then we can explain it like this: We set a breakpoint at the location object is created and we enable the object creation hook.  We do steppingfor one instruction and we get the reference.
 
@@
 
-\subsection{Data collection}
-
-\subsection{User interface}
+\subsection{Data collection and presentation}
+In additional to the data collected by the \textit{lastChange} algorithm to correctly identify the last change, the list of available variables and their values (one level) are collected.
 
@@
 
-%\section{}
 %---------------------------------------------------------------------------------------------------
@@
 
+\bibitem[Firebug(2010)]{Firebug}
+Firebug. \newblock http://getfirebug.com.
+
 \bibitem[Ko(2008)]{Ko}

### 2010-10-20 papers/pldi2011/sigplanconf-template.tex

@@
 Then it is enough to set objet id and call \texttt{watch()} with the property name.
-In section 4.1, we explain how we get reference to the created objects.
+Consider that in this way, we implicitly assume that the object will be created at the same place in the next re-executions.
+This assumption will be discussed later.
+
+In the next section, we explain the algorithm for getting a reference to the object after its creation.
+We could replace this algorithm with a much simpler algorithm if Firefox supported these two features.
+First instead of line number of object creation point, it gave us the program counter.
+Second, there was a way to hook object creation and get a reference to the created object.
+Having this two features, it was enough to set a hook at the instruction and once the execution reaches to instruction, we enable the object creation hook and we step one instruction and we get the reference to the object.
 
@@
 By parsing the source code we can find all statements that create a new object.
-It might be an object constructed by \texttt{\{\}} or \texttt{new ...
-} or spcial objects like function which can be created by \texttt{function()}.
-Every recently created object might be assigned to a variable or property by \texttt{=} or \texttt{:} or be passed to a function as an argument.
-For the first two case we create a list of assignees.
-Having the list of possible assignees we do stepping and after every step we check those assignees values and if the value is changed, we consider the new value
- as a created object.
+It might be an object constructed by object initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new constructor()}) or function objects which can be created by \texttt{function()} statement.
+Every created object might be assigned to a statement (which is evaluated as a pointer) by \texttt{=} or object property by \texttt{:} or might be passed to a function as an argument.
+For the first case, by parsing the code we create the list of all statements. For the second case, we also create the full path of object property in the scope.
+We set a breakpoint at the line and once the breakpoint hits, we evaluate all statements in the list and we do stepping and after every step we check those assignees values and if the value is changed, we consider the new value as a created object.
 
@@
  %Then we can explain it like this: We set a breakpoint at the location object is created and we enable the object creation hook.  We do steppingfor one instruction and we get the reference.
+
+ %I was thinking that perhaps Fireforx 4.0 may support these features.I know that in the new version of JS (1.8.5) and Fireforx 4.0 there is a new function Object(), which is the main object constructor.
+If for all cases of object creations ({}, new, function),  the engine first calls this function then by modifying or setting a hook in this function we can track object creation.
+Do you know anyone in Mozilla team who can answer this question?Do you know whether firefox 4 still supports objectTrace flag or not?
+
+\begin{figure}[htp]
+\begin{verbatim}
+Case 1:
+20 x.y = new myConstructor();
+
+Case 2:
+19  parentObject = {
+20   	  self : {
+21  			x : 5
+22  }}
+
+Case 3:
+20 myFunction({myProperty:5})
+
+\end{verbatim}
+\caption{A few cases shows possible object creations.}
+\label{fig:objectCreation}
+\end{figure}
 

### 2010-10-20 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 However, it shows a new QP panel, centered on the source at line 29
-(Figure ~\ref{fig:example3}), the point of \testit{lastChange}.  To
+(Figure ~\ref{fig:example3}), the point of \textit{lastChange}.  To
 the right, the TraceData panels shows values of properties from the
@@
     x++;
-    f();
+    if (!stop) f();
   }
@@
 \end{figure}
-
-The scope id is kept as a variable in the scope, \texttt{\_scopeId}.
-As we said, a hook is set on the first instruction of the function defines the variable.
-Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function.
-For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
 
@@
 \section{JavaScript implementation}
-The JavaScript prototype is implemented as an extension to Firebug[] javasrcipt debugger.
+The JavaScript prototype is implemented as an extension to Firebug\cite{Firebug} javasrcipt debugger.
+In this section, first we explain technical details for the \textit{lastChange} implementation skipped in the previous section.
+Then we address other issues, such as re-execution, data collection and presentation.
 
-\subsection{Tracking object creation}
-Now we discuss two mentioned assumptions.
-In the standard JavaScript every object has a \texttt{watch()} function which receives two parameters, a property name and another function as a hook.
-Whenever the property with the given name changes the hook function is called.
-The issue with using this function is that it can only be applied to available objects.
+\subsection{Algorithm technical details}
+\subsubsection{\texttt{objectId()}}
+The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable.
+Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program.
+Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function.
+As a parameter it can be specified that the defined property is not enumerable.
+Then it is enough to assign a new generated id to this property.
+
+\subsubsection{\texttt{scopeId()}}
+The scope id is kept as a variable in the scope, \texttt{\_scopeId}.
+As we said, a hook is set on the first instruction of the function defines the variable.
+Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function.
+For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
+
+\subsubsection{\texttt{setPropertyChangeHook()}}
+To implement this operation, we use two features that are available in Firefox JavaScript engine.
+First, every regular JavaScript object has a \texttt{watch()} function which receives two parameters, a property name and another function as a callback.
+Whenever the property with the given name changes the calleback function is called.
+The hook is set by this function is enabled even if the property is removed and added again [ref].
+The issue with this function is that it can only be applied to available objects.
 However, at the beginning of re-execution there is no object available.
-To solve this issue we use a feature in Firefox JavaScript engine, setting a flag gives us the place the object created (e.g., myFile.js, line 24).
-Though this is a limited data it can help us to get a reference to the object once it is created.
-Therefore, at the reproduction point, debugger gets the creation location of \texttt{bar} and once the execution reaches to that location it gets a reference to the created object and sets a unique id for it.
+To solve this issue we use the second feature.
+Enabling a flag gives us the place the object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
+Though this is a limited data, it helps us to get a reference to the object once it is created.
+Then it is enough to set objet id and call \texttt{watch()} with the property name.
+Consider that in this way, we implicitly assume that the object will be created at the same place in the next re-executions.
+This assumption will be discussed later.
+
+In the next section, we explain the algorithm for getting a reference to the object after its creation.
+We could replace this algorithm with a much simpler algorithm if Firefox supported these two features.
+First instead of line number of object creation point, it gave us the program counter.
+Second, there was a way to hook object creation and get a reference to the created object.
+Having this two features, it was enough to set a hook at the instruction and once the execution reaches to instruction, we enable the object creation hook and we step one instruction and we get the reference to the object.
+
+\subsubsection{Tracking object creation}
+Having the source file url and the line number in wich the object created, we want to get a reference to the created object.
+Due to the fact that more than one object might be created in a line and there is no way to distinguish between them, we get references to all created objects.
+By parsing the source code we can find all statements that create a new object.
+It might be an object constructed by object initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new constructor()}) or function objects which can be created by \texttt{function()} statement.
+Every created object might be assigned to a statement (which is evaluated as a pointer) by \texttt{=} or object property by \texttt{:} or might be passed to a function as an argument.
+For the first case, by parsing the code we create the list of all statements. For the second case, we also create the full path of object property in the scope.
+We set a breakpoint at the line and once the breakpoint hits, we evaluate all statements in the list and we do stepping and after every step we check those assignees values and if the value is changed, we consider the new value as a created object.
+
+ %One solution is to assume that jsd has features that simplify it:first: Setting the flag (object track) returns the exact location of object creation instead of the line number.second: It is possible to set hook on object creation and this returns a reference to the created object.
+ %Then we can explain it like this: We set a breakpoint at the location object is created and we enable the object creation hook.  We do steppingfor one instruction and we get the reference.
+
+ %I was thinking that perhaps Fireforx 4.0 may support these features.I know that in the new version of JS (1.8.5) and Fireforx 4.0 there is a new function Object(), which is the main object constructor.
+If for all cases of object creations ({}, new, function),  the engine first calls this function then by modifying or setting a hook in this function we can track object creation.
+Do you know anyone in Mozilla team who can answer this question?Do you know whether firefox 4 still supports objectTrace flag or not?
+
+\begin{figure}[htp]
+\begin{verbatim}
+Case 1:
+20 x.y = new myConstructor();
+
+Case 2:
+19  parentObject = {
+20   	  newObject : {
+21  			x : 5
+22  }}
+
+Case 3:
+20 myFunction({myProperty:5});
+
+\end{verbatim}
+\caption{A few cases shows possible object creations.}
+\label{fig:objectCreation}
+\end{figure}
 

### 2010-10-21 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 Backward search from bug symptoms to defects-which cause the bug-is a natural way to debugging.
-However, due to the lack of support for easily bakward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy-if it is not pracatically impossible-demands a lot of effort from developers.
-Tracking origins to wrong values is a fundumental step in this process and any aid in this regard can greatly reduce the complexity of debugging for developers.
+However, due to the lack of support for easily backward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy-if it is not practically impossible-demands a lot of effort from developers.
+Tracking origins to wrong values is a fundamental step in this process and any aid in this regard can greatly reduce the complexity of debugging for developers.
 
@@
 Although \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires bug reproduction by re-executions.
-In other words \textit{bug reproduciblity} (i.e., a test case is available which reproduces the bug) is the only prerequisite for \textit{lastChange} functinality.
+In other words \textit{bug reproducibility} (i.e., a test case is available which reproduces the bug) is the only prerequisite for \textit{lastChange} functionality.
 
-As a proof of concept, we developed \textit{Querypointer}, a prototype which enhances Firebug JavaScript debugger with \textit{lastChange} feature.
+As a proof of concept, we developed \textit{Querypointer}, a prototype which enhances a popular JavaScript debugger, Firebug, with \textit{lastChange} feature.
 Moreover, \textit{Querypointer} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
@@
 According to \cite{LaToza}, developers spend about fifty percent of their time debugging.
-Therefore, every improvement to debugging techniques and tools can considerably save developers' time and improve programs' quality.
+Therefore, enhancements to debugging techniques and tools can considerably save developers' time and improve programs' quality.
 
 Locating defects cause the bug is the main part of debugging.
-A common strategy for locating defects is starting from bug symptoms and backward movement by following the origings to wrong values.
+A common strategy for locating defects is starting from bug symptoms and backward movement by following the origins to wrong values.
 While this strategy seems straightforward and effective, applying this strategy using traditional methods is complicated.
 There are two traditional approaches to debugging, breakpoint-based and log-based debugging.
-None of these approaches assist developer in finding origings to a wrong value.
-It is due to developer to search source files, find the list of possible origings to a wrong value and set breakpoints or insert log statements in a way that covers all possible origins.
+None of these approaches assist developer in finding origins to a wrong value.
+It is due to developer to search source files, find the list of possible origins to a wrong value and set breakpoints or insert log statements in a way that covers all possible origins.
 
@@
 It is very common that developer has to repeat this step several times due to insufficient collected data.
-Once the adequate data is collected, it still requires analysis and understanding.
+Once the adequate data is collected, it still requires analyzing and understanding.
 Developers usually end up in dealing with long log files and analyzing huge collected data.
 
-Our proposal is a new functionality in debuggers which locates the origin of a wrong value, call it \textit{lastChange}.
-The only prerequisite for \textit{lastChange} functionality is bug reproduciblity (i.e., there is a test case which reproduces the bug).
-Assume that the program execution is paused on a breakpoint and the developer is suspicious about the value of an object property or variable.
-The developer selects \textit{lastChange} on the value and it is due to debugger to locate and shows the last change of object property or variable.
+To address the mentioned problems, we propose a new functionality in debuggers, \textit{lastChange}, which locates the origin of a wrong value.
+It works based on program re-execution similar to the practice in using breakpoints and log statements.
+Contrary to other replay-based alogrithms which require the same re-executions (instruction by instruction), the only prerequisite for \textit{lastChange} functionality is bug reproducibility (i.e., there is a test case which reproduces the bug).
+Assume that the program execution is paused on a breakpoint and the developer is suspicious about the value of an object property or a variable.
+The developer queries \textit{lastChange} on the value and it is due to debugger to locate and shows the last change of the object property or variable.
 Debugger reproduces the buggy execution and collects limited data and once the execution reaches the same place (i.e., the same breakpoint hit), call it \textit{reproduction point}, it pauses the execution, analyzes the collected data and shows the location of the last change to the developer.
-Developer can also examine the program state at the located point of execution, and ask for a new \textit{lastChange} at this point.
+The developer can also examine the program state at the located point of execution, and continue debugging by more \textit{lastChange} queries from that point.
 
-Our contribution in this paper is the algorightm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point.
+Our contribution in this paper is the algorithm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point.
 The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibiltily of the algorithm with \textit{Querypointer}, an implementation extending the Firebug JavaScript debugger.
-\textit{Querypointer} also provides mechanism for automated bug reproduction, and a centralized user interface which summarizes investigated execution points and collected results.
+We demonstrate the feasibility of the algorithm with \textit{Querypointer}, an implementation extending the Firebug JavaScript debugger.
+\textit{Querypointer} also provides mechanism for automated bug reproduction, and a novel user interface which summarizes investigated execution points and collected results.
 
@@
 In section 4, we explain the details of the JavaScript prototype implementation.
+We discuss the effect of non-determinism on the \textit{lastChange} algorithm.
+Section 6 contains an evaluation of \text{lastChange} functionality.
 
@@
 and \texttt{bar()}. As developers we often encounter function calls
-which seem perpheral to our current concern; they may have been added
+which seem peripheral to our current concern; they may have been added
 by another developer, or we may have forgotten their exact properties
@@
 interesting, and what they do in practice may cause bugs.
-
-To start debugging, the developer sets a breakpoint
-on line 22 and once the button is clicked execution is paused at line
-22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
-execution is paused. Firebug has several panels (e.g., HTML, CSS,
-Script, DOM, etc.) that each demonstrate one aspect of the Web page.
-The Script panel contains the list of all loaded source
-files and regular debugging facilities such as setting breakpoints and
-stepping. To the right of the script panel, the Watch panel shows the program state
-where the developer can examine object and variable values. In our case, the
-\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
 
@@
 
-\begin{figure}[htp]
-\includegraphics{5-example-points.jpg}
-\caption{The examinated points before locating the defect.}
-\label{fig:example-points}
-\end{figure}
+To start debugging, the developer sets a breakpoint
+on line 22 and once the button is clicked execution is paused at line
+22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
+execution is paused. Firebug has several panels (e.g., HTML, CSS,
+Script, DOM, etc.) that each demonstrate one aspect of the Web page.
+The Script panel contains the list of all loaded source
+files and regular debugging facilities such as setting breakpoints and
+stepping. To the right of the script panel, the Watch panel shows the program state
+where the developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
 
@@
 resemble the Script and Watch panels, but they show data collected by
-the debugger at an execution point which has now past: these are
+the debugger at an execution point which is now past: these are
 'traces' or 'logs' of information collected during the re-execution.
+
+Looking at line 29, it seems that something is wrong with
+\texttt{myCondition.value} which causes line 29 execution. The
+developer examines \texttt{myCondition.value} and it is
+\texttt{undefined}. The next step is to know when this property got
+this value. To do so, the developer runs \textit{lastChange} command
+on \texttt{myCondition.value} at this point. Debugger re-executes the
+execution and pauses at the reproduction point and shows line 25-the
+place \texttt{undefined} value is assigned to
+\texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
+clear that the bug occurs because \texttt{oldValue} is
+\texttt{undefined} once execution reaches line 25.
+
+As demonstrated in Figure ~\ref{fig:example-points}, the developer
+examined three points of execution. The first point was the breakpoint set by the developer.
+The second and third points preceded the breakpoint in time.
+All three points-the history
+of the search for the defect-are available through the debugger's
+interface. On the top of the left panel in Figure ~\ref{fig:example4}
+there is an opened list which shows all three examined points. The
+first one is the breakpoint on line 22, the second one is the point
+which is the last change of \texttt{myObject.myProperty} before
+reaching the breakpoint and finally the last one is the point of
+execution in which \texttt{myCondition.value} gets the
+\texttt{undefined} value. Moreover, the source lines related to these
+points are tagged with red-cycle icons.
+
+\begin{figure}[htp]
+\includegraphics{5-example-points.jpg}
+\caption{The examined points before locating the defect.}
+\label{fig:example-points}
+\end{figure}
 
@@
 \end{figure*}
-
-Looking at line 29, it seems that something is wrong with
-\texttt{myCondition.value} which causes line 29 execution. The
-developer examines \texttt{myCondition.value} and it is
-\texttt{undefined}. The next step is to know when this property got
-this value. To do so, the developer runs \textit{lastChange} command
-on \texttt{myCondition.value} at this point. Debugger re-executes the
-execution and pauses at the reproduction point and shows line 25-the
-place \texttt{undefined} value is assigned to
-\texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
-clear that the bug occurs because \texttt{oldValue} is
-\texttt{undefined} once execution reaches line 25.
-
-As demonstrated in Figure ~\ref{fig:example-points}, the developer
-examinated three points of execution. The first point was the breakpoint set by the developer.
-The second and third points preceded the breakpoint in time.
-All three points-the history
-of the search for the defect-are available through the debugger's
-interface. On the top of the left panel in Figure ~\ref{fig:example3}
-there is an opened list which shows all three examinated points. The
-first one is the breakpoint on line 22, the second one is the point
-which is the last change of \texttt{myObject.myProperty} before the
-reaching the breakpoint and finally the last one is the point of
-execution in which \texttt{myCondition.value} gets the
-\texttt{undefined} value. Moreover, the source lines related to these
-points are tagged with red-cycle icons.
 
@@
 
-\section{Converting \textit{lastChange} result to a conditional breakpoint}
+\section{Discussion}
+\subsection{Converting \textit{lastChange} result to a conditional breakpoint}
 We believe that in many cases it is possible to convert the \textit{lastChange} result to a conditional breakpoint and therefore debugger is able to pause at the point
@@
 %---------------------------------------------------------------------------------------------------
-\section{Reproducible Non-deterministic Execution}
+\subsection{Reproducible Non-deterministic Execution}
 Thus far we have not discussed problems caused by mul-tiple threads or other sources of non-deterministic execu-tions.
@@
 \section{Evaluation}
+\subsection{\textit{lastChange} effectiveness}
+
 \subsection{Execution overhead analysis}
-%If we assume for every change event k additionial instructions should be executed and the number of instructions executed in one execution is n and the number of change %events is m then the total amount of instructions is n+mk.
-The overhead is mk/n.
-for m=10^3, k=10^2 and n=10^10 the overhead is very low about 10^-5.
+If we assume that the total number of instructions in an execution is $n$ and $m$ change event happens during one execution and for every change event $k$ additionial instructions should be executed, the execution overhead of our approach is $mk/n$.
+For $m=10^3$, $k=10^2$ and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
 

### 2010-10-21 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 In JavaScript, every available variable in a frame comes from one of the scopes in the frame's scope chain.
-There are five different scope types: global, local, with, catch, closure.
 We explain each case separately.
@@
 Once developer asks for the last change of variable \texttt{foo} at the reproduction point, debugger first determines the variable's scope as follows: it iterates over the scopes in the scope chain and the first scope which has a variable with the same name is the variable's scope.
-There are five different scope types: local, global, \texttt{with}, closure, \texttt{catch}.
+There are five different scope types: local, global, \texttt{with}, closure and \texttt{catch}.
 We explain these cases in two groups.
@@
 For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be changed in lines 10 to 23.
-Therefore, after locating the function in which the variable is defined, it is enough to parse the code inside the function block and set a hook on all lines where the variable is assigned a new value.% TODO lines or instruction???
+Therefore, after locating the function in which the variable is defined, it is enough to parse the code inside the function block and set a hook on all lines where the variable is assigned a new value.
+% TODO lines or instruction???
 We also set a hook at the first line of the function which is corresponding to the line variable is defined.
@@
 These two cases are different due the fact that \texttt{var1} in \texttt{firstChild} is a local variable but in \texttt{secondChild} is a closure variable.
-
-Everytime one of the hooks hits a new change event is inserted to the list of change events.
-During execution the same variable might be changed several times but in different scopes.
-Figure ~\ref{fig:recursive} demonstrates one case that a scope identifier is necessary for locating the right answer.
-In this case the same variable \texttt{x} is changed several times but in different scopes due to the recursive calls.
-Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
 
@@
 
+Everytime one of the hooks hits a new change event is inserted to the list of change events.
+During execution the same variable might be changed several times but in different scopes.
+Figure ~\ref{fig:recursive} demonstrates a case that the same variable \texttt{x} is changed several times but in different scopes due to the recursive calls.
+Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
+To address this issue, we employ \texttt{scopeId()} operation-explained in the next section-which returns a unique id for a scopes during on execution.
+The scope id is kept at every variable change event.
+Once the execution reaches the reproduction point, using variable's scope id, the last change is recognized.
+
 \begin{figure}[htp]
@@
 
-To address this issue, debugger does a dependency analysis between all \textit{lastChange} queries and computes the additional data required to be collected at each point.
-For example in the mentioned case, \texttt{baz} id- if it is available- should be collected at all points \texttt{x} changes.
+To address this issue, we use Algorithm \ref{dependency-analysis}, to create the list of additional data should be collected at a change event.
+This algorithm does does a dependency analysis between all \textit{lastChange} queries and computes the list additional data required to be collected at each change event.
+For example in the mentioned case, \texttt{baz} id-if it is available- should be collected at all points \texttt{x} changes.
 Having this additional data, locating point C, using \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
@@
 \FOR{$q$ in $queries$} 
- \FOR {$p$ was defined at the $q$ result}
+ \FOR {$p$ is defined at the $q$ result}
    \IF {$p$ is a lastChange on object property} 
-     \STATE property id should be stored at $q$ change events. 
+     \STATE the property owner id should be stored at $q$ change events. 
    \ELSIF {$p$ is a lastChange on variable} 
-     \STATE variable scope id should be stored at $q$ change events.
+     \STATE the variable scope id should be stored at $q$ change events.
 	 \ENDIF 

### 2010-10-21 papers/pldi2011/sigplanconf-template.tex

@@
 
-Looking at line 29, it seems that something is wrong with
-\texttt{myCondition.value} which causes line 29 execution. The
-developer examines \texttt{myCondition.value} and it is
-\texttt{undefined}. The next step is to know when this property got
-this value. To do so, the developer runs \textit{lastChange} command
-on \texttt{myCondition.value} at this point. Debugger re-executes the
-execution and pauses at the reproduction point and shows line 25-the
-place \texttt{undefined} value is assigned to
-\texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
-clear that the bug occurs because \texttt{oldValue} is
-\texttt{undefined} once execution reaches line 25.
-
-As demonstrated in Figure ~\ref{fig:example-points}, the developer
-examinated three points of execution. The first point was the breakpoint set by the developer.
-The second and third points preceded the breakpoint in time.
-All three points-the history
-of the search for the defect-are available through the debugger's
-interface. On the top of the left panel in Figure ~\ref{fig:example3}
-there is an opened list which shows all three examinated points. The
-first one is the breakpoint on line 22, the second one is the point
-which is the last change of \texttt{myObject.myProperty} before the
-reaching the breakpoint and finally the last one is the point of
-execution in which \texttt{myCondition.value} gets the
-\texttt{undefined} value. Moreover, the source lines related to these
-points are tagged with red-cycle icons.
-
 Notice that in our example, \textit{lastChange} combines some aspects
@@
 \end{figure}
+
+Everytime one of the hooks hits a new change event is inserted to the list of change events.
+During execution the same variable might be changed several times but in different scopes.
+Figure ~\ref{fig:recursive} demonstrates a case that the same variable \texttt{x} is changed several times but in different scopes due to the recursive calls.
+Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
+To address this issue, we employ \texttt{scopeId()} operation-explained in the next section-which returns a unique id for a scopes during on execution.
+The scope id is kept at every variable change event.
+Once the execution reaches the reproduction point, using variable's scope id, the last change is recognized.
 
@@
 \section{JavaScript implementation}
-The JavaScript prototype is implemented as an extension to Firebug\cite{Firebug} javasrcipt debugger.
-In this section, first we explain technical details for the \textit{lastChange} implementation skipped in the previous section.
-Then we address other issues, such as re-execution, data collection and presentation.
+We implemented \textit{Querypointer}, an Extension to Firebug JavaScript debugger, which provides \textit{lastChange} functionality.
+Firebug is an add-on of Firefox browser.
+Firefox JavaScript engine provides a JavaScript debugging interface and \textit{Querypointer} is developed over this interface.
+The debugging support in JavaScript comparing to more traditional languages such as Java and C\# is less comprehensive.
+Some part of this flaw is due to the dynamic nature of JavaScript.
+For example, JavaScript does not have classes and therefore setting watchpoint on properties before program execution is not possible.
+We explain how we could overcome these limitations and provide required operations for \textit{lastChange} algorithm implementation.
+Moreover, we breifly describe mechanisms for automated execution reproduction, data collection and presentation.
 
@@
 19  parentObject = {
-20   	  self : {
+20   	  newObject : {
 21  			x : 5
@@
 Case 3:
-20 myFunction({myProperty:5})
+20 myFunction({myProperty:5});
 

### 2010-10-21 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 \section{JavaScript implementation}
-The JavaScript prototype is implemented as an extension to Firebug\cite{Firebug} javasrcipt debugger.
-In this section, first we explain technical details for the \textit{lastChange} implementation skipped in the previous section.
-Then we address other issues, such as re-execution, data collection and presentation.
+We implemented \textit{Querypointer}, an Extension to Firebug JavaScript debugger, which provides \textit{lastChange} functionality.
+Firebug is an add-on of Firefox browser.
+Firefox JavaScript engine provides a JavaScript debugging interface and \textit{Querypointer} is developed over this interface.
+The debugging support in JavaScript comparing to more traditional languages such as Java and C\# is less evolved.
+Some part of this flaw is due to the dynamic nature of JavaScript.
+For example, JavaScript does not have classes and therefore setting watchpoint on properties before program execution is not possible.
+We explain how we could overcome these limitations and provide required operations for \textit{lastChange} algorithm implementation.
+Moreover, we breifly describe mechanisms for automated execution reproduction, data collection and presentation.
 
 \subsection{Algorithm technical details}
-\subsubsection{\texttt{objectId()}}
-The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable.
-Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program.
-Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function.
-As a parameter it can be specified that the defined property is not enumerable.
-Then it is enough to assign a new generated id to this property.
+\subsubsection{\texttt{objectId()} operation}
+\texttt{objectId()} operation receives a regular JavaScript object and returns an id which is unique during one execution.
+This operation keeps the object id in an object property with name \texttt{\_objectId}.
+Once this operation receives an object, it returns \texttt{\_objectId} value if this property is already defined, otherwise it generates a new id and sets this property object.
+To set the property, it calls \texttt{defineProperty} standard JavaScript function.
+\texttt{defineProperty} receives an argument which specifies whether the property is enumerable or not.
+By setting the enumerable field \texttt{false} for \texttt{\_objectId}, this property will not apear in \texttt{for(property in object)} loops and therfore has no effect on the program execution.
+Consider that \texttt{\_objectId} is not set for all objects but only those objects that need an id.
 
-\subsubsection{\texttt{scopeId()}}
-The scope id is kept as a variable in the scope, \texttt{\_scopeId}.
-As we said, a hook is set on the first instruction of the function defines the variable.
-Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function.
-For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
+\subsubsection{\texttt{scopeId()} operation}
+The scope id is kept as a variable with name \texttt{\_scopeId} in the scope.
+We explained that we set a hook at the first instruction of the function which defines the variable.
+Once this hook hits, \texttt{\_scopeId} is set by calling \texttt{eval()} function.
+For example, executing \texttt{eval( var \_scopeId = 10)} creates a variable with name \texttt{\_scopeId} and value \texttt{10} in the local scope which is our interesting scope.
 

### 2010-10-21 papers/pldi2011/sigplanconf-template.tex

@@
 Firefox JavaScript engine provides a JavaScript debugging interface and \textit{Querypointer} is developed over this interface.
-The debugging support in JavaScript comparing to more traditional languages such as Java and C\# is less comprehensive.
+The debugging support in JavaScript comparing to more traditional languages such as Java and C\# is less evolved.
 Some part of this flaw is due to the dynamic nature of JavaScript.
@@
 \subsection{Algorithm technical details}
-\subsubsection{\texttt{objectId()}}
-The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable.
-Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program.
-Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function.
-As a parameter it can be specified that the defined property is not enumerable.
-Then it is enough to assign a new generated id to this property.
+\subsubsection{\texttt{objectId()} operation}
+\texttt{objectId()} operation receives a regular JavaScript object and returns an id which is unique during one execution.
+This operation keeps the object id in an object property with name \texttt{\_objectId}.
+Once this operation receives an object, it returns \texttt{\_objectId} value if this property is already defined, otherwise it generates a new id and sets this property object.
+To set the property, it calls \texttt{defineProperty} standard JavaScript function.
+\texttt{defineProperty} receives an argument which specifies whether the property is enumerable or not.
+By setting the enumerable field \texttt{false} for \texttt{\_objectId}, this property will not apear in \texttt{for(property in object)} loops and therfore has no effect on the program execution.
+Consider that \texttt{\_objectId} is not set for all objects but only those objects that need an id.
 
-\subsubsection{\texttt{scopeId()}}
-The scope id is kept as a variable in the scope, \texttt{\_scopeId}.
-As we said, a hook is set on the first instruction of the function defines the variable.
-Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function.
-For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.
+\subsubsection{\texttt{scopeId()} operation}
+The scope id is kept as a variable with name \texttt{\_scopeId} in the scope.
+We explained that we set a hook at the first instruction of the function which defines the variable.
+Once this hook hits, \texttt{\_scopeId} is set by calling \texttt{eval()} function.
+For example, executing \texttt{eval( var \_scopeId = 10)} creates a variable with name \texttt{\_scopeId} and value \texttt{10} in the local scope which is our interesting scope.
 
-\subsubsection{\texttt{setPropertyChangeHook()}}
-To implement this operation, we use two features that are available in Firefox JavaScript engine.
-First, every regular JavaScript object has a \texttt{watch()} function which receives two parameters, a property name and another function as a callback.
+\subsubsection{\texttt{setPropertyChangeHook()} operation}
+We implement a slightly different version of this operation.
+Setting a flag into the Firefox JavaScript engine we can get the place am object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
+We can assume that an object is created in the same place in the next re-executions.
+This assumption does not lead to a wrong answer.
+We will discuss it in the next section when we discuss the effect of non-determinism.
+Having this assumption, it is enough to set property change hook for the objects created at one place.
+
+The Firefox JavaScript engine supports watching property changes in an object.
+Every object has a \texttt{watch()} function which receives two parameters, a property name and another function as the callback.
 Whenever the property with the given name changes the calleback function is called.
-The hook is set by this function is enabled even if the property is removed and added again [ref].
-The issue with this function is that it can only be applied to available objects.
-However, at the beginning of re-execution there is no object available.
-To solve this issue we use the second feature.
-Enabling a flag gives us the place the object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
-Though this is a limited data, it helps us to get a reference to the object once it is created.
-Then it is enough to set objet id and call \texttt{watch()} with the property name.
-Consider that in this way, we implicitly assume that the object will be created at the same place in the next re-executions.
-This assumption will be discussed later.
+The hook is set by this function remains enabled even if the property is deleted and defined again.
+This function can only be applied to avaialbe objects.
+However, at the beginning of execution, no object excepting the global object is available.
 
-In the next section, we explain the algorithm for getting a reference to the object after its creation.
-We could replace this algorithm with a much simpler algorithm if Firefox supported these two features.
-First instead of line number of object creation point, it gave us the program counter.
-Second, there was a way to hook object creation and get a reference to the created object.
-Having this two features, it was enough to set a hook at the instruction and once the execution reaches to instruction, we enable the object creation hook and we step one instruction and we get the reference to the object.
+If we could get a reference to the object just after its creation, we could use \texttt{watch()} function to monitor property changes in the object.
+In the next section we explain the algorithm we devised for this purpose by parsing and analyzing the code.
+This algorithm could be replaced by a much simpler one if Firefox debugging interface gives us the program counter of object creation instead of line number and also provides object creation hook.
+By these assumptions, it was enough to set a hook on the object creation location.
+Once the execution reaches this location, by enabling object creation hook, we could get a reference to the new object.
 

### 2010-10-21 trunk/papers/pldi2011/sigplanconf-template.tex
section 3, only reform paragraphs no edits

@@
 
-The story starts when developer examines the program state at a breakpoint hit and asks for the \textit{lastChange} of a value.
-The \textit{lastChange} algorithm is based on program re-execution.
-Therefore it is assumed that the execution can be reproduced automatically (e.g., by a given test case) or with the developer's assistance.
-The breakpoint hit becomes the \textit{reproduction point}.
-Debugger sets hooks on all instructions that might be the result of \textit{lastChange} query, re-executes the program, at every hook hit, \textit{change event}, collects limited data and once the execution reaches the reproduction point, it analyzes the collected data and shows the result.
-The result is a partial snapshot of the program state at the execution point that last change occured.
+The story starts when developer examines the program state at a
+breakpoint hit and asks for the \textit{lastChange} of a value. The
+\textit{lastChange} algorithm is based on program
+re-execution. Therefore it is assumed that the execution can be
+reproduced automatically (e.g., by a given test case) or with the
+developer's assistance. The breakpoint hit becomes the
+\textit{reproduction point}. Debugger sets hooks on all instructions
+that might be the result of \textit{lastChange} query, re-executes the
+program, at every hook hit, \textit{change event}, collects limited
+data and once the execution reaches the reproduction point, it
+analyzes the collected data and shows the result. The result is a
+partial snapshot of the program state at the execution point that last
+change occured.
 
-As we shown in the previous section, a \textit{lastChange} query can be performed on the result of another \textit{lastChange} query.
-If we name the reproduction point \textit{R}, we can write the first \textit{lastChange} in the introductory example in this form: \textit{lastChange(R, myObject.myProperty)}.
-It means that this query is defined at \textit{R}.
-If we name the result of this query \textit{A}, we can write the second \textit{lastChange} in this form: \textit{lastChange(A, myCondition.value)}.
-In this way, a sequence of \textit{lastChange} queries with any length can be defined.
+As we shown in the previous section, a \textit{lastChange} query can
+be performed on the result of another \textit{lastChange} query. If we
+name the reproduction point \textit{R}, we can write the first
+\textit{lastChange} in the introductory example in this form:
+\textit{lastChange(R, myObject.myProperty)}. It means that this query
+is defined at \textit{R}. If we name the result of this query
+\textit{A}, we can write the second \textit{lastChange} in this form:
+\textit{lastChange(A, myCondition.value)}. In this way, a sequence of
+\textit{lastChange} queries with any length can be defined.
 
-\textit{lastChange} can be called on two different types of values: An object property or a variable value.
-In JavaScript, every available variable in a frame comes from one of the scopes in the frame's scope chain.
-We explain each case separately.
+\textit{lastChange} can be called on two different types of values: An
+object property or a variable value. In JavaScript, every available
+variable in a frame comes from one of the scopes in the frame's scope
+chain. We explain each case separately.
 
 \subsection{\textit{lastChange} on object propery}
-To simplify the algorithm explanation and avoid technical details, we assume two basic operations and later we explain the details of these two operations.
-The first opertion is \texttt{objectId()} which gets a JavaScript object and returns an integer as its identifier.
-This identifier is unique for every object during one execution.
-The second operation is \texttt{setPropertyChangeHook()} which gets function as the callback and a string as the property name like \texttt{foo}.
-Whenever property \texttt{foo} in any object changes the callback will be called.
-The callback function receives a reference to the owner of \texttt{foo}.
+To simplify the algorithm explanation and avoid technical details, we
+assume two basic operations and later we explain the details of these
+two operations. The first opertion is \texttt{objectId()} which gets a
+JavaScript object and returns an integer as its identifier. This
+identifier is unique for every object during one execution. The second
+operation is \texttt{setPropertyChangeHook()} which gets function as
+the callback and a string as the property name like
+\texttt{foo}. Whenever property \texttt{foo} in any object changes the
+callback will be called. The callback function receives a reference to
+the owner of \texttt{foo}.
 
@@
 \includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
-\caption{The list of property \texttt{foo} change events and \texttt{bar} id at the reproduction point which identifies the last change of \texttt{bar.foo} in the list.
-Column 3 is also a change of the object we want to study, id 1010, but it is not the last change; Column 5 is also a change of a property \texttt{foo} but its not for the object we are interested in.}
+\caption{The list of property \texttt{foo} change events and
+  \texttt{bar} id at the reproduction point which identifies the last
+  change of \texttt{bar.foo} in the list. Column 3 is also a change of
+  the object we want to study, id 1010, but it is not the last change;
+  Column 5 is also a change of a property \texttt{foo} but its not for
+  the object we are interested in.}
 \label{fig:foo-changes1}
@@
 
-Once developer asks for the last change of \texttt{bar.foo} at the reproduction point, debugger calls \texttt{setPropertyChangeHook()} with \texttt{foo} as the property name and re-executes the program.
-Whenever \texttt{foo} changes and the callback function is called, debugger first calls \texttt{objectId()} on the \texttt{foo} owner object.
-Then it stores owner id and stack frame locations.
-The reason we keep object id instead of a reference to the object itself is to let garbage collector to destroy dead objects.
-Whenever the execution reaches the reproduction point it looks at the history of \texttt{foo} changes and finds the last \texttt{foo} change with the same object id as \texttt{bar} id at the reproduction point.
-Figure ~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change events in a hypothetical execution.
-\texttt{bar} id at the reproduction point is 1010, so the last change of \texttt{bar.foo} is the fourth column.
+Once developer asks for the last change of \texttt{bar.foo} at the
+reproduction point, debugger calls \texttt{setPropertyChangeHook()}
+with \texttt{foo} as the property name and re-executes the
+program. Whenever \texttt{foo} changes and the callback function is
+called, debugger first calls \texttt{objectId()} on the \texttt{foo}
+owner object. Then it stores owner id and stack frame locations. The
+reason we keep object id instead of a reference to the object itself
+is to let garbage collector to destroy dead objects. Whenever the
+execution reaches the reproduction point it looks at the history of
+\texttt{foo} changes and finds the last \texttt{foo} change with the
+same object id as \texttt{bar} id at the reproduction point. Figure
+~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change
+events in a hypothetical execution. \texttt{bar} id at the
+reproduction point is 1010, so the last change of \texttt{bar.foo} is
+the fourth column.
 
 \subsection{\textit{lastChange} on variable} 
-In JavaScript, every frame has a scope chain and every available variable in the frame comes from one of the scopes in the frame's scope chain.
-Once developer asks for the last change of variable \texttt{foo} at the reproduction point, debugger first determines the variable's scope as follows: it iterates over the scopes in the scope chain and the first scope which has a variable with the same name is the variable's scope.
-There are five different scope types: local, global, \texttt{with}, closure and \texttt{catch}.
-We explain these cases in two groups.
+In JavaScript, every frame has a scope chain and every available
+variable in the frame comes from one of the scopes in the frame's
+scope chain. Once developer asks for the last change of variable
+\texttt{foo} at the reproduction point, debugger first determines the
+variable's scope as follows: it iterates over the scopes in the scope
+chain and the first scope which has a variable with the same name is
+the variable's scope. There are five different scope types: local,
+global, \texttt{with}, closure and \texttt{catch}. We explain these
+cases in two groups.
 
 \subsubsection{global and \texttt{with} scopes}
-Global scope is the the most outer scope in the scope chain and it is also refered as global object which is usually \texttt{window} object.
-This scope is a regular JavaScript object and therefore every global variable is a property of global object.
-Similar to global scope, \texttt{with} scopes are also regular objects.
-A \texttt{with} scope is created by a \texttt{with()} block with an object as the parameter.
-Every property of passed object is available inside the block as a variable.
-Debugger treats the case where variable's scope is global or \texttt{with}, like \textit{lastChange} on an object property.
+Global scope is the the most outer scope in the scope chain and it is
+also refered as global object which is usually \texttt{window}
+object. This scope is a regular JavaScript object and therefore every
+global variable is a property of global object. Similar to global
+scope, \texttt{with} scopes are also regular objects. A \texttt{with}
+scope is created by a \texttt{with()} block with an object as the
+parameter. Every property of passed object is available inside the
+block as a variable. Debugger treats the case where variable's scope
+is global or \texttt{with}, like \textit{lastChange} on an object
+property.
 
 \subsubsection{local, closure and \texttt{catch} scopes}
-Local scope refers to the most nested scope in the scope chain.
-Closure scope refers to the scope which is created once a function is defined.
-Catch scope is the scope created in the catch block of try-catch statements and contains the exception variable.
-These scopes are not necessarily regular JavaScript objects.
-Therefore, to track changes to a variable in these scopes we use a different strategy.
+Local scope refers to the most nested scope in the scope
+chain. Closure scope refers to the scope which is created once a
+function is defined. Catch scope is the scope created in the catch
+block of try-catch statements and contains the exception
+variable. These scopes are not necessarily regular JavaScript
+objects. Therefore, to track changes to a variable in these scopes we
+use a different strategy.
 
@@
 
-A variable in these types of scope can only be changed in the function the variable is defined or the nested fuctions.
-For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be changed in lines 10 to 23.
-Therefore, after locating the function in which the variable is defined, it is enough to parse the code inside the function block and set a hook on all lines where the variable is assigned a new value.
-% TODO lines or instruction???
-We also set a hook at the first line of the function which is corresponding to the line variable is defined.
-In Figure ~\ref{fig:js-closure}, if the execution is paused at line 17 and the last change of \texttt{var1} is queried, two hooks on lines 16 and 17 will be set, but if the execution is paused at line 20 , four hooks on lines 11, 12, 14, 20 will be set.
-These two cases are different due the fact that \texttt{var1} in \texttt{firstChild} is a local variable but in \texttt{secondChild} is a closure variable.
+A variable in these types of scope can only be changed in the function
+the variable is defined or the nested fuctions. For example in Figure
+~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
+changed in lines 10 to 23. Therefore, after locating the function in
+which the variable is defined, it is enough to parse the code inside
+the function block and set a hook on all lines where the variable is
+assigned a new value. % TODO lines or instruction??? 
+We also set a hook at the first line of the function which is
+corresponding to the line variable is defined. In Figure
+~\ref{fig:js-closure}, if the execution is paused at line 17 and the
+last change of \texttt{var1} is queried, two hooks on lines 16 and 17
+will be set, but if the execution is paused at line 20 , four hooks on
+lines 11, 12, 14, 20 will be set. These two cases are different due
+the fact that \texttt{var1} in \texttt{firstChild} is a local variable
+but in \texttt{secondChild} is a closure variable.
 
@@
 \end{verbatim}
-\caption{A recursive call trace demonstrates the need for scope id. Querying \textit{lastChange} on \texttt{x} at point C should return point A not B.}
+\caption{A recursive call trace demonstrates the need for scope
+  id. Querying \textit{lastChange} on \texttt{x} at point C should
+  return point A not B.}
 \label{fig:recursive}
@@
 
-Everytime one of the hooks hits a new change event is inserted to the list of change events.
-During execution the same variable might be changed several times but in different scopes.
-Figure ~\ref{fig:recursive} demonstrates a case that the same variable \texttt{x} is changed several times but in different scopes due to the recursive calls.
-Without the scope id calling \textit{lastChange(x)} at point C will return point B while the right answer is point A.
-To address this issue, we employ \texttt{scopeId()} operation-explained in the next section-which returns a unique id for a scopes during on execution.
-The scope id is kept at every variable change event.
-Once the execution reaches the reproduction point, using variable's scope id, the last change is recognized.
+Everytime one of the hooks hits a new change event is inserted to the
+list of change events. During execution the same variable might be
+changed several times but in different scopes. Figure
+~\ref{fig:recursive} demonstrates a case that the same variable
+\texttt{x} is changed several times but in different scopes due to the
+recursive calls. Without the scope id calling \textit{lastChange(x)}
+at point C will return point B while the right answer is point A. To
+address this issue, we employ \texttt{scopeId()} operation-explained
+in the next section-which returns a unique id for a scopes during on
+execution. The scope id is kept at every variable change event. Once
+the execution reaches the reproduction point, using variable's scope
+id, the last change is recognized.
 
@@
 \includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
-\caption{The list of variable \texttt{foo} change events and the \texttt{foo}'s scope id at the reproduction point which identifies the last change.}
+\caption{The list of variable \texttt{foo} change events and the
+  \texttt{foo}'s scope id at the reproduction point which identifies
+  the last change.}
 \label{fig:foo-changes2}
@@
 \subsection{\textit{lastChange} on \textit{lastChange}}
-The algorithm we explained so far needs an enhancement to support longer sequence of \textit{lastChange}s. We explain first the issue and then the solution. Consider the following points:
+The algorithm we explained so far needs an enhancement to support
+longer sequence of \textit{lastChange}s. We explain first the issue
+and then the solution. Consider the following points:
 
@@
  \end{center}
-According to the algorithm explained in the previous section none of the points B and C can be identified before reaching point A.
-Therefore, all \texttt{x} changes for piont B and all \texttt{y} changes for point C are stored.
-Once the execution reaches point A, and the exact \texttt{bar} id reveals, point B can be identified among the change events in the history of \texttt{x} changes.
-The problem arises in recognizing point C.
-To recognize point C, we need \texttt{baz} id at point B, but B is a past program state, and \texttt{baz} id has not been collected at this point.
+According to the algorithm explained in the previous section none of
+the points B and C can be identified before reaching point
+A. Therefore, all \texttt{x} changes for piont B and all \texttt{y}
+changes for point C are stored. Once the execution reaches point A,
+and the exact \texttt{bar} id reveals, point B can be identified among
+the change events in the history of \texttt{x} changes. The problem
+arises in recognizing point C. To recognize point C, we need
+\texttt{baz} id at point B, but B is a past program state, and
+\texttt{baz} id has not been collected at this point.
 
-To address this issue, we use Algorithm \ref{dependency-analysis}, to create the list of additional data should be collected at a change event.
-This algorithm does does a dependency analysis between all \textit{lastChange} queries and computes the list additional data required to be collected at each change event.
-For example in the mentioned case, \texttt{baz} id-if it is available- should be collected at all points \texttt{x} changes.
-Having this additional data, locating point C, using \texttt{baz} id at point B is straightforward (Figure ~\ref{fig:lastchange-lastchange}).
+To address this issue, we use Algorithm \ref{dependency-analysis}, to
+create the list of additional data should be collected at a change
+event. This algorithm does does a dependency analysis between all
+\textit{lastChange} queries and computes the list additional data
+required to be collected at each change event. For example in the
+mentioned case, \texttt{baz} id-if it is available- should be
+collected at all points \texttt{x} changes. Having this additional
+data, locating point C, using \texttt{baz} id at point B is
+straightforward (Figure ~\ref{fig:lastchange-lastchange}).
 
@@
 \includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
-\caption{The list of change events stored for locating point B, the \textit{lastChange} of \texttt{bar.x} at the reproduction point, and point C, the \textit{lastChange} of  \texttt{baz.y} at point B.}
+\caption{The list of change events stored for locating point B, the
+  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
+  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
 \label{fig:lastchange-lastchange}
@@
 
-\subsubsection{\texttt{setPropertyChangeHook()}}
-To implement this operation, we use two features that are available in Firefox JavaScript engine.
-First, every regular JavaScript object has a \texttt{watch()} function which receives two parameters, a property name and another function as a callback.
+\subsubsection{\texttt{setPropertyChangeHook()} operation}
+We implement a slightly different version of this operation.
+Setting a flag into the Firefox JavaScript engine we can get the place am object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
+We can assume that an object is created in the same place in the next re-executions.
+This assumption does not lead to a wrong answer.
+We will discuss it in the next section when we discuss the effect of non-determinism.
+Having this assumption, it is enough to set property change hook for the objects created at one place.
+
+The Firefox JavaScript engine supports watching property changes in an object.
+Every object has a \texttt{watch()} function which receives two parameters, a property name and another function as the callback.
 Whenever the property with the given name changes the calleback function is called.
-The hook is set by this function is enabled even if the property is removed and added again [ref].
-The issue with this function is that it can only be applied to available objects.
-However, at the beginning of re-execution there is no object available.
-To solve this issue we use the second feature.
-Enabling a flag gives us the place the object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
-Though this is a limited data, it helps us to get a reference to the object once it is created.
-Then it is enough to set objet id and call \texttt{watch()} with the property name.
-Consider that in this way, we implicitly assume that the object will be created at the same place in the next re-executions.
-This assumption will be discussed later.
+The hook is set by this function remains enabled even if the property is deleted and defined again.
+This function can only be applied to avaialbe objects.
+However, at the beginning of execution, no object excepting the global object is available.
 
-In the next section, we explain the algorithm for getting a reference to the object after its creation.
-We could replace this algorithm with a much simpler algorithm if Firefox supported these two features.
-First instead of line number of object creation point, it gave us the program counter.
-Second, there was a way to hook object creation and get a reference to the created object.
-Having this two features, it was enough to set a hook at the instruction and once the execution reaches to instruction, we enable the object creation hook and we step one instruction and we get the reference to the object.
+If we could get a reference to the object just after its creation, we could use \texttt{watch()} function to monitor property changes in the object.
+In the next section we explain the algorithm we devised for this purpose by parsing and analyzing the code.
+This algorithm could be replaced by a much simpler one if Firefox debugging interface gives us the program counter of object creation instead of line number and also provides object creation hook.
+By these assumptions, it was enough to set a hook on the object creation location.
+Once the execution reaches this location, by enabling object creation hook, we could get a reference to the new object.
 

### 2010-10-21 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 We implement a slightly different version of this operation.
-Setting a flag into the Firefox JavaScript engine we can get the place am object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
+Setting a flag into the Firefox JavaScript engine we can get the place an object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
 We can assume that an object is created in the same place in the next re-executions.
@@
 
-\subsubsection{Tracking object creation}
-Having the source file url and the line number in wich the object created, we want to get a reference to the created object.
-Due to the fact that more than one object might be created in a line and there is no way to distinguish between them, we get references to all created objects.
-By parsing the source code we can find all statements that create a new object.
-It might be an object constructed by object initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new constructor()}) or function objects which can be created by \texttt{function()} statement.
-Every created object might be assigned to a statement (which is evaluated as a pointer) by \texttt{=} or object property by \texttt{:} or might be passed to a function as an argument.
-For the first case, by parsing the code we create the list of all statements. For the second case, we also create the full path of object property in the scope.
-We set a breakpoint at the line and once the breakpoint hits, we evaluate all statements in the list and we do stepping and after every step we check those assignees values and if the value is changed, we consider the new value as a created object.
-
 %One solution is to assume that jsd has features that simplify it:first: Setting the flag (object track) returns the exact location of object creation instead of the line number.second: It is possible to set hook on object creation and this returns a reference to the created object.
@@
 
+\subsubsection{Tracking object creation}
+The only data we have is the object creation location including the file url and the line number and the goal is to get a reference to this object.
+Although in the most regular cases we have only one statement and one object creation in a line, there are cases that more than one object might be created in a line.
+There is no way to recognize the interesting object among these new objects.
+So instead of one object, we monitor all new objects created in the line.
+
+An object might be created by one of these statements: An object initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new constructor()}) or function objects which can be created by \texttt{function()} statement.
+By parsing the source code we can easily recognize the statements create an object.
+The next step is getting a reference to the new object.
+
+The new object can be assigned to an object property or variable by \texttt{=}.
+In these cases we keep the assignee statement at the left side.
+The idea is that we create a list of assignee statements that the new objects are assigned to them.
+We set a hook on the creation line.
+Once the hook hits, we evaluate all statements.
+Then we do stepping(step-over) and after each step we evaluate the statements.
+Every statement which has a new value, we consider the new value-if it is an object-as a new object.
+For example in Figure ~\ref{fig:objectCreation}(a), if the creation line number is 20, we have only one statement which creates a new object and it is assigned to \texttt{x.y}.
+
+The new object can also be set as the property of a parent object by \texttt{:}.
+This case is also treated similar to previous case.
+The only difference is that the full path of property from the root parent in the local scope should be considered as the assignee statement.
+For example in Figure ~\ref{fig:objectCreation}(b), if the creation line is 20, we keep \texttt{parentObject.newObject}.
+In this case stepping should be continued until the end of line 22 for getting a reference to the created new object.
+
+There is another case for new objects and when they are passed as arguments to other functions ~\ref{fig:objectCreation}(c).
+In these cases instead of step-over we use step-in and we get the corresponding argument as a new object.
+
+%The algorithm is not complete and it is tried to support more and more cases
+
 \begin{figure}[htp]
 \begin{verbatim}
-Case 1:
+(a) Case 1:
 20 x.y = new myConstructor();
 
-Case 2:
+(b) Case 2:
 19  parentObject = {
@@
 
-Case 3:
+(c) Case 3:
 20 myFunction({myProperty:5});
@@
 \subsection{Execution reproduction}
-Altough execution reproduction is basicly should be provided by the developer, we tried to devise some automatic way which reproduces the execution.
-In the prototype, develooper can choose among three reproduction options.
-The first one is using a test case which provided by developer.
-The second one is by record and replay and the third one is local-reproduction.
+Although execution reproduction is basicly should be provided by the developer, we tried to devise some automatic way which reproduces the execution.
+In \textit{Querypointer}, develooper can directly provide a test case which reproduces the execution.
+It is also possible to use two automatic reproduction option: record-replay or local-reproduction .
 
-Two parts should be carefully considered in execution reproduction.
+Two elements should be carefully considered in execution reproduction.
 First, the initial state should be the same as previous execution.
 Second, the similar actions and events should be applied to the program during the execution.
-In the record and replay approach, debugger stores the initial page url and user actions and during replay phase, opens the same url and emulates user actions.
+In Record-replay approach, debugger stores the initial page url and user actions and during replay phase, opens the same url and simulates user actions.
 In the local reproduction approach, debugger calls the funtion on the bottom of stack with the same parameters.
+The idea behind local-reproduction is that in many web pages it is enough to replay the event to reproduce the bug.
+While record-replay approach gives better warranty about the same initial states, the local-reproudction gives us shorter cycles.
+It is also possible to uses thes approaches in combination.
+For example, debugger locally reproduce the execution and if it couldn't find the answer, reproduce the whole execution by record-replay.
+% should we talk about counting breakpoint hits for stopping at the right place?
 
 \subsection{Data collection and presentation}
-In additional to the data collected by the \textit{lastChange} algorithm to correctly identify the last change, the list of available variables and their values (one level) are collected.
+So far, we talked about the data collected at change events for \textit{lastChange} algorithm.
+However, if developer needs to explore the program state at a given point, more data is required.
+It is possible to postpone data collection until user requests.
+It is also possible to collect the list of available variable.
+\textit{Querypointer} collects data in one level depth.
+More data will be collected upon the developer's request by re-execution.
+
+We needed to build an interface to different execution points which are presented at the same time.
+The current \textit{Querypointer} interface resembles the script panel interface while it keeps the history of navigation.
 

### 2010-10-21 papers/pldi2011/sigplanconf-template.tex

@@
 In future we hope to compare queries from successive executions as a tool for learning about non-deterministic executions.
+
+\subsection{Reproduction point}
 

### 2010-10-22 papers/pldi2011/sigplanconf-template.tex
some improvements to section 3

@@
 
-The story starts when developer examines the program state at a
-breakpoint hit and asks for the \textit{lastChange} of a value. The
-\textit{lastChange} algorithm is based on program
-re-execution. Therefore it is assumed that the execution can be
-reproduced automatically (e.g., by a given test case) or with the
-developer's assistance. The breakpoint hit becomes the
-\textit{reproduction point}. Debugger sets hooks on all instructions
-that might be the result of \textit{lastChange} query, re-executes the
-program, at every hook hit, \textit{change event}, collects limited
-data and once the execution reaches the reproduction point, it
-analyzes the collected data and shows the result. The result is a
-partial snapshot of the program state at the execution point that last
-change occured.
+The \textit{lastChange} algorithm is based on program re-execution of
+a program halted on a breakpoint. The breakpoint hit becomes the
+\textit{reproduction point}. The algorithm starts when developer
+examines the program state at a breakpoint hit and asks for the
+\textit{lastChange} of a value.  Debugger sets hooks (a callback
+function dependent upon the underlying runtime) on all instructions
+that might be the result of \textit{lastChange} query. Then the
+debugger re-executes the program and every time the hook hits it
+checks for a \textit{change event}. In the case of a change, it stores
+part of the program state values.  Once the execution reaches the
+reproduction point, it analyzes the collected data and shows the
+result.  The program state at the execution point for the last change
+event is the \textit{lastChange}.
 
-As we shown in the previous section, a \textit{lastChange} query can
+While \textit{lastChange} itself is not a different kind 'breakpoint',
+all of the assumptions developers already have for breakpoints hold
+for \textit{lastChange}. In particular the re-execution is just the
+same operation developers use to debug with breakpoints. Because
+\textit{lastChange} dramatically reduces the developers work in
+setting and removing breakpoints, the re-execution step will become a
+much larege fraction of the debug time. Therefore automatic mechanisms
+for re-execution will be corresponding more valuable for debugging
+with \textit{lastChange}.
+
+As we described in the preceding section, a \textit{lastChange} query can
 be performed on the result of another \textit{lastChange} query. If we
@@
 \textit{lastChange} can be called on two different types of values: An
-object property or a variable value. In JavaScript, every available
-variable in a frame comes from one of the scopes in the frame's scope
-chain. We explain each case separately.
+object property or a variable value. Three different variations of the
+algorithm are required, one for object property and two more depending
+upon the scope of a variable.
 
 \subsection{\textit{lastChange} on object propery}
-To simplify the algorithm explanation and avoid technical details, we
-assume two basic operations and later we explain the details of these
-two operations. The first opertion is \texttt{objectId()} which gets a
-JavaScript object and returns an integer as its identifier. This
-identifier is unique for every object during one execution. The second
-operation is \texttt{setPropertyChangeHook()} which gets function as
-the callback and a string as the property name like
-\texttt{foo}. Whenever property \texttt{foo} in any object changes the
-callback will be called. The callback function receives a reference to
-the owner of \texttt{foo}.
+To simplify the algorithm explanation and defer technical details, we
+define two basic operations and later we explain the details of these
+two operations. The first opertion is \texttt{objectId()}: given a
+JavaScript object it returns an integer as its identifier. This
+identifier is unique to the object during one execution. The second
+operation is \texttt{setPropertyChangeHook()}: given a function and a
+string, the function is called whenever a property changes and its
+name matches the string For example, if the property might be
+\texttt{foo} so changes to \texttt{bar.foo} or \texttt{baz.foo} would
+call the function.  The callback function receives a reference to the
+owner of \texttt{foo}.
 
@@
 
-Once developer asks for the last change of \texttt{bar.foo} at the
-reproduction point, debugger calls \texttt{setPropertyChangeHook()}
-with \texttt{foo} as the property name and re-executes the
-program. Whenever \texttt{foo} changes and the callback function is
-called, debugger first calls \texttt{objectId()} on the \texttt{foo}
-owner object. Then it stores owner id and stack frame locations. The
-reason we keep object id instead of a reference to the object itself
-is to let garbage collector to destroy dead objects. Whenever the
-execution reaches the reproduction point it looks at the history of
-\texttt{foo} changes and finds the last \texttt{foo} change with the
-same object id as \texttt{bar} id at the reproduction point. Figure
-~\ref{fig:foo-changes1} shows the list of property \texttt{foo} change
-events in a hypothetical execution. \texttt{bar} id at the
-reproduction point is 1010, so the last change of \texttt{bar.foo} is
-the fourth column.
+To see how these functions work, suppose the developer asks for the
+last change of \texttt{bar.foo} at the reproduction point in a
+program. The debugger calls \texttt{setPropertyChangeHook()} with
+\texttt{foo} as the property name and re-executes the
+program. Whenever \texttt{foo} changes and the callback function is to
+be called, debugger first calls \texttt{objectId()} on the
+\texttt{foo} owner object. Then it stores this owner id, the stack
+frame locations, and other state values in scope at the call point.
+Whenever the execution reaches the reproduction point the debugger
+looks at the history of \texttt{foo} changes and finds the last
+\texttt{foo} change with the same object id as \texttt{bar} id at the
+reproduction point. Figure ~\ref{fig:foo-changes1} shows the list of
+property \texttt{foo} change events in a hypothetical
+execution. \texttt{bar} id at the reproduction point is 1010, so the
+last change of \texttt{bar.foo} is the fourth column.  By using an
+object id instead of an object reference we allow the garbage
+collector to reclaim the space for dead objects just at would in the
+absence of the debugger.
 
@@
 Global scope is the the most outer scope in the scope chain and it is
-also refered as global object which is usually \texttt{window}
-object. This scope is a regular JavaScript object and therefore every
-global variable is a property of global object. Similar to global
-scope, \texttt{with} scopes are also regular objects. A \texttt{with}
+also refered to as the global object (the \texttt{window}
+object in Web pages). This scope is a regular JavaScript object and therefore every
+global variable is a property of global object. Similarly,
+ \texttt{with} scopes are also regular objects. A \texttt{with}
 scope is created by a \texttt{with()} block with an object as the
-parameter. Every property of passed object is available inside the
+parameter. Every property of this parameter object is available inside the
 block as a variable. Debugger treats the case where variable's scope
@@
 
-A variable in these types of scope can only be changed in the function
-the variable is defined or the nested fuctions. For example in Figure
+Only operations in the scope of the these varibles can change their value; that includes the defining scope and scopes nested inside of them.
+For example in Figure
 ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
@@
 the function block and set a hook on all lines where the variable is
-assigned a new value. % TODO lines or instruction??? 
+assigned a new value. \textit{What if we called this operation setVariableChangeHook() and defered the discussion to 4??}
 We also set a hook at the first line of the function which is
@@
 
-Everytime one of the hooks hits a new change event is inserted to the
+Every time one of the hooks hits a new change event is inserted to the
 list of change events. During execution the same variable might be
@@
 the points B and C can be identified before reaching point
-A. Therefore, all \texttt{x} changes for piont B and all \texttt{y}
+A. Therefore, all \texttt{x} changes for point B and all \texttt{y}
 changes for point C are stored. Once the execution reaches point A,

### 2010-10-22 trunk/papers/pldi2011/sigplanconf-template.tex
narrow paragraphs only change

@@
 \begin{abstract}
-Backward search from bug symptoms to defects-which cause the bug-is a natural way to debugging.
-However, due to the lack of support for easily backward movement by  traditional debugging approaches (e.g., breakpoint-based or log-based debugging), applying this strategy-if it is not practically impossible-demands a lot of effort from developers.
-Tracking origins to wrong values is a fundamental step in this process and any aid in this regard can greatly reduce the complexity of debugging for developers.
+Backward search from bug symptoms to defects-which cause the bug-is a
+natural way to debugging. However, due to the lack of support for
+easily backward movement by traditional debugging approaches (e.g.,
+breakpoint-based or log-based debugging), applying this strategy-if it
+is not practically impossible-demands a lot of effort from
+developers. Tracking origins to wrong values is a fundamental step in
+this process and any aid in this regard can greatly reduce the
+complexity of debugging for developers.
 
-To address this problem, we propose a new functionality in debuggers, \textit{lastChange}, which locates the last place a value is changed and lets developer to collect data and ask for more \textit{lastChange} queries at the located point.
-Although \textit{lastChange} algorithm is based on program re-execution, contrary to other replay-based algorithms which require exactly the same re-executions, it only requires bug reproduction by re-executions.
-In other words \textit{bug reproducibility} (i.e., a test case is available which reproduces the bug) is the only prerequisite for \textit{lastChange} functionality.
+To address this problem, we propose a new functionality in debuggers,
+\textit{lastChange}, which locates the last place a value is changed
+and lets developer to collect data and ask for more
+\textit{lastChange} queries at the located point. Although
+\textit{lastChange} algorithm is based on program re-execution,
+contrary to other replay-based algorithms which require exactly the
+same re-executions, it only requires bug reproduction by
+re-executions. In other words \textit{bug reproducibility} (i.e., a
+test case is available which reproduces the bug) is the only
+prerequisite for \textit{lastChange} functionality.
 
-As a proof of concept, we developed \textit{Querypointer}, a prototype which enhances a popular JavaScript debugger, Firebug, with \textit{lastChange} feature.
-Moreover, \textit{Querypointer} provides mechanisms for automated bug reproduction, and a novel user interface to investigated execution points and results.
+As a proof of concept, we developed \textit{Querypointer}, a prototype
+which enhances a popular JavaScript debugger, Firebug, with
+\textit{lastChange} feature. Moreover, \textit{Querypointer} provides
+mechanisms for automated bug reproduction, and a novel user interface
+to investigated execution points and results.
 
@@
 
-The next dilemma is data collection.
-In breakpoint debugging, developer has to memorize values or manually collect data at every breakpoint hit.
-As the number of breakpoint hits increases, the process of checking the program state, collecting data and resuming the execution becomes cumbersome.
-While in breakpoint-based debugging, the whole program state is available to developer, in log-based debugging, developer has to decide about data should be collected when inserts the log statement.
-It is very common that developer has to repeat this step several times due to insufficient collected data.
-Once the adequate data is collected, it still requires analyzing and understanding.
-Developers usually end up in dealing with long log files and analyzing huge collected data.
+The next dilemma is data collection. In breakpoint debugging,
+developer has to memorize values or manually collect data at every
+breakpoint hit. As the number of breakpoint hits increases, the
+process of checking the program state, collecting data and resuming
+the execution becomes cumbersome. While in breakpoint-based debugging,
+the whole program state is available to developer, in log-based
+debugging, developer has to decide about data should be collected when
+inserts the log statement. It is very common that developer has to
+repeat this step several times due to insufficient collected
+data. Once the adequate data is collected, it still requires analyzing
+and understanding. Developers usually end up in dealing with long log
+files and analyzing huge collected data.
 
-To address the mentioned problems, we propose a new functionality in debuggers, \textit{lastChange}, which locates the origin of a wrong value.
-It works based on program re-execution similar to the practice in using breakpoints and log statements.
-Contrary to other replay-based alogrithms which require the same re-executions (instruction by instruction), the only prerequisite for \textit{lastChange} functionality is bug reproducibility (i.e., there is a test case which reproduces the bug).
-Assume that the program execution is paused on a breakpoint and the developer is suspicious about the value of an object property or a variable.
-The developer queries \textit{lastChange} on the value and it is due to debugger to locate and shows the last change of the object property or variable.
-Debugger reproduces the buggy execution and collects limited data and once the execution reaches the same place (i.e., the same breakpoint hit), call it \textit{reproduction point}, it pauses the execution, analyzes the collected data and shows the location of the last change to the developer.
-The developer can also examine the program state at the located point of execution, and continue debugging by more \textit{lastChange} queries from that point.
+To address the mentioned problems, we propose a new functionality in
+debuggers, \textit{lastChange}, which locates the origin of a wrong
+value. It works based on program re-execution similar to the practice
+in using breakpoints and log statements. Contrary to other
+replay-based alogrithms which require the same re-executions
+(instruction by instruction), the only prerequisite for
+\textit{lastChange} functionality is bug reproducibility (i.e., there
+is a test case which reproduces the bug). Assume that the program
+execution is paused on a breakpoint and the developer is suspicious
+about the value of an object property or a variable. The developer
+queries \textit{lastChange} on the value and it is due to debugger to
+locate and shows the last change of the object property or
+variable. Debugger reproduces the buggy execution and collects limited
+data and once the execution reaches the same place (i.e., the same
+breakpoint hit), call it \textit{reproduction point}, it pauses the
+execution, analyzes the collected data and shows the location of the
+last change to the developer. The developer can also examine the
+program state at the located point of execution, and continue
+debugging by more \textit{lastChange} queries from that point.
 
-Our contribution in this paper is the algorithm \textit{lastchange}, which locates the last place a value is changed, gathers other values from that execution point, and allows \textit{lastChange} operations from that point.
-The algorithm builds on existing breakpoint debugger technology.
-We demonstrate the feasibility of the algorithm with \textit{Querypointer}, an implementation extending the Firebug JavaScript debugger.
-\textit{Querypointer} also provides mechanism for automated bug reproduction, and a novel user interface which summarizes investigated execution points and collected results.
+Our contribution in this paper is the algorithm \textit{lastchange},
+which locates the last place a value is changed, gathers other values
+from that execution point, and allows \textit{lastChange} operations
+from that point. The algorithm builds on existing breakpoint debugger
+technology. We demonstrate the feasibility of the algorithm with
+\textit{Querypointer}, an implementation extending the Firebug
+JavaScript debugger. \textit{Querypointer} also provides mechanism for
+automated bug reproduction, and a novel user interface which
+summarizes investigated execution points and collected results.
 
-The rest of the paper is organized as follows.
-First, we demonstrate the \textit{lastChange} usage on a simple example with the comparison to breakpoint debugging.
-Section 3 presents \textit{lastChange} algorithm.
-In section 4, we explain the details of the JavaScript prototype implementation.
-We discuss the effect of non-determinism on the \textit{lastChange} algorithm.
-Section 6 contains an evaluation of \text{lastChange} functionality.
+The rest of the paper is organized as follows. First, we demonstrate
+the \textit{lastChange} usage on a simple example with the comparison
+to breakpoint debugging. Section 3 presents \textit{lastChange}
+algorithm. In section 4, we explain the details of the JavaScript
+prototype implementation. We discuss the effect of non-determinism on
+the \textit{lastChange} algorithm. Section 6 contains an evaluation of
+\text{lastChange} functionality.
 
@@
 \section{JavaScript implementation}
-We implemented \textit{Querypointer}, an Extension to Firebug JavaScript debugger, which provides \textit{lastChange} functionality.
-Firebug is an add-on of Firefox browser.
-Firefox JavaScript engine provides a JavaScript debugging interface and \textit{Querypointer} is developed over this interface.
-The debugging support in JavaScript comparing to more traditional languages such as Java and C\# is less evolved.
-Some part of this flaw is due to the dynamic nature of JavaScript.
-For example, JavaScript does not have classes and therefore setting watchpoint on properties before program execution is not possible.
-We explain how we could overcome these limitations and provide required operations for \textit{lastChange} algorithm implementation.
-Moreover, we breifly describe mechanisms for automated execution reproduction, data collection and presentation.
+We implemented \textit{Querypointer}, an Extension to Firebug
+JavaScript debugger, which provides \textit{lastChange}
+functionality. Firebug is an add-on of Firefox browser. Firefox
+JavaScript engine provides a JavaScript debugging interface and
+\textit{Querypointer} is developed over this interface. The debugging
+support in JavaScript comparing to more traditional languages such as
+Java and C\# is less evolved. Some part of this flaw is due to the
+dynamic nature of JavaScript. For example, JavaScript does not have
+classes and therefore setting watchpoint on properties before program
+execution is not possible. We explain how we could overcome these
+limitations and provide required operations for \textit{lastChange}
+algorithm implementation. Moreover, we breifly describe mechanisms for
+automated execution reproduction, data collection and presentation.
 
@@
 \subsubsection{\texttt{objectId()} operation}
-\texttt{objectId()} operation receives a regular JavaScript object and returns an id which is unique during one execution.
-This operation keeps the object id in an object property with name \texttt{\_objectId}.
-Once this operation receives an object, it returns \texttt{\_objectId} value if this property is already defined, otherwise it generates a new id and sets this property object.
-To set the property, it calls \texttt{defineProperty} standard JavaScript function.
-\texttt{defineProperty} receives an argument which specifies whether the property is enumerable or not.
-By setting the enumerable field \texttt{false} for \texttt{\_objectId}, this property will not apear in \texttt{for(property in object)} loops and therfore has no effect on the program execution.
-Consider that \texttt{\_objectId} is not set for all objects but only those objects that need an id.
+\texttt{objectId()} operation receives a regular JavaScript object and
+returns an id which is unique during one execution. This operation
+keeps the object id in an object property with name
+\texttt{\_objectId}. Once this operation receives an object, it
+returns \texttt{\_objectId} value if this property is already defined,
+otherwise it generates a new id and sets this property object. To set
+the property, it calls \texttt{defineProperty} standard JavaScript
+function. \texttt{defineProperty} receives an argument which specifies
+whether the property is enumerable or not. By setting the enumerable
+field \texttt{false} for \texttt{\_objectId}, this property will not
+apear in \texttt{for(property in object)} loops and therfore has no
+effect on the program execution. Consider that \texttt{\_objectId} is
+not set for all objects but only those objects that need an id.
 
 \subsubsection{\texttt{scopeId()} operation}
-The scope id is kept as a variable with name \texttt{\_scopeId} in the scope.
-We explained that we set a hook at the first instruction of the function which defines the variable.
-Once this hook hits, \texttt{\_scopeId} is set by calling \texttt{eval()} function.
-For example, executing \texttt{eval( var \_scopeId = 10)} creates a variable with name \texttt{\_scopeId} and value \texttt{10} in the local scope which is our interesting scope.
+The scope id is kept as a variable with name \texttt{\_scopeId} in the
+scope. We explained that we set a hook at the first instruction of the
+function which defines the variable. Once this hook hits,
+\texttt{\_scopeId} is set by calling \texttt{eval()} function. For
+example, executing \texttt{eval( var \_scopeId = 10)} creates a
+variable with name \texttt{\_scopeId} and value \texttt{10} in the
+local scope which is our interesting scope.
 
 \subsubsection{\texttt{setPropertyChangeHook()} operation}
-We implement a slightly different version of this operation.
-Setting a flag into the Firefox JavaScript engine we can get the place an object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
-We can assume that an object is created in the same place in the next re-executions.
-This assumption does not lead to a wrong answer.
-We will discuss it in the next section when we discuss the effect of non-determinism.
-Having this assumption, it is enough to set property change hook for the objects created at one place.
+We implement a slightly different version of this operation. Setting a
+flag into the Firefox JavaScript engine we can get the place an object
+created including the JavaScript file url and line number (e.g.,
+myFile.js, line 24). We can assume that an object is created in the
+same place in the next re-executions. This assumption does not lead to
+a wrong answer. We will discuss it in the next section when we discuss
+the effect of non-determinism. Having this assumption, it is enough to
+set property change hook for the objects created at one place.
 
-The Firefox JavaScript engine supports watching property changes in an object.
-Every object has a \texttt{watch()} function which receives two parameters, a property name and another function as the callback.
-Whenever the property with the given name changes the calleback function is called.
-The hook is set by this function remains enabled even if the property is deleted and defined again.
-This function can only be applied to avaialbe objects.
-However, at the beginning of execution, no object excepting the global object is available.
+The Firefox JavaScript engine supports watching property changes in an
+object. Every object has a \texttt{watch()} function which receives
+two parameters, a property name and another function as the
+callback. Whenever the property with the given name changes the
+calleback function is called. The hook is set by this function remains
+enabled even if the property is deleted and defined again. This
+function can only be applied to avaialbe objects. However, at the
+beginning of execution, no object excepting the global object is
+available.
 
-If we could get a reference to the object just after its creation, we could use \texttt{watch()} function to monitor property changes in the object.
-In the next section we explain the algorithm we devised for this purpose by parsing and analyzing the code.
-This algorithm could be replaced by a much simpler one if Firefox debugging interface gives us the program counter of object creation instead of line number and also provides object creation hook.
-By these assumptions, it was enough to set a hook on the object creation location.
-Once the execution reaches this location, by enabling object creation hook, we could get a reference to the new object.
+If we could get a reference to the object just after its creation, we
+could use \texttt{watch()} function to monitor property changes in the
+object. In the next section we explain the algorithm we devised for
+this purpose by parsing and analyzing the code. This algorithm could
+be replaced by a much simpler one if Firefox debugging interface gives
+us the program counter of object creation instead of line number and
+also provides object creation hook.  By these assumptions, it was
+enough to set a hook on the object creation location. Once the
+execution reaches this location, by enabling object creation hook, we
+could get a reference to the new object.
 
@@
 \subsubsection{Tracking object creation}
-The only data we have is the object creation location including the file url and the line number and the goal is to get a reference to this object.
-Although in the most regular cases we have only one statement and one object creation in a line, there are cases that more than one object might be created in a line.
-There is no way to recognize the interesting object among these new objects.
-So instead of one object, we monitor all new objects created in the line.
+The only data we have is the object creation location including the
+file url and the line number and the goal is to get a reference to
+this object. Although in the most regular cases we have only one
+statement and one object creation in a line, there are cases that more
+than one object might be created in a line. There is no way to
+recognize the interesting object among these new objects. So instead
+of one object, we monitor all new objects created in the line.
 
-An object might be created by one of these statements: An object initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new constructor()}) or function objects which can be created by \texttt{function()} statement.
-By parsing the source code we can easily recognize the statements create an object.
-The next step is getting a reference to the new object.
+An object might be created by one of these statements: An object
+initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new
+  constructor()}) or function objects which can be created by
+\texttt{function()} statement. By parsing the source code we can
+easily recognize the statements create an object. The next step is
+getting a reference to the new object.
 
-The new object can be assigned to an object property or variable by \texttt{=}.
-In these cases we keep the assignee statement at the left side.
-The idea is that we create a list of assignee statements that the new objects are assigned to them.
-We set a hook on the creation line.
-Once the hook hits, we evaluate all statements.
-Then we do stepping(step-over) and after each step we evaluate the statements.
-Every statement which has a new value, we consider the new value-if it is an object-as a new object.
-For example in Figure ~\ref{fig:objectCreation}(a), if the creation line number is 20, we have only one statement which creates a new object and it is assigned to \texttt{x.y}.
+The new object can be assigned to an object property or variable by
+\texttt{=}. In these cases we keep the assignee statement at the left
+side. The idea is that we create a list of assignee statements that
+the new objects are assigned to them. We set a hook on the creation
+line. Once the hook hits, we evaluate all statements. Then we do
+stepping(step-over) and after each step we evaluate the
+statements. Every statement which has a new value, we consider the new
+value-if it is an object-as a new object. For example in Figure
+~\ref{fig:objectCreation}(a), if the creation line number is 20, we
+have only one statement which creates a new object and it is assigned
+to \texttt{x.y}.
 
-The new object can also be set as the property of a parent object by \texttt{:}.
-This case is also treated similar to previous case.
-The only difference is that the full path of property from the root parent in the local scope should be considered as the assignee statement.
-For example in Figure ~\ref{fig:objectCreation}(b), if the creation line is 20, we keep \texttt{parentObject.newObject}.
-In this case stepping should be continued until the end of line 22 for getting a reference to the created new object.
+The new object can also be set as the property of a parent object by
+\texttt{:}. This case is also treated similar to previous case. The
+only difference is that the full path of property from the root parent
+in the local scope should be considered as the assignee statement. For
+example in Figure ~\ref{fig:objectCreation}(b), if the creation line
+is 20, we keep \texttt{parentObject.newObject}. In this case stepping
+should be continued until the end of line 22 for getting a reference
+to the created new object.
 
-There is another case for new objects and when they are passed as arguments to other functions ~\ref{fig:objectCreation}(c).
-In these cases instead of step-over we use step-in and we get the corresponding argument as a new object.
+There is another case for new objects and when they are passed as
+arguments to other functions ~\ref{fig:objectCreation}(c). In these
+cases instead of step-over we use step-in and we get the corresponding
+argument as a new object.
 
@@
 \subsection{Execution reproduction}
-Although execution reproduction is basicly should be provided by the developer, we tried to devise some automatic way which reproduces the execution.
-In \textit{Querypointer}, develooper can directly provide a test case which reproduces the execution.
-It is also possible to use two automatic reproduction option: record-replay or local-reproduction .
+Although execution reproduction is basicly should be provided by the
+developer, we tried to devise some automatic way which reproduces the
+execution. In \textit{Querypointer}, develooper can directly provide a
+test case which reproduces the execution. It is also possible to use
+two automatic reproduction option: record-replay or local-reproduction
+.
 
-Two elements should be carefully considered in execution reproduction.
-First, the initial state should be the same as previous execution.
-Second, the similar actions and events should be applied to the program during the execution.
-In Record-replay approach, debugger stores the initial page url and user actions and during replay phase, opens the same url and simulates user actions.
-In the local reproduction approach, debugger calls the funtion on the bottom of stack with the same parameters.
-The idea behind local-reproduction is that in many web pages it is enough to replay the event to reproduce the bug.
-While record-replay approach gives better warranty about the same initial states, the local-reproudction gives us shorter cycles.
-It is also possible to uses thes approaches in combination.
-For example, debugger locally reproduce the execution and if it couldn't find the answer, reproduce the whole execution by record-replay.
+Two elements should be carefully considered in execution
+reproduction. First, the initial state should be the same as previous
+execution. Second, the similar actions and events should be applied to
+the program during the execution. In Record-replay approach, debugger
+stores the initial page url and user actions and during replay phase,
+opens the same url and simulates user actions. In the local
+reproduction approach, debugger calls the funtion on the bottom of
+stack with the same parameters. The idea behind local-reproduction is
+that in many web pages it is enough to replay the event to reproduce
+the bug. While record-replay approach gives better warranty about the
+same initial states, the local-reproudction gives us shorter
+cycles. It is also possible to uses thes approaches in
+combination. For example, debugger locally reproduce the execution and
+if it couldn't find the answer, reproduce the whole execution by
+record-replay.
 % should we talk about counting breakpoint hits for stopping at the right place?
@@
 \subsection{Data collection and presentation}
-So far, we talked about the data collected at change events for \textit{lastChange} algorithm.
-However, if developer needs to explore the program state at a given point, more data is required.
-It is possible to postpone data collection until user requests.
-It is also possible to collect the list of available variable.
-\textit{Querypointer} collects data in one level depth.
-More data will be collected upon the developer's request by re-execution.
+So far, we talked about the data collected at change events for
+\textit{lastChange} algorithm. However, if developer needs to explore
+the program state at a given point, more data is required. It is
+possible to postpone data collection until user requests. It is also
+possible to collect the list of available
+variable. \textit{Querypointer} collects data in one level depth. More
+data will be collected upon the developer's request by re-execution.
 
-We needed to build an interface to different execution points which are presented at the same time.
-The current \textit{Querypointer} interface resembles the script panel interface while it keeps the history of navigation.
+We needed to build an interface to different execution points which
+are presented at the same time. The current \textit{Querypointer}
+interface resembles the script panel interface while it keeps the
+history of navigation.
 
@@
 \subsection{Converting \textit{lastChange} result to a conditional breakpoint}
-We believe that in many cases it is possible to convert the \textit{lastChange} result to a conditional breakpoint and therefore debugger is able to pause at the point
- instead of showing collected data to the developer. Here, we present an example which shows a case this transformation is not possible.
+We believe that in many cases it is possible to convert the
+\textit{lastChange} result to a conditional breakpoint and therefore
+debugger is able to pause at the point instead of showing collected
+data to the developer. Here, we present an example which shows a case
+this transformation is not possible.
 
-Figure ~\ref{fig:counter-example} shows a function with processes an array.
-The array contains numbers except one itme which is \texttt{undefined} and it causes a bug in line 30.
-There is a call to \texttt{randomPermutation} function in line 11 which randomly permutates the array item.
-So at every execution the \texttt{undefined} item will be in a new place.
-Calling \textit{lastChange} on \texttt{x} at the place bug happens, gives a point which shows line 14.
-Although this point exists at every re-execution but it can not be identified by a conditional breakpoint.
+Figure ~\ref{fig:counter-example} shows a function with processes an
+array. The array contains numbers except one itme which is
+\texttt{undefined} and it causes a bug in line 30. There is a call to
+\texttt{randomPermutation} function in line 11 which randomly
+permutates the array item. So at every execution the
+\texttt{undefined} item will be in a new place. Calling
+\textit{lastChange} on \texttt{x} at the place bug happens, gives a
+point which shows line 14. Although this point exists at every
+re-execution but it can not be identified by a conditional breakpoint.
 
@@
 \subsection{Reproducible Non-deterministic Execution}
-Thus far we have not discussed problems caused by mul-tiple threads or other sources of non-deterministic execu-tions.
-We want to explain why we believe \textit{lastChange} is robust in the practically important case where a bug is reproducible even though the execution may not be deterministic.
-Because \textit{lastChange} require re-execution, we rely on reproducible but not necessarily deterministic execution.
-A bug is reproducible for a developer when the developer can start from a determined initial state, operate on the program with a list of actions, and reproduce the symptoms of the bug.
-The details of the execution can change each time we re-execute the buggy program, but the buggy result is the same.
-The entire query chain reapplies during each execution so the data we show the developer will be internally consistent.
-The reproducibility of the bug means that the defect is very unlikely to depend on the order of events during the execution.
+Thus far we have not discussed problems caused by mul-tiple threads or
+other sources of non-deterministic execu-tions. We want to explain why
+we believe \textit{lastChange} is robust in the practically important
+case where a bug is reproducible even though the execution may not be
+deterministic.  Because \textit{lastChange} require re-execution, we
+rely on reproducible but not necessarily deterministic execution. A
+bug is reproducible for a developer when the developer can start from
+a determined initial state, operate on the program with a list of
+actions, and reproduce the symptoms of the bug. The details of the
+execution can change each time we re-execute the buggy program, but
+the buggy result is the same. The entire query chain reapplies during
+each execution so the data we show the developer will be internally
+consistent. The reproducibility of the bug means that the defect is
+very unlikely to depend on the order of events during the execution.
 
-In this important case of reproducible bugs, \textit{lastChange} are more effective than breakpoints.
-In the case of logically deterministic program execution, we can use the result from a \textit{lastChange} operation to set a conditional breakpoint then re-execute the program to position the execution trace backwards from our first breakpoint.
+In this important case of reproducible bugs, \textit{lastChange} are
+more effective than breakpoints. In the case of logically
+deterministic program execution, we can use the result from a
+\textit{lastChange} operation to set a conditional breakpoint then
+re-execute the program to position the execution trace backwards from
+our first breakpoint.
+
 %(This may be a useful adjunct for Querypoint debuggers to implement, but this backwards motion in the execution logic is not required for Querypoint debugging.) Thus in this case Querypoint debugging can do the same kinds of things as conventional breakpoints just more automatically.
 
-In the case of a non-deterministic program, a \textit{lastChange} is not equivalent to any series of conventional watchpoints or breakpoints.
-Each time we re-execute a non-deterministic program, the details of execution in-struction order may change.
-For example, if we record the source code lines every time a conventional watchpoint hits, the record may differ each time we re-execute.
-Sup-pose we consult one such record and set a breakpoint on the last entry, the apparent lastChange source line.
-When we re-execute, the breakpoint will hit, but the information we gain may be incorrect: this may not be the lastChange for this particular re-execution.
-The \textit{lastChange} method records the values we need and the sequence of source lines from all of the watchpoints, then analyzes the record to select the correct lastChange point.
-The data shown to the developer will be internally consistent, but of course it may change from a previous re-execution, surprising the developer.
-This is just a signal that the execution is not deterministic.
-In future we hope to compare queries from successive executions as a tool for learning about non-deterministic executions.
+In the case of a non-deterministic program, a \textit{lastChange} is
+not equivalent to any series of conventional watchpoints or
+breakpoints. Each time we re-execute a non-deterministic program, the
+details of execution in-struction order may change. For example, if we
+record the source code lines every time a conventional watchpoint
+hits, the record may differ each time we re-execute. Sup-pose we
+consult one such record and set a breakpoint on the last entry, the
+apparent lastChange source line. When we re-execute, the breakpoint
+will hit, but the information we gain may be incorrect: this may not
+be the lastChange for this particular re-execution. The
+\textit{lastChange} method records the values we need and the sequence
+of source lines from all of the watchpoints, then analyzes the record
+to select the correct lastChange point. The data shown to the
+developer will be internally consistent, but of course it may change
+from a previous re-execution, surprising the developer. This is just a
+signal that the execution is not deterministic. In future we hope to
+compare queries from successive executions as a tool for learning
+about non-deterministic executions.
+
+\subsection{Reproduction point}
 
@@
 \subsection{Execution overhead analysis}
-If we assume that the total number of instructions in an execution is $n$ and $m$ change event happens during one execution and for every change event $k$ additionial instructions should be executed, the execution overhead of our approach is $mk/n$.
-For $m=10^3$, $k=10^2$ and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
+If we assume that the total number of instructions in an execution is
+$n$ and $m$ change event happens during one execution and for every
+change event $k$ additionial instructions should be executed, the
+execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
+and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
 
@@
 
-\textit{lastChange} functionality supports obtaining information about the execution state logically earlier in the control flow.
-This support resembles a mixture of replay-based and logging-based debugging.
-Replay-based approaches capture limited data during execution and replay the bug-gy execution to reach past points.
-In contrast, logging-based approaches collect enough data during execution to relieve developer from re-execution.
-Replay-based approaches impose much less runtime overhead (about two orders of magnitudes) comparing to logging-based appproches.
-However, developer has to re-execute the buggy execution several times.
-\textit{lastChange} functionality collects data on re-execution but this data is limited to the current queries of developer.
+\textit{lastChange} functionality supports obtaining information about
+the execution state logically earlier in the control flow. This
+support resembles a mixture of replay-based and logging-based
+debugging. Replay-based approaches capture limited data during
+execution and replay the bug-gy execution to reach past points. In
+contrast, logging-based approaches collect enough data during
+execution to relieve developer from re-execution. Replay-based
+approaches impose much less runtime overhead (about two orders of
+magnitudes) comparing to logging-based appproches. However, developer
+has to re-execute the buggy execution several
+times. \textit{lastChange} functionality collects data on re-execution
+but this data is limited to the current queries of developer.
 
-Among replay-based debuggers we compare to bdb \cite{Boothe} and reverse watchpoint \cite{Maruyama}.
-A bidirectional C debugger, bdb employs a step counter to locate the requested point from the beginning of execution.
-It relies on deterministic execution replay (i.e., the same sequence of instructions in re-execution) and records the results of non-deterministic system calls and re-injects them into the program when it is replayed.
-It makes use of checkpoints to reduce the time needed for re-execution.
-Reverse watchpoint, is proposed by Maruyama et al., analyses the execution and moves the debugger to the last write access of a selected variable by re-executing the program from the \cite{Maruyama}.
-Similar to bdb it relies on deterministic replay and uses a counter to correctly locate a point in the next execution.
-The main disadvantage of these appraoches is requiring the exactly the same executions.
-Even one instruction difference between in two executions leads to wrong results.
-This requirement is that much restricting that after ten years from bdb paper publication, there is no newer implementation of this idea.
-On the other hand, \textit{lastChange} doesn't require any special feature in the re-rexecution and it is fit to everyday's developers' debugging practice.
+Among replay-based debuggers we compare to bdb \cite{Boothe} and
+reverse watchpoint \cite{Maruyama}.  A bidirectional C debugger, bdb
+employs a step counter to locate the requested point from the
+beginning of execution. It relies on deterministic execution replay
+(i.e., the same sequence of instructions in re-execution) and records
+the results of non-deterministic system calls and re-injects them into
+the program when it is replayed. It makes use of checkpoints to reduce
+the time needed for re-execution.  Reverse watchpoint, is proposed by
+Maruyama et al., analyses the execution and moves the debugger to the
+last write access of a selected variable by re-executing the program
+from the \cite{Maruyama}.  Similar to bdb it relies on deterministic
+replay and uses a counter to correctly locate a point in the next
+execution. The main disadvantage of these appraoches is requiring the
+exactly the same executions. Even one instruction difference between
+in two executions leads to wrong results. This requirement is that
+much restricting that after ten years from bdb paper publication,
+there is no newer implementation of this idea. On the other hand,
+\textit{lastChange} doesn't require any special feature in the
+re-rexecution and it is fit to everyday's developers' debugging
+practice.
 
-Among logging-based approaches are "omniscient" debuggers ODB\cite{Lewis} and Unstuck[].
-Omniscient debuggers have been proposed as a solution for the problems of breakpoint-debugging.
-Both approaches keep the log history in memory and hence can only record and store the complete history for a short period of time.
-These debuggers record all the events that occur during the buggy execution and later let the developer to navigate through the obtained execution log.
-In this approach there is no execution to resume: moving backwards in the log can be similar to moving forwards.
-Omniscient debuggers suffer from a different set of issues.
-First, the recording step is time expensive and it should be repeated in case of changes in program.
-Second, the execution log cannot fully replace the live execution.
-There are other aspects of execution (e.g., program user interface, file system, database tables, etc.) which are also important in debugging and are not available to the developer in omniscient debuggers.
-Third, querying collected data (e.g., to restore the program state at a certain point) may not be efficient enough for debugging of realistic programs.
+Among logging-based approaches are "omniscient" debuggers
+ODB\cite{Lewis} and Unstuck[]. Omniscient debuggers have been proposed
+as a solution for the problems of breakpoint-debugging. Both
+approaches keep the log history in memory and hence can only record
+and store the complete history for a short period of time. These
+debuggers record all the events that occur during the buggy execution
+and later let the developer to navigate through the obtained execution
+log. In this approach there is no execution to resume: moving
+backwards in the log can be similar to moving forwards. Omniscient
+debuggers suffer from a different set of issues. First, the recording
+step is time expensive and it should be repeated in case of changes in
+program. Second, the execution log cannot fully replace the live
+execution. There are other aspects of execution (e.g., program user
+interface, file system, database tables, etc.) which are also
+important in debugging and are not available to the developer in
+omniscient debuggers. Third, querying collected data (e.g., to restore
+the program state at a certain point) may not be efficient enough for
+debugging of realistic programs.
 
-A more scalable approach has been proposed by Pothier et al.
-\cite{Pothier}.
-Their back-in-time debugger, TOD, addresses the space problem by storing execution events in a distributed database.
-Comparing to Omniscient debuggers our approach is lightweight and more flexible.
-Developer can start debugging just after reproducing bug without a capturing step.
-Changing inputs or environment settings and re-executing to investigate the bug works as in conventional breakpoint debuggers.
+A more scalable approach has been proposed by Pothier et
+al. \cite{Pothier}. Their back-in-time debugger, TOD, addresses the
+space problem by storing execution events in a distributed
+database. Comparing to Omniscient debuggers our approach is
+lightweight and more flexible. Developer can start debugging just
+after reproducing bug without a capturing step.  Changing inputs or
+environment settings and re-executing to investigate the bug works as
+in conventional breakpoint debuggers.
 
-Two new directions in logging debuggers explore more detailed use of the log and more effective logging approaches.
-WhyLine\cite{Ko} provides visual interface to collected runtime information and let developer to move  on execution log using queries expressed in terms of the programming objects.
-WhyLine stores the program user in-terface in addition to program trace and provides answers to why and why not questions to the user.
-Jive\cite{Czyz} depicts the history of execution by a sequence diagram and lets user to query on events database.
-Both tools suffer from similar issues with omniscient debuggers;
+Two new directions in logging debuggers explore more detailed use of
+the log and more effective logging approaches. WhyLine\cite{Ko}
+provides visual interface to collected runtime information and let
+developer to move on execution log using queries expressed in terms of
+the programming objects. WhyLine stores the program user in-terface in
+addition to program trace and provides answers to why and why not
+questions to the user. Jive\cite{Czyz} depicts the history of
+execution by a sequence diagram and lets user to query on events
+database. Both tools suffer from similar issues with omniscient
+debuggers;
 %both provide models for extending Querypoint debugging to obtain a better user interface while retaining the flexible conven-tional replay model of debugging.
 
-A recent work by Lienhard et al.\cite{Lienhard} suggests virtual machine level support for keeping the object flow.
-It rep-laces every object reference with an alias object which keeps the history of changes to the object reference.
-In this way, when an object is collected by garbage collector, its track of changes (if it is not referenced by other alias-es) will be also collected.
-Though this approach incurs less runtime overhead (7 times to 115 times) in comparison to omniscient debuggers, it adds memory overhead.
-Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
-Moreover, the Lienhard et al.
-debugger significantly changes the virtual machine, while our approach is a generalization to conditional breakpoints and available debugger infrastructure can be adapted to support it.
+A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
+machine level support for keeping the object flow. It rep-laces every
+object reference with an alias object which keeps the history of
+changes to the object reference. In this way, when an object is
+collected by garbage collector, its track of changes (if it is not
+referenced by other alias-es) will be also collected. Though this
+approach incurs less runtime overhead (7 times to 115 times) in
+comparison to omniscient debuggers, it adds memory
+overhead. Querypoint debugging uses re-executions to gather
+infor-mation requested by the developer: the memory overhead depends
+on the query not the entire program. Moreover, the Lienhard et
+al. debugger significantly changes the virtual machine, while our
+approach is a generalization to conditional breakpoints and available
+debugger infrastructure can be adapted to support it.
 
-\textit{lastChange} functionality does rely on a conventional breakpoint to begin queries, a requirement not shared by full logging solutions.
-Here we leverage past experience of developers, but there are also new tools [] to help with this problem in the case of graphical and event based systems.
+\textit{lastChange} functionality does rely on a conventional
+breakpoint to begin queries, a requirement not shared by full logging
+solutions.  Here we leverage past experience of developers, but there
+are also new tools [] to help with this problem in the case of
+graphical and event based systems.
 

### 2010-10-22 papers/pldi2011/sigplanconf-template.tex
some changes for section 4

@@
 \section{JavaScript implementation}
-We implemented \textit{Querypointer}, an Extension to Firebug JavaScript debugger, which provides \textit{lastChange} functionality.
-Firebug is an add-on of Firefox browser.
-Firefox JavaScript engine provides a JavaScript debugging interface and \textit{Querypointer} is developed over this interface.
-The debugging support in JavaScript comparing to more traditional languages such as Java and C\# is less evolved.
-Some part of this flaw is due to the dynamic nature of JavaScript.
-For example, JavaScript does not have classes and therefore setting watchpoint on properties before program execution is not possible.
-We explain how we could overcome these limitations and provide required operations for \textit{lastChange} algorithm implementation.
-Moreover, we breifly describe mechanisms for automated execution reproduction, data collection and presentation.
+To verify the \textit{lastChange} algorithm we
+implemented it in an extension to the Firebug
+JavaScript debugger\cite{firebug-version-1.6}. 
+Firebug itself is an extension of the Firefox browser\cite{firefox-version-3.6}. The Firefox
+JavaScript engine provides a JavaScript debugging interface and
+\textit{Querypointer} is developed over this interface.
 
@@
 \subsubsection{\texttt{objectId()} operation}
-\texttt{objectId()} operation receives a regular JavaScript object and returns an id which is unique during one execution.
-This operation keeps the object id in an object property with name \texttt{\_objectId}.
-Once this operation receives an object, it returns \texttt{\_objectId} value if this property is already defined, otherwise it generates a new id and sets this property object.
-To set the property, it calls \texttt{defineProperty} standard JavaScript function.
-\texttt{defineProperty} receives an argument which specifies whether the property is enumerable or not.
-By setting the enumerable field \texttt{false} for \texttt{\_objectId}, this property will not apear in \texttt{for(property in object)} loops and therfore has no effect on the program execution.
-Consider that \texttt{\_objectId} is not set for all objects but only those objects that need an id.
+\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
+It returns the value if this property is already defined,
+otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
+for each new \texttt{\_objectId} needed. \textit{CHECK THAT} To set
+the property, we call the \texttt{defineProperty} standard JavaScript
+function. \texttt{defineProperty} receives an argument which specifies
+whether the property is enumerable or not. By setting the enumerable
+field \texttt{false} for \texttt{\_objectId}, this property will not
+apear in \texttt{for(property in object)} loops and therfore has no
+effect on the program execution. Note that \texttt{\_objectId} is
+not set for all objects but only those objects that need an id.
 
 \subsubsection{\texttt{scopeId()} operation}
-The scope id is kept as a variable with name \texttt{\_scopeId} in the scope.
-We explained that we set a hook at the first instruction of the function which defines the variable.
-Once this hook hits, \texttt{\_scopeId} is set by calling \texttt{eval()} function.
-For example, executing \texttt{eval( var \_scopeId = 10)} creates a variable with name \texttt{\_scopeId} and value \texttt{10} in the local scope which is our interesting scope.
+The scope id is kept as a variable with name \texttt{\_scopeId} in the
+scope. We explained that we set a hook at the first instruction of the
+function which defines the variable. Once this hook hits,
+\texttt{\_scopeId} is set by calling JavaScript's dynamic compilation function \texttt{eval()}. For
+example, executing \texttt{eval( var \_scopeId = 10)} creates a
+variable with name \texttt{\_scopeId} and value \texttt{10} in the
+scope of the \texttt{eval()} call, which is our interesting scope.
 
 \subsubsection{\texttt{setPropertyChangeHook()} operation}
-We implement a slightly different version of this operation.
-Setting a flag into the Firefox JavaScript engine we can get the place an object created including the JavaScript file url and line number (e.g., myFile.js, line 24).
-We can assume that an object is created in the same place in the next re-executions.
-This assumption does not lead to a wrong answer.
-We will discuss it in the next section when we discuss the effect of non-determinism.
-Having this assumption, it is enough to set property change hook for the objects created at one place.
+The Firefox JavaScript engine supports watching property changes in an
+object. Every object has a function \texttt{watch(propName, callback)}
+which receives two parameters, a property name and function.  Whenever
+the property with the given name changes, the \texttt{callback} function is
+called. The hook set by this function remains enabled even if the
+property is deleted and defined again.
 
-The Firefox JavaScript engine supports watching property changes in an object.
-Every object has a \texttt{watch()} function which receives two parameters, a property name and another function as the callback.
-Whenever the property with the given name changes the calleback function is called.
-The hook is set by this function remains enabled even if the property is deleted and defined again.
-This function can only be applied to avaialbe objects.
-However, at the beginning of execution, no object excepting the global object is available.
+For our purposes, the \texttt{watch()} function only covers the case
+of global object properties. At the beginning of execution, no object
+excepting the global object is available. Therefore we defined and
+implemented \texttt{setPropertyChangeHook()} to work in the rest of
+the cases.
 
-If we could get a reference to the object just after its creation, we could use \texttt{watch()} function to monitor property changes in the object.
-In the next section we explain the algorithm we devised for this purpose by parsing and analyzing the code.
-This algorithm could be replaced by a much simpler one if Firefox debugging interface gives us the program counter of object creation instead of line number and also provides object creation hook.
-By these assumptions, it was enough to set a hook on the object creation location.
-Once the execution reaches this location, by enabling object creation hook, we could get a reference to the new object.
-
-%One solution is to assume that jsd has features that simplify it:first: Setting the flag (object track) returns the exact location of object creation instead of the line number.second: It is possible to set hook on object creation and this returns a reference to the created object.
- %Then we can explain it like this: We set a breakpoint at the location object is created and we enable the object creation hook.  We do steppingfor one instruction and we get the reference.
-
- %I was thinking that perhaps Fireforx 4.0 may support these features.I know that in the new version of JS (1.8.5) and Fireforx 4.0 there is a new function Object(), which is the main object constructor.
-If for all cases of object creations ({}, new, function),  the engine first calls this function then by modifying or setting a hook in this function we can track object creation.
-Do you know anyone in Mozilla team who can answer this question?Do you know whether firefox 4 still supports objectTrace flag or not?
+The Firefox JavaScript engine does not current support
+\texttt{setPropertyChangeHook()} (see however \cite{bugzilla}).  For
+the our \textit{lastChange} prototype we created a version of
+\texttt{setPropertyChangeHook()} using only features of the current
+engine.  The basic strategy is to get a reference to the object just
+after its creation, then use \texttt{watch()} function to monitor
+property changes in the object.  Setting a flag into the Firefox
+JavaScript engine we can get file URL and line number for each object
+creation (e.g., myFile.js, line 24). We set a breakpoint on this line
+and analyze the source code to determine which object was created.
 
 \subsubsection{Tracking object creation}
-The only data we have is the object creation location including the file url and the line number and the goal is to get a reference to this object.
-Although in the most regular cases we have only one statement and one object creation in a line, there are cases that more than one object might be created in a line.
-There is no way to recognize the interesting object among these new objects.
-So instead of one object, we monitor all new objects created in the line.
+The only data we have is the object creation location including the
+file url and the line number and the goal is to get a reference to
+this object. Although in the most regular cases we have only one
+statement and one object creation in a line, there are cases that more
+than one object might be created in a line. There is no way to
+recognize the interesting object among these new objects. So instead
+of one object, we monitor all new objects created in the line.
 
-An object might be created by one of these statements: An object initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new constructor()}) or function objects which can be created by \texttt{function()} statement.
-By parsing the source code we can easily recognize the statements create an object.
-The next step is getting a reference to the new object.
+An object might be created by one of these statements: An object
+initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new
+  constructor()}) or function objects which can be created by
+\texttt{function()} statement. By parsing the source code we can
+easily recognize the statements create an object. The next step is
+getting a reference to the new object.
 
-The new object can be assigned to an object property or variable by \texttt{=}.
-In these cases we keep the assignee statement at the left side.
-The idea is that we create a list of assignee statements that the new objects are assigned to them.
-We set a hook on the creation line.
-Once the hook hits, we evaluate all statements.
-Then we do stepping(step-over) and after each step we evaluate the statements.
-Every statement which has a new value, we consider the new value-if it is an object-as a new object.
-For example in Figure ~\ref{fig:objectCreation}(a), if the creation line number is 20, we have only one statement which creates a new object and it is assigned to \texttt{x.y}.
+The new object can be assigned to an object property or variable by
+\texttt{=}. In these cases we keep the assignee statement at the left
+side. The idea is that we create a list of assignee statements that
+the new objects are assigned to them. We set a hook on the creation
+line. Once the hook hits, we evaluate all statements. Then we do
+stepping(step-over) and after each step we evaluate the
+statements. Every statement which has a new value, we consider the new
+value-if it is an object-as a new object. For example in Figure
+~\ref{fig:objectCreation}(a), if the creation line number is 20, we
+have only one statement which creates a new object and it is assigned
+to \texttt{x.y}.
 
-The new object can also be set as the property of a parent object by \texttt{:}.
-This case is also treated similar to previous case.
-The only difference is that the full path of property from the root parent in the local scope should be considered as the assignee statement.
-For example in Figure ~\ref{fig:objectCreation}(b), if the creation line is 20, we keep \texttt{parentObject.newObject}.
-In this case stepping should be continued until the end of line 22 for getting a reference to the created new object.
+The new object can also be set as the property of a parent object by
+\texttt{:}. This case is also treated similar to previous case. The
+only difference is that the full path of property from the root parent
+in the local scope should be considered as the assignee statement. For
+example in Figure ~\ref{fig:objectCreation}(b), if the creation line
+is 20, we keep \texttt{parentObject.newObject}. In this case stepping
+should be continued until the end of line 22 for getting a reference
+to the created new object.
 
-There is another case for new objects and when they are passed as arguments to other functions ~\ref{fig:objectCreation}(c).
-In these cases instead of step-over we use step-in and we get the corresponding argument as a new object.
+There is another case for new objects and when they are passed as
+arguments to other functions ~\ref{fig:objectCreation}(c). In these
+cases instead of step-over we use step-in and we get the corresponding
+argument as a new object.
 
@@
 \end{verbatim}
-\caption{A few cases shows possible object creations.}
+\caption{Examples of three types of JavaScript object creatin statements.}
 \label{fig:objectCreation}
@@
 \subsection{Reproducible Non-deterministic Execution}
-Thus far we have not discussed problems caused by mul-tiple threads or other sources of non-deterministic execu-tions.
-We want to explain why we believe \textit{lastChange} is robust in the practically important case where a bug is reproducible even though the execution may not be deterministic.
-Because \textit{lastChange} require re-execution, we rely on reproducible but not necessarily deterministic execution.
-A bug is reproducible for a developer when the developer can start from a determined initial state, operate on the program with a list of actions, and reproduce the symptoms of the bug.
-The details of the execution can change each time we re-execute the buggy program, but the buggy result is the same.
-The entire query chain reapplies during each execution so the data we show the developer will be internally consistent.
-The reproducibility of the bug means that the defect is very unlikely to depend on the order of events during the execution.
+Thus far we have not discussed problems caused by mul-tiple threads or
+other sources of non-deterministic execu-tions. We want to explain why
+we believe \textit{lastChange} is robust in the practically important
+case where a bug is reproducible even though the execution may not be
+deterministic.  Because \textit{lastChange} require re-execution, we
+rely on reproducible but not necessarily deterministic execution. A
+bug is reproducible for a developer when the developer can start from
+a determined initial state, operate on the program with a list of
+actions, and reproduce the symptoms of the bug. The details of the
+execution can change each time we re-execute the buggy program, but
+the buggy result is the same. The entire query chain reapplies during
+each execution so the data we show the developer will be internally
+consistent. The reproducibility of the bug means that the defect is
+very unlikely to depend on the order of events during the execution.
 
-In this important case of reproducible bugs, \textit{lastChange} are more effective than breakpoints.
-In the case of logically deterministic program execution, we can use the result from a \textit{lastChange} operation to set a conditional breakpoint then re-execute the program to position the execution trace backwards from our first breakpoint.
+In this important case of reproducible bugs, \textit{lastChange} are
+more effective than breakpoints. In the case of logically
+deterministic program execution, we can use the result from a
+\textit{lastChange} operation to set a conditional breakpoint then
+re-execute the program to position the execution trace backwards from
+our first breakpoint.
+
 %(This may be a useful adjunct for Querypoint debuggers to implement, but this backwards motion in the execution logic is not required for Querypoint debugging.) Thus in this case Querypoint debugging can do the same kinds of things as conventional breakpoints just more automatically.
 
-In the case of a non-deterministic program, a \textit{lastChange} is not equivalent to any series of conventional watchpoints or breakpoints.
-Each time we re-execute a non-deterministic program, the details of execution in-struction order may change.
-For example, if we record the source code lines every time a conventional watchpoint hits, the record may differ each time we re-execute.
-Sup-pose we consult one such record and set a breakpoint on the last entry, the apparent lastChange source line.
-When we re-execute, the breakpoint will hit, but the information we gain may be incorrect: this may not be the lastChange for this particular re-execution.
-The \textit{lastChange} method records the values we need and the sequence of source lines from all of the watchpoints, then analyzes the record to select the correct lastChange point.
-The data shown to the developer will be internally consistent, but of course it may change from a previous re-execution, surprising the developer.
-This is just a signal that the execution is not deterministic.
-In future we hope to compare queries from successive executions as a tool for learning about non-deterministic executions.
+In the case of a non-deterministic program, a \textit{lastChange} is
+not equivalent to any series of conventional watchpoints or
+breakpoints. Each time we re-execute a non-deterministic program, the
+details of execution in-struction order may change. For example, if we
+record the source code lines every time a conventional watchpoint
+hits, the record may differ each time we re-execute. Sup-pose we
+consult one such record and set a breakpoint on the last entry, the
+apparent lastChange source line. When we re-execute, the breakpoint
+will hit, but the information we gain may be incorrect: this may not
+be the lastChange for this particular re-execution. The
+\textit{lastChange} method records the values we need and the sequence
+of source lines from all of the watchpoints, then analyzes the record
+to select the correct lastChange point. The data shown to the
+developer will be internally consistent, but of course it may change
+from a previous re-execution, surprising the developer. This is just a
+signal that the execution is not deterministic. In future we hope to
+compare queries from successive executions as a tool for learning
+about non-deterministic executions.
 

### 2010-10-22 papers/pldi2011/sigplanconf-template.tex
combine two subsections: conditional breakpoints and reproducible non-determinism

@@
 \section{Discussion}
-\subsection{Converting \textit{lastChange} result to a conditional breakpoint}
-We believe that in many cases it is possible to convert the
-\textit{lastChange} result to a conditional breakpoint and therefore
-debugger is able to pause at the point instead of showing collected
-data to the developer. Here, we present an example which shows a case
-this transformation is not possible.
 
+%---------------------------------------------------------------------------------------------------
+\subsection{Reproducible Non-deterministic Execution}
+
+By construction \textit{lastChange} works whenever conventional
+breakpoint debugging works. By that we mean that, since we use
+conventional breakpoint debugging technology under the covers,
+\textit{lastChange} works whenever breakpoint debugging
+works. However, there are cases where breakpoint debugging fails but
+\textit{lastChange} works.  These are cases of \textit{reproducible
+  non-deterministic} execution.
+
+A bug is \textit{reproducible} for a developer when the developer can
+start from a determined initial state, operate on the program with a
+list of actions, and reproduce the symptoms of the bug. The details of
+the execution can change each time we re-execute the buggy program,
+but the buggy result is the same.  The reproducibility of the bug
+means that the defect is very unlikely to depend on the order of
+events during the execution. When the developer selects a value and
+asks for \textit{lastChange}, they are expressing an hyptothesis that
+the value is related to the defect. Therefore the reproducibility of
+the bug makes it very unlikely that the \textit{lastChange} will
+depend upon order of events during execution.
+
+Since \textit{lastChange} does not rely on determinism, some bugs that
+confound breakpoint debuggers will be easier to find with
+\textit{lastChange}.  Consider the following example.
 Figure ~\ref{fig:counter-example} shows a function with processes an
@@
 
-%---------------------------------------------------------------------------------------------------
-\subsection{Reproducible Non-deterministic Execution}
-Thus far we have not discussed problems caused by mul-tiple threads or
-other sources of non-deterministic execu-tions. We want to explain why
-we believe \textit{lastChange} is robust in the practically important
-case where a bug is reproducible even though the execution may not be
-deterministic.  Because \textit{lastChange} require re-execution, we
-rely on reproducible but not necessarily deterministic execution. A
-bug is reproducible for a developer when the developer can start from
-a determined initial state, operate on the program with a list of
-actions, and reproduce the symptoms of the bug. The details of the
-execution can change each time we re-execute the buggy program, but
-the buggy result is the same. The entire query chain reapplies during
-each execution so the data we show the developer will be internally
-consistent. The reproducibility of the bug means that the defect is
-very unlikely to depend on the order of events during the execution.
+Thus in the case of a non-deterministic program, a \textit{lastChange}
+is not equivalent to any series of conventional watchpoints or
+breakpoints. The extra power of \textit{lastChange} derives from its
+analysis of the entire execution up to the reproduction point and its
+memory of previous work on the defect.  Each time we re-execute a
+non-deterministic program, the details of execution instruction order
+may change. For example, if we record the source code lines every time
+a conventional watchpoint hits, the record may differ each time we
+re-execute. But \textit{lastChange} does not ask the developer to
+consider these single points.  Rather we analyze all of the
+watchpoints in an entire execution at the reproduction point where we
+know the defect has already occured and only show the final result to
+the developer.
 
-In this important case of reproducible bugs, \textit{lastChange} are
-more effective than breakpoints. In the case of logically
-deterministic program execution, we can use the result from a
-\textit{lastChange} operation to set a conditional breakpoint then
-re-execute the program to position the execution trace backwards from
-our first breakpoint.
-
-%(This may be a useful adjunct for Querypoint debuggers to implement, but this backwards motion in the execution logic is not required for Querypoint debugging.) Thus in this case Querypoint debugging can do the same kinds of things as conventional breakpoints just more automatically.
-
-In the case of a non-deterministic program, a \textit{lastChange} is
-not equivalent to any series of conventional watchpoints or
-breakpoints. Each time we re-execute a non-deterministic program, the
-details of execution in-struction order may change. For example, if we
-record the source code lines every time a conventional watchpoint
-hits, the record may differ each time we re-execute. Sup-pose we
-consult one such record and set a breakpoint on the last entry, the
-apparent lastChange source line. When we re-execute, the breakpoint
-will hit, but the information we gain may be incorrect: this may not
-be the lastChange for this particular re-execution. The
-\textit{lastChange} method records the values we need and the sequence
-of source lines from all of the watchpoints, then analyzes the record
-to select the correct lastChange point. The data shown to the
-developer will be internally consistent, but of course it may change
-from a previous re-execution, surprising the developer. This is just a
-signal that the execution is not deterministic. In future we hope to
-compare queries from successive executions as a tool for learning
-about non-deterministic executions.
+Of course there can be cases where the defect is reproducible but the
+value from \textit{lastChange} is not. As in conventional breakpoint
+debugging, we can only determine this empirically, by observing
+multiple executions with different values. Unlike conventionaly
+breakpoint debugging, implementations of \textit{lastChange} readily
+aid in detecting such cases: as we work back through a series of
+\textit{lastChange} requests we can compare values with previous
+executions. Different values on different executions will signal that
+the execution is not deterministic. In future we hope to compare
+queries from successive executions as a tool for learning about
+non-deterministic executions.
 

### 2010-10-25 papers/pldi2011/sigplanconf-template.tex
adding setVariableChangeHook to section 4.

@@
 objects. Therefore, to track changes to a variable in these scopes we
-use a different strategy.
+need a different approach.
 
-\begin{figure}[htp]
-\begin{verbatim}
-10  function parent(){
-11    var var1;
-12    var1 = ...;
-13    function myfun(){
-14      var1 = ...;
-15      function firstChild(){
-16       	var var1;
-17        var1 = ...;
-18      }  
-19      function secondChild(){
-20        var1 = ...;			      
-21      }
-22    }  
-23  }    
-\end{verbatim}
-\caption{Sample JavaScript code demonstrating local and clousure variables.}
-\label{fig:js-closure}
-\end{figure}
-
-Only operations in the scope of the these varibles can change their value; that includes the defining scope and scopes nested inside of them.
-For example in Figure
-~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
-changed in lines 10 to 23. Therefore, after locating the function in
-which the variable is defined, it is enough to parse the code inside
-the function block and set a hook on all lines where the variable is
-assigned a new value. \textit{What if we called this operation setVariableChangeHook() and defered the discussion to 4??}
-We also set a hook at the first line of the function which is
-corresponding to the line variable is defined. In Figure
-~\ref{fig:js-closure}, if the execution is paused at line 17 and the
-last change of \texttt{var1} is queried, two hooks on lines 16 and 17
-will be set, but if the execution is paused at line 20 , four hooks on
-lines 11, 12, 14, 20 will be set. These two cases are different due
-the fact that \texttt{var1} in \texttt{firstChild} is a local variable
-but in \texttt{secondChild} is a closure variable.
+All scopes in the scope chains come from blocks around the executing code.
+Comparing the scope chain and the script we can identify the code block     % perhaps needs more explanation
+(script) corresponding to the variable scope. Similar to \textit{lastChange} 
+on object property, we define two basic operations \texttt{scopeId()} and
+\texttt{setVariableChangeHook()}. The first one given an scope and its defining 
+block(script) returns an integer as the scope's identifier. The second one 
+given a callback function, a block(script) and a variable name, the function is called
+whenever the variable is changed. After developer asks for the \textit{lastChange}
+on a variable, in re-exeuction whenever the script is loaded, \texttt{setVariableChangeHook()}
+is called. Every time the callback function is called a new change 
+event is inserted to the list of change events.
 
@@
 
-Every time one of the hooks hits a new change event is inserted to the
-list of change events. During execution the same variable might be
-changed several times but in different scopes. Figure
-~\ref{fig:recursive} demonstrates a case that the same variable
+Figure ~\ref{fig:recursive} demonstrates a case that the same variable
 \texttt{x} is changed several times but in different scopes due to the
-recursive calls. Without the scope id calling \textit{lastChange(x)}
-at point C will return point B while the right answer is point A. To
-address this issue, we employ \texttt{scopeId()} operation-explained
-in the next section-which returns a unique id for a scopes during on
-execution. The scope id is kept at every variable change event. Once
-the execution reaches the reproduction point, using variable's scope
-id, the last change is recognized.
+recursive calls. Without considering the scopes calling \textit{lastChange(x)}
+at point C will return point B while the right answer is point A. Using
+\texttt{scopId()} operation, the scope id is also stored at every variable
+change event.
+
+After developer asks for the \textit{lastChange} on a variable, 
+Once the execution reaches the reproduction point, using variable's scope
+id, the last change is recognized (Figure ~\ref{fig:foo-changes2}).
 
@@
 otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. \textit{CHECK THAT} To set
+for each new \texttt{\_objectId} needed. To set %\textit{CHECK THAT} 
 the property, we call the \texttt{defineProperty} standard JavaScript
@@
 not set for all objects but only those objects that need an id.
-
-\subsubsection{\texttt{scopeId()} operation}
-The scope id is kept as a variable with name \texttt{\_scopeId} in the
-scope. We explained that we set a hook at the first instruction of the
-function which defines the variable. Once this hook hits,
-\texttt{\_scopeId} is set by calling JavaScript's dynamic compilation function \texttt{eval()}. For
-example, executing \texttt{eval( var \_scopeId = 10)} creates a
-variable with name \texttt{\_scopeId} and value \texttt{10} in the
-scope of the \texttt{eval()} call, which is our interesting scope.
 
@@
 \label{fig:objectCreation}
+\end{figure}
+
+\subsubsection{\texttt{scopeId()} operation}
+The scope id is kept as a variable with name \texttt{\_scopeId} in the
+scope. We explained that we set a hook at the first instruction of the
+function which defines the variable. Once this hook hits,
+\texttt{\_scopeId} is set by calling JavaScript's dynamic compilation function \texttt{eval()}. For
+example, executing \texttt{eval( var \_scopeId = 10)} creates a
+variable with name \texttt{\_scopeId} and value \texttt{10} in the
+scope of the \texttt{eval()} call, which is our interesting scope.
+
+\subsubsection{\texttt{setVariableChangeHook()} operation}
+Only operations in the scope of these varibles can change their value; 
+that includes the defining scope and scopes nested inside of them.
+For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
+changed in lines 10 to 23. Therefore, after locating the function in
+which the variable is defined, it is enough to parse the code inside
+the function block and set a hook on all lines where the variable is
+assigned a new value. 
+We also set a hook at the first line of the function which is
+corresponding to the line variable is defined. In Figure
+~\ref{fig:js-closure}, if the execution is paused at line 17 and the
+last change of \texttt{var1} is queried, two hooks on lines 16 and 17
+will be set, but if the execution is paused at line 20 , four hooks on
+lines 11, 12, 14, 20 will be set. These two cases are different due
+the fact that \texttt{var1} in \texttt{firstChild} is a local variable
+but in \texttt{secondChild} is a closure variable.
+
+\begin{figure}[htp]
+\begin{verbatim}
+10  function parent(){
+11    var var1;
+12    var1 = ...;
+13    function myfun(){
+14      var1 = ...;
+15      function firstChild(){
+16       	var var1;
+17        var1 = ...;
+18      }  
+19      function secondChild(){
+20        var1 = ...;			      
+21      }
+22    }  
+23  }    
+\end{verbatim}
+\caption{Sample JavaScript code demonstrating local and clousure variables.}
+\label{fig:js-closure}
 \end{figure}

### 2010-10-25 papers/pldi2011/sigplanconf-template.tex
execution reproduction and data collection are moved to section 5.

@@
 
-\subsection{Algorithm technical details}
-\subsubsection{\texttt{objectId()} operation}
+\subsection{\texttt{objectId()} operation}
 \texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
@@
 
-\subsubsection{\texttt{setPropertyChangeHook()} operation}
+\subsection{\texttt{setPropertyChangeHook()} operation}
 The Firefox JavaScript engine supports watching property changes in an
@@
 
-\subsubsection{Tracking object creation}
+\subsection{Tracking object creation}
 The only data we have is the object creation location including the
@@
 
-\subsubsection{\texttt{scopeId()} operation}
+\subsection{\texttt{scopeId()} operation}
 The scope id is kept as a variable with name \texttt{\_scopeId} in the
@@
 
-\subsubsection{\texttt{setVariableChangeHook()} operation}
+\subsection{\texttt{setVariableChangeHook()} operation}
 Only operations in the scope of these varibles can change their value; 
@@
 \end{figure}
-
-\subsection{Execution reproduction}
-Although execution reproduction is basicly should be provided by the
-developer, we tried to devise some automatic way which reproduces the
-execution. In \textit{Querypointer}, develooper can directly provide a
-test case which reproduces the execution. It is also possible to use
-two automatic reproduction option: record-replay or local-reproduction
-.
-
-Two elements should be carefully considered in execution
-reproduction. First, the initial state should be the same as previous
-execution. Second, the similar actions and events should be applied to
-the program during the execution. In Record-replay approach, debugger
-stores the initial page url and user actions and during replay phase,
-opens the same url and simulates user actions. In the local
-reproduction approach, debugger calls the funtion on the bottom of
-stack with the same parameters. The idea behind local-reproduction is
-that in many web pages it is enough to replay the event to reproduce
-the bug. While record-replay approach gives better warranty about the
-same initial states, the local-reproudction gives us shorter
-cycles. It is also possible to uses thes approaches in
-combination. For example, debugger locally reproduce the execution and
-if it couldn't find the answer, reproduce the whole execution by
-record-replay.
-% should we talk about counting breakpoint hits for stopping at the right place?
-
-\subsection{Data collection and presentation}
-So far, we talked about the data collected at change events for
-\textit{lastChange} algorithm. However, if developer needs to explore
-the program state at a given point, more data is required. It is
-possible to postpone data collection until user requests. It is also
-possible to collect the list of available
-variable. \textit{Querypointer} collects data in one level depth. More
-data will be collected upon the developer's request by re-execution.
-
-We needed to build an interface to different execution points which
-are presented at the same time. The current \textit{Querypointer}
-interface resembles the script panel interface while it keeps the
-history of navigation.
 
@@
 non-deterministic executions.
+
+\subsection{Execution reproduction}
+Although execution reproduction is basicly should be provided by the
+developer, we tried to devise some automatic way which reproduces the
+execution. In \textit{Querypointer}, develooper can directly provide a
+test case which reproduces the execution. It is also possible to use
+two automatic reproduction option: record-replay or local-reproduction
+.
+
+Two elements should be carefully considered in execution
+reproduction. First, the initial state should be the same as previous
+execution. Second, the similar actions and events should be applied to
+the program during the execution. In Record-replay approach, debugger
+stores the initial page url and user actions and during replay phase,
+opens the same url and simulates user actions. In the local
+reproduction approach, debugger calls the funtion on the bottom of
+stack with the same parameters. The idea behind local-reproduction is
+that in many web pages it is enough to replay the event to reproduce
+the bug. While record-replay approach gives better warranty about the
+same initial states, the local-reproudction gives us shorter
+cycles. It is also possible to uses thes approaches in
+combination. For example, debugger locally reproduce the execution and
+if it couldn't find the answer, reproduce the whole execution by
+record-replay.
+% should we talk about counting breakpoint hits for stopping at the right place?
+
+\subsection{Data collection and presentation}
+So far, we talked about the data collected at change events for
+\textit{lastChange} algorithm. However, if developer needs to explore
+the program state at a given point, more data is required. It is
+possible to postpone data collection until user requests. It is also
+possible to collect the list of available
+variable. \textit{Querypointer} collects data in one level depth. More
+data will be collected upon the developer's request by re-execution.
+
+We needed to build an interface to different execution points which
+are presented at the same time. The current \textit{Querypointer}
+interface resembles the script panel interface while it keeps the
+history of navigation.
 

### 2010-10-26 papers/pldi2011/sigplanconf-template.tex
rough draft of evaluation section

@@
 
+We have presented the \texttt{lastChange} algorithm and describe our
+prototype implementation. Now we want to convince you that the
+algorithm has practical value. Ultimately, practical value can only be
+proven by developers in the field using the technique. This paper is
+one step to convince implementers to put \texttt{lastChange} in the
+field.  Thus our goal here is a persausive argument.
+
+The key ingredients in our argument are: 
+\begin{enumerate}
+   \item developers need an operation like \texttt{lastChange}, 
+   \item developers can learn to use \texttt{lastChange}, 
+   \item practical implementations are feasible with modest
+invested development time,
+   \item in most cases \texttt{lastChange} will be much faster than current alternatives,
+   \item the worst cases are not more common or more painful than
+alternatives.
+\end{enumerate}
+
+\subsection{developers need an operation like \protect\texttt{lastChange} }
+
+We have shown how \texttt{lastChange} identifies the prior point in
+program execution where a program state value changes. Is it something
+the developer needs to do?  Since ultimately programs are just
+transformation of state values, debugging is ultimately backtracking
+to find defects in program state change.  When a developer halts a
+program on a breakpoint they have three kinds of information: a model
+of the program in their head, a call stack showing what part of the
+program is halted, and the state at that point (a combination of the
+debugger's view of the program internal state and the output of the
+program up to this point of execution). If the model does not match
+the call stack or if no value in the viewable program state aligns
+with the developers model for this point in execution, the developer
+will seek another view by changing the breakpoint or the input
+data. If a value appears incorrect, they may have a flash of insight
+and know the defect. Otherwise they need to figure out what operation
+causes the incorrect value. Thus \texttt{lastChange} addresses a key
+part of the debugging process.
+
+\subsection{developers can learn to use \protect\texttt{lastChange}}
+
+If \texttt{lastChange} could be useful, can developers figure out how
+to use it? We hope that our prototype demonstrates that
+\texttt{lastChange} can be easily activated by operations on the
+graphical representation of erroneous data in a debugger. Intepreting
+the results should be only slightly more difficult. We designed the
+user interface for the results from \texttt{lastChange} to resemble
+the results from a breakpoint, with the source code of the change
+point highlighted and the state of the program presented the way state
+is presented from a breakpoint. Based on this user interface, we
+believe developers can start to use \texttt{lastChange} with minimal
+training. Of course developers may initially confuse the result of
+\texttt{lastChange} with being halted in a debugger at the point of
+last change. The value of the result will motivate them to clarify the
+issue.
+
+\subsection{practical implementations are feasible}
+
+We described our prototype implementation in Sec. 4. A fully usable
+implementation would require access to the object id at the point of
+object creation and \texttt{setPropertyChangeHook()}. Many
+object-oriented runtimes provide object identifiers\cite{} and some
+provide access to object creation\cite{}. In the particular case of
+the Firefox Web browser we used for our prototype, the primary barrier
+to practical implementation would likely be integration with the
+increasingly sophisticated just in time compilers\cite{}.
+
+\subsection{in most cases \protect\texttt{lastChange} will be much faster than current alternatives}
+
+When developers try \texttt{lastChange}, will they get results fast
+enough to benefit? While we only used our prototype on toy programs,
+\textit{lastChange} seemed as fast as re-execution.  Recall that we
+insert additional code through debugger callbacks, then re-execute the
+program. The additional code we insert is proportional (in our
+JavaScript algorithm) to 1) the number of places a property or
+variable with a given name is changed, 2) the number of places objects
+are created. (Something about the likely overhead in Firefox).
+
+For comparison we should use the practical alternative: developers
+setting breakpoints. For the vast majority of programs, a developer
+will take much more time to set one breakpoint than
+\texttt{lastChange} would add. But typically the developer may not
+guess the point of last change. They must then ponder another
+breakpoint, and re-execution.
+
+We could also compare to solutions based on logging or tracing. Manual
+logging has very high overhead: the developer must add code, debug
+that added code, then analyze the log. (To be fair, the log can become
+a permenant debugging aid.) Automatic logging as we discussion in
+\secref{related} causes about one or two orders of magnitude slow down.
+
+\subsection{the worst cases are not more common or more painful than alternatives}
+
+Finally we consider the worst cases: what about code that changes
+objects in long running loops? Every time through the loop we incur
+the call back overhead; if the loop itself has relatively little code
+the overhead could be very large; if the loop computation is a
+significant fraction of the full program, the slowdown would be
+enormous.
+
+Of course breakpoints are not feasible in these cases and logging
+becomes unyieldy. Since automatic logging solutions are highly tuned,
+their overhead in this case will likely be much less than
+\texttt{lastChange}. On the other hand, \texttt{lastChange} integrates
+with an interactive debugger and detecting that we are in a high
+overhead loop is simply a matter of checking our internal counter. In
+such unusual cases we may simply offer the developer the option of
+studying the loop code then omitting it from \texttt{lastChange}
+operations. As a practical result, this is no different from similar
+issues developers face with any debugger today: occasionally a
+debugger causes too much overhead to be useful for debugging. On
+balance we think \texttt{lastChange} will rarely encounter these kinds
+of issues.
+
 %---------------------------------------------------------------------------------------------------

### 2010-10-26 papers/pldi2011/sigplanconf-template.tex

@@
 that might be the result of \textit{lastChange} query. Then the
-debugger re-executes the program and every time the hook hits it
+debugger re-executes the program and every time a hook hits it
 checks for a \textit{change event}. In the case of a change, it stores
@@
 
-While \textit{lastChange} itself is not a different kind 'breakpoint',
+While \textit{lastChange} itself is not a different kind \textit{breakpoint},
 all of the assumptions developers already have for breakpoints hold
@@
 setting and removing breakpoints, the re-execution step will become a
-much larege fraction of the debug time. Therefore automatic mechanisms
+much larger fraction of the debug time. Therefore automatic mechanisms
 for re-execution will be corresponding more valuable for debugging
@@
 call the function.  The callback function receives a reference to the
-owner of \texttt{foo}.
+owner of \texttt{foo}. In the next section, we describe how we use
+a slightly different version of this operation which is restricted 
+to only created objects in one location instead of all objects.
 
@@
 Local scope refers to the most nested scope in the scope
-chain. Closure scope refers to the scope which is created once a
-function is defined. Catch scope is the scope created in the catch
+chain and contains the local variables. Closure scope refers to the 
+scope which is created for a nested function and contains variables 
+defined in the outer block. Catch scope is the scope created in the catch
 block of try-catch statements and contains the exception
 variable. These scopes are not necessarily regular JavaScript
-objects. Therefore, to track changes to a variable in these scopes we
-need a different approach.
-
-All scopes in the scope chains come from blocks around the executing code.
-Comparing the scope chain and the script we can identify the code block     % perhaps needs more explanation
-(script) corresponding to the variable scope. Similar to \textit{lastChange} 
-on object property, we define two basic operations \texttt{scopeId()} and
-\texttt{setVariableChangeHook()}. The first one given an scope and its defining 
-block(script) returns an integer as the scope's identifier. The second one 
-given a callback function, a block(script) and a variable name, the function is called
-whenever the variable is changed. After developer asks for the \textit{lastChange}
-on a variable, in re-exeuction whenever the script is loaded, \texttt{setVariableChangeHook()}
-is called. Every time the callback function is called a new change 
-event is inserted to the list of change events.
+objects. Scope object is usually a transient copy of a native object. 
+Therefore, to track changes to a variable in these scopes we
+employ a different approach.
 
@@
 
-Figure ~\ref{fig:recursive} demonstrates a case that the same variable
+Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
+a code block, enclosed the executing code. In
+JavaScript, a code block can be identified by the file url the 
+the block's first program counter. Given this information, debugger is
+able to recognize the code block once it is loaded.
+Similar to \textit{lastChange} on object property, we define two basic operations: 
+\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one 
+given a scope returns an integer as the scope's identifier. The second one 
+given a callback function, a code block and a variable name-
+which is defined inside the block-, the function is called
+whenever the variable is changed. Figure ~\ref{fig:recursive} demonstrates a case that the same variable
 \texttt{x} is changed several times but in different scopes due to the
@@
 at point C will return point B while the right answer is point A. Using
-\texttt{scopId()} operation, the scope id is also stored at every variable
+\texttt{scopeId()} operation, the scope id is also stored at every variable
 change event.
 
-After developer asks for the \textit{lastChange} on a variable, 
-Once the execution reaches the reproduction point, using variable's scope
-id, the last change is recognized (Figure ~\ref{fig:foo-changes2}).
+If developer asks for the last change of \texttt{foo} at the 
+reproduction point in a program, debugger calls 
+\texttt{setVariableChangeHook()} with the variable's defining
+block and name as parameters and re-executes the
+program. Whenever \texttt{foo} changes and the callback function is to
+be called, debugger first calls \texttt{scopeId()} on the
+variable's scope. Then it stores this scope id, the stack
+frame locations, and other state values in scope at the call point.
+Whenever the execution reaches the reproduction point the debugger
+looks at the history of \texttt{foo} changes and finds the last
+\texttt{foo} change with the same scope id as the variable's scope id
+at the reproduction point (Figure ~\ref{fig:foo-changes2}).
 
@@
 implemented it in an extension to the Firebug
-JavaScript debugger\cite{firebug-version-1.6}. 
-Firebug itself is an extension of the Firefox browser\cite{firefox-version-3.6}. The Firefox
-JavaScript engine provides a JavaScript debugging interface and
+JavaScript debugger[].%\cite{firebug-version-1.6}. 
+Firebug itself is an extension of the Firefox browser[]. %\cite{firefox-version-3.6}
+The Firefox JavaScript engine provides a JavaScript debugging interface and
 \textit{Querypointer} is developed over this interface.
@@
 
-\section{Discussion}
-
-We have presented the \texttt{lastChange} algorithm and describe our
-prototype implementation. Now we want to convince you that the
-algorithm has practical value. Ultimately, practical value can only be
-proven by developers in the field using the technique. This paper is
-one step to convince implementers to put \texttt{lastChange} in the
-field.  Thus our goal here is a persausive argument.
-
-The key ingredients in our argument are: 
-\begin{enumerate}
-   \item developers need an operation like \texttt{lastChange}, 
-   \item developers can learn to use \texttt{lastChange}, 
-   \item practical implementations are feasible with modest
-invested development time,
-   \item in most cases \texttt{lastChange} will be much faster than current alternatives,
-   \item the worst cases are not more common or more painful than
-alternatives.
-\end{enumerate}
-
-\subsection{developers need an operation like \protect\texttt{lastChange} }
-
-We have shown how \texttt{lastChange} identifies the prior point in
-program execution where a program state value changes. Is it something
-the developer needs to do?  Since ultimately programs are just
-transformation of state values, debugging is ultimately backtracking
-to find defects in program state change.  When a developer halts a
-program on a breakpoint they have three kinds of information: a model
-of the program in their head, a call stack showing what part of the
-program is halted, and the state at that point (a combination of the
-debugger's view of the program internal state and the output of the
-program up to this point of execution). If the model does not match
-the call stack or if no value in the viewable program state aligns
-with the developers model for this point in execution, the developer
-will seek another view by changing the breakpoint or the input
-data. If a value appears incorrect, they may have a flash of insight
-and know the defect. Otherwise they need to figure out what operation
-causes the incorrect value. Thus \texttt{lastChange} addresses a key
-part of the debugging process.
-
-\subsection{developers can learn to use \protect\texttt{lastChange}}
-
-If \texttt{lastChange} could be useful, can developers figure out how
-to use it? We hope that our prototype demonstrates that
-\texttt{lastChange} can be easily activated by operations on the
-graphical representation of erroneous data in a debugger. Intepreting
-the results should be only slightly more difficult. We designed the
-user interface for the results from \texttt{lastChange} to resemble
-the results from a breakpoint, with the source code of the change
-point highlighted and the state of the program presented the way state
-is presented from a breakpoint. Based on this user interface, we
-believe developers can start to use \texttt{lastChange} with minimal
-training. Of course developers may initially confuse the result of
-\texttt{lastChange} with being halted in a debugger at the point of
-last change. The value of the result will motivate them to clarify the
-issue.
-
-\subsection{practical implementations are feasible}
-
-We described our prototype implementation in Sec. 4. A fully usable
-implementation would require access to the object id at the point of
-object creation and \texttt{setPropertyChangeHook()}. Many
-object-oriented runtimes provide object identifiers\cite{} and some
-provide access to object creation\cite{}. In the particular case of
-the Firefox Web browser we used for our prototype, the primary barrier
-to practical implementation would likely be integration with the
-increasingly sophisticated just in time compilers\cite{}.
-
-\subsection{in most cases \protect\texttt{lastChange} will be much faster than current alternatives}
-
-When developers try \texttt{lastChange}, will they get results fast
-enough to benefit? While we only used our prototype on toy programs,
-\textit{lastChange} seemed as fast as re-execution.  Recall that we
-insert additional code through debugger callbacks, then re-execute the
-program. The additional code we insert is proportional (in our
-JavaScript algorithm) to 1) the number of places a property or
-variable with a given name is changed, 2) the number of places objects
-are created. (Something about the likely overhead in Firefox).
-
-For comparison we should use the practical alternative: developers
-setting breakpoints. For the vast majority of programs, a developer
-will take much more time to set one breakpoint than
-\texttt{lastChange} would add. But typically the developer may not
-guess the point of last change. They must then ponder another
-breakpoint, and re-execution.
-
-We could also compare to solutions based on logging or tracing. Manual
-logging has very high overhead: the developer must add code, debug
-that added code, then analyze the log. (To be fair, the log can become
-a permenant debugging aid.) Automatic logging as we discussion in
-\secref{related} causes about one or two orders of magnitude slow down.
-
-\subsection{the worst cases are not more common or more painful than alternatives}
-
-Finally we consider the worst cases: what about code that changes
-objects in long running loops? Every time through the loop we incur
-the call back overhead; if the loop itself has relatively little code
-the overhead could be very large; if the loop computation is a
-significant fraction of the full program, the slowdown would be
-enormous.
-
-Of course breakpoints are not feasible in these cases and logging
-becomes unyieldy. Since automatic logging solutions are highly tuned,
-their overhead in this case will likely be much less than
-\texttt{lastChange}. On the other hand, \texttt{lastChange} integrates
-with an interactive debugger and detecting that we are in a high
-overhead loop is simply a matter of checking our internal counter. In
-such unusual cases we may simply offer the developer the option of
-studying the loop code then omitting it from \texttt{lastChange}
-operations. As a practical result, this is no different from similar
-issues developers face with any debugger today: occasionally a
-debugger causes too much overhead to be useful for debugging. On
-balance we think \texttt{lastChange} will rarely encounter these kinds
-of issues.
-
 %---------------------------------------------------------------------------------------------------
-\subsection{Reproducible Non-deterministic Execution}
-
-By construction \textit{lastChange} works whenever conventional
-breakpoint debugging works. By that we mean that, since we use
-conventional breakpoint debugging technology under the covers,
-\textit{lastChange} works whenever breakpoint debugging
-works. However, there are cases where breakpoint debugging fails but
-\textit{lastChange} works.  These are cases of \textit{reproducible
-  non-deterministic} execution.
-
-A bug is \textit{reproducible} for a developer when the developer can
-start from a determined initial state, operate on the program with a
-list of actions, and reproduce the symptoms of the bug. The details of
-the execution can change each time we re-execute the buggy program,
-but the buggy result is the same.  The reproducibility of the bug
-means that the defect is very unlikely to depend on the order of
-events during the execution. When the developer selects a value and
-asks for \textit{lastChange}, they are expressing an hyptothesis that
-the value is related to the defect. Therefore the reproducibility of
-the bug makes it very unlikely that the \textit{lastChange} will
-depend upon order of events during execution.
-
-Since \textit{lastChange} does not rely on determinism, some bugs that
-confound breakpoint debuggers will be easier to find with
-\textit{lastChange}.  Consider the following example.
-Figure ~\ref{fig:counter-example} shows a function with processes an
-array. The array contains numbers except one itme which is
-\texttt{undefined} and it causes a bug in line 30. There is a call to
-\texttt{randomPermutation} function in line 11 which randomly
-permutates the array item. So at every execution the
-\texttt{undefined} item will be in a new place. Calling
-\textit{lastChange} on \texttt{x} at the place bug happens, gives a
-point which shows line 14. Although this point exists at every
-re-execution but it can not be identified by a conditional breakpoint.
-
-\begin{figure}[htp]
-\begin{verbatim}
-10 function randomProcess(array){
-11   randomPermutation(array);
-12   var x, y;
-13   for (var i=0 ; i<array.length ; i++){
-14      x = array[i]
-...
-30      y = x+1;
-31   }
-32 }
-\end{verbatim}
-\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
-\label{fig:counter-example}
-\end{figure}
-
-Thus in the case of a non-deterministic program, a \textit{lastChange}
-is not equivalent to any series of conventional watchpoints or
-breakpoints. The extra power of \textit{lastChange} derives from its
-analysis of the entire execution up to the reproduction point and its
-memory of previous work on the defect.  Each time we re-execute a
-non-deterministic program, the details of execution instruction order
-may change. For example, if we record the source code lines every time
-a conventional watchpoint hits, the record may differ each time we
-re-execute. But \textit{lastChange} does not ask the developer to
-consider these single points.  Rather we analyze all of the
-watchpoints in an entire execution at the reproduction point where we
-know the defect has already occured and only show the final result to
-the developer.
-
-Of course there can be cases where the defect is reproducible but the
-value from \textit{lastChange} is not. As in conventional breakpoint
-debugging, we can only determine this empirically, by observing
-multiple executions with different values. Unlike conventionaly
-breakpoint debugging, implementations of \textit{lastChange} readily
-aid in detecting such cases: as we work back through a series of
-\textit{lastChange} requests we can compare values with previous
-executions. Different values on different executions will signal that
-the execution is not deterministic. In future we hope to compare
-queries from successive executions as a tool for learning about
-non-deterministic executions.
 
@@
 
-\subsection{Reproduction point}
+\section{The effect of Non-determinism}  %flying over non-determinism
+\subsection{Reproducible Non-deterministic Execution}
+
+By construction \textit{lastChange} works whenever conventional
+breakpoint debugging works. By that we mean that, since we use
+conventional breakpoint debugging technology under the covers,
+\textit{lastChange} works whenever breakpoint debugging
+works. However, there are cases where breakpoint debugging fails but
+\textit{lastChange} works.  These are cases of \textit{reproducible
+  non-deterministic} execution.
+
+A bug is \textit{reproducible} for a developer when the developer can
+start from a determined initial state, operate on the program with a
+list of actions, and reproduce the symptoms of the bug. The details of
+the execution can change each time we re-execute the buggy program,
+but the buggy result is the same.  The reproducibility of the bug
+means that the defect is very unlikely to depend on the order of
+events during the execution. When the developer selects a value and
+asks for \textit{lastChange}, they are expressing an hyptothesis that
+the value is related to the defect. Therefore the reproducibility of
+the bug makes it very unlikely that the \textit{lastChange} will
+depend upon order of events during execution.
+
+Since \textit{lastChange} does not rely on determinism, some bugs that
+confound breakpoint debuggers will be easier to find with
+\textit{lastChange}.  Consider the following example.
+Figure ~\ref{fig:counter-example} shows a function with processes an
+array. The array contains numbers except one itme which is
+\texttt{undefined} and it causes a bug in line 30. There is a call to
+\texttt{randomPermutation} function in line 11 which randomly
+permutates the array item. So at every execution the
+\texttt{undefined} item will be in a new place. Calling
+\textit{lastChange} on \texttt{x} at the place bug happens, gives a
+point which shows line 14. Although this point exists at every
+re-execution but it can not be identified by a conditional breakpoint.
+
+\begin{figure}[htp]
+\begin{verbatim}
+10 function randomProcess(array){
+11   randomPermutation(array);
+12   var x, y;
+13   for (var i=0 ; i<array.length ; i++){
+14      x = array[i]
+...
+30      y = x+1;
+31   }
+32 }
+\end{verbatim}
+\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
+\label{fig:counter-example}
+\end{figure}
+
+Thus in the case of a non-deterministic program, a \textit{lastChange}
+is not equivalent to any series of conventional watchpoints or
+breakpoints. The extra power of \textit{lastChange} derives from its
+analysis of the entire execution up to the reproduction point and its
+memory of previous work on the defect.  Each time we re-execute a
+non-deterministic program, the details of execution instruction order
+may change. For example, if we record the source code lines every time
+a conventional watchpoint hits, the record may differ each time we
+re-execute. But \textit{lastChange} does not ask the developer to
+consider these single points.  Rather we analyze all of the
+watchpoints in an entire execution at the reproduction point where we
+know the defect has already occured and only show the final result to
+the developer.
+
+Of course there can be cases where the defect is reproducible but the
+value from \textit{lastChange} is not. As in conventional breakpoint
+debugging, we can only determine this empirically, by observing
+multiple executions with different values. Unlike conventionaly
+breakpoint debugging, implementations of \textit{lastChange} readily
+aid in detecting such cases: as we work back through a series of
+\textit{lastChange} requests we can compare values with previous
+executions. Different values on different executions will signal that
+the execution is not deterministic. In future we hope to compare
+queries from successive executions as a tool for learning about
+non-deterministic executions.
+
+%\subsection{Reproduction point}
+
+\section{Discussion}
+
+We have presented the \textit{lastChange} algorithm and describe our
+prototype implementation. Now we want to convince you that the
+algorithm has practical value. Ultimately, practical value can only be
+proven by developers in the field using the technique. This paper is
+one step to convince implementers to put \textit{lastChange} in the
+field.  Thus our goal here is a persausive argument.
+
+The key ingredients in our argument are: 
+\begin{enumerate}
+   \item developers need an operation like \textit{lastChange}, 
+   \item developers can learn to use \textit{lastChange}, 
+   \item practical implementations are feasible with modest
+invested development time,
+   \item in most cases \textit{lastChange} will be much faster than current alternatives,
+   \item the worst cases are not more common or more painful than
+alternatives.
+\end{enumerate}
+
+\subsection{developers need an operation like \protect\textit{lastChange} }
+
+We have shown how \textit{lastChange} identifies the prior point in
+program execution where a program state value changes. Is it something
+the developer needs to do?  Since ultimately programs are just
+transformation of state values, debugging is ultimately backtracking
+to find defects in program state change.  When a developer halts a
+program on a breakpoint they have three kinds of information: a model
+of the program in their head, a call stack showing what part of the
+program is halted, and the state at that point (a combination of the
+debugger's view of the program internal state and the output of the
+program up to this point of execution). If the model does not match
+the call stack or if no value in the viewable program state aligns
+with the developers model for this point in execution, the developer
+will seek another view by changing the breakpoint or the input
+data. If a value appears incorrect, they may have a flash of insight
+and know the defect. Otherwise they need to figure out what operation
+causes the incorrect value. Thus \textit{lastChange} addresses a key
+part of the debugging process.
+
+\subsection{developers can learn to use \protect\texttt{lastChange}}
+
+If \texttt{lastChange} could be useful, can developers figure out how
+to use it? We hope that our prototype demonstrates that
+\textit{lastChange} can be easily activated by operations on the
+graphical representation of erroneous data in a debugger. Intepreting
+the results should be only slightly more difficult. We designed the
+user interface for the results from \textit{lastChange} to resemble
+the results from a breakpoint, with the source code of the change
+point highlighted and the state of the program presented the way state
+is presented from a breakpoint. Based on this user interface, we
+believe developers can start to use \textit{lastChange} with minimal
+training. Of course developers may initially confuse the result of
+\textit{lastChange} with being halted in a debugger at the point of
+last change. The value of the result will motivate them to clarify the
+issue.
+
+\subsection{practical implementations are feasible}
+
+We described our prototype implementation in Sec. 4. A fully usable
+implementation would require access to the object id at the point of
+object creation and \texttt{setPropertyChangeHook()}. Many
+object-oriented runtimes provide object identifiers[] and some
+provide access to object creation[]. In the particular case of
+the Firefox Web browser we used for our prototype, the primary barrier
+to practical implementation would likely be integration with the
+increasingly sophisticated just in time compilers [].
+
+\subsection{in most cases \protect\texttt{lastChange} will be much faster than current alternatives}
+
+When developers try \textit{lastChange}, will they get results fast
+enough to benefit? While we only used our prototype on toy programs,
+\textit{lastChange} seemed as fast as re-execution.  Recall that we
+insert additional code through debugger callbacks, then re-execute the
+program. The additional code we insert is proportional (in our
+JavaScript algorithm) to 1) the number of places a property or
+variable with a given name is changed, 2) the number of places objects
+are created. (Something about the likely overhead in Firefox).
+
+For comparison we should use the practical alternative: developers
+setting breakpoints. For the vast majority of programs, a developer
+will take much more time to set one breakpoint than
+\textit{lastChange} would add. But typically the developer may not
+guess the point of last change. They must then ponder another
+breakpoint, and re-execution.
+
+We could also compare to solutions based on logging or tracing. Manual
+logging has very high overhead: the developer must add code, debug
+that added code, then analyze the log. (To be fair, the log can become
+a permenant debugging aid.) Automatic logging as we discussion in
+[secref] causes about one or two orders of magnitude slow down.
+
+\subsection{the worst cases are not more common or more painful than alternatives}
+
+Finally we consider the worst cases: what about code that changes
+objects in long running loops? Every time through the loop we incur
+the call back overhead; if the loop itself has relatively little code
+the overhead could be very large; if the loop computation is a
+significant fraction of the full program, the slowdown would be
+enormous.
+
+Of course breakpoints are not feasible in these cases and logging
+becomes unyieldy. Since automatic logging solutions are highly tuned,
+their overhead in this case will likely be much less than
+\textit{lastChange}. On the other hand, \textit{lastChange} integrates
+with an interactive debugger and detecting that we are in a high
+overhead loop is simply a matter of checking our internal counter. In
+such unusual cases we may simply offer the developer the option of
+studying the loop code then omitting it from \textit{lastChange}
+operations. As a practical result, this is no different from similar
+issues developers face with any debugger today: occasionally a
+debugger causes too much overhead to be useful for debugging. On
+balance we think \textit{lastChange} will rarely encounter these kinds
+of issues.
 
 \section{Evaluation}
-\subsection{\textit{lastChange} effectiveness}
-
-\subsection{Execution overhead analysis}
+%\subsection{\textit{lastChange} effectiveness}
+%\subsection{Execution overhead analysis}
+
 If we assume that the total number of instructions in an execution is

### 2010-10-26 papers/pldi2011/sigplanconf-template.tex

@@
 a code block, enclosed the executing code. In
-JavaScript, a code block can be identified by the file url the 
-the block's first program counter. Given this information, debugger is
+JavaScript, a code block can be identified by the file url and the 
+the block's first instruction program counter. Given this information, debugger is
 able to recognize the code block once it is loaded.
@@
 
-If developer asks for the last change of \texttt{foo} at the 
+If developer asks for the last change of variable \texttt{foo} at the 
 reproduction point in a program, debugger calls 
@@
 the points B and C can be identified before reaching point
-A. Therefore, all \texttt{x} changes for point B and all \texttt{y}
-changes for point C are stored. Once the execution reaches point A,
+A. Therefore, all \texttt{x} change events for point B and all \texttt{y}
+change events for point C are stored. Once the execution reaches point A,
 and the exact \texttt{bar} id reveals, point B can be identified among
@@
 
-\FOR{$q$ in $queries$} 
+\FOR{$q$ in $lastChange queries$} 
  \FOR {$p$ is defined at the $q$ result}

### 2010-10-26 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 Local scope refers to the most nested scope in the scope
-chain. Closure scope refers to the scope which is created once a
-function is defined. Catch scope is the scope created in the catch
+chain and contains the local variables. Closure scope refers to the 
+scope which is created for a nested function and contains variables 
+defined in the outer block. Catch scope is the scope created in the catch
 block of try-catch statements and contains the exception
 variable. These scopes are not necessarily regular JavaScript
-objects. Therefore, to track changes to a variable in these scopes we
-use a different strategy.
+objects. Scope object is usually a transient copy of a native object. 
+Therefore, to track changes to a variable in these scopes we
+employ a different approach.
+
+\begin{figure}[htp]
+\begin{verbatim}
+
+  function f(){
+    var x;
+    x++;
+    if (!stop) f();
+  }
+
+Sample Trace:
+
+   f()
+A  |  x changes; 
+   |  f()
+   |  |  x changes;
+   |  |  f()
+B  |  |  |  x changes; 
+C  |  ?
+
+\end{verbatim}
+\caption{A recursive call trace demonstrates the need for scope
+  id. Querying \textit{lastChange} on \texttt{x} at point C should
+  return point A not B.}
+\label{fig:recursive}
+\end{figure}
+
+Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
+a code block, enclosed the executing code. In
+JavaScript, a code block can be identified by the file url and the 
+the block's first instruction program counter. Given this information, debugger is
+able to recognize the code block once it is loaded.
+Similar to \textit{lastChange} on object property, we define two basic operations: 
+\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one 
+given a scope returns an integer as the scope's identifier. The second one 
+given a callback function, a code block and a variable name-
+which is defined inside the block-, the function is called
+whenever the variable is changed. Figure ~\ref{fig:recursive} demonstrates a case that the same variable
+\texttt{x} is changed several times but in different scopes due to the
+recursive calls. Without considering the scopes calling \textit{lastChange(x)}
+at point C will return point B while the right answer is point A. Using
+\texttt{scopeId()} operation, the scope id is also stored at every variable
+change event.
+
+If developer asks for the last change of variable \texttt{foo} at the 
+reproduction point in a program, debugger calls 
+\texttt{setVariableChangeHook()} with the variable's defining
+block and name as parameters and re-executes the
+program. Whenever \texttt{foo} changes and the callback function is to
+be called, debugger first calls \texttt{scopeId()} on the
+variable's scope. Then it stores this scope id, the stack
+frame locations, and other state values in scope at the call point.
+Whenever the execution reaches the reproduction point the debugger
+looks at the history of \texttt{foo} changes and finds the last
+\texttt{foo} change with the same scope id as the variable's scope id
+at the reproduction point (Figure ~\ref{fig:foo-changes2}).
+
+\begin{figure}[htp]
+\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
+\caption{The list of variable \texttt{foo} change events and the
+  \texttt{foo}'s scope id at the reproduction point which identifies
+  the last change.}
+\label{fig:foo-changes2}
+\end{figure}
+
+\subsection{\textit{lastChange} on \textit{lastChange}}
+The algorithm we explained so far needs an enhancement to support
+longer sequence of \textit{lastChange}s. We explain first the issue
+and then the solution. Consider the following points:
+
+\begin{center}
+\textit{
+ point A : the reproduction point \\
+ point B : lastChange(A, bar.x) \\
+ point C : lastChange(B, baz.y) 
+ }
+ \end{center}
+According to the algorithm explained in the previous section none of
+the points B and C can be identified before reaching point
+A. Therefore, all \texttt{x} change events for point B and all \texttt{y}
+change events for point C are stored. Once the execution reaches point A,
+and the exact \texttt{bar} id reveals, point B can be identified among
+the change events in the history of \texttt{x} changes. The problem
+arises in recognizing point C. To recognize point C, we need
+\texttt{baz} id at point B, but B is a past program state, and
+\texttt{baz} id has not been collected at this point.
+
+To address this issue, we use Algorithm \ref{dependency-analysis}, to
+create the list of additional data should be collected at a change
+event. This algorithm does does a dependency analysis between all
+\textit{lastChange} queries and computes the list additional data
+required to be collected at each change event. For example in the
+mentioned case, \texttt{baz} id-if it is available- should be
+collected at all points \texttt{x} changes. Having this additional
+data, locating point C, using \texttt{baz} id at point B is
+straightforward (Figure ~\ref{fig:lastchange-lastchange}).
+
+\begin{algorithm}
+\caption{\textit{lastChange} queries dependency analysis.}
+\label{dependency-analysis}
+\begin{algorithmic}
+
+\FOR{$q$ in $lastChange queries$} 
+ \FOR {$p$ is defined at the $q$ result}
+   \IF {$p$ is a lastChange on object property} 
+     \STATE the property owner id should be stored at $q$ change events. 
+   \ELSIF {$p$ is a lastChange on variable} 
+     \STATE the variable scope id should be stored at $q$ change events.
+	 \ENDIF 
+ \ENDFOR 
+\ENDFOR
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{figure}[htp]
+\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
+\caption{The list of change events stored for locating point B, the
+  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
+  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
+\label{fig:lastchange-lastchange}
+\end{figure}
+
+%---------------------------------------------------------------------------------------------------
+\section{JavaScript implementation}
+To verify the \textit{lastChange} algorithm we
+implemented it in an extension to the Firebug
+JavaScript debugger\cite{Firebug}. %\cite{firebug-version-1.6}. 
+Firebug itself is an extension of the Firefox browser\cite{Firefox}. %\cite{firefox-version-3.6}
+The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and
+\textit{Querypointer} is developed over this interface.
+
+\subsection{\texttt{objectId()} operation}
+\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
+It returns the value if this property is already defined,
+otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
+for each new \texttt{\_objectId} needed. To set %\textit{CHECK THAT} 
+the property, we call the \texttt{defineProperty} standard JavaScript
+function. \texttt{defineProperty} receives an argument which specifies
+whether the property is enumerable or not. By setting the enumerable
+field \texttt{false} for \texttt{\_objectId}, this property will not
+apear in \texttt{for(property in object)} loops and therfore has no
+effect on the program execution. Note that \texttt{\_objectId} is
+not set for all objects but only those objects that need an id.
+
+\subsection{\texttt{setPropertyChangeHook()} operation}
+The Firefox JavaScript engine supports watching property changes in an
+object. Every object has a function \texttt{watch(propName, callback)}
+which receives two parameters, a property name and function.  Whenever
+the property with the given name changes, the \texttt{callback} function is
+called. The hook set by this function remains enabled even if the
+property is deleted and defined again.
+
+For our purposes, the \texttt{watch()} function only covers the case
+of global object properties. At the beginning of execution, no object
+excepting the global object is available. Therefore we defined and
+implemented \texttt{setPropertyChangeHook()} to work in the rest of
+the cases.
+
+The Firefox JavaScript engine does not current support
+\texttt{setPropertyChangeHook()} (see however []).  For %\cite{bugzilla}
+the our \textit{lastChange} prototype we created a version of
+\texttt{setPropertyChangeHook()} using only features of the current
+engine.  The basic strategy is to get a reference to the object just
+after its creation, then use \texttt{watch()} function to monitor
+property changes in the object.  Setting a flag into the Firefox
+JavaScript engine we can get file URL and line number for each object
+creation (e.g., myFile.js, line 24). We set a hook on this line
+and analyze the source code to determine which object was created.
+
+\subsection{Tracking object creation}
+The only data we have is the object creation location including the
+file url and the line number and the goal is to get a reference to
+this object. Although in the most regular cases we have only one
+statement and one object creation in a line, there are cases that more
+than one object might be created in a line. There is no way to
+recognize the interesting object among these new objects. So instead
+of one object, we monitor all new objects created in the line.
+
+An object might be created by one of these statements: An object
+initializer (\texttt{\{...\}}), \textit{new} operator (\texttt{new 
+constructor()}) or function definition statment (\texttt{function()}). 
+By parsing the source code we can easily recognize the statements 
+create an object. The next step is getting a reference to the new object.
+
+The new object can be assigned to an object property or variable by
+an assignment (\texttt{=}). In these cases we keep the assignee statement 
+at the left side. The idea is that we create a list of assignee statements 
+that the new objects are assigned to them. We set a hook on the creation
+line. Once the hook hits, we evaluate all assignee statements. Then 
+we do stepping(step-over) and after each step we evaluate the
+statements. Every statement which has a new value, we consider the new
+value-if it is an object-as a new object. For example in Figure
+~\ref{fig:objectCreation}(a), if the creation line number is 20, we
+have only one statement which creates a new object and it is assigned
+to \texttt{x.y}.
+
+\begin{figure}[htp]
+\begin{verbatim}
+(a) Case 1:
+20 x.y = new myConstructor();
+
+(b) Case 2:
+19  parentObject = {
+20   	  newObject : {
+21  			x : 5
+22  }}
+
+(c) Case 3:
+20 myFunction({myProperty:5});
+
+(d) Case 4:
+20 a[++i] = new myConstructor();
+
+\end{verbatim}
+\caption{Examples of three types of JavaScript object creatin statements.}
+\label{fig:objectCreation}
+\end{figure}
+
+The new object can also be set as the property of a parent object by a
+colon (\texttt{:}). This case is also treated similar to previous case. The
+only difference is that the full path of property from the root parent
+in the local scope should be considered as the assignee statement. For
+example in Figure~\ref{fig:objectCreation}(b), if the creation line
+is 20, we keep \texttt{parentObject.newObject}. In this case stepping
+should be continued until the end of line 22 for getting a reference
+to the created new object.
+
+There is another case for new objects and when they are passed as
+arguments to other functions Figure~\ref{fig:objectCreation}(c). In these
+cases instead of step-over we use step-in and we get the corresponding
+argument as a new object.
+
+Although this approach is successful in many ordinary cases, there are some 
+cases that this approach doesn't work. For example in a case
+where the new object is assigned to \texttt{a[++i]} where i is a variable
+(Figure ~\ref{fig:objectCreation}(d)), \texttt{a[++i]} is kept in the list
+of assignee statements. Obviously, evaluating this statement doesn't return
+a reference to the new object.
+
+%The algorithm is not complete and it is tried to support more and more cases
+
+\subsection{\texttt{scopeId()} operation}
+Debugger sets a hook at the beginning of all code blocks need
+a scope id whenever the block is loaded. The scope id is kept as a variable with name 
+\texttt{\_scopeId} in the scope. Whenever the hook hits which means a new scope
+is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
+function \texttt{eval()}. For example, executing \texttt{eval( var \_scopeId = 10)} creates a
+variable with name \texttt{\_scopeId} and value \texttt{10} in the
+scope of the \texttt{eval()} call, which is our interesting scope.
+
+\subsection{\texttt{setVariableChangeHook()} operation}
+Variables defined in local, closure and catch scopes are only change in
+their scope; that includes the defining scope and scopes nested inside of them.
+For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
+changed in lines 10 to 23. Therefore, after locating the function in
+which the variable is defined, it is enough to parse the code inside
+the function block and set a hook on all lines where the variable is
+assigned a new value. 
+We also set a hook at the first line of the function which is
+corresponding to the line variable is defined. In Figure
+~\ref{fig:js-closure}, if the execution is paused at line 17 and the
+last change of \texttt{var1} is queried, two hooks on lines 16 and 17
+will be set, but if the execution is paused at line 20 , four hooks on
+lines 11, 12, 14, 20 will be set. These two cases are different due
+the fact that \texttt{var1} in \texttt{firstChild} is a local variable
+but in \texttt{secondChild} is a closure variable.
 
@@
 
-Only operations in the scope of the these varibles can change their value; that includes the defining scope and scopes nested inside of them.
-For example in Figure
-~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
-changed in lines 10 to 23. Therefore, after locating the function in
-which the variable is defined, it is enough to parse the code inside
-the function block and set a hook on all lines where the variable is
-assigned a new value. \textit{What if we called this operation setVariableChangeHook() and defered the discussion to 4??}
-We also set a hook at the first line of the function which is
-corresponding to the line variable is defined. In Figure
-~\ref{fig:js-closure}, if the execution is paused at line 17 and the
-last change of \texttt{var1} is queried, two hooks on lines 16 and 17
-will be set, but if the execution is paused at line 20 , four hooks on
-lines 11, 12, 14, 20 will be set. These two cases are different due
-the fact that \texttt{var1} in \texttt{firstChild} is a local variable
-but in \texttt{secondChild} is a closure variable.
-
-\begin{figure}[htp]
-\begin{verbatim}
-
-  function f(){
-    var x;
-    x++;
-    if (!stop) f();
-  }
-
-Sample Trace:
-
-   f()
-A  |  x changes; 
-   |  f()
-   |  |  x changes;
-   |  |  f()
-B  |  |  |  x changes; 
-C  |  ?
-
-\end{verbatim}
-\caption{A recursive call trace demonstrates the need for scope
-  id. Querying \textit{lastChange} on \texttt{x} at point C should
-  return point A not B.}
-\label{fig:recursive}
-\end{figure}
-
-Every time one of the hooks hits a new change event is inserted to the
-list of change events. During execution the same variable might be
-changed several times but in different scopes. Figure
-~\ref{fig:recursive} demonstrates a case that the same variable
-\texttt{x} is changed several times but in different scopes due to the
-recursive calls. Without the scope id calling \textit{lastChange(x)}
-at point C will return point B while the right answer is point A. To
-address this issue, we employ \texttt{scopeId()} operation-explained
-in the next section-which returns a unique id for a scopes during on
-execution. The scope id is kept at every variable change event. Once
-the execution reaches the reproduction point, using variable's scope
-id, the last change is recognized.
-
-\begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
-\caption{The list of variable \texttt{foo} change events and the
-  \texttt{foo}'s scope id at the reproduction point which identifies
-  the last change.}
-\label{fig:foo-changes2}
-\end{figure}
-
-\subsection{\textit{lastChange} on \textit{lastChange}}
-The algorithm we explained so far needs an enhancement to support
-longer sequence of \textit{lastChange}s. We explain first the issue
-and then the solution. Consider the following points:
-
-\begin{center}
-\textit{
- point A : the reproduction point \\
- point B : lastChange(A, bar.x) \\
- point C : lastChange(B, baz.y) 
- }
- \end{center}
-According to the algorithm explained in the previous section none of
-the points B and C can be identified before reaching point
-A. Therefore, all \texttt{x} changes for point B and all \texttt{y}
-changes for point C are stored. Once the execution reaches point A,
-and the exact \texttt{bar} id reveals, point B can be identified among
-the change events in the history of \texttt{x} changes. The problem
-arises in recognizing point C. To recognize point C, we need
-\texttt{baz} id at point B, but B is a past program state, and
-\texttt{baz} id has not been collected at this point.
-
-To address this issue, we use Algorithm \ref{dependency-analysis}, to
-create the list of additional data should be collected at a change
-event. This algorithm does does a dependency analysis between all
-\textit{lastChange} queries and computes the list additional data
-required to be collected at each change event. For example in the
-mentioned case, \texttt{baz} id-if it is available- should be
-collected at all points \texttt{x} changes. Having this additional
-data, locating point C, using \texttt{baz} id at point B is
-straightforward (Figure ~\ref{fig:lastchange-lastchange}).
-
-\begin{algorithm}
-\caption{\textit{lastChange} queries dependency analysis.}
-\label{dependency-analysis}
-\begin{algorithmic}
-
-\FOR{$q$ in $queries$} 
- \FOR {$p$ is defined at the $q$ result}
-   \IF {$p$ is a lastChange on object property} 
-     \STATE the property owner id should be stored at $q$ change events. 
-   \ELSIF {$p$ is a lastChange on variable} 
-     \STATE the variable scope id should be stored at $q$ change events.
-	 \ENDIF 
- \ENDFOR 
-\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-\begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
-\caption{The list of change events stored for locating point B, the
-  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
-  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
-\label{fig:lastchange-lastchange}
-\end{figure}
-
 %---------------------------------------------------------------------------------------------------
-\section{JavaScript implementation}
-We implemented \textit{Querypointer}, an Extension to Firebug
-JavaScript debugger, which provides \textit{lastChange}
-functionality. Firebug is an add-on of Firefox browser. Firefox
-JavaScript engine provides a JavaScript debugging interface and
-\textit{Querypointer} is developed over this interface. The debugging
-support in JavaScript comparing to more traditional languages such as
-Java and C\# is less evolved. Some part of this flaw is due to the
-dynamic nature of JavaScript. For example, JavaScript does not have
-classes and therefore setting watchpoint on properties before program
-execution is not possible. We explain how we could overcome these
-limitations and provide required operations for \textit{lastChange}
-algorithm implementation. Moreover, we breifly describe mechanisms for
-automated execution reproduction, data collection and presentation.
-
-\subsection{Algorithm technical details}
-\subsubsection{\texttt{objectId()} operation}
-\texttt{objectId()} operation receives a regular JavaScript object and
-returns an id which is unique during one execution. This operation
-keeps the object id in an object property with name
-\texttt{\_objectId}. Once this operation receives an object, it
-returns \texttt{\_objectId} value if this property is already defined,
-otherwise it generates a new id and sets this property object. To set
-the property, it calls \texttt{defineProperty} standard JavaScript
-function. \texttt{defineProperty} receives an argument which specifies
-whether the property is enumerable or not. By setting the enumerable
-field \texttt{false} for \texttt{\_objectId}, this property will not
-apear in \texttt{for(property in object)} loops and therfore has no
-effect on the program execution. Consider that \texttt{\_objectId} is
-not set for all objects but only those objects that need an id.
-
-\subsubsection{\texttt{scopeId()} operation}
-The scope id is kept as a variable with name \texttt{\_scopeId} in the
-scope. We explained that we set a hook at the first instruction of the
-function which defines the variable. Once this hook hits,
-\texttt{\_scopeId} is set by calling \texttt{eval()} function. For
-example, executing \texttt{eval( var \_scopeId = 10)} creates a
-variable with name \texttt{\_scopeId} and value \texttt{10} in the
-local scope which is our interesting scope.
-
-\subsubsection{\texttt{setPropertyChangeHook()} operation}
-We implement a slightly different version of this operation. Setting a
-flag into the Firefox JavaScript engine we can get the place an object
-created including the JavaScript file url and line number (e.g.,
-myFile.js, line 24). We can assume that an object is created in the
-same place in the next re-executions. This assumption does not lead to
-a wrong answer. We will discuss it in the next section when we discuss
-the effect of non-determinism. Having this assumption, it is enough to
-set property change hook for the objects created at one place.
-
-The Firefox JavaScript engine supports watching property changes in an
-object. Every object has a \texttt{watch()} function which receives
-two parameters, a property name and another function as the
-callback. Whenever the property with the given name changes the
-calleback function is called. The hook is set by this function remains
-enabled even if the property is deleted and defined again. This
-function can only be applied to avaialbe objects. However, at the
-beginning of execution, no object excepting the global object is
-available.
-
-If we could get a reference to the object just after its creation, we
-could use \texttt{watch()} function to monitor property changes in the
-object. In the next section we explain the algorithm we devised for
-this purpose by parsing and analyzing the code. This algorithm could
-be replaced by a much simpler one if Firefox debugging interface gives
-us the program counter of object creation instead of line number and
-also provides object creation hook.  By these assumptions, it was
-enough to set a hook on the object creation location. Once the
-execution reaches this location, by enabling object creation hook, we
-could get a reference to the new object.
-
-%One solution is to assume that jsd has features that simplify it:first: Setting the flag (object track) returns the exact location of object creation instead of the line number.second: It is possible to set hook on object creation and this returns a reference to the created object.
- %Then we can explain it like this: We set a breakpoint at the location object is created and we enable the object creation hook.  We do steppingfor one instruction and we get the reference.
-
- %I was thinking that perhaps Fireforx 4.0 may support these features.I know that in the new version of JS (1.8.5) and Fireforx 4.0 there is a new function Object(), which is the main object constructor.
-If for all cases of object creations ({}, new, function),  the engine first calls this function then by modifying or setting a hook in this function we can track object creation.
-Do you know anyone in Mozilla team who can answer this question?Do you know whether firefox 4 still supports objectTrace flag or not?
-
-\subsubsection{Tracking object creation}
-The only data we have is the object creation location including the
-file url and the line number and the goal is to get a reference to
-this object. Although in the most regular cases we have only one
-statement and one object creation in a line, there are cases that more
-than one object might be created in a line. There is no way to
-recognize the interesting object among these new objects. So instead
-of one object, we monitor all new objects created in the line.
-
-An object might be created by one of these statements: An object
-initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new
-  constructor()}) or function objects which can be created by
-\texttt{function()} statement. By parsing the source code we can
-easily recognize the statements create an object. The next step is
-getting a reference to the new object.
-
-The new object can be assigned to an object property or variable by
-\texttt{=}. In these cases we keep the assignee statement at the left
-side. The idea is that we create a list of assignee statements that
-the new objects are assigned to them. We set a hook on the creation
-line. Once the hook hits, we evaluate all statements. Then we do
-stepping(step-over) and after each step we evaluate the
-statements. Every statement which has a new value, we consider the new
-value-if it is an object-as a new object. For example in Figure
-~\ref{fig:objectCreation}(a), if the creation line number is 20, we
-have only one statement which creates a new object and it is assigned
-to \texttt{x.y}.
-
-The new object can also be set as the property of a parent object by
-\texttt{:}. This case is also treated similar to previous case. The
-only difference is that the full path of property from the root parent
-in the local scope should be considered as the assignee statement. For
-example in Figure ~\ref{fig:objectCreation}(b), if the creation line
-is 20, we keep \texttt{parentObject.newObject}. In this case stepping
-should be continued until the end of line 22 for getting a reference
-to the created new object.
-
-There is another case for new objects and when they are passed as
-arguments to other functions ~\ref{fig:objectCreation}(c). In these
-cases instead of step-over we use step-in and we get the corresponding
-argument as a new object.
-
-%The algorithm is not complete and it is tried to support more and more cases
-
-\begin{figure}[htp]
-\begin{verbatim}
-(a) Case 1:
-20 x.y = new myConstructor();
-
-(b) Case 2:
-19  parentObject = {
-20   	  newObject : {
-21  			x : 5
-22  }}
-
-(c) Case 3:
-20 myFunction({myProperty:5});
-
-\end{verbatim}
-\caption{A few cases shows possible object creations.}
-\label{fig:objectCreation}
-\end{figure}
-
 \subsection{Execution reproduction}
@@
 
-\section{Discussion}
-\subsection{Converting \textit{lastChange} result to a conditional breakpoint}
-We believe that in many cases it is possible to convert the
-\textit{lastChange} result to a conditional breakpoint and therefore
-debugger is able to pause at the point instead of showing collected
-data to the developer. Here, we present an example which shows a case
-this transformation is not possible.
-
+\section{The effect of Non-determinism}  %flying over non-determinism
+\subsection{Reproducible Non-deterministic Execution}
+
+By construction \textit{lastChange} works whenever conventional
+breakpoint debugging works. By that we mean that, since we use
+conventional breakpoint debugging technology under the covers,
+\textit{lastChange} works whenever breakpoint debugging
+works. However, there are cases where breakpoint debugging fails but
+\textit{lastChange} works.  These are cases of \textit{reproducible
+  non-deterministic} execution.
+
+A bug is \textit{reproducible} for a developer when the developer can
+start from a determined initial state, operate on the program with a
+list of actions, and reproduce the symptoms of the bug. The details of
+the execution can change each time we re-execute the buggy program,
+but the buggy result is the same.  The reproducibility of the bug
+means that the defect is very unlikely to depend on the order of
+events during the execution. When the developer selects a value and
+asks for \textit{lastChange}, they are expressing an hyptothesis that
+the value is related to the defect. Therefore the reproducibility of
+the bug makes it very unlikely that the \textit{lastChange} will
+depend upon order of events during execution.
+
+Since \textit{lastChange} does not rely on determinism, some bugs that
+confound breakpoint debuggers will be easier to find with
+\textit{lastChange}.  Consider the following example.
 Figure ~\ref{fig:counter-example} shows a function with processes an
@@
 
-%---------------------------------------------------------------------------------------------------
-\subsection{Reproducible Non-deterministic Execution}
-Thus far we have not discussed problems caused by mul-tiple threads or
-other sources of non-deterministic execu-tions. We want to explain why
-we believe \textit{lastChange} is robust in the practically important
-case where a bug is reproducible even though the execution may not be
-deterministic.  Because \textit{lastChange} require re-execution, we
-rely on reproducible but not necessarily deterministic execution. A
-bug is reproducible for a developer when the developer can start from
-a determined initial state, operate on the program with a list of
-actions, and reproduce the symptoms of the bug. The details of the
-execution can change each time we re-execute the buggy program, but
-the buggy result is the same. The entire query chain reapplies during
-each execution so the data we show the developer will be internally
-consistent. The reproducibility of the bug means that the defect is
-very unlikely to depend on the order of events during the execution.
-
-In this important case of reproducible bugs, \textit{lastChange} are
-more effective than breakpoints. In the case of logically
-deterministic program execution, we can use the result from a
-\textit{lastChange} operation to set a conditional breakpoint then
-re-execute the program to position the execution trace backwards from
-our first breakpoint.
-
-%(This may be a useful adjunct for Querypoint debuggers to implement, but this backwards motion in the execution logic is not required for Querypoint debugging.) Thus in this case Querypoint debugging can do the same kinds of things as conventional breakpoints just more automatically.
-
-In the case of a non-deterministic program, a \textit{lastChange} is
-not equivalent to any series of conventional watchpoints or
-breakpoints. Each time we re-execute a non-deterministic program, the
-details of execution in-struction order may change. For example, if we
-record the source code lines every time a conventional watchpoint
-hits, the record may differ each time we re-execute. Sup-pose we
-consult one such record and set a breakpoint on the last entry, the
-apparent lastChange source line. When we re-execute, the breakpoint
-will hit, but the information we gain may be incorrect: this may not
-be the lastChange for this particular re-execution. The
-\textit{lastChange} method records the values we need and the sequence
-of source lines from all of the watchpoints, then analyzes the record
-to select the correct lastChange point. The data shown to the
-developer will be internally consistent, but of course it may change
-from a previous re-execution, surprising the developer. This is just a
-signal that the execution is not deterministic. In future we hope to
-compare queries from successive executions as a tool for learning
-about non-deterministic executions.
-
-\subsection{Reproduction point}
+Thus in the case of a non-deterministic program, a \textit{lastChange}
+is not equivalent to any series of conventional watchpoints or
+breakpoints. The extra power of \textit{lastChange} derives from its
+analysis of the entire execution up to the reproduction point and its
+memory of previous work on the defect.  Each time we re-execute a
+non-deterministic program, the details of execution instruction order
+may change. For example, if we record the source code lines every time
+a conventional watchpoint hits, the record may differ each time we
+re-execute. But \textit{lastChange} does not ask the developer to
+consider these single points.  Rather we analyze all of the
+watchpoints in an entire execution at the reproduction point where we
+know the defect has already occured and only show the final result to
+the developer.
+
+Of course there can be cases where the defect is reproducible but the
+value from \textit{lastChange} is not. As in conventional breakpoint
+debugging, we can only determine this empirically, by observing
+multiple executions with different values. Unlike conventionaly
+breakpoint debugging, implementations of \textit{lastChange} readily
+aid in detecting such cases: as we work back through a series of
+\textit{lastChange} requests we can compare values with previous
+executions. Different values on different executions will signal that
+the execution is not deterministic. In future we hope to compare
+queries from successive executions as a tool for learning about
+non-deterministic executions.
+
+%\subsection{Reproduction point}
+
+\section{Discussion}
+
+We have presented the \textit{lastChange} algorithm and describe our
+prototype implementation. Now we want to convince you that the
+algorithm has practical value. Ultimately, practical value can only be
+proven by developers in the field using the technique. This paper is
+one step to convince implementers to put \textit{lastChange} in the
+field.  Thus our goal here is a persausive argument.
+
+The key ingredients in our argument are: 
+\begin{enumerate}
+   \item developers need an operation like \textit{lastChange}, 
+   \item developers can learn to use \textit{lastChange}, 
+   \item practical implementations are feasible with modest
+invested development time,
+   \item in most cases \textit{lastChange} will be much faster than current alternatives,
+   \item the worst cases are not more common or more painful than
+alternatives.
+\end{enumerate}
+
+\subsection{developers need an operation like \protect\textit{lastChange} }
+
+We have shown how \textit{lastChange} identifies the prior point in
+program execution where a program state value changes. Is it something
+the developer needs to do?  Since ultimately programs are just
+transformation of state values, debugging is ultimately backtracking
+to find defects in program state change.  When a developer halts a
+program on a breakpoint they have three kinds of information: a model
+of the program in their head, a call stack showing what part of the
+program is halted, and the state at that point (a combination of the
+debugger's view of the program internal state and the output of the
+program up to this point of execution). If the model does not match
+the call stack or if no value in the viewable program state aligns
+with the developers model for this point in execution, the developer
+will seek another view by changing the breakpoint or the input
+data. If a value appears incorrect, they may have a flash of insight
+and know the defect. Otherwise they need to figure out what operation
+causes the incorrect value. Thus \textit{lastChange} addresses a key
+part of the debugging process.
+
+\subsection{developers can learn to use \protect\texttt{lastChange}}
+
+If \texttt{lastChange} could be useful, can developers figure out how
+to use it? We hope that our prototype demonstrates that
+\textit{lastChange} can be easily activated by operations on the
+graphical representation of erroneous data in a debugger. Intepreting
+the results should be only slightly more difficult. We designed the
+user interface for the results from \textit{lastChange} to resemble
+the results from a breakpoint, with the source code of the change
+point highlighted and the state of the program presented the way state
+is presented from a breakpoint. Based on this user interface, we
+believe developers can start to use \textit{lastChange} with minimal
+training. Of course developers may initially confuse the result of
+\textit{lastChange} with being halted in a debugger at the point of
+last change. The value of the result will motivate them to clarify the
+issue.
+
+\subsection{practical implementations are feasible}
+
+We described our prototype implementation in Sec. 4. A fully usable
+implementation would require access to the object id at the point of
+object creation and \texttt{setPropertyChangeHook()}. Many
+object-oriented runtimes provide object identifiers[] and some
+provide access to object creation[]. In the particular case of
+the Firefox Web browser we used for our prototype, the primary barrier
+to practical implementation would likely be integration with the
+increasingly sophisticated just in time compilers [].
+
+\subsection{in most cases \protect\texttt{lastChange} will be much faster than current alternatives}
+
+When developers try \textit{lastChange}, will they get results fast
+enough to benefit? While we only used our prototype on toy programs,
+\textit{lastChange} seemed as fast as re-execution.  Recall that we
+insert additional code through debugger callbacks, then re-execute the
+program. The additional code we insert is proportional (in our
+JavaScript algorithm) to 1) the number of places a property or
+variable with a given name is changed, 2) the number of places objects
+are created. (Something about the likely overhead in Firefox).
+
+For comparison we should use the practical alternative: developers
+setting breakpoints. For the vast majority of programs, a developer
+will take much more time to set one breakpoint than
+\textit{lastChange} would add. But typically the developer may not
+guess the point of last change. They must then ponder another
+breakpoint, and re-execution.
+
+We could also compare to solutions based on logging or tracing. Manual
+logging has very high overhead: the developer must add code, debug
+that added code, then analyze the log. (To be fair, the log can become
+a permenant debugging aid.) Automatic logging as we discussion in
+[secref] causes about one or two orders of magnitude slow down.
+
+\subsection{the worst cases are not more common or more painful than alternatives}
+
+Finally we consider the worst cases: what about code that changes
+objects in long running loops? Every time through the loop we incur
+the call back overhead; if the loop itself has relatively little code
+the overhead could be very large; if the loop computation is a
+significant fraction of the full program, the slowdown would be
+enormous.
+
+Of course breakpoints are not feasible in these cases and logging
+becomes unyieldy. Since automatic logging solutions are highly tuned,
+their overhead in this case will likely be much less than
+\textit{lastChange}. On the other hand, \textit{lastChange} integrates
+with an interactive debugger and detecting that we are in a high
+overhead loop is simply a matter of checking our internal counter. In
+such unusual cases we may simply offer the developer the option of
+studying the loop code then omitting it from \textit{lastChange}
+operations. As a practical result, this is no different from similar
+issues developers face with any debugger today: occasionally a
+debugger causes too much overhead to be useful for debugging. On
+balance we think \textit{lastChange} will rarely encounter these kinds
+of issues.
 
 \section{Evaluation}
-\subsection{\textit{lastChange} effectiveness}
-
-\subsection{Execution overhead analysis}
+%\subsection{\textit{lastChange} effectiveness}
+%\subsection{Execution overhead analysis}
+
 If we assume that the total number of instructions in an execution is
@@
 
-\begin{thebibliography}{10}
+\begin{thebibliography}{13}
 \softraggedright
@@
 
+\bibitem[Firefox(2010)]{Firefox}
+Firefox. \newblock http://www.mozilla.com.
+
 \bibitem[Ko(2008)]{Ko}
@@
 
+\bibitem[JSD(2010)]{JSD}
+Mozila JavaScript Debugging Interface. \newblock http://www.mozilla.org/js/jsd.
+
 \bibitem[Pothier(2007)]{Pothier}

### 2010-10-26 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 
-%---------------------------------------------------------------------------------------------------
 \section{Introduction}
@@
 
-%---------------------------------------------------------------------------------------------------
 \section{Introductory example}
@@
 
-%---------------------------------------------------------------------------------------------------
 \section{\textit{lastChange} Algorithm}
@@
 The Firefox JavaScript engine does not current support
-\texttt{setPropertyChangeHook()} (see however []).  For %\cite{bugzilla}
+\texttt{setPro-}
+\texttt{pertyChangeHook()} (see however []).  For %\cite{bugzilla}
 the our \textit{lastChange} prototype we created a version of
@@
 
-An object might be created by one of these statements: An object
+An object might be created by one of these statements: object
 initializer (\texttt{\{...\}}), \textit{new} operator (\texttt{new 
@@
 
-%The algorithm is not complete and it is tried to support more and more cases
-
 \subsection{\texttt{scopeId()} operation}
@@
 variable with name \texttt{\_scopeId} and value \texttt{10} in the
-scope of the \texttt{eval()} call, which is our interesting scope.
+scope of the \texttt{eval()} call, which is our interesting scope. \texttt{scopeId()}
+operation returns the value of \texttt{\_scopeId} in the scope.
 
@@
 
-%---------------------------------------------------------------------------------------------------
 \subsection{Execution reproduction}
@@
 test case which reproduces the execution. It is also possible to use
-two automatic reproduction option: record-replay or local-reproduction
-.
+two automatic reproduction option: record-replay or local-reproduction.
 
@@
 
-\subsection{Data collection and presentation}
+\subsection{Data collection}
 So far, we talked about the data collected at change events for
@@
 history of navigation.
+
+% Discuss what happens when assumptions changes, like object creation location.
 

### 2010-10-27 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 reproduction point in a program, debugger calls 
-\texttt{setVariableChangeHook()} with the variable's defining
+\texttt{setVariableChangeH-} \texttt{ook()} with the variable's defining
 block and name as parameters and re-executes the
@@
 and analyze the source code to determine which object was created.
+
+Here, we implicitly assumed that the object will be created at 
+the same location in the next execution. So, what does happens if it
+is not true? Well, once the execution reaches the reproduction point, it
+reveals that the object has been created in different location. This time,
+debugger re-executes the program considering both locations as possible 
+object creation locations.
 
@@
 
-\subsection{Execution reproduction}
-Although execution reproduction is basicly should be provided by the
-developer, we tried to devise some automatic way which reproduces the
-execution. In \textit{Querypointer}, develooper can directly provide a
-test case which reproduces the execution. It is also possible to use
-two automatic reproduction option: record-replay or local-reproduction.
-
-Two elements should be carefully considered in execution
-reproduction. First, the initial state should be the same as previous
-execution. Second, the similar actions and events should be applied to
-the program during the execution. In Record-replay approach, debugger
-stores the initial page url and user actions and during replay phase,
-opens the same url and simulates user actions. In the local
-reproduction approach, debugger calls the funtion on the bottom of
-stack with the same parameters. The idea behind local-reproduction is
-that in many web pages it is enough to replay the event to reproduce
-the bug. While record-replay approach gives better warranty about the
-same initial states, the local-reproudction gives us shorter
-cycles. It is also possible to uses thes approaches in
-combination. For example, debugger locally reproduce the execution and
-if it couldn't find the answer, reproduce the whole execution by
-record-replay.
-% should we talk about counting breakpoint hits for stopping at the right place?
-
-\subsection{Data collection}
-So far, we talked about the data collected at change events for
-\textit{lastChange} algorithm. However, if developer needs to explore
-the program state at a given point, more data is required. It is
-possible to postpone data collection until user requests. It is also
-possible to collect the list of available
-variable. \textit{Querypointer} collects data in one level depth. More
-data will be collected upon the developer's request by re-execution.
-
-We needed to build an interface to different execution points which
-are presented at the same time. The current \textit{Querypointer}
-interface resembles the script panel interface while it keeps the
-history of navigation.
+\subsection{Re-Execution, reproduction point and data collection}
+\textit{Querypointer} needs a test case to reproduce the
+execution and conditions to correctly recognize the reproduction point. 
+Although both elements can be directly provided by developer, \textit{Querypointer}
+is also able to automatically create them from the first execution.
+
+\textit{Querypointer} keeps track of breakpoint hits and user steppings. For example, 
+if developer query \textit{lastChange} at the third hit of breakpoint \textit{b}, in
+re-execution, third hit of breakpoint b recognized as the reproduction point.
+
+To build a test case from one execution, two elements should be carefully 
+considered. First, the initial state should be the same as the initial state
+of execution. Second, similar actions and events should be applied to
+the program during the execution. \textit{Querypointer} supports two mechanism
+for automatic re-execution: local-reproduction, record-replay. The first one,
+recalls the function at the bottom of call stack with the same parameters. The idea
+behind this mechanism is that many bugs in web pages can be reproduced by firing
+an event like clicking on a button. The second one, in the first execution, record phase, 
+stores the initial page url and captures user actions. In the replay phase, it opens
+the same url and applies user actions. The local reproduction mechanism provides
+shorter re-execution cycles while the record-replay is more accurate about the
+initial state.
+
+In addition to the data collected at every change event for identifying the \textit{lastChange}
+result, \textit{Querypointer} partially stores values in program state. If developer asks for 
+some values which have not been stored, \textit{Querypointer} re-executes and collects the requested data.
+There is a trade-off between the amount of data collected at every change event and the number of re-executions. 
+By default, \textit{Querypointer} stores values up to one level depth in objects.
 
@@
 
+\bibitem[Bond(2010)]{Bond2}
+M.D. Bond, G.Z. Baker, S.Z. Guyer, and Z. Samuel. \newblock Breadcrumbs: efficient context sensitivity for dynamic bug detection analyses.
+\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
+June, 2010.
+
 \bibitem[Boothe(2000)]{Boothe}

### 2010-10-27 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 last write access of a selected variable by re-executing the program
-from the \cite{Maruyama}.  Similar to bdb it relies on deterministic
+from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
 replay and uses a counter to correctly locate a point in the next
@@
 exactly the same executions. Even one instruction difference between
-in two executions leads to wrong results. This requirement is that
+two executions leads to wrong results. This requirement is that
 much restricting that after ten years from bdb paper publication,
@@
 
-Among logging-based approaches are "omniscient" debuggers
-ODB\cite{Lewis} and Unstuck[]. Omniscient debuggers have been proposed
-as a solution for the problems of breakpoint-debugging. Both
+Among logging-based approaches are \textit{omniscient} debuggers
+ODB\cite{Lewis} and Unstuck\cite{Hofer}. Both
 approaches keep the log history in memory and hence can only record
@@
 database. Both tools suffer from similar issues with omniscient
-debuggers;
+debuggers.
 %both provide models for extending Querypoint debugging to obtain a better user interface while retaining the flexible conven-tional replay model of debugging.
@@
 A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
-machine level support for keeping the object flow. It rep-laces every
+machine level support for keeping the object flow. It replaces every
 object reference with an alias object which keeps the history of
@@
 collected by garbage collector, its track of changes (if it is not
-referenced by other alias-es) will be also collected. Though this
+referenced by other aliases) will be also collected. Though this
 approach incurs less runtime overhead (7 times to 115 times) in
 comparison to omniscient debuggers, it adds memory
-overhead. Querypoint debugging uses re-executions to gather
-infor-mation requested by the developer: the memory overhead depends
-on the query not the entire program. Moreover, the Lienhard et
-al. debugger significantly changes the virtual machine, while our
-approach is a generalization to conditional breakpoints and available
-debugger infrastructure can be adapted to support it.
-
-\textit{lastChange} functionality does rely on a conventional
-breakpoint to begin queries, a requirement not shared by full logging
-solutions.  Here we leverage past experience of developers, but there
-are also new tools [] to help with this problem in the case of
-graphical and event based systems.
+overhead.
+
+Origin tracking of undefined and null values employing \textit{value piggybacking} technique proposed by
+Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
+First, it is limited to undefined and null values. Second, this approach dosen't return the last change
+of a null variable but the first place that the null value is originated.
+
+%Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
+Moreover, the Lienhard et al.
+debugger significantly changes the virtual machine, while our approach is a generalization to conditional breakpoints and available debugger infrastructure can be adapted to support it.
+
+%\textit{lastChange} functionality does rely on a conventional breakpoint to begin queries, a requirement not shared by full logging solutions.
+Here we leverage past experience of developers, but there are also new tools [] to help with this problem in the case of graphical and event based systems.
 
@@
 
+\bibitem[Hofer(2006)]{Hofer}
+C. Hofer, M. Denker, and C. St\'{e}phane. \newblock Implementing a backward-in-time debugger.
+\newblock In Proceedings of\emph{NODe’06},
+volume P-88, pages 17–32. Lecture Notes in Informatics, 2006.
+
 \bibitem[Ko(2008)]{Ko}

### 2010-10-27 papers/pldi2011/sigplanconf-template.tex
reword abstract

@@
 \begin{abstract}
-Backward search from bug symptoms to defects-which cause the bug-is a
-natural way to debugging. However, due to the lack of support for
-easily backward movement by traditional debugging approaches (e.g.,
-breakpoint-based or log-based debugging), applying this strategy-if it
-is not practically impossible-demands a lot of effort from
-developers. Tracking origins to wrong values is a fundamental step in
-this process and any aid in this regard can greatly reduce the
-complexity of debugging for developers.
-
-To address this problem, we propose a new functionality in debuggers,
-\textit{lastChange}, which locates the last place a value is changed
-and lets developer to collect data and ask for more
-\textit{lastChange} queries at the located point. Although
-\textit{lastChange} algorithm is based on program re-execution,
-contrary to other replay-based algorithms which require exactly the
-same re-executions, it only requires bug reproduction by
-re-executions. In other words \textit{bug reproducibility} (i.e., a
-test case is available which reproduces the bug) is the only
-prerequisite for \textit{lastChange} functionality.
+
+Developers often seek the origins of wrong values they see in their
+debugger. Their search must be backwards in time: the code causing the
+wrong value executed before the wrong value appeared. Searching with
+breakpoint- or log- based debuggers demands persistance and
+significant experience with the application being debugged. We propose
+a new approach, an algorithm \textit{lastChange}, which automatically
+locates the last point that a value was changed and related
+information such as the call stack and program state. Starting from a
+program halted on a breakpoint, the \textit{lastChange} solution
+applies queries to the live program during re-execution. Thus
+\textit{lastChange} combines the flexibility of breakpoint debugging
+with the expressive power of log-based query debugging.  Contrary to
+other replay-based algorithms which require exactly the same
+re-executions, \textit{lastChange} only requires \textit{bug
+  reproducibility}, a test case is available which reproduces the bug.
 
@@
 implemented it in an extension to the Firebug
-JavaScript debugger[].%\cite{firebug-version-1.6}. 
-Firebug itself is an extension of the Firefox browser[]. %\cite{firefox-version-3.6}
-The Firefox JavaScript engine provides a JavaScript debugging interface and
+JavaScript debugger\cite{Firebug}. %\cite{firebug-version-1.6}. 
+Firebug itself is an extension of the Firefox browser\cite{Firefox}. %\cite{firefox-version-3.6}
+The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and
 \textit{Querypointer} is developed over this interface.
@@
 The Firefox JavaScript engine does not current support
-\texttt{setPropertyChangeHook()} (see however \cite{bugzilla}).  For
+\texttt{setPro-}
+\texttt{pertyChangeHook()} (see however []).  For %\cite{bugzilla}
 the our \textit{lastChange} prototype we created a version of
@@
 JavaScript engine we can get file URL and line number for each object
-creation (e.g., myFile.js, line 24). We set a breakpoint on this line
+creation (e.g., myFile.js, line 24). We set a hook on this line
 and analyze the source code to determine which object was created.
+
+Here, we implicitly assumed that the object will be created at 
+the same location in the next execution. So, what does happens if it
+is not true? Well, once the execution reaches the reproduction point, it
+reveals that the object has been created in different location. This time,
+debugger re-executes the program considering both locations as possible 
+object creation locations.
 
@@
 
-An object might be created by one of these statements: An object
-initializer(\texttt{\{...\}}) or \textit{new} operator (\texttt{new
-  constructor()}) or function objects which can be created by
-\texttt{function()} statement. By parsing the source code we can
-easily recognize the statements create an object. The next step is
-getting a reference to the new object.
+An object might be created by one of these statements: object
+initializer (\texttt{\{...\}}), \textit{new} operator (\texttt{new 
+constructor()}) or function definition statment (\texttt{function()}). 
+By parsing the source code we can easily recognize the statements 
+create an object. The next step is getting a reference to the new object.
 
 The new object can be assigned to an object property or variable by
-\texttt{=}. In these cases we keep the assignee statement at the left
-side. The idea is that we create a list of assignee statements that
-the new objects are assigned to them. We set a hook on the creation
-line. Once the hook hits, we evaluate all statements. Then we do
-stepping(step-over) and after each step we evaluate the
+an assignment (\texttt{=}). In these cases we keep the assignee statement 
+at the left side. The idea is that we create a list of assignee statements 
+that the new objects are assigned to them. We set a hook on the creation
+line. Once the hook hits, we evaluate all assignee statements. Then 
+we do stepping(step-over) and after each step we evaluate the
 statements. Every statement which has a new value, we consider the new
@@
 
-The new object can also be set as the property of a parent object by
-\texttt{:}. This case is also treated similar to previous case. The
-only difference is that the full path of property from the root parent
-in the local scope should be considered as the assignee statement. For
-example in Figure ~\ref{fig:objectCreation}(b), if the creation line
-is 20, we keep \texttt{parentObject.newObject}. In this case stepping
-should be continued until the end of line 22 for getting a reference
-to the created new object.
-
-There is another case for new objects and when they are passed as
-arguments to other functions ~\ref{fig:objectCreation}(c). In these
-cases instead of step-over we use step-in and we get the corresponding
-argument as a new object.
-
-%The algorithm is not complete and it is tried to support more and more cases
-
 \begin{figure}[htp]
@@
 
+(d) Case 4:
+20 a[++i] = new myConstructor();
+
 \end{verbatim}
@@
 
+The new object can also be set as the property of a parent object by a
+colon (\texttt{:}). This case is also treated similar to previous case. The
+only difference is that the full path of property from the root parent
+in the local scope should be considered as the assignee statement. For
+example in Figure~\ref{fig:objectCreation}(b), if the creation line
+is 20, we keep \texttt{parentObject.newObject}. In this case stepping
+should be continued until the end of line 22 for getting a reference
+to the created new object.
+
+There is another case for new objects and when they are passed as
+arguments to other functions Figure~\ref{fig:objectCreation}(c). In these
+cases instead of step-over we use step-in and we get the corresponding
+argument as a new object.
+
+Although this approach is successful in many ordinary cases, there are some 
+cases that this approach doesn't work. For example in a case
+where the new object is assigned to \texttt{a[++i]} where i is a variable
+(Figure ~\ref{fig:objectCreation}(d)), \texttt{a[++i]} is kept in the list
+of assignee statements. Obviously, evaluating this statement doesn't return
+a reference to the new object.
+
 \subsection{\texttt{scopeId()} operation}
-The scope id is kept as a variable with name \texttt{\_scopeId} in the
-scope. We explained that we set a hook at the first instruction of the
-function which defines the variable. Once this hook hits,
-\texttt{\_scopeId} is set by calling JavaScript's dynamic compilation function \texttt{eval()}. For
-example, executing \texttt{eval( var \_scopeId = 10)} creates a
+Debugger sets a hook at the beginning of all code blocks need
+a scope id whenever the block is loaded. The scope id is kept as a variable with name 
+\texttt{\_scopeId} in the scope. Whenever the hook hits which means a new scope
+is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
+function \texttt{eval()}. For example, executing \texttt{eval( var \_scopeId = 10)} creates a
 variable with name \texttt{\_scopeId} and value \texttt{10} in the
-scope of the \texttt{eval()} call, which is our interesting scope.
+scope of the \texttt{eval()} call, which is our interesting scope. \texttt{scopeId()}
+operation returns the value of \texttt{\_scopeId} in the scope.
 
 \subsection{\texttt{setVariableChangeHook()} operation}
-Only operations in the scope of these varibles can change their value; 
-that includes the defining scope and scopes nested inside of them.
+Variables defined in local, closure and catch scopes are only change in
+their scope; that includes the defining scope and scopes nested inside of them.
 For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
@@
 
-%---------------------------------------------------------------------------------------------------
-
-\subsection{Execution reproduction}
-Although execution reproduction is basicly should be provided by the
-developer, we tried to devise some automatic way which reproduces the
-execution. In \textit{Querypointer}, develooper can directly provide a
-test case which reproduces the execution. It is also possible to use
-two automatic reproduction option: record-replay or local-reproduction
-.
-
-Two elements should be carefully considered in execution
-reproduction. First, the initial state should be the same as previous
-execution. Second, the similar actions and events should be applied to
-the program during the execution. In Record-replay approach, debugger
-stores the initial page url and user actions and during replay phase,
-opens the same url and simulates user actions. In the local
-reproduction approach, debugger calls the funtion on the bottom of
-stack with the same parameters. The idea behind local-reproduction is
-that in many web pages it is enough to replay the event to reproduce
-the bug. While record-replay approach gives better warranty about the
-same initial states, the local-reproudction gives us shorter
-cycles. It is also possible to uses thes approaches in
-combination. For example, debugger locally reproduce the execution and
-if it couldn't find the answer, reproduce the whole execution by
-record-replay.
-% should we talk about counting breakpoint hits for stopping at the right place?
-
-\subsection{Data collection and presentation}
-So far, we talked about the data collected at change events for
-\textit{lastChange} algorithm. However, if developer needs to explore
-the program state at a given point, more data is required. It is
-possible to postpone data collection until user requests. It is also
-possible to collect the list of available
-variable. \textit{Querypointer} collects data in one level depth. More
-data will be collected upon the developer's request by re-execution.
-
-We needed to build an interface to different execution points which
-are presented at the same time. The current \textit{Querypointer}
-interface resembles the script panel interface while it keeps the
-history of navigation.
+\subsection{Re-Execution, reproduction point and data collection}
+\textit{Querypointer} needs a test case to reproduce the
+execution and conditions to correctly recognize the reproduction point. 
+Although both elements can be directly provided by developer, \textit{Querypointer}
+is also able to automatically create them from the first execution.
+
+\textit{Querypointer} keeps track of breakpoint hits and user steppings. For example, 
+if developer query \textit{lastChange} at the third hit of breakpoint \textit{b}, in
+re-execution, third hit of breakpoint b recognized as the reproduction point.
+
+To build a test case from one execution, two elements should be carefully 
+considered. First, the initial state should be the same as the initial state
+of execution. Second, similar actions and events should be applied to
+the program during the execution. \textit{Querypointer} supports two mechanism
+for automatic re-execution: local-reproduction, record-replay. The first one,
+recalls the function at the bottom of call stack with the same parameters. The idea
+behind this mechanism is that many bugs in web pages can be reproduced by firing
+an event like clicking on a button. The second one, in the first execution, record phase, 
+stores the initial page url and captures user actions. In the replay phase, it opens
+the same url and applies user actions. The local reproduction mechanism provides
+shorter re-execution cycles while the record-replay is more accurate about the
+initial state.
+
+In addition to the data collected at every change event for identifying the \textit{lastChange}
+result, \textit{Querypointer} partially stores values in program state. If developer asks for 
+some values which have not been stored, \textit{Querypointer} re-executes and collects the requested data.
+There is a trade-off between the amount of data collected at every change event and the number of re-executions. 
+By default, \textit{Querypointer} stores values up to one level depth in objects.
+
+% Discuss what happens when assumptions changes, like object creation location.
 
@@
 
+\bibitem[Firefox(2010)]{Firefox}
+Firefox. \newblock http://www.mozilla.com.
+
+\bibitem[Hofer(2006)]{Hofer}
+C. Hofer, M. Denker, and C. St\'{e}phane. \newblock Implementing a backward-in-time debugger.
+\newblock In Proceedings of\emph{NODe’06},
+volume P-88, pages 17–32. Lecture Notes in Informatics, 2006.
+
 \bibitem[Ko(2008)]{Ko}

### 2010-10-27 trunk/papers/pldi2011/sigplanconf-template.tex
reword introduction

@@
 \section{Introduction}
-Debugging is an inevitable part of programming, still hard and time-consuming.
-To fix a bug, developers have to reproduce and monitor the buggy execution several times to understand the program's unexpected behavior.
-Trial and error, guess-work and analyzing huge collected data are the inseparable parts of this process.
-According to \cite{LaToza}, developers spend about fifty percent of their time debugging.
-Therefore, enhancements to debugging techniques and tools can considerably save developers' time and improve programs' quality.
-
-Locating defects cause the bug is the main part of debugging.
-A common strategy for locating defects is starting from bug symptoms and backward movement by following the origins to wrong values.
-While this strategy seems straightforward and effective, applying this strategy using traditional methods is complicated.
-There are two traditional approaches to debugging, breakpoint-based and log-based debugging.
-None of these approaches assist developer in finding origins to a wrong value.
-It is due to developer to search source files, find the list of possible origins to a wrong value and set breakpoints or insert log statements in a way that covers all possible origins.
-
-The next dilemma is data collection. In breakpoint debugging,
-developer has to memorize values or manually collect data at every
-breakpoint hit. As the number of breakpoint hits increases, the
-process of checking the program state, collecting data and resuming
-the execution becomes cumbersome. While in breakpoint-based debugging,
-the whole program state is available to developer, in log-based
-debugging, developer has to decide about data should be collected when
-inserts the log statement. It is very common that developer has to
-repeat this step several times due to insufficient collected
-data. Once the adequate data is collected, it still requires analyzing
-and understanding. Developers usually end up in dealing with long log
-files and analyzing huge collected data.
-
-To address the mentioned problems, we propose a new functionality in
+
+According to \cite{LaToza}, developers spend about fifty percent of
+their time debugging. To fix a bug, developers typically reproduce and
+monitor the buggy execution several times to understand the program's
+unexpected behavior. Trial and error, guess-work, and analyzing large
+and complicated data make debugging difficult and time-consuming. Any
+enhancement to debugging techniques and tools can save developers'
+time, reducing development costs and improve programs' quality.
+
+A common strategy for locating defects starts from bug symptoms and
+works backwards, moving from a point in the program execution where a
+value appears to be incorrect back to the point were that value was
+set.  There are two conventional approaches used: breakpoint-based and
+log-based debugging. Both approaches require tedious steps of
+selecting data to be collected, collecting the data, then analyzing
+the results.
+
+In breakpoint debugging, developers select data to be collected by
+searching through source files and setting breakpoints. To determine
+where a value was set incorrectly, a developer must list and set
+breakpoints at all possible points of the change for the value. At
+every breakpoint the developer must determine if the location is in
+fact related to the questionable value change then study the complex
+debugger user interface and memorize values or manually collect
+data. As the number of breakpoint hits increases, the process of
+checking the program state, collecting data and resuming the execution
+becomes cumbersome.
+
+In log-based debugging, developers select data to be collected by
+inserting statements for all points of possible change.  While in
+breakpoint-based debugging, the whole program state is available to
+developer, in log-based debugging, developer has to decide about data
+should be collected when inserts the log statement. It is very common
+that developer has to repeat this step several times due to
+insufficient collected data, or to wait a long time because too much
+data is recorded. Once the adequate data is collected, it still
+requires analyzing and understanding. Developers usually end up in
+dealing with long log files and analyzing huge collected data.  None
+of these approaches assist developer in finding origins to a wrong
+value.
+
+To address these problems, we propose a new functionality in
 debuggers, \textit{lastChange}, which locates the origin of a wrong
-value. It works based on program re-execution similar to the practice
-in using breakpoints and log statements. Contrary to other
-replay-based alogrithms which require the same re-executions
-(instruction by instruction), the only prerequisite for
-\textit{lastChange} functionality is bug reproducibility (i.e., there
-is a test case which reproduces the bug). Assume that the program
-execution is paused on a breakpoint and the developer is suspicious
-about the value of an object property or a variable. The developer
-queries \textit{lastChange} on the value and it is due to debugger to
-locate and shows the last change of the object property or
-variable. Debugger reproduces the buggy execution and collects limited
-data and once the execution reaches the same place (i.e., the same
-breakpoint hit), call it \textit{reproduction point}, it pauses the
-execution, analyzes the collected data and shows the location of the
-last change to the developer. The developer can also examine the
-program state at the located point of execution, and continue
-debugging by more \textit{lastChange} queries from that point.
+value. It uses program re-execution similar to the practice
+in using breakpoints and log statements.
+
+Imagine a program execution paused on a breakpoint and a developer
+suspicious about the value of an object property or a variable. The
+developer queries \textit{lastChange} on the value. The debugger
+locates and shows the last change of the object property or
+variable. Debugger reproduces the buggy execution and collects data
+and once the execution reaches the same place (i.e., the same
+breakpoint hit), it pauses the execution, analyzes the collected data
+and shows the location of the last change to the developer. The
+developer can also examine the program state at the located point of
+execution, and continue debugging by more \textit{lastChange} queries
+from that point.
+
+We refer to the breakpoint used in \textit{lastChange} as the
+\textit{reproduction point}: it is then point the developer knows
+reproduces the bug and it is the point were the \textit{lastChange}
+algorithm ends. The ability to identify this reproduction point, that
+is a test case and a breakpoint after the bug is appears, is the only
+prerequisite for \textit{lastChange} functionality.  This means
+\textit{lastChange} can be implemented on top of a conventional
+breakpoint debugger and it does not require a special environment to
+create identical, instruction by instruction, re-executions.
 

### 2010-10-27 papers/pldi2011/sigplanconf-template.tex
remove section Evaluation

@@
 
-\section{Evaluation}
+%\section{Evaluation}
 %\subsection{\textit{lastChange} effectiveness}
@@
 
-If we assume that the total number of instructions in an execution is
-$n$ and $m$ change event happens during one execution and for every
-change event $k$ additionial instructions should be executed, the
-execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
-and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
+%If we assume that the total number of instructions in an execution is
+%$n$ and $m$ change event happens during one execution and for every
+%change event $k$ additionial instructions should be executed, the
+%execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
+%and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
 

### 2010-10-28 papers/pldi2011/sigplanconf-template.tex

@@
 wrong value executed before the wrong value appeared. Searching with
-breakpoint- or log- based debuggers demands persistance and
+breakpoint- or log- based debuggers demands persistence and
 significant experience with the application being debugged. We propose
@@
 
-As a proof of concept, we developed \textit{Querypointer}, a prototype
+As a proof of concept, we developed \textit{Querypoint}, a prototype
 which enhances a popular JavaScript debugger, Firebug, with
-\textit{lastChange} feature. Moreover, \textit{Querypointer} provides
+\textit{lastChange} feature. Moreover, \textit{Querypoint} provides
 mechanisms for automated bug reproduction, and a novel user interface
@@
 
-Our contribution in this paper is the algorithm \textit{lastchange},
+Our contribution in this paper is the algorithm \textit{lastChange},
 which locates the last place a value is changed, gathers other values
@@
 technology. We demonstrate the feasibility of the algorithm with
-\textit{Querypointer}, an implementation extending the Firebug
-JavaScript debugger. \textit{Querypointer} also provides mechanism for
+\textit{Querypoint}, an implementation extending the Firebug
+JavaScript debugger. \textit{Querypoint} also provides mechanism for
 automated bug reproduction, and a novel user interface which
@@
 \section{Introductory example}
+\label{sec:introExample}
 
@@
 To start debugging, the developer sets a breakpoint
-on line 22 and once the button is clicked execution is paused at line
+on line 22 and, once the button is clicked, execution is paused at line
 22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
@@
 this value. To do so, the developer runs \textit{lastChange} command
-on \texttt{myCondition.value} at this point. Debugger re-executes the
-execution and pauses at the reproduction point and shows line 25-the
-place \texttt{undefined} value is assigned to
+on \texttt{myCondition.value} at this point. This re-executes the
+program and pauses at the reproduction point,  showing line 25-the
+place \texttt{oldValue} is assigned to
 \texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
@@
 As demonstrated in Figure ~\ref{fig:example-points}, the developer
-examined three points of execution. The first point was the breakpoint set by the developer.
-The second and third points preceded the breakpoint in time.
+examined three points of execution. The first point, the reproduction point,  was the breakpoint set by the developer.
+The second and third points preceded the reproduction point in execution sequence.
 All three points-the history
@@
 \includegraphics{5-example-points.jpg}
-\caption{The examined points before locating the defect.}
+\caption{The examined points before locating the defect.
+The arrow represents the logical forward progress of the program.
+Three actual executions are superimposed on this arrow.
+All three stop at the reproduction point indicated by the circle 1.
+After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
+After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
 \label{fig:example-points}
@@
 
-\subsection{\textit{lastChange} on object propery}
+\subsection{\textit{lastChange} on object property}
 To simplify the algorithm explanation and defer technical details, we
 define two basic operations and later we explain the details of these
-two operations. The first opertion is \texttt{objectId()}: given a
+two operations. The first operation is \texttt{objectId()}: given a
 JavaScript object it returns an integer as its identifier. This
-identifier is unique to the object during one execution. The second
+identifier is unique to the object during one execution.  By using an
+object id instead of an object reference we allow the garbage
+collector to reclaim the space for dead objects just at would in the
+absence of the debugger. The second
 operation is \texttt{setPropertyChangeHook()}: given a function and a
@@
 to only created objects in one location instead of all objects.
-
-\begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
-\caption{The list of property \texttt{foo} change events and
-  \texttt{bar} id at the reproduction point which identifies the last
-  change of \texttt{bar.foo} in the list. Column 3 is also a change of
-  the object we want to study, id 1010, but it is not the last change;
-  Column 5 is also a change of a property \texttt{foo} but its not for
-  the object we are interested in.}
-\label{fig:foo-changes1}
-\end{figure}
 
@@
 execution. \texttt{bar} id at the reproduction point is 1010, so the
-last change of \texttt{bar.foo} is the fourth column.  By using an
-object id instead of an object reference we allow the garbage
-collector to reclaim the space for dead objects just at would in the
-absence of the debugger.
+last change of \texttt{bar.foo} is the fourth column.
+
+\begin{figure}[htp]
+\includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
+\caption{The list of property \texttt{foo} change events and
+  \texttt{bar} id at the reproduction point which identifies the last
+  change of \texttt{bar.foo} in the list. Column 3 is also a change of
+  the object we want to study, id 1010, but it is not the last change;
+  Column 5 is also a change of a property \texttt{foo} but its not for
+  the object we are interested in.}
+\label{fig:foo-changes1}
+\end{figure}
 
@@
 variable in the frame comes from one of the scopes in the frame's
-scope chain. Once developer asks for the last change of variable
-\texttt{foo} at the reproduction point, debugger first determines the
+scope chain. Once a developer asks for the last change of a variable with name 
+\texttt{foo} at the reproduction point, the debugger first determines the
 variable's scope as follows: it iterates over the scopes in the scope
@@
 
+\begin{figure}[htp]
+\begin{verbatim}
+
+  function f(){
+    var x;
+    x++;
+    if (!stop) f();
+  }
+
+Sample Trace:
+
+   f()
+A  |  x changes, scope 1 
+   |  f()
+   |  |  x changes, scope 2
+   |  |  f()
+B  |  |  |  x changes, scope 3 
+C  |  ... , scope 1
+
+\end{verbatim}
+\caption{A recursive call trace demonstrates the need for scope
+  id. Querying \textit{lastChange} on \texttt{x} at point C should
+  return point A not B.}
+\label{fig:recursive}
+\end{figure}
+
 \subsubsection{global and \texttt{with} scopes}
 Global scope is the the most outer scope in the scope chain and it is
-also refered to as the global object (the \texttt{window}
+also referred to as the global object (the \texttt{window}
 object in Web pages). This scope is a regular JavaScript object and therefore every
@@
 parameter. Every property of this parameter object is available inside the
-block as a variable. Debugger treats the case where variable's scope
+block as a variable. \textit{lastChange} treats the case where variable's scope
 is global or \texttt{with}, like \textit{lastChange} on an object
@@
 employ a different approach.
-
-\begin{figure}[htp]
-\begin{verbatim}
-
-  function f(){
-    var x;
-    x++;
-    if (!stop) f();
-  }
-
-Sample Trace:
-
-   f()
-A  |  x changes; 
-   |  f()
-   |  |  x changes;
-   |  |  f()
-B  |  |  |  x changes; 
-C  |  ?
-
-\end{verbatim}
-\caption{A recursive call trace demonstrates the need for scope
-  id. Querying \textit{lastChange} on \texttt{x} at point C should
-  return point A not B.}
-\label{fig:recursive}
-\end{figure}
 
@@
 recursive calls. Without considering the scopes calling \textit{lastChange(x)}
-at point C will return point B while the right answer is point A. Using
-\texttt{scopeId()} operation, the scope id is also stored at every variable
-change event.
-
-If developer asks for the last change of variable \texttt{foo} at the 
+at point \texttt{C} in scope 1 will return point \texttt{B} which is a change of \texttt{x} in 
+scope 2 while the right answer is point \texttt{A}. To resolve this issue, an id
+is assigned to the scope by \texttt{ScopeId()} operation and the scope id is also stored 
+at every variable change event.
+
+If the developer asks for the last change of variable \texttt{foo} at the 
 reproduction point in a program, debugger calls 
-\texttt{setVariableChangeH-} \texttt{ook()} with the variable's defining
+\texttt{setVariableChang-} \texttt{eHook()} with the variable's defining
 block and name as parameters and re-executes the
@@
 The algorithm we explained so far needs an enhancement to support
-longer sequence of \textit{lastChange}s. We explain first the issue
+cascades of \textit{lastChange}s. We explain first the issue
 and then the solution. Consider the following points:
@@
  \end{center}
-According to the algorithm explained in the previous section none of
-the points B and C can be identified before reaching point
-A. Therefore, all \texttt{x} change events for point B and all \texttt{y}
+According to the algorithm explained in the previous section
+the points B and C cannot be identified before reaching point
+A. That is, as execution moves through point B we cannot know it will be the point of last change until
+we reach A, and we cannot apply the simple algorithm to look for point C until we know B. 
+ Therefore, all \texttt{x} change events for point B and all \texttt{y}
 change events for point C are stored. Once the execution reaches point A,
@@
 event. This algorithm does does a dependency analysis between all
-\textit{lastChange} queries and computes the list additional data
+\textit{lastChange} queries and computes the list of additional data
 required to be collected at each change event. For example in the
@@
 collected at all points \texttt{x} changes. Having this additional
-data, locating point C, using \texttt{baz} id at point B is
-straightforward (Figure ~\ref{fig:lastchange-lastchange}).
+data, \texttt{baz} id at point B, it is enough to look at the list
+of \texttt{y} changes and find the last change event with the same 
+owner id (Figure ~\ref{fig:lastchange-lastchange}).
 
@@
 The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and
-\textit{Querypointer} is developed over this interface.
+\textit{Querypoint} is developed over this interface.
+Our prototype implementation defines our four primitive operations in JavaScript code and using techniques which are cumbersome and comparatively slow to execute.
+A professionally useful debugger would implement these primitive operations in the Javasript engine.
 
@@
 otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. To set %\textit{CHECK THAT} 
+for each new \texttt{\_objectId} needed. To set
 the property, we call the \texttt{defineProperty} standard JavaScript
@@
 of global object properties. At the beginning of execution, no object
-excepting the global object is available. Therefore we defined and
-implemented \texttt{setPropertyChangeHook()} to work in the rest of
-the cases.
-
-The Firefox JavaScript engine does not current support
-\texttt{setPro-}
-\texttt{pertyChangeHook()} (see however []).  For %\cite{bugzilla}
+excepting the global object is available.  For 
 the our \textit{lastChange} prototype we created a version of
-\texttt{setPropertyChangeHook()} using only features of the current
-engine.  The basic strategy is to get a reference to the object just
+\texttt{setPropertyChangeHook()}.  The basic strategy is to get a reference to the object just
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object.  Setting a flag into the Firefox
+property changes in the object.  Setting a flag\cite{JSD} into the Firefox
 JavaScript engine we can get file URL and line number for each object
@@
 
-Here, we implicitly assumed that the object will be created at 
-the same location in the next execution. So, what does happens if it
-is not true? Well, once the execution reaches the reproduction point, it
-reveals that the object has been created in different location. This time,
-debugger re-executes the program considering both locations as possible 
-object creation locations.
-
-\subsection{Tracking object creation}
 The only data we have is the object creation location including the
@@
 
-\begin{figure}[htp]
-\begin{verbatim}
-(a) Case 1:
-20 x.y = new myConstructor();
-
-(b) Case 2:
-19  parentObject = {
-20   	  newObject : {
-21  			x : 5
-22  }}
-
-(c) Case 3:
-20 myFunction({myProperty:5});
-
-(d) Case 4:
-20 a[++i] = new myConstructor();
-
-\end{verbatim}
-\caption{Examples of three types of JavaScript object creatin statements.}
-\label{fig:objectCreation}
-\end{figure}
-
 The new object can also be set as the property of a parent object by a
@@
 There is another case for new objects and when they are passed as
-arguments to other functions Figure~\ref{fig:objectCreation}(c). In these
+arguments to other functions (Figure~\ref{fig:objectCreation}(c)). In these
 cases instead of step-over we use step-in and we get the corresponding
@@
 of assignee statements. Obviously, evaluating this statement doesn't return
-a reference to the new object.
+a reference to the new object. Our prototype implementation does not yet handle these kinds of unusual cases.
+
+Throughout this section we implicitly assumed that the object will be created at 
+the same location in the next execution. So, what does happens if it
+is not true? Well, once the execution reaches the reproduction point, it
+reveals that the object has been created in different location. This time,
+debugger re-executes the program considering both locations as possible 
+object creation locations.
+
+\begin{figure}[htp]
+\begin{verbatim}
+(a) Case 1:
+20 x.y = new myConstructor();
+
+(b) Case 2:
+19  parentObject = {
+20   	  newObject : {
+21  			x : 5
+22  }}
+
+(c) Case 3:
+20 myFunction({myProperty:5});
+
+(d) Case 4:
+20 a[++i] = new myConstructor();
+
+\end{verbatim}
+\caption{Examples of three types of JavaScript object creatin statements.}
+\label{fig:objectCreation}
+\end{figure}
 
 \subsection{\texttt{scopeId()} operation}
-Debugger sets a hook at the beginning of all code blocks need
+The debugger sets a hook at the beginning of all code blocks needing
 a scope id whenever the block is loaded. The scope id is kept as a variable with name 
-\texttt{\_scopeId} in the scope. Whenever the hook hits which means a new scope
+\texttt{\_scopeId} in the scope. Whenever the hook hits,  meaning a new scope
 is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
@@
 \subsection{\texttt{setVariableChangeHook()} operation}
-Variables defined in local, closure and catch scopes are only change in
+Variables defined in local, closure, and catch scopes are only changed in
 their scope; that includes the defining scope and scopes nested inside of them.
@@
 \subsection{Re-Execution, reproduction point and data collection}
-\textit{Querypointer} needs a test case to reproduce the
+\textit{Querypoint} needs a test case to reproduce the
 execution and conditions to correctly recognize the reproduction point. 
-Although both elements can be directly provided by developer, \textit{Querypointer}
+Although both elements can be directly provided by developer, \textit{Querypoint}
 is also able to automatically create them from the first execution.
 
-\textit{Querypointer} keeps track of breakpoint hits and user steppings. For example, 
+\textit{Querypoint} keeps track of breakpoint hits and single steps. For example, 
 if developer query \textit{lastChange} at the third hit of breakpoint \textit{b}, in
@@
 of execution. Second, similar actions and events should be applied to
-the program during the execution. \textit{Querypointer} supports two mechanism
+the program during the execution. \textit{Querypoint} supports two mechanism
 for automatic re-execution: local-reproduction, record-replay. The first one,
@@
 In addition to the data collected at every change event for identifying the \textit{lastChange}
-result, \textit{Querypointer} partially stores values in program state. If developer asks for 
-some values which have not been stored, \textit{Querypointer} re-executes and collects the requested data.
+result, \textit{Querypoint} partially stores values in program state. If developer asks for 
+some values which have not been stored, \textit{Querypoint} re-executes and collects the requested data.
 There is a trade-off between the amount of data collected at every change event and the number of re-executions. 
-By default, \textit{Querypointer} stores values up to one level depth in objects.
+By default, \textit{Querypoint} stores values up to one level depth in objects.
 
@@
 
-\section{The effect of Non-determinism}  %flying over non-determinism
-\subsection{Reproducible Non-deterministic Execution}
+\section{Reproducible Non-deterministic Execution}
 
@@
 events during the execution. When the developer selects a value and
-asks for \textit{lastChange}, they are expressing an hyptothesis that
+asks for \textit{lastChange}, they are expressing an hypothesis that
 the value is related to the defect. Therefore the reproducibility of
@@
 confound breakpoint debuggers will be easier to find with
-\textit{lastChange}.  Consider the following example.
-Figure ~\ref{fig:counter-example} shows a function with processes an
-array. The array contains numbers except one itme which is
+\textit{lastChange}.  Consider the example in 
+Figure ~\ref{fig:counter-example}. It shows a function which processes an
+array. The array contains numbers except one item which is
 \texttt{undefined} and it causes a bug in line 30. There is a call to
 \texttt{randomPermutation} function in line 11 which randomly
-permutates the array item. So at every execution the
+permutes the array item. So at every execution the
 \texttt{undefined} item will be in a new place. Calling
@@
 watchpoints in an entire execution at the reproduction point where we
-know the defect has already occured and only show the final result to
+know the defect has already occurred and only show the final result to
 the developer.
@@
 debugging, we can only determine this empirically, by observing
-multiple executions with different values. Unlike conventionaly
+multiple executions with different values. Unlike conventional
 breakpoint debugging, implementations of \textit{lastChange} readily
@@
 one step to convince implementers to put \textit{lastChange} in the
-field.  Thus our goal here is a persausive argument.
+field.  Thus our goal here is a persuasive argument for potential implementors.
 
@@
 
-\subsection{developers need an operation like \protect\textit{lastChange} }
+\subsection{Developers need an operation like \protect\textit{lastChange} }
 
@@
 and know the defect. Otherwise they need to figure out what operation
-causes the incorrect value. Thus \textit{lastChange} addresses a key
+causes the incorrect value. Here \textit{lastChange} takes over and addresses a key
 part of the debugging process.
 
-\subsection{developers can learn to use \protect\texttt{lastChange}}
+\subsection{Developers can learn to use \protect\texttt{lastChange}}
 
@@
 \textit{lastChange} can be easily activated by operations on the
-graphical representation of erroneous data in a debugger. Intepreting
+graphical representation of erroneous data in a debugger. Interpreting
 the results should be only slightly more difficult. We designed the
@@
 
-\subsection{practical implementations are feasible}
+\subsection{Practical implementations are feasible}
 
@@
 
-\subsection{in most cases \protect\texttt{lastChange} will be much faster than current alternatives}
+\subsection{In most cases \protect\texttt{lastChange} will be much faster than current alternatives}
 
@@
 that added code, then analyze the log. (To be fair, the log can become
-a permenant debugging aid.) Automatic logging as we discussion in
-[secref] causes about one or two orders of magnitude slow down.
-
-\subsection{the worst cases are not more common or more painful than alternatives}
+a permanent debugging aid.) Automatic logging as we discussion in
+\ref{sec:relatedWork} causes about one or two orders of magnitude slow down.
+
+\subsection{The worst cases are not more common or more painful than alternatives}
 
@@
 Of course breakpoints are not feasible in these cases and logging
-becomes unyieldy. Since automatic logging solutions are highly tuned,
+becomes unwieldy. Since automatic logging solutions are highly tuned,
 their overhead in this case will likely be much less than
@@
 %$n$ and $m$ change event happens during one execution and for every
-%change event $k$ additionial instructions should be executed, the
+%change event $k$ additional instructions should be executed, the
 %execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
@@
 \section{Related Work}
+\label{sec:relatedWork}
 
@@
 approaches impose much less runtime overhead (about two orders of
-magnitudes) comparing to logging-based appproches. However, developer
+magnitudes) comparing to logging-based approaches. However, developer
 has to re-execute the buggy execution several
@@
 replay and uses a counter to correctly locate a point in the next
-execution. The main disadvantage of these appraoches is requiring the
+execution. The main disadvantage of these approaches is requiring the
 exactly the same executions. Even one instruction difference between
@@
 \textit{lastChange} doesn't require any special feature in the
-re-rexecution and it is fit to everyday's developers' debugging
+re-execution and it is fit to  developers' everyday debugging
 practice.
@@
 
-\section{Conclusions and Future Work}
+\section{Conclusion}
+\textit{lastChange} provides critical information for debugging programs: the location and state at the point where a questionable value was assigned.
+It builds upon existing technology and developer experience making it a practical solution for implementers.
+Our prototype demonstrates the feasibility of \textit{lastChange} and its user interface hints at the potential this approach can have in organizing the debugging experience.
 
@@
 \bibitem[Hofer(2006)]{Hofer}
-C. Hofer, M. Denker, and C. St\'{e}phane. \newblock Implementing a backward-in-time debugger.
-\newblock In Proceedings of\emph{NODe’06},
-volume P-88, pages 17–32. Lecture Notes in Informatics, 2006.
+C. Hofer, M. Denker, and S. Ducasse. \newblock Implementing a backward-in-time debugger.
+\newblock In Proceedings of\emph{NODe'06},
+volume P-88, pages 17-32. Lecture Notes in Informatics, 2006.
 

### 2010-10-28 papers/pldi2011/sigplanconf-template.tex

@@
 \caption{A recursive call trace demonstrates the need for scope
-  id. Querying \textit{lastChange} on \texttt{x} at point C should
-  return point A not B.}
+  id. In the absence of scope id, querying \textit{lastChange} on \texttt{x}
+  at point C in scope 1 returns point B which is the last change of variable 
+  \texttt{x} but happens in another scope. However, the right answer is point A
+  which is in the same scope as point C.}
 \label{fig:recursive}
@@
 Firebug itself is an extension of the Firefox browser\cite{Firefox}. %\cite{firefox-version-3.6}
-The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and
+The Firefox JavaScript engine provides a JavaScript debugging interface [] and %\cite{JSD}
 \textit{Querypoint} is developed over this interface.
@@
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object.  Setting a flag\cite{JSD} into the Firefox
+property changes in the object.  Setting a flag[] into the Firefox %\cite{JSD}
 JavaScript engine we can get file URL and line number for each object

### 2010-10-28 papers/pldi2011/sigplanconf-template.tex

@@
   point. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth,
-    height=.19\textheight]{1-bp22.jpg}}
+    height=.17\textheight]{1-bp22.jpg}}
 
@@
   value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
-    height=.19\textheight]{2-bp22-lastChange.jpg}}
+    height=.17\textheight]{2-bp22-lastChange.jpg}}
 
@@
   point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,
-    height=.23\textheight]{3-lastChange.jpg}}
+    height=.21\textheight]{3-lastChange.jpg}}
 

### 2010-10-29 trunk/papers/pldi2011/sigplanconf-template.tex
minor fix ups to related work

@@
 developer queries \textit{lastChange} on the value. The debugger
-locates and shows the last change of the object property or
-variable. Debugger reproduces the buggy execution and collects data
+reproduces the buggy execution and collects data
 and once the execution reaches the same place (i.e., the same
@@
 We refer to the breakpoint used in \textit{lastChange} as the
-\textit{reproduction point}: it is then point the developer knows
+\textit{reproduction point}: this is a point where the developer knows
 reproduces the bug and it is the point were the \textit{lastChange}
-algorithm ends. The ability to identify this reproduction point, that
-is a test case and a breakpoint after the bug is appears, is the only
+algorithm ends. The ability to identify this reproduction point, i.e.
+ a test case and a breakpoint after the bug is appears, is the only
 prerequisite for \textit{lastChange} functionality.  This means
@@
 
+\begin{figure}[htp]
+\begin{verbatim}
+
+  function f(){
+    var x;
+    x++;
+    if (!stop) f();
+  }
+
+Sample Trace:
+
+   f()
+A  |  x changes, scope 1 
+   |  f()
+   |  |  x changes, scope 2
+   |  |  f()
+B  |  |  |  x changes, scope 3 
+C  |  ... , scope 1
+
+\end{verbatim}
+\caption{A recursive call trace demonstrates the need for scope
+  id. In the absence of scope id, querying \textit{lastChange} on \texttt{x}
+  at point C in scope 1 returns point B which is the last change of variable 
+  \texttt{x} but happens in another scope. However, the right answer is point A
+  which is in the same scope as point C.}
+\label{fig:recursive}
+\end{figure}
+
 \subsubsection{global and \texttt{with} scopes}
 Global scope is the the most outer scope in the scope chain and it is
-also refered to as the global object (the \texttt{window}
+also referred to as the global object (the \texttt{window}
 object in Web pages). This scope is a regular JavaScript object and therefore every
@@
 Firebug itself is an extension of the Firefox browser\cite{Firefox}. %\cite{firefox-version-3.6}
-The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and
-\textit{Querypointer} is developed over this interface.
+The Firefox JavaScript engine provides a JavaScript debugging interface [] and %\cite{JSD}
+\textit{Querypoint} is developed over this interface.
+Our prototype implementation defines our four primitive operations in JavaScript code and using techniques which are cumbersome and comparatively slow to execute.
+A professionally useful debugger would implement these primitive operations in the Javasript engine.
 
@@
 of global object properties. At the beginning of execution, no object
-excepting the global object is available. Therefore we defined and
-implemented \texttt{setPropertyChangeHook()} to work in the rest of
-the cases.
-
-The Firefox JavaScript engine does not current support
-\texttt{setPro-}
-\texttt{pertyChangeHook()} (see however []).  For %\cite{bugzilla}
+excepting the global object is available.  For 
 the our \textit{lastChange} prototype we created a version of
-\texttt{setPropertyChangeHook()} using only features of the current
-engine.  The basic strategy is to get a reference to the object just
+\texttt{setPropertyChangeHook()}.  The basic strategy is to get a reference to the object just
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object.  Setting a flag into the Firefox
+property changes in the object.  Setting a flag[] into the Firefox %\cite{JSD}
 JavaScript engine we can get file URL and line number for each object
@@
 
-If we assume that the total number of instructions in an execution is
-$n$ and $m$ change event happens during one execution and for every
-change event $k$ additionial instructions should be executed, the
-execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
-and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
+%If we assume that the total number of instructions in an execution is
+%$n$ and $m$ change event happens during one execution and for every
+%change event $k$ additional instructions should be executed, the
+%execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
+%and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
 
 \section{Related Work}
+\label{sec:relatedWork}
 
@@
 debugging. Replay-based approaches capture limited data during
-execution and replay the bug-gy execution to reach past points. In
+execution and replay the buggy execution to reach past points. In
 contrast, logging-based approaches collect enough data during
@@
 replay and uses a counter to correctly locate a point in the next
-execution. The main disadvantage of these appraoches is requiring the
+execution. The main disadvantage of these approaches is requiring the
 exactly the same executions. Even one instruction difference between
-two executions leads to wrong results. This requirement is that
-much restricting that after ten years from bdb paper publication,
-there is no newer implementation of this idea. On the other hand,
+two executions leads to wrong results. On the other hand,
 \textit{lastChange} doesn't require any special feature in the
-re-rexecution and it is fit to everyday's developers' debugging
+re-execution and it is fit to  developers' everyday debugging
 practice.
@@
 
-Two new directions in logging debuggers explore more detailed use of
-the log and more effective logging approaches. WhyLine\cite{Ko}
-provides visual interface to collected runtime information and let
-developer to move on execution log using queries expressed in terms of
-the programming objects. WhyLine stores the program user in-terface in
-addition to program trace and provides answers to why and why not
-questions to the user. Jive\cite{Czyz} depicts the history of
-execution by a sequence diagram and lets user to query on events
-database. Both tools suffer from similar issues with omniscient
-debuggers.
-%both provide models for extending Querypoint debugging to obtain a better user interface while retaining the flexible conven-tional replay model of debugging.
-
 A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
@@
 
+Two new directions in logging debuggers explore more detailed use of
+the log and more effective logging approaches. WhyLine\cite{Ko}
+provides visual interface to collected runtime information and let
+developer to move on execution log using queries expressed in terms of
+the programming objects. WhyLine stores the program user interface in
+addition to program trace and provides answers to why and why not
+questions to the user. Jive\cite{Czyz} depicts the history of
+execution by a sequence diagram and lets user to query on events
+database. Both tools suffer from the requirement of gathering tracing information before their unique capabilities can be used.
+We imagine that the runtime queries we use in \textit{lastChange}  may be used to gather data incrementally for these kinds of debugging approaches.
+
 %Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.

### 2010-10-29 papers/pldi2011/sigplanconf-template.tex

@@
 Firebug itself is an extension of the Firefox browser\cite{Firefox}. %\cite{firefox-version-3.6}
-The Firefox JavaScript engine provides a JavaScript debugging interface [] and %\cite{JSD}
+The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and 
 \textit{Querypoint} is developed over this interface.
@@
 otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. To set
-the property, we call the \texttt{defineProperty} standard JavaScript
-function. \texttt{defineProperty} receives an argument which specifies
-whether the property is enumerable or not. By setting the enumerable
+for each new \texttt{\_objectId} needed. To assign the id to the object we 
+set the id as a regular object property. This might change
+the program behaviour due to the appearance of this property in 
+\texttt{for(property in object)} loops. \texttt{defineProperty} is a standard JavaScript
+function which is available in the next version of Firefox\footnote[1]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty}. \texttt{defineProperty} receives 
+an argument which specifies whether the property is enumerable or not. By setting the enumerable
 field \texttt{false} for \texttt{\_objectId}, this property will not
@@
 exactly the same executions. Even one instruction difference between
-two executions leads to wrong results. This requirement is that
-much restricting that after ten years from bdb paper publication,
-there is no newer implementation of this idea. On the other hand,
+two executions leads to wrong results. On the other hand,
 \textit{lastChange} doesn't require any special feature in the
@@
 
+\bibitem[JSD(2010)]{JSD}
+Mozila JavaScript Debugging Interface(JSD). \newblock http://www.mozilla.org/js/jsd.
+
 \bibitem[Ko(2008)]{Ko}

### 2010-10-29 papers/pldi2011/sigplanconf-template.tex

@@
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object.  Setting a flag[] into the Firefox %\cite{JSD}
+property changes in the object. Setting a flag\footnote[2]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox %\cite{JSD}
 JavaScript engine we can get file URL and line number for each object

### 2010-10-29 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 to practical implementation would likely be integration with the
-increasingly sophisticated just in time compilers [].
+increasingly sophisticated just in time compilers []. In the case of
+tracking variable changes, \texttt{setVariableChangeHook()} can be implemented
+similar to \texttt{setPropertyChangeHook()} if JavaScript scopes-like regular 
+JavaScript objects-support \texttt{watch()} function.
 
 \subsection{In most cases \protect\texttt{lastChange} will be much faster than current alternatives}
-
 When developers try \textit{lastChange}, will they get results fast
@@
 
-\begin{thebibliography}{13}
+\begin{thebibliography}{16}
 \softraggedright

### 2010-11-01 trunk/papers/pldi2011/sigplanconf-template.tex
Claude's comments (first series).

@@
 enhancement to debugging techniques and tools can save developers'
-time, reducing development costs and improve programs' quality.
+time, reduce development costs and improve programs' quality.
 
@@
 value appears to be incorrect back to the point were that value was
-set.  There are two conventional approaches used: breakpoint-based and
+set.  Two conventional approaches are used: breakpoint-based and
 log-based debugging. Both approaches require tedious steps of
@@
 searching through source files and setting breakpoints. To determine
-where a value was set incorrectly, a developer must list and set
-breakpoints at all possible points of the change for the value. At
-every breakpoint the developer must determine if the location is in
+where a value was set incorrectly, a developer must set
+breakpoints at all possible points where the value changes. At
+every breakpoint, the developer must determine if the location is in
 fact related to the questionable value change then study the complex
@@
 breakpoint-based debugging, the whole program state is available to
-developer, in log-based debugging, developer has to decide about data
+developer, in log-based debugging, developer has to decide what data
 should be collected when inserts the log statement. It is very common
-that developer has to repeat this step several times due to
+that the developer has to repeat this step several times due to
 insufficient collected data, or to wait a long time because too much
@@
 
-To address these problems, we propose a new functionality in
+To address these problems, we introduce a new functionality in
 debuggers, \textit{lastChange}, which locates the origin of a wrong
@@
 algorithm ends. The ability to identify this reproduction point, i.e.
- a test case and a breakpoint after the bug is appears, is the only
+ a test case and a breakpoint after the bug has appeared, is the only
 prerequisite for \textit{lastChange} functionality.  This means
@@
 Our contribution in this paper is the algorithm \textit{lastChange},
-which locates the last place a value is changed, gathers other values
+which locates the last place a value has changed, gathers other values
 from that execution point, and allows \textit{lastChange} operations
@@
 
-To start debugging, the developer sets a breakpoint
-on line 22 and, once the button is clicked, execution is paused at line
+By browsing through the code, the developer can quickly determine that the value displayed on the 
+button is set at line 22. To start debugging, the developer sets a breakpoint
+on line 22. Once the button is clicked, execution is paused at line
 22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
@@
 To apply backward search strategy for locating defects, the developer
-first needs to know the origin to the wrong value. To achieve this
-goal using breakpoints, the developer should search code to find and
-set breakpoint at all possible places that
-\texttt{myObject.myProperty} might get a new value.  However, an
+first needs to know the origin of the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find all possible places that
+\texttt{myObject.myProperty} might get a new value and set breakpoint at these locations. However, an
 object and property can be accessed and changed through different
@@
 may lead to the incorrect value observed at line 22. All this work
-must be repeated if a new alias is discovered or if the some
+must be repeated if a new alias is discovered or if some
 information related to the buggy result was missed while stopped on
@@
 
-In contrast, we propose a high-level function in debugger,
+In contrast, we have added a high-level function in debugger,
 \textit{lastChange}, which provides the answer without tedious manual
@@
 re-executes the program and halts again at the breakpoint on line 22.
-However, it shows a new QP panel, centered on the source at line 29
+However, it shows a new panel, called QP, centered on the source at line 29
 (Figure ~\ref{fig:example3}), the point of \textit{lastChange}.  To
-the right, the TraceData panels shows values of properties from the
+the right, the TraceData panel shows values of properties of the
 program state when it passed through line 29.  These two panels
 resemble the Script and Watch panels, but they show data collected by
-the debugger at an execution point which is now past: these are
+the debugger at one execution point which is now past: these are
 'traces' or 'logs' of information collected during the re-execution.
@@
 \texttt{undefined}. The next step is to know when this property got
-this value. To do so, the developer runs \textit{lastChange} command
+this value. To do so, the developer reruns \textit{lastChange} command
 on \texttt{myCondition.value} at this point. This re-executes the
@@
 place \texttt{oldValue} is assigned to
-\texttt{myCondition.value} (Figure ~\ref{fig:example3}). Now it is
+\texttt{myCondition.value} (Figure ~\ref{fig:example4}). Now it is
 clear that the bug occurs because \texttt{oldValue} is
@@
 
-As demonstrated in Figure ~\ref{fig:example-points}, the developer
+As demonstrated in Figure ~\ref{fig:example-points}, the developer has
 examined three points of execution. The first point, the reproduction point,  was the breakpoint set by the developer.
@@
 first one is the breakpoint on line 22, the second one is the point
-which is the last change of \texttt{myObject.myProperty} before
+which is when \texttt{myObject.myProperty} changed before
 reaching the breakpoint and finally the last one is the point of
@@
 points are tagged with red-cycle icons.
+
+\begin{figure*}[htp]
+
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:example2}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel at the right shows the program state at
+  the paused
+  point. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth,
+    height=.17\textheight]{1-bp22.jpg}}
+
+\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
+on the
+  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
+    height=.17\textheight]{2-bp22-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,
+    height=.21\textheight]{3-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. The opened list on the top of the left
+  panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth,
+    height=.23\textheight]{4-lastChange2.jpg}}
+
+\caption{The stages of locating the defect using \textit{lastChange} feature.}
+\label{fig:lastChange}
+\end{figure*}
 
@@
 
-\begin{figure*}[htp]
-
-\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:example2}. The Script
-  panel is selected; it gives access to
-  all loaded source files and allows breakpoints to be set on lines. In this
-  figure, the execution is paused at line 22 by a regular
-  breakpoint. The Watch panel at the right shows the program state at
-  the paused
-  point. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth,
-    height=.17\textheight]{1-bp22.jpg}}
-
-\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
-on the
-  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
-    height=.17\textheight]{2-bp22-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myObject.myProperty}. The left panel, QP, shows the source
-  code at the point of \textit{lastChange}; The right panel,
-  TraceData, shows the collected data at the
-  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,
-    height=.21\textheight]{3-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. The opened list on the top of the left
-  panel shows the visited execution points. Clicking on each point in
-  the list shows the corresponding code and
-  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth,
-    height=.23\textheight]{4-lastChange2.jpg}}
-
-\caption{The stages of locating the defect using \textit{lastChange} feature.}
-\label{fig:lastChange}
-\end{figure*}
-
 Notice that in our example, \textit{lastChange} combines some aspects
@@
 and without a special execution environment beyond the debugger. The
-state of the program memory and the call stack are available at the
+state of the program memory and the call stack are available at each
 lastChange point. Like log-based debugging, the program state and the
 call stack are recorded during program execution. We can't halt the
-program at \textit{lastChange} because we don't know which is the last
+program at \textit{lastChange} because we don't know which point is the last
 one until we return to the original breakpoint. (In section 5 we
@@
 The \textit{lastChange} algorithm is based on program re-execution of
-a program halted on a breakpoint. The breakpoint hit becomes the
-\textit{reproduction point}. The algorithm starts when developer
+a program halted on a breakpoint. The algorithm starts when developer
 examines the program state at a breakpoint hit and asks for the
-\textit{lastChange} of a value.  Debugger sets hooks (a callback
+\textit{lastChange} of a value. The breakpoint hit becomes the
+\textit{reproduction point}. Debugger sets hooks (a callback
 function dependent upon the underlying runtime) on all instructions
@@
 reproduction point, it analyzes the collected data and shows the
-result.  The program state at the execution point for the last change
+result.  The program state at the execution point of the last change
 event is the \textit{lastChange}.
 
-While \textit{lastChange} itself is not a different kind \textit{breakpoint},
+As \textit{lastChange} itself is not a different kind of \textit{breakpoint},
 all of the assumptions developers already have for breakpoints hold
@@
 object id instead of an object reference we allow the garbage
-collector to reclaim the space for dead objects just at would in the
+collector to reclaim the space for dead objects just as it would in the
 absence of the debugger. The second
@@
 string, the function is called whenever a property changes and its
-name matches the string For example, if the property might be
+name matches the string For example, if the is 
 \texttt{foo} so changes to \texttt{bar.foo} or \texttt{baz.foo} would
@@
 a slightly different version of this operation which is restricted 
-to only created objects in one location instead of all objects.
+to the created objects in one location instead of all objects.
 
@@
   function f(){
-    var x;
+    var x = 0;
     x++;
@@
 block as a variable. \textit{lastChange} treats the case where variable's scope
-is global or \texttt{with}, like \textit{lastChange} on an object
+is global or \texttt{with}, like it does on an object
 property.
@@
 Local scope refers to the most nested scope in the scope
-chain and contains the local variables. Closure scope refers to the 
+chain which contains the local variables. Closure scope refers to the 
 scope which is created for a nested function and contains variables 
@@
 a code block, enclosed the executing code. In
-JavaScript, a code block can be identified by the file url and the 
-the block's first instruction program counter. Given this information, debugger is
+JavaScript, a code block can be identified by the file url and  
+the block's first instruction program counter. Given this information, the debugger is
 able to recognize the code block once it is loaded.
 Similar to \textit{lastChange} on object property, we define two basic operations: 
-\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one 
-given a scope returns an integer as the scope's identifier. The second one 
+\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one, 
+given a scope returns an integer as the scope's identifier. The second one, 
 given a callback function, a code block and a variable name-
 which is defined inside the block-, the function is called
-whenever the variable is changed. Figure ~\ref{fig:recursive} demonstrates a case that the same variable
+whenever the variable is changed. Figure ~\ref{fig:recursive} demonstrates a case in which the same syntactically variable
 \texttt{x} is changed several times but in different scopes due to the
@@
 The algorithm we explained so far needs an enhancement to support
-cascades of \textit{lastChange}s. We explain first the issue
+cascades of \textit{lastChange}s. We first explain the issue
 and then the solution. Consider the following points:
@@
 To address this issue, we use Algorithm \ref{dependency-analysis}, to
-create the list of additional data should be collected at a change
-event. This algorithm does does a dependency analysis between all
+create the list of additional data (object id or scope id) should be collected at a change
+event. This algorithm does a dependency analysis between all
 \textit{lastChange} queries and computes the list of additional data
@@
 constructor()}) or function definition statment (\texttt{function()}). 
-By parsing the source code we can easily recognize the statements 
+By parsing the source code we can recognize the statements that
 create an object. The next step is getting a reference to the new object.
 
-The new object can be assigned to an object property or variable by
+The new object can be assigned to an object property or a variable by
 an assignment (\texttt{=}). In these cases we keep the assignee statement 
 at the left side. The idea is that we create a list of assignee statements 
-that the new objects are assigned to them. We set a hook on the creation
+that the new objects are assigned to. We set a hook on the creation
 line. Once the hook hits, we evaluate all assignee statements. Then 
@@
 Although this approach is successful in many ordinary cases, there are some 
-cases that this approach doesn't work. For example in a case
+cases where this approach doesn't work. For example in a case
 where the new object is assigned to \texttt{a[++i]} where i is a variable
@@
 of assignee statements. Obviously, evaluating this statement doesn't return
-a reference to the new object. Our prototype implementation does not yet handle these kinds of unusual cases.
+a reference to the new object. Our prototype implementation does not handle these kinds of unusual cases yet.
 
@@
 The debugger sets a hook at the beginning of all code blocks needing
-a scope id whenever the block is loaded. The scope id is kept as a variable with name 
-\texttt{\_scopeId} in the scope. Whenever the hook hits,  meaning a new scope
+a scope id. The scope id is kept as a variable with name 
+\texttt{\_scopeId} in the scope. Whenever the hook is hit,  meaning a new scope
 is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
@@
 Variables defined in local, closure, and catch scopes are only changed in
-their scope; that includes the defining scope and scopes nested inside of them.
+their scope; that includes the defining scope and scopes nested whithin them.
 For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
@@
 We also set a hook at the first line of the function which is
-corresponding to the line variable is defined. In Figure
+corresponding to the line where the variable is defined. In Figure
 ~\ref{fig:js-closure}, if the execution is paused at line 17 and the
@@
 \textit{Querypoint} keeps track of breakpoint hits and single steps. For example, 
-if developer query \textit{lastChange} at the third hit of breakpoint \textit{b}, in
-re-execution, third hit of breakpoint b recognized as the reproduction point.
+if the developer queries \textit{lastChange} at the third hit of breakpoint \textit{b}, in
+re-execution, the third hit is recognized as the reproduction point.
 
@@
 for automatic re-execution: local-reproduction, record-replay. The first one,
-recalls the function at the bottom of call stack with the same parameters. The idea
+recalls the function at the bottom of the call stack with the same parameters. The idea
 behind this mechanism is that many bugs in web pages can be reproduced by firing

### 2010-11-01 trunk/papers/pldi2011/sigplanconf-template.tex
Claude's comments - 2

@@
 events during the execution. When the developer selects a value and
-asks for \textit{lastChange}, they are expressing an hypothesis that
+asks for \textit{lastChange}, they are expressing the hypothesis that
 the value is related to the defect. Therefore the reproducibility of
@@
 \texttt{undefined} item will be in a new place. Calling
-\textit{lastChange} on \texttt{x} at the place bug happens, gives a
+\textit{lastChange} on \texttt{x} at the place the bug happens, gives a
 point which shows line 14. Although this point exists at every
@@
 breakpoint debugging, implementations of \textit{lastChange} readily
-aid in detecting such cases: as we work back through a series of
+help in detecting such cases: as we work back through a series of
 \textit{lastChange} requests we can compare values with previous
@@
 
-We have presented the \textit{lastChange} algorithm and describe our
+We have presented the \textit{lastChange} algorithm and described our
 prototype implementation. Now we want to convince you that the
@@
 program on a breakpoint they have three kinds of information: a model
-of the program in their head, a call stack showing what part of the
+of the program in their mind, a call stack showing what part of the
 program is halted, and the state at that point (a combination of the
@@
 
-We described our prototype implementation in Sec. 4. A fully usable
+We have described our prototype implementation in Sec. 4. A fully usable
 implementation would require access to the object id at the point of
@@
 replay and uses a counter to correctly locate a point in the next
-execution. The main disadvantage of these approaches is requiring the
+execution. The main disadvantage of these approaches is that they require 
 exactly the same executions. Even one instruction difference between
@@
 Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
-First, it is limited to undefined and null values. Second, this approach dosen't return the last change
+First, it is limited to undefined and null values. Second, this approach dose not return the last change
 of a null variable but the first place that the null value is originated.
@@
 the log and more effective logging approaches. WhyLine\cite{Ko}
-provides visual interface to collected runtime information and let
-developer to move on execution log using queries expressed in terms of
+provides visual interface to collected runtime information and lets
+developer moves on execution log using queries expressed in terms of
 the programming objects. WhyLine stores the program user interface in

### 2010-11-01 papers/pldi2011/sigplanconf-template.tex

@@
 significant experience with the application being debugged. We propose
-a new approach, an algorithm \textit{lastChange}, which automatically
+a new approach, an algorithm called \textit{lastChange}, which automatically
 locates the last point that a value was changed and related
@@
 
-\bibitem[JSD(2010)]{JSD}
-Mozila JavaScript Debugging Interface(JSD). \newblock http://www.mozilla.org/js/jsd.
-
 \bibitem[Ko(2008)]{Ko}

### 2010-11-02 trunk/papers/pldi2011/sigplanconf-template.tex
fixes for claude's comments

@@
 We have presented the \textit{lastChange} algorithm and described our
-prototype implementation. Now we want to convince you that the
-algorithm has practical value. Ultimately, practical value can only be
-proven by developers in the field using the technique. This paper is
-one step to convince implementers to put \textit{lastChange} in the
-field.  Thus our goal here is a persuasive argument for potential implementors.
+prototype implementation. Our goal is practical improvements in debugging. To achieve our goal we need practical JavaScript engines
+to add new debug primitives so that developers in the field can use our new technique. This paper is
+one step to convince implementers to enable \textit{lastChange}.
+Thus we summarize here our arguments that \textit{lastChange} should be supported.
 
@@
 studying the loop code then omitting it from \textit{lastChange}
-operations. As a practical result, this is no different from similar
-issues developers face with any debugger today: occasionally a
+operations. Developers face this issue with any debugger today: occasionally a
 debugger causes too much overhead to be useful for debugging. On
@@
 
-\textit{lastChange} functionality supports obtaining information about
+The algorithm we presented in this paper provides a way to obtain information about
 the execution state logically earlier in the control flow. This

### 2010-11-04 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/trace.js
jsdeventhandler is more independent from firebug-service new test cases

@@ -185,6 +185,9 @@ with (Lang){
                     if (!scope)
                         return null;
 
+                    if (!QPFBUG.Conf.COLLECT_DATA)
+                        return  new TraceScope(null, "", {}); //returns empty scope
+
                     var traceScope;
                     var parentScope, jsClassName, variables, values;
 

### 2010-11-04 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/debugservice.js

@@ -24,6 +24,10 @@ with (Lang){
             this.listeningToFunctions = 0;
             this.nextListenerId = 0;
             this.nextJSObjectId = 0;
+
+            this.counterInterrupt = 0;
+            this.counterFunction = 0;
+            this.counterBreakpoint = 0;
         };
 
         constructor.prototype =
@@ -256,6 +260,7 @@ with (Lang){
 
             //------------------------------------------ jsd hooks -------------------------------------------------
             onInterrupt: function(context, frame, type, rv){
+                this.counterInterrupt++;
                 var copy = cloneObject(this.interruptListeners);
                 for (var i in copy){
                     var interruptListener = copy[i];
@@ -268,6 +273,7 @@ with (Lang){
             },
 
             onFunction: function(context, frame, type){
+                this.counterFunction++;
                 var copy = cloneObject(this.functionListeners);
                 for (var i in copy){
                     var functionListener = copy[i]; 
@@ -280,6 +286,7 @@ with (Lang){
             },
 
             onBreakpoint: function(context, frame, type, rv){
+                this.counterBreakpoint++;
                 var eventRequests = context.qpfbug.eventRequests;
                 var eventRequest;
                 var script = frame.script;

### 2010-11-04 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/jsdeventhandler.js

@@ -17,14 +17,10 @@ var __owner = QPFBUG.Classes;
 
 __owner.JSDEventHandler = function(){
 
-        var constructor = function(ds,fbs){
-            this.ds = ds;
-            this.fbs = fbs;
+        var constructor = function(){
+            this.ds = DebugService.getInstance();
+            this.fbs = QPFBUG.fbs;
             this.cachedContexts = {}; // map <context.uid, executionContext.tag>
-            this.counter = 0;
-            this.counterInterrupt = 0;
-            this.counterFunction = 0;
-            this.counterBreakpoint = 0;
         };
 
         constructor.prototype =
@@ -41,18 +37,18 @@ __owner.JSDEventHandler = function(){
                 // ----- jsd hooks -----
                 //this.replaceFBSFunction("onScriptCreated");
                 //this.replaceFBSFunction("onScriptDestroyed");
-                this.replaceFBSFunction("onDebugger");
+                //this.replaceFBSFunction("onDebugger");
                 //this.replaceFBSFunction("onDebug");
-                this.replaceFBSFunction("onBreakpoint");
+                //this.replaceFBSFunction("onBreakpoint");
                 //this.replaceFBSFunction("onThrow");
                 //this.replaceFBSFunction("onError");
                 //this.replaceFBSFunction("onTopLevel");
-                this.replaceFBSFunction("onInterrupt");
-                this.replaceFBSFunction("onFunction");
+                //this.replaceFBSFunction("onInterrupt");
+                //this.replaceFBSFunction("onFunction");
 
                 // ----- hook/unhook -----
-                //this.replaceFBSFunction("hookScripts");
-                //this.replaceFBSFunction("unhookScripts");
+                this.replaceFBSFunction("hookScripts");
+                this.replaceFBSFunction("unhookScripts");
                 this.replaceFBSFunction("hookInterrupts");
                 this.replaceFBSFunction("unhookInterrupts");
                 this.replaceFBSFunction("hookFunctions");
@@ -76,7 +72,7 @@ __owner.JSDEventHandler = function(){
             },
 
             // ---------------------------------------   fbs functions -----------------------------
-            // Do not use "this" in the following methods.
+            // Important: Do not use "this" in the following methods.
             // because it can be jsdEventHandler or fbs.
             // enables debugger
             enableDebugger : function(){
[…]

### 2010-11-04 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/hardwiredreproducer.js

@@ -35,7 +35,6 @@ __owner.HardWiredReproducer = function(){
                         var tabBrowser = $("content");
                         tabBrowser.removeTab(oldTab);
 
-
                         var openNewTab = function(url, callback)
                         {
                             var tabbrowser = getBrowser();

### 2010-11-04 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/util/lang.js

@@ -40,7 +40,7 @@ with (QPFBUG.Classes){
                             try{
                                 return f.apply(this, arguments); //we use "this" instead of "obj" to make sure "this" is the same as normal execution.
                             }catch(exc){
-                                QPFBUG.Classes.Lang.trace("Error : " + exc, exc);
+                                Lang.trace("Error : " + exc, exc);
                             }
                         }
                     }(p, obj_p);
@@ -136,6 +136,16 @@ with (QPFBUG.Classes){
                 return copy;
             }
             return object;
+        },
+
+        wait: function(millis)
+        {
+            var time = Lang.currentTimeMillis();
+            var curDate = null;
+
+            do {
+                curDate = Lang.currentTimeMillis();
+            }while(curDate-time < millis);
         },
 
         //--------------------------------- from firebug lib.js -----------------------------

### 2010-11-04 qp-fbug/qp-fbug-0.1/src/chrome/content/basics.js
jsdeventhandler is more independent from firebug-service new test cases

@@ -4,10 +4,15 @@ QPFBUG = {};
 
 QPFBUG.Classes = {};
 
-QPFBUG.DBG = true;
+//Configuration
+QPFBUG.Conf = {};
+
+QPFBUG.Conf.COLLECT_DATA = true;
+
+//Debugging
+
+QPFBUG.DBG = false;
 
 //do not include these classes: TraceUtils, Lang, JSDEventHandler, HaltObject, DebugService;
 QPFBUG.DBG_Filter = ["Manager", "ModuleEventHandler", "UIEventHandler", // "DebugService", "ExecutionMonitor",
                      "DebugModel", "Trace", "DebugSession", "Reproduction", "Reproducer", "UIUtils"];
-
-

### 2010-11-04 qp-fbug/qp-fbug-0.1/src/chrome/content/di/monitor.js

@@ -1,0 +1,38 @@
+var EXPORTED_SYMBOLS = ["loadModule"];
+loadModule = function(QPFBUG)
+{
+
+with (QPFBUG.Classes){
+with (Lang){
+
+var __owner = QPFBUG.Classes;
+
+//--------------------------------- Monitor --------------------------------
+
+__owner.Monitor = function(){
+
+        var constructor = function(){
+            this.counter = 0;
+            this.counterInterrupt = 0;
+            this.counterFunction = 0;
+            this.counterBreakpoint = 0;
+        };
+
+        constructor.prototype =
+        {
+
+        };
+
+        constructor.getInstance = function(){
+            if (!QPFBUG.monitor)
+            {
+                QPFBUG.monitor = new Monitor();
+            }
+            return QPFBUG.monitor;
+        };
+
+        return constructor;
+    }();
+}}
+
+};

### 2010-11-04 qp-fbug/qp-fbug-0.1/src/chrome/content/scripts.js

@@ -1,5 +1,5 @@
 // Although this file may be for every new window
-// the js files are loaded only once fore thw whole firefox process.
+// the js files are loaded only once fore the whole firefox process.
 
 var loadScript = function(path, scope)
 {
@@ -74,6 +74,8 @@ loadScript("resource://qpfbug/di/haltobject.js");
 loadScript("resource://qpfbug/di/executionmonitor.js");
 loadScript("resource://qpfbug/di/steppingdriver.js");
 loadScript("resource://qpfbug/di/scriptanalyzer.js");
+loadScript("resource://qpfbug/di/monitor.js");
+
 
 loadScript("resource://qpfbug/parser/jsparser.js");
 

### 2010-11-04 qp-fbug/qp-fbug-0.1/test/usecase/test_double_lastchange.js

@@ -1,4 +1,5 @@
-// Test entry point.                
+//TODO Note: This test is not complete!
+// Test entry point.
 function runTest()
 {
 
@@ -55,13 +56,13 @@ function runTest()
     }
 
     var clickOn_MyObject = function(){
-        var myObjectElt = FW.FBL.getElementsByClass(testData.watchesPanelNode, "memberLabel userLabel")[1];
+        var myObjectElt = FW.FBL.getElementsByClass(testData.watchesPanelNode, "memberLabel userLabel")[1]; //myObject
         FBTest.click(myObjectElt);
         setTimeout(lastChangeOn_MyProperty, 100);
     }
 
     var lastChangeOn_MyProperty = function(){
-        var myPropertyElt = FW.FBL.getElementsByClass(testData.watchesPanelNode, "memberLabel userLabel")[2];
+        var myPropertyElt = FW.FBL.getElementsByClass(testData.watchesPanelNode, "memberLabel userLabel")[2]; //myProperty
         FBTest.executeContextMenuCommand(myPropertyElt, "lastChange", function()
         {
             setTimeout(end, 10000000);

### 2010-11-04 papers/pldi2011/sigplanconf-template.tex

@@
 
-\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
+%\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
+%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+%           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}
+
+\authorinfo{Salman Mirghasemi}
            {Ecole Polytechnique F\'ed\'erale de Lausanne}
-           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}
+           {salman.mirghasemi@epfl.ch}
 
@@
            {johnjbarton@johnjbarton.com}
+
+\authorinfo{Claude Petitpierre}
+           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+           {claude.petitpierre@epfl.ch}
 
@@
 events during the execution. When the developer selects a value and
-asks for \textit{lastChange}, they are expressing the hypothesis that
+asks for \textit{lastChange}, the developer is expressing the hypothesis that
 the value is related to the defect. Therefore the reproducibility of

### 2010-11-06 qp-fbug/qp-fbug-0.1/src/chrome/content/di/debugservice.js
performance bug resolved. code improvements.

@@ -25,9 +25,6 @@ with (Lang){
             this.nextListenerId = 0;
             this.nextJSObjectId = 0;
 
-            this.counterInterrupt = 0;
-            this.counterFunction = 0;
-            this.counterBreakpoint = 0;
         };
 
         constructor.prototype =
@@ -116,8 +113,8 @@ with (Lang){
 
 
             //--------------------------------- SteppingDriver ----------------------------
-            getSteppingDriver: function(stepHandler, context){
-                return new SteppingDriver(this.nextListenerId++, stepHandler, context);
+            getSteppingDriver: function(context){
+                return new SteppingDriver(this.nextListenerId++, context);
             },
 
             releaseSteppingDriver: function(steppingDriver){
@@ -260,7 +257,7 @@ with (Lang){
 
             //------------------------------------------ jsd hooks -------------------------------------------------
             onInterrupt: function(context, frame, type, rv){
-                this.counterInterrupt++;
+                QPFBUG.monitor.ds_counterInterrupt++;
                 var copy = cloneObject(this.interruptListeners);
                 for (var i in copy){
                     var interruptListener = copy[i];
@@ -273,7 +270,7 @@ with (Lang){
             },
 
             onFunction: function(context, frame, type){
-                this.counterFunction++;
+                QPFBUG.monitor.ds_counterFunction++;
                 var copy = cloneObject(this.functionListeners);
                 for (var i in copy){
                     var functionListener = copy[i]; 
@@ -286,7 +283,7 @@ with (Lang){
             },
 
             onBreakpoint: function(context, frame, type, rv){
-                this.counterBreakpoint++;
+                QPFBUG.monitor.ds_counterBreakpoint++;
                 var eventRequests = context.qpfbug.eventRequests;
                 var eventRequest;
                 var script = frame.script;

### 2010-11-06 qp-fbug/qp-fbug-0.1/src/chrome/content/di/steppingdriver.js

@@ -9,17 +9,16 @@ with (Lang){
 
     //Note: There is one assumption behind current Stepping Driver implementation:
     //  It supports only one thread's interrupts/functions during one step.
-    //  Considering restricting events to a context if we assumet that
+    //  Considering restricting events to a context if we assume that
     //  a context only has one running thread, we can have the above assumption.
     //
     //--------------------------- Stepping Driver ----------------------
     __owner.SteppingDriver = function(){
 
-        var constructor = function(id, stepHandler, context){
+        var constructor = function(id, context){
             this.id = id;
             this.steppingMode = SteppingDriver.STEP_MODES.STEP_MIN; //default
             this.debugService = DebugService.getInstance();
-            this.stepHandler = stepHandler;
             this.context = context;
             this.registeredForInterrupts = false;
             this.registeredForFunctions = false;
@@ -30,7 +29,8 @@ with (Lang){
         constructor.prototype = {
 
             //stops at the first interrupt in this context
-            start: function(){
+            stepSoon: function(stepHandler){
+                this.stepHandler = stepHandler;
                 this.isStopped = false;
                 this.steppingMode = SteppingDriver.STEP_MODES.STEP_MIN; 
                 this.registerAsInterruptListener();
@@ -40,7 +40,8 @@ with (Lang){
                 this.startPC = -1;
             },
 
-            step: function(steppingMode, startScriptTag, startLineNo, startPC){
+            step: function(stepHandler, steppingMode, startScriptTag, startLineNo, startPC){
+                this.stepHandler = stepHandler;
                 this.isStopped = false;
                 this.steppingMode = steppingMode;
                 this.startScriptTag = startScriptTag;
@@ -114,6 +115,7 @@ with (Lang){
 
             // ------------------------------ functions called by debug service -------------
             onInterrupt: function(context, frame, type, rv){
+                trace("steppingDriver : onInterrupt " + type + " " + frame.line+ " " + frame.script.baseLineNumber + " " +frame.script.lineExtent);
                 if (context != this.context)
                     return;
                 with(SteppingDriver.STEP_MODES){
@@ -147,6 +149,7 @@ with (Lang){
             },
 
             onFunction: function(context, frame, type){
+                trace("steppingDriver : onFunction " + type + " " + frame.line);
                 var rv = null;
                 var stackDepthChange = 0;
 

### 2010-11-06 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/executionmonitor.js
performance bug resolved. code improvements.

@@ -20,7 +20,10 @@ with (Lang){
         constructor.prototype = {
 
             start: function(callBack, propertyName, frame, type, rv){
-                this.steppingDriver = DebugService.getInstance().getSteppingDriver(this, this.context);
+                trace("ExecutionMonitor starts: " + frame.script.fileName + " " + frame.line);
+                this.steppingDriver = DebugService.getInstance().getSteppingDriver(this.context);
+                this.fileName = frame.script.fileName;
+                this.line = frame.line;
                 this.startScriptTag = frame.script.tag;
                 this.startPC = frame.pc;
                 this.startStackFrameDepth = callStackDepth(frame);
@@ -40,12 +43,13 @@ with (Lang){
                     var refValue = evalInFrame(frame, monitorRef);
                     this.monitorRefValues.push(refValue);
                 }
-                this.steppingDriver.step(3, this.startScriptTag, frame.line, this.startPC); //todo correct line number
+                this.steppingDriver.step(this, 3, this.startScriptTag, this.line, this.startPC); //todo correct line number
             },
 
             stop: function(){
                 this.isStopped = true;
                 DebugService.getInstance().releaseSteppingDriver(this.steppingDriver);
+                trace("ExecutionMonitor ends: " + this.fileName + " " + this.line);
             },
 
             //todo
@@ -66,6 +70,7 @@ with (Lang){
 
                 for (var i=0 ; i<this.monitorRefs.length ; i++){
                     var monitorRef = this.monitorRefs[i];
+                    trace("assignee: " + monitorRef);
                     var refValue = evalInFrame(frame, monitorRef);
                     if (refValue != this.monitorRefValues[i]){
                         this.monitorRefValues[i] = refValue;
@@ -77,17 +82,26 @@ with (Lang){
                             //Object.defineProperty(refValue, "__QPFBUG_ID", { value: objectId });
                             // code for firefox 3.5+
                             //refValue.__defineGetter__("__QPFBUG_ID", function(){return objectId;})
+                            //refValue.__objectId = objectId;
                             this.monitorRefGotNewValue[i] = true;
                             refValue.watch(this.propertyName, bind(this.callBack, this, refValue));
                         }
                     }
                 }
+
                 var shouldContinue = false;
                 for (var i=0 ; i<this.monitorRefs.length ; i++){
                     if (!this.monitorRefGotNewValue[i])
[…]

### 2010-11-06 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/jsdeventhandler.js

@@ -212,6 +212,7 @@ __owner.JSDEventHandler = function(){
                 if (jsdEventHandler.ds_hooksState.interruptHook){
                     var context = jsdEventHandler.getContextFromFrame(frame);
 
+                    Monitor.getInstance().test++;
                     if (context)
                         returnValue = ds.onInterrupt(context, frame, type, rv);
                 }
@@ -304,7 +305,6 @@ __owner.JSDEventHandler = function(){
 
                 jsdEventHandler.fbs_unhookInterrupts.apply(fbs, arguments);
 
-                Monitor.getInstance().counter = 0;
             },
             
             hookFunctions: function(){
@@ -399,9 +399,13 @@ __owner.JSDEventHandler = function(){
                         var context = DebugService.getInstance().registeredContexts[uid];
                         if (context.window == rootWindow)
                         {
-                            this.cachedContexts[frame.executionContext.tag] = context.uid;
+                            if(!this.cachedContexts[frame.executionContext.tag])
+                                this.cachedContexts[frame.executionContext.tag] = {id:context.uid, counter:1};
                             return context;
                         }
+//                        else{
+//                            trace(":::: " + frame.script.fileName + " " + frame.line);
+//                        }
                     }
                 }
                 return null;

### 2010-11-06 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/monitor.js

@@ -12,15 +12,30 @@ var __owner = QPFBUG.Classes;
 __owner.Monitor = function(){
 
         var constructor = function(){
+
+            //jsdeventhandler
             this.counter = 0;
             this.counterInterrupt = 0;
             this.counterFunction = 0;
             this.counterBreakpoint = 0;
+
+            //debugservice
+            this.ds_counterInterrupt = 0;
+            this.ds_counterFunction = 0;
+            this.ds_counterBreakpoint = 0;
+
+            this.test = 0;
         };
 
         constructor.prototype =
         {
-
+            reset : function(){
+                for (p in this){
+                    if (typeof(this[p])=="number"){
+                        this[p] = 0;
+                    }
+                }
+            }
         };
 
         constructor.getInstance = function(){

### 2010-11-15 qp-fbug/qp-fbug-0.1/src/chrome/content/init.js
set depth back to 2

@@ -19,7 +19,7 @@ FBL.ns(function() { with (FBL)
         Firebug.registerModule(ModuleEventHandler.getInstance(window));
 
         FBTrace.DBG_QUERYPOINT = false;
-        QPFBUG.Conf.DATA_COLLECTION_DEPTH = 1;
+        QPFBUG.Conf.DATA_COLLECTION_DEPTH = 2;
 
     }
 }});

### 2010-11-16 qp-fbug/qp-fbug-0.1/src/chrome/content/di/jsdeventhandler.js
QPFBUG works without chromebug.

@@ -21,6 +21,7 @@ __owner.JSDEventHandler = function(){
             this.ds = DebugService.getInstance();
             this.fbs = QPFBUG.fbs;
             this.cachedContexts = {}; // map <context.uid, executionContext.tag>
+
         };
 
         constructor.prototype =
@@ -31,6 +32,7 @@ __owner.JSDEventHandler = function(){
 
                 // ----- fbs functions -----
                 this.replaceFBSFunction("enableDebugger");
+                this.replaceFBSFunction("onDebuggerActivated");
                 //this.replaceFBSFunction("onBreak");
 
 
@@ -55,20 +57,29 @@ __owner.JSDEventHandler = function(){
                 this.replaceFBSFunction("unhookFunctions");
                 //this.replaceFBSFunction("hookCalls");
 
-                // ---- update jsd ----
-                this.fbs.unhookScripts();
-                this.fbs.getJSD().flags = 0;
-                this.fbs.hookScripts();
+                var jsd = this.fbs.getJSD();
+
+                if (jsd){  //if jsd already loaded to firebug-service (in case of running chromebug)
+                    // ---- update jsd ----
+                    this.fbs.unhookScripts();
+
+                    jsd.flags = 0;
+
+                    this.fbs.hookScripts();
+
+                    this.fbs_hooksState = {regularHooks: true,
+                        interruptHook: !!jsd.interruptHook,
+                        functionHook: !!jsd.functionHook}
+                }else{
+                    this.fbs_hooksState = {regularHooks: true,
+                        interruptHook: false,
+                        functionHook: false}
+                }
 
                 this.ds_hooksState = {regularHooks: true,
                      interruptHook: false,
-                     functionHook: false
-                }
+                     functionHook: false }
 
-                this.fbs_hooksState = {regularHooks: true,
-                    interruptHook: !!this.fbs.getJSD().interruptHook,
-                    functionHook: !!this.fbs.getJSD().functionHook
-                    }
             },
 
             // ---------------------------------------   fbs functions -----------------------------
@@ -82,7 +93,19 @@ __owner.JSDEventHandler = function(){
                 var returnValue = jsdEventHandler.fbs_enableDebugger.apply(fbs, arguments);
 
                 //activate object tracing
-                this.fbs.getJSD().flags = 0;
+                jsdEventHandler.fbs.getJSD().flags = 0;
+
+                return returnValue;
+            },
+
[…]

### 2010-11-16 qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js
Implement re-run to obtain one value

@@ -455,7 +455,7 @@ Firebug.Querypoint.TraceDataPanel.prototype = extend(Firebug.WatchPanel.prototyp
 
         // Put the lastChange values at top TODO diff
         for (var watch in tracepoint.traceWatches){
-            this.addMember({expr: watch, value: tracepoint.traceWatches[watch] }, "query", traceMembers, watch, tracepoint.traceWatches[watch], 0 );        
+            this.addMember({expr: watch, value: tracepoint.traceWatches[watch] }, "query", traceMembers, watch, tracepoint.traceWatches[watch], 0 );
         }
 
         if (tracepoint.getQueryType() === "lastChange")
@@ -816,14 +816,29 @@ Firebug.Querypoint.LastChangeTracepointRep = domplate(Firebug.Querypoint.Tracepo
 
 Firebug.Querypoint.TraceDataNotCollectedRep = domplate(Firebug.Rep,
 {
-    tag: FirebugReps.OBJECTBOX({"class": "qpDataNotCollectedBox ", onclick:"$onCollectOnRerun"},
+    tag: FirebugReps.OBJECTBOX({"class": "qpDataNotCollectedBox ", onclick:"$onCollectOnRerun", _repObject: "$object"},
             SPAN({"class": "qpDataNotCollected", role: "presentation"},"rerun")
             ),
 
     onCollectOnRerun:function(event)
     {
         var row = getAncestorByClass(event.target, "memberRow");
-        FBTrace.sysout("Rerun to collect data requested for "+row.textContent, event);
+        var panel = Firebug.getElementPanel(row);
+        var path = panel.getPropertyPath(row);
+        var tracepoint = panel.mainPanel.location;
+        FBTrace.sysout("onCollectOnRerun "+path.join('')+" row "+row+" location: "+tracepoint, tracepoint);
+
+
+        try
+        {
+            tracepoint.querypoint.addQueryWatch(path.join(''));
+            QPFBUG.Classes.Manager.getInstance().replay(panel.mainPanel.context);
+            FBTrace.sysout("Rerun to collect data requested for "+row.textContent+" set depth "+QPFBUG.Conf.DATA_COLLECTION_DEPTH, event);
+        }
+        catch(exc)
+        {
+            FBTrace.sysout("rerun FAILS "+exc, exc);
+        }
     },
 
     // * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * * *

### 2010-11-16 qp-fbug/qp-fbug-0.1/src/chrome/content/ui/uiutils.js
guard tracing one time

@@ -34,7 +34,8 @@ with (Lang){
             {
             for(var i = 0; i < tps.length; i++)
             {
-                FBTrace.sysout("qp.eachTracepoint "+i+"/"+tps.length, tps[i]);
+                if (FBTrace.DBG_QUERYPOINT)
+                    FBTrace.sysout("qp.eachTracepoint "+i+"/"+tps.length, tps[i]);
 
                 fnOfTracepoint(tps[i]);
             }
@@ -60,11 +61,11 @@ with (Lang){
          {
             return tracepoint.querypoint;
          },
-         
+
          getTraceData: function(tracepoint)
          {
-        	 // Salman, need help here.
-        	 return {expr: "traceDataExpr", traceData: {value: "traceDataValue", otherProps: "here"} };
+             // Salman, need help here.
+             return {expr: "traceDataExpr", traceData: {value: "traceDataValue", otherProps: "here"} };
          },
      };
 }}

### 2010-11-16 qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js
output timing info in fbtrace

@@ -20,10 +20,17 @@ Firebug.Querypoint.QPModule = extend(Firebug.ActivableModule,
 {
     dispatchName: "qpModule",
 
+    initialize: function()
+    {
+        Firebug.Debugger.addListener(this);
+        FBTrace.sysout("Querypoint.QPModule.initialize ",Firebug.Debugger);
+    },
+
     initContext: function(context, persistedState)
     {
         context.Firebug = Firebug; // I guess.
-        Firebug.Debugger.addListener(this);
+        Firebug.Querypoint.timestamp = new Date().getTime();
+        FBTrace.sysout("Querypoint initContext "+context.getName());
     },
 
     onQuerypointHit: function(context)
@@ -35,8 +42,11 @@ Firebug.Querypoint.QPModule = extend(Firebug.ActivableModule,
 
     onStartDebugging: function(context)
     {
-        if (FBTrace.DBG_QUERYPOINT)
-            FBTrace.sysout("onStartDebugging tracepoints.show "+context.qpfbug.newResults);
+        //if (FBTrace.DBG_QUERYPOINT)
+        var now = new Date().getTime();
+        var delta = now - Firebug.Querypoint.timestamp;
+        Firebug.Querypoint.timestamp = now;
+            FBTrace.sysout("Querypoint user start debugging, new QP results: "+context.qpfbug.newResults+" time "+delta);
         if (context.qpfbug.newResults)
         {
 //            context.qpfbug.inSession = true;  // I don't know how we will get out of this state
@@ -827,7 +837,6 @@ Firebug.Querypoint.TraceDataNotCollectedRep = domplate(Firebug.Rep,
         var path = panel.getPropertyPath(row);
         var tracepoint = panel.mainPanel.location;
         FBTrace.sysout("onCollectOnRerun "+path.join('')+" row "+row+" location: "+tracepoint, tracepoint);
-
 
         try
         {

### 2010-11-17 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js
querypoints panel color changes.

@@ -471,15 +471,15 @@ Firebug.Querypoint.TraceDataPanel.prototype = extend(Firebug.WatchPanel.prototyp
         if (tracepoint.getQueryType() === "lastChange")
         {
             var diff = new Firebug.Querypoint.TraceDataDiff(tracepoint.oldValue, tracepoint.newValue);
-            var lastChangeExpr = tracepoint.querypoint.refQueryexpr.expr;
-            this.addMember({expr: lastChangeExpr, value: diff }, "query", traceMembers, lastChangeExpr, diff, 0 );
+            var lastChangeExpr = "["+tracepoint.querypoint.refQueryexpr.expr+"]";
+            this.addMember({expr: lastChangeExpr, value: diff }, "result", traceMembers, lastChangeExpr, diff, 0 );
         }
 
         if (FBTrace.DBG_QUERYPOINT)
             FBTrace.sysout("TraceDataPanel.rebuild traceWatches: "+tracepoint.traceWatches, tracepoint.traceWatches);
 
         // At QP we show some data
-        this.addMember({expr: "this", value: tracepoint.traceFrame.traceThis }, "scopes", traceMembers, "this", tracepoint.traceFrame.traceThis, 0 );
+        this.addMember({expr: "this", value: tracepoint.traceFrame.traceThis }, "user", traceMembers, "this", tracepoint.traceFrame.traceThis, 0 );
 
         var scope = tracepoint.traceFrame.traceScope;
         var scopeMembers = this.getMembers(scope.variableValues, 0, this.context);

### 2010-11-18 papers/pldi2011/sigplanconf-template.tex

@@
-\documentclass[preprint]{sigplanconf}
+\documentclass{sigplanconf} %[preprint]
 
@@
 
-\authorinfo{Salman Mirghasemi}
-           {Ecole Polytechnique F\'ed\'erale de Lausanne}
-           {salman.mirghasemi@epfl.ch}
-
-\authorinfo{John J. Barton}
-           {IBM Research - Almaden}
-           {johnjbarton@johnjbarton.com}
-
-\authorinfo{Claude Petitpierre}
-           {Ecole Polytechnique F\'ed\'erale de Lausanne}
-           {claude.petitpierre@epfl.ch}
+%\authorinfo{Salman Mirghasemi}
+%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+%           {salman.mirghasemi@epfl.ch}
+
+%\authorinfo{John J. Barton}
+%           {IBM Research - Almaden}
+%           {johnjbarton@johnjbarton.com}
+
+%\authorinfo{Claude Petitpierre}
+%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+%           {claude.petitpierre@epfl.ch}
+
+\authorinfo{First Author}
+           {AAA university}
+           {a@a.com}
+
+\authorinfo{Second Author}
+           {BBB company}
+           {b@b.com}
+
+\authorinfo{Third Author}
+           {CCC university}
+           {c@c.com}
 
@@
 breakpoint- or log- based debuggers demands persistence and
-significant experience with the application being debugged. We propose
-a new approach, an algorithm called \textit{lastChange}, which automatically
-locates the last point that a value was changed and related
+significant experience with the application being debugged. We propose a new 
+practical technique called \textit{lastChange}, which automatically
+locates the last point that a variable or an object property  was changed and provides related
 information such as the call stack and program state. Starting from a
@@
 with the expressive power of log-based query debugging.  Contrary to
-other replay-based algorithms which require exactly the same
-re-executions, \textit{lastChange} only requires \textit{bug
+other replay-based approaches which require exactly the same
+re-executions (fully deterministic), \textit{lastChange} only requires \textit{bug 
 reproducibility}, a test case is available which reproduces the bug.
 
+%TODO these paragraph should contain the summary of evaluation results.
 As a proof of concept, we developed \textit{Querypoint}, a prototype
@@
 According to \cite{LaToza}, developers spend about fifty percent of
-their time debugging. To fix a bug, developers typically reproduce and
-monitor the buggy execution several times to understand the program's
-unexpected behavior. Trial and error, guess-work, and analyzing large
-and complicated data make debugging difficult and time-consuming. Any
-enhancement to debugging techniques and tools can save developers'
-time, reduce development costs and improve programs' quality.
+their time debugging. Trial and error, guess-work, and analyzing large
+and complicated data make debugging difficult and time-consuming. To fix 
+a bug, developers typically reproduce and monitor the buggy execution several 
+times to understand the program's unexpected behavior. Therefore, any
+enhancement to debugging techniques and tools which automates or facilitates developers' actions
+on execution traces, can save developers' time, reduce development costs and improve programs' quality.
 
@@
 value. It uses program re-execution similar to the practice
-in using breakpoints and log statements.
-
-Imagine a program execution paused on a breakpoint and a developer
-suspicious about the value of an object property or a variable. The
+in using breakpoints and log statements. Imagine a program execution 
+paused on a breakpoint and the developer is
+suspicious about the value of a variable or an object property. The
 developer queries \textit{lastChange} on the value. The debugger
@@
 
-Our contribution in this paper is the algorithm \textit{lastChange},
+Our contribution in this paper is the technique \textit{lastChange},
 which locates the last place a value has changed, gathers other values
 from that execution point, and allows \textit{lastChange} operations
-from that point. The algorithm builds on existing breakpoint debugger
-technology. We demonstrate the feasibility of the algorithm with
+from that point. The technique builds on existing breakpoint debugger
+technology. We demonstrate the feasibility of the approach with
 \textit{Querypoint}, an implementation extending the Firebug
@@
 prototype implementation. We discuss the effect of non-determinism on
-the \textit{lastChange} algorithm. Section 6 contains an evaluation of
-\text{lastChange} functionality.
+the \textit{lastChange} results in section 5. %TODO update it according to new
+Section 6 contains an evaluation of\text{lastChange} functionality.
 
@@
 
+\section{Evaluation}
+%To verify that lastChange can be effective we performed a small study of developers debugging with and without lastChange.
+Our goal is small, only to show that one aspect of debugging, the determination the causes of incorrect values, can be improved.
+The broader impact of lastChange on the total debugging process will have to wait for implementation of the functions described in section XX directly in a Web browser JavaScript engine.
+
+%Four experienced Javascript developers used the Firebug debugger on four small programs we provided.
+Each developer first used breakpoint debugging on two programs.
+Then we had them read sections YY - ZZ of this paper.
+Finally each developer applied the Querypoint prototype to two more programs.
+The programs were preselected so each developer saw them in a different order.
+Figure AA compares the human and computing times for these tests.
+[results]
+
+% Of course these programs were designed to highlight lastChange and all kinds of debugging issues have been hidden by the design of our tests.
+Our results show that when a defect relates to incorrect values and a developer recognizes that this, then the operational mechanics of lastChange lead to the defect much more quickly than breakpoints.
+
 \section{Discussion}

### 2010-11-18 papers/pldi2011/sigplanconf-template.tex

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+\usepackage[tight,normalsize]{subfigure}
+%\usepackage{caption}
 \usepackage{algorithmic}
@@
 on line 22. Once the button is clicked, execution is paused at line
-22. Figure ~\ref{fig:example1} shows the Firebug debugger while the
+22. Figure~\ref{fig:example1} shows the Firebug debugger while the
 execution is paused. Firebug has several panels (e.g., HTML, CSS,
@@
 \texttt{myObject.myProperty} in the Watch panel, the developer can run
-\textit{lastChange} command (Figure ~\ref{fig:example2}). Debugger
+\textit{lastChange} command (Figure ~\ref{fig:example1}). Debugger
 re-executes the program and halts again at the breakpoint on line 22.
 However, it shows a new panel, called QP, centered on the source at line 29
-(Figure ~\ref{fig:example3}), the point of \textit{lastChange}.  To
+(Figure~\ref{fig:example3}), the point of \textit{lastChange}.  To
 the right, the TraceData panel shows values of properties of the
@@
 place \texttt{oldValue} is assigned to
-\texttt{myCondition.value} (Figure ~\ref{fig:example4}). Now it is
-clear that the bug occurs because \texttt{oldValue} is
-\texttt{undefined} once execution reaches line 25.
-
-As demonstrated in Figure ~\ref{fig:example-points}, the developer has
-examined three points of execution. The first point, the reproduction point,  was the breakpoint set by the developer.
-The second and third points preceded the reproduction point in execution sequence.
-All three points-the history
-of the search for the defect-are available through the debugger's
-interface. On the top of the left panel in Figure ~\ref{fig:example4}
-there is an opened list which shows all three examined points. The
-first one is the breakpoint on line 22, the second one is the point
-which is when \texttt{myObject.myProperty} changed before
-reaching the breakpoint and finally the last one is the point of
-execution in which \texttt{myCondition.value} gets the
-\texttt{undefined} value. Moreover, the source lines related to these
-points are tagged with red-cycle icons.
+\texttt{myCondition.value}. To examine \texttt{oldValue}
+ at this point, developer enters it to the watch box and after re-execution the value
+ is available. Now it is clear that the bug occurs because \texttt{oldValue} is
+\texttt{undefined} once execution reaches line 25 (Figure~\ref{fig:example4}).
 
@@
 
-\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:example2}. The Script
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
   panel is selected; it gives access to
@@
   the paused
-  point. ]{\label{fig:example1}\includegraphics[width=1.0\textwidth,
-    height=.17\textheight]{1-bp22.jpg}}
-
-\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
-on the
-  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
-    height=.17\textheight]{2-bp22-lastChange.jpg}}
+  point.
+Developer can query \textit{lastChange} on a \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
+  ]{1-bp22.jpg}}
+
+%\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
+%on the
+%  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
+%    height=.17\textheight]{2-bp22-lastChange.jpg}}
 
@@
   TraceData, shows the collected data at the
-  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,
-    height=.21\textheight]{3-lastChange.jpg}}
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
+  ]{3-lastChange.jpg}}
 
 \subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. The opened list on the top of the left
-  panel shows the visited execution points. Clicking on each point in
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can
+  enter the expression in the watch box and after re-execution the result is available.
+  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
   the list shows the corresponding code and
-  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth,
-    height=.23\textheight]{4-lastChange2.jpg}}
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
+    ]{4-lastChange2.jpg}}
 
@@
 \end{figure}
+
+As demonstrated in Figure ~\ref{fig:example-points}, the developer has
+examined three points of execution. The first point, the reproduction point,  was the breakpoint set by the developer.
+The second and third points preceded the reproduction point in execution sequence.
+All three points-the history
+of the search for the defect-are available through the debugger's
+interface. On the top of the left panel in Figure~\ref{fig:example4}
+there is an opened list which shows all three examined points. The
+first one is the breakpoint on line 22, the second one is the point
+which is when \texttt{myObject.myProperty} changed before
+reaching the breakpoint and finally the last one is the point of
+execution in which \texttt{myCondition.value} gets the
+\texttt{undefined} value. Moreover, the source lines related to these
+points are marked with red-cycle icons.
 

### 2010-11-18 trunk/papers/pldi2011/sigplanconf-template.tex

@@
 
-\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
-           {Ecole Polytechnique F\'ed\'erale de Lausanne}
-           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}
-
-\authorinfo{John J. Barton}
-           {IBM Research - Almaden}
-           {johnjbarton@johnjbarton.com}
+%\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
+%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+%           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}
+
+%\authorinfo{Salman Mirghasemi}
+%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+%           {salman.mirghasemi@epfl.ch}
+
+%\authorinfo{John J. Barton}
+%           {IBM Research - Almaden}
+%           {johnjbarton@johnjbarton.com}
+
+%\authorinfo{Claude Petitpierre}
+%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+%           {claude.petitpierre@epfl.ch}
+
+\authorinfo{First Author}
+           {AAA university}
+           {a@a.com}
+
+\authorinfo{Second Author}
+           {BBB company}
+           {b@b.com}
+
+\authorinfo{Third Author}
+           {CCC university}
+           {c@c.com}
 
@@
 breakpoint- or log- based debuggers demands persistence and
-significant experience with the application being debugged. We propose
-a new approach, an algorithm called \textit{lastChange}, which automatically
-locates the last point that a value was changed and related
+significant experience with the application being debugged. We propose a new 
+practical technique called \textit{lastChange}, which automatically
+locates the last point that a variable or an object property was changed and provides related
 information such as the call stack and program state. Starting from a
@@
 string, the function is called whenever a property changes and its
-name matches the string For example, if the is 
+name matches the string. For example, if the string is 
 \texttt{foo} so changes to \texttt{bar.foo} or \texttt{baz.foo} would
@@
 \subsubsection{global and \texttt{with} scopes}
-Global scope is the the most outer scope in the scope chain and it is
+Global scope is the most outer scope in the scope chain and it is
 also referred to as the global object (the \texttt{window}
@@
 the block's first instruction program counter. Given this information, the debugger is
-able to recognize the code block once it is loaded.
+able to recognize the code block in loaded scripts or once it is loaded.
 Similar to \textit{lastChange} on object property, we define two basic operations: 
@@
 given a scope returns an integer as the scope's identifier. The second one, 
-given a callback function, a code block and a variable name-
-which is defined inside the block-, the function is called
+given a callback function, a code block and a variable name-which is defined inside the block, the function is called
 whenever the variable is changed. Figure ~\ref{fig:recursive} demonstrates a case in which the same syntactically variable
 \texttt{x} is changed several times but in different scopes due to the
-recursive calls. Without considering the scopes calling \textit{lastChange(x)}
-at point \texttt{C} in scope 1 will return point \texttt{B} which is a change of \texttt{x} in 
-scope 2 while the right answer is point \texttt{A}. To resolve this issue, an id
+recursive calls. Without considering the scopes the last change of x
+at point \texttt{C} in scope 1 is point \texttt{B} which is a change of \texttt{x} in 
+scope 2 while the right last change is point \texttt{A}. To resolve this issue, an id
 is assigned to the scope by \texttt{ScopeId()} operation and the scope id is also stored 
@@
 %\subsection{Reproduction point}
+
+\section{Evaluation}
+%To verify that lastChange can be effective we performed a small study of developers debugging with and without lastChange.
+Our goal is small, only to show that one aspect of debugging, the determination the causes of incorrect values, can be improved.
+The broader impact of lastChange on the total debugging process will have to wait for implementation of the functions described in section XX directly in a Web browser JavaScript engine.
+
+%Four experienced Javascript developers used the Firebug debugger on four small programs we provided.
+Each developer first used breakpoint debugging on two programs.
+Then we had them read sections YY - ZZ of this paper.
+Finally each developer applied the Querypoint prototype to two more programs.
+The programs were preselected so each developer saw them in a different order.
+Figure AA compares the human and computing times for these tests.
+[results]
+
+% Of course these programs were designed to highlight lastChange and all kinds of debugging issues have been hidden by the design of our tests.
+Our results show that when a defect relates to incorrect values and a developer recognizes that this, then the operational mechanics of lastChange lead to the defect much more quickly than breakpoints.
 

### 2010-11-19 papers/pldi2011/sigplanconf-template.tex

@@
 \subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
   enter the expression in the watch box and after re-execution the result is available.
@@
 field \texttt{false} for \texttt{\_objectId}, this property will not
-apear in \texttt{for(property in object)} loops and therfore has no
+apear in \texttt{for(property in object)} loops and therefore has no
 effect on the program execution. Note that \texttt{\_objectId} is
@@
 Throughout this section we implicitly assumed that the object will be created at 
-the same location in the next execution. So, what does happens if it
+the same location in the next execution. So, what does happen if it
 is not true? Well, once the execution reaches the reproduction point, it
@@
 \section{Reproducible Non-deterministic Execution}
-
-By construction \textit{lastChange} works whenever conventional
-breakpoint debugging works. By that we mean that, since we use
-conventional breakpoint debugging technology under the covers,
-\textit{lastChange} works whenever breakpoint debugging
-works. However, there are cases where breakpoint debugging fails but
-\textit{lastChange} works.  These are cases of \textit{reproducible
-  non-deterministic} execution.
-
-A bug is \textit{reproducible} for a developer when the developer can
+We claimed that the only prerequisite for \textit{lastChange} function is bug
+reproducibility. A bug is \textit{reproducible} for a developer when the developer can
 start from a determined initial state, operate on the program with a
@@
 the bug makes it very unlikely that the \textit{lastChange} will
-depend upon order of events during execution.
-
-Since \textit{lastChange} does not rely on determinism, some bugs that
-confound breakpoint debuggers will be easier to find with
-\textit{lastChange}.  Consider the example in 
-Figure ~\ref{fig:counter-example}. It shows a function which processes an
+depend upon order of events during execution. In this section we discuss issues regarding to non-determinism.
+
+\subsection{Pausing at \textit{lastChange} Result}
+A \textit{lastChange} result can be recognized early when it occurs if it can
+be defined by a conditional breakpoint. A proposal for the condition is the event index
+in the history of change events. This condition obviously works for deterministic 
+executions. Therefore, if developer specifies an execution determinitic, every lastChange
+will become pausable. Moroever, it works in a non-deterministic execution if non-determinism
+has no effect on the event index. If in several executions, the \textit{lastChange} result happens at
+the same index in the list of change events, it is very likely that in the next execution, the 
+same index be the result. Debugger can propose it as a pausable point to the developer or optimizes data
+collection by focusing on this point. The correctness of this guess can be verified at the reproduction
+point.
+
+There are cases where finding the appropriate condition requires developer's knowledge.
+Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
 array. The array contains numbers except one item which is
@@
 point which shows line 14. Although this point exists at every
-re-execution but it can not be identified by a conditional breakpoint.
+re-execution but it can not be identified by any condition excepting
+the value of item.
 
@@
 
-Thus in the case of a non-deterministic program, a \textit{lastChange}
-is not equivalent to any series of conventional watchpoints or
-breakpoints. The extra power of \textit{lastChange} derives from its
-analysis of the entire execution up to the reproduction point and its
-memory of previous work on the defect.  Each time we re-execute a
-non-deterministic program, the details of execution instruction order
-may change. For example, if we record the source code lines every time
+\subsection{\textit{lastChange} Result Consistency}
+Each time we re-execute a non-deterministic program, 
+the details of execution instruction order may change. 
+For example, if we record the source code lines every time
 a conventional watchpoint hits, the record may differ each time we
 re-execute. But \textit{lastChange} does not ask the developer to
-consider these single points.  Rather we analyze all of the
-watchpoints in an entire execution at the reproduction point where we
-know the defect has already occurred and only show the final result to
-the developer.
-
-Of course there can be cases where the defect is reproducible but the
+consider these single points. Rather it analyzes all of the
+change events in an entire execution at the reproduction point where the bug
+has already occurred and shows the final result to the developer.
+
+Of course there can be cases where the bug is reproducible but the
 value from \textit{lastChange} is not. As in conventional breakpoint
@@
 executions. Different values on different executions will signal that
-the execution is not deterministic. In future we hope to compare
-queries from successive executions as a tool for learning about
-non-deterministic executions.
+the execution is not deterministic. Consider the example in Figure~\ref{fig:nondeterministic-values}. 
+Assume that at the first exeuction, developers sees that \texttt{a} is \texttt{true} and asks
+for the \textit{lastChange} of \texttt{a} at breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
+and \texttt{b} is \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
+result shows line 10, which is a correct answer for this execution but not for the previous one.
+When user asks for the \textit{lastChange} on variable \texttt{a}, debugger stores \texttt{a} value and compares
+it to the \texttt{a} value in the next executions. So if this value is different, debuggers inform the developer
+that the \textit{lastChange} query is made on a different value. In cases that the value is not a primitive but an object,
+the properties of the object examined by the developer are stored and compared.
+
+\begin{figure}[htp]
+\begin{verbatim}
+10 a = false;
+11 b = false;
+...
+20 if ( random() ) { a = true; } else { b = true; }
+...
+30 if (a || b) { bug();  /* breakpoint */ }
+\end{verbatim}
+\caption{\textit{lastChange} on non-deterministic values.}
+\label{fig:nondeterministic-values}
+\end{figure}
 
@@
 
+%TODOWe have also developed a prototype implementation of the debugger control part of lastChange for Java.
+The main differences (one or two sentences).
+We will report on this implementation in a later publication
 \subsection{Developers need an operation like \protect\textit{lastChange} }

### 2010-11-19 papers/ecoop2011/ecoop2011-lastChange.tex

--- 2010-11-19 papers/pldi2011/sigplanconf-template.tex
@@
-\documentclass{sigplanconf} %[preprint]
-
-% The following \documentclass options may be useful:
+%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
 %
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
-
-\usepackage{amsmath}
+% This is the LaTeX source for the instructions to authors using
+% the LaTeX document class 'llncs.cls' for contributions to
+% the Lecture Notes in Computer Sciences series.
+% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
+%
+% It may be used as a template for your own input - copy it
+% to a new file with a new name and use it as the basis
+% for your article.
+%
+% NB: the document class 'llncs' has its own and detailed documentation, see
+% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[runningheads,a4paper]{llncs}
+
+\usepackage{amssymb}
+\setcounter{tocdepth}{3}
 \usepackage{graphicx}
-\usepackage[tight,normalsize]{subfigure}
-%\usepackage{caption}
+\usepackage{subfigure} %[tight,normalsize]
 \usepackage{algorithmic}
@@
 
+\usepackage{url}
+\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
+\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
+\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
+\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+\noindent\keywordname\enspace\ignorespaces#1}
+
 \begin{document}
 
-\conferenceinfo{PLDI'11}{June 4-8, San Jose, California.} 
-\copyrightyear{2011} 
-\copyrightdata{[to be supplied]}
-
-\titlebanner{preprint}        % These are ignored unless
-\preprintfooter{}   % 'preprint' option specified.
-
+\mainmatter  % start of an individual contribution
+
+% first the title is needed
 \title{Debugging by \textit{lastChange}}
-\subtitle{}
-
-%\authorinfo{Salman Mirghasemi\and Claude Petitpierre}
-%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
+
+% a short form should be given in case it is too long for the running head
+\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}
+
+% the name(s) of the author(s) follow(s) next
+%
+% NB: Chinese authors should write their first names(s) in front of
+% their surnames. This ensures that the names appear correctly in
+% the running heads and the author index.
+%
+
 %           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}
@@
 
-\authorinfo{First Author}
-           {AAA university}
-           {a@a.com}
-
-\authorinfo{Second Author}
-           {BBB company}
-           {b@b.com}
-
-\authorinfo{Third Author}
-           {CCC university}
-           {c@c.com}
-
+\author{Salman Mirghasemi\inst{1} \and John J. Barton\inst{2} \and Claude Petitpierre\inst{1}}
+
+%
+%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
+% (feature abused for this document to repeat the title also on left hand pages)
+
+% the affiliations are given next; don't give your e-mail address
+% unless you accept that it will be published
+\institute{Ecole Polytechnique F\'ed\'erale de Lausanne\\
+\path|{salman.mirghasemi,claude.petitpierre}@epfl.ch| \\
+IBM Research - Almaden \\
+\path|johnjbarton@johnjbarton.com|}
+
+%
+% NB: a more complex sample for affiliations and the mapping to the
+% corresponding authors can be found in the file "llncs.dem"
+% (search for the string "\mainmatter" where a contribution starts).
+% "llncs.dem" accompanies the document class "llncs.cls".
+%
+
+\toctitle{Lecture Notes in Computer Science}
+\tocauthor{Authors' Instructions}
 \maketitle
@@
 \begin{abstract}
-
 Developers often seek the origins of wrong values they see in their
@@
 
+\keywords{Debugging, Locating Defects, Querypoint, LastChange, Breakpoint,
+ Watchpoint, Logging}
 \end{abstract}
-
-\category{D.2.5}{Testing and Debugging}{Debugging aids}
-\category{D.2.6}{Programming Environments}{Integrated environments}
-
-\terms
-Algorithms, Human Factors, Languages
-
-\keywords
-LastChange, Locating Defects, Breakpoint, Watchpoint, Logging
 
@@
 prototype implementation. We discuss the effect of non-determinism on
-the \textit{lastChange} results in section 5. %TODO update it according to new
-Section 6 contains an evaluation of\text{lastChange} functionality.
+the \textit{lastChange} results in section 5.  %TODO update it according to new Section 6 contains an evaluation of\text{lastChange} functionality.
 
@@
 
-% We recommend abbrvnat bibliography style.
-
-\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
+\subsubsection*{Acknowledgments.} The heading should be treated as a
+subsubsection heading and should not be assigned a number.
 
 \begin{thebibliography}{16}
-\softraggedright
-
-\bibitem[Bond(2007)]{Bond}
+\bibitem{Bond}%[Bond(2007)]
 M.D. Bond, N. Nethercote, S.W. Kent, S.Z. Guyer, and K.S. McKinley. \newblock Tracking bad apples: reporting the origin of null and undefined value errors.
@@
 
-\bibitem[Bond(2010)]{Bond2}
+\bibitem{Bond2}%[Bond(2010)]
 M.D. Bond, G.Z. Baker, S.Z. Guyer, and Z. Samuel. \newblock Breadcrumbs: efficient context sensitivity for dynamic bug detection analyses.
@@
 
-\bibitem[Boothe(2000)]{Boothe}
+\bibitem{Boothe}%[Boothe(2000)]
 B. Boothe. \newblock Efficient algorithms for bidirectional debugging.
@@
 
-\bibitem[Czyz(2007)]{Czyz}
+\bibitem{Czyz}%[Czyz(2007)]
 J.K. Czyz, and B. Jayaraman. \newblock Declarative and visual debugging in Eclipse.
@@
 
-\bibitem[Firebug(2010)]{Firebug}
+\bibitem{Firebug}%[Firebug(2010)]
 Firebug. \newblock http://getfirebug.com.
 
-\bibitem[Firefox(2010)]{Firefox}
+\bibitem{Firefox}%[Firefox(2010)]
 Firefox. \newblock http://www.mozilla.com.
 
-\bibitem[Hofer(2006)]{Hofer}
+\bibitem{Hofer}%[Hofer(2006)]
 C. Hofer, M. Denker, and S. Ducasse. \newblock Implementing a backward-in-time debugger.
@@
 
-\bibitem[Ko(2008)]{Ko}
+\bibitem{Ko}%[Ko(2008)]
 A.J. Ko, and B.A. Myers. \newblock Debugging reinvented: asking and answering why and why not questions about program behavior.
@@
 
-\bibitem[LaToza(2006)]{LaToza}
+\bibitem{LaToza}%[LaToza(2006)]
 T.D. LaToza, G. Venolia, and R. DeLine. \newblock Maintaining mental models: a study of developer work habits
@@
 
-\bibitem[Lewis(2003)]{Lewis}
+\bibitem{Lewis}%[Lewis(2003)]
 B. Lewis, and M. Ducasse. \newblock Using events to debug Java programs backwards in time.
@@
 
-\bibitem[Lienhard(2008)]{Lienhard}
+\bibitem{Lienhard}%[Lienhard(2008)]
 A. Lienhard, T. G\^{\i}rba, and O. Nierstrasz. \newblock Practical Object-Oriented Back-in-Time Debugging.
@@
 
-\bibitem[Maruyama(2003)]{Maruyama}
+\bibitem{Maruyama}%[Maruyama(2003)]
 K. Maruyama, and T. Kazutaka. \newblock Debugging with Reverse Watchpoint.
@@
 
-\bibitem[JSD(2010)]{JSD}
+\bibitem{JSD}%[JSD(2010)]
 Mozila JavaScript Debugging Interface. \newblock http://www.mozilla.org/js/jsd.
 
-\bibitem[Pothier(2007)]{Pothier}
+\bibitem{Pothier}%[Pothier(2007)]
 G. Pothier, \'{E}. Tanter, and J. Piquer. \newblock Scalable omniscient debugging.

### 2010-11-22 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/scripts.js
queryexpr has a type field. querydata is replaced by queryexpr .

@@ -47,7 +47,7 @@ loadScript("resource://qpfbug/util/monitor.js");
 loadScript("resource://qpfbug/concept/debugmodel.js");
 loadScript("resource://qpfbug/concept/querypoint.js");
 loadScript("resource://qpfbug/concept/queryexpr.js");
-loadScript("resource://qpfbug/concept/querydata.js");
+//loadScript("resource://qpfbug/concept/querydata.js");
 loadScript("resource://qpfbug/concept/trace.js");
 loadScript("resource://qpfbug/concept/tracepoint.js");
 loadScript("resource://qpfbug/concept/tracedata.js");

### 2010-11-22 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugmodel.js
queryexpr has a type field. querydata is replaced by queryexpr .

@@ -60,8 +60,8 @@ with (Lang){
                                                     null, null, null);
 
                     // updates querypoint queryDataList
-                    type = QueryData.TYPES.PARENT_CREATIONDATA | QueryData.TYPES.PARENT_VALUE;
-                    queryData = new QueryData(type, 0, ".owner" );
+                    var type = 0;
+                    var queryData = new QueryExpr(0, ".owner" );
                     querypoint.addQueryData(queryData)
 
                     // add trace point to the list
@@ -70,8 +70,8 @@ with (Lang){
 
                     // updates refQuerypoint queryDataList
                     refQuerypoint.addDependentQuerypoint(querypoint);
-                    var type = QueryData.TYPES.PARENT_CREATIONDATA | QueryData.TYPES.PARENT_VALUE;
-                    var queryData = new QueryData(type, valueFrameNo, valueRef);
+
+                    queryData = new QueryExpr(valueFrameNo, valueRef);
                     refQuerypoint.addQueryData(queryData);
 
                     return querypoint;

### 2010-11-22 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/querydata.js

@@ -8,36 +8,20 @@ with (Lang){
 
     //------------------------------- QueryData ----------------------------------
     // This object specifies data should be collected for an object at a point.
+    // @Deprecated
     __owner.QueryData =
         function(){
-            var constructor = function(type, frameNo, expr){
+            var constructor = function(queryExpr){
 
-                this.type = type;
-                //frame number
-                this.frameNo = frameNo;
-                //reference to object or value (in general it can be any expression that can be evaluated)
-                this.expr = expr;
-
-                this.propertyName = expr.substring(expr.lastIndexOf(".")+1, expr.length);
-                if (expr.lastIndexOf(".") >= 0)
-                    this.parentRef = expr.substring(0, expr.lastIndexOf("."));
+                this.queryExpr = queryExpr;
             };
 
             constructor.prototype = {
                 toString: function()
                 {
-            		return "[QueryData "+this.propertyName+"]";
+            		return "[QueryData]";
                 }
             };
-
-            constructor.TYPES = {
-                PARENT_NOTHING: 0,
-                PARENT_CREATIONDATA: 1,
-                PARENT_VALUE: 2,
-                PARENT_CREATIONDATA: 4,
-                OBJECT_VALUE: 8,
-                ALL:127,
-            }
 
             return constructor;
         }();

### 2010-11-22 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/queryexpr.js

@@ -10,7 +10,7 @@ with (Lang){
     // This object uniquely specifies an object at a point.
     __owner.QueryExpr =
         function(){
-            var constructor = function(frameNo, expr){
+            var constructor = function(frameNo, expr){ //TODO for "special" cases frameNo is not required
                 //frame number : the frame, ref should be evaluated in. Frame 0 is the top frame in the stack.
                 this.frameNo = frameNo;
 
@@ -19,9 +19,17 @@ with (Lang){
                 this.expr = expr;
 
                 // if these are derived properties we should compute them lazy
-                this.propertyName = expr.substring(expr.lastIndexOf(".")+1, expr.length);
-                if (expr.lastIndexOf(".") >= 0)
+                if (expr.indexOf(".")=== 0){ //starts with dot
+                    this.type = QueryExpr.TYPES.SPECIAL;
+                    this.specialRef = expr.substring(1);
+                }else if (expr.lastIndexOf(".") >= 0){
+                    this.type = QueryExpr.TYPES.PROPERTY;
+                    this.propertyName = expr.substring(expr.lastIndexOf(".")+1, expr.length);
                     this.parentRef = expr.substring(0, expr.lastIndexOf("."));
+                }else{
+                    this.type = QueryExpr.TYPES.VARIABLE;
+                    this.variableName = expr;
+                }
 
             };
 
@@ -29,7 +37,25 @@ with (Lang){
                 toString: function()
                 {
                     return "[QueryExpr]";
-                }
+                },
+
+                isSpecial: function(){
+                    return this.type === QueryExpr.TYPES.SPECIAL;
+                },
+
+                isProperty: function(){
+                    return this.type === QueryExpr.TYPES.PROPERTY;
+                },
+
+                isVariable: function(){
+                    return this.type === QueryExpr.TYPES.VARIABLE;
+                },
+            };
+
+            constructor.TYPES = {
+                SPECIAL: 1,
+                PROPERTY: 2,
+                VARIABLE: 3,
             };
 
             return constructor;

### 2010-11-22 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/trace.js
traceObject is added.

@@ -23,7 +23,7 @@ with (Lang){
 
                 addLastChangeTracepoint: function(querypoint, context, eventId, frame, parent, oldValue, newValue, isObjectCreation){
 
-                    var tracepoint = this.addTracepoint(querypoint, context, eventId, frame, oldValue, newValue);
+                    var tracepoint = this.addTracepoint(querypoint, context, eventId, frame, parent, oldValue, newValue);
 
                     if (isObjectCreation){ //correct last frame line number
                         //todo change it  perhaps you can keep the creation url, line number in querypoint as a traceResult summary itself
@@ -46,29 +46,6 @@ with (Lang){
                         }
                     }
 
-
-                    //add .owner trace object
-                    var queryData;
-                    for (var i=0 ; i<querypoint.queryDataList.length ; i++){
-                        if (querypoint.queryDataList[i].expr == ".owner"){
-                            queryData = querypoint.queryDataList[i];
-                            break;
-                        }
-                    }
-
-                    var parentJSDIValue = QPFBUG.fbs.getJSD().wrapValue(parent);
-                    var traceData = new TraceData(queryData, parent, oldValue);
-
-                    var parentJSDIObject = parentJSDIValue.objectValue;
-                    if (parentJSDIObject)
-                    {
-                        traceData.parentCreatorURL = parentJSDIObject.creatorURL;
-                        traceData.parentCreatorLine = parentJSDIObject.creatorLine;
-                        traceData.parentConstructorURL = parentJSDIObject.constructorURL;
-                        traceData.parentConstructorLine = parentJSDIObject.constructorLine;
-                    }
-
-                    tracepoint.addTraceData(traceData);
                     trace("LastChange Tracepoint", tracepoint);
                     return tracepoint;
                 },
@@ -79,7 +56,7 @@ with (Lang){
                     return tracepoint;
                 },
 
-                addTracepoint: function(querypoint, context, eventId, frame, oldValue, newValue)
+                addTracepoint: function(querypoint, context, eventId, frame, parent, oldValue, newValue)
                 {
                     var dataCollectionDepth = QPFBUG.Conf.DATA_COLLECTION_DEPTH;
                     var querypointId = querypoint.id;
@@ -98,58 +75,61 @@ with (Lang){
                     for (var i=0 ; i<querypoint.queryDataList.length ; i++)
                     {
                         var queryData = querypoint.queryDataList[i];
-
-                        //todo find the right frame based on queryData.frameNo
[…]

### 2010-11-22 qp-fbug/qp-fbug-0.1/src/chrome/content/di/debugservice.js

@@ -347,7 +347,7 @@ with (Lang){
             onObjectCreation: function(eventRequest, object, frame, type, rv){
                 QPFBUG.monitor.ds_objectCreation++;
 
-                var objectId = object["___qpfbug_objectId___"];
+                var objectId = getObjectId(object);
                 //JSD doesn't give us txhe watch call back then we need to keep it here.
 
                 var watchEventRequests = object["___qpfbug_watchRequests___"]; // list of watchEventRequests

### 2010-11-22 qp-fbug/qp-fbug-0.1/src/chrome/content/util/lang.js

@@ -182,6 +182,20 @@ with (QPFBUG.Classes){
             return object;
         },
 
+        getObjectId: function(object){
+            var id = object["___qpfbug_objectId___"];
+            if (!id){
+                id = DebugService.getInstance().getNextJSObjectId();
+                object["___qpfbug_objectId___"] = id;
+            }
+            return id;
+
+            // Code for Gecko 2 (fireforx 4)
+            //Object.defineProperty(refValue, "__QPFBUG_ID", { value: objectId });
+            // code for firefox 3.5+
+            //refValue.__defineGetter__("__QPFBUG_ID", function(){return objectId;})
+        },
+
         wait: function(millis)
         {
             var time = Lang.currentTimeMillis();

### 2010-11-22 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/querypoint.js
traceObject is added.

@@ -29,8 +29,8 @@ with (Lang){
                 this.hitCount = hitCount;
 
                 //obj should be traced at this point
-                this.queryDataList = [];
-                this.queryWatchList = [];  // a list of watch expressions
+                this.queryDataList = [];   // the list of query expressions (QueryExpr) 
+                this.queryWatchList = [];  // the list of watch expressions
             };
 
             constructor.prototype = {

### 2010-11-22 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/tracedata.js

@@ -12,14 +12,16 @@ with (Lang){
 
     __owner.TraceData =
         function(){
-            var constructor = function(queryData, parentValue, value){
+            var constructor = function(queryData, parentTraceObject, value){
                 this.queryData = queryData;
-                this.parentValue = parentValue ;
+
+                this.parentTraceObject = parentTraceObject;
                 this.value = value;
-                this.parentCreatorURL = null;
-                this.parentCreatorLine = 0;
-                this.parentConstructorURL = null;
-                this.parentConstructorLine = 0;
+
+//                this.scopeType;
+
+
+                //scopeType
             };
 
             constructor.prototype = {
@@ -27,7 +29,10 @@ with (Lang){
                 {
                     return "[TraceData]";
                 }
+
+
             };
+
 
             return constructor;
         }();

### 2010-11-22 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/traceobject.js

@@ -1,0 +1,35 @@
+var EXPORTED_SYMBOLS = ["loadModule"];
+loadModule = function(QPFBUG)
+{
+
+with (QPFBUG.Classes){
+with (Lang){
+
+    var __owner = QPFBUG.Classes;
+
+    //------------------------------- TraceObject ----------------------------------
+
+    __owner.TraceObject =
+        function(){
+            var constructor = function(){
+                this.id = 0;
+                this.creatorURL = null;
+                this.creatorLine = 0;
+                this.constructorURL = null;
+                this.constructorLine = 0;
+            };
+
+            constructor.prototype = {
+                toString: function()
+                {
+                    return "[TraceObject]";
+                }
+
+            };
+
+            return constructor;
+        }();
+
+}}
+
+};

### 2010-11-22 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/core/manager.js

@@ -134,12 +134,12 @@ with (Lang){
                                      );
 
                         if (traceData){
-                            var url = traceData.parentCreatorURL;
-                            var lineNo = traceData.parentCreatorLine;
+                            var url = traceData.parentTraceObject.creatorURL;
+                            var lineNo = traceData.parentTraceObject.creatorLine;
 
                             if (!url){
-                                url = traceData.parentConstructorURL;
-                                lineNo = traceData.parentConstructorLine;
+                                url = traceData.parentTraceObject.constructorURL;
+                                lineNo = traceData.parentTraceObject.constructorLine;
                             }
                             if (url){    //todo
                                 url = normalizeURL(url);

### 2010-11-22 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/executionmonitor.js

@@ -98,17 +98,9 @@ with (Lang){
                         this.monitorRefValues[i] = refValue;
                         if (typeof(refValue) == "object")
                         {
-                            var objectId = refValue["___qpfbug_objectId___"];
-                            if (!objectId){ //no id for this object
-                                objectId = DebugService.getInstance().getNextJSObjectId();
-                                // Code for Gecko 2 (fireforx 4)
-                                //Object.defineProperty(refValue, "__QPFBUG_ID", { value: objectId });
-                                // code for firefox 3.5+
-                                //refValue.__defineGetter__("__QPFBUG_ID", function(){return objectId;})
-                                this.monitorRefGotNewValue[i] = true;
-                                refValue["___qpfbug_objectId___"] = objectId;
-                                trace(monitorRef + " with id '" + objectId + "' was created.");
-                            }
+                            var objectId = getObjectId(refValue);
+                            this.monitorRefGotNewValue[i] = true;
+                            trace(monitorRef + " with id '" + objectId + "' was created.");
                             this.callBack(this.eventRequest, refValue, frame, type, rv);
                         }
                     }

### 2010-11-22 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/scripts.js

@@ -51,6 +51,7 @@ loadScript("resource://qpfbug/concept/queryexpr.js");
 loadScript("resource://qpfbug/concept/trace.js");
 loadScript("resource://qpfbug/concept/tracepoint.js");
 loadScript("resource://qpfbug/concept/tracedata.js");
+loadScript("resource://qpfbug/concept/traceobject.js");
 loadScript("resource://qpfbug/concept/tracescope.js");
 loadScript("resource://qpfbug/concept/traceframe.js");
 loadScript("resource://qpfbug/concept/debugsession.js");

### 2010-11-23 papers/ecoop2011/ecoop2011-lastChange.tex
edit section 5 to reorder subsections and change intro

@@
 the execution can change each time we re-execute the buggy program,
-but the buggy result is the same.  The reproducibility of the bug
+but the buggy result is the same.  All modern debuggers in wide use that we know 
+about rely on reproducible but non-deterministic execution for simple practical reasons: 
+developers must reproduce a bug to study it and modern execution environments 
+are not deterministic.
+
+ In this section we discuss non-determinism and \textit{lastChange}. However we want 
+to emphasize that when developers have to think about non-determistic execution 
+it usually means that bugs are not reproducible. 
+The reproducibility of the bug
 means that the defect is very unlikely to depend on the order of
-events during the execution. When the developer selects a value and
+events during the execution. Conversely, if the defect depends on order of execution, 
+it will likely fail to reproduce on every execution. By relying on reproducibility but 
+not requiring deterministic execution, \textit{lastChange} covers the common case 
+developers focus on while not adding addition complexity to the implementation.
+
+\subsection{\textit{lastChange} Result Consistency}
+Each time we re-execute a non-deterministic program, 
+the details of execution instruction order may change. 
+For example, if we record the source code lines every time
+a conventional watchpoint hits, the record may differ each time we
+re-execute. But \textit{lastChange} does not ask the developer to
+consider these single points. Rather it analyzes all of the
+change events in an entire execution at the reproduction point where the bug
+has already occurred and shows the final result to the developer. 
+Neither the data gathering nor the analysis require deterministic execution.
+
+When the developer selects a value and
 asks for \textit{lastChange}, the developer is expressing the hypothesis that
-the value is related to the defect. Therefore the reproducibility of
+the value is related to the defect. Since the defect does not depend on
+ exeuction order, the reproducibility of
 the bug makes it very unlikely that the \textit{lastChange} will
-depend upon order of events during execution. In this section we discuss issues regarding to non-determinism.
+depend upon order of events during execution.
+Of course there can be rare cases where the bug is reproducible but the
+value from \textit{lastChange} is not. As in conventional breakpoint
+debugging, we can only determine this empirically, by observing
+multiple executions with different values. Unlike conventional
+breakpoint debugging, implementations of \textit{lastChange} readily
+help in detecting such cases: as we work back through a series of
+\textit{lastChange} requests we can compare values with previous
+executions. Different values on different executions will signal that
+the execution is not deterministic.
+
+Consider the example in Figure~\ref{fig:nondeterministic-values}. 
+Assume that at the first exeuction, developers sees that \texttt{a} is \texttt{true} and asks
+for the \textit{lastChange} of \texttt{a} at breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
+and \texttt{b} is \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
+result shows line 10, which is a correct answer for this execution but not for the previous one.
+When user asks for the \textit{lastChange} on variable \texttt{a}, debugger stores \texttt{a} value and compares
+it to the \texttt{a} value in the next executions. So if this value is different, debuggers inform the developer
+that the \textit{lastChange} query is made on a different value. In cases that the value is not a primitive but an object,
+the properties of the object examined by the developer are stored and compared.
+
+\begin{figure}[htp]
+\begin{verbatim}
+10 a = false;
+11 b = false;
+...
+20 if ( random() ) { a = true; } else { b = true; }
+...
+30 if (a || b) { bug();  /* breakpoint */ }
+\end{verbatim}
+\caption{\textit{lastChange} on non-deterministic values.}
+\label{fig:nondeterministic-values}
+\end{figure}
 
@@
 \label{fig:counter-example}
-\end{figure}
-
-\subsection{\textit{lastChange} Result Consistency}
-Each time we re-execute a non-deterministic program, 
-the details of execution instruction order may change. 
-For example, if we record the source code lines every time
-a conventional watchpoint hits, the record may differ each time we
-re-execute. But \textit{lastChange} does not ask the developer to
-consider these single points. Rather it analyzes all of the
-change events in an entire execution at the reproduction point where the bug
-has already occurred and shows the final result to the developer.
-
-Of course there can be cases where the bug is reproducible but the
-value from \textit{lastChange} is not. As in conventional breakpoint
-debugging, we can only determine this empirically, by observing
-multiple executions with different values. Unlike conventional
-breakpoint debugging, implementations of \textit{lastChange} readily
-help in detecting such cases: as we work back through a series of
-\textit{lastChange} requests we can compare values with previous
-executions. Different values on different executions will signal that
-the execution is not deterministic. Consider the example in Figure~\ref{fig:nondeterministic-values}. 
-Assume that at the first exeuction, developers sees that \texttt{a} is \texttt{true} and asks
-for the \textit{lastChange} of \texttt{a} at breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
-and \texttt{b} is \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
-result shows line 10, which is a correct answer for this execution but not for the previous one.
-When user asks for the \textit{lastChange} on variable \texttt{a}, debugger stores \texttt{a} value and compares
-it to the \texttt{a} value in the next executions. So if this value is different, debuggers inform the developer
-that the \textit{lastChange} query is made on a different value. In cases that the value is not a primitive but an object,
-the properties of the object examined by the developer are stored and compared.
-
-\begin{figure}[htp]
-\begin{verbatim}
-10 a = false;
-11 b = false;
-...
-20 if ( random() ) { a = true; } else { b = true; }
-...
-30 if (a || b) { bug();  /* breakpoint */ }
-\end{verbatim}
-\caption{\textit{lastChange} on non-deterministic values.}
-\label{fig:nondeterministic-values}
 \end{figure}

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/queryexpr.js
lastChange works on "global window" and "with" scopes variables.

@@ -22,13 +22,13 @@ with (Lang){
                 if (expr.indexOf(".")=== 0){ //starts with dot
                     this.type = QueryExpr.TYPES.SPECIAL;
                     this.specialRef = expr.substring(1);
-                }else if (expr.lastIndexOf(".") >= 0){
+                }else if (expr.lastIndexOf(".") > 0){
                     this.type = QueryExpr.TYPES.PROPERTY;
                     this.propertyName = expr.substring(expr.lastIndexOf(".")+1, expr.length);
                     this.parentRef = expr.substring(0, expr.lastIndexOf("."));
                 }else{
                     this.type = QueryExpr.TYPES.VARIABLE;
-                    this.variableName = expr;
+                    this.propertyName = this.variableName = expr; //todo you can also remove variableName
                 }
 
             };

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/querypoint.js

@@ -10,7 +10,7 @@ with (Lang){
     // trace point is kept in debug model.
     __owner.Querypoint =
         function(){
-            var constructor = function(id, queryType, refQuerypoint, refQueryexpr, url, lineNo, hitCount){
+            var constructor = function(id, queryType, refQuerypoint, refQueryExpr, url, lineNo, hitCount){
                 this.id = id;
                 this.queryType = queryType;
 
@@ -20,7 +20,7 @@ with (Lang){
 
                 // lastChange
                 // what we are looking for its last change
-                this.refQueryexpr = refQueryexpr;
+                this.refQueryExpr = refQueryExpr;
                 this.dependentQuerypoints = [];
 
                 // breakpoint
@@ -29,14 +29,14 @@ with (Lang){
                 this.hitCount = hitCount;
 
                 //obj should be traced at this point
-                this.queryDataList = [];   // the list of query expressions (QueryExpr) 
+                this.queryExprList = [];   // the list of query expressions (QueryExpr)
                 this.queryWatchList = [];  // the list of watch expressions
             };
 
             constructor.prototype = {
-                addQueryData : function(queryData){
-                    this.queryDataList.push(queryData);
-                    return queryData;
+                addQueryExpr : function(queryExpr){
+                    this.queryExprList.push(queryExpr);
+                    return queryExpr;
                 },
 
                 addQueryWatch : function(expr){
@@ -62,7 +62,7 @@ with (Lang){
                 {
                     if (this.getQueryType() === "lastChange")
                     {
-                        return this.refQueryexpr.expr;
+                        return this.refQueryExpr.expr;
                     }
                 },
             };

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/trace.js

@@ -22,22 +22,21 @@ with (Lang){
             constructor.prototype = {
 
                 addLastChangeTracepoint: function(querypoint, context, eventId, frame, parent, oldValue, newValue, isObjectCreation){
-
                     var tracepoint = this.addTracepoint(querypoint, context, eventId, frame, parent, oldValue, newValue);
 
                     if (isObjectCreation){ //correct last frame line number
                         //todo change it  perhaps you can keep the creation url, line number in querypoint as a traceResult summary itself
                         var traceData = context.qpfbug.debugSession.getLastTraceData(
                                      querypoint.refQuerypoint,
-                                     querypoint.refQueryexpr.frameNo,
-                                     querypoint.refQueryexpr.expr
+                                     querypoint.refQueryExpr.frameNo,
+                                     querypoint.refQueryExpr.expr
                                      );
 
                         if (traceData){
-                            var lineNo = traceData.parentCreatorLine;
+                            var lineNo = traceData.parentTrace.creatorLine;
 
                             if (!lineNo){
-                                lineNo = traceData.parentConstructorLine;
+                                lineNo = traceData.parentTrace.constructorLine;
                             }
 
                             if (typeof(lineNo) !== "undefined"){
@@ -66,29 +65,35 @@ with (Lang){
 
                     var stackTraceXB = QPFBUG.FBL.getCorrectedStackTrace(frame, context);
                     var traceThis = copyObject(unwrapIValue(frame.thisValue), dataCollectionDepth);
-                    var traceFrame = new TraceFrame(stackTraceXB, this.getTraceScope(frame.scope, dataCollectionDepth), traceThis);
+                    var traceFrame = new TraceFrame(stackTraceXB, this.getTraceScope(frame.scope, true, dataCollectionDepth), traceThis);
                     var traceOldValue = copyObject(oldValue, dataCollectionDepth);
                     var traceNewValue = copyObject(newValue, dataCollectionDepth);
                     var tracepoint = new Tracepoint(++this.nextTracepointId, eventId, querypoint, traceFrame, traceOldValue, traceNewValue);
 
 
-                    for (var i=0 ; i<querypoint.queryDataList.length ; i++)
+                    for (var i=0 ; i<querypoint.queryExprList.length ; i++)
                     {
-                        var queryData = querypoint.queryDataList[i];
+                        var queryExpr = querypoint.queryExprList[i];
                         var traceData;
 
-                        if (queryData.isSpecial()){
[…]

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/tracepoint.js

@@ -31,11 +31,11 @@ with (Lang){
                     this.traceWatches[watchExpr] = value;
                 },
 
-                getTraceData: function(frameNo, ref){
+                getTraceData: function(frameNo, expr){
                     for (var i=0; i<this.traceDataList.length ; i++)
                     {
-                        if (this.traceDataList[i].queryData.frameNo == frameNo &&
-                            this.traceDataList[i].queryData.expr == ref)
+                        if (this.traceDataList[i].queryExpr.frameNo == frameNo &&
+                            this.traceDataList[i].queryExpr.expr == expr)
                             return this.traceDataList[i];
                     }
                     return null;

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/tracescope.js

@@ -13,9 +13,17 @@ with (Lang){
     __owner.TraceScope =
         function(){
             var constructor = function(parentScope, jsClassName, variableValues){
+                this.id = null;
                 this.parentScope = parentScope;
                 this.jsClassName = jsClassName;
                 this.variableValues = variableValues;
+
+                //if the scope is a regular js object
+                this.creatorURL = null;
+                this.creatorLine = 0;
+                this.constructorURL = null;
+                this.constructorLine = 0;
+
             };
 
             constructor.prototype = {

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugmodel.js
lastChange works on "global window" and "with" scopes variables.

@@ -46,33 +46,32 @@ with (Lang){
                          var qp = this.querypoints[id];
                          if (qp.queryType === DebugModel.QUERY_TYPES.LASTCHANGE){
                              if (qp.refQuerypoint === refQuerypoint
-                                && qp.refQueryexpr.frameNo === valueFrameNo
-                                && qp.refQueryexpr.expr === valueRef)
+                                && qp.refQueryExpr.frameNo === valueFrameNo
+                                && qp.refQueryExpr.expr === valueRef)
                                 return qp;
                          }
                     }
 
                     // makes querypoint
-                    var refQueryexpr = new QueryExpr(valueFrameNo, valueRef);
+                    var refQueryExpr = new QueryExpr(valueFrameNo, valueRef);
                     var id = ++this.nextQuerypointId;
                     var querypoint = new Querypoint(id, DebugModel.QUERY_TYPES.LASTCHANGE,
-                                                    refQuerypoint, refQueryexpr,
+                                                    refQuerypoint, refQueryExpr,
                                                     null, null, null);
 
-                    // updates querypoint queryDataList
+                    // updates querypoint queryExprList
                     var type = 0;
-                    var queryData = new QueryExpr(0, ".owner" );
-                    querypoint.addQueryData(queryData)
+                    var queryExpr = new QueryExpr(0, ".parent" );
+                    querypoint.addQueryExpr(queryExpr)
 
                     // add trace point to the list
                     this.querypoints[id] = querypoint;
                     this.querypointsSize++;
 
-                    // updates refQuerypoint queryDataList
+                    // updates refQuerypoint queryExprList
                     refQuerypoint.addDependentQuerypoint(querypoint);
 
-                    queryData = new QueryExpr(valueFrameNo, valueRef);
-                    refQuerypoint.addQueryData(queryData);
+                    refQuerypoint.addQueryExpr(refQueryExpr);
 
                     return querypoint;
                 },
@@ -96,7 +95,7 @@ with (Lang){
                     this.querypoints[id] = querypoint;
                     this.querypointsSize++;
 
-                    // updates refQuerypoint queryDataList
+                    // updates refQuerypoint queryExprList
                     refQuerypoint.addDependentQuerypoint(querypoint);
 
                     return querypoint;

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/querydata.js

@@ -1,31 +1,0 @@
-var EXPORTED_SYMBOLS = ["loadModule"];
-loadModule = function(QPFBUG)
-{
-
-with (QPFBUG.Classes){
-with (Lang){
-    var __owner = QPFBUG.Classes;
-
-    //------------------------------- QueryData ----------------------------------
-    // This object specifies data should be collected for an object at a point.
-    // @Deprecated
-    __owner.QueryData =
-        function(){
-            var constructor = function(queryExpr){
-
-                this.queryExpr = queryExpr;
-            };
-
-            constructor.prototype = {
-                toString: function()
-                {
-            		return "[QueryData]";
-                }
-            };
-
-            return constructor;
-        }();
-
-}}
-
-};

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/tracedata.js

@@ -12,16 +12,12 @@ with (Lang){
 
     __owner.TraceData =
         function(){
-            var constructor = function(queryData, parentTraceObject, value){
-                this.queryData = queryData;
+            var constructor = function(queryExpr, value){
+                this.queryExpr = queryExpr;
 
-                this.parentTraceObject = parentTraceObject;
+                this.parentTrace = null;  //a traceObject or a traceScope
+
                 this.value = value;
-
-//                this.scopeType;
-
-
-                //scopeType
             };
 
             constructor.prototype = {

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/traceobject.js

@@ -12,7 +12,7 @@ with (Lang){
     __owner.TraceObject =
         function(){
             var constructor = function(){
-                this.id = 0;
+                this.id = null;
                 this.creatorURL = null;
                 this.creatorLine = 0;
                 this.constructorURL = null;

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/core/manager.js

@@ -129,25 +129,25 @@ with (Lang){
                     if (querypoint.queryType == DebugModel.QUERY_TYPES.LASTCHANGE){
                         var traceData = context.qpfbug.debugSession.getLastTraceData(
                                      querypoint.refQuerypoint,
-                                     querypoint.refQueryexpr.frameNo,
-                                     querypoint.refQueryexpr.expr
+                                     querypoint.refQueryExpr.frameNo,
+                                     querypoint.refQueryExpr.expr
                                      );
 
                         if (traceData){
-                            var url = traceData.parentTraceObject.creatorURL;
-                            var lineNo = traceData.parentTraceObject.creatorLine;
+                            var url = traceData.parentTrace.creatorURL;
+                            var lineNo = traceData.parentTrace.creatorLine;
 
                             if (!url){
-                                url = traceData.parentTraceObject.constructorURL;
-                                lineNo = traceData.parentTraceObject.constructorLine;
+                                url = traceData.parentTrace.constructorURL;
+                                lineNo = traceData.parentTrace.constructorLine;
                             }
                             if (url){    //todo
                                 url = normalizeURL(url);
                                 eventRequest = DebugService.getInstance().createModificationWatchpointRequest(
-                                    context, bind(this.onModificationWatchpointEvent, this), url, lineNo, querypoint.refQueryexpr.propertyName);
+                                    context, bind(this.onModificationWatchpointEvent, this), url, lineNo, querypoint.refQueryExpr.propertyName);
                             }else{
                                 eventRequest = DebugService.getInstance().createModificationWatchpointRequest(
-                                    context, bind(this.onModificationWatchpointEvent, this), null, null, querypoint.refQueryexpr.propertyName);
+                                    context, bind(this.onModificationWatchpointEvent, this), null, null, querypoint.refQueryExpr.propertyName);
                             }
 
                         }

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/debugservice.js

@@ -141,6 +141,59 @@ with (Lang){
                 return ++this.nextEventId;
             },
 
+            getObjectId: function(object, set){
+                var id = object["___qpfbug_objectId___"];
+                if (!id && set){
+                    id = DebugService.getInstance().getNextJSObjectId();
+                    object["___qpfbug_objectId___"] = id;
+                }
+                return id;
+
+                // Code for Gecko 2 (fireforx 4)
+                //Object.defineProperty(refValue, "__QPFBUG_ID", { value: objectId });
+                // code for firefox 3.5+
+                //refValue.__defineGetter__("__QPFBUG_ID", function(){return objectId;})
+            },
+
+            //JSD doesn't give us the watch call back then we need to keep old watch call backs in this way
+            addWatchRequest: function(object, propertyName, watchRequest){
+
+                var allWatchRequests = object["___qpfbug_watchRequests___"]; // list of allWatchRequests
+
+                if (!allWatchRequests){
+                    allWatchRequests = {};
+                    object["___qpfbug_watchRequests___"] = allWatchRequests;
+                }
+
+                var watchRequests = allWatchRequests[propertyName];
+
+                if (!watchRequests){
+                    watchRequests = [watchRequest];
+                }else{ //the object has id and therefore another watch callback
+                    watchRequests.push(watchRequest);
+                }
+
+                allWatchRequests[propertyName] = watchRequests;
+
+                return watchRequests;
+            },
+
+            getScopeId: function(scope){
+                var id = scope["___qpfbug_scopeId___"];
+                return id;
+            },
+
+            setScopeId: function(frame){
+                var scope = frame.scope;
+                var unWrappedScope  = unwrapIValueObject(scope);
+                var id = unWrappedScope["___qpfbug_scopeId___"];
+                if (!id){
+                    id = DebugService.getInstance().getNextJSObjectId();
+                    evalInFrame(frame, "var ___qpfbug_scopeId___ = "+id);
+                }
+                return id;
+            },
+
             //--------------------------------- register/unregister listeners ----------------------------
             // interrupt
             registerInterruptListener: function(interruptListener){
@@ -180,7 +233,9 @@ with (Lang){
             enableEventRequest: function(context, eventRequest){
                 if (eventRequest.type == EventRequest.TYPES.WATCHPOINT  && !eventRequest.w_ownerCreationUrl){ //todo improve it
                     var unwrapped = unwrapObject(context.window);
[…]

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/executionmonitor.js

@@ -98,7 +98,7 @@ with (Lang){
                         this.monitorRefValues[i] = refValue;
                         if (typeof(refValue) == "object")
                         {
-                            var objectId = getObjectId(refValue);
+                            var objectId = DebugService.getInstance().getObjectId(refValue, true);
                             this.monitorRefGotNewValue[i] = true;
                             trace(monitorRef + " with id '" + objectId + "' was created.");
                             this.callBack(this.eventRequest, refValue, frame, type, rv);

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/scripts.js

@@ -47,7 +47,6 @@ loadScript("resource://qpfbug/util/monitor.js");
 loadScript("resource://qpfbug/concept/debugmodel.js");
 loadScript("resource://qpfbug/concept/querypoint.js");
 loadScript("resource://qpfbug/concept/queryexpr.js");
-//loadScript("resource://qpfbug/concept/querydata.js");
 loadScript("resource://qpfbug/concept/trace.js");
 loadScript("resource://qpfbug/concept/tracepoint.js");
 loadScript("resource://qpfbug/concept/tracedata.js");

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js

@@ -471,7 +471,7 @@ Firebug.Querypoint.TraceDataPanel.prototype = extend(Firebug.WatchPanel.prototyp
         if (tracepoint.getQueryType() === "lastChange")
         {
             var diff = new Firebug.Querypoint.TraceDataDiff(tracepoint.oldValue, tracepoint.newValue);
-            var lastChangeExpr = "["+tracepoint.querypoint.refQueryexpr.expr+"]";
+            var lastChangeExpr = "["+tracepoint.querypoint.refQueryExpr.expr+"]";
             this.addMember({expr: lastChangeExpr, value: diff }, "result", traceMembers, lastChangeExpr, diff, 0 );
         }
 

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/util/lang.js

@@ -179,21 +179,7 @@ with (QPFBUG.Classes){
                 }
                 return copy;
             }
-            return object;
-        },
-
-        getObjectId: function(object){
-            var id = object["___qpfbug_objectId___"];
-            if (!id){
-                id = DebugService.getInstance().getNextJSObjectId();
-                object["___qpfbug_objectId___"] = id;
-            }
-            return id;
-
-            // Code for Gecko 2 (fireforx 4)
-            //Object.defineProperty(refValue, "__QPFBUG_ID", { value: objectId });
-            // code for firefox 3.5+
-            //refValue.__defineGetter__("__QPFBUG_ID", function(){return objectId;})
+            return object; 
         },
 
         wait: function(millis)

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugmodel.js
traceutils -> logutils trace() - > log()

@@ -116,7 +116,7 @@ with (Lang){
 //                    var iDontUnderstandThisDataStructure = this.querypoints[this.nextQuerypointId - 1];  // I guess this one has to exist ?
 //                    if (iDontUnderstandThisDataStructure)
 //                    	list.push(iDontUnderstandThisDataStructure);
-//                    trace("getQuerypoints "+list.length, {list: list, list0: list[0], list1: list[1]});
+//                    log("getQuerypoints "+list.length, {list: list, list0: list[0], list1: list[1]});
                     return list;
                 },
 

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugsession.js

@@ -68,11 +68,11 @@ var __owner = QPFBUG.Classes;
             {
                 var tps = [];
                 var trace = this.reproductions[reproductionId].trace;
-                Lang.trace("getTracepoints "+trace, trace);
+                Lang.log("getTracepoints "+trace, trace);
                 if (trace)
                 {
                     var qps = this.debugModel.querypoints;
-                    Lang.trace("getTracepoints qps "+ this.debugModel.querypointsSize, qps);
+                    Lang.log("getTracepoints qps "+ this.debugModel.querypointsSize, qps);
                     for (var i in qps)
                     {
                         var tp = trace.getAssignedTracepointByQuerypoint(qps[i]);

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/trace.js

@@ -45,13 +45,13 @@ with (Lang){
                         }
                     }
 
-                    trace("LastChange Tracepoint", tracepoint);
+                    log("LastChange Tracepoint", tracepoint);
                     return tracepoint;
                 },
 
                 addBreakpointTracepoint: function(querypoint, context, eventId, frame){
                     var tracepoint = this.addTracepoint(querypoint, context, eventId, frame);
-                    trace("Breakpoint Tracepoint", tracepoint);
+                    log("Breakpoint Tracepoint", tracepoint);
                     return tracepoint;
                 },
 
@@ -206,7 +206,7 @@ with (Lang){
                 {
                     return this.assignedTracepoints[querypoint.id];
 //                    var points = this.tracepoints[];
-//                    trace("getLastTracepointByQuerypoint "+points, {querypoint: querypoint, tracepoints: this.tracepoints});
+//                    log("getLastTracepointByQuerypoint "+points, {querypoint: querypoint, tracepoints: this.tracepoints});
 //                    if (points && points.length)
 //                        return points[points.length - 1];
                 },
@@ -242,8 +242,8 @@ with (Lang){
 
                     var id;
 
-//                        trace("::::::::::::::::::::::",scope);
-//                        trace("----------------------",unwrapObject(unWrappedScope));
+//                        log("::::::::::::::::::::::",scope);
+//                        log("----------------------",unwrapObject(unWrappedScope));
                     if (jsClassName == "Call"){
 //                        var id = DebugService.getInstance().getScopeId(scope);
 //                        traceScope.id = id;

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/dev/doubledebugger.js

@@ -154,9 +154,9 @@ with (Lang){
                     var fbs = this.fbs;
                     return function(frame, type, val){
                          if (DBG_DOUBLEDEBUGGER)
-                             trace("<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<, stopped: " + QPFBUG.doubleDebugger.stopped);
+                             log("<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<, stopped: " + QPFBUG.doubleDebugger.stopped);
 //                         if (DBG_DOUBLEDEBUGGER)
-//                             trace("Execution hook, "+ frame.script.fileName + ", " +frame.line , frame);
+//                             log("Execution hook, "+ frame.script.fileName + ", " +frame.line , frame);
 
                          if (QPFBUG.doubleDebugger.stopped == 2) // we let 2 pauses and therefore 2 debuggers at a time
                              return Ci.jsdIExecutionHook.RETURN_CONTINUE;
@@ -178,7 +178,7 @@ with (Lang){
 //                         fbs.unhookFunctions();
 
                          if (DBG_DOUBLEDEBUGGER)
-                             trace("----------------------------------, stopped: " + QPFBUG.doubleDebugger.stopped);
+                             log("----------------------------------, stopped: " + QPFBUG.doubleDebugger.stopped);
                          //because debugFrame may not exist later due to our artificial
                          // changes by calling unPause() we keep
                          // execution context reference.
@@ -205,7 +205,7 @@ with (Lang){
                              rv =  fn.apply(fbs, arguments);
                          }catch(e)
                          {
-                             trace("FBS onBreakpoint Exception! : " + e, e)
+                             log("FBS onBreakpoint Exception! : " + e, e)
                          }
 
                          if (QPFBUG.doubleDebugger.stopped == 1 
@@ -230,7 +230,7 @@ with (Lang){
                          QPFBUG.doubleDebugger.stopped--;
 
                          if (DBG_DOUBLEDEBUGGER)
-                             trace(">>>>>>>>>>>>>>>>>>>>>>>>>>>>>>, stopped: " + QPFBUG.doubleDebugger.stopped);
+                             log(">>>>>>>>>>>>>>>>>>>>>>>>>>>>>>, stopped: " + QPFBUG.doubleDebugger.stopped);
                          return rv;
 
                     }

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/di/debugservice.js

@@ -354,7 +354,7 @@ with (Lang){
 
             onBreakpoint: function(context, frame, type, rv){
                 QPFBUG.monitor.ds_counterBreakpoint++;
-                trace("On Breakpoint : " + frame.line);
+                log("On Breakpoint : " + frame.line);
                 var eventRequests = context.qpfbug.eventRequests;
                 var eventRequest;
                 var script = frame.script;
@@ -371,7 +371,7 @@ with (Lang){
                             {
                                 if ( bp.scriptsWithBreakpoint[iScript] && (bp.scriptsWithBreakpoint[iScript].tag == script.tag) && (bp.pc[iScript] == pc) )
                                 {
-                                    trace("On Breakpoint : " + bp.href +  ": " + bp.lineNo);
+                                    log("On Breakpoint : " + bp.href +  ": " + bp.lineNo);
 
                                     if (eventRequest.isBreakpoint())
                                     {
@@ -420,7 +420,7 @@ with (Lang){
                    delete object[propertyName];
                }
 
-                trace("Object('"+ objectId + "') watch() was called.");
+                log("Object('"+ objectId + "') watch() was called.");
             },
 
             onPropertyChanged: function(eventRequests, object, propertyName, oldValue, newValue){

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/di/jsdeventhandler.js

@@ -427,7 +427,7 @@ __owner.JSDEventHandler = function(){
                             return context;
                         }
 //                        else{
-//                            trace(":::: " + frame.script.fileName + " " + frame.line);
+//                            log(":::: " + frame.script.fileName + " " + frame.line);
 //                        }
                     }
                 }

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/di/scriptanalyzer.js

@@ -25,7 +25,7 @@ with (Lang){
                 }
 
                 this.root = this.jsParser.parse(source)
-                trace("ScriptAnalyzer : ROOT", this.root);
+                log("ScriptAnalyzer : ROOT", this.root);
             };
 
             constructor.prototype = {

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/di/steppingdriver.js

@@ -115,7 +115,7 @@ with (Lang){
 
             // ------------------------------ functions called by debug service -------------
             onInterrupt: function(context, frame, type, rv){
-//                trace("steppingDriver : onInterrupt " + type + " " + frame.line+ " " +frame.pc + " "+ frame.script.baseLineNumber + " " +frame.script.lineExtent);
+//                log("steppingDriver : onInterrupt " + type + " " + frame.line+ " " +frame.pc + " "+ frame.script.baseLineNumber + " " +frame.script.lineExtent);
                 if (context != this.context)
                     return;
                 with(SteppingDriver.STEP_MODES){
@@ -149,7 +149,7 @@ with (Lang){
             },
 
             onFunction: function(context, frame, type){
-//                trace("steppingDriver : onFunction " + type + " " + frame.line);
+//                log("steppingDriver : onFunction " + type + " " + frame.line);
                 var rv = null;
                 var stackDepthChange = 0;
 

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/record-replay/userinputhandler.js

@@ -37,7 +37,7 @@ __owner.UserInputHandler = function(){
             },
 
             onEvent : function(originalEvent){
-                //trace(" on user input event : " + originalEvent.toString(), originalEvent);
+                //log(" on user input event : " + originalEvent.toString(), originalEvent);
         		var evt = new RecordedEvent("UI", originalEvent);
                 if(originalEvent.type == "resize") {
 //                    evt.oldWidth = this.innerDimensions.width;

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/scripts.js

@@ -41,7 +41,7 @@ QPFBUG.Classes.FB = {};
 loadScript("resource://qpfbug/util/lang.js");
 loadScript("resource://qpfbug/util/statemachine.js");
 loadScript("resource://qpfbug/util/timer.js");
-loadScript("resource://qpfbug/util/traceutils.js");
+loadScript("resource://qpfbug/util/logutils.js");
 loadScript("resource://qpfbug/util/monitor.js");
 
 loadScript("resource://qpfbug/concept/debugmodel.js");

### 2010-11-23 qp-fbug/qp-fbug-0.1/src/chrome/content/util/lang.js

@@ -23,10 +23,10 @@ with (QPFBUG.Classes){
             return (new Date()).getTime();
         },
 
-        trace: function(message, obj)
+        log: function(message, obj)
         {
             if (FBTrace.DBG_QUERYPOINT)
-                TraceUtils.trace(arguments.callee.caller, message, obj);
+                LogUtils.log(arguments.callee.caller, message, obj);
         },
 
         wrapFunctionsWithTryCatch: function(obj)
@@ -41,7 +41,7 @@ with (QPFBUG.Classes){
                             try{
                                 return f.apply(this, arguments); //we use "this" instead of "obj" to make sure "this" is the same as normal execution.
                             }catch(exc){
-                                Lang.trace("Error : " + exc, exc);
+                                Lang.log("Error : " + exc, exc);
                             }
                         }
                     }(p, obj_p);
@@ -173,7 +173,7 @@ with (QPFBUG.Classes){
                         copy[p] = this.copyObject(object[p], depth-1);
                     } catch(exc) {
                         // Access to some objects will fail, that's life in Mozilla land
-                        // Lang.trace("Error in copyObject(): " + type + " - " + exc.message, exc);
+                        // Lang.log("Error in copyObject(): " + type + " - " + exc.message, exc);
                         // break;
                     }
                 }
@@ -215,9 +215,9 @@ with (QPFBUG.Classes){
 
         getCorrectedStackTrace : QPFBUG.FBL.getCorrectedStackTrace,
 
-        getCorrectedStackTrace : QPFBUG.FBL.clearNode,
+        clearNode : QPFBUG.FBL.clearNode,
 
-        getCorrectedStackTrace : QPFBUG.FBL.createMenuItem,
+        createMenuItem : QPFBUG.FBL.createMenuItem,
 
         $ : QPFBUG.FBL.$,
 

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/basics.js
traceutils -> logutils trace() - > log()

@@ -11,6 +11,6 @@ QPFBUG.Conf = {};
 
 QPFBUG.DBG = false;
 
-//do not include these classes: TraceUtils, Lang, JSDEventHandler, HaltObject, DebugService;
+//do not include these classes: LogUtils, Lang, JSDEventHandler, HaltObject, DebugService;
 QPFBUG.DBG_Filter = ["Manager", "ModuleEventHandler", "UIEventHandler", // "DebugService", "ExecutionMonitor",
                      "DebugModel", "Trace", "DebugSession", "Reproduction", "Reproducer", "UIUtils"];

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/core/moduleeventhandler.js

@@ -47,7 +47,7 @@ with (Lang){
 //            //todo change it
 //            onStartDebugging: function(context)
 //            {
-//                trace("onStartDebugging tracepoints.show "+context.qpfbug.inQuery);
+//                log("onStartDebugging tracepoints.show "+context.qpfbug.inQuery);
 //                if (context.qpfbug.newResults)
 //                {
 //                    context.qpfbug.firefoxWindow.Firebug.chrome.selectSupportingPanel(UIUtils.getDebugModel(context), context, true);

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/di/executionmonitor.js

@@ -20,7 +20,7 @@ with (Lang){
         constructor.prototype = {
 
             start: function(callBack, eventRequest, frame, type, rv){
-                trace("ExecutionMonitor starts: " + frame.script.fileName + " " + frame.line);
+                log("ExecutionMonitor starts: " + frame.script.fileName + " " + frame.line);
                 this.steppingDriver = DebugService.getInstance().getSteppingDriver(this.context);
                 this.fileName = frame.script.fileName;
                 this.line = frame.line;
@@ -34,9 +34,9 @@ with (Lang){
                 this.endPC = -1;
 //                if (frame.line === frame.script.baseLineNumber +frame.script.lineExtent -1) //it is the last line
 //                {
-//                    trace("The end line : " + frame.line);
+//                    log("The end line : " + frame.line);
 //                }else{
-//                    trace("---line--- " + frame.script.pcToLine(frame.pc, Ci.jsdIScript.PCMAP_SOURCETEXT));
+//                    log("---line--- " + frame.script.pcToLine(frame.pc, Ci.jsdIScript.PCMAP_SOURCETEXT));
 //                    var pcToLine_pp = frame.script.pcToLine(frame.pc, Ci.jsdIScript.PCMAP_PRETTYPRINT);
 //
 //                    //find next executable line in pp
@@ -47,13 +47,13 @@ with (Lang){
 //
 //                    var nextLinePC_pp = frame.script.lineToPc(pcToLine_pp + toAdd , Ci.jsdIScript.PCMAP_PRETTYPRINT);
 //                    var nextLine = frame.script.pcToLine(nextLinePC_pp , Ci.jsdIScript.PCMAP_SOURCETEXT);
-//                    trace("---line--- " + pcToLine_pp + " " + nextLinePC_pp + " " + nextLine);
+//                    log("---line--- " + pcToLine_pp + " " + nextLinePC_pp + " " + nextLine);
 //
 //                    this.endPC = nextLinePC_pp;
 //                    this.endPC = 35;
 //                }
 
-                trace("--------script ---- \n", frame.script.functionSource);
+                log("--------script ---- \n", frame.script.functionSource);
                 this.scriptAnalyzer = new ScriptAnalyzer(frame.script.functionSource);
                 this.monitorRefs = this.scriptAnalyzer.getRefsToCreatedObjects(true);
                 this.monitorRefValues = [];
@@ -61,7 +61,7 @@ with (Lang){
[…]

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/record-replay/replayer.js

@@ -17,13 +17,13 @@ __owner.Replayer = function(){
         constructor.prototype =
         {
             start : function(win) {
-                trace("record items: " + this.record.length ,this.record);
-                trace("win: " ,win);
+                log("record items: " + this.record.length ,this.record);
+                log("win: " ,win);
                 for (var i=0 ; i<this.record.length ; i++){
-                    trace("replayer: " + this.record[i].originalEvent.type);
+                    log("replayer: " + this.record[i].originalEvent.type);
                     if (this.record[i].originalEvent.type != "resize")
                         ReplayUtils.fireEvent(win.document, win.document, this.record[i]);
-                    trace("**************");
+                    log("**************");
                     
                 }
             },

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/record-replay/replayutils.js

@@ -88,7 +88,7 @@ __owner.ReplayUtils = {
         },
 
         fireEvent : function(document, element, event){
-            trace("-------------------------------");
+            log("-------------------------------");
             var evt = document.createEvent("HTMLEvents");
             evt.initEvent(event, true, true ); // event type,bubbling,cancelable
             return !element.dispatchEvent(evt);

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/replayreproducer.js

@@ -25,7 +25,7 @@ __owner.ReplayReproducer = function(){  // todo inherit from Reproducer
 
                 reproduce: function (context, debugSessionId, reproductionId)
                 {
-                    trace("Reproduction Starts: " + reproductionId + ".");
+                    log("Reproduction Starts: " + reproductionId + ".");
                     var  win = context.window;
                     var url = context.window.location.toString();
 
@@ -36,7 +36,7 @@ __owner.ReplayReproducer = function(){  // todo inherit from Reproducer
                     };
 
                     if (!record){
-                        trace("Error: There is no record to replay!")
+                        log("Error: There is no record to replay!")
                         return;
                     };
 
@@ -56,7 +56,7 @@ __owner.ReplayReproducer = function(){  // todo inherit from Reproducer
                                 }
                         );
 
-                        trace("Reproduction Ends: " + reproductionId + ".");
+                        log("Reproduction Ends: " + reproductionId + ".");
                     }
 
 

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/reproducer.js

@@ -33,7 +33,7 @@ __owner.Reproducer = function(){
             {
                 var reproducer = this.getReproducer(reproducerKind);
 
-                trace("reproduce "+reproducerKind, {context: context, debugSessionId: debugSessionId, reproductionId: reproductionId});
+                log("reproduce "+reproducerKind, {context: context, debugSessionId: debugSessionId, reproductionId: reproductionId});
 
                 reproducer.reproduce(context, debugSessionId, reproductionId);
             },

### 2010-11-23 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/util/logutils.js

@@ -6,36 +6,36 @@ loadModule = function(QPFBUG)
 with (QPFBUG.Classes){
 with (Lang){
 
-    //--------------------------------- TraceUtils --------------------------------
+    //--------------------------------- LogUtils --------------------------------
 
-    QPFBUG.Classes.TraceUtils = {
+    QPFBUG.Classes.LogUtils = {
 
         wrappedClasses : [],
 
-        traceClassesFunctionCalls: function(list){
+        logClassesFunctionCalls: function(list){
             for (var i=0 ; i<list.length ; i++){
-                    TraceUtils.traceClassFunctionCalls(list[i]);
+                    LogUtils.logClassFunctionCalls(list[i]);
             }
         },
 
-        traceClassFunctionCalls: function(className)
+        logClassFunctionCalls: function(className)
         {
-            if (arrayContainsObject(TraceUtils.wrappedClasses, className))
+            if (arrayContainsObject(LogUtils.wrappedClasses, className))
                 return;
             var class = QPFBUG.Classes[className];
             if (!class){
-                trace("there is no class with this name : " + className);
+                log("there is no class with this name : " + className);
                 return;
             }
 
-            TraceUtils.traceDataFunctionCalls(className, class);
+            LogUtils.logDataFunctionCalls(className, class);
             if (class.prototype)
-                TraceUtils.traceDataFunctionCalls(className, class.prototype);
+                LogUtils.logDataFunctionCalls(className, class.prototype);
 
-            TraceUtils.wrappedClasses.push(className);
+            LogUtils.wrappedClasses.push(className);
         },
 
-        traceDataFunctionCalls: function(objName, obj, functionName) //todo instead of getting one function name get a list
+        logDataFunctionCalls: function(objName, obj, functionName) //todo instead of getting one function name get a list
         {
             for (var p in obj)
             {
@@ -47,14 +47,14 @@ with (Lang){
                                                      //todo parse f.toSource() and pass arguments names
                             return function(){
                                     var caller = arguments.callee.caller;
-                                    var thread = TraceUtils.enterThread(caller, f);
-                                    var space = TraceUtils.getPre(thread);
+                                    var thread = LogUtils.enterThread(caller, f);
+                                    var space = LogUtils.getPre(thread);
                                     var argumentsCopy = cloneArray(arguments); //because "arguments" is not longer available when function returns
[…]

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/basics.js
supports possibleToStop at querypoints. (Less data collection, appropriate icons.)
Fixing bugs including "lastChange on 'this' properties didn't work." -> A special firefox wrapper issue.

reRun button on Script panel call manager.replay.

@@ -11,6 +11,6 @@ QPFBUG.Conf = {};
 
 QPFBUG.DBG = false;
 
-//do not include these classes: LogUtils, Lang, JSDEventHandler, HaltObject, DebugService;
-QPFBUG.DBG_Filter = ["Manager", "ModuleEventHandler", "UIEventHandler", // "DebugService", "ExecutionMonitor",
+//do not include these classes: LogUtils, Lang, JSDEventHandler, HaltObject, DebugService, ExecutionMonitor;
+QPFBUG.DBG_LIST = ["Manager", "ModuleEventHandler", "UIEventHandler",
                      "DebugModel", "Trace", "DebugSession", "Reproduction", "Reproducer", "UIUtils"];

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugmodel.js

@@ -12,6 +12,7 @@ with (Lang){
             var constructor = function(){
                  this.querypoints = {};
                  this.querypointsSize = 0;
+                 this.breakpoint_querypointsSize = 0;
                  this.nextQuerypointId = 0;
             };
 
@@ -32,10 +33,12 @@ with (Lang){
                     var id = ++this.nextQuerypointId;
                     var querypoint = new Querypoint(id, DebugModel.QUERY_TYPES.BREAKPOINT,
                                                     null, null,
-                                                    url, lineNo, hitCount);
+                                                    url, lineNo, hitCount,
+                                                    true, false);
 
                     this.querypoints[id] = querypoint;
                     this.querypointsSize++;
+                    this.breakpoint_querypointsSize++;
                     return querypoint;
                 },
 
@@ -57,7 +60,8 @@ with (Lang){
                     var id = ++this.nextQuerypointId;
                     var querypoint = new Querypoint(id, DebugModel.QUERY_TYPES.LASTCHANGE,
                                                     refQuerypoint, refQueryExpr,
-                                                    null, null, null);
+                                                    null, null, null,
+                                                    false, false);
 
                     // updates querypoint queryExprList
                     var type = 0;
@@ -90,7 +94,8 @@ with (Lang){
                     var id = ++this.nextQuerypointId;
                     var querypoint = new Querypoint(id, DebugModel.QUERY_TYPES.LASTCONDITION,
                                                     refQuerypoint, null,
-                                                    null, null, null);
+                                                    null, null, null,
+                                                    false, false);
 
                     this.querypoints[id] = querypoint;
                     this.querypointsSize++;

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugsession.js

@@ -104,7 +104,11 @@ var __owner = QPFBUG.Classes;
             },
 
             moreQuerypointsToFind: function(){
-                return (this.getNumberOfQuerypoints() > this.reproduction.trace.assignedTracepointsSize);
+                return (this.debugModel.querypointsSize > this.reproduction.trace.assignedTracepointsSize);
+            },
+
+            moreReproductionPointsToFind: function(){
+                return (this.debugModel.breakpoint_querypointsSize > this.reproduction.trace.assignedBreakpointTracepointsSize);
             },
 
         }

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/querypoint.js

@@ -10,7 +10,7 @@ with (Lang){
     // trace point is kept in debug model.
     __owner.Querypoint =
         function(){
-            var constructor = function(id, queryType, refQuerypoint, refQueryExpr, url, lineNo, hitCount){
+            var constructor = function(id, queryType, refQuerypoint, refQueryExpr, url, lineNo, hitCount, possibleToStop, stopEnabled){
                 this.id = id;
                 this.queryType = queryType;
 
@@ -31,6 +31,11 @@ with (Lang){
                 //obj should be traced at this point
                 this.queryExprList = [];   // the list of query expressions (QueryExpr)
                 this.queryWatchList = [];  // the list of watch expressions
+
+                this.possibleToStop = possibleToStop;
+                this.stopEnabled = stopEnabled;
+                this.stopIndex = -1;
+                this.nonDeterminismInStopIndex = false;
             };
 
             constructor.prototype = {
@@ -65,6 +70,19 @@ with (Lang){
                         return this.refQueryExpr.expr;
                     }
                 },
+
+                isPossibleToStop: function(){
+                    return this.possibleToStop;
+                },
+
+                setStopEnabled: function(newValue){ 
+                    this.stopEnabled = newValue;
+                },
+
+                isStopEnabled: function(){
+                    return this.stopEnabled;
+                },
+
             };
             return constructor;
         }();

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/trace.js

@@ -17,6 +17,7 @@ with (Lang){
                 this.tracepoints = {}; //<int querypointId, [] tracepoints>
                 this.assignedTracepoints = {};
                 this.assignedTracepointsSize = 0;
+                this.assignedBreakpointTracepointsSize = 0;
             };
 
             constructor.prototype = {
@@ -57,18 +58,23 @@ with (Lang){
 
                 addTracepoint: function(querypoint, context, eventId, frame, parent, oldValue, newValue)
                 {
-                    var dataCollectionDepth = QPFBUG.Conf.DATA_COLLECTION_DEPTH;
                     var querypointId = querypoint.id;
                     if (!this.tracepoints[querypointId]){
                         this.tracepoints[querypointId] = [];
                     }
+
+                    var index = this.tracepoints[querypointId].length;
+
+                    var dataCollectionDepth = QPFBUG.Conf.DATA_COLLECTION_DEPTH;
+                    if (querypoint.possibleToStop && querypoint.stopIndex != index)
+                        dataCollectionDepth = 0;
 
                     var stackTraceXB = QPFBUG.FBL.getCorrectedStackTrace(frame, context);
                     var traceThis = copyObject(unwrapIValue(frame.thisValue), dataCollectionDepth);
                     var traceFrame = new TraceFrame(stackTraceXB, this.getTraceScope(frame.scope, true, dataCollectionDepth), traceThis);
                     var traceOldValue = copyObject(oldValue, dataCollectionDepth);
                     var traceNewValue = copyObject(newValue, dataCollectionDepth);
-                    var tracepoint = new Tracepoint(++this.nextTracepointId, eventId, querypoint, traceFrame, traceOldValue, traceNewValue);
+                    var tracepoint = new Tracepoint(++this.nextTracepointId, eventId, index, querypoint, traceFrame, traceOldValue, traceNewValue);
 
 
                     for (var i=0 ; i<querypoint.queryExprList.length ; i++)
@@ -85,7 +91,6 @@ with (Lang){
                             }else if (querypoint.refQueryExpr.isVariable()){ //&& with
                                 var parentJSDIValue = QPFBUG.fbs.getJSD().wrapValue(parent);
                                 traceData.parentTrace = this.getTraceObject(parentJSDIValue);
-//                                traceData.parentTrace = this.getTraceScope(frame.scope,false,0);
                             }
                         }
                         if (queryExpr.isProperty()){
@@ -96,13 +101,15 @@ with (Lang){
[…]

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/core/manager.js

@@ -80,6 +80,7 @@ with (Lang){
                     newResults : false, //todo
                     reproducer: this.reproducer,
                     recorder: null,
+                    passBreakpointEventsToFirebug: false,
                 };
 //                if (debugSession.getNumberOfQuerypoints > 0){
                 reproduction.start(context);
@@ -180,9 +181,10 @@ with (Lang){
                 this.collectData(context, querypoint, eventId, frame);
                 if (context.qpfbug.debugSession.needsAnotherReproduction()){   //todo: && there is no more reproduction point to visit
                     this.replay(context);
-                }else{
+                }else if(!context.qpfbug.debugSession.moreReproductionPointsToFind()){
                     //show new found querypoints
                     context.qpfbug.newResults = true;
+                    context.qpfbug.passBreakpointEventsToFirebug = true;
                 }
             },
 

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/localreproducer.js

@@ -20,7 +20,8 @@ __owner.LocalReproducer = function(){
             reproduce: function (context, debugSessionId, reproductionId)
             {
                 var Firebug = context.Firebug; // we are in a module and don't have access to Firebug in this scope.
-                Firebug.Debugger.rerun(context);
+//                Firebug.Debugger.rerun(context);
+                Firebug.Debugger.localRerun(context);
             },
 
             toString: function()  // todo to base class

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/uieventhandler.js

@@ -20,7 +20,15 @@ __owner.UIEventHandler = function(){
 
             init : function()
             {
+                this.updateScriptPanel();
                 this.addLastChangeMenuItem();
+            },
+
+            updateScriptPanel: function(){
+                with(this.win){
+                    Firebug.Debugger.localRerun = Firebug.Debugger.rerun;
+                    Firebug.Debugger.rerun = bind(Manager.getInstance().replay,Manager.getInstance());
+                }
             },
             //----------------------- Changes getContextMenuItems --------------
             // Adds "lastChange" menuItem to popup menu

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/util/logutils.js

@@ -101,7 +101,7 @@ with (Lang){
         },
 
 
-        spaces: {},
+        spaces: {},  //spaces strings catch
         
         getPre: function(thread){
             var depth = thread.depth;
@@ -136,8 +136,6 @@ with (Lang){
 
             FBTrace.sysout(message, obj);
         },
-
-
 
 
     };

### 2010-11-25 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/tracepoint.js
supports possibleToStop at querypoints. (Less data collection, appropriate icons.)
Fixing bugs including "lastChange on 'this' properties didn't work." -> A special firefox wrapper issue.

reRun button on Script panel call manager.replay.

@@ -11,11 +11,12 @@ with (Lang){
     // trace point is kept in debug model.
     __owner.Tracepoint =
         function(){
-            var constructor = function(id, eventId, querypoint, traceFrame, oldValue, newValue){
+            var constructor = function(id, eventId, index, querypoint, traceFrame, oldValue, newValue){
                 this.id = id;
+                this.eventId = eventId;
+                this.index = index;
                 this.querypoint = querypoint;
                 this.traceFrame = traceFrame;
-                this.eventId = eventId;
                 this.oldValue = oldValue;
                 this.newValue = newValue;
                 this.traceDataList = [];

### 2010-11-25 qp-fbug/qp-fbug-0.1/src/chrome/content/di/debugservice.js

@@ -90,9 +90,7 @@ with (Lang){
                 context.qpfbug.eventRequests = null;
             },
 
-            onModificationWatchpointEvent: function(eventRequests, object, propertyName, oldValue, newValue, frame, type, rv, isObjectCreation){
-
-                var eventId = this.getNextEventId();
+            onModificationWatchpointEvent: function(eventId, eventRequests, object, propertyName, oldValue, newValue, frame, type, rv, isObjectCreation){
 
                 //Note this method might be called indirectly by watch, onPropertyChange->halt , onHalst -> onModificationWatchpoint
                 // or it might be called executionMonitor -> onObjectCreation -> onModification
@@ -115,7 +113,7 @@ with (Lang){
                 }
             },
 
-            onBreakpointEvent: function(eventRequest, frame, type, rv){
+            onBreakpointEvent: function(eventId, eventRequest, frame, type, rv){
                 var eventId = this.getNextEventId();
                 eventRequest.callBack(eventRequest, eventId, frame, type, rv);
             },
@@ -232,10 +230,10 @@ with (Lang){
             //--------------------------------- EventRequest-SourceFile --------------------------------
             enableEventRequest: function(context, eventRequest){
                 if (eventRequest.type == EventRequest.TYPES.WATCHPOINT  && !eventRequest.w_ownerCreationUrl){ //todo improve it
-                    var unwrapped = unwrapObject(context.window);
-                    this.getObjectId(unwrapped, true); //sets object id for window
-                    var watchRequests = this.addWatchRequest(unwrapped, eventRequest.w_propertyName, eventRequest);
-                    unwrapped.watch(eventRequest.w_propertyName, bindAtHead(this.onPropertyChanged, this, watchRequests, context.window));
+                    var window = unwrapObject(context.window);
+                    this.getObjectId(window, true); //sets object id for window
+                    var watchRequests = this.addWatchRequest(window, eventRequest.w_propertyName, eventRequest);
+                    window.watch(eventRequest.w_propertyName, bindAtHead(this.onPropertyChanged, this, watchRequests, window));
                 };
 
                 //set hooks for already loaded sourcefiles
@@ -355,10 +353,12 @@ with (Lang){
             onBreakpoint: function(context, frame, type, rv){
                 QPFBUG.monitor.ds_counterBreakpoint++;
                 log("On Breakpoint : " + frame.line);
+                var eventId = this.getNextEventId();
                 var eventRequests = context.qpfbug.eventRequests;
[…]

### 2010-11-25 qp-fbug/qp-fbug-0.1/src/chrome/content/di/executionmonitor.js

@@ -19,7 +19,7 @@ with (Lang){
 
         constructor.prototype = {
 
-            start: function(callBack, eventRequest, frame, type, rv){
+            start: function(callBack, eventRequests, frame, type, rv){
                 log("ExecutionMonitor starts: " + frame.script.fileName + " " + frame.line);
                 this.steppingDriver = DebugService.getInstance().getSteppingDriver(this.context);
                 this.fileName = frame.script.fileName;
@@ -28,7 +28,7 @@ with (Lang){
                 this.startPC = frame.pc;
                 this.startStackFrameDepth = callStackDepth(frame);
                 this.callBack = callBack;
-                this.eventRequest = eventRequest;
+                this.eventRequests = eventRequests;
                 this.isStopped = false;
 
                 this.endPC = -1;
@@ -101,7 +101,7 @@ with (Lang){
                             var objectId = DebugService.getInstance().getObjectId(refValue, true);
                             this.monitorRefGotNewValue[i] = true;
                             log(monitorRef + " with id '" + objectId + "' was created.");
-                            this.callBack(this.eventRequest, refValue, frame, type, rv);
+                            this.callBack(this.eventRequests, refValue, frame, type, rv);
                         }
                     }
                 }

### 2010-11-25 qp-fbug/qp-fbug-0.1/src/chrome/content/di/jsdeventhandler.js

@@ -179,6 +179,12 @@ __owner.JSDEventHandler = function(){
 
                 if (context && !context.qpfbug)//only for debugging
                     return returnValue;
+
+                //todo update according it john:frame.pc == 0 means breakpoint was set by Firebug unless sourceFile.breakOnZero == script.tag; in which case the user set the breakpoint.
+                if (context && !context.qpfbug.passBreakpointEventsToFirebug && frame.pc!=0){ //breakpoint which are set at pc==0 are set by firebug for recognizing the script load
+//                    log(frame.script.fileName+":"+frame.line+":"+frame.pc);
+                    return returnValue;
+                }
                 // fbs removes the breakpoint from the script if it doesn't have
                 // the breakpoint in its list, so it should be called
                 // if this breakpoint is one of its breakpoints.

### 2010-11-25 qp-fbug/qp-fbug-0.1/src/chrome/content/init.js

@@ -4,8 +4,10 @@ FBL.ns(function() { with (FBL)
 {
     with(QPFBUG.Classes){
 
-        if (QPFBUG.DBG)
-            TraceUtils.traceClassesFunctionCalls(QPFBUG.DBG_Filter);
+        if (QPFBUG.DBG){
+            LogUtils.logClassesFunctionCalls(QPFBUG.DBG_LIST);
+            FBTrace.DBG_QUERYPOINT = true;
+        }
 
         //store firebug classes
 
@@ -18,7 +20,6 @@ FBL.ns(function() { with (FBL)
         // A new Module event handler is created for every new firefox window
         Firebug.registerModule(ModuleEventHandler.getInstance(window));
 
-        FBTrace.DBG_QUERYPOINT = false;
         QPFBUG.Conf.DATA_COLLECTION_DEPTH = 2;
 
     }

### 2010-11-25 qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js

@@ -56,6 +56,19 @@ Firebug.Querypoint.QPModule = extend(Firebug.ActivableModule,
 
     },
 
+     //this operation has a conceptual problem. A breakpoint is different from a breakpointQuerypoint.
+     // The first one may happen many times but the second one happens only once.
+     // So it is necessary that developer adds breakpointQuerypoint at a specific hit of a breakpoint.
+//    onToggleBreakpoint: function(context, url, lineNo, isSet) //is called from debugger.js //todo currently it is not possible to add breakpoint directly in QP panel so we add breakpoints when they are added to Script panel
+//    {
+//         var debugSession = context.qpfbug.debugSession;
+//         var debugModel = debugSession.debugModel;
+//         if (isSet){
+//            debugModel.addQuerypoint_Breakpoint(url, lineNo, 0);
+//        }
+//    },
+
+
 
 });
 
@@ -332,8 +345,15 @@ Firebug.Querypoint.QPSourceViewPanel.prototype = extend(Firebug.SourceBoxPanel,
                             var row = sourceBox.getLineNode(lineNo);
                             if (FBTrace.DBG_QUERYPOINT)
                                 FBTrace.sysout("qp.decorator found line "+row);
-                            if (row) // we *should* only be called for lines in the viewport...
+                            if (row){ // we *should* only be called for lines in the viewport...
                                 row.setAttribute("tracepoint", "true");
+                                if (tp.querypoint.isPossibleToStop()){
+                                    row.setAttribute("possibleToStop", "true");
+                                }
+                                if (tp.querypoint.isStopEnabled()){
+                                    row.setAttribute("stopEnabled", "true");
+                                }
+                            }
                         }
                     }
                 });;

### 2010-11-25 qp-fbug/qp-fbug-0.1/src/chrome/content/core/manager.js
rerun button in Script panel is always enabled. manager.replay gets a target querypoint.

@@ -80,9 +80,12 @@ with (Lang){
                     newResults : false, //todo
                     reproducer: this.reproducer,
                     recorder: null,
-                    passBreakpointEventsToFirebug: false,
+                    passBreakpointEventsToFirebug: true,
                 };
-//                if (debugSession.getNumberOfQuerypoints > 0){
+
+                if (reproduction.targetQuerypoint)
+                    context.qpfbug. passBreakpointEventsToFirebug = false;
+
                 reproduction.start(context);
                 this.enableQuerypoints(context);
 //                }
@@ -180,7 +183,7 @@ with (Lang){
 
                 this.collectData(context, querypoint, eventId, frame);
                 if (context.qpfbug.debugSession.needsAnotherReproduction()){   //todo: && there is no more reproduction point to visit
-                    this.replay(context);
+                    this.replay(context, reproduction.targetQuerypoint);
                 }else if(!context.qpfbug.debugSession.moreReproductionPointsToFind()){
                     //show new found querypoints
                     context.qpfbug.newResults = true;
@@ -202,7 +205,7 @@ with (Lang){
                     //todo move this tag to another place
                     context.qpfbug.newResults = true;
 
-                    this.replay(context);
+                    this.replay(context, querypointB);
                 }
             },
 
@@ -240,7 +243,7 @@ with (Lang){
                         context.qpfbug.newResults = true;
 
                         this.collectData(context, querypoint, -1, frame); //todo eventId == -1  ? centerlize eventid and give a coorect one here
-                        this.replay(context);
+                        this.replay(context, querypointB);
                     }
                 }
             },
@@ -267,11 +270,12 @@ with (Lang){
 
             },
 
-            replay: function(context){
+            replay: function(context, targetQuerypoint){
                 var debugSession = context.qpfbug.debugSession;
                 var reproduction = context.qpfbug.debugSession.reproduction;
 
                 var newReproduction = debugSession.nextReproduction();
+                newReproduction.targetQuerypoint = targetQuerypoint;
                 this.disableQuerypoints(context);
                 this.getReproducer().reproduce(context, debugSession.id, newReproduction.id);
             }

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js
rerun button in Script panel is always enabled. manager.replay gets a target querypoint.

@@ -283,11 +283,21 @@ Firebug.Querypoint.QPSourceViewPanel.prototype = extend(Firebug.SourceBoxPanel,
 
     getDefaultLocation: function()
     {
-        var list = this.getLocationList()
         if (FBTrace.DBG_QUERYPOINT)
             FBTrace.sysout("getDefaultLocation "+list, list);
-        if (list)
+
+        var targetQuerypoint = UIUtils.getReproduction(this.context).targetQuerypoint;
+        var tp;
+        if (targetQuerypoint)
+             tp = UIUtils.getTracepointByQuerypoint(this.context, targetQuerypoint);
+        if (tp)
+             return tp;
+
+        var list = this.getLocationList()
+        if (list){
             return list.pop();
+        }
+
     },
 
     getLocationContent: function(objects, popup)
@@ -861,7 +871,7 @@ Firebug.Querypoint.TraceDataNotCollectedRep = domplate(Firebug.Rep,
         try
         {
             tracepoint.querypoint.addQueryWatch(path.join(''));
-            QPFBUG.Classes.Manager.getInstance().replay(panel.mainPanel.context);
+            QPFBUG.Classes.Manager.getInstance().replay(panel.mainPanel.context, tracepoint.querypoint);
             FBTrace.sysout("Rerun to collect data requested for "+row.textContent+" set depth "+QPFBUG.Conf.DATA_COLLECTION_DEPTH, event);
         }
         catch(exc)

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/uieventhandler.js

@@ -28,6 +28,15 @@ __owner.UIEventHandler = function(){
                 with(this.win){
                     Firebug.Debugger.localRerun = Firebug.Debugger.rerun;
                     Firebug.Debugger.rerun = bind(Manager.getInstance().replay,Manager.getInstance());
+
+                    var old_SyncCommands = Firebug.Debugger.syncCommands;
+                    Firebug.Debugger.syncCommands = function(context){
+                        old_SyncCommands.apply(Firebug.Debugger, arguments);
+                        var chrome = Firebug.chrome;
+                        if (!chrome)
+                            return;
+                        chrome.setGlobalAttribute("cmd_rerun", "disabled", "false"); //enable re_run again
+                    }
                 }
             },
             //----------------------- Changes getContextMenuItems --------------

### 2010-11-25 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/uiutils.js

@@ -62,6 +62,11 @@ with (Lang){
             return tracepoint.querypoint;
          },
 
+         getTracepointByQuerypoint: function(context, querypoint)
+         {
+            return context.qpfbug.debugSession.reproduction.trace.getAssignedTracepointByQuerypoint(querypoint);
+         },
+
          getTraceData: function(tracepoint)
          {
              // Salman, need help here.

### 2010-11-30 qp-fbug/qp-fbug-0.1/src/chrome/content/ui/uiutils.js
LastChange is removed for "this" and result row in Watches panel. It is also removed from Dom and DomSide panels. Code polishing.

@@ -96,8 +96,16 @@ with (Lang){
                  if (parseInt(row.getAttribute("level")) == level)
                      return row;
              }
-         }
+         },
          
+         isResultRow: function(row)
+         {
+             for(var current = row; current ; current = UIUtils.getParentRow(current)){
+                 if (hasClass(current, "resultRow")) //if the root parent has "resultRow" class
+                    return true;
+             }
+             return false
+         }
 
      };
 }}

### 2010-12-01 trunk/qp-fbug/qp-fbug-0.1/test/basics/test_basics.js
basic test was updated, #classes.

@@ -9,7 +9,7 @@ function runTest()
         var classesNo = 0;
         for (var i in QPFBUG.Classes)
             classesNo++;
-        FBTest.compare( 44, classesNo, "Number of classes");
+        FBTest.compare( 43, classesNo, "Number of classes");
         FBTest.ok(QPFBUG.debugService, "QPFBUG.debugService");
         FBTest.ok(QPFBUG.manager, "QPFBUG.manager");
         FBTest.ok(QPFBUG.jsdEventHandler, "QPFBUG.jsdEventHandler");

### 2010-12-01 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/reproduction.js
page reload with the same or a new url is considered as a request for a fresh debug session with no QP.

@@ -52,6 +52,10 @@ __owner.Reproduction =
                     this.stateMachine.transit("stop");
                 },
 
+                isAlreadyStarted : function(){
+                    return !this.stateMachine.isState("notstarted");
+                },
+
                 newBreakEvent : function(breakEvent){
 
                 }

### 2010-12-01 qp-fbug/qp-fbug-0.1/src/chrome/content/core/manager.js

@@ -72,6 +72,15 @@ with (Lang){
 
                 reproduction = debugSession.reproduction;
 
+                //it means that no new reproduction is assigned
+                //for example, page is reloaded
+                //so a new debug session will be created.
+                if (reproduction.isAlreadyStarted()){
+                    debugSession = this.newDebugSession();
+                    reproduction = debugSession.reproduction;
+                }
+
+
                 //todo if !debugSession || !reproduction then ?
 
                 //set qpfbug data holder for the context

### 2010-12-01 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/core/manager.js
LocalReproduction is supported.

@@ -80,27 +80,14 @@ with (Lang){
                     reproduction = debugSession.reproduction;
                 }
 
+                var reproducerName = win.Firebug.getPref("extensions.firebug", "querypoints.reproducer");
+                context.qpfbug = {};
+                context.qpfbug.reproducer = Reproducer.getInstance().getReproducer(reproducerName);
+                context.qpfbug.Firebug = win.Firebug; //to keep a reference to Firebug
 
                 //todo if !debugSession || !reproduction then ?
 
-                //set qpfbug data holder for the context
-                context.qpfbug = {
-                    Firebug: win.Firebug,
-                    debugSession : debugSession,
-                    newResults : false, //todo
-                    reproducer: this.reproducer,
-                    recorder: null,
-                    passBreakpointEventsToFirebug: true,
-                };
-
-                var reproducerName = win.Firebug.getPref("extensions.firebug", "querypoints.reproducer");
-                context.qpfbug.reproducer = Reproducer.getInstance().getReproducer(reproducerName);
-
-                if (reproduction.targetQuerypoint)
-                    context.qpfbug.breakEnabled = false;
-
-                reproduction.start(context);
-                this.enableQuerypoints(context);
+                this.onReproductionStart(context, debugSessionId);
 
             },
 
@@ -126,6 +113,24 @@ with (Lang){
                     context.qpfbug.debugSession.record = context.qpfbug.recorder.record;
                 }
                 delete context.qpfbug;
+            },
+
+            onReproductionStart: function(context, debugSessionId){
+
+                var debugSession = this.getDebugSession(debugSessionId)
+                var reproduction = debugSession.reproduction;
+
+                //set qpfbug data holder for the context
+                context.qpfbug.debugSession = debugSession;
+                context.qpfbug.newResults = false; //todo
+                context.qpfbug.recorder= null;
+                context.qpfbug.breakEnabled= true;
+
+                if (reproduction.targetQuerypoint)
+                    context.qpfbug.breakEnabled = false;
+
+                reproduction.start(context);
+                this.enableQuerypoints(context);
             },
 
             enableQuerypoints: function(context){

### 2010-12-01 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/reproducer/localreproducer.js

@@ -20,6 +20,9 @@ __owner.LocalReproducer = function(){
             reproduce: function (context, debugSessionId, reproductionId)
             {
                 var Firebug = context.qpfbug.Firebug; // we are in a module and don't have access to Firebug in this scope.
+
+                Manager.getInstance().onReproductionStart(context, debugSessionId);
+
 //                Firebug.Debugger.rerun(context);
                 Firebug.Debugger.localRerun(context);
             },

### 2010-12-01 qp-fbug/qp-fbug-0.1/src/chrome/content/ui/uieventhandler.js
lastChange will not be shown on variables. It will be added later when it is supported on all kinds of scope.

@@ -83,6 +83,9 @@ __owner.UIEventHandler = function(){
                             if (propertyPath == "this") // no lastChange for "this"
                                 return items;
 
+                            if (propertyPath.indexOf(".") < 0) //a root variable
+                                return items;
+
                             if (domPanel.selection instanceof JSDConstants.jsdIStackFrame) { //watches panel
                                 if (domPanel.context.stopped){
                                     var isWatch = false;
@@ -110,6 +113,9 @@ __owner.UIEventHandler = function(){
                     };
 
                     // change domPanels
+                    //feature lastChange in these two panels can be enabled if context.stopped
+                    //        It needs more changes for passing right data to action.
+
                     //panelType_Dom.prototype.getContextMenuItems = new_GetContextMenuItems;
                     //panelType_DomSide.prototype.getContextMenuItems = new_GetContextMenuItems;
                     panelType_Watches.prototype.getContextMenuItems = new_GetContextMenuItems;

### 2010-12-01 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/basics.js
lastChange will not be shown on variables. It will be added later when it is supported on all kinds of scope.

@@ -11,7 +11,7 @@ QPFBUG.Conf = {};
 QPFBUG.Conf.DATA_COLLECTION_DEPTH = 2;
 
 //Debugging
-QPFBUG.DBG = true;
+QPFBUG.DBG = false;
 
 //do not include these classes: LogUtils, Lang (might cause loops),
 //                              JSDEventHandler (too many calls),

### 2010-12-02 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js
add timing for user study

@@ -42,20 +42,41 @@ Firebug.Querypoint.QPModule = extend(Firebug.ActivableModule,
 
     onStartDebugging: function(context)
     {
-        //if (FBTrace.DBG_QUERYPOINT)
+        // ** Timing for the user study **
         var now = new Date().getTime();
         var delta = now - Firebug.Querypoint.timestamp;
         Firebug.Querypoint.timestamp = now;
-            FBTrace.sysout("Querypoint user start debugging, new QP results: "+context.qpfbug.newResults+" time "+delta);
+        FBTrace.sysout("Querypoint user starts debugging, new QP results: "+context.qpfbug.newResults+" delta time "+delta+"ms");
+        // ********************************
+
         if (context.qpfbug.newResults)
         {
 //            context.qpfbug.inSession = true;  // I don't know how we will get out of this state
             Firebug.chrome.selectSupportingPanel(UIUtils.getDebugModel(context), context, true);
             delete context.qpfbug.newResults;
         }
-
     },
 
+    onResume: function(context)
+    {
+        // ** Timing for the user study **
+        var now = new Date().getTime();
+        var delta = now - Firebug.Querypoint.timestamp;
+        Firebug.Querypoint.timestamp = now;
+        FBTrace.sysout("Querypoint resume delta time "+delta+"ms");
+        // ********************************
+    },
+
+    onStop: function(context,frame, type,rv)
+    {
+        // ** Timing for the user study **
+        var sayType = type;
+        if (type === 1) sayType = "breakpoint";
+        if (type === 0) sayType = "interrupt";
+
+        FBTrace.sysout("Querypoint stop type: "+sayType);
+        // ********************************
+    },
      //this operation has a conceptual problem. A breakpoint is different from a breakpointQuerypoint.
      // The first one may happen many times but the second one happens only once.
      // So it is necessary that developer adds breakpointQuerypoint at a specific hit of a breakpoint.

### 2010-12-02 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugmodel.js
Only the active path of querypoints from a reproduction point is shown.

@@ -12,6 +12,7 @@ with (Lang){
             var constructor = function(){
                  this.querypoints = {};
                  this.querypointsSize = 0;
+                 this.enabledQuerypointsSize = 0;
                  this.breakpoint_querypointsSize = 0;
                  this.nextQuerypointId = 0;
             };
@@ -104,6 +105,33 @@ with (Lang){
                     refQuerypoint.addDependentQuerypoint(querypoint);
 
                     return querypoint;
+                },
+
+                enableQuerypoint: function(querypoint){
+                    querypoint.setEnabled(true);
+                    this.enabledQuerypointsSize++;
+                    if (querypoint.queryType === DebugModel.QUERY_TYPES.LASTCHANGE ||
+                        querypoint.queryType === DebugModel.QUERY_TYPES.LASTCONDITION){
+                        var siblings = querypoint.refQuerypoint.dependentQuerypoints;
+                        for (var i=0 ; i<siblings.length; i++){
+                            if (siblings[i] !== querypoint){
+                                this.disableQuerypoint(siblings[i]);
+                            }
+                        }
+
+                    }
+
+                },
+
+                disableQuerypoint: function(querypoint){
+                    if (querypoint.isEnabled()){
+                        querypoint.setEnabled(false);
+                        this.enabledQuerypointsSize--;
+                        var dependentQuerypoints = querypoint.dependentQuerypoints;
+                        for (var i=0 ; i<dependentQuerypoints.length; i++){
+                            this.disableQuerypoint(dependentQuerypoints[i]);
+                        }
+                    }
                 },
 
                 getLastQuerypoint: function()

### 2010-12-02 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/concept/querypoint.js

@@ -13,7 +13,7 @@ with (Lang){
             var constructor = function(id, queryType, refQuerypoint, refQueryExpr, url, lineNo, hitCount, breakable, breakEnabled){
                 this.id = id;
                 this.queryType = queryType;
-
+                this.enabled = false;
                 //lastCondition && //lastChange
                 // ref point object
                 this.refQuerypoint = refQuerypoint;
@@ -39,6 +39,15 @@ with (Lang){
             };
 
             constructor.prototype = {
+
+                isEnabled: function(){
+                    return this.enabled;
+                },
+
+                setEnabled: function(enabled){
+                    this.enabled = enabled;
+                },
+
                 addQueryExpr : function(queryExpr){
                     this.queryExprList.push(queryExpr);
                     return queryExpr;

### 2010-12-02 qp-fbug/qp-fbug-0.1/src/chrome/content/concept/debugsession.js
Only the active path of querypoints from a reproduction point is shown.

@@ -84,10 +84,11 @@ var __owner = QPFBUG.Classes;
             },
 
             getNumberOfQuerypoints: function(){
-                return this.debugModel.querypointsSize;
+                return this.debugModel.enabledQuerypointsSize;
             },
 
-            needsAnotherReproduction: function(){ //todo it only works for one reproduction point
+            needsAnotherReproduction: function(){
+                //todo numberOfQuerypoints is the total number of querypoints. It is only used for recognizing a new querypoint. It should be changed.
                 if (this.reproduction.numberOfQuerypoints == this.reproduction.previousReproduction.numberOfQuerypoints) //if there is no new querypoint
                     return false;
                 if (this.getNumberOfQuerypoints() === this.reproduction.trace.assignedTracepointsSize)// todo
@@ -104,10 +105,11 @@ var __owner = QPFBUG.Classes;
             },
 
             moreQuerypointsToFind: function(){
-                return (this.debugModel.querypointsSize > this.reproduction.trace.assignedTracepointsSize);
+                return (this.debugModel.enabledQuerypointsSize > this.reproduction.trace.assignedTracepointsSize);
             },
 
             moreReproductionPointsToFind: function(){
+                //todo change it to enabled breeakpoint querypoints . Currently all breakpoint querypoints are enabled so it doesn't cause any problem.
                 return (this.debugModel.breakpoint_querypointsSize > this.reproduction.trace.assignedBreakpointTracepointsSize);
             },
 

### 2010-12-02 qp-fbug/qp-fbug-0.1/src/chrome/content/core/manager.js

@@ -138,6 +138,10 @@ with (Lang){
                 var querypoints = context.qpfbug.debugSession.debugModel.querypoints;
                 for (var i in querypoints){
                     var querypoint = querypoints[i];
+
+                    if (!querypoint.isEnabled())
+                        continue;
+
                     var eventRequest = null;
 
                     if (querypoint.queryType == DebugModel.QUERY_TYPES.BREAKPOINT){
@@ -199,13 +203,14 @@ with (Lang){
                 var querypoint = eventRequest.querypoint;
 
                 this.collectData(context, querypoint, eventId, frame);
-                if (context.qpfbug.debugSession.needsAnotherReproduction()){   //todo: && there is no more reproduction point to visit
-                    this.replay(context, reproduction.targetQuerypoint);
-                }else if(!context.qpfbug.debugSession.moreReproductionPointsToFind()){
-                    //show new found querypoints
-                    context.qpfbug.newResults = true;
-                    context.qpfbug.breakEnabled = true;
-                }
+                if (!context.qpfbug.debugSession.moreReproductionPointsToFind())
+                    if (context.qpfbug.debugSession.needsAnotherReproduction()){   
+                        this.replay(context, reproduction.targetQuerypoint);
+                    }else {
+                        //show new found querypoints
+                        context.qpfbug.newResults = true;
+                        context.qpfbug.breakEnabled = true;
+                    }
             },
 
             //------------------------------- actions ---------------------------------------
@@ -216,6 +221,7 @@ with (Lang){
 
                 //todo set the correct frame number
                 var querypointB = debugModel.addQuerypoint_LastChange(querypoint, 0, propertyPath);
+                debugModel.enableQuerypoint(querypointB);
 
                 //todo move this tag to another place
                 context.qpfbug.newResults = true;
@@ -241,9 +247,11 @@ with (Lang){
                 {
                     //todo set the correct hit count + steps (in, over, out)
                     querypoint = debugModel.addQuerypoint_Breakpoint(href, line, 0);
+                    debugModel.enableQuerypoint(querypoint);
 
                     //todo set the correct frame number
                     var querypointB = debugModel.addQuerypoint_LastChange(querypoint, 0, propertyPath);
+                    debugModel.enableQuerypoint(querypointB);
 
                     //todo move this tag to another place
                     context.qpfbug.newResults = true;

### 2010-12-03 trunk/qp-fbug/qp-fbug-0.1/src/chrome/content/ui/querypoints.js
QP tab lable is changed to Querypoints. If there is no result a message apears.

@@ -53,6 +53,15 @@ Firebug.Querypoint.QPModule = extend(Firebug.ActivableModule,
         {
 //            context.qpfbug.inSession = true;  // I don't know how we will get out of this state
             Firebug.chrome.selectSupportingPanel(UIUtils.getDebugModel(context), context, true);
+
+            var targetQuerypoint = UIUtils.getReproduction(context).targetQuerypoint;
+            var tp;
+            if (targetQuerypoint){
+                tp = UIUtils.getTracepointByQuerypoint(context, targetQuerypoint);
+                if (!tp)
+                    alert("No result for the last change of '" + targetQuerypoint.refQueryExpr.expr + "' has been found!");
+            }
+
             delete context.qpfbug.newResults;
         }
     },
@@ -99,7 +108,7 @@ Firebug.Querypoint.QPSourceViewPanel = function QPSourceViewPanel() {};
 Firebug.Querypoint.QPSourceViewPanel.prototype = extend(Firebug.SourceBoxPanel,
 {
     name: "tracepoints",
-    title: "QP",
+    title: "Querypoints",
     parentPanel: null,
     breakable: false,
     enableA11y: true,
@@ -309,10 +318,11 @@ Firebug.Querypoint.QPSourceViewPanel.prototype = extend(Firebug.SourceBoxPanel,
 
         var targetQuerypoint = UIUtils.getReproduction(this.context).targetQuerypoint;
         var tp;
-        if (targetQuerypoint)
-             tp = UIUtils.getTracepointByQuerypoint(this.context, targetQuerypoint);
-        if (tp)
-             return tp;
+        if (targetQuerypoint){
+            tp = UIUtils.getTracepointByQuerypoint(this.context, targetQuerypoint);
+            if (tp)
+                return tp;
+        }
 
         var list = this.getLocationList()
         if (list){

### 2010-12-06 trunk/papers/ecoop2011/ecoop2011-lastChange.tex
updates to pp.
updates to first 3 sections.

--- 2010-11-23 papers/ecoop2011/ecoop2011-lastChange.tex
@@
 % a short form should be given in case it is too long for the running head
-\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}
+\titlerunning{Debugging by \textit{lastChange}}
 
@@
 
-%           {\{salman.mirghasemi,claude.petitpierre\}@epfl.ch}
-
-%\authorinfo{Salman Mirghasemi}
-%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
-%           {salman.mirghasemi@epfl.ch}
-
-%\authorinfo{John J. Barton}
-%           {IBM Research - Almaden}
-%           {johnjbarton@johnjbarton.com}
-
-%\authorinfo{Claude Petitpierre}
-%           {Ecole Polytechnique F\'ed\'erale de Lausanne}
-%           {claude.petitpierre@epfl.ch}
-
 \author{Salman Mirghasemi\inst{1} \and John J. Barton\inst{2} \and Claude Petitpierre\inst{1}}
@@
 breakpoint- or log- based debuggers demands persistence and
-significant experience with the application being debugged. We propose a new 
-practical technique called \textit{lastChange}, which automatically
-locates the last point that a variable or an object property was changed and provides related
-information such as the call stack and program state. Starting from a
+significant experience with the application being debugged.
+
+We introduce a new practical functionality in debuggers called \textit{lastChange}, 
+which automatically locates the last point that a variable or an object property 
+has been changed and provides related information such as the call stack and program state. Starting from a 
 program halted on a breakpoint, the \textit{lastChange} solution
@@
 other replay-based approaches which require exactly the same
-re-executions (fully deterministic), \textit{lastChange} only requires \textit{bug 
+re-executions (deterministic executions), \textit{lastChange} only requires \textit{bug 
 reproducibility}, a test case is available which reproduces the bug.
@@
 According to \cite{LaToza}, developers spend about fifty percent of
-their time debugging. Trial and error, guess-work, and analyzing large
-and complicated data make debugging difficult and time-consuming. To fix 
-a bug, developers typically reproduce and monitor the buggy execution several 
-times to understand the program's unexpected behavior. Therefore, any
-enhancement to debugging techniques and tools which automates or facilitates developers' actions
-on execution traces, can save developers' time, reduce development costs and improve programs' quality.
+their time debugging. To fix a bug, developers typically reproduce 
+and monitor the buggy execution several times to understand the 
+program's unexpected behavior. Trial and error, guess-work, and 
+analyzing large and complicated data make debugging difficult and time-consuming. 
+Therefore, enhancements to debugging techniques and tools which automate 
+or facilitate developers' actions on execution trace, can save developers' 
+time which consequently lead to development costs reduction and programs' 
+quality improvement.
 
@@
 from that point. The technique builds on existing breakpoint debugger
-technology. We demonstrate the feasibility of the approach with
-\textit{Querypoint}, an implementation extending the Firebug
+technology. We demonstrate the feasibility of the approach with %TODO
+\textit{Querypoint}, an implementation extending Firebug
 JavaScript debugger. \textit{Querypoint} also provides mechanism for
@@
 interesting, and what they do in practice may cause bugs.
+
+By browsing through the code, the developer can quickly determine that the value displayed on the 
+button is set at line 22. To start debugging, the developer sets a breakpoint
+on line 22. Once the button is clicked, execution is paused at line
+22. Figure~\ref{fig:example1} shows the Firebug debugger while the
+execution is paused. Firebug has several panels (e.g., HTML, CSS,
+Script, DOM, etc.) that each demonstrate one aspect of the Web page.
+The Script panel contains the list of all loaded source
+files and regular debugging facilities such as setting breakpoints and
+stepping. To the right of the script panel, the Watch panel shows the program state
+where the developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
+
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin of the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find all possible places that
+\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these alias or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
 
@@
 
-By browsing through the code, the developer can quickly determine that the value displayed on the 
-button is set at line 22. To start debugging, the developer sets a breakpoint
-on line 22. Once the button is clicked, execution is paused at line
-22. Figure~\ref{fig:example1} shows the Firebug debugger while the
-execution is paused. Firebug has several panels (e.g., HTML, CSS,
-Script, DOM, etc.) that each demonstrate one aspect of the Web page.
-The Script panel contains the list of all loaded source
-files and regular debugging facilities such as setting breakpoints and
-stepping. To the right of the script panel, the Watch panel shows the program state
-where the developer can examine object and variable values. In our case, the
-\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
-
-To apply backward search strategy for locating defects, the developer
-first needs to know the origin of the wrong value. To achieve this
-goal using breakpoints, the developer should search code to find all possible places that
-\texttt{myObject.myProperty} might get a new value and set breakpoint at these locations. However, an
-object and property can be accessed and changed through different
-names and methods. There is no simple way to identify these alias or
-even their total number.  The developer can make a good guess and set
-breakpoints on lines where the property seems to be changed. Then they
-re-execute the program and examine the state looking for values that
-may lead to the incorrect value observed at line 22. All this work
-must be repeated if a new alias is discovered or if some
-information related to the buggy result was missed while stopped on
-one of the breakpoints.
-
 In contrast, we have added a high-level function in debugger,
@@
 
-\begin{figure*}[htp]
-
-\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
-  panel is selected; it gives access to
-  all loaded source files and allows breakpoints to be set on lines. In this
-  figure, the execution is paused at line 22 by a regular
-  breakpoint. The Watch panel at the right shows the program state at
-  the paused
-  point.
-Developer can query \textit{lastChange} on a \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
-  ]{1-bp22.jpg}}
-
-%\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
-%on the
-%  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
-%    height=.17\textheight]{2-bp22-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myObject.myProperty}. The left panel, QP, shows the source
-  code at the point of \textit{lastChange}; The right panel,
-  TraceData, shows the collected data at the
-  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
-  ]{3-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
-  enter the expression in the watch box and after re-execution the result is available.
-  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
-  the list shows the corresponding code and
-  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
-    ]{4-lastChange2.jpg}}
-
-\caption{The stages of locating the defect using \textit{lastChange} feature.}
-\label{fig:lastChange}
-\end{figure*}
-
-\begin{figure}[htp]
-\includegraphics{5-example-points.jpg}
-\caption{The examined points before locating the defect.
-The arrow represents the logical forward progress of the program.
-Three actual executions are superimposed on this arrow.
-All three stop at the reproduction point indicated by the circle 1.
-After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
-After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
-\label{fig:example-points}
-\end{figure}
-
 As demonstrated in Figure ~\ref{fig:example-points}, the developer has
@@
 
+\begin{figure*}[htp]
+
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel at the right shows the program state at
+  the paused
+  point.
+Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
+  ]{1-bp22.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
+  ]{3-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
+  enter the expression in the watch box and after re-execution the result is available.
+  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
+    ]{4-lastChange2.jpg}}
+
+\caption{The stages of locating the defect using \textit{lastChange} feature.}
+\label{fig:lastChange}
+\end{figure*}
+
+\begin{figure}[htp]
+\centering
+
+\includegraphics{5-example-points.jpg}
+\caption{The examined points before locating the defect.
+The arrow represents the logical forward progress of the program.
+Three actual executions are superimposed on this arrow.
+All three stop at the reproduction point indicated by the circle 1.
+After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
+After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
+\label{fig:example-points}
+\end{figure}
+
 \section{\textit{lastChange} Algorithm}
@@
 is defined at \textit{R}. If we name the result of this query
-\textit{A}, we can write the second \textit{lastChange} in this form:
-\textit{lastChange(A, myCondition.value)}. In this way, a sequence of
+\textit{L}, we can write the second \textit{lastChange} in this form:
+\textit{lastChange(L, myCondition.value)}. In this way, a sequence of
 \textit{lastChange} queries with any length can be defined.
@@
 \begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
+\centering 
+\includegraphics[height=.2\textheight]{6-foo-changes1.jpg} 
 \caption{The list of property \texttt{foo} change events and
@@
 variable in the frame comes from one of the scopes in the frame's
-scope chain. Once a developer asks for the last change of a variable with name 
+scope chain. Once the developer asks for the last change of a variable with name 
 \texttt{foo} at the reproduction point, the debugger first determines the
@@
 
-\begin{figure}[htp]
-\begin{verbatim}
-
-  function f(){
-    var x = 0;
-    x++;
-    if (!stop) f();
-  }
-
-Sample Trace:
-
-   f()
-A  |  x changes, scope 1 
-   |  f()
-   |  |  x changes, scope 2
-   |  |  f()
-B  |  |  |  x changes, scope 3 
-C  |  ... , scope 1
-
-\end{verbatim}
-\caption{A recursive call trace demonstrates the need for scope
-  id. In the absence of scope id, querying \textit{lastChange} on \texttt{x}
-  at point C in scope 1 returns point B which is the last change of variable 
-  \texttt{x} but happens in another scope. However, the right answer is point A
-  which is in the same scope as point C.}
-\label{fig:recursive}
-\end{figure}
-
 \subsubsection{global and \texttt{with} scopes}
@@
 global variable is a property of global object. Similarly,
- \texttt{with} scopes are also regular objects. A \texttt{with}
+ \texttt{with} scopes are also regular JavaScript objects. A \texttt{with}
 scope is created by a \texttt{with()} block with an object as the
@@
 given a callback function, a code block and a variable name-which is defined inside the block, the function is called
-whenever the variable is changed. Figure ~\ref{fig:recursive} demonstrates a case in which the same syntactically variable
+whenever the variable is changed.
+
+\begin{figure}[htp]
+\begin{verbatim}
+
+  function f(){
+    var x = 0;
+    x++;
+    if (!stop) f();
+  }
+
+Sample Trace:
+
+   f()
+A  |  x changes, scope 1 
+   |  f()
+   |  |  x changes, scope 2
+   |  |  f()
+B  |  |  |  x changes, scope 3 
+C  |  ... , scope 1
+
+\end{verbatim}
+\caption{A recursive call trace demonstrates the need for scope
+  id. In the absence of scope id, querying \textit{lastChange} on \texttt{x}
+  at point C in scope 1 returns point B which is the last change of variable 
+  \texttt{x} but happens in another scope. However, the right answer is point A
+  which is in the same scope as point C.}
+\label{fig:recursive}
+\end{figure}
+
+Figure ~\ref{fig:recursive} demonstrates a case in which the same syntactically variable
 \texttt{x} is changed several times but in different scopes due to the
@@
 reproduction point in a program, debugger calls 
-\texttt{setVariableChang-} \texttt{eHook()} with the variable's defining
+\texttt{setVariableChangeHook()} with the variable's defining
 block and name as parameters and re-executes the
@@
 \begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
+\centering 
+\includegraphics[height=.12\textheight]{7-foo-changes2.jpg}
 \caption{The list of variable \texttt{foo} change events and the
@@
 
-To address this issue, we use Algorithm \ref{dependency-analysis}, to
+To address this issue, we perform dependency analysis (Figure~\ref{fig:dependency-analysis}), to
 create the list of additional data (object id or scope id) should be collected at a change
@@
 
-\begin{algorithm}
-\caption{\textit{lastChange} queries dependency analysis.}
-\label{dependency-analysis}
+\begin{figure}[htp]
+\centering 
+%\begin{algorithm}
 \begin{algorithmic}
@@
 \end{algorithmic}
-\end{algorithm}
+%\end{algorithm}
+\caption{\textit{lastChange} queries dependency analysis.}
+\label{fig:dependency-analysis}
+\end{figure}
 
 \begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
+\centering 
+\includegraphics[height=.3\textheight]{8-lastchange-lastchange.jpg}
 \caption{The list of change events stored for locating point B, the

### 2010-12-06 trunk/papers/ecoop2011/ecoop2011-lastChange.tex
updates to sections 4 and 5.

@@
 of global object properties. At the beginning of execution, no object
-excepting the global object is available.  For 
-the our \textit{lastChange} prototype we created a version of
+excepting the global object and its predefined properties is available.  For 
+our \textit{lastChange} prototype we created a version of
 \texttt{setPropertyChangeHook()}.  The basic strategy is to get a reference to the object just
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object. Setting a flag\footnote[2]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox %\cite{JSD}
+property changes in the object. Setting off a flag\footnote[2]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
 JavaScript engine we can get file URL and line number for each object
@@
 
-There is another case for new objects and when they are passed as
+There is another case for new objects where they are passed as
 arguments to other functions (Figure~\ref{fig:objectCreation}(c)). In these
@@
 Although this approach is successful in many ordinary cases, there are some 
-cases where this approach doesn't work. For example in a case
+cases that a more comprehensive analysis needed for correct behaviour. For example in a case
 where the new object is assigned to \texttt{a[++i]} where i is a variable
@@
 \end{verbatim}
-\caption{Examples of three types of JavaScript object creatin statements.}
+\caption{Examples of different cases for getting references to created JavaScript objects.}
 \label{fig:objectCreation}
@@
 is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
-function \texttt{eval()}. For example, executing \texttt{eval( var \_scopeId = 10)} creates a
+function \texttt{eval()}. For example, executing \texttt{eval("var \_scopeId = 10")} creates a
 variable with name \texttt{\_scopeId} and value \texttt{10} in the
@@
 the program during the execution. \textit{Querypoint} supports two mechanism
-for automatic re-execution: local-reproduction, record-replay. The first one,
+for automatic re-execution: local-reproduction and record-replay. The first one,
 recalls the function at the bottom of the call stack with the same parameters. The idea
@@
 for the \textit{lastChange} of \texttt{a} at breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
-and \texttt{b} is \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
+and \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
 result shows line 10, which is a correct answer for this execution but not for the previous one.
@@
 in the history of change events. This condition obviously works for deterministic 
-executions. Therefore, if developer specifies an execution determinitic, every lastChange
+executions. Therefore, if developer specifies an execution deterministic, every lastChange
 will become pausable. Moroever, it works in a non-deterministic execution if non-determinism

### 2010-12-07 trunk/papers/ecoop2011/ecoop2011-lastChange.tex
edits towards final

@@
 significant experience with the application being debugged. 
-
-We introduce a new practical functionality in debuggers called \textit{lastChange}, 
+We introduce a new, practical feature for debuggers called \textit{lastChange}, 
 which automatically locates the last point that a variable or an object property 
-has been changed and provides related information such as the call stack and program state. Starting from a 
+has been changed. Starting from a 
 program halted on a breakpoint, the \textit{lastChange} solution
-applies queries to the live program during re-execution. Thus
+applies queries to the live program during re-execution, recording the call stack 
+and limited program state each time the property value changes.
+When the program halts again on the breakpoint, the recorded information 
+can be shown to the developer.
+As a proof of this concept, we developed \textit{Querypoint}, a prototype
+which enhances the popular Firebug JavaScript debugger with
+ the \textit{lastChange} feature and studied users applying the prototype to 
+some simple test cases.
+ The approach used in implementing 
 \textit{lastChange} combines the flexibility of breakpoint debugging
@@
 other replay-based approaches which require exactly the same
-re-executions (deterministic executions), \textit{lastChange} only requires \textit{bug 
-reproducibility}, a test case is available which reproduces the bug.
-
-%TODO these paragraph should contain the summary of evaluation results.
-As a proof of concept, we developed \textit{Querypoint}, a prototype
-which enhances a popular JavaScript debugger, Firebug, with
-\textit{lastChange} feature. Moreover, \textit{Querypoint} provides
-mechanisms for automated bug reproduction, and a novel user interface
-to investigated execution points and results.
+re-executions (deterministic executions), our new approach only requires \textit{bug 
+reproducibility}, that is a test case is available which reproduces the bug.
 
@@
 \includegraphics[height=.2\textheight]{6-foo-changes1.jpg} 
-\caption{The list of property \texttt{foo} change events and
-  \texttt{bar} id at the reproduction point which identifies the last
-  change of \texttt{bar.foo} in the list. Column 3 is also a change of
+\caption{A hypothetical list of  change events for a property \texttt{foo}. 
+Each change event adds a column with the id of the object changed, the call stack,
+and some program state such as local variable values. 
+At the reproduction point  we determine which id  corresponds to 
+object \texttt{bar} and read out column 4,  the last
+  change of \texttt{bar.foo}. Column 3 is also a change of
   the object we want to study, id 1010, but it is not the last change;
@@
 \subsection{Pausing at \textit{lastChange} Result}
+\label{sec:pausing}
 A \textit{lastChange} result can be recognized early when it occurs if it can
@@
 
-%\subsection{Reproduction point}
-
-\section{Evaluation}
-%To verify that lastChange can be effective we performed a small study of developers debugging with and without lastChange.
-Our goal is small, only to show that one aspect of debugging, the determination the causes of incorrect values, can be improved.
-The broader impact of lastChange on the total debugging process will have to wait for implementation of the functions described in section XX directly in a Web browser JavaScript engine.
-
-%Four experienced Javascript developers used the Firebug debugger on four small programs we provided.
-Each developer first used breakpoint debugging on two programs.
-Then we had them read sections YY - ZZ of this paper.
-Finally each developer applied the Querypoint prototype to two more programs.
-The programs were preselected so each developer saw them in a different order.
-Figure AA compares the human and computing times for these tests.
-[results]
-
-% Of course these programs were designed to highlight lastChange and all kinds of debugging issues have been hidden by the design of our tests.
-Our results show that when a defect relates to incorrect values and a developer recognizes that this, then the operational mechanics of lastChange lead to the defect much more quickly than breakpoints.
+\section{User Study}
+We supplied four experienced Javascript developers with our prototype lastChange in an 
+extended Firebug debugger. Following a tutorial and a practice case, we observed as they 
+applied both conventional breakpoint and \textit{lastChange} on two small programs we 
+provided. (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
+All four developers successfully applied \textit{lastChange} to the test programs 
+and understood how it could help debugging.
+
+We designed the example programs to require two steps of \textit{lastChange}; 
+all four users took more steps (5, 10, 10, and more than 25) to find the defect location with breakpoints.  
+To find locations for breakpoints two users scrolled through the source, 
+another searched the text, a third set a lot of breakpoints to get an understand of the control flow. 
+Based on our own experience we expect these strategies represent the kinds of approaches 
+developers have available. These operations are time consuming and tedious: all four users 
+found the defect location with just two \textit{lastChange} operations.
+Of course these programs were designed to highlight lastChange and many kinds of debugging 
+issues have been hidden by the design of our tests. Our results show that when a defect 
+relates to incorrect values and a developer recognizes that this, then the operational 
+mechanics of lastChange lead to the defect much more quickly than breakpoints.
+
+Our observation and discussions with users also brought out several important issues and improvements
+for our user interface. Perhaps the most important and challenging improvement would be better integration 
+with breakpoint debugging. Our implementation put the results of \textit{lastChange} in a similar but different
+view from breakpoint debugging. This focuses attention on value changes, but it makes studying control 
+flow more difficult: we don't support single stepping from a \textit{lastChange} result. In our next iteration we 
+plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
 
@@
 If \texttt{lastChange} could be useful, can developers figure out how
-to use it? We hope that our prototype demonstrates that
+to use it? While our user study was small , our prototype demonstrates that
 \textit{lastChange} can be easily activated by operations on the
-graphical representation of erroneous data in a debugger. Interpreting
-the results should be only slightly more difficult. We designed the
+graphical representation of erroneous data in a debugger and the 
+results can be interpreted by users. We designed the
 user interface for the results from \textit{lastChange} to resemble
@@
 believe developers can start to use \textit{lastChange} with minimal
-training. Of course developers may initially confuse the result of
-\textit{lastChange} with being halted in a debugger at the point of
-last change. The value of the result will motivate them to clarify the
-issue.
+training. Of course our users may not be representative, but the key point here
+is that the learning curve small compared with the challenge of learning 
+breakpoint debugging in the first place.
 
@@
 
-We have described our prototype implementation in Sec. 4. A fully usable
+We have described our prototype all-JavaScript implementation in Sec. 4. It is adequate for 
+exploring the ideas and may even be usable in production. However significant 
+improvments can be made. A fully usable
 implementation would require access to the object id at the point of
@@
 \subsection{In most cases \protect\texttt{lastChange} will be much faster than current alternatives}
+
 When developers try \textit{lastChange}, will they get results fast
 enough to benefit? While we only used our prototype on toy programs,
-\textit{lastChange} seemed as fast as re-execution.  Recall that we
+\textit{lastChange} seemed as fast as breakpoint re-execution.
+But what can we say about realistic programs?
+
+Recall that we
 insert additional code through debugger callbacks, then re-execute the
@@
 variable with a given name is changed, 2) the number of places objects
-are created. (Something about the likely overhead in Firefox).
+are created. The overhead for each execution at a change event
+ depends upon the amount of data we store for each change event; 
+the overhead for object creation could be small since we only need to 
+determine if the object is one we need to watch.
+
+We implemented a
+simple and effective mechanism allowing developers to control 
+overhead: we stored data to a depth of two property accesses 
+(e.g. foo.bar.x), then placed a 're-run' button 
+in the user interface at the third level. If developers reached the 
+third level they can see more data at the cost of one more replay.
 
@@
 guess the point of last change. They must then ponder another
-breakpoint, and re-execution.
+breakpoint and re-execute. Unlike the re-execution we use to 
+optimize performance in \textit{lastChange}, 
+developers still will not know if the breakpoint they hit is the point of last change
+ or even if it is related to the change at all.
 
@@
 a permanent debugging aid.) Automatic logging as we discussion in
-\ref{sec:relatedWork} causes about one or two orders of magnitude slow down.
+\ref{sec:relatedWork} causes about one or two orders of magnitude slow down as well
+as requiring a completely different set of development tools.
 
@@
 operations. Developers face this issue with any debugger today: occasionally a
-debugger causes too much overhead to be useful for debugging. On
-balance we think \textit{lastChange} will rarely encounter these kinds
-of issues.
+debugger causes too much overhead to be useful for debugging. 
+Users \textit{lastChange} may encounter these kinds of cases, but 
+that is the nature of debugging: you need different tools for 
+different kinds of problems.
 

### 2010-12-08 papers/ecoop2011/ecoop2011-lastChange.tex
re-edit pass complete

@@
 breakpoint- or log- based debuggers demands persistence and
-significant experience with the application being debugged. We propose a new 
-practical technique called \textit{lastChange}, which automatically
-locates the last point that a variable or an object property was changed and provides related
-information such as the call stack and program state. Starting from a
+significant experience with the application being debugged. 
+We introduce a new, practical feature for debuggers called \textit{lastChange}, 
+which automatically locates the last point that a variable or an object property 
+has been changed. Starting from a 
 program halted on a breakpoint, the \textit{lastChange} solution
-applies queries to the live program during re-execution. Thus
+applies queries to the live program during re-execution, recording the call stack 
+and limited program state each time the property value changes.
+When the program halts again on the breakpoint, the recorded information 
+can be shown to the developer.
+As a proof of this concept, we developed \textit{Querypoint}, a prototype
+which enhances the popular Firebug JavaScript debugger with
+ the \textit{lastChange} feature and studied users applying the prototype to 
+some simple test cases.
+ The approach used in implementing 
 \textit{lastChange} combines the flexibility of breakpoint debugging
@@
 other replay-based approaches which require exactly the same
-re-executions (fully deterministic), \textit{lastChange} only requires \textit{bug 
-reproducibility}, a test case is available which reproduces the bug.
-
-%TODO these paragraph should contain the summary of evaluation results.
-As a proof of concept, we developed \textit{Querypoint}, a prototype
-which enhances a popular JavaScript debugger, Firebug, with
-\textit{lastChange} feature. Moreover, \textit{Querypoint} provides
-mechanisms for automated bug reproduction, and a novel user interface
-to investigated execution points and results.
+re-executions (deterministic executions), our new approach only requires \textit{bug 
+reproducibility}, that is a test case is available which reproduces the bug.
 
@@
 According to \cite{LaToza}, developers spend about fifty percent of
-their time debugging. Trial and error, guess-work, and analyzing large
-and complicated data make debugging difficult and time-consuming. To fix 
-a bug, developers typically reproduce and monitor the buggy execution several 
-times to understand the program's unexpected behavior. Therefore, any
-enhancement to debugging techniques and tools which automates or facilitates developers' actions
-on execution traces, can save developers' time, reduce development costs and improve programs' quality.
+their time debugging. To fix a bug, developers typically reproduce 
+and monitor the buggy execution several times to understand the 
+program's unexpected behavior. Trial-and-error, guess-work, and 
+analyzing complicated data make debugging difficult and time-consuming. 
+Therefore, enhancements to debugging techniques and tools which automate 
+debugging operations can save developer 
+time, reducing development costs  and impoving software quality.
 
@@
 value. It uses program re-execution similar to the practice
-in using breakpoints and log statements. Imagine a program execution 
+in using breakpoints and manually inserted log statements. 
+Imagine a program execution 
 paused on a breakpoint and the developer is
@@
 reproduces the buggy execution and collects data
-and once the execution reaches the same place (i.e., the same
+when the data field changes. Once the execution reaches the same place 
+(i.e., the same
 breakpoint hit), it pauses the execution, analyzes the collected data
@@
 
+As we detail in the Related Work section, numerous papers explore forms 
+of automatic logging of program state, augmented with queries on the log. 
+This replaces the developer time needed to 
+insert statement manually with computer time to write the voluminious logs. 
+Our approach uses semi-automatic live-execution queries: user interface 
+operations allow the developer to select queries and these queries operate on the live program during re-execution.
+
 We refer to the breakpoint used in \textit{lastChange} as the
-\textit{reproduction point}: this is a point where the developer knows
-reproduces the bug and it is the point were the \textit{lastChange}
-algorithm ends. The ability to identify this reproduction point, i.e.
+\textit{reproduction point}: this is any point where the developer knows
+the bug has been reproduced. It is also the point were each \textit{lastChange}
+algorithm cycle ends. The ability to identify this reproduction point, i.e.
  a test case and a breakpoint after the bug has appeared, is the only
@@
 interesting, and what they do in practice may cause bugs.
+
+By browsing through the code or other means\cite{Barton2010},
+ the developer determines that the value displayed on the 
+button is set at line 22. Since the displayed value is incorrect we know 
+the bug occured before we hit this line.
+To start debugging, the developer sets a breakpoint
+on line 22. Once the button is clicked, execution is paused at line
+22. Figure~\ref{fig:example1} shows the Firebug debugger while the
+execution is paused. Firebug has several panels (e.g., HTML, CSS,
+Script, DOM, etc.) that each demonstrate one aspect of the Web page.
+The Script panel contains the list of all loaded source
+files and regular debugging facilities such as setting breakpoints and
+stepping. To the right of the script panel, the Watch panel shows the program state
+where the developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
+
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin of the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find all possible places that
+\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these alias or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
 
@@
 \texttt{undefined}. The next step is to know when this property got
-this value. To do so, the developer reruns \textit{lastChange} command
+this value. To do so, the developer runs the \textit{lastChange} command
 on \texttt{myCondition.value} at this point. This re-executes the
@@
 place \texttt{oldValue} is assigned to
-\texttt{myCondition.value}. To examine \texttt{oldValue}
- at this point, developer enters it to the watch box and after re-execution the value
- is available. Now it is clear that the bug occurs because \texttt{oldValue} is
+\texttt{myCondition.value}. If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
+the debugger can notify the developer that this variable is never assigned a value.
+ Now it is clear that the bug occurs because \texttt{oldValue} is
 \texttt{undefined} once execution reaches line 25 (Figure~\ref{fig:example4}).
-
-\begin{figure*}[htp]
-
-\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
-  panel is selected; it gives access to
-  all loaded source files and allows breakpoints to be set on lines. In this
-  figure, the execution is paused at line 22 by a regular
-  breakpoint. The Watch panel at the right shows the program state at
-  the paused
-  point.
-Developer can query \textit{lastChange} on a \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
-  ]{1-bp22.jpg}}
-
-%\subfigure[Developer can query \textit{lastChange} on a value by right-clicking 
-%on the
-%  value of \texttt{myProperty}.]{\label{fig:example2}\includegraphics[width=1.0\textwidth,
-%    height=.17\textheight]{2-bp22-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myObject.myProperty}. The left panel, QP, shows the source
-  code at the point of \textit{lastChange}; The right panel,
-  TraceData, shows the collected data at the
-  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
-  ]{3-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
-  enter the expression in the watch box and after re-execution the result is available.
-  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
-  the list shows the corresponding code and
-  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
-    ]{4-lastChange2.jpg}}
-
-\caption{The stages of locating the defect using \textit{lastChange} feature.}
-\label{fig:lastChange}
-\end{figure*}
-
-\begin{figure}[htp]
-\includegraphics{5-example-points.jpg}
-\caption{The examined points before locating the defect.
-The arrow represents the logical forward progress of the program.
-Three actual executions are superimposed on this arrow.
-All three stop at the reproduction point indicated by the circle 1.
-After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
-After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
-\label{fig:example-points}
-\end{figure}
 
@@
 \texttt{undefined} value. Moreover, the source lines related to these
-points are marked with red-cycle icons.
+points are marked with red "Q" icons.
 
@@
 discuss cases were it is possible to pause at lines of \textit{lastChange}).
+
+\begin{figure*}[htp]
+
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel at the right shows the program state at
+  the paused
+  point.
+Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
+  ]{1-bp22.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
+  ]{3-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
+  enter the expression in the watch box and after re-execution the result is available.
+  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
+    ]{4-lastChange2.jpg}}
+
+\caption{The stages of locating the defect using \textit{lastChange} feature.}
+\label{fig:lastChange}
+\end{figure*}
+
+\begin{figure}[htp]
+\centering
+
+\includegraphics{5-example-points.jpg}
+\caption{The examined points before locating the defect.
+The arrow represents the logical forward progress of the program.
+Three actual executions are superimposed on this arrow.
+All three stop at the reproduction point indicated by the circle 1.
+After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
+After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
+\label{fig:example-points}
+\end{figure}
 
@@
 
-As \textit{lastChange} itself is not a different kind of \textit{breakpoint},
-all of the assumptions developers already have for breakpoints hold
-for \textit{lastChange}. In particular the re-execution is just the
-same operation developers use to debug with breakpoints. Because
-\textit{lastChange} dramatically reduces the developers work in
-setting and removing breakpoints, the re-execution step will become a
-much larger fraction of the debug time. Therefore automatic mechanisms
-for re-execution will be corresponding more valuable for debugging
-with \textit{lastChange}.
-
 As we described in the preceding section, a \textit{lastChange} query can
@@
 is defined at \textit{R}. If we name the result of this query
-\textit{A}, we can write the second \textit{lastChange} in this form:
-\textit{lastChange(A, myCondition.value)}. In this way, a sequence of
+\textit{L}, we can write the second \textit{lastChange} in this form:
+\textit{lastChange(L, myCondition.value)}. In this way, a sequence of
 \textit{lastChange} queries with any length can be defined.
 
-\textit{lastChange} can be called on two different types of values: An
-object property or a variable value. Three different variations of the
-algorithm are required, one for object property and two more depending
-upon the scope of a variable.
+\textit{lastChange} can be called on object property, on a variable value, 
+or on the results of a \textit{lastChange}. We explain each case in the following subsections.
 
@@
 name matches the string. For example, if the string is 
-\texttt{foo} so changes to \texttt{bar.foo} or \texttt{baz.foo} would
+\texttt{foo} changes to \texttt{bar.foo} or \texttt{baz.foo} would
 call the function.  The callback function receives a reference to the
-owner of \texttt{foo}. In the next section, we describe how we use
-a slightly different version of this operation which is restricted 
-to the created objects in one location instead of all objects.
+owner of \texttt{foo}.
 
@@
 frame locations, and other state values in scope at the call point. 
+Then the callback returns to continue execution. Thus the query is not 
+a breakpoint in the sense of pausing for user interaction, but breakpoint 
+technology can be used to implement the query.
 Whenever the execution reaches the reproduction point the debugger
@@
 \begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{6-foo-changes1.jpg}
-\caption{The list of property \texttt{foo} change events and
-  \texttt{bar} id at the reproduction point which identifies the last
-  change of \texttt{bar.foo} in the list. Column 3 is also a change of
+\centering 
+\includegraphics[height=.2\textheight]{6-foo-changes1.jpg} 
+\caption{A hypothetical list of  change events for a property \texttt{foo}. 
+Each change event adds a column with the id of the object changed, the call stack,
+and some program state such as local variable values. 
+At the reproduction point  we determine which id  corresponds to 
+object \texttt{bar} and read out column 4,  the last
+  change of \texttt{bar.foo}. Column 3 is also a change of
   the object we want to study, id 1010, but it is not the last change;
@@
 given a callback function, a code block and a variable name-which is defined inside the block, the function is called
-whenever the variable is changed. Figure ~\ref{fig:recursive} demonstrates a case in which the same syntactically variable
-\texttt{x} is changed several times but in different scopes due to the
-recursive calls. Without considering the scopes the last change of x
-at point \texttt{C} in scope 1 is point \texttt{B} which is a change of \texttt{x} in 
-scope 2 while the right last change is point \texttt{A}. To resolve this issue, an id
-is assigned to the scope by \texttt{ScopeId()} operation and the scope id is also stored 
-at every variable change event.
+whenever the variable is changed.
+
+\begin{figure}[htp]
+\begin{verbatim}
+
+  function f(){
+    var x = 0;
+    x++;
+    if (!stop) f();
+  }
+
+Sample Trace:
+
+   f()
+A  |  x changes, scope 1 
+   |  f()
+   |  |  x changes, scope 2
+   |  |  f()
+B  |  |  |  x changes, scope 3 
+C  |  ... , scope 1
+
+\end{verbatim}
+\caption{A recursive call trace illustrating the scope
+  id.
+The lines in the bottom half of the diagram simulate a trace of the change events for the variable \texttt{x} as the function \texttt{f()} calls itself.
+Each call creates a scope; eventually when the variable \texttt{stop} is changed by an external process we return from the recursion.
+The lines marked A, B, and C are discussed in the text.}
+\label{fig:recursive}
+\end{figure}
+
+Figure ~\ref{fig:recursive} illustrates how the \texttt{ScopeId()} operation separates instances 
+of a variable in different scopes having the same name.
+If we ask for the last change on \texttt{x} at point labeled \texttt{C} in scope with id 1, we want the change at line \texttt{A} in scope 1, not 
+the change at the line marked \texttt{B}, where a variable named \texttt{x} in scope 3 is changed.
 
@@
 \begin{figure}[htp]
-\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
-\caption{The list of variable \texttt{foo} change events and the
-  \texttt{foo}'s scope id at the reproduction point which identifies
+\centering 
+\includegraphics[height=.12\textheight]{7-foo-changes2.jpg}
+\caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
+change event the scope id returns by \texttt{ScopeId()} is recorded along with call stack and program state information. 
+   The last column having the scope id \texttt{foo} at the reproduction point indicates 
   the last change.}
@@
 \subsection{\textit{lastChange} on \textit{lastChange}}
-The algorithm we explained so far needs an enhancement to support
-cascades of \textit{lastChange}s. We first explain the issue
-and then the solution. Consider the following points:
-
+The \textit{lastChange} algorithm records changes by id (either object or scope id), then reads out the last change when we
+arrive at the reproduction point and discover the id of the requested value.
+When we perform \textit{lastChange} based on a previous \textit{lastChange} the query algorithm 
+must retain additional information. Consider the following example:
 \begin{center}
@@
  \end{center}
-According to the algorithm explained in the previous section
-the points B and C cannot be identified before reaching point
-A. That is, as execution moves through point B we cannot know it will be the point of last change until
-we reach A, and we cannot apply the simple algorithm to look for point C until we know B. 
- Therefore, all \texttt{x} change events for point B and all \texttt{y}
-change events for point C are stored. Once the execution reaches point A,
-and the exact \texttt{bar} id reveals, point B can be identified among
-the change events in the history of \texttt{x} changes. The problem
-arises in recognizing point C. To recognize point C, we need
-\texttt{baz} id at point B, but B is a past program state, and
-\texttt{baz} id has not been collected at this point.
-
-To address this issue, we use Algorithm \ref{dependency-analysis}, to
-create the list of additional data (object id or scope id) should be collected at a change
-event. This algorithm does a dependency analysis between all
-\textit{lastChange} queries and computes the list of additional data
-required to be collected at each change event. For example in the
-mentioned case, \texttt{baz} id-if it is available- should be
-collected at all points \texttt{x} changes. Having this additional
-data, \texttt{baz} id at point B, it is enough to look at the list
-of \texttt{y} changes and find the last change event with the same 
-owner id (Figure ~\ref{fig:lastchange-lastchange}).
-
-\begin{algorithm}
-\caption{\textit{lastChange} queries dependency analysis.}
-\label{dependency-analysis}
+where point A is a breakpoint, point B is the last change of the object property \texttt{bar.x} at point A, and
+point C is the last change of the object property \texttt{baz.y} at point B. 
+The object referenced by \texttt{baz} changes upon re-execution. Therefore when the developer
+asks for the last change of \texttt{baz.y}, we need to track objects named \texttt{baz}
+at changes of \texttt{bar.x} and changes to objects named \texttt{y}. Then at the reproduction point
+we need to work out which \texttt{baz} the developer wanted, then select the last change of that \texttt{baz.y}.
+Figure ~\ref{fig:lastchange-lastchange} illustrates the extra row of data tracking of \texttt{baz} objects 
+at \texttt{x} change events 
+and how the id values allow the last change of \texttt{baz.y} to be worked out.
+
+In the general case we perform dependency analysis  as outlined in 
+Figure~\ref{fig:dependency-analysis} to
+create the list of additional data (object id or scope id) to be collected at a change
+event. The process can be repeated to cascade \textit{lastChange} arbitrarily deep.
+
+\begin{figure}[htp]
+\centering 
+%\begin{algorithm}
 \begin{algorithmic}
@@
 Our prototype implementation defines our four primitive operations in JavaScript code and using techniques which are cumbersome and comparatively slow to execute.
-A professionally useful debugger would implement these primitive operations in the Javasript engine.
+However the JavaScript prototype is
+easy to explore, change, and share with others for feedback.
+  A professionally useful debugger would implement these primitive operations within the JavaScript engine.
 
@@
 otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. To assign the id to the object we 
-set the id as a regular object property. This might change
-the program behaviour due to the appearance of this property in 
-\texttt{for(property in object)} loops. \texttt{defineProperty} is a standard JavaScript
-function which is available in the next version of Firefox\footnote[1]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty}. \texttt{defineProperty} receives 
-an argument which specifies whether the property is enumerable or not. By setting the enumerable
+for each new \texttt{\_objectId} needed. This use of a regular object property  might change
+the program behaviour. For example it will apear as an extra property in 
+\texttt{for(property in object)} loops. 
+The next version of Firefox\footnote[1]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty}.
+provides an alternative via \texttt{defineProperty} a standard JavaScript
+function which receives 
+an argument specifying whether the property is enumerable or not. By setting the enumerable
 field \texttt{false} for \texttt{\_objectId}, this property will not
@@
 of global object properties. At the beginning of execution, no object
-excepting the global object is available.  For 
-the our \textit{lastChange} prototype we created a version of
+excepting the global object and its predefined properties is available.  For 
+our \textit{lastChange} prototype we created a version of
 \texttt{setPropertyChangeHook()}.  The basic strategy is to get a reference to the object just
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object. Setting a flag\footnote[2]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox %\cite{JSD}
-JavaScript engine we can get file URL and line number for each object
+property changes in the object. Setting a flag\footnote[2]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
+JavaScript engine, we can get file URL and line number for each object
 creation (e.g., myFile.js, line 24). We set a hook on this line
-and analyze the source code to determine which object was created.
+and parse the source code to determine which object was created.
 
@@
 reveals that the object has been created in different location. This time,
-debugger re-executes the program considering both locations as possible 
+prototype re-executes the program considering both locations as possible 
 object creation locations.
@@
 \subsection{\texttt{scopeId()} operation}
-The debugger sets a hook at the beginning of all code blocks needing
+The prototype sets a hook at the beginning of all code blocks needing
 a scope id. The scope id is kept as a variable with name 
@@
 
-\textit{Querypoint} keeps track of breakpoint hits and single steps. For example, 
+To replay execution, \textit{Querypoint} keeps track of breakpoint hits and single steps. For example, 
 if the developer queries \textit{lastChange} at the third hit of breakpoint \textit{b}, in
@@
 the program during the execution. \textit{Querypoint} supports two mechanism
-for automatic re-execution: local-reproduction, record-replay. The first one,
-recalls the function at the bottom of the call stack with the same parameters. The idea
-behind this mechanism is that many bugs in web pages can be reproduced by firing
-an event like clicking on a button. The second one, in the first execution, record phase, 
-stores the initial page url and captures user actions. In the replay phase, it opens
-the same url and applies user actions. The local reproduction mechanism provides
+for automatic re-execution: callstack-reproduction and record-replay. In callstack reproduction the function from
+the earliest frame of the call stack with the same parameters. The idea
+behind this mechanism is that many bugs in web pages can be reproduced by re-firing
+an event like clicking on a button. The record-replay execution uses two phases. In the record phase, it 
+stores the initial page url and the events and parameters corresponding to user actions. In the replay phase, it opens
+the same url and simulated events as if they were user actions. The local reproduction mechanism provides
 shorter re-execution cycles while the record-replay is more accurate about the
@@
 In addition to the data collected at every change event for identifying the \textit{lastChange}
-result, \textit{Querypoint} partially stores values in program state. If developer asks for 
+result, \textit{Querypoint} partially stores values in program state.
+There is a trade-off between the amount of data collected at every change event and the number of re-executions.
+If developer asks for
 some values which have not been stored, \textit{Querypoint} re-executes and collects the requested data.
-There is a trade-off between the amount of data collected at every change event and the number of re-executions. 
-By default, \textit{Querypoint} stores values up to one level depth in objects.
 
@@
 
-\subsection{Pausing at \textit{lastChange} Result}
-A \textit{lastChange} result can be recognized early when it occurs if it can
-be defined by a conditional breakpoint. A proposal for the condition is the event index
-in the history of change events. This condition obviously works for deterministic 
-executions. Therefore, if developer specifies an execution determinitic, every lastChange
-will become pausable. Moroever, it works in a non-deterministic execution if non-determinism
-has no effect on the event index. If in several executions, the \textit{lastChange} result happens at
-the same index in the list of change events, it is very likely that in the next execution, the 
-same index be the result. Debugger can propose it as a pausable point to the developer or optimizes data
-collection by focusing on this point. The correctness of this guess can be verified at the reproduction
-point.
-
-There are cases where finding the appropriate condition requires developer's knowledge.
+\subsection{Combination of \textit{lastChange} and breakpoint debugging}
+\label{sec:pausing}
+Using \textit{lastChange} a developer can work backwards on the flow of data, but sometimes bugs are more obvious when
+we watch control flow forwards. Consider for example, 
+\begin{verbatim}
+44              vector.r = Math.floor(Math.random()*5)*6;
+45              if (vector.r !== 0 && vector.r < 30);
+46                   return vector;
+\end{verbatim}
+where \textit{lastChange} shows us that \texttt{vector.r} is zero at line 44. In our user studies, developers
+wanted to single step forward from line 44. If they could do this, they may be surprised to see line 46 execute 
+even if \texttt{vector.r} is zero, directing their attention to line 45 where they can discover the errant semicolon.
+However, a \textit{lastChange} is just a query result, not a breakpoint. Under what conditions can we 
+cause the debugger to stop at the \textit{lastChange} point?
+
+In the case that the execution is deterministic, the \textit{lastChange}
+event index can be used as an index for a conditional breakpoint. 
+Moreover, this works in a non-deterministic execution if non-determinism
+has no effect on the event index.  The debugger can easily set this conditional breakpoint
+and reexecute the program. If the stream of change events differs in this re-execution the
+developer can be warned that the conditional breakpoint may not be the \textit{lastChange} point.
+However, if the stream of events is the same, we do not know that the 
+conditional breakpoint matches the last 
+change, this fact  can only verify  at the reproduction point. These theoretical concerns are not
+likely to cause significant practical problems: if the value at the conditional breakpoint is not suspcious, 
+then the developer will know to simply return to \textit{lastChange} or move on to another tactic to find the bug.
+
+There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
+to formulate a conditional breakpoint.
 Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
@@
 point which shows line 14. Although this point exists at every
-re-execution but it can not be identified by any condition excepting
-the value of item.
+re-execution but it can not be identified by an event index. A conditional breakpoint on 
+the value of the item would succeed and the developer can reason from the 
+\textit{lastChange} results to create the condition.
 
@@
 
-%\subsection{Reproduction point}
-
-\section{Evaluation}
-%To verify that lastChange can be effective we performed a small study of developers debugging with and without lastChange.
-Our goal is small, only to show that one aspect of debugging, the determination the causes of incorrect values, can be improved.
-The broader impact of lastChange on the total debugging process will have to wait for implementation of the functions described in section XX directly in a Web browser JavaScript engine.
-
-%Four experienced Javascript developers used the Firebug debugger on four small programs we provided.
-Each developer first used breakpoint debugging on two programs.
-Then we had them read sections YY - ZZ of this paper.
-Finally each developer applied the Querypoint prototype to two more programs.
-The programs were preselected so each developer saw them in a different order.
-Figure AA compares the human and computing times for these tests.
-[results]
-
-% Of course these programs were designed to highlight lastChange and all kinds of debugging issues have been hidden by the design of our tests.
-Our results show that when a defect relates to incorrect values and a developer recognizes that this, then the operational mechanics of lastChange lead to the defect much more quickly than breakpoints.
+\section{User Study}
+We supplied four experienced Javascript developers with our prototype lastChange in an 
+extended Firebug debugger. Following a tutorial and a practice case, we observed as they 
+applied both conventional breakpoint and \textit{lastChange} on two small programs we 
+provided. (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
+All four developers successfully applied \textit{lastChange} to the test programs 
+and understood how it could help debugging.
+
+We designed the example programs to require two steps of \textit{lastChange}; 
+all four users took more steps (5, 10, 10, and more than 25) to find the defect location with breakpoints.  
+To find locations for breakpoints two users scrolled through the source, 
+another searched the text, a third set a lot of breakpoints to get an understand of the control flow. 
+Based on our own experience we expect these strategies represent the kinds of approaches 
+developers have available. These operations are time consuming and tedious: all four users 
+found the defect location with just two \textit{lastChange} operations. Based on our measurements,
+this makes \textit{lastChange} about three times faster than breakpoints for the navigation from 
+the reproduction point to the defect.
+Of course these programs were designed to highlight lastChange and many kinds of debugging 
+issues have been hidden by the design of our tests. Our results show that, when a defect 
+relates to incorrect values and a developer recognizes this, then the operational 
+mechanics of lastChange lead to the defect much more quickly than breakpoints.
+
+Our observation and discussions with users also brought out several important issues and improvements
+for our user interface. Perhaps the most important and challenging improvement would be better integration 
+with breakpoint debugging. Our implementation put the results of \textit{lastChange} in a similar but different
+view from breakpoint debugging. This focuses attention on value changes, but it makes studying control 
+flow more difficult: we don't support single stepping from a \textit{lastChange} result in our user interface. In our next iteration we 
+plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
 
@@
 believe developers can start to use \textit{lastChange} with minimal
-training. Of course developers may initially confuse the result of
-\textit{lastChange} with being halted in a debugger at the point of
-last change. The value of the result will motivate them to clarify the
-issue.
+training. Of course our users may not be representative, but the key point here
+is that the learning curve small compared with the challenge of learning 
+breakpoint debugging in the first place.
+
+While \textit{lastChange} is not a breakpoint, 
+all of the assumptions developers already have for breakpoints hold
+for \textit{lastChange}. In particular the re-execution is just the
+same operation developers use to debug with breakpoints. 
+In our own experience, \textit{lastChange} dramatically reduces the work in
+setting and removing breakpoints, so work to cause re-execution  become noticable.
+Therefore automatic mechanisms
+for re-execution will be corresponding more valuable for debugging
+with \textit{lastChange}.  (Our \textit{Querypoint} prototype  
+implements a simple form of automatic 
+re-execution for both breakpoint and \textit{lastChange}).
 
@@
 operations. Developers face this issue with any debugger today: occasionally a
-debugger causes too much overhead to be useful for debugging. On
-balance we think \textit{lastChange} will rarely encounter these kinds
-of issues.
-
-%\section{Evaluation}
-%\subsection{\textit{lastChange} effectiveness}
-%\subsection{Execution overhead analysis}
-
-%If we assume that the total number of instructions in an execution is
-%$n$ and $m$ change event happens during one execution and for every
-%change event $k$ additional instructions should be executed, the
-%execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
-%and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
+debugger causes too much overhead to be useful for debugging. 
+Users \textit{lastChange} may encounter these kinds of cases, but 
+that is the nature of debugging: you need different tools for 
+different kinds of problems.
+
+\subsection{Generalizations}
+Our \textit{lastChange} algorithm can be viewed as a particular interface to a general facility. 
+The general facility replays execution, querys the runtime at points of interest during execution,
+and analyzes the result at the reproduction point. We have selected one kind of query and analysis
+that can be easily integrated in existing debuggers and explained to developers, providing automation of 
+the problem of finding the point of last change. We believe other
+kinds of queries and analysis can be invented and integrated to automate other aspects of debugging.
+Moreover, the query history analysis used to test for non-determinism here may also be the basis for
+more effective user interfaces to debugging sessions. The series of cascaded \textit{lastChange} queries becomes 
+logical path followed by the developer seeking the defect and this path may be useful if presented in effective user interfaces.
 
@@
 
-The algorithm we presented in this paper provides a way to obtain information about
-the execution state logically earlier in the control flow. This
-support resembles a mixture of replay-based and logging-based
+The algorithm we presented in this paper obtain information about
+the execution state logically earlier in the control flow by querying 
+the executioin state during replay using the technology of 
+conventional breakpoint debuggers.  This
+approach resembles the operational model of replay-based debugging 
+and the query approach of logging-based
 debugging.  Replay-based approaches capture limited data during
@@
 contrast, logging-based approaches collect enough data during
-execution to relieve developer from re-execution. Replay-based
+execution to relieve developer from re-execution, then query the data to 
+inform the developer. Replay-based
 approaches impose much less runtime overhead (about two orders of
@@
 has to re-execute the buggy execution several
-times. \textit{lastChange} functionality collects data on re-execution
-but this data is limited to the current queries of developer.
+times. \textit{lastChange} collects data on re-execution by queries
+selected by developer interaction with the debugger. Therefore we have 
+the selectivity of the replay-based approaches that improves performance, 
+but we have the flexibilty of the queries so we do not require deterministic replay.
 

### 2010-12-08 papers/ecoop2011/ecoop2011-lastChange.tex

@@
 \usepackage{algorithm}
+\usepackage{textcomp}
 
@@
 
-By browsing through the code or other means\cite{Barton2010},
+By browsing through the code or other means\cite{Barton},
  the developer determines that the value displayed on the 
@@
 \centering 
-\includegraphics[height=.2\textheight]{6-foo-changes1.jpg} 
+\includegraphics[height=.23\textheight]{6-foo-changes1.jpg} 
 \caption{A hypothetical list of  change events for a property \texttt{foo}. 
@@
 \centering 
-\includegraphics[height=.12\textheight]{7-foo-changes2.jpg}
+\includegraphics[height=.14\textheight]{7-foo-changes2.jpg}
 \caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
@@
 
-\FOR{$q$ in $lastChange queries$} 
+\FOR{$q$ in $lastChange$ queries} 
  \FOR {$p$ is defined at the $q$ result}
@@
 To verify the \textit{lastChange} algorithm we
-implemented it in an extension to the Firebug
-JavaScript debugger\cite{Firebug}. %\cite{firebug-version-1.6}. 
-Firebug itself is an extension of the Firefox browser\cite{Firefox}. %\cite{firefox-version-3.6}
+implemented\footnote[1]{http://code.google.com/p/querypoint-debugging} it in an extension to the Firebug
+JavaScript debugger\footnote[2]{http://getfirebug.com}. %\cite{Firebug}. %\cite{firebug-version-1.6}. 
+Firebug itself is an extension of the Firefox browser.%\cite{Firefox}. %\cite{firefox-version-3.6}
 The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and 
@@
 \texttt{for(property in object)} loops. 
-The next version of Firefox\footnote[1]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty}.
+The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty}.
 provides an alternative via \texttt{defineProperty} a standard JavaScript
@@
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object. Setting a flag\footnote[2]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
+property changes in the object. Setting a flag\footnote[4]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
 JavaScript engine, we can get file URL and line number for each object
@@
 We supplied four experienced Javascript developers with our prototype lastChange in an 
-extended Firebug debugger. Following a tutorial and a practice case, we observed as they 
+extended Firebug debugger\footnote[5]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
 applied both conventional breakpoint and \textit{lastChange} on two small programs we 
@@
 We designed the example programs to require two steps of \textit{lastChange}; 
-all four users took more steps (5, 10, 10, and more than 25) to find the defect location with breakpoints.  
+all four users took more steps (9, 13, 12, and more than 30) to find the defect location with breakpoints.  
 To find locations for breakpoints two users scrolled through the source, 
@@
 transformation of state values, debugging is ultimately backtracking
-to find defects in program state change.  When a developer halts a
+to find defects in program state change[].  When a developer halts a
 program on a breakpoint they have three kinds of information: a model
@@
 implementation would require access to the object id at the point of
-object creation and \texttt{setPropertyChangeHook()}. Many
-object-oriented runtimes provide object identifiers[] and some
-provide access to object creation[]. In the particular case of
-the Firefox Web browser we used for our prototype, the primary barrier
+object creation and \texttt{setPropertyChan geHook()}. Many
+object-oriented runtimes provide object identifiers and 
+provide access to object creation directly or by bytecode instrumentation\cite{JPDA}. 
+In the particular case of the Firefox Web browser we used for our prototype, the primary barrier
 to practical implementation would likely be integration with the
@@
 \begin{thebibliography}{16}
+
+\bibitem{Barton}%[Bond(2010)]
+J.J. Barton, and J. Odvarko. \newblock Dynamic and graphical web page breakpoints.
+\newblock In \emph{Conference on World Wide Web(WWW)},
+April, 2010.
+
 \bibitem{Bond}%[Bond(2007)]
@@
 
-\bibitem{Firebug}%[Firebug(2010)]
-Firebug. \newblock http://getfirebug.com.
-
-\bibitem{Firefox}%[Firefox(2010)]
-Firefox. \newblock http://www.mozilla.com.
+%\bibitem{Firebug}%[Firebug(2010)]
+%Firebug. \newblock http://getfirebug.com.
+
+%\bibitem{Firefox}%[Firefox(2010)]
+%Firefox. \newblock http://www.mozilla.com.
 
@@
 
+\bibitem{JPDA}%[JSD(2010)]
+Java Platform Debugger Architecture. \newblock http://java.sun.com/javase/technologies/ core/toolsapis/jpda.
+
 \bibitem{Ko}%[Ko(2008)]

### 2010-12-09 papers/ecoop2011/ecoop2011-lastChange.tex

@@
 % unless you accept that it will be published
-\institute{Ecole Polytechnique F\'ed\'erale de Lausanne\\
+\institute{Ecole Polytechnique F\'ed\'erale de Lausanne \\
 \path|{salman.mirghasemi,claude.petitpierre}@epfl.ch| \\
-IBM Research - Almaden \\
+\and IBM Research - Almaden \\
 \path|johnjbarton@johnjbarton.com|}
@@
 re-executions (deterministic executions), our new approach only requires \textit{bug 
-reproducibility}, that is a test case is available which reproduces the bug.
+reproducibility}, that means a test case is available which reproduces the bug.
 
@@
 prototype implementation. We discuss the effect of non-determinism on
-the \textit{lastChange} results in section 5.  %TODO update it according to new Section 6 contains an evaluation of\text{lastChange} functionality.
+the \textit{lastChange} results in section 5. The user study results 
+are presented in section 6. %TODO update it according to new Section 6 contains an evaluation of\text{lastChange} functionality.
 
@@
 \texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
-
-To apply backward search strategy for locating defects, the developer
-first needs to know the origin of the wrong value. To achieve this
-goal using breakpoints, the developer should search code to find all possible places that
-\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
-object and property can be accessed and changed through different
-names and methods. There is no simple way to identify these alias or
-even their total number.  The developer can make a good guess and set
-breakpoints on lines where the property seems to be changed. Then they
-re-execute the program and examine the state looking for values that
-may lead to the incorrect value observed at line 22. All this work
-must be repeated if a new alias is discovered or if some
-information related to the buggy result was missed while stopped on
-one of the breakpoints.
 
@@
 
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin of the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find all possible places that
+\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these aliases or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
+
 In contrast, we have added a high-level function in debugger,
@@
 the debugger at one execution point which is now past: these are
-'traces' or 'logs' of information collected during the re-execution.
+\textit{traces} or \textit{logs} of information collected during the re-execution.
 
@@
 \texttt{undefined} value. Moreover, the source lines related to these
-points are marked with red "Q" icons.
+points are marked with red \textbf{Q} icons.
+
+\begin{figure*}[htp]
+
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel at the right shows the program state at
+  the paused
+  point.
+Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
+  ]{1-bp22.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
+  ]{3-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
+  enter the expression in the watch box and after re-execution the result is available.
+  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
+    ]{4-lastChange2.jpg}}
+
+\caption{The stages of locating the defect using \textit{lastChange} feature.}
+\label{fig:lastChange}
+\end{figure*}
+
+\begin{figure}[htp]
+\centering
+
+\includegraphics{5-example-points.jpg}
+\caption{The examined points before locating the defect.
+The arrow represents the logical forward progress of the program.
+Three actual executions are superimposed on this arrow.
+All three stop at the reproduction point indicated by circle 1.
+After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
+After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
+\label{fig:example-points}
+\end{figure}
 
@@
 discuss cases were it is possible to pause at lines of \textit{lastChange}).
-
-\begin{figure*}[htp]
-
-\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
-  panel is selected; it gives access to
-  all loaded source files and allows breakpoints to be set on lines. In this
-  figure, the execution is paused at line 22 by a regular
-  breakpoint. The Watch panel at the right shows the program state at
-  the paused
-  point.
-Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
-  ]{1-bp22.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myObject.myProperty}. The left panel, QP, shows the source
-  code at the point of \textit{lastChange}; The right panel,
-  TraceData, shows the collected data at the
-  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
-  ]{3-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
-  enter the expression in the watch box and after re-execution the result is available.
-  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
-  the list shows the corresponding code and
-  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
-    ]{4-lastChange2.jpg}}
-
-\caption{The stages of locating the defect using \textit{lastChange} feature.}
-\label{fig:lastChange}
-\end{figure*}
-
-\begin{figure}[htp]
-\centering
-
-\includegraphics{5-example-points.jpg}
-\caption{The examined points before locating the defect.
-The arrow represents the logical forward progress of the program.
-Three actual executions are superimposed on this arrow.
-All three stop at the reproduction point indicated by the circle 1.
-After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
-After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
-\label{fig:example-points}
-\end{figure}
 
@@
   the object we want to study, id 1010, but it is not the last change;
-  Column 5 is also a change of a property \texttt{foo} but its not for
+  Column 5 is also a change of a property \texttt{foo} but it is not for
   the object we are interested in.}
@@
 \texttt{for(property in object)} loops. 
-The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty}.
-provides an alternative via \texttt{defineProperty} a standard JavaScript
+The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty} provides an alternative via \texttt{defineProperty} a standard JavaScript
 function which receives 
@@
 statement and one object creation in a line, there are cases that more
-than one object might be created in a line. There is no way to
+than one object might be created in a line. There is no simple way to
 recognize the interesting object among these new objects. So instead
@@
 \end{verbatim}
-\caption{Examples of different cases for getting references to created JavaScript objects.}
+\caption{Examples of different cases in getting references to created JavaScript objects.}
 \label{fig:objectCreation}
@@
 their scope; that includes the defining scope and scopes nested whithin them.
-For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
+For example in Figure ~\ref{fig:js-closure}, variable \texttt{myVar} in line 11 can only be
 changed in lines 10 to 23. Therefore, after locating the function in
@@
 ~\ref{fig:js-closure}, if the execution is paused at line 17 and the
-last change of \texttt{var1} is queried, two hooks on lines 16 and 17
+last change of \texttt{myVar} is queried, two hooks on lines 16 and 17
 will be set, but if the execution is paused at line 20 , four hooks on
 lines 11, 12, 14, 20 will be set. These two cases are different due
-the fact that \texttt{var1} in \texttt{firstChild} is a local variable
+the fact that \texttt{myVar} in \texttt{firstChild} is a local variable
 but in \texttt{secondChild} is a closure variable.
@@
 10  function parent(){
-11    var var1;
-12    var1 = ...;
+11    var myVar;
+12    myVar = ...;
 13    function myfun(){
-14      var1 = ...;
+14      myVar = ...;
 15      function firstChild(){
-16       	var var1;
-17        var1 = ...;
+16       	var myVar;
+17        myVar = ...;
 18      }  
 19      function secondChild(){
-20        var1 = ...;			      
+20        myVar = ...;			      
 21      }
@@
 for automatic re-execution: callstack-reproduction and record-replay. In callstack reproduction the function from
-the earliest frame of the call stack with the same parameters. The idea
+the earliest frame of the call stack is called with the same parameters. The idea
 behind this mechanism is that many bugs in web pages can be reproduced by re-firing
@@
 means that the defect is very unlikely to depend on the order of
-events during the execution. Conversely, if the defect depends on order of execution, 
+events during the execution. Conversely, if the defect depends on the order of execution, 
 it will likely fail to reproduce on every execution. By relying on reproducibility but 
@@
 Assume that at the first exeuction, developers sees that \texttt{a} is \texttt{true} and asks
-for the \textit{lastChange} of \texttt{a} at breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
+for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
 and \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
@@
 that the \textit{lastChange} query is made on a different value. In cases that the value is not a primitive but an object,
-the properties of the object examined by the developer are stored and compared.
+the primitive properties of the object examined by the developer are stored and compared.
 
@@
 alternatives.
+	 \item the \textit{lastChange} approach can be generalized to other queries.
 \end{enumerate}
@@
 transformation of state values, debugging is ultimately backtracking
-to find defects in program state change[].  When a developer halts a
+to find defects in program state change\cite{Zeller}.  When a developer halts a
 program on a breakpoint they have three kinds of information: a model
@@
 training. Of course our users may not be representative, but the key point here
-is that the learning curve small compared with the challenge of learning 
+is that the learning curve is small compared with the challenge of learning 
 breakpoint debugging in the first place.
@@
 to practical implementation would likely be integration with the
-increasingly sophisticated just in time compilers []. In the case of
+increasingly sophisticated just in time compilers. In the case of
 tracking variable changes, \texttt{setVariableChangeHook()} can be implemented
@@
 that added code, then analyze the log. (To be fair, the log can become
-a permanent debugging aid.) Automatic logging as we discussion in
-\ref{sec:relatedWork} causes about one or two orders of magnitude slow down as well
+a permanent debugging aid.) Automatic logging as we discuss in 
+section \ref{sec:relatedWork} causes about one or two orders of magnitude slow down as well
 as requiring a completely different set of development tools.
@@
 debugger causes too much overhead to be useful for debugging. 
-Users \textit{lastChange} may encounter these kinds of cases, but 
+The users of \textit{lastChange} may encounter these kinds of cases, but 
 that is the nature of debugging: you need different tools for 
@@
 referenced by other aliases) will be also collected. Though this
-approach incurs less runtime overhead (7 times to 115 times) in
-comparison to omniscient debuggers, it adds memory
+approach incurs less runtime overhead in
+comparison to omniscient debuggers (7 times to 115 times), it adds memory
 overhead.
 
-Origin tracking of undefined and null values employing \textit{value piggybacking} technique proposed by
+Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
 Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
-First, it is limited to undefined and null values. Second, this approach dose not return the last change
-of a null variable but the first place that the null value is originated.
+First, it is limited to \texttt{undefined} and \texttt{null} values. Second, this approach dose not return the last change
+of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
 
@@
 
-\subsubsection*{Acknowledgments.} The heading should be treated as a
-subsubsection heading and should not be assigned a number.
+%Leo (the non-det values case), other readers
+\subsubsection*{Acknowledgments.} TODO
 
@@
 
+\bibitem{Zeller}%[Pothier(2007)]
+A. Zeller. \newblock Why programs fail: A gauide to systematic debugging.
+Morgan Kaufmann (2005)
+
 \end{thebibliography}

### 2010-12-09 papers/ecoop2011/ecoop2011-lastChange.tex
fixed Salman note of 12/9

@@
  the \textit{lastChange} feature and studied users applying the prototype to 
-some simple test cases.
+some test cases.
  The approach used in implementing 
@@
 with the expressive power of log-based query debugging.  Contrary to
-other replay-based approaches which require exactly the same
+other replay-based approaches, which require exactly the same
 re-executions (deterministic executions), our new approach only requires \textit{bug 
-reproducibility}, that means a test case is available which reproduces the bug.
+reproducibility}, meaning a test case is available which reproduces the bug and a 
+way to halt execution reablity after the reproduction.
 
@@
 analyzing complicated data make debugging difficult and time-consuming. 
-Therefore, enhancements to debugging techniques and tools which automate 
-debugging operations can save developer 
+Enhancements to debugging to automate 
+debugging operations save developer 
 time, reducing development costs  and impoving software quality.
@@
 depend upon order of events during execution.
-Of course there can be rare cases where the bug is reproducible but the
+There can be rare cases where the bug is reproducible but the
 value from \textit{lastChange} is not. As in conventional breakpoint
@@
 the reproduction point to the defect.
-Of course these programs were designed to highlight lastChange and many kinds of debugging 
-issues have been hidden by the design of our tests. Our results show that, when a defect 
+(We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
+issues have been hidden by the design of our tests). Our results show that, when a defect 
 relates to incorrect values and a developer recognizes this, then the operational 
@@
 believe developers can start to use \textit{lastChange} with minimal
-training. Of course our users may not be representative, but the key point here
+training. Our users may not be representative, but the key point here
 is that the learning curve is small compared with the challenge of learning 
@@
 
-Of course breakpoints are not feasible in these cases and logging
+These are difficult issues for other techniques as well:  breakpoints are not feasible in these cases and logging
 becomes unwieldy. Since automatic logging solutions are highly tuned,

### 2010-12-10 papers/ecoop2011/ecoop2011-lastChange.tex
edited for correct layout.
updates to related work.

@@
 % unless you accept that it will be published
-\institute{Ecole Polytechnique F\'ed\'erale de Lausanne \\
+\institute{\'Ecole Polytechnique F\'ed\'erale de Lausanne \\
 \path|{salman.mirghasemi,claude.petitpierre}@epfl.ch| \\
@@
 \texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
+
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin of the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find all possible places that
+\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these aliases or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
 
@@
 
-To apply backward search strategy for locating defects, the developer
-first needs to know the origin of the wrong value. To achieve this
-goal using breakpoints, the developer should search code to find all possible places that
-\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
-object and property can be accessed and changed through different
-names and methods. There is no simple way to identify these aliases or
-even their total number.  The developer can make a good guess and set
-breakpoints on lines where the property seems to be changed. Then they
-re-execute the program and examine the state looking for values that
-may lead to the incorrect value observed at line 22. All this work
-must be repeated if a new alias is discovered or if some
-information related to the buggy result was missed while stopped on
-one of the breakpoints.
-
 In contrast, we have added a high-level function in debugger,
@@
 
+Bhansali et al. \cite{Bhansali} attempted to attack performance overhead 
+and large trace size in their time-travelling debugger, Nirvana. Nirvana 
+first collects a full compressed trace of program execution and then 
+re-simulate the execution. Their results are quite similar to omniscient 
+debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
+re-simulation.
+
 A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
@@
 %Leo (the non-det values case), other readers
-\subsubsection*{Acknowledgments.} TODO
+%\subsubsection*{Acknowledgments.} TODO
 
@@
 
-\bibitem{Barton}%[Bond(2010)]
+\bibitem{Barton}
 J.J. Barton, and J. Odvarko. \newblock Dynamic and graphical web page breakpoints.
@@
 April, 2010.
+
+\bibitem{Bhansali}
+S. Bhansali, W. Chen, S. de Jong, A. Edwards, R. Murray, M. Drini\'{c}, D. Miho\v{c}ka, J. Chau. \newblock Framework for instruction-level tracing and analysis of program executions.
+\newblock In \emph{International Conference on Virtual Execution Environments(VEE)},
+June, 2006.
 
@@
 
-\bibitem{Bond2}%[Bond(2010)]
-M.D. Bond, G.Z. Baker, S.Z. Guyer, and Z. Samuel. \newblock Breadcrumbs: efficient context sensitivity for dynamic bug detection analyses.
-\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
-June, 2010.
+%\bibitem{Bond2}%[Bond(2010)]
+%M.D. Bond, G.Z. Baker, S.Z. Guyer, and Z. Samuel. \newblock Breadcrumbs: efficient context sensitivity for dynamic bug detection analyses.
+%\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
+%June, 2010.
 

### 2010-12-13 trunk/papers/ecoop2011/ecoop2011-lastChange.tex
small correction.

@@
 % unless you accept that it will be published
-\institute{Ecole Polytechnique F\'ed\'erale de Lausanne\\
+\institute{\'Ecole Polytechnique F\'ed\'erale de Lausanne \\
 \path|{salman.mirghasemi,claude.petitpierre}@epfl.ch| \\
-IBM Research - Almaden \\
+\and IBM Research - Almaden \\
 \path|johnjbarton@johnjbarton.com|}
@@
 with the expressive power of log-based query debugging.  Contrary to
-other replay-based approaches which require exactly the same
+other replay-based approaches, which require exactly the same
 re-executions (deterministic executions), our new approach only requires \textit{bug 
-reproducibility}, that is a test case is available which reproduces the bug.
+reproducibility}, meaning a test case is available which reproduces the bug and a 
+way to halt execution reliably after the reproduction.
 
@@
 and monitor the buggy execution several times to understand the 
-program's unexpected behavior. Trial and error, guess-work, and 
-analyzing large and complicated data make debugging difficult and time-consuming. 
-Therefore, enhancements to debugging techniques and tools which automate 
-or facilitate developers' actions on execution trace, can save developers' 
-time which consequently lead to development costs reduction and programs' 
-quality improvement.
+program's unexpected behavior. Trial-and-error, guess-work, and 
+analyzing complicated data make debugging difficult and time-consuming. 
+Enhancements to debugging to automate 
+debugging operations save developer 
+time, reducing development costs  and impoving software quality.
 
@@
 
-By browsing through the code, the developer can quickly determine that the value displayed on the 
-button is set at line 22. To start debugging, the developer sets a breakpoint
+By browsing through the code or other means\cite{Barton},
+ the developer determines that the value displayed on the 
+button is set at line 22. Since the displayed value is incorrect we know 
+the bug occured before we hit this line.
+To start debugging, the developer sets a breakpoint
 on line 22. Once the button is clicked, execution is paused at line
@@
 object and property can be accessed and changed through different
-names and methods. There is no simple way to identify these alias or
+names and methods. There is no simple way to identify these aliases or
 even their total number.  The developer can make a good guess and set
@@
 place \texttt{oldValue} is assigned to
-\texttt{myCondition.value}. To examine \texttt{oldValue}
- at this point, developer enters it to the watch box and after re-execution the value
- is available. Now it is clear that the bug occurs because \texttt{oldValue} is
+\texttt{myCondition.value}. If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
+the debugger can notify the developer that this variable is never assigned a value.
+ Now it is clear that the bug occurs because \texttt{oldValue} is
 \texttt{undefined} once execution reaches line 25 (Figure~\ref{fig:example4}).
@@
 \texttt{undefined} value. Moreover, the source lines related to these
-points are marked with red-cycle icons.
+points are marked with red \textbf{Q} icons.
+
+\begin{figure*}[htp]
+
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel at the right shows the program state at
+  the paused
+  point.
+Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
+  ]{1-bp22.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
+  ]{3-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
+  enter the expression in the watch box and after re-execution the result is available.
+  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
+    ]{4-lastChange2.jpg}}
+
+\caption{The stages of locating the defect using \textit{lastChange} feature.}
+\label{fig:lastChange}
+\end{figure*}
+
+\begin{figure}[htp]
+\centering
+
+\includegraphics{5-example-points.jpg}
+\caption{The examined points before locating the defect.
+The arrow represents the logical forward progress of the program.
+Three actual executions are superimposed on this arrow.
+All three stop at the reproduction point indicated by circle 1.
+After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
+After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
+\label{fig:example-points}
+\end{figure}
 
@@
 
-\textit{lastChange} can be called on two different types of values: An
-object property or a variable value. Three different variations of the
-algorithm are required, one for object property and two more depending
-upon the scope of a variable.
+\textit{lastChange} can be called on object property, on a variable value, 
+or on the results of a \textit{lastChange}. We explain each case in the following subsections.
 
@@
 \end{verbatim}
-\caption{A recursive call trace demonstrates the need for scope
-  id. In the absence of scope id, querying \textit{lastChange} on \texttt{x}
-  at point C in scope 1 returns point B which is the last change of variable 
-  \texttt{x} but happens in another scope. However, the right answer is point A
-  which is in the same scope as point C.}
+\caption{A recursive call trace illustrating the scope
+  id.
+The lines in the bottom half of the diagram simulate a trace of the change events for the variable \texttt{x} as the function \texttt{f()} calls itself.
+Each call creates a scope; eventually when the variable \texttt{stop} is changed by an external process we return from the recursion.
+The lines marked A, B, and C are discussed in the text.}
 \label{fig:recursive}
@@
 
-Figure ~\ref{fig:recursive} demonstrates a case in which the same syntactically variable
-\texttt{x} is changed several times but in different scopes due to the
-recursive calls. Without considering the scopes the last change of x
-at point \texttt{C} in scope 1 is point \texttt{B} which is a change of \texttt{x} in 
-scope 2 while the right last change is point \texttt{A}. To resolve this issue, an id
-is assigned to the scope by \texttt{ScopeId()} operation and the scope id is also stored 
-at every variable change event.
+Figure ~\ref{fig:recursive} illustrates how the \texttt{ScopeId()} operation separates instances 
+of a variable in different scopes having the same name.
+If we ask for the last change on \texttt{x} at point labeled \texttt{C} in scope with id 1, we want the change at line \texttt{A} in scope 1, not 
+the change at the line marked \texttt{B}, where a variable named \texttt{x} in scope 3 is changed.
 
@@
 \centering 
-\includegraphics[height=.12\textheight]{7-foo-changes2.jpg}
-\caption{The list of variable \texttt{foo} change events and the
-  \texttt{foo}'s scope id at the reproduction point which identifies
+\includegraphics[height=.14\textheight]{7-foo-changes2.jpg}
+\caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
+change event the scope id returns by \texttt{ScopeId()} is recorded along with call stack and program state information. 
+   The last column having the scope id \texttt{foo} at the reproduction point indicates 
   the last change.}
@@
  \end{center}
-According to the algorithm explained in the previous section
-the points B and C cannot be identified before reaching point
-A. That is, as execution moves through point B we cannot know it will be the point of last change until
-we reach A, and we cannot apply the simple algorithm to look for point C until we know B. 
- Therefore, all \texttt{x} change events for point B and all \texttt{y}
-change events for point C are stored. Once the execution reaches point A,
-and the exact \texttt{bar} id reveals, point B can be identified among
-the change events in the history of \texttt{x} changes. The problem
-arises in recognizing point C. To recognize point C, we need
-\texttt{baz} id at point B, but B is a past program state, and
-\texttt{baz} id has not been collected at this point.
-
-To address this issue, we perform dependency analysis (Figure~\ref{fig:dependency-analysis}), to
-create the list of additional data (object id or scope id) should be collected at a change
-event. This algorithm does a dependency analysis between all
-\textit{lastChange} queries and computes the list of additional data
-required to be collected at each change event. For example in the
-mentioned case, \texttt{baz} id-if it is available- should be
-collected at all points \texttt{x} changes. Having this additional
-data, \texttt{baz} id at point B, it is enough to look at the list
-of \texttt{y} changes and find the last change event with the same 
-owner id (Figure ~\ref{fig:lastchange-lastchange}).
+where point A is a breakpoint, point B is the last change of the object property \texttt{bar.x} at point A, and
+point C is the last change of the object property \texttt{baz.y} at point B. 
+The object referenced by \texttt{baz} changes upon re-execution. Therefore when the developer
+asks for the last change of \texttt{baz.y}, we need to track objects named \texttt{baz}
+at changes of \texttt{bar.x} and changes to objects named \texttt{y}. Then at the reproduction point
+we need to work out which \texttt{baz} the developer wanted, then select the last change of that \texttt{baz.y}.
+Figure ~\ref{fig:lastchange-lastchange} illustrates the extra row of data tracking of \texttt{baz} objects 
+at \texttt{x} change events 
+and how the id values allow the last change of \texttt{baz.y} to be worked out.
+
+In the general case we perform dependency analysis  as outlined in 
+Figure~\ref{fig:dependency-analysis} to
+create the list of additional data (object id or scope id) to be collected at a change
+event. The process can be repeated to cascade \textit{lastChange} arbitrarily deep.
 
@@
 otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. To assign the id to the object we 
-set the id as a regular object property. This might change
-the program behaviour due to the appearance of this property in 
-\texttt{for(property in object)} loops. \texttt{defineProperty} is a standard JavaScript
-function which is available in the next version of Firefox\footnote[1]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty}. \texttt{defineProperty} receives 
-an argument which specifies whether the property is enumerable or not. By setting the enumerable
+for each new \texttt{\_objectId} needed. This use of a regular object property  might change
+the program behaviour. For example it will apear as an extra property in 
+\texttt{for(property in object)} loops. 
+The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty} provides an alternative via \texttt{defineProperty} a standard JavaScript
+function which receives 
+an argument specifying whether the property is enumerable or not. By setting the enumerable
 field \texttt{false} for \texttt{\_objectId}, this property will not
@@
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object. Setting off a flag\footnote[2]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
-JavaScript engine we can get file URL and line number for each object
+property changes in the object. Setting a flag\footnote[4]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
+JavaScript engine, we can get file URL and line number for each object
 creation (e.g., myFile.js, line 24). We set a hook on this line
-and analyze the source code to determine which object was created.
+and parse the source code to determine which object was created.
 
@@
 the program during the execution. \textit{Querypoint} supports two mechanism
-for automatic re-execution: local-reproduction and record-replay. The first one,
-recalls the function at the bottom of the call stack with the same parameters. The idea
-behind this mechanism is that many bugs in web pages can be reproduced by firing
-an event like clicking on a button. The second one, in the first execution, record phase, 
-stores the initial page url and captures user actions. In the replay phase, it opens
-the same url and applies user actions. The local reproduction mechanism provides
+for automatic re-execution: callstack-reproduction and record-replay. In callstack reproduction the function from
+the earliest frame of the call stack is called with the same parameters. The idea
+behind this mechanism is that many bugs in web pages can be reproduced by re-firing
+an event like clicking on a button. The record-replay execution uses two phases. In the record phase, it 
+stores the initial page url and the events and parameters corresponding to user actions. In the replay phase, it opens
+the same url and simulated events as if they were user actions. The local reproduction mechanism provides
 shorter re-execution cycles while the record-replay is more accurate about the
@@
 
-\subsection{Pausing at \textit{lastChange} Result}
+\subsection{Combination of \textit{lastChange} and breakpoint debugging}
 \label{sec:pausing}
-A \textit{lastChange} result can be recognized early when it occurs if it can
-be defined by a conditional breakpoint. A proposal for the condition is the event index
-in the history of change events. This condition obviously works for deterministic 
-executions. Therefore, if developer specifies an execution deterministic, every lastChange
-will become pausable. Moroever, it works in a non-deterministic execution if non-determinism
-has no effect on the event index. If in several executions, the \textit{lastChange} result happens at
-the same index in the list of change events, it is very likely that in the next execution, the 
-same index be the result. Debugger can propose it as a pausable point to the developer or optimizes data
-collection by focusing on this point. The correctness of this guess can be verified at the reproduction
-point.
-
-There are cases where finding the appropriate condition requires developer's knowledge.
+Using \textit{lastChange} a developer can work backwards on the flow of data, but sometimes bugs are more obvious when
+we watch control flow forwards. Consider for example, 
+\begin{verbatim}
+44              vector.r = Math.floor(Math.random()*5)*6;
+45              if (vector.r !== 0 && vector.r < 30);
+46                   return vector;
+\end{verbatim}
+where \textit{lastChange} shows us that \texttt{vector.r} is zero at line 44. In our user studies, developers
+wanted to single step forward from line 44. If they could do this, they may be surprised to see line 46 execute 
+even if \texttt{vector.r} is zero, directing their attention to line 45 where they can discover the errant semicolon.
+However, a \textit{lastChange} is just a query result, not a breakpoint. Under what conditions can we 
+cause the debugger to stop at the \textit{lastChange} point?
+
+In the case that the execution is deterministic, the \textit{lastChange}
+event index can be used as an index for a conditional breakpoint. 
+Moreover, this works in a non-deterministic execution if non-determinism
+has no effect on the event index.  The debugger can easily set this conditional breakpoint
+and reexecute the program. If the stream of change events differs in this re-execution the
+developer can be warned that the conditional breakpoint may not be the \textit{lastChange} point.
+However, if the stream of events is the same, we do not know that the 
+conditional breakpoint matches the last 
+change, this fact  can only verify  at the reproduction point. These theoretical concerns are not
+likely to cause significant practical problems: if the value at the conditional breakpoint is not suspcious, 
+then the developer will know to simply return to \textit{lastChange} or move on to another tactic to find the bug.
+
+There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
+to formulate a conditional breakpoint.
 Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
@@
 developers have available. These operations are time consuming and tedious: all four users 
-found the defect location with just two \textit{lastChange} operations.
-Of course these programs were designed to highlight lastChange and many kinds of debugging 
-issues have been hidden by the design of our tests. Our results show that when a defect 
-relates to incorrect values and a developer recognizes that this, then the operational 
+found the defect location with just two \textit{lastChange} operations. Based on our measurements,
+this makes \textit{lastChange} about three times faster than breakpoints for the navigation from 
+the reproduction point to the defect.
+(We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
+issues have been hidden by the design of our tests). Our results show that, when a defect 
+relates to incorrect values and a developer recognizes this, then the operational 
 mechanics of lastChange lead to the defect much more quickly than breakpoints.
@@
 view from breakpoint debugging. This focuses attention on value changes, but it makes studying control 
-flow more difficult: we don't support single stepping from a \textit{lastChange} result. In our next iteration we 
+flow more difficult: we don't support single stepping from a \textit{lastChange} result in our user interface. In our next iteration we 
 plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
@@
 transformation of state values, debugging is ultimately backtracking
-to find defects in program state change.  When a developer halts a
+to find defects in program state change\cite{Zeller}.  When a developer halts a
 program on a breakpoint they have three kinds of information: a model
@@
 believe developers can start to use \textit{lastChange} with minimal
-training. Of course our users may not be representative, but the key point here
-is that the learning curve small compared with the challenge of learning 
+training. Our users may not be representative, but the key point here
+is that the learning curve is small compared with the challenge of learning 
 breakpoint debugging in the first place.
+
+While \textit{lastChange} is not a breakpoint, 
+all of the assumptions developers already have for breakpoints hold
+for \textit{lastChange}. In particular the re-execution is just the
+same operation developers use to debug with breakpoints. 
+In our own experience, \textit{lastChange} dramatically reduces the work in
+setting and removing breakpoints, so work to cause re-execution  become noticable.
+Therefore automatic mechanisms
+for re-execution will be corresponding more valuable for debugging
+with \textit{lastChange}.  (Our \textit{Querypoint} prototype  
+implements a simple form of automatic 
+re-execution for both breakpoint and \textit{lastChange}).
 
@@
 implementation would require access to the object id at the point of
-object creation and \texttt{setPropertyChangeHook()}. Many
-object-oriented runtimes provide object identifiers[] and some
-provide access to object creation[]. In the particular case of
-the Firefox Web browser we used for our prototype, the primary barrier
+object creation and \texttt{setPropertyChan geHook()}. Many
+object-oriented runtimes provide object identifiers and 
+provide access to object creation directly or by bytecode instrumentation\cite{JPDA}. 
+In the particular case of the Firefox Web browser we used for our prototype, the primary barrier
 to practical implementation would likely be integration with the
-increasingly sophisticated just in time compilers []. In the case of
+increasingly sophisticated just in time compilers. In the case of
 tracking variable changes, \texttt{setVariableChangeHook()} can be implemented
@@
 
-%\section{Evaluation}
-%\subsection{\textit{lastChange} effectiveness}
-%\subsection{Execution overhead analysis}
-
-%If we assume that the total number of instructions in an execution is
-%$n$ and $m$ change event happens during one execution and for every
-%change event $k$ additional instructions should be executed, the
-%execution overhead of our approach is $mk/n$. For $m=10^3$, $k=10^2$
-%and $n=10^{10}$ the overhead is very low and about $10^{-5}$.
+\subsection{Generalizations}
+Our \textit{lastChange} algorithm can be viewed as a particular interface to a general facility. 
+The general facility replays execution, querys the runtime at points of interest during execution,
+and analyzes the result at the reproduction point. We have selected one kind of query and analysis
+that can be easily integrated in existing debuggers and explained to developers, providing automation of 
+the problem of finding the point of last change. We believe other
+kinds of queries and analysis can be invented and integrated to automate other aspects of debugging.
+Moreover, the query history analysis used to test for non-determinism here may also be the basis for
+more effective user interfaces to debugging sessions. The series of cascaded \textit{lastChange} queries becomes 
+logical path followed by the developer seeking the defect and this path may be useful if presented in effective user interfaces.
 
@@
 
-\subsubsection*{Acknowledgments.} The heading should be treated as a
-subsubsection heading and should not be assigned a number.
+%Leo (the non-det values case), other readers
+%\subsubsection*{Acknowledgments.} TODO
 
 \begin{thebibliography}{16}
+
+\bibitem{Barton}
+J.J. Barton, and J. Odvarko. \newblock Dynamic and graphical web page breakpoints.
+\newblock In \emph{Conference on World Wide Web(WWW)},
+April, 2010.
+
+\bibitem{Bhansali}
+S. Bhansali, W. Chen, S. de Jong, A. Edwards, R. Murray, M. Drini\'{c}, D. Miho\v{c}ka, J. Chau. \newblock Framework for instruction-level tracing and analysis of program executions.
+\newblock In \emph{International Conference on Virtual Execution Environments(VEE)},
+June, 2006.
+
 \bibitem{Bond}%[Bond(2007)]

### 2010-12-14 trunk/papers/ecoop2011/ecoop2011-lastChange.tex
ack is added.

@@
 \subsection{\textit{lastChange} Result Consistency}
+\label{sec:resultConsistency}
+
 Each time we re-execute a non-deterministic program, 
@@
 this makes \textit{lastChange} about three times faster than breakpoints for the navigation from 
-the reproduction point to the defect.
+the reproduction point to the defect
 (We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
@@
 transformation of state values, debugging is ultimately backtracking
-to find defects in program state change\cite{Zeller}.  When a developer halts a
+to find defects in program state change\cite{Weiser,Zeller}.  When a developer halts a
 program on a breakpoint they have three kinds of information: a model
@@
 
-\subsection{Developers can learn to use \protect\texttt{lastChange}}
+\subsection{Developers can learn to use \protect\textit{lastChange}}
 
@@
 
-\subsection{In most cases \protect\texttt{lastChange} will be much faster than current alternatives}
+\subsection{In most cases \protect\textit{lastChange} will be much faster than current alternatives}
 
@@
 overhead: we stored data to a depth of two property accesses 
-(e.g. foo.bar.x), then placed a 're-run' button 
+(e.g. foo.bar.x), then placed a \textit{re-run} button 
 in the user interface at the third level. If developers reached the 
@@
 %Leo (the non-det values case), other readers
-%\subsubsection*{Acknowledgments.} TODO
+\subsubsection*{Acknowledgments.} The authors thank Leo Meyerovich for reading a draft of this paper and suggesting the example in section \ref{sec:resultConsistency} and
+Jan Odvarko and Mike Collins for testing the prototype before our user study and providing helpful suggestions.
 
@@
 
-\bibitem{Zeller}%[Pothier(2007)]
+\bibitem{Weiser}
+M. Weiser. \newblock Program slicing.
+\newblock \emph{IEEE Transactions on
+Software Engineering}, vol. SE-10, no. 4, pp. 352–357,
+July 1984.
+
+\bibitem{Zeller}
 A. Zeller. \newblock Why programs fail: A gauide to systematic debugging.

### 2010-12-21 papers/qsic2011/bare_conf.tex
new paper is added.

\documentclass[conference]{IEEEtran}

\usepackage{graphicx}
\usepackage{subfigure}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Better JavaScript Runtime Understanding by Automatic Function Naming}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Salman Mirghasemi}
\IEEEauthorblockA{\'Ecole Polytechnique F\'ed\'erale de Lausanne\\
Lausanne, Switzerland\\
salman.mirghasemi@epfl.ch}
\and
\IEEEauthorblockN{John J. Barton}
\IEEEauthorblockA{IBM Research - Almaden\\
San Jose, USA\\
johnjbarton@johnjbarton.com}
\and
\IEEEauthorblockN{Claude Petitpierre}
\IEEEauthorblockA{\'Ecole Polytechnique F\'ed\'erale de Lausanne\\
Lausanne, Switzerland\\
claude.petitpierre@epfl.ch}}
\maketitle

\begin{abstract}
%\boldmath
%Understanding runtime elments play a key role in program comprehension. In dynamic weak-typed languages like JavaScript, runtime elements are mainly concrete values that tell a little about their meta data and structure. This dynamic languages feature makes their understanding hard.
\end{abstract}

\section{Introduction}
Today JavaScript has a unique role in web programming, considered as the web assembly language. This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.It is very likely that JavaScript keeps this critical role at least for the next few years. Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing. Morover, JavaScript is also becoming a general purpose computing platform with office applications[], browsers[], server-side applications[] and development environments \cite{Ingalls} being developed in JavaScript.

JavaScript developers have to improve their develoment processes and practices to cope with these fast changes. They need modern editors for writing and editing larger programs and effective tools for understanding complicated JavaScript runtime. However, there has been severe inherent barriers for improving JavaScript tool support. 
Unlike many traditional object oriented languages such as Java and C\#, it does not have classes, and does not encourage encapsulation or even structured programming JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}. It means that the code contains less data about JavaScript elements and how they are related. For example, a variable value can be primitive values, objects with any structure or even a function. Therefore, lack of describing data in JavaScript code is a fundamental issue in enhancing tools.

Catching errors early (i.e., before or at the time of compilation) is an important feature for editors. It can saves developers' time, prevents bugs and improves the program reliability. However, many errors can not be recognized without a strong typing stystem. To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}. These approaches analyze source codes and deduce possible values and object structures based on possible program control flows lead to assignment to a variable. The discovered facts about variables are not only useful for catching errors but to provide modern editors' features such as auto-complete and refactoring.

Although the mentioned approaches are able to recognize errors or provide modern editing features by the the discovered facts about JavaScript elements, they do not have means to transform this information to the developer. For example, objects are not associated to classes in JavaScript, and no structure can be assumed by the developer.
If it is discovered that a variable value is only constructed by a specific function, this information can also be shared with the developer. The function can work like a class and gives some cue to the developer about the object structure. However, due to dynamic nature of JavaScript many elements have no identifier. Therefore, even in the cases that the constructor of an object is known, it can not be presented because the constructor has no identifier or the identifier is not recognizable for the developer.

% about JavaScript elements less explicit meta data for the code exist is available to editors and tools for program verifiction,

As a consequence, the information provided in editors and tools for JavaScript elements is usually limited and doesn't give enough hint for rapid recall to developers. 
Understanding runtime elments play a key role in program comprehension.
In dynamic weak-typed languages like JavaScript, runtime elements are
only concrete values that tell a little about their meta data and structure.
This dynamic languages feature makes their understanding hard.

%For example to know an object, developer has to examine the object properties and from the property names and values, some connections
%understanding JavaScript code and its runtime is much harder for developers.

\section{Motivation}

%___ The importance of having function names
%___ The problem in Firebug and V8 webkit
%___ related work for type system

\begin{figure*}[htp]
\centerline{
\subfigure[Firefox Firebug Debugger]{\label{fig_first_case}\includegraphics[width=.47\textwidth]{fbug-callstack.jpg}}
\hfil
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth]{chrome-callstack.jpg}}}
\caption{These two figures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
The Google Chrome debugger is unable to find three function names and The Firebug debugger fails at one case.}
\label{debuggers}
\end{figure*}

\section{The Function Naming Problem}
%___ why it is hard
%-- Check here: http://kangax.github.com/nfe/

\section{Automatic Funcation Naming}

\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.

\section{Related Work}
%Another strand of research has tried to investigate how to provide better tools for developers for catching errors early. Being a weakly typed language with no type declarations and only run-time checking of calls and field accesses, it is natural to try to provide a static type system for JavaScript [2, 1, 3, 24, 13]. Finally, after many years of neglect, modern implementations of JavaScript have started to appear which use state of the art just-in-time compilation techniques [10].

%For JavaScript, Anderson et al. proposed a type system with definite and potential types [2, 1, 3], while Heidegger and Thiemann following up on some of their earlier work [24, 18] propose recency types in [13], and Furr et al. proposed a related system for DRuby [9]. While all of these type systems acknowledge some minor simplifications to the target language, they rely on fairly similar assumptions. For instance, Thiemann writes: “Usually, no further properties are defined after the initialization and the type of the properties rarely changes.” This suggests that object types are stable at run-time and can be described using, e.g., traditional rowtypes. In fact all the proposals take the view that an object’s type should be the sum of all possible fields and methods that it could contain, with some of them being undefined; they differ mostly on how to perform strong updates to avoid polluting all properties with undefined values. Interestingly, language implementors make similar assumptions. For instance, Google’s V8 JavaScript engine is reported to optimistically associate “classes” to objects on the assumption that their shape will not change too much, though with a fallback case for highly dynamic objects 3. This design is similar to implementations of one of JavaScript’s influences, Self [5], and is expected to work for the same reasons. As the above mentioned hypothesis is crucial for the applicability and usefulness of the results, it deserves careful study. In fact, we have found a number of similar assumptions in the literature which we list below.We first review the salient features of the language to provide sufficient background for readers unfamiliar with JavaScript.

\section{Conclusion}
In this paper we presented an approach for naming JavaScript functions both
as individual objects and in call stack.

\begin{thebibliography}{10}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\bibitem{Anderson}
C. Anderson, P. Giannini, and S. Drossopoulou. \newblock Towards Type Inference for JavaScript.
\newblock In \emph{Proceedings of the 19th European conference on Object-Oriented Programming(ECOOP)},
July, 2005.

\bibitem{Anderson2}
C. Anderson and P. Giannini. \newblock Type checking for javascript.
\newblock \emph{Electr. Notes Theor. Comput. Sci.}, 138(2), 2005.

\bibitem{ECMA}
ECMA International.
\newblock \emph{ECMA-262: ECMAScript Language Specification},
ECMA (European Association for Standardizing Information
and Communication Systems), Geneva, Switzerland, third edition,
December 1999.

\bibitem{Heidegger}
P. Heidegger and P. Thiemann.\newblock Recency types for dynamically-typed, object-based languages.
\newblock In \emph{Proceedings of Foundations of Object Oriented Languages (FOOL)},
2009.

\bibitem{Ingalls}
D. Ingalls, K. Palacz, S. Uhler and A. Taivalsaari.\newblock The lively kernel a self-supporting system on
a web page.
\newblock In \emph{Self-Sustaining Systems},
2008.

\bibitem{Richards}
G. Richards, S. Lebresne, B. Burg and J. Vitek.\newblock An analysis of the dynamic behavior of JavaScript programs.
\newblock In \emph{Proceedings of the 2010 ACM SIGPLAN conference on Programming language design and implementation(PLDI)},
June, 2010.

\bibitem{Thiemann}
P. Thiemann.\newblock Towards a type system for analyzing JavaScript programs.
\newblock In \emph{Proceedings of European Symposium on Programming (ESOP)},
2005.

\end{thebibliography}

% that's all folks
\end{document}

### 2010-12-22 trunk/papers/qsic2011/bare_conf.tex
new sections are added.

--- 2010-12-21 papers/qsic2011/bare_conf.tex
@@
 
-\section{Motivation}
+\section{The Function Naming Problem}
+Figure~\ref{debuggers} shows the call stack view of two famous JavaScript debuggers, Firebug and Google Chrome , paused at the same breakpoint.
+The differences between two call stack, particularly in the first two frames, are due to different implementations of event handling in the underlying platforms.
+Google chrome shows \texttt{anonymouse} for three functions which doesn't give any useful information to the developer.
+The developer has to look at the specified source file and line number to recall the function.
+Although Firebug shows more function names, it is also unsuccessful about one function.
 
+%___ why it is hard
+%-- Check here: http://kangax.github.com/nfe/
 %___ The importance of having function names
-%___ The problem in Firebug and V8 webkit
 %___ related work for type system
@@
 
-\section{The Function Naming Problem}
-%___ why it is hard
-%-- Check here: http://kangax.github.com/nfe/
+The importance of function names is not limited only to call stack view.
+A function can be used as a constructor for creating new objects.
+The constructor name like class name in traditional languages such as Java, can be used in object representation.
+It can help developer in understanding the structure and role of object without looking into its properties.
 
@@
 
-\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
+%explain function expression and function declerations
+%moreover explain creation of the list of outer scopes.
+
+\subsection{A Global Name for a Function Object}
+
+\begin{figure}[htp]
+\begin{verbatim}
+(a) Case 1:
+ function foo(){ ... }
+
+(b) Case 2:
+ var foo = function { ... }
+
+(c) Case 3:
+ var foo = {
+     bar : function { ...}
+ }
+
+(d) Case 4:
+
+ var foo = function(){
+           ....
+           return function(){ ... }
+ }()
+
+(e) Case 5:
+ var foo = function(){ 
+ 					 return ...;
+ }()
+
+(f) Case 6:
+ var foo = function(){
+
+ }()();
+
+(g)
+ foo(function(){ ... });
+
+(h)
+ array = [...., function(){},...]
+
+(i)
+ array[i] = function(){};
+
+\end{verbatim}
+\caption{Different cases of function object creation.}
+\label{fig:functionCreation}
+\end{figure}
+
+\subsection{Naming Functions in Call Stack}
 

### 2010-12-28 trunk/papers/qsic2011/bare_conf.tex

@@
 %\boldmath
-%Understanding runtime elments play a key role in program comprehension.
-In dynamic weak-typed languages like JavaScript, runtime elements are mainly concrete values that tell a little about their meta data and structure.
-This dynamic languages feature makes their understanding hard.
+Understanding JavaScript code due to its dynamic, weakly-typed nature is complicated.
+Developers usually understand JavaScript programs by running them and examining their elements at runtime.
+However, understanding the concrete value of an element is not always straightforward.
+Among all runtime elments in JavaScript functions are more important: they are used as object constructors and apear in call stack.
+We discuss the function names usage in improving concrete values presentation.
+Morover, we propose an approach for automatic function naming in JavaScript.
 \end{abstract}
@@
 \section{Introduction}
-Today JavaScript has a unique role in web programming, considered as the web assembly language.
-This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.It is very likely that JavaScript keeps this critical role at least for the next few years.
+The unique and important role of JavaScript in web programming is undeniable.
+This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
+It is very likely that JavaScript keeps this crucial role at least for the next few years.
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
-Morover, JavaScript is also becoming a general purpose computing platform with office applications[], browsers[], server-side applications[] and development environments \cite{Ingalls} being developed in JavaScript.
+Morover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}.
+There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.
 
-JavaScript developers have to improve their develoment processes and practices to cope with these fast changes.
+To cope with the pace of changes, JavaScript developers need to improve their develoment processes and practices.
 They need modern editors for writing and editing larger programs and effective tools for understanding complicated JavaScript runtime.
@@
 Unlike many traditional object oriented languages such as Java and C\#, it does not have classes, and does not encourage encapsulation or even structured programming JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
-It means that the code contains less data about JavaScript elements and how they are related.
-For example, a variable value can be primitive values, objects with any structure or even a function.
-Therefore, lack of describing data in JavaScript code is a fundamental issue in enhancing tools.
+As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
+A variable value can be a primitive value, an object with any structure or even a function.
+One callsite may invoke different function bodies with different number of arities that none of them can be understood from the code.
+Therefore, the lack of descriptive data in JavaScript code is the most fundumental issue in enhancing JavaScript tool support.
 
-Catching errors early (i.e., before or at the time of compilation) is an important feature for editors.
-It can saves developers' time, prevents bugs and improves the program reliability.
+Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
+It can save developers' time, prevent bugs and improve the program reliability.
 However, many errors can not be recognized without a strong typing stystem.
 To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
-These approaches analyze source codes and deduce possible values and object structures based on possible program control flows lead to assignment to a variable.
-The discovered facts about variables are not only useful for catching errors but to provide modern editors' features such as auto-complete and refactoring.
+These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
+These discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
+Moreover, these infered data can help in code coprehension if they are properly presented.
+However, none of the mentioned approaches provided effective means for sharing this information with the developer.
 
-Although the mentioned approaches are able to recognize errors or provide modern editing features by the the discovered facts about JavaScript elements, they do not have means to transform this information to the developer.
-For example, objects are not associated to classes in JavaScript, and no structure can be assumed by the developer.
-If it is discovered that a variable value is only constructed by a specific function, this information can also be shared with the developer.
-The function can work like a class and gives some cue to the developer about the object structure.
-However, due to dynamic nature of JavaScript many elements have no identifier.
-Therefore, even in the cases that the constructor of an object is known, it can not be presented because the constructor has no identifier or the identifier is not recognizable for the developer.
+%talk about runtime tools
+Developers usually understand JavaScript code by examining the running program in debuggers.
+At runtime, concrete values are available and developer can directly check and understand object structures and control flows.
+However, understanding a concrete value is not always straightforward, particulary for non-primitive values such as objects and functions.
+To facilitate understanding these complex values, debuggers show a summary of these objects.
+For example, the name of object constructor must appear in its summary.
 
-% about JavaScript elements less explicit meta data for the code exist is available to editors and tools for program verifiction,
+Functions are central to program comprehension in JavaScript.
+They are first-class objects that can be used for object construction and be passed as function call arguments.
+However, there is a serious issue with JavaScript functions that makes understanding them very difficult.
+Functions can be defined and created with no identifier or name.
+A function name is important for referring and recalling the function's functionality.
+Morover, the name of an object's constructor can work like a class name and summarizes the object structure.
 
-As a consequence, the information provided in editors and tools for JavaScript elements is usually limited and doesn't give enough hint for rapid recall to developers. 
-Understanding runtime elments play a key role in program comprehension.
-In dynamic weak-typed languages like JavaScript, runtime elements are
-only concrete values that tell a little about their meta data and structure.
-This dynamic languages feature makes their understanding hard.
+In this paper, we propose an approach for automatic naming of functions in JavaScript.
+The function names can be used in debuggers for more descriptive object summaries or callstack view.
+Moreover, these function names can be used in integration with proposed JavaScript typing systems for providing modern editing features.
+
+%Many developers develop JavaScript in object-oriented way.
+%
 
@@
 %understanding JavaScript code and its runtime is much harder for developers.
-
-\section{The Function Naming Problem}
-Figure~\ref{debuggers} shows the call stack view of two famous JavaScript debuggers, Firebug and Google Chrome , paused at the same breakpoint.
-The differences between two call stack, particularly in the first two frames, are due to different implementations of event handling in the underlying platforms.
-Google chrome shows \texttt{anonymouse} for three functions which doesn't give any useful information to the developer.
-The developer has to look at the specified source file and line number to recall the function.
-Although Firebug shows more function names, it is also unsuccessful about one function.
-
-%___ why it is hard
-%-- Check here: http://kangax.github.com/nfe/
-%___ The importance of having function names
-%___ related work for type system
+% we propose automatic function naming with these features
+% 1) expected by user 2) different situations
 
@@
 \subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth]{chrome-callstack.jpg}}}
-\caption{These two figures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
+\caption{These two pictures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
 The Google Chrome debugger is unable to find three function names and The Firebug debugger fails at one case.}
@@
 
-The importance of function names is not limited only to call stack view.
-A function can be used as a constructor for creating new objects.
+\section{The Function Naming Problem}
+Figure~\ref{debuggers} shows the call stack view of Firefox Firebug and Google Chrome JavaScript debuggers, paused at the same breakpoint.
+The differences between two call stack, particularly in the first two frames, are due to different implementations of event handling in the underlying platforms.
+Google chrome shows \texttt{anonymouse} for three functions which doesn't give any useful information to the developer.
+The developer has to look at the specified source file and line number to recall the function.
+Although Firebug shows more function names, it is also unsuccessful about one function.
+
+%___ The importance of having function names
+The importance of function names is not only limited to call stack view.
+A function can be used as a constructor for constructing new objects.
 The constructor name like class name in traditional languages such as Java, can be used in object representation.
-It can help developer in understanding the structure and role of object without looking into its properties.
+It can assist developers in understanding the structure and role of the object without looking into its properties.
 
-\section{Automatic Funcation Naming}
+In JavaScript, defining \textit{identifier} for functions is optional.
+A function can be assigned to a variable or an object property with any name.
+Therefore a function object can be called by different names during in life time.
+%___ why it is hard
+
+%Many developers develop JavaScript in object-oriented way.
+%
+
+%___ related work for type system
+
+%-- Check here: http://kangax.github.com/nfe/
+%function body(source), function object
 
@@
 %moreover explain creation of the list of outer scopes.
+In JavaScrip a function can be defined by a function expression or a function decleration \cite{ECMA}.
+From the same function expression or decleration, function objects are created.
+In addition to function source code, the clousure scopes are also important for understanding the function operation.
+The clousure scopes include all available variables to the function at the time of creation.
+The location of function definition in the source code is enough for knowing the clousure scopes.
+Therefore, a function body with its location in a source code defines a category of function objects with the similar behaviour.
+Is it possible to assing a name to every function object in JavaScript in a way that:
+1) Function objects with the same code has the same name.
+2) The proposed name recalls the function for the developer.
+
+\section{Automatic Funcation Naming}
+To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
+First, assigning a global name to the function which identifies the function in the whole program.
+Second, naming a function in a call stack.
 
@@
 
+\begin{figure}[htp]
+\begin{verbatim}
+(a)
+ foo();
+(b)
+ foo.bar();
+(c)
+ foo.apply(bar, args);
+
+\end{verbatim}
+\caption{Different cases of function object creation.}
+\label{fig:functionCall}
+\end{figure}
+
 \section{Related Work}
@@
 
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
 \bibitem{Anderson}
@@
 
+\bibitem{CJS}
+Common JS.
+\newblock http://www.commonjs.org/
+
 \bibitem{ECMA}
@@
 December 1999.
+
+\bibitem{FAO}
+Firefox Add-ons.
+\newblock https://addons.mozilla.org/en-US/developers/docs/gett ing-started.
+
+\bibitem{GCE}
+Google Chrome Extensions.
+\newblock http://code.google.com/chrome/extensions.
 
@@
 
+\bibitem{JSOffice}
+JScript development in Microsoft Office 11.
+\newblock http://msdn.microsoft.com/ en-us/library/aa202668(office.11).aspx
+
+\bibitem{JSOffice2}
+JavaScript development in OpenOffice.
+\newblock http://framework.openoffice.org/ scripting/release-0.2/javascript-devguide.html
+
 \bibitem{Richards}
@@
 June, 2010.
+
+\bibitem{SSJSR}
+Server-Side JavaScript Reference v1.2.
+\newblock http://research.nihonsoft.org/ javascript/ServerReferenceJS12.
 

### 2010-12-31 papers/qsic2011/bare_conf.tex

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Better JavaScript Runtime Understanding by Automatic Function Naming}
+\title{Better JavaScript Runtime Understanding by Automated Function Name Extraction}
 
@@
 \begin{abstract}
-%\boldmath
-%Understanding runtime elments play a key role in program comprehension.
-In dynamic weak-typed languages like JavaScript, runtime elements are mainly concrete values that tell a little about their meta data and structure.
-This dynamic languages feature makes their understanding hard.
+Understanding JavaScript code due to its dynamic, weakly-typed nature is complicated.
+Developers usually understand JavaScript programs by running them and examining their elements at runtime.
+However, understanding concrete values, particularly user-defined and function objects, is not always straightforward.
+Function names can aid in this regard; they can apear as the constructor name in object representation or as the functions identifier in callstack.
+Unfortunately, a very low proportion (less than 15\%) of JavaScript functions are named.
+We propose an approach for automated function naming based on source code analysis.
+We applied our approach over two relatively large JavaScript programs.
 \end{abstract}
@@
 \section{Introduction}
-Today JavaScript has a unique role in web programming, considered as the web assembly language.
-This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.It is very likely that JavaScript keeps this critical role at least for the next few years.
+The unique and important role of JavaScript in web programming is undeniable.
+With the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
+This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
+It is very likely that JavaScript keeps this crucial role at least for the next few years.
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
-Morover, JavaScript is also becoming a general purpose computing platform with office applications[], browsers[], server-side applications[] and development environments \cite{Ingalls} being developed in JavaScript.
+Morover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}.
+There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.
 
-JavaScript developers have to improve their develoment processes and practices to cope with these fast changes.
+To cope with the pace of changes, JavaScript developers need to improve their develoment processes and practices.
 They need modern editors for writing and editing larger programs and effective tools for understanding complicated JavaScript runtime.
 However, there has been severe inherent barriers for improving JavaScript tool support.
-Unlike many traditional object oriented languages such as Java and C\#, it does not have classes, and does not encourage encapsulation or even structured programming JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
-It means that the code contains less data about JavaScript elements and how they are related.
-For example, a variable value can be primitive values, objects with any structure or even a function.
-Therefore, lack of describing data in JavaScript code is a fundamental issue in enhancing tools.
+Unlike many traditional object oriented languages such as Java and C\#, it does not have classes, and does not encourage encapsulation or even structured programming.
+JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
+As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
+A variable value can be a primitive value, an object with any structure or even a function.
+One callsite may invoke different function bodies with different number of arities that none of them can be understood from the code.
+Therefore, the lack of descriptive data in JavaScript code is the most fundumental issue in enhancing JavaScript tool support.
 
-Catching errors early (i.e., before or at the time of compilation) is an important feature for editors.
-It can saves developers' time, prevents bugs and improves the program reliability.
+Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
+It can save developers' time, prevent bugs and improve the program reliability.
 However, many errors can not be recognized without a strong typing stystem.
 To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
-These approaches analyze source codes and deduce possible values and object structures based on possible program control flows lead to assignment to a variable.
-The discovered facts about variables are not only useful for catching errors but to provide modern editors' features such as auto-complete and refactoring.
+These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
+These discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
+Moreover, these infered data can help in code coprehension if they are properly presented.
+Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
 
-Although the mentioned approaches are able to recognize errors or provide modern editing features by the the discovered facts about JavaScript elements, they do not have means to transform this information to the developer.
-For example, objects are not associated to classes in JavaScript, and no structure can be assumed by the developer.
-If it is discovered that a variable value is only constructed by a specific function, this information can also be shared with the developer.
-The function can work like a class and gives some cue to the developer about the object structure.
-However, due to dynamic nature of JavaScript many elements have no identifier.
-Therefore, even in the cases that the constructor of an object is known, it can not be presented because the constructor has no identifier or the identifier is not recognizable for the developer.
+Developers usually understand JavaScript code by examining the running program in debuggers.
+At runtime, concrete values are available and developer can directly check and understand object structures and control flows.
+Understanding a concrete value, particulary for non-primitive values such as objects and functions, is not always straightforward.
+To facilitate understanding these complex values at the first place, debuggers show a summary of these objects.
+For example, in case of user-defined objects, the name of object's constructor can be very helpful in the object summary.
+It can work like a class name and summarizes the object structure.
 
-% about JavaScript elements less explicit meta data for the code exist is available to editors and tools for program verifiction,
-
-As a consequence, the information provided in editors and tools for JavaScript elements is usually limited and doesn't give enough hint for rapid recall to developers. 
-Understanding runtime elments play a key role in program comprehension.
-In dynamic weak-typed languages like JavaScript, runtime elements are
-only concrete values that tell a little about their meta data and structure.
-This dynamic languages feature makes their understanding hard.
-
-%For example to know an object, developer has to examine the object properties and from the property names and values, some connections
-%understanding JavaScript code and its runtime is much harder for developers.
-
-\section{Motivation}
-
-%___ The importance of having function names
-%___ The problem in Firebug and V8 webkit
-%___ related work for type system
+Functions are central to program comprehension in JavaScript. They are first-class objects that are used for different purposes by developers; 
+they may be used as an object  constructor, a clousure scope(module) or even  passed as an argument in a function call.
+However, there is a subtle issue with JavaScript functions that makes working with them in debuggers quite impossible: functions can be defined and created with no name or identifier.
+The function name is necessary for referring and recalling the function's functionality, but only a small proportion(less than 15\%) of JavaScript functions are named.
 
@@
 \centerline{
-\subfigure[Firefox Firebug Debugger]{\label{fig_first_case}\includegraphics[width=.47\textwidth]{fbug-callstack.jpg}}
+\subfigure[Firefox Firebug Debugger]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.27\textheight]{fbug-objects.jpg}}
 \hfil
-\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth]{chrome-callstack.jpg}}}
-\caption{These two figures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
-The Google Chrome debugger is unable to find three function names and The Firebug debugger fails at one case.}
-\label{debuggers}
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.27\textheight]{chrome-objects.jpg}}}
+\caption{These two pictures show the variables view of Firebug and Google Chrome JavaScript debuggers paused at the same breakpoint.}
+\label{debuggers-objects}
 \end{figure*}
 
+In this paper, we propose automated JavaScript function naming based on extracted data by anaylizing the source code.
+The candidate function names can be used in debuggers for more descriptive object summaries and callstack view.
+Moreover, these function names can be used in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+
 \section{The Function Naming Problem}
+
+The importance of function names is not only limited to call stack view.
+A function can be used as a constructor for constructing new objects.
+The constructor name like class name in traditional languages such as Java, can be used in object representation.
+It can assist developers in understanding the structure and role of the object without looking into its properties.
+%function body(source), function object
+
+In JavaScript, defining \textit{identifier} for functions is optional.
+A function can be assigned to a variable or an object property with any name.
+Therefore a function object can be called by different names during in life time.
 %___ why it is hard
-%-- Check here: http://kangax.github.com/nfe/
+
+\subsection{Constructor Name}
+Figure~\ref{debuggers-objects} shows the variables view of Firefox and Google Chrome debuggers, paused at the same breakpoint.
+To know a variable value developer first check the summary value presented besides the variable name.
+If the summary value is not enough, then developer can expand the variable node to examin variable properties.
+In this case, the values of all variables are created using a constructor and the constructor name can be included in the summary.
+However, instead of the name of constructor which can hint the developer about the object structure, only \texttt{Object} is shown.
+
+%Many developers develop JavaScript in object-oriented way.
+%
+
+JavaScript is an imperative, objectoriented
+language with Java-like syntax, but unlike Java it employs
+a prototype-based object system. An object is a set of properties,
+a mutable map from strings to values. A property that evaluates
+to a closure and is called using the context of its parent object
+plays the role of a method in Java. Each object has prototype field
+which refers to another object. Property lookup involves searching
+the current object, then its parent, and its parent until the property
+is found. The JavaScript object system is extremely flexible. As a
+result, it is difficult to constrain the behavior of any given object.
+For example, it is possible to modify the contents of any prototype
+at any time or to replace a prototype field altogether. In JavaScript,
+any function can be a constructor for a “class” of objects, and
+contains a prototype field, initially referencing an empty object.
+The new keyword creates an object based on the prototype field and
+using the function as a constructor. The semantics of new is simple,
+but unusual: first, an empty object is created, with its parent set
+to the object referenced by the prototype field of the constructor
+function; second, the constructor is called, with this bound to
+the new object. The object referenced by the keyword this is not
+determined by lexical scoping, but instead by the caller; finally the
+return value from the constructor (if any) is discarded, and the new
+expression evaluates to this.%richards
+
+\subsection{Callstack View}
+Figure~\ref{debuggers-callstack} shows the call stack view of Firefox Firebug and Google Chrome JavaScript debuggers, paused at the same breakpoint.
+The differences between two call stacks, particularly in the first two frames, are due to different implementations of event handling in the underlying platforms.
+Google chrome shows \texttt{anonymouse} as the identifier for three functions which doesn't give any useful information to the developer.
+The developer has to locate the function by its source file and line number to recall the function functionality.
+Although Firebug shows more function names, it is also speechless about one function.
+
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Firefox Firebug Debugger]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{fbug-callstack.jpg}}
+\hfil
+\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{chrome-callstack.jpg}}}
+\caption{These two pictures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
+The Google Chrome debugger is unable to find three function names and The Firebug debugger fails at one case.}
+\label{debuggers-callstack}
+\end{figure*}
+
+%explain function expression and function declerations
+%moreover explain creation of the list of outer scopes.
+%Functions can be defined and created with no name or identifier.
+In JavaScrip a function can be defined by a function expression or a function decleration \cite{ECMA}.
+From the same function expression or decleration, function objects are created.
+In addition to function source code, the clousure scopes are also important for understanding the function operation.
+The clousure scopes include all available variables to the function at the time of creation.
+The location of function definition in the source code is enough for knowing the clousure scopes.
+Therefore, a function body with its location in a source code defines a category of function objects with the similar behaviour.
+Is it possible to assing a name to every function object in JavaScript in a way that:
+1) Function objects with the same code has the same name.
+2) The proposed name recalls the function for the developer.
+3) Describes the function behaviour.
+%uinque?!
+%For example to know an object, developer has to examine the object properties and from the property names and values, some connections
+%understanding JavaScript code and its runtime is much harder for developers.
+% we propose automatic function naming with these features
+% 1) expected by user 2) different situations
 
 \section{Automatic Funcation Naming}
+%-- Check here: http://kangax.github.com/nfe/
+To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
+First, assigning a global name to the function which identifies the function in the whole program.
+Second, naming a function in a call stack.
 
-\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.
+A function object in JavaScript can be defined by \texttt{function \textit{identifier} (args)\{...\}} or \texttt{new Function(args, source)}.
+\subsection{A Global Name for a Function Object}
+
+%\begin{center}
+    %\begin{tabular}{ | l | l | l | p{5cm} |}
+    %\hline
+    %& Type & Sample & Description \\ \hline
+    %a & Named & function foo(){...} & The function is named. \\ \hline
+    %a & Named & function foo(){...} & The function is named. \\ \hline
+    %a & Named & function foo(){...} & The function is named. \\ 
+    %\hline
+    %\end{tabular}
+%\end{center}
+
+\begin{figure}[htp]
+\begin{verbatim}
+(a) Case 1:
+ function foo(){ ... }
+
+(b) Case 2:
+ var foo = function { ... }
+
+(c) Case 3:
+ var foo = {
+     bar : function { ...}
+ }
+
+(d) Case 4:
+
+ var foo = function(){
+           ....
+           return function(){ ... }
+ }()
+
+(e) Case 5:
+ var foo = function(){ 
+ 					 return ...;
+ }()
+
+(f) Case 6:
+ var foo = function(){
+
+ }()();
+
+(g)
+ foo(function(){ ... });
+
+(h)
+ array = [...., function(){},...]
+
+(i)
+ array[i] = function(){};
+
+(j)
+ eval(); & new Function("");
+
+\end{verbatim}
+\caption{Different cases of function object creation.}
+\label{fig:functionCreation}
+\end{figure}
+
+\subsection{Naming Functions in Call Stack}
+%new Function ([arg1[, arg2[, ... argN]],] functionBody)
+%this[ optall.queue === false ? "each" : "queue" ](function() {})
+
+\begin{figure}[htp]
+\begin{verbatim}
+(a)
+ foo();
+(b)
+ foo.bar();
+(c)
+ foo.apply(bar, args);
+
+\end{verbatim}
+\caption{Different cases of function object creation.}
+\label{fig:functionCall}
+\end{figure}
+
+\section{evaluation}
+%Firebug, JQuery,
+
+%JQuery
+% core.js
 

### 2011-01-01 trunk/papers/qsic2011/bare_conf.tex

@@
 \begin{abstract}
-%\boldmath
 Understanding JavaScript code due to its dynamic, weakly-typed nature is complicated.
 Developers usually understand JavaScript programs by running them and examining their elements at runtime.
-However, understanding the concrete value of an element is not always straightforward.
-Among all runtime elments in JavaScript functions are more important: they are used as object constructors and apear in call stack.
-We discuss the function names usage in improving concrete values presentation.
-Morover, we propose an approach for automatic function naming in JavaScript.
+However, understanding concrete values, particularly user-defined and function objects, is not always straightforward.
+Function names can aid in this regard; they can appear as the constructor name in object representation or as the functions identifier in callstack.
+Unfortunately, a very low proportion (less than 15\%) of JavaScript functions are named in the first place.
+We propose an approach for automated JavaScript function naming based on source code analysis.
+We applied our approach over two relatively large JavaScript programs.
 \end{abstract}
@@
 The unique and important role of JavaScript in web programming is undeniable.
+With the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
 This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
@@
 However, there has been severe inherent barriers for improving JavaScript tool support.
-Unlike many traditional object oriented languages such as Java and C\#, it does not have classes, and does not encourage encapsulation or even structured programming JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
+Unlike many traditional object oriented languages such as Java and C\#, it does not have classes, and does not encourage encapsulation or even structured programming.
+JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
 As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
@@
 Moreover, these infered data can help in code coprehension if they are properly presented.
-However, none of the mentioned approaches provided effective means for sharing this information with the developer.
+Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
 
-%talk about runtime tools
 Developers usually understand JavaScript code by examining the running program in debuggers.
 At runtime, concrete values are available and developer can directly check and understand object structures and control flows.
-However, understanding a concrete value is not always straightforward, particulary for non-primitive values such as objects and functions.
-To facilitate understanding these complex values, debuggers show a summary of these objects.
-For example, the name of object constructor must appear in its summary.
+Understanding a concrete value, particulary for non-primitive values such as objects and functions, is not always straightforward.
+To facilitate understanding these complex values at the first place, debuggers show a summary of these objects.
+For example, in case of user-defined objects, the name of object's constructor can be very helpful in the object summary.
+It can work like a class name and summarizes the object structure.
 
-Functions are central to program comprehension in JavaScript.
-They are first-class objects that can be used for object construction and be passed as function call arguments.
-However, there is a serious issue with JavaScript functions that makes understanding them very difficult.
-Functions can be defined and created with no identifier or name.
-A function name is important for referring and recalling the function's functionality.
-Morover, the name of an object's constructor can work like a class name and summarizes the object structure.
+Functions are central to program comprehension in JavaScript. They are first-class objects that are used for different purposes by developers; 
+they may be used as an object  constructor, a clousure scope(module) or even  passed as an argument in a function call.
+However, there is a subtle issue with JavaScript functions that makes working with them in debuggers quite impossible: functions can be defined and created with no name or identifier.
+This problem particularly shows up in debuggers \cite{Zaytsev}.
+The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 15\%) of JavaScript functions are named.
 
-In this paper, we propose an approach for automatic naming of functions in JavaScript.
-The function names can be used in debuggers for more descriptive object summaries or callstack view.
-Moreover, these function names can be used in integration with proposed JavaScript typing systems for providing modern editing features.
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Firefox Firebug Debugger]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.27\textheight]{fbug-objects.jpg}}
+\hfil
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.27\textheight]{chrome-objects.jpg}}}
+\caption{These two pictures show the variables view of Firebug and Google Chrome JavaScript debuggers paused at the same breakpoint.}
+\label{debuggers-objects}
+\end{figure*}
+
+In this paper, we propose automated JavaScript function naming based on extracted data from source code analysis.
+The candidate function names can be used in debuggers for more descriptive object summaries and callstack view.
+Moreover, these function names can be used in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+
+\section{The Function Naming Problem}
+
+A JavaScript function can be defined in different ways: by the {\small\texttt{function}} operator (i.e., function decleration or expression) or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
+Once a statement which defines a function is evaluated, a {\small\texttt{Function}} object is created.
+Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects may be created.
+To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
+
+{\small\texttt{Function}} objects have no name by default; as the {\small\texttt{Function}} constructor doesn't receive any name.
+According to ECMA specification, a function name (identifier) can be specified after the {\small\texttt{function}} operator (It is mandatory for function declerations but optional for function expressions) \cite{ECMA}.
+However, the usage of function identifiers is limited.
+The reason is that, function names, in addition to naming the function, has an effect on available variables in the scopes.
+In the case of function declearations, the function object is assigned to a variable in the function scope, but in the case of function expressions, the function object is available only inside the function.
+The confusing behavior of function identifiers get worse by function statements introduced by some browser such as Firfox.
+Function statements are like function expressions, but the function object is available in the entire function scope like function declarations \cite{Zaytsev}.
+Therefore, developers often prefer to omit the function identifier in function statement to avoid their confusing impacts.
+
+%In JavaScript, defining \textit{identifier} for functions is optional. 
+A function object can be assigned to a variable or an object property with any name. Therefore a function object can be called by different names during in life time. 
+%___ why it is hard
+
+%The importance of function names is not only limited to call stack view.
+A function can be used as a constructor for constructing new objects.
+The constructor name like class name in traditional languages such as Java, can be used in object representation.
+It can assist developers in understanding the structure and role of the object without looking into its properties.
+
+\subsection{Constructor Name}
+In Java, an object is a set of properties, a mutable map from strings to values. The JavaScript object system is extremely flexible. As a
+result, it is difficult to constrain the behavior of any given object.In JavaScript,
+any function can be a constructor for a “class” of objects, and
+contains a prototype field, initially referencing an empty object.
+The new keyword creates an object based on the prototype field and
+using the function as a constructor.
+
+Figure~\ref{debuggers-objects} shows the variables view of Firefox and Google Chrome debuggers, paused at the same breakpoint.
+To know a variable value developer first check the summary value presented besides the variable name.
+If the summary value is not enough, then developer can expand the variable node to examin variable properties.
+In this case, the values of all variables are created using a constructor and the constructor name can be included in the summary.
+However, instead of the name of constructor which can hint the developer about the object structure, only \texttt{Object} is shown.
 
@@
 %
+
+%JavaScript is an imperative, objectoriented language with Java-like syntax, but unlike Java it employs a prototype-based object system.
+An object is a set of properties, a mutable map from strings to values.
+A property that evaluates to a closure and is called using the context of its parent object plays the role of a method in Java.
+Each object has prototype field which refers to another object.
+Property lookup involves searching the current object, then its parent, and its parent until the property is found.
+The JavaScript object system is extremely flexible.
+As a result, it is difficult to constrain the behavior of any given object.
+For example, it is possible to modify the contents of any prototype at any time or to replace a prototype field altogether.
+In JavaScript, any function can be a constructor for a “class” of objects, and contains a prototype field, initially referencing an empty object.
+The new keyword creates an object based on the prototype field and using the function as a constructor.
+The semantics of new is simple, but unusual: first, an empty object is created, with its parent set to the object referenced by the prototype field of the constructor function; second, the constructor is called, with this bound to the new object.
+The object referenced by the keyword this is not determined by lexical scoping, but instead by the caller; finally the return value from the constructor (if any) is discarded, and the new expression evaluates to this.%richards
+
+\subsection{Callstack View}
+Figure~\ref{debuggers-callstack} shows the call stack view of Firefox Firebug and Google Chrome JavaScript debuggers, paused at the same breakpoint.
+The differences between two call stacks, particularly in the first two frames, are due to different implementations of event handling in the underlying platforms.
+Google chrome shows \texttt{anonymouse} as the identifier for three functions which doesn't give any useful information to the developer.
+The developer has to locate the function by its source file and line number to recall the function functionality.
+Although Firebug shows more function names, it is also speechless about one function.
+
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Firefox Firebug Debugger]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{fbug-callstack.jpg}}
+\hfil
+\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{chrome-callstack.jpg}}}
+\caption{These two pictures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
+The Google Chrome debugger is unable to find three function names and The Firebug debugger fails at one case.}
+\label{debuggers-callstack}
+\end{figure*}
+
+%moreover explain creation of the list of outer scopes.
+In addition to function source code, the clousure scopes are also important for understanding the function operation.
+The clousure scopes include all available variables to the function at the time of creation.
+The location of function definition in the source code is enough for knowing the clousure scopes.
+Therefore, a function body with its location in a source code defines a category of function objects with the similar behaviour.
+
+Is it possible to assing a name to every function object in JavaScript in a way that:
+
+\begin{enumerate}
+   \item Function objects with the same code has the same name.
+   \item The proposed name recalls the function for the developer.
+   \item Describes the function behaviour.
+\end{enumerate}
+%uinque?!
+%not very long like google chrome  xxxx.yyy.zzz
 
@@
 
-\begin{figure*}[htp]
-\centerline{
-\subfigure[Firefox Firebug Debugger]{\label{fig_first_case}\includegraphics[width=.47\textwidth]{fbug-callstack.jpg}}
-\hfil
-\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth]{chrome-callstack.jpg}}}
-\caption{These two pictures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
-The Google Chrome debugger is unable to find three function names and The Firebug debugger fails at one case.}
-\label{debuggers}
-\end{figure*}
-
-\section{The Function Naming Problem}
-Figure~\ref{debuggers} shows the call stack view of Firefox Firebug and Google Chrome JavaScript debuggers, paused at the same breakpoint.
-The differences between two call stack, particularly in the first two frames, are due to different implementations of event handling in the underlying platforms.
-Google chrome shows \texttt{anonymouse} for three functions which doesn't give any useful information to the developer.
-The developer has to look at the specified source file and line number to recall the function.
-Although Firebug shows more function names, it is also unsuccessful about one function.
-
-%___ The importance of having function names
-The importance of function names is not only limited to call stack view.
-A function can be used as a constructor for constructing new objects.
-The constructor name like class name in traditional languages such as Java, can be used in object representation.
-It can assist developers in understanding the structure and role of the object without looking into its properties.
-
-In JavaScript, defining \textit{identifier} for functions is optional.
-A function can be assigned to a variable or an object property with any name.
-Therefore a function object can be called by different names during in life time.
-%___ why it is hard
-
-%Many developers develop JavaScript in object-oriented way.
-%
-
-%___ related work for type system
-
+\section{Automatic Funcation Naming}
 %-- Check here: http://kangax.github.com/nfe/
-%function body(source), function object
-
-%explain function expression and function declerations
-%moreover explain creation of the list of outer scopes.
-In JavaScrip a function can be defined by a function expression or a function decleration \cite{ECMA}.
-From the same function expression or decleration, function objects are created.
-In addition to function source code, the clousure scopes are also important for understanding the function operation.
-The clousure scopes include all available variables to the function at the time of creation.
-The location of function definition in the source code is enough for knowing the clousure scopes.
-Therefore, a function body with its location in a source code defines a category of function objects with the similar behaviour.
-Is it possible to assing a name to every function object in JavaScript in a way that:
-1) Function objects with the same code has the same name.
-2) The proposed name recalls the function for the developer.
-
-\section{Automatic Funcation Naming}
 To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
@@
 
+A function object in JavaScript can be defined by \texttt{function \textit{identifier} (args)\{...\}} or \texttt{new Function(args, source)}.
 \subsection{A Global Name for a Function Object}
+
+%\begin{center}
+    %\begin{tabular}{ | l | l | l | p{5cm} |}
+    %\hline
+    %& Type & Sample & Description \\ \hline
+    %a & Named & function foo(){...} & The function is named. \\ \hline
+    %a & Named & function foo(){...} & The function is named. \\ \hline
+    %a & Named & function foo(){...} & The function is named. \\ 
+    %\hline
+    %\end{tabular}
+%\end{center}
 
@@
 
+(j)
+ eval(); & new Function("");
+
 \end{verbatim}
@@
 \subsection{Naming Functions in Call Stack}
+%new Function ([arg1[, arg2[, ... argN]],] functionBody)
+%this[ optall.queue === false ? "each" : "queue" ](function() {})
 
@@
  foo.apply(bar, args);
-
+(d)
+ foo.call();
 \end{verbatim}
@@
 \end{figure}
+
+\section{evaluation}
+%Firebug, JQuery,
+
+%JQuery
+% core.js
 
@@
 
+\bibitem{Zaytsev}
+J. Zaytsev.\newblock Named function expressions demystified.
+\newblock http://kangax.github.com/nfe,
+June, 2010.
+
 \end{thebibliography}

### 2011-01-03 papers/qsic2011/bare_conf.tex

@@
 However, understanding concrete values, particularly user-defined and function objects, is not always straightforward.
-Function names can aid in this regard; they can apear as the constructor name in object representation or as the functions identifier in callstack.
-Unfortunately, a very low proportion (less than 15\%) of JavaScript functions are named.
-We propose an approach for automated function naming based on source code analysis.
+Function names can aid in this regard; they can appear as the constructor name in object representation or as the functions identifier in callstack.
+Unfortunately, a very low proportion (less than 15\%) of JavaScript functions are named in the first place.
+We propose an approach for automated JavaScript function naming based on source code analysis.
 We applied our approach over two relatively large JavaScript programs.
@@
 However, there is a subtle issue with JavaScript functions that makes working with them in debuggers quite impossible: functions can be defined and created with no name or identifier.
-The function name is necessary for referring and recalling the function's functionality, but only a small proportion(less than 15\%) of JavaScript functions are named.
+This problem particularly shows up in debuggers \cite{Zaytsev}.
+The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 15\%) of JavaScript functions are named.
 
-\begin{figure*}[htp]
+\begin{figure*}[!t]
 \centerline{
-\subfigure[Firefox Firebug Debugger]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.27\textheight]{fbug-objects.jpg}}
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{chrome-objects.jpg}}
 \hfil
-\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.27\textheight]{chrome-objects.jpg}}}
-\caption{These two pictures show the variables view of Firebug and Google Chrome JavaScript debuggers paused at the same breakpoint.}
+\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{fbug-objects.jpg}}}
+\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
 \label{debuggers-objects}
@@
 
-In this paper, we propose automated JavaScript function naming based on extracted data by anaylizing the source code.
+In this paper, we propose automated JavaScript function naming based on extracted data from the source code.
 The candidate function names can be used in debuggers for more descriptive object summaries and callstack view.
@@
 
-The importance of function names is not only limited to call stack view.
-A function can be used as a constructor for constructing new objects.
-The constructor name like class name in traditional languages such as Java, can be used in object representation.
-It can assist developers in understanding the structure and role of the object without looking into its properties.
-%function body(source), function object
+A JavaScript function can be defined in different ways: by the {\small\texttt{function}} operator (i.e., function decleration or expression) or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
+Once a statement which defines a function is evaluated, a {\small\texttt{Function}} object is created.
+Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects may be created.
+To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
 
-In JavaScript, defining \textit{identifier} for functions is optional.
-A function can be assigned to a variable or an object property with any name.
-Therefore a function object can be called by different names during in life time.
-%___ why it is hard
+{\small\texttt{Function}} objects have no name by default; as the {\small\texttt{Function}} constructor doesn't receive any name.
+According to ECMA specification, a function name (identifier) can be specified after the {\small\texttt{function}} operator (It is mandatory for function declerations but optional for function expressions) \cite{ECMA}.
+However, the usage of function identifiers is limited.
+The reason is that, function names, in addition to naming the function, has an effect on available variables in the scopes.
+In the case of function declearations, the function object is assigned to a variable in the function scope, but in the case of function expressions, the function object is available only inside the function.
+The confusing behavior of function identifiers get worse by function statements introduced by some browser such as Firfox.
+Function statements are like function expressions, but the function object is available in the entire function scope like function declarations \cite{Zaytsev}.
+Therefore, developers often prefer to omit the function identifier in function statement to avoid their confusing impact.
+
+Functions in JavaScript are first-class objects.
+They can be assigned to any variable or object proeprty, or passed as an argument to a function.
+It is common that the same functionis called by various names in different contexts.
+Therefore, it is usually very difficult to recall the function operation from its local name.
+Developers have usually the option to look at the function code, but it is tedious and time-consuming.
+Two main issues apears in debuggers due to the lack of function name.
+First, object constructor name which can faciliate understanding the object value, is not available in the object summary.
+Second, the callstack view is less informative.
+We disscuss these issues in the next subsections.
 
 \subsection{Constructor Name}
-Figure~\ref{debuggers-objects} shows the variables view of Firefox and Google Chrome debuggers, paused at the same breakpoint.
-To know a variable value developer first check the summary value presented besides the variable name.
-If the summary value is not enough, then developer can expand the variable node to examin variable properties.
-In this case, the values of all variables are created using a constructor and the constructor name can be included in the summary.
-However, instead of the name of constructor which can hint the developer about the object structure, only \texttt{Object} is shown.
+JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new Constructor()}}).
+A constructor is a regular JavaScript function.
+Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called.
+The role of constructor is to initialize the empty object.
+Although the structure of object imposed by the constructor, unlike class-based object-oriented languages, may not remain intact during the object's lifetime \cite{Richards}, the constructor can still be used to classify the object.
+Debuggers employ this fact and display the constructor name in the object summary.
 
-%Many developers develop JavaScript in object-oriented way.
-%
+Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code.
+We set a breakpoint on line 13 and examin the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
+Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}.
+However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects.
+The developer has to expand the object nodes to recognize their differences.
+Firebug classify objects in the same general class, but includes some of the object properties in the summary.
+These additional properties may hint develooper about the object structures.
+{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain this behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
 
-JavaScript is an imperative, objectoriented
-language with Java-like syntax, but unlike Java it employs
-a prototype-based object system. An object is a set of properties,
-a mutable map from strings to values. A property that evaluates
-to a closure and is called using the context of its parent object
-plays the role of a method in Java. Each object has prototype field
-which refers to another object. Property lookup involves searching
-the current object, then its parent, and its parent until the property
-is found. The JavaScript object system is extremely flexible. As a
-result, it is difficult to constrain the behavior of any given object.
-For example, it is possible to modify the contents of any prototype
-at any time or to replace a prototype field altogether. In JavaScript,
-any function can be a constructor for a “class” of objects, and
-contains a prototype field, initially referencing an empty object.
-The new keyword creates an object based on the prototype field and
-using the function as a constructor. The semantics of new is simple,
-but unusual: first, an empty object is created, with its parent set
-to the object referenced by the prototype field of the constructor
-function; second, the constructor is called, with this bound to
-the new object. The object referenced by the keyword this is not
-determined by lexical scoping, but instead by the caller; finally the
-return value from the constructor (if any) is discarded, and the new
-expression evaluates to this.%richards
-
-\subsection{Callstack View}
-Figure~\ref{debuggers-callstack} shows the call stack view of Firefox Firebug and Google Chrome JavaScript debuggers, paused at the same breakpoint.
-The differences between two call stacks, particularly in the first two frames, are due to different implementations of event handling in the underlying platforms.
-Google chrome shows \texttt{anonymouse} as the identifier for three functions which doesn't give any useful information to the developer.
-The developer has to locate the function by its source file and line number to recall the function functionality.
-Although Firebug shows more function names, it is also speechless about one function.
-
-\begin{figure*}[htp]
+\begin{figure*}[!t]
 \centerline{
-\subfigure[Firefox Firebug Debugger]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{fbug-callstack.jpg}}
+\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{chrome-callstack.jpg}}
 \hfil
-\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{chrome-callstack.jpg}}}
-\caption{These two pictures show the call stack view of Firebug and Google Chrome JavaScript debuggers paused at the same point. 
-The Google Chrome debugger is unable to find three function names and The Firebug debugger fails at one case.}
+\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{fbug-callstack.jpg}}}
+\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
 \label{debuggers-callstack}
@@
 
-%explain function expression and function declerations
-%moreover explain creation of the list of outer scopes.
-%Functions can be defined and created with no name or identifier.
-In JavaScrip a function can be defined by a function expression or a function decleration \cite{ECMA}.
-From the same function expression or decleration, function objects are created.
-In addition to function source code, the clousure scopes are also important for understanding the function operation.
-The clousure scopes include all available variables to the function at the time of creation.
-The location of function definition in the source code is enough for knowing the clousure scopes.
-Therefore, a function body with its location in a source code defines a category of function objects with the similar behaviour.
-Is it possible to assing a name to every function object in JavaScript in a way that:
-1) Function objects with the same code has the same name.
-2) The proposed name recalls the function for the developer.
-3) Describes the function behaviour.
-%uinque?!
-%For example to know an object, developer has to examine the object properties and from the property names and values, some connections
-%understanding JavaScript code and its runtime is much harder for developers.
-% we propose automatic function naming with these features
-% 1) expected by user 2) different situations
+\begin{figure}[!t]
+{\small 
+\begin{verbatim}
+9  var main = function(){
+10   return function(){
+11     var foo = new FOO("a");
+12     var bar = new BAR("b");
+13     var result = op(
+14       function(value){
+15         return value;
+16        });
+17   }
+18 }();
+19 var FOO = function(a){
+20   this.a = a;
+21 }
+22 var BAR = function(b){
+23   this.b = b;
+24 }
+25 var op = function(){
+26   var local;
+27   return function(callBack){
+28     local++;
+29     return callBack(local);
+30   }
+31 }();
+\end{verbatim}}
+\caption{An excerpt of a JavaScript code.}
+\label{js-code}
+\end{figure}
 
-\section{Automatic Funcation Naming}
-%-- Check here: http://kangax.github.com/nfe/
+\subsection{Callstack View}
+To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
+Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
+The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
+Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
+Firebug performs better by guessing three function names but it still fails in one case.
+In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+
+\section{Automated Funcation Naming}
+    To tackle the aforementioned function naming issues, we propose automated function naming by anlysing the source code. A function name must help the developer to
+distinguish the function from other functions with different behaviours.
+The behaviour of a function is dependent to its source code, ebclosing scopes (because of global and closure variables), the object bound to {\small\texttt{this}}-depending how it is called- and passed arguments.
+The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
+Therefore, to name a function object, it is enough to name its \textit{function body}.
+    A function body can uniquly be identified by its location in the source file.
+A naive proposal for the function name for a function body is a combination of file name and the line number.
+Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+In contrast, we use names in the source code to name unnamed functions.
+    Once a function object is created, one of these cases would happen:
+    \begin{enumerate}
+		\item the function object is assigned to a variable or one of its properties.
+		\item it is assigned to a property of a new object.
+		\item it is assigned to a new array index.
+		\item it is called.
+		\item it is returned from a function call.
+		\item it is passed as an argument to a function.
+		\end{enumerate}
+
 To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
@@
 
+%The object referenced by the keyword {\small\texttt{this}} is not determined by lexical scoping, but instead by the caller;
 \begin{figure}[htp]
@@
 
+%namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
+%commonjs requriejs, ...
+%the function name not very long like google chrome  xxxx.yyy.zzz
+
 \section{Related Work}
-%Another strand of research has tried to investigate how to provide better tools for developers for catching errors early.
-Being a weakly typed language with no type declarations and only run-time checking of calls and field accesses, it is natural to try to provide a static type system for JavaScript [2, 1, 3, 24, 13].
-Finally, after many years of neglect, modern implementations of JavaScript have started to appear which use state of the art just-in-time compilation techniques [10].
-
-%For JavaScript, Anderson et al.
-proposed a type system with definite and potential types [2, 1, 3], while Heidegger and Thiemann following up on some of their earlier work [24, 18] propose recency types in [13], and Furr et al.
-proposed a related system for DRuby [9].
-While all of these type systems acknowledge some minor simplifications to the target language, they rely on fairly similar assumptions.
-For instance, Thiemann writes: “Usually, no further properties are defined after the initialization and the type of the properties rarely changes.” This suggests that object types are stable at run-time and can be described using, e.g., traditional rowtypes.
-In fact all the proposals take the view that an object’s type should be the sum of all possible fields and methods that it could contain, with some of them being undefined; they differ mostly on how to perform strong updates to avoid polluting all properties with undefined values.
-Interestingly, language implementors make similar assumptions.
-For instance, Google’s V8 JavaScript engine is reported to optimistically associate “classes” to objects on the assumption that their shape will not change too much, though with a fallback case for highly dynamic objects 3.
-This design is similar to implementations of one of JavaScript’s influences, Self [5], and is expected to work for the same reasons.
-As the above mentioned hypothesis is crucial for the applicability and usefulness of the results, it deserves careful study.
-In fact, we have found a number of similar assumptions in the literature which we list below.We first review the salient features of the language to provide sufficient background for readers unfamiliar with JavaScript.
 

### 2011-01-17 trunk/papers/issta2011/sigproc-sp.tex

--- 2011-01-03 papers/qsic2011/bare_conf.tex
@@
-\documentclass[conference]{IEEEtran}
+% THIS IS SIGPROC-SP.TEX - VERSION 3.1
+% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
+% APRIL 2009
+%
+% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
+% LaTeX2e document class file for Conference Proceedings submissions.
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) Page numbering
+% ---------------------------------------------------------------------------------------------------------------
+% It is an example which *does* use the .bib file (from which the .bbl file
+% is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission,
+% you need to 'insert'  your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% Questions regarding SIGS should be sent to
+% Adrienne Griscti ---> griscti@acm.org
+%
+% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
+% Gerald Murray ---> murray@hq.acm.org
+%
+% For tracking purposes - this is V3.1SP - APRIL 2009
+
+\documentclass{acm_proc_article-sp}
 
@@
 
-\hyphenation{op-tical net-works semi-conduc-tor}
+\begin{document}
 
-\begin{document}
+\title{Better JavaScript Runtime Understanding by Automated Function Name Extraction}
 %
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Better JavaScript Runtime Understanding by Automated Function Name Extraction}
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{\IEEEauthorblockN{Salman Mirghasemi}
-\IEEEauthorblockA{\'Ecole Polytechnique F\'ed\'erale de Lausanne\\
-Lausanne, Switzerland\\
-salman.mirghasemi@epfl.ch}
-\and
-\IEEEauthorblockN{John J. Barton}
-\IEEEauthorblockA{IBM Research - Almaden\\
-San Jose, USA\\
-johnjbarton@johnjbarton.com}
-\and
-\IEEEauthorblockN{Claude Petitpierre}
-\IEEEauthorblockA{\'Ecole Polytechnique F\'ed\'erale de Lausanne\\
-Lausanne, Switzerland\\
-claude.petitpierre@epfl.ch}}
+\numberofauthors{3} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
+%
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+\alignauthor
+Salman Mirghasemi\\
+       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne}\\
+       \affaddr{Lausanne, Switzerland}\\
+       \email{salman.mirghasemi@epfl.ch}
+% 2nd. author
+\alignauthor
+John J. Barton\\
+       \affaddr{IBM Research - Almaden}\\
+       \affaddr{San Jose, USA}\\
+       \email{johnjbarton@johnjbarton.com}
+% 3rd. author
+\alignauthor Claude Petitpierre\\
+       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne}\\
+       \affaddr{Lausanne, Switzerland}\\
+       \email{claude.petitpierre@epfl.ch}
+}
+
 \maketitle
-
 \begin{abstract}
@@
 Function names can aid in this regard; they can appear as the constructor name in object representation or as the functions identifier in callstack.
-Unfortunately, a very low proportion (less than 15\%) of JavaScript functions are named in the first place.
-We propose an approach for automated JavaScript function naming based on source code analysis.
-We applied our approach over two relatively large JavaScript programs.
+Unfortunately, only a very low proportion (less than 10\%) of JavaScript functions are named by developers in the first place.
+As a solution to this issue, we propose an approach for automated JavaScript function naming based on source code analysis.
+We applied our approach on several JavaScript projects and the resutls are very promising.
+
 \end{abstract}
+
+\category{D.2.5}{Testing and Debugging}{Debugging aids}
+\category{D.2.6}{Programming Environments}{Integrated environments}
+
+\terms{Algorithms, Human Factors, Languages}
+
+\keywords{Debugging, JavaScript, Function Name} % NOT required for Proceedings
 
@@
 The unique and important role of JavaScript in web programming is undeniable.
-With the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
+Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
 This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
@@
 
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
+\hfil
+\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
+\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
+\label{debuggers-objects}
+\end{figure*}
+
 To cope with the pace of changes, JavaScript developers need to improve their develoment processes and practices.
@@
 However, there has been severe inherent barriers for improving JavaScript tool support.
-Unlike many traditional object oriented languages such as Java and C\#, it does not have classes, and does not encourage encapsulation or even structured programming.
+JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
 JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
 As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
-A variable value can be a primitive value, an object with any structure or even a function.
+The value of a variable can be a primitive value, an object with any structure or even a function.
 One callsite may invoke different function bodies with different number of arities that none of them can be understood from the code.
@@
 Developers usually understand JavaScript code by examining the running program in debuggers.
-At runtime, concrete values are available and developer can directly check and understand object structures and control flows.
+At runtime, concrete values are available and the developer can directly check and understand object structures and control flows.
 Understanding a concrete value, particulary for non-primitive values such as objects and functions, is not always straightforward.
@@
 they may be used as an object  constructor, a clousure scope(module) or even  passed as an argument in a function call.
-However, there is a subtle issue with JavaScript functions that makes working with them in debuggers quite impossible: functions can be defined and created with no name or identifier.
+However, there is a subtle issue with JavaScript functions that makes working with them quite difficult: functions can be defined and created with no name or identifier.
 This problem particularly shows up in debuggers \cite{Zaytsev}.
-The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 15\%) of JavaScript functions are named.
-
-\begin{figure*}[!t]
-\centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{chrome-objects.jpg}}
-\hfil
-\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{fbug-objects.jpg}}}
-\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
-\label{debuggers-objects}
-\end{figure*}
+The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 10\%) of JavaScript functions are named.
 
@@
 
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
+\hfil
+\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
+\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
+\label{debuggers-callstack}
+\end{figure*}
+
 \section{The Function Naming Problem}
@@
 Once a statement which defines a function is evaluated, a {\small\texttt{Function}} object is created.
-Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects may be created.
+Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects can be created from that definition.
 To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
@@
 Function statements are like function expressions, but the function object is available in the entire function scope like function declarations \cite{Zaytsev}.
-Therefore, developers often prefer to omit the function identifier in function statement to avoid their confusing impact.
+Therefore, developers often prefer to omit the function identifier in the function statement to avoid its confusing impact.
 
@@
 They can be assigned to any variable or object proeprty, or passed as an argument to a function.
-It is common that the same functionis called by various names in different contexts.
+It is common that the same function is called by various names in different contexts.
 Therefore, it is usually very difficult to recall the function operation from its local name.
@@
 First, object constructor name which can faciliate understanding the object value, is not available in the object summary.
-Second, the callstack view is less informative.
-We disscuss these issues in the next subsections.
+Second, the callstack view is usually full of \textit{anonymous} functions and therefore less informative.
+We disscuss these issues in the next two subsections.
 
@@
 Although the structure of object imposed by the constructor, unlike class-based object-oriented languages, may not remain intact during the object's lifetime \cite{Richards}, the constructor can still be used to classify the object.
-Debuggers employ this fact and display the constructor name in the object summary.
+Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.
 
@@
 However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects.
-The developer has to expand the object nodes to recognize their differences.
+The developer has to expand the object nodes to recognize their similarities and differences.
 Firebug classify objects in the same general class, but includes some of the object properties in the summary.
@@
 
-\begin{figure*}[!t]
-\centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{chrome-callstack.jpg}}
-\hfil
-\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{fbug-callstack.jpg}}}
-\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
-\label{debuggers-callstack}
-\end{figure*}
-
-\begin{figure}[!t]
+\begin{figure}[htp]
 {\small 
@@
 
+The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
+The {\small\texttt{this}} value is missed in both views.
+The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+
 \section{Automated Funcation Naming}
@@
 distinguish the function from other functions with different behaviours.
-The behaviour of a function is dependent to its source code, ebclosing scopes (because of global and closure variables), the object bound to {\small\texttt{this}}-depending how it is called- and passed arguments.
+The behaviour of a function is dependent to its source code, enclosing scopes (because of global and closure variables), the object bound to {\small\texttt{this}}-depending how it is called- and passed arguments.
 The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
 Therefore, to name a function object, it is enough to name its \textit{function body}.
-    A function body can uniquly be identified by its location in the source file.
-A naive proposal for the function name for a function body is a combination of file name and the line number.
+    A function body can be uniquly identified by its location in the source file.
+A naive proposal for the function name for a function body is a combination of the function file name and line number.
 Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
-In contrast, we use names in the source code to name unnamed functions.
+
+In contrast, we use names in the source code to name nameless functions. 
     Once a function object is created, one of these cases would happen:
@@
 
+%ACKNOWLEDGMENTS are optional
+%\section{Acknowledgments}
+
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+
+%\bibliographystyle{abbrv}
+%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
+%APPENDICES are optional
+%\balancecolumns
+
 \begin{thebibliography}{10}
@@
 
-% that's all folks
 \end{document}

### 2011-01-20 trunk/papers/issta2011/sigproc-sp.tex

@@
 \usepackage{subfigure}
+\usepackage{multirow}
+\usepackage{rotating}
+\usepackage{array}
 
@@
 Function names can aid in this regard; they can appear as the constructor name in object representation or as the functions identifier in callstack.
-Unfortunately, only a very low proportion (less than 10\%) of JavaScript functions are named by developers in the first place.
+Unfortunately, only a very low proportion (less than 5\%) of JavaScript functions are named by developers in the first place.
 As a solution to this issue, we propose an approach for automated JavaScript function naming based on source code analysis.
@@
 There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.
-
-\begin{figure*}[htp]
-\centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
-\hfil
-\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
-\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
-\label{debuggers-objects}
-\end{figure*}
 
@@
 Understanding a concrete value, particulary for non-primitive values such as objects and functions, is not always straightforward.
-To facilitate understanding these complex values at the first place, debuggers show a summary of these objects.
+To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
 For example, in case of user-defined objects, the name of object's constructor can be very helpful in the object summary.
@@
 This problem particularly shows up in debuggers \cite{Zaytsev}.
-The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 10\%) of JavaScript functions are named.
+The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 5\%) of JavaScript functions are named.
 
@@
 
+\begin{table}
+\centering
+\caption{The total number of functions and the number of named functions in five famous JavaScript projects.}
+  \begin{tabular}{ | l | l | c | c | c |}
+  \hline
+   Project & Description & Total & Named \\ 
+  \hline 
+   jQuery & JavaScript Library & 422 & 23 \\ 
+  \hline 
+   Prototype & JavaScript Framework & 645 & 203 \\ 
+  \hline 
+   Closure & Google Web Library & 9195 & 208 \\ 
+  \hline 
+   YUI &  Yahoo UI Library & 22346 & 922 \\ 
+  \hline 
+   Firebug & Web Development Tool & 3424 & 406 \\ 
+  \hline 
+  \end{tabular}
+ \label{functions} 
+\end{table}
+
 \begin{figure*}[htp]
 \centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
 \hfil
-\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
-\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
-\label{debuggers-callstack}
+\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
+\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
+\label{debuggers-objects}
 \end{figure*}
@@
 In the case of function declearations, the function object is assigned to a variable in the function scope, but in the case of function expressions, the function object is available only inside the function.
-The confusing behavior of function identifiers get worse by function statements introduced by some browser such as Firfox.
+The confusing behavior of function identifiers get worse by function statements introduced by some browsers such as Firfox.
 Function statements are like function expressions, but the function object is available in the entire function scope like function declarations \cite{Zaytsev}.
 Therefore, developers often prefer to omit the function identifier in the function statement to avoid its confusing impact.
+
+To support the above argument, we analyzed the source code of five famous JavaScript projects.
+For every project, the total number of functions and the number of functions with name are collected (Table~\ref{functions}).
+The ratio of the number of functions with names to the total number of functions is less than 13 percent in all projects excepting Prototype and the average ratio is less than 5 percent.
+Our analysis does not include the functions defined by dynamically created scripts evaluated by {\small\texttt{eval}} function.
 
@@
 These additional properties may hint develooper about the object structures.
-{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain this behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
+{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
 
@@
 To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
+Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debugger and Firebug.
+The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
+Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
+Firebug performs better by guessing three function names but it still fails in one case.
+In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+
+The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
+The {\small\texttt{this}} value is missed in both views.
+The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
+\hfil
+\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
+\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
+\label{debuggers-callstack}
+\end{figure*}
+
+\section{Automated Funcation Naming}
+    To tackle the aforementioned function naming issues, we propose automated function naming by anlysing the source code. A function name must help the developer to
+distinguish the function from other functions with different behaviours.
+The behaviour of a function is dependent to its source code, enclosing scopes (e.g., global and closure variables), the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
+The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
+Therefore, to name a function object, it is enough to name its \textit{function body}.
+    A function body can be uniquly identified by its location in the source file.
+A naive proposal for the function name for a function body is a combination of the function file name and line number.
+Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+Morover, A proposed function name should be close to the name a developer would choose for the function.
+
+Once a function object is created, one of these cases would happen: the function object is
+    \begin{enumerate}
+		\item assigned to a property of a new object in an object literal.
+		\item assigned to a new array index in an array literal.
+		\item assigned to an object property through direct access.
+		\item assigned to an object property through hashmap access by a string.
+		\item assigned to an object property through hashmap access by a variable name.
+		\item assigned to an object property through hashmap access by a JavaScript expression.
+		\item assigned to an array index.
+		\item assigned to a variable.
+		\item directly called.
+		\item returned from a function call.
+		\item passed as an argument to a function.
+		\end{enumerate}
+
+\begin{table}
+\centering
+\caption{Different cases of function object creation and usage in JavaScript.}
+\scalebox{0.8}{
+\renewcommand\arraystretch{2.0}
+\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
+  \hline
+   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+  \hline
+
+   1 &
+   &  
+   & \multicolumn{2}{|m{2.8cm}|}{
+     \raggedright property of a new object in an object literal.}
+   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
+   \cline{0-0}\cline{4-6}
+
+	 2 &
+	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+	 & \multicolumn{2}{|m{2.8cm}|}{
+	   new array index in an array literal.} 
+   & foo = [..., function()\{...\}, ...] \\ 
+   \cline{0-0}\cline{4-6}
+
+   3 &
+   & 
+   &  
+   & direct access.
+   & bar.foo = function()\{...\}\\
+   \cline{0-0}\cline{5-6}
+
+   4 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+   & 
+   & 
+   & \raggedright hashmap access by a string. 
+   & bar["foo"] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   5 &
+   & 
+   & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
+   & \raggedright hashmap access by a variable name.
+   & bar[foo] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   6 &
+   & 
+   & 
+   & \raggedright hashmap access by a JavaScript expression.
+   & bar["f"+"oo"] = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   7 &
+   &
+   & \multicolumn{2}{|l|}{
+      array index.}
+   & foo[0] = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   8 &
+   & 
+   & \multicolumn{2}{|l|}{
+      variable.}
+   & foo = function()\{...\} \\
+   \cline{0-0}\cline{3-6}
+
+   9 &
+   & \multicolumn{3}{|m{3.8cm}|}{
+     \raggedright directly called.}
+   & function()\{...\}() \\
+   \cline{0-0}\cline{3-6}
+
+   10 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright returned from a function call.}
+   & \{... return function()\{...\}\} \\
+   \cline{0-0}\cline{3-6}
+
+   11 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright passed as an argument to a function.}
+   & foo(..., function()\{\}, ...) \\
+   \hline
+
+  \end{tabular}
+  }
+\end{table}
+
+%to remove
+To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
 Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
@@
 
-\section{Automated Funcation Naming}
-    To tackle the aforementioned function naming issues, we propose automated function naming by anlysing the source code. A function name must help the developer to
-distinguish the function from other functions with different behaviours.
-The behaviour of a function is dependent to its source code, enclosing scopes (because of global and closure variables), the object bound to {\small\texttt{this}}-depending how it is called- and passed arguments.
-The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
-Therefore, to name a function object, it is enough to name its \textit{function body}.
-    A function body can be uniquly identified by its location in the source file.
-A naive proposal for the function name for a function body is a combination of the function file name and line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
+Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
+The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
+Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
+Firebug performs better by guessing three function names but it still fails in one case.
+In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
 
-In contrast, we use names in the source code to name nameless functions. 
-    Once a function object is created, one of these cases would happen:
-    \begin{enumerate}
-		\item the function object is assigned to a variable or one of its properties.
-		\item it is assigned to a property of a new object.
-		\item it is assigned to a new array index.
-		\item it is called.
-		\item it is returned from a function call.
-		\item it is passed as an argument to a function.
-		\end{enumerate}
+The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
+The {\small\texttt{this}} value is missed in both views.
+The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
 
-To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
+To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
+Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
+The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
+Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
+Firebug performs better by guessing three function names but it still fails in one case.
+In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+
+The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
+The {\small\texttt{this}} value is missed in both views.
+The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+
+\subsection{Naming Functions in Call Stack}
+
+%To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
 First, assigning a global name to the function which identifies the function in the whole program.
@@
 
-A function object in JavaScript can be defined by \texttt{function \textit{identifier} (args)\{...\}} or \texttt{new Function(args, source)}.
-\subsection{A Global Name for a Function Object}
+%A function object in JavaScript can be defined by \texttt{function \textit{identifier} (args)\{...\}} or \texttt{new Function(args, source)}.
+%\subsection{A Global Name for a Function Object}
 
-%\begin{center}
-    %\begin{tabular}{ | l | l | l | p{5cm} |}
-    %\hline
-    %& Type & Sample & Description \\ \hline
-    %a & Named & function foo(){...} & The function is named. \\ \hline
-    %a & Named & function foo(){...} & The function is named. \\ \hline
-    %a & Named & function foo(){...} & The function is named. \\ 
-    %\hline
-    %\end{tabular}
-%\end{center}
-
-\begin{figure}[htp]
-\begin{verbatim}
-(a) Case 1:
- function foo(){ ... }
-
-(b) Case 2:
- var foo = function { ... }
-
-(c) Case 3:
- var foo = {
-     bar : function { ...}
- }
-
-(d) Case 4:
-
- var foo = function(){
-           ....
-           return function(){ ... }
- }()
-
-(e) Case 5:
- var foo = function(){ 
- 					 return ...;
- }()
-
-(f) Case 6:
- var foo = function(){
-
- }()();
-
-(g)
- foo(function(){ ... });
-
-(h)
- array = [...., function(){},...]
-
-(i)
- array[i] = function(){};
-
-(j)
- eval(); & new Function("");
-
-\end{verbatim}
-\caption{Different cases of function object creation.}
-\label{fig:functionCreation}
-\end{figure}
-
-\subsection{Naming Functions in Call Stack}
 %new Function ([arg1[, arg2[, ... argN]],] functionBody)

### 2011-01-22 papers/issta2011/sigproc-sp.tex

--- 2011-01-20 trunk/papers/issta2011/sigproc-sp.tex
@@
 Our analysis does not include the functions defined by dynamically created scripts evaluated by {\small\texttt{eval}} function.
+Among all functions defined in these five projects, only 8 functions (less than 0.02 percent) are defined by the {\small\texttt{Function}} constructor.
 
@@
 
+JavaScript does not support a packageing mechanism to be used for modular programming.
+Scripts are loaded from different files and executed within the same or different global objects.
+Developers usually use objectts at the top level to encapsulate properties, objects and functions from a framework or library.
+The same mechanism can be used to define nested subpackages.
+As the project size and the number of functions increases, the function name may not be enough to recognize the function.
+The developer also wants to know the function's library or package name.
+
 \begin{figure*}[htp]
@@
 	   new array index in an array literal.} 
-   & foo = [..., function()\{...\}, ...] \\ 
+   & [..., function()\{...\}, ...] \\ 
    \cline{0-0}\cline{4-6}
@@
   }
+ \label{function-types} 
 \end{table}
 
-%to remove
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+Table~\ref{function-types} shows JavaScript code corresponding to each case.
+The first one usually apears when developers try to group a set of functions in a new object.
+A common case is the {\small\texttt{prototype}} property of a constructor.
+It resembles the class structure in traditional object-oriented languages.
+When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
+Another case is when the owner object is a shared object which contains a set of utility functions.
+We assign the property name which the function body is assigned to as the function name.
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+In the second case, we first need to name the array literal contains the function body.
+If the name is {\small\texttt{foo}}, knowing the index of function body ({\small\texttt{i}}, {{\small\texttt{foo[i]}} is assigned as the function body name.
+The array literal can be consumed in a similar way as a function object (excepting the ninth case, as it can not be called), so the naming of array literal can be recursively done similar to a function object.
 
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+For the third and fourth cases where the function object is assigned to an object property we use the object property as the function name.
+In the fifth and sixth cases, {\small\texttt{bar}} can be an object or an array.
+For these two cases we use the expression inside {\small\texttt{[]}} as the function name.
+For the cases seven and eight, we use the left side of the assignment as the name candidate.
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
-
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
-
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+Calling functions objects just after their creations is a common pattern in JavaScript.
+This pattern is usually used for building modules employing the clousure feature in JavaScript.
+Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
 

### 2011-01-24 trunk/papers/issta2011/sigproc-sp.tex

@@
   \hline 
-   YUI &  Yahoo UI Library & 22346 & 922 \\ 
+   YUI &  Yahoo UI Library & 21080 & 901 \\ 
   \hline 
@@
   }
+ \label{function-types} 
 \end{table}
 
-%to remove
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+Table~\ref{function-types} shows JavaScript code corresponding to each case.
+The first one usually apears when developers try to group a set of functions in a new object.
+A common case is the {\small\texttt{prototype}} property of a constructor.
+It resembles the class structure in traditional object-oriented languages.
+When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
+Another case is when the owner object is a shared object which contains a set of utility functions.
+We assign the property name which the function body is assigned to as the function name.
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+In the second case, we first need to name the array literal contains the function body.
+If the name is {\small\texttt{foo}}, knowing the index of function body ({\small\texttt{i}}, {{\small\texttt{foo[i]}} is assigned as the function body name.
+The array literal can be consumed in a similar way as a function object (excepting the ninth case, as it can not be called), so the naming of array literal can be recursively done similar to a function object.
 
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+For the third and fourth cases where the function object is assigned to an object property we use the object property as the function name.
+In the fifth and sixth cases, {\small\texttt{bar}} can be an object or an array.
+For these two cases we use the expression inside {\small\texttt{[]}} as the function name.
+For the cases seven and eight, we use the left side of the assignment as the name candidate.
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+Calling functions objects just after their creations is a common pattern in JavaScript.
+This pattern is usually used for building modules employing the clousure feature in JavaScript.
+Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
 
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
-
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+\begin{table*}
+\centering
+\caption{The number nameless functions in each category defined in table~\ref{function-types}.}
+  \begin{tabular}{ | l | c | c | c | c | c | c | c | c | c | c | c |}
+  \hline
+     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+  \hline 
+   jQuery & 223(58\%) & 0  & 34(8\%) & 0 & 10(2\%) & 2 & 0 & 24(6\%) & 9(2\%) & 0 & 86(21\%)  \\ 
+  \hline 
+   Prototype & 265(60\%) & 0 & 28(6\%)& 0 & 0 & 1& 0 & 25(5\%)& 44(10\%)& 8(1\%) & 71(16\%) \\ 
+  \hline 
+   Closure & 23 (0.2\%)& 0 & 8465(94\%)& 3 & 4 & 0 & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
+  \hline 
+   YUI & 13278(66\%)& 6 & 1705(8\%)& 0 & 90(0.5\%)& 0 & 0 & 1121(6\%)& 171(1\%)& 93(0.5\%)& 3715(18\%)\\ 
+  \hline 
+   Firebug & 2296(76\%)& 0 & 539(18\%)& 1 & 0 & 0 & 0 & 14(0.5\%)& 7(0.2\%)& 6(0.2\%)& 149(5\%) \\ 
+  \hline 
+   Total & 49\%& 0\% & 33\% & 0\% & 0.3\% & 0\% & 0\% & 4\%& 0.7\%& 0.5\%& 13\% \\ 
+  \hline 
+  \end{tabular}
+ \label{functions-types-count} 
+\end{table*}
 

### 2011-01-28 papers/issta2011/sigproc-sp.tex

--- 2011-01-20 trunk/papers/issta2011/sigproc-sp.tex
@@
 Function names can aid in this regard; they can appear as the constructor name in object representation or as the functions identifier in callstack.
-Unfortunately, only a very low proportion (less than 5\%) of JavaScript functions are named by developers in the first place.
+Unfortunately, only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
 As a solution to this issue, we propose an approach for automated JavaScript function naming based on source code analysis.
@@
 This problem particularly shows up in debuggers \cite{Zaytsev}.
-The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 5\%) of JavaScript functions are named.
+The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.
 
@@
 \centering
-\caption{The total number of functions and the number of named functions in five famous JavaScript projects.}
-  \begin{tabular}{ | l | l | c | c | c |}
+\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
+\scalebox{0.9}{
+  \begin{tabular}{ | l | l | l | l | l |}
   \hline
@@
   \hline 
-   jQuery & JavaScript Library & 422 & 23 \\ 
+   Closure & Google Web Library & 9195 & 208(2\%) \\ 
   \hline 
-   Prototype & JavaScript Framework & 645 & 203 \\ 
+   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
   \hline 
-   Closure & Google Web Library & 9195 & 208 \\ 
+   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
   \hline 
-   YUI &  Yahoo UI Library & 22346 & 922 \\ 
+   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
   \hline 
-   Firebug & Web Development Tool & 3424 & 406 \\ 
+   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
+  \hline 
+   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
+  \hline 
+   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
+  \hline 
+   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
+  \hline 
+   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
+  \hline 
+   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
+  \hline 
+   All &  & 96008 & 6008(6.3\%) \\ 
   \hline 
   \end{tabular}
+  }
  \label{functions} 
@@
 
-To support the above argument, we analyzed the source code of five famous JavaScript projects.
+To support the above argument, we analyzed the source code of ten famous JavaScript projects.
 For every project, the total number of functions and the number of functions with name are collected (Table~\ref{functions}).
-The ratio of the number of functions with names to the total number of functions is less than 13 percent in all projects excepting Prototype and the average ratio is less than 5 percent.
+The ratio of the number of functions with names to the total number of functions is less than 13 percent in all projects excepting Prototype and the average ratio is less than 7 percent.
 Our analysis does not include the functions defined by dynamically created scripts evaluated by {\small\texttt{eval}} function.
+Among all functions defined in these ten projects, only 8 functions (less than 0.02 percent) are defined by the {\small\texttt{Function}} constructor.
 
@@
 Firebug classify objects in the same general class, but includes some of the object properties in the summary.
-These additional properties may hint develooper about the object structures.
+These additional properties may hint developer about the object structures.
 {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
@@
 
+A function name must help the developer to
+distinguish the function from other functions with different behaviours.
+The behaviour of a function is dependent to its source code, enclosing scopes (e.g., global and closure variables), the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
+The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
+Therefore, to name a function object, it is enough to name its \textit{function body}.
+
+A function body can be uniquly identified by its location in the source file.
+A naive proposal for the function name for a function body is a combination of the function file name and line number.
+Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+Morover, A proposed function name should be close to the name a developer would choose for the function.
+
+JavaScript does not support a packageing mechanism to be used for modular programming.
+Scripts are loaded from different files and executed within the same or different global objects.
+Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
+The same mechanism can be used to define nested subpackages.
+As the project size and the number of functions increases, the function name may not be enough to recognize the function.
+The developer also wants to know the function's library or package name.
+
 \begin{figure*}[htp]
@@
 \section{Automated Funcation Naming}
-    To tackle the aforementioned function naming issues, we propose automated function naming by anlysing the source code. A function name must help the developer to
-distinguish the function from other functions with different behaviours.
-The behaviour of a function is dependent to its source code, enclosing scopes (e.g., global and closure variables), the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
-The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
-Therefore, to name a function object, it is enough to name its \textit{function body}.
-    A function body can be uniquly identified by its location in the source file.
-A naive proposal for the function name for a function body is a combination of the function file name and line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
-Morover, A proposed function name should be close to the name a developer would choose for the function.
 
-Once a function object is created, one of these cases would happen: the function object is
-    \begin{enumerate}
-		\item assigned to a property of a new object in an object literal.
-		\item assigned to a new array index in an array literal.
-		\item assigned to an object property through direct access.
-		\item assigned to an object property through hashmap access by a string.
-		\item assigned to an object property through hashmap access by a variable name.
-		\item assigned to an object property through hashmap access by a JavaScript expression.
-		\item assigned to an array index.
-		\item assigned to a variable.
-		\item directly called.
-		\item returned from a function call.
-		\item passed as an argument to a function.
-		\end{enumerate}
+    To tackle the aforementioned issues caused due to the lack of function names, we propose automated function naming by anlyzing the source code and extracting the initial name used for the function object after its creation.
+To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
+
+    We can recognize seven function bodies, none of them has a name.
+The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
+The result is to variable {\small\texttt{main}}.
+Therefore the internal function body is named {\small\texttt{main}} as its result is assinged to a variable with this name.
+What about the outer function itself?
+We name that
+ {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
 
@@
 	   new array index in an array literal.} 
-   & foo = [..., function()\{...\}, ...] \\ 
+   & foo\textsuperscript{*} = [..., function()\{...\}, ...] \\ 
    \cline{0-0}\cline{4-6}
@@
    & direct access.
-   & bar.foo = function()\{...\}\\
+   & bar\textsuperscript{*}.foo = function()\{...\}\\
    \cline{0-0}\cline{5-6}
@@
    & \raggedright hashmap access by a string. 
-   & bar["foo"] = function()\{...\} \\
+   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
    \cline{0-0}\cline{5-6}
@@
    & \raggedright hashmap access by a variable name.
-   & bar[foo] = function()\{...\} \\
+   & bar\textsuperscript{*}[foo] = function()\{...\} \\
    \cline{0-0}\cline{5-6}
@@
    & \raggedright hashmap access by a JavaScript expression.
-   & bar["f"+"oo"] = function()\{...\} \\
+   & bar\textsuperscript{*}["f"+"oo"] = function()\{...\} \\
    \cline{0-0}\cline{4-6}
@@
       array index.}
-   & foo[0] = function()\{...\} \\
+   & foo\textsuperscript{*}[0] = function()\{...\} \\
    \cline{0-0}\cline{4-6}
@@
      \raggedright directly called.}
-   & function()\{...\}() \\
+   & foo\textsuperscript{*} = function()\{...\}() \\
    \cline{0-0}\cline{3-6}
@@
      \raggedright passed as an argument to a function.}
-   & foo(..., function()\{\}, ...) \\
+   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
    \hline
@@
   }
+ \label{function-types} 
 \end{table}
 
-%to remove
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+ We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
+A better name would be the the argument name in the called function (here {\small\texttt{callback}}).
+However the latter requires knowning the function body of the called function which is not always possible.
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+    As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are assigned to variable with the same names.
+Similar to the first two functions which are named as {\small\texttt{mainClosure}} and {\small\texttt{main}}, the functions in lines 25 and 27 can be name {\small\texttt{opClosure}} and {\small\texttt{op}} respectively.
 
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+\begin{table*}
+\centering
+\caption{The number of nameless functions in each category defined in table~\ref{function-types}.}
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+  \hline 
+   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
+  \hline 
+   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
+  \hline 
+   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
+  \hline 
+   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
+  \hline 
+   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
+  \hline 
+   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
+  \hline 
+   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
+  \hline 
+   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
+  \hline 
+   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
+  \hline 
+   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
+  \hline 
+   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
+  \hline 
+  \end{tabular}
+ \label{function-types-count} 
+\end{table*}
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+\subsection{Naming Scheme}
+We can generalize the approach used for naming functions in the example.
+Once a function object is created, one of the cases presented in Table~\ref{function-types} can happen.
+For every case, we will explain how a name can be assinged to the function.
+Names which are specified with a star can be more comprehensive elements which reduced to a name.
+We discuss this reduction in ~\ref{sec:general-element-naming}.
+Table~\ref{function-types-count} shows the number of nameless functions in each category in the studied projects.
+These numbers shows how frequent and important a category of functions is in these projects.
+%they have similar pattern
 
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+\subsubsection{Case 1: in Object Literal}
+ This case usually apears when developers try to group a set of functions in a new object.
+A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
+This structure resembles the class structure in traditional object-oriented languages.
+When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
+This structure is also used  when the owner object is a shared object with a set of utility functions.
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+ The majority of nameless functions (more than 65\%) in almost all studied projects (except Closure), are defined in object literals.
+For this group of functions we assign the property name used to keep a reference to the function object as the function name.
 
+\subsubsection{Case 2: in Array Literal}
+Contrary to the previous case the appearance of this case is limited.
+It usually appears in initializations or when an array of functions are passed as an argument.
+Among all projects only two projects have instances of nameless functions defined in this way.
+If we assume that the array literal has a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
+
+\subsubsection{Case3: setProperty by Direct Access }
+This case is the second most common case in the studied projects.
+Here, we can see why the Closure project is different from other projects in the first case.
+About 94\% of nameless functions in this project are defined in this way.
+It seems that the Closure developers follow an internal standard for function objects creation and usage.
+Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
+This case usually happens when the functinos are assinged to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
+
+\subsubsection{Case 4: setProperty by String}
+In JavaScript, objects are like hashmaps and their properties can also be accessed by strings.
+In general an expression can be specified in the brackets after the object.
+The expression is evaluated at runtime and the result which should be a string is used to access the property.
+In the simplest form, the expression can be a string.
+As this form can be completely replaced by the direct access, we see few instances of this form for function object assignment.
+The string inside the brackets become the function name in this case.
+
+\subsubsection{Case 5: setProperty by variable}
+The usage of this case is also limited. This form usually apears when the same function body is assigned to different properties in a loop. Therefore, the variable
+ name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
+Morover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
+To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
+
+\subsubsection{Case 6: setProperty by Expression}
+ A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condtion?"prop1":"prop2"}}.
+To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
+
+%jQuery.fn["inner" + name] = function() {
+%dojo[dojo._defaultXhr ? "_defaultXhr" : "xhr"] = function
+%scope[this.triggerEvent]
+
+\subsubsection{Case 7: setArray}
+We only observed one instance of this form in the studied projects. The function name consists of the array name with the index like {\small\texttt{foo[0]}}.
+
+\subsubsection{Case 8: setVariable }
+As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
+and its internal scopes.
+Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name is the local function name.
+Therefore, for this group of functions the variable name is used as the function name.
+
+\subsubsection{Case 9: Called}
+Calling functions objects just after their creations is a common pattern in JavaScript.
+This pattern is usually used for building modules employing the clousure feature in JavaScript.
+Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
+
+If the function call has no result, it means that the function initializes and set some values for later use.
+Therefore we name the function {\small\texttt{init}}.
+If the function returns a value and it is assinged to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
+
+\subsubsection{Case 10: Returned}
+Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
+Many constructors are build by this form and therfore the name of thes functions appear in object summaries.
+
+If the function is returned from a function which is just called after its creation(case 9), and the result is assigned to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
+Otherwise, if the name of outer function is {\small\texttt{foo}}, we name the function {\small\texttt{fooResult}}.
+
+% this is also important as many constructor/classes are made in this way
+
+\subsubsection{Case 11: as an Argument}
+Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
+{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
+functions as arguments is to register function in a global shared object.
+The function is usually registered with a name which is also passed as string argument.
+Therefore, to imporove our naming approach, we include the first string argument (if there is any) in the name.
+For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
+
+% to register a function with a name
+% to wrap the function
+% as a callback
+
+\subsection{Recursive Naming of Elements}
+\label{sec:general-element-naming}
+
+\subsection{Similar Function Names in a File}
+It is conceivable, that function bodies are named with the same names in a file.
+It can happen in different situations.
+One of the common cases is the two different function bodies may assing to a property based on a condition (e.g., the browser).
+For these cases we add a dollar sign and an index to the similar function names.
+For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+
+%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
+% more than one return
+
+\subsection{Package Name}
+
+\subsection{Functions created by \texttt{eval()}}
+The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is avaialble.
+However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
+
+\section{Improved by Runtime Data}
 \subsection{Naming Functions in Call Stack}
 
-%To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
-First, assigning a global name to the function which identifies the function in the whole program.
-Second, naming a function in a call stack.
-
-%A function object in JavaScript can be defined by \texttt{function \textit{identifier} (args)\{...\}} or \texttt{new Function(args, source)}.
-%\subsection{A Global Name for a Function Object}
-
-%new Function ([arg1[, arg2[, ... argN]],] functionBody)
-%this[ optall.queue === false ? "each" : "queue" ](function() {})
-
-%The object referenced by the keyword {\small\texttt{this}} is not determined by lexical scoping, but instead by the caller;
 \begin{figure}[htp]
@@
 \section{evaluation}
+
+\subsection{Developers' vs. Automated Names}
+\subsection{Compared to Firebug \texttt{guessFunctionName()}}
+\subsection{Manual Check}
 %Firebug, JQuery,

### 2011-02-02 trunk/papers/issta2011/sigproc-sp.tex

--- 2011-01-20 trunk/papers/issta2011/sigproc-sp.tex
@@
 
-To support the above argument, we analyzed the source code of five famous JavaScript projects.
+To support the above argument, we analyzed the source code of ten famous JavaScript projects.
 For every project, the total number of functions and the number of functions with name are collected (Table~\ref{functions}).
-The ratio of the number of functions with names to the total number of functions is less than 13 percent in all projects excepting Prototype and the average ratio is less than 5 percent.
+The ratio of the number of functions with names to the total number of functions is less than 13 percent in all projects excepting Prototype and the average ratio is less than 7 percent.
 Our analysis does not include the functions defined by dynamically created scripts evaluated by {\small\texttt{eval}} function.
+Among all functions defined in these ten projects, only 116 functions (less than 0.12 percent) are defined by the {\small\texttt{Function}} constructor.
 
@@
 \section{Automated Funcation Naming}
-    To tackle the aforementioned function naming issues, we propose automated function naming by anlysing the source code. A function name must help the developer to
-distinguish the function from other functions with different behaviours.
-The behaviour of a function is dependent to its source code, enclosing scopes (e.g., global and closure variables), the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
-The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
-Therefore, to name a function object, it is enough to name its \textit{function body}.
-    A function body can be uniquly identified by its location in the source file.
-A naive proposal for the function name for a function body is a combination of the function file name and line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
-Morover, A proposed function name should be close to the name a developer would choose for the function.
 
-Once a function object is created, one of these cases would happen: the function object is
-    \begin{enumerate}
-		\item assigned to a property of a new object in an object literal.
-		\item assigned to a new array index in an array literal.
-		\item assigned to an object property through direct access.
-		\item assigned to an object property through hashmap access by a string.
-		\item assigned to an object property through hashmap access by a variable name.
-		\item assigned to an object property through hashmap access by a JavaScript expression.
-		\item assigned to an array index.
-		\item assigned to a variable.
-		\item directly called.
-		\item returned from a function call.
-		\item passed as an argument to a function.
-		\end{enumerate}
+    To tackle the aforementioned issues caused due to the lack of function names, we propose automated function naming by anlyzing the source code and extracting the initial name used for the function object after its creation.
+To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
+
+    We can recognize seven function bodies in the code, none of them has a name.
+The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
+The result is assigned to variable {\small\texttt{main}}.
+Therefore the internal function body is named {\small\texttt{main}} as its corresponding function object is assinged to a variable with this name.
+What about the outer function itself?
+We name that
+ {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
 
@@
    & \raggedright hashmap access by a JavaScript expression.
-   & bar["f"+"oo"] = function()\{...\} \\
+   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
    \cline{0-0}\cline{4-6}
@@
   }
+ \label{function-types} 
 \end{table}
 
-%to remove
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+ The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
+We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
+A better name would be the the argument name in the called function (here {\small\texttt{callback}}).
+However the latter requires knowning the function body of the called function which is not always possible.
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+    As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are assigned to variable with the same names.
+Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}}, the functions in lines 25 and 27 can be named {\small\texttt{opClosure}} and {\small\texttt{op}} respectively.
 
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+\begin{table*}
+\centering
+\caption{The number of nameless functions in each category defined in table~\ref{function-types}.}
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+  \hline 
+   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
+  \hline 
+   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
+  \hline 
+   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
+  \hline 
+   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
+  \hline 
+   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
+  \hline 
+   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
+  \hline 
+   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
+  \hline 
+   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
+  \hline 
+   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
+  \hline 
+   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
+  \hline 
+   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
+  \hline 
+  \end{tabular}
+ \label{function-types-count} 
+\end{table*}
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+\subsection{Naming Scheme}
+We can generalize the approach used for naming functions in the example by studying differnt cases that a function object can be created and used.
+Once a function object is created, one of the cases presented in Table~\ref{function-types} can happen.
+One common case of function object creation is by top script named function bodies.
+We did not considered this case as a separate case as it can be transformed to case 8 where a function body is assigned to a variable.
+Moreover, Note that functions are created by {\small\texttt{Function}} constructor can be replace by a function body and named in the same way.
+For every case, we will explain how a name can be assinged to the function.
 
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debuggers and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+Names which are specified with a star are reduced from a JavaScript expression.
+We discuss this reduction in ~\ref{sec:general-element-naming}.
+Table~\ref{function-types-count} shows the number of nameless functions in each category in the studied projects.
+These numbers shows how frequent and important a category of functions is in these projects.
+%they have similar pattern
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+\subsubsection{Case 1: in Object Literal}
+ This case usually apears when developers try to group a set of functions in a new object.
+A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
+This structure resembles the class structure in traditional object-oriented languages.
+When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
+This structure is also used  when the owner object is a shared object with a set of utility functions.
 
+ The majority of nameless functions (more than 65\%) in almost all studied projects (except Closure), are defined in object literals.
+For this group of functions we assign the property name used to keep a reference to the function object as the function name.
+
+\subsubsection{Case 2: in Array Literal}
+Contrary to the previous case the appearance of this case is very limited.
+It usually appears in initializations or when an array of functions are passed as an argument.
+Among all projects only two projects have instances of nameless functions defined in this way.
+To name the function body defined in an array literal, first we must name the array literal.
+To name the array literal, we consider it as a function body and we employ the same algorithm we use for naming a function body.
+If the array literal receives a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
+
+\subsubsection{Case3: setProperty by Direct Access }
+This case is the second most common case in the studied projects.
+Here, we can see why the Closure project is different from other projects in the first case.
+About 94\% of nameless functions in this project are defined in this way.
+It seems that the Closure developers follow an internal standard for function objects creation and usage.
+Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
+This case usually happens when the functinos are assinged to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
+
+\subsubsection{Case 4: setProperty by String}
+In JavaScript, objects are like hashmaps and their properties can also be accessed by strings.
+In general an expression can be specified in the brackets after the object.
+The expression is evaluated at runtime and the result which should be a string is used to access the property.
+In the simplest form, the expression can be a string.
+As this form can be completely replaced by the direct access, we see few instances of this form for function object assignment.
+The string inside the brackets become the function name in this case.
+
+\subsubsection{Case 5: setProperty by variable}
+The usage of this case is also limited. This form usually apears when the same function body is assigned to different properties in a loop. Therefore, the variable
+ name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
+Morover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
+To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
+
+\subsubsection{Case 6: setProperty by Expression}
+ A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condtion?"prop1":"prop2"}}.
+To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
+
+%jQuery.fn["inner" + name] = function() {
+%dojo[dojo._defaultXhr ? "_defaultXhr" : "xhr"] = function
+%scope[this.triggerEvent]
+
+\subsubsection{Case 7: setArray}
+We only observed one instance of this form in the studied projects. The function name consists of the array name with the index like {\small\texttt{foo[0]}}.
+
+\subsubsection{Case 8: setVariable }
+As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
+and its internal scopes.
+Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name is the local function name.
+Therefore, for this group of functions the variable name is used as the function name.
+
+\subsubsection{Case 9: Called}
+Calling functions objects just after their creations is a common pattern in JavaScript.
+This pattern is usually used for building modules employing the clousure feature in JavaScript.
+Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
+
+If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
+In this case, we name the function {\small\texttt{Closure}}.
+If the function returns a value and it is assinged to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
+
+\subsubsection{Case 10: Returned}
+Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
+Many constructors are build by this form and therfore the name of thes functions appear in object summaries.
+
+If the function is returned from a function which is just called after its creation(case 9), and the result is assigned to {\small\texttt{foo}}, we name the function {\small\texttt{foo}}.
+Otherwise, if the name of outer function is {\small\texttt{foo}}, we name the function {\small\texttt{fooResult}}.
+
+% this is also important as many constructor/classes are made in this way
+
+\subsubsection{Case 11: as an Argument}
+Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
+{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
+functions as arguments is to register function in a global shared object.
+The function is usually registered with a name which is also passed as string argument.
+Therefore, to imporove our naming approach, we include the first string argument (if there is any) in the name.
+For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
+
+% to register a function with a name
+% to wrap the function
+% as a callback
+
+\subsection{Reducing a JavaScript Expression to a Name}
+\label{sec:general-element-naming}
+
+\begin{table}
+\centering
+\caption{JavaScript Expression Reduction to Name.}
+\scalebox{0.9}{
+  \begin{tabular}{ | l | l | l |}
+  \hline
+   Description & Total & Named \\ 
+  \hline 
+   Primitive Value & value & value.toString() \\ 
+  \hline 
+   Variable & foo & foo \\ 
+  \hline 
+   GetProp & bar.foo & Name(bar).foo \\ 
+  \hline 
+   GetElem & bar[foo] & Name(bar)+[Name(foo)] \\ 
+  \hline 
+   Add & bar op foo & Name(bar)+op+Name(foo) \\ 
+  \hline 
+   Condition & cond?bar:foo & Name(bar)+":"+Name(foo) \\ 
+  \hline 
+  \end{tabular}
+  }
+ \label{expression-reduction} 
+\end{table}
+
+\subsection{Similar Function Names in a File}
+It is conceivable, that function bodies are named with the same names in a file.
+It can happen in different situations.
+One of the common cases is the two different function bodies may assing to a property based on a condition (e.g., the browser).
+For these cases we add a dollar sign and an index to the similar function names.
+For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+
+%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
+% more than one return
+
+\subsection{Package Name}
+
+\subsection{Functions created by {\large \texttt{eval()}}}}
+The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is avaialble.
+However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
+
+\section{Improved by Runtime Data}
 \subsection{Naming Functions in Call Stack}
 
-%To choose the most appropriate name for a function which has the characteristics defined in the previous section, we consider two cases.
-First, assigning a global name to the function which identifies the function in the whole program.
-Second, naming a function in a call stack.
-
-%A function object in JavaScript can be defined by \texttt{function \textit{identifier} (args)\{...\}} or \texttt{new Function(args, source)}.
-%\subsection{A Global Name for a Function Object}
-
-%new Function ([arg1[, arg2[, ... argN]],] functionBody)
-%this[ optall.queue === false ? "each" : "queue" ](function() {})
-
-%The object referenced by the keyword {\small\texttt{this}} is not determined by lexical scoping, but instead by the caller;
 \begin{figure}[htp]
@@
 \section{evaluation}
+
+\subsection{Developers' vs. Automated Names}
+
+\subsection{Compared to Firebug {\large \texttt{guessFunctionName()}}}
+Firebug uses a utility function called {\small \texttt{guessFunctionName()}} to name nameless functions.
+This algorithm used in the function searches lines around the line the function definition line for specific patterns by regular expressions. The
+  first string matches one of the patterns becomes the name of the function. We compared the results of our algorithm to Firebug's in table~\ref{firebug}.
+
+The first column shows, how many functions get similar names by both algorithm. In average, for 60\% of functions both algorithms produce the same names.
+Firebug is not able to name about 15\% of functions. In 35\% of functions the results are different. In most cases, the proposed name by Firebug is the name of another function and is wrong.
+
+\begin{table}
+\centering
+\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
+\scalebox{0.9}{
+  \begin{tabular}{ | l | l | l | l | l |}
+  \hline
+   Project & Similar & Different & UnNamed \\ 
+  \hline 
+   Closure & 8524(1\%) & 9195 & 516(2\%) \\ 
+  \hline 
+   DoJo & 12180(1\%) & 9195 & 5780(2\%) \\ 
+  \hline 
+   ExtJS & 100(1\%) & 9195 & 208(2\%) \\ 
+  \hline 
+   Firebug & 2901(1\%) & 9195 & 494(0\%) \\ 
+  \hline 
+   jQuery & 283(1\%) & 9195 & 117(0\%) \\ 
+  \hline 
+   MochiKit &  1568(1\%) & 9195 & 234(2\%) \\ 
+  \hline 
+   MooTools & 440(1\%) & 9195 & 128(2\%) \\ 
+  \hline 
+   Prototype & 292(1\%) & 9195 & 326(0\%) \\ 
+  \hline 
+   Scriptaculous &  100(1\%) & 9195 & 397(2\%) \\ 
+  \hline 
+   YUI &  11248(1\%) & 9195 & 3702(2\%) \\ 
+  \hline 
+   All & 100(1\%) & 9195 & 208(2\%) \\ 
+  \hline 
+  \end{tabular}
+  }
+ \label{firebug} 
+\end{table}
+
+\subsection{Manual Check}
 %Firebug, JQuery,

### 2011-03-07 papers/fse2011/sig-alternate.tex

--- 2010-12-14 trunk/papers/ecoop2011/ecoop2011-lastChange.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is the LaTeX source for the instructions to authors using
-% the LaTeX document class 'llncs.cls' for contributions to
-% the Lecture Notes in Computer Sciences series.
-% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
-%
-% It may be used as a template for your own input - copy it
-% to a new file with a new name and use it as the basis
-% for your article.
-%
-% NB: the document class 'llncs' has its own and detailed documentation, see
-% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\documentclass[runningheads,a4paper]{llncs}
+% This is "sig-alternate.tex" V1.9 April 2009
+% This file should be compiled with V2.4 of "sig-alternate.cls" April 2009
+%
+% This example file demonstrates the use of the 'sig-alternate.cls'
+% V2.4 LaTeX2e document class file. It is for those submitting
+% articles to ACM Conference Proceedings WHO DO NOT WISH TO
+% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
+% The 'sig-alternate.cls' file will produce a similar-looking,
+% albeit, 'tighter' paper resulting in, invariably, fewer pages.
+%
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V2.4) produces:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) NO page numbers
+%
+% as against the acm_proc_article-sp.cls file which
+% DOES NOT produce 1) thru' 3) above.
+%
+% Using 'sig-alternate.cls' you have control, however, from within
+% the source .tex file, over both the CopyrightYear
+% (defaulted to 200X) and the ACM Copyright Data
+% (defaulted to X-XXXXX-XX-X/XX/XX).
+% e.g.
+% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
+% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
+%
+% ---------------------------------------------------------------------------------------------------------------
+% This .tex source is an example which *does* use
+% the .bib file (from which the .bbl file % is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission, you *NEED* to 'insert'
+% your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% ================= IF YOU HAVE QUESTIONS =======================
+% Questions regarding the SIGS styles, SIGS policies and
+% procedures, Conferences etc. should be sent to
+% Adrienne Griscti (griscti@acm.org)
+%
+% Technical questions _only_ to
+% Gerald Murray (murray@hq.acm.org)
+% ===============================================================
+%
+% For tracking purposes - this is V1.9 - April 2009
+
+\documentclass{sig-alternate}
 
@@
 
-\usepackage{url}
-\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
-\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
-\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
-\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-\noindent\keywordname\enspace\ignorespaces#1}
+%\usepackage{url}
+%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
+%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
+%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
+%\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+%\noindent\keywordname\enspace\ignorespaces#1}
 
@@
 
-\mainmatter  % start of an individual contribution
-
-% first the title is needed
-\title{Debugging by \textit{lastChange}}
-
-% a short form should be given in case it is too long for the running head
-\titlerunning{Debugging by \textit{lastChange}}
-
-% the name(s) of the author(s) follow(s) next
-%
-% NB: Chinese authors should write their first names(s) in front of
-% their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
-%
-
-\author{Salman Mirghasemi\inst{1} \and John J. Barton\inst{2} \and Claude Petitpierre\inst{1}}
-
-%
-%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
-% (feature abused for this document to repeat the title also on left hand pages)
-
-% the affiliations are given next; don't give your e-mail address
-% unless you accept that it will be published
-\institute{\'Ecole Polytechnique F\'ed\'erale de Lausanne \\
-\path|{salman.mirghasemi,claude.petitpierre}@epfl.ch| \\
-\and IBM Research - Almaden \\
-\path|johnjbarton@johnjbarton.com|}
-
-%
-% NB: a more complex sample for affiliations and the mapping to the
-% corresponding authors can be found in the file "llncs.dem"
-% (search for the string "\mainmatter" where a contribution starts).
-% "llncs.dem" accompanies the document class "llncs.cls".
-%
-
-\toctitle{Lecture Notes in Computer Science}
-\tocauthor{Authors' Instructions}
+%
+% --- Author Metadata here ---
+\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+% --- End of Author Metadata ---
+
+\title{Debugging by {\huge\bf\textit{lastChange}}}
+
+%\subtitle{[Extended Abstract]
+%\titlenote{A full version of this paper is available as
+%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
+%\LaTeX$2_\epsilon$\ and BibTeX} at
+%\texttt{www.acm.org/eaddress.htm}}}
+
+%
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+%
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
+
+\numberofauthors{3} %  in this sample file, there are a *total*
+% of EIGHT authors. SIX appear on the 'first-page' (for formatting
+% reasons) and the remaining two appear in the \additionalauthors section.
+%
+\author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
+\alignauthor
+Salman Mirghasemi\\
+       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne, Switzerland}\\
+       \email{salman.mirghasemi@epfl.ch}
+% 2nd. author
+\alignauthor
+John J. Barton\\
+       \affaddr{IBM Research - Almadan}\\
+       \email{bartonjj@us.ibm.com}
+% 3rd. author
+\alignauthor 
+Claude Petitpierre\\
+       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne, Switzerland}\\
+       \email{claude.petitpierre@epfl.ch}
+}
+
+% There's nothing stopping you putting the seventh, eighth, etc.
+% author on the opening page (as the 'third row') but we ask,
+% for aesthetic reasons that you place these 'additional authors'
+% in the \additional authors block, viz.
+% Just remember to make sure that the TOTAL number of authors
+% is the number that will appear on the first page PLUS the
+% number that will appear in the \additionalauthors section.
+
 \maketitle
@@
 
-\keywords{Debugging, Locating Defects, Querypoint, LastChange, Breakpoint,
+\end{abstract}
+
+\category{D.2.5}{Testing and Debugging}{Debugging aids}
+\category{D.2.6}{Programming Environments}{Integrated environments}
+
+% A category with the (minimum) three required fields
+%\category{H.4}{Information Systems Applications}{Miscellaneous}
+%A category including the fourth, optional field follows...
+%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+
+\terms
+{Algorithms, Human Factors, Languages}
+
+\keywords
+{Debugging, Locating Defects, Querypoint, LastChange, Breakpoint,
  Watchpoint, Logging}
-\end{abstract}
 
@@
 requires analyzing and understanding. Developers usually end up in
-dealing with long log files and analyzing huge collected data.  None
-of these approaches assist developer in finding origins to a wrong
+dealing with long log files and analyzing huge amounts of collected data. 
+None of these approaches assist developer in finding origins to a wrong
 value.
@@
 in using breakpoints and manually inserted log statements. 
-Imagine a program execution 
+Imagine that a program execution is
 paused on a breakpoint and the developer is
@@
 
-As we detail in the Related Work section, numerous papers explore forms 
+As we detail in section \ref{sec:relatedWork}, numerous papers explore forms 
 of automatic logging of program state, augmented with queries on the log. 
@@
 example. The example demonstrates a buggy JavaScript code in a HTML
-page (Figure ~\ref{fig:js-code}). The page contains a button (line 40)
+page (Figure~\ref{fig:js-code}). The page contains a button (line 40)
 showing the value of \texttt{myObject.myProperty}.  When the user
@@
 \texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
-
-To apply backward search strategy for locating defects, the developer
-first needs to know the origin of the wrong value. To achieve this
-goal using breakpoints, the developer should search code to find all possible places that
-\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
-object and property can be accessed and changed through different
-names and methods. There is no simple way to identify these aliases or
-even their total number.  The developer can make a good guess and set
-breakpoints on lines where the property seems to be changed. Then they
-re-execute the program and examine the state looking for values that
-may lead to the incorrect value observed at line 22. All this work
-must be repeated if a new alias is discovered or if some
-information related to the buggy result was missed while stopped on
-one of the breakpoints.
 
@@
 
-In contrast, we have added a high-level function in debugger,
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin of the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find all possible places that
+\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these aliases or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
+
+In contrast, we have added a high-level function in the debugger,
 \textit{lastChange}, which provides the answer without tedious manual
@@
 \texttt{myObject.myProperty} in the Watch panel, the developer can run
-\textit{lastChange} command (Figure ~\ref{fig:example1}). Debugger
+\textit{lastChange} command (Figure~\ref{fig:example1}). The debugger
 re-executes the program and halts again at the breakpoint on line 22.
@@
 
-As demonstrated in Figure ~\ref{fig:example-points}, the developer has
+As demonstrated in Figure~\ref{fig:example-points}, the developer has
 examined three points of execution. The first point, the reproduction point,  was the breakpoint set by the developer.
@@
   figure, the execution is paused at line 22 by a regular
-  breakpoint. The Watch panel at the right shows the program state at
+  breakpoint. The Watch panel on the right shows the program state at
   the paused
@@
 
-\section{\textit{lastChange} Algorithm}
+\section{{\large\bf\textit{lastChange}} Algorithm}
 
@@
 
-\subsection{\textit{lastChange} on object property}
+\subsection{{\large\bf\textit{lastChange}} on object property}
 To simplify the algorithm explanation and defer technical details, we
@@
 \texttt{foo} change with the same object id as \texttt{bar} id at the
-reproduction point. Figure ~\ref{fig:foo-changes1} shows the list of
+reproduction point. Figure~\ref{fig:foo-changes1} shows the list of
 property \texttt{foo} change events in a hypothetical
@@
 \centering 
-\includegraphics[height=.23\textheight]{6-foo-changes1.jpg} 
+\includegraphics [width=.48\textwidth]{6-foo-changes1.jpg} 
 \caption{A hypothetical list of  change events for a property \texttt{foo}. 
@@
 
-\subsection{\textit{lastChange} on variable} 
+\subsection{{\large\bf\textit{lastChange}} on variable} 
 In JavaScript, every frame has a scope chain and every available
@@
 
-Figure ~\ref{fig:recursive} illustrates how the \texttt{ScopeId()} operation separates instances 
+Figure~\ref{fig:recursive} illustrates how the \texttt{ScopeId()} operation separates instances 
 of a variable in different scopes having the same name.
@@
 reproduction point in a program, debugger calls 
-\texttt{setVariableChangeHook()} with the variable's defining
+\texttt{setVari- ableChangeHook()} with the variable's defining
 block and name as parameters and re-executes the
@@
 \texttt{foo} change with the same scope id as the variable's scope id
-at the reproduction point (Figure ~\ref{fig:foo-changes2}).
+at the reproduction point (Figure~\ref{fig:foo-changes2}).
 
@@
 \centering 
-\includegraphics[height=.14\textheight]{7-foo-changes2.jpg}
+\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
 \caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
@@
 
-\subsection{\textit{lastChange} on \textit{lastChange}}
+\subsection{{\large\bf\textit{lastChange}} on {\large\bf\textit{lastChange}}}
 The \textit{lastChange} algorithm records changes by id (either object or scope id), then reads out the last change when we
@@
 we need to work out which \texttt{baz} the developer wanted, then select the last change of that \texttt{baz.y}.
-Figure ~\ref{fig:lastchange-lastchange} illustrates the extra row of data tracking of \texttt{baz} objects 
+Figure~\ref{fig:lastchange-lastchange} illustrates the extra row of data tracking of \texttt{baz} objects 
 at \texttt{x} change events 
@@
 
-\begin{figure}[htp]
-\centering 
-\includegraphics[height=.3\textheight]{8-lastchange-lastchange.jpg}
-\caption{The list of change events stored for locating point B, the
-  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
-  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
-\label{fig:lastchange-lastchange}
-\end{figure}
-
 %---------------------------------------------------------------------------------------------------
@@
 JavaScript debugger\footnote[2]{http://getfirebug.com}. %\cite{Firebug}. %\cite{firebug-version-1.6}. 
-Firebug itself is an extension of the Firefox browser.%\cite{Firefox}. %\cite{firefox-version-3.6}
+Firebug itself is an extension of the Firefox browser. %\cite{Firefox}. %\cite{firefox-version-3.6}
 The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and 
@@
 
-\subsection{\texttt{objectId()} operation}
+\begin{figure}[htp]
+\centering 
+\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
+\caption{The list of change events stored for locating point B, the
+  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
+  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
+\label{fig:lastchange-lastchange}
+\end{figure}
+
+\subsection{{\large\bf\texttt{objectId()}} operation}
 \texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
@@
 
-\subsection{\texttt{setPropertyChangeHook()} operation}
+\subsection{{\large\bf\texttt{setPropertyChangeHook()}} operation}
 The Firefox JavaScript engine supports watching property changes in an
@@
 file url and the line number and the goal is to get a reference to
-this object. Although in the most regular cases we have only one
+this object. Although in most regular cases we have only one
 statement and one object creation in a line, there are cases that more
@@
 statements. Every statement which has a new value, we consider the new
-value-if it is an object-as a new object. For example in Figure
+value (if it is an object) as a new object. For example in Figure
 ~\ref{fig:objectCreation}(a), if the creation line number is 20, we
@@
 where the new object is assigned to \texttt{a[++i]} where i is a variable
-(Figure ~\ref{fig:objectCreation}(d)), \texttt{a[++i]} is kept in the list
+(Figure~\ref{fig:objectCreation}(d)), \texttt{a[++i]} is kept in the list
 of assignee statements. Obviously, evaluating this statement doesn't return
@@
 Throughout this section we implicitly assumed that the object will be created at 
-the same location in the next execution. So, what does happen if it
-is not true? Well, once the execution reaches the reproduction point, it
+the same location in the next execution. So, what happens if it
+is not true? Once the execution reaches the reproduction point, it
 reveals that the object has been created in different location. This time,
@@
 
-\subsection{\texttt{scopeId()} operation}
+\subsection{{\large\bf\texttt{scopeId()}} operation}
 The prototype sets a hook at the beginning of all code blocks needing
@@
 
-\subsection{\texttt{setVariableChangeHook()} operation}
+\subsection{{\large\bf\texttt{setVariableChangeHook()}} operation}
 Variables defined in local, closure, and catch scopes are only changed in
 their scope; that includes the defining scope and scopes nested whithin them.
-For example in Figure ~\ref{fig:js-closure}, variable \texttt{myVar} in line 11 can only be
+For example in Figure~\ref{fig:js-closure}, variable \texttt{myVar} in line 11 can only be
 changed in lines 10 to 23. Therefore, after locating the function in
@@
 stores the initial page url and the events and parameters corresponding to user actions. In the replay phase, it opens
-the same url and simulated events as if they were user actions. The local reproduction mechanism provides
+the same url and simulates events as if they were user actions. The callstack reproduction mechanism provides
 shorter re-execution cycles while the record-replay is more accurate about the
@@
 
-\subsection{\textit{lastChange} Result Consistency}
+\subsection{{\large\bf\textit{lastChange}} Result Consistency}
 \label{sec:resultConsistency}
@@
 When user asks for the \textit{lastChange} on variable \texttt{a}, debugger stores \texttt{a} value and compares
-it to the \texttt{a} value in the next executions. So if this value is different, debuggers inform the developer
+it to the \texttt{a} value in the next executions. So if this value is different, debugger informs the developer
 that the \textit{lastChange} query is made on a different value. In cases that the value is not a primitive but an object,
@@
 
-\subsection{Combination of \textit{lastChange} and breakpoint debugging}
+\subsection{Combination of {\large\bf\textit{lastChange}} and breakpoint debugging}
 \label{sec:pausing}
@@
 applied both conventional breakpoint and \textit{lastChange} on two small programs we 
-provided. (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
+provided (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
 All four developers successfully applied \textit{lastChange} to the test programs 
@@
 We will report on this implementation in a later publication
-\subsection{Developers need an operation like \protect\textit{lastChange} }
+\subsection{Developers need an operation like \protect{\large\bf\textit{last- Change}} }
 
@@
 
-\subsection{Developers can learn to use \protect\textit{lastChange}}
+\subsection{Developers can learn to use \protect{\large\bf\textit{lastChange}}}
 
 If \texttt{lastChange} could be useful, can developers figure out how
-to use it? While our user study was small , our prototype demonstrates that
+to use it? While our user study was small, our prototype demonstrates that
 \textit{lastChange} can be easily activated by operations on the
@@
 for re-execution will be corresponding more valuable for debugging
-with \textit{lastChange}.  (Our \textit{Querypoint} prototype  
+with \textit{lastChange} (Our \textit{Querypoint} prototype  
 implements a simple form of automatic 
@@
 
-\subsection{In most cases \protect\textit{lastChange} will be much faster than current alternatives}
+\subsection{In most cases \protect{\large\bf\textit{lastChange}} will be much faster than current alternatives}
 
@@
 logging has very high overhead: the developer must add code, debug
-that added code, then analyze the log. (To be fair, the log can become
-a permanent debugging aid.) Automatic logging as we discuss in 
+that added code, then analyze the log (To be fair, the log can become
+a permanent debugging aid). Automatic logging as we discuss in 
 section \ref{sec:relatedWork} causes about one or two orders of magnitude slow down as well
@@
 
-%Leo (the non-det values case), other readers
-\subsubsection*{Acknowledgments.} The authors thank Leo Meyerovich for reading a draft of this paper and suggesting the example in section \ref{sec:resultConsistency} and
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
+The authors thank Leo Meyerovich for reading a draft of this paper and suggesting the example in section \ref{sec:resultConsistency} and
 Jan Odvarko and Mike Collins for testing the prototype before our user study and providing helpful suggestions.
 
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
 \begin{thebibliography}{16}
@@
 \newblock \emph{IEEE Transactions on
-Software Engineering}, vol. SE-10, no. 4, pp. 352–357,
+Software Engineering}, vol. SE-10, no. 4, pp. 352-357,
 July 1984.
@@
 
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
 \end{document}

### 2011-03-08 trunk/papers/fse2011/sig-alternate.tex

--- 2011-03-07 papers/fse2011/sig-alternate.tex
@@
 \usepackage{textcomp}
+\usepackage{listings}
+\usepackage[T1]{fontenc}
 
@@
 \begin{figure}[htp]
-\begin{verbatim}
+
+%\includegraphics[width=.5\textwidth]{
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\lstset{emph={myProperty},emphstyle=\textit}
+%\lstset{backgroundcolor=\color{yellow}}
+\lstdefinelanguage{myLang}
+{morekeywords={html, script, button, if, function, var}}
+
+\begin{lstlisting}[language=myLang, framerule=0pt]
 1 <html>
@@
 43 </html>
-\end{verbatim}
+\end{lstlisting}
+%\end{verbatim}
 \caption{A Web page containing JavaScript code. Some lines not related to our paper have been elided.}
@@
 \begin{figure}[htp]
-\begin{verbatim}
-
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[language=myLang, framerule=0pt]
   function f(){
@@
 C  |  ... , scope 1
-
-\end{verbatim}
+\end{lstlisting}
+%\end{verbatim}
 \caption{A recursive call trace illustrating the scope
@@
 must retain additional information. Consider the following example:
-\begin{center}
-\textit{
- point A : the reproduction point \\
- point B : lastChange(A, bar.x) \\
+
+\lstdefinelanguage{myLang2}
+{morekeywords={point, lastChange}}
+
+\lstset{basicstyle=\small}
+\begin{lstlisting}[language=myLang2, framerule=0pt]
+ point A : the reproduction point 
+ point B : lastChange(A, bar.x) 
  point C : lastChange(B, baz.y) 
- }
- \end{center}
+\end{lstlisting}
+
+%\begin{center}
+%\textit{
+% }
+% \end{center}
+
 where point A is a breakpoint, point B is the last change of the object property \texttt{bar.x} at point A, and
@@
 \begin{figure}[htp]
-\begin{verbatim}
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[language=myLang, framerule=0pt]
 (a) Case 1:
@@
  20 a[++i] = new myConstructor();
-
-\end{verbatim}
+\end{lstlisting} 
+%\end{verbatim}
 \caption{Examples of different cases in getting references to created JavaScript objects.}
@@
 \begin{figure}[htp]
-\begin{verbatim}
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[language=myLang, framerule=0pt]
 10  function parent(){
@@
 23  }    
-\end{verbatim}
+\end{lstlisting}
+%\end{verbatim}
 \caption{Sample JavaScript code demonstrating local and clousure variables.}
@@
 \begin{figure}[htp]
-\begin{verbatim}
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[language=myLang, framerule=0pt]
 10 a = false;
@@
 30 if (a || b) { bug();  /* breakpoint */ }
-\end{verbatim}
+\end{lstlisting}
+%\end{verbatim}
 \caption{\textit{lastChange} on non-deterministic values.}
@@
 we watch control flow forwards. Consider for example,
-\begin{verbatim}
+
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[language=myLang, framerule=0pt]
 44 vector.r = Math.floor(Math.random()*5)*6;
@@
 46   return vector;
-\end{verbatim}
+\end{lstlisting}
+%\end{verbatim}
 where \textit{lastChange} shows us that \texttt{vector.r} is zero at line 44. In our user studies, developers
@@
 \begin{figure}[htp]
-\begin{verbatim}
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[language=myLang, framerule=0pt]
 10 function randomProcess(array){
@@
 32 }
-\end{verbatim}
+\end{lstlisting}
+%\end{verbatim}
 \caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}

### 2011-03-08 papers/fse2011/sig-alternate.tex

@@
 
+Program slicing\cite{Weiser} approaches debugging from a completely different perspective.
+Given a point of interest {\bf S} in a program, a \textit{slice} is an executable subset of the program affecting {\bf S}.
+Many studies have shown ways to compute the slice more quickly or to constrain the slice to a smaller subset of the program \cite{Horwitz, Sridharan}.
+Dynamic slicing \cite{Korel} applies slicing analysis at run time and thus most closely resembles lastChange from among the slicing approaches.
+Our lastChange approach can be related this way: first, allow the developer to select from {\bf S} a key critical value {\bf V}.
+Then compute a slice affecting {\bf V}.
+Show the developer only the most relevant part of that slice (the lastChange).
+Finally iterate towards the fault by chaining new slice-selection criteria.
+
+Both approaches rely on selecting {\bf S}.
+Both approaches differ from breakpoint debugging in analyzing a program from a known good point (e.g.
+start of the program) to {\bf S}.
+Slicing reduces the space the developer needs to search, but provides no guidance within the slice; lastChange explores the slice using developer-selected search criteria, but does not help the developer recognize code that cannot impact {\bf S}.
+Slicing requires a sophisticated compiler-like technology while lastChange builds on familiar run-time debugger technology.
+
 %Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
@@
 
+\bibitem{Horwitz}%[Hofer(2006)]
+S. Horwitz, B. Liblit, and M. Polishchuk. \newblock Better Debugging via Output Tracing and Callstack-Sensitive Slicing.
+\emph{IEEE Transactions on
+Software Engineering}, 36(1):7-19, 2010.
+
 \bibitem{JPDA}%[JSD(2010)]
@@
 
+\bibitem{Korel}%[Ko(2008)]
+B. Korel and J. Laski. \newblock Dynamic Program Slicing.
+\newblock \emph{Information Processing Letters},
+ 29(3):155-163, 1988.
+
 \bibitem{LaToza}%[LaToza(2006)]
@@
 October, 2007.
+
+\bibitem{Sridharan}%[Boothe(2000)]
+M. Sridharan, S.J. Fink , and R. Bodik. \newblock Thin slicing.
+\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
+June, 2007.
 

### 2011-03-09 papers/fse2011/sig-alternate.tex
Edit sections 1 and 2

@@
 analyzing complicated data make debugging difficult and time-consuming. 
-Enhancements to debugging to automate 
-debugging operations save developer 
-time, reducing development costs  and impoving software quality.
+Enhanced debugging operations save  
+time, reducing development costs  and improve software quality.
 
@@
 value appears to be incorrect back to the point were that value was
-set.  Two conventional approaches are used: breakpoint-based and
-log-based debugging. Both approaches require tedious steps of
+set.  Two conventional approaches, breakpoint-based and
+log-based debugging, require tedious steps of
 selecting data to be collected, collecting the data, then analyzing
@@
 insufficient collected data, or to wait a long time because too much
-data is recorded. Once the adequate data is collected, it still
+data is recorded. Once adequate data is collected, it still
 requires analyzing and understanding. Developers usually end up in
 dealing with long log files and analyzing huge amounts of collected data. 
-None of these approaches assist developer in finding origins to a wrong
+Niether approach assists the developer in finding origins to a wrong
 value.
 
-To address these problems, we introduce a new functionality in
-debuggers, \textit{lastChange}, which locates the origin of a wrong
-value. It uses program re-execution similar to the practice
-in using breakpoints and manually inserted log statements. 
+Our new functionality in
+debuggers, \textit{lastChange}, locates the origin of a wrong
+value by queries on the running program.
 Imagine that a program execution is
@@
 suspicious about the value of a variable or an object property. The
-developer queries \textit{lastChange} on the value. The debugger
-reproduces the buggy execution and collects data
+developer selects \textit{lastChange} on the value. The debugger
+replays the buggy execution and collects data
 when the data field changes. Once the execution reaches the same place 
@@
 
-As we detail in section \ref{sec:relatedWork}, numerous papers explore forms 
-of automatic logging of program state, augmented with queries on the log. 
-This replaces the developer time needed to 
-insert statement manually with computer time to write the voluminious logs. 
-Our approach uses semi-automatic live-execution queries: user interface 
-operations allow the developer to select queries and these queries operate on the live program during re-execution.
-
-We refer to the breakpoint used in \textit{lastChange} as the
-\textit{reproduction point}: this is any point where the developer knows
-the bug has been reproduced. It is also the point were each \textit{lastChange}
-algorithm cycle ends. The ability to identify this reproduction point, i.e.
- a test case and a breakpoint after the bug has appeared, is the only
-prerequisite for \textit{lastChange} functionality.  This means
-\textit{lastChange} can be implemented on top of a conventional
-breakpoint debugger and it does not require a special environment to
-create identical, instruction by instruction, re-executions.
-
 Our contribution in this paper is the technique \textit{lastChange},
@@
 from that point. The technique builds on existing breakpoint debugger
-technology. We demonstrate the feasibility of the approach with %TODO
+technology  and it does not require a special environment to
+create identical, instruction by instruction, re-executions. We demonstrate the feasibility of the approach with 
 \textit{Querypoint}, an implementation extending Firebug
@@
 summarizes investigated execution points and collected results.
+The \textit{lastChange} algorigthm provides information on important program
+values during the program execution without voluminous logs and without tedious
+ insertion and removal of breakpoints. We believe other queries over the
+ running program can be formulated to generalize this technique.
 
@@
 this value. To do so, the developer runs the \textit{lastChange} command
-on \texttt{myCondition.value} at this point. This re-executes the
-program and pauses at the reproduction point,  showing line 25-the
+on \texttt{myCondition.value} at this point. The debugger re-executes the
+program and break again on line 22, analyzes it queries and shows the developer line 25-the
 place \texttt{oldValue} is assigned to
-\texttt{myCondition.value}. If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
-the debugger can notify the developer that this variable is never assigned a value.
+\texttt{myCondition.value}. (If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
+the debugger can notify the developer that this variable is never assigned a value).
  Now it is clear that the bug occurs because \texttt{oldValue} is
@@
 As demonstrated in Figure~\ref{fig:example-points}, the developer has
-examined three points of execution. The first point, the reproduction point,  was the breakpoint set by the developer.
+examined three points of execution. The first point  was the breakpoint set by the developer. 
+We call this special breakpoint the \textit{reproduction point}.
 The second and third points preceded the reproduction point in execution sequence.

### 2011-03-09 trunk/papers/fse2011/sig-alternate.tex

@@
 \usepackage[T1]{fontenc}
+\usepackage{hyperref}
+\usepackage{cite} %after hyperref
 
@@
 % --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+\conferenceinfo{ESEC/FSE}{'11 SZEGED, HUNGARY}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 analyzing complicated data make debugging difficult and time-consuming. 
-Enhancements to debugging to automate 
-debugging operations save developer 
-time, reducing development costs  and impoving software quality.
+Enhanced debugging operations save  
+time, reduce development costs and improve software quality.
 
@@
 insufficient collected data, or to wait a long time because too much
-data is recorded. Once the adequate data is collected, it still
+data is recorded. Once adequate data is collected, it still
 requires analyzing and understanding. Developers usually end up in
 dealing with long log files and analyzing huge amounts of collected data. 
-None of these approaches assist developer in finding origins to a wrong
+Neither approach efficiently assists the developer in finding origins to a wrong
 value.
 
-To address these problems, we introduce a new functionality in
-debuggers, \textit{lastChange}, which locates the origin of a wrong
-value. It uses program re-execution similar to the practice
-in using breakpoints and manually inserted log statements. 
+Our new functionality in
+debuggers, \textit{lastChange}, locates the origin of a wrong
+value by queries on the running program.
 Imagine that a program execution is
@@
 \texttt{myObject.myProperty} by one (line 15) and calls
-\texttt{updateButton} function which updates button's text to the new
+\texttt{updateButton} function which updates the button's text to the new
 value (line 22).  Once the page is loaded for the first time the
@@
 interesting, and what they do in practice may cause bugs.
-
-By browsing through the code or other means\cite{Barton},
- the developer determines that the value displayed on the 
-button is set at line 22. Since the displayed value is incorrect we know 
-the bug occured before we hit this line.
-To start debugging, the developer sets a breakpoint
-on line 22. Once the button is clicked, execution is paused at line
-22. Figure~\ref{fig:example1} shows the Firebug debugger while the
-execution is paused. Firebug has several panels (e.g., HTML, CSS,
-Script, DOM, etc.) that each demonstrate one aspect of the Web page.
-The Script panel contains the list of all loaded source
-files and regular debugging facilities such as setting breakpoints and
-stepping. To the right of the script panel, the Watch panel shows the program state
-where the developer can examine object and variable values. In our case, the
-\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
 
@@
 
+By browsing through the code or other means\cite{Barton},
+ the developer determines that the value displayed on the 
+button is set at line 22. Since the displayed value is incorrect we know 
+the bug occured before we hit this line.
+To start debugging, the developer sets a breakpoint
+on line 22. Once the button is clicked, execution is paused at line
+22. Figure~\ref{fig:example1} shows the Firebug debugger while the
+execution is paused. Firebug has several panels (e.g., HTML, CSS,
+Script, DOM, etc.) that each demonstrate one aspect of the Web page.
+The Script panel contains the list of all loaded source
+files and regular debugging facilities such as setting breakpoints and
+stepping. To the right of the script panel, the Watch panel shows the program state
+where the developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
+
 To apply backward search strategy for locating defects, the developer
@@
 
+\begin{figure}[htp]
+\centering
+
+\includegraphics[width=.48\textwidth]{5-example-points.png}
+\caption{The examined points before locating the defect.
+The arrow represents the logical forward progress of the program.
+Three actual executions are superimposed on this arrow.
+All three stop at the reproduction point indicated by circle 1.
+After the first execution, the developer asks for lastChange as described in section \ref{sec:introExample}, yielding information  indicated by circle 2.
+After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
+\label{fig:example-points}
+\end{figure}
+
 Looking at line 29, it seems that something is wrong with
@@
 this value. To do so, the developer runs the \textit{lastChange} command
-on \texttt{myCondition.value} at this point. This re-executes the
-program and pauses at the reproduction point,  showing line 25-the
+on \texttt{myCondition.value} at this point. The debugger re-executes the
+program and breaks again on line 22, analyzes its queries and shows the developer line 25-the
 place \texttt{oldValue} is assigned to
-\texttt{myCondition.value}. If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
-the debugger can notify the developer that this variable is never assigned a value.
+\texttt{myCondition.value}. (If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
+the debugger can notify the developer that this variable is never assigned a value).
  Now it is clear that the bug occurs because \texttt{oldValue} is
@@
 
-\begin{figure}[htp]
-\centering
-
-\includegraphics{5-example-points.jpg}
-\caption{The examined points before locating the defect.
-The arrow represents the logical forward progress of the program.
-Three actual executions are superimposed on this arrow.
-All three stop at the reproduction point indicated by circle 1.
-After the first execution, the developer asks for lastChange as described in \ref{sec:introExample}, yielding information  indicated by circle 2.
-After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
-\label{fig:example-points}
-\end{figure}
-
 Notice that in our example, \textit{lastChange} combines some aspects
@@
 program at \textit{lastChange} because we don't know which point is the last
-one until we return to the original breakpoint. (In section 5 we
-discuss cases were it is possible to pause at lines of \textit{lastChange}).
-
-\section{{\large\bf\textit{lastChange}} Algorithm}
+one until we return to the original breakpoint. In section 5 we
+discuss cases were it is possible to pause at lines of \textit{lastChange}.
+
+\section{lastChange Algorithm}
 
@@
 \centering 
-\includegraphics [width=.48\textwidth]{6-foo-changes1.jpg} 
+\includegraphics [width=.48\textwidth] {6-foo-changes1.png} %[width=.48\textwidth][scale=0.75]
 \caption{A hypothetical list of  change events for a property \texttt{foo}. 
@@
 \centering 
-\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
+\includegraphics[width=.40\textwidth]{7-foo-changes2.png}
 \caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
@@
 \centering 
-\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.jpg}
+\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.png}
 \caption{The list of change events stored for locating point B, the
@@
 
-\subsection{{\large\bf\texttt{objectId()}} operation}
+\subsection{{\normalsize\bf\texttt{objectId()}} operation}
 \texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
@@
 
-\subsection{{\large\bf\texttt{setPropertyChangeHook()}} operation}
+\subsection{{\normalsize\bf\texttt{setPropertyChangeHook()}} operation}
 The Firefox JavaScript engine supports watching property changes in an
@@
 
-\subsection{{\large\bf\texttt{scopeId()}} operation}
+\subsection{{\normalsize\bf\texttt{scopeId()}} operation}
 The prototype sets a hook at the beginning of all code blocks needing
@@
 
-\subsection{{\large\bf\texttt{setVariableChangeHook()}} operation}
+\subsection{{\normalsize\bf\texttt{setVariableChangeHook()}} operation}
 Variables defined in local, closure, and catch scopes are only changed in

### 2011-03-09 trunk/papers/fse2011/sig-alternate.tex

@@
 Salman Mirghasemi\\
-       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne, Switzerland}\\
+       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}\\
        \email{salman.mirghasemi@epfl.ch}
@@
 Claude Petitpierre\\
-       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne, Switzerland}\\
+       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Switzerland}\\
        \email{claude.petitpierre@epfl.ch}
@@
 name matches the string. For example, if the string is 
-\texttt{foo} changes to \texttt{bar.foo} or \texttt{baz.foo} would
+\texttt{foo}, changes to \texttt{bar.foo} or \texttt{baz.foo} would
 call the function.  The callback function receives a reference to the
@@
 
-Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
-a code block, enclosed the executing code. In
-JavaScript, a code block can be identified by the file url and  
-the block's first instruction program counter. Given this information, the debugger is
-able to recognize the code block in loaded scripts or once it is loaded.
-Similar to \textit{lastChange} on object property, we define two basic operations: 
-\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one, 
-given a scope returns an integer as the scope's identifier. The second one, 
-given a callback function, a code block and a variable name-which is defined inside the block, the function is called
-whenever the variable is changed.
-
 \begin{figure}[htp]
@@
 
-Figure~\ref{fig:recursive} illustrates how the \texttt{ScopeId()} operation separates instances 
+Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
+a code block, enclosed the executing code. In
+JavaScript, a code block can be identified by the file url and  
+the block's first instruction program counter. Given this information, the debugger is
+able to recognize the code block in loaded scripts or once it is loaded.
+Similar to \textit{lastChange} on object property, we define two basic operations: 
+\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one, 
+given a scope returns an integer as the scope's identifier. The second one, 
+given a callback function, a code block and a variable name-which is defined inside the block, the function is called
+whenever the variable is changed.
+
+Figure~\ref{fig:recursive} illustrates how the \texttt{scopeId()} operation separates instances 
 of a variable in different scopes having the same name.
@@
 \caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
-change event the scope id returns by \texttt{ScopeId()} is recorded along with call stack and program state information. 
+change event the scope id returns by \texttt{scopeId()} is recorded along with call stack and program state information. 
    The last column having the scope id \texttt{foo} at the reproduction point indicates 

### 2011-03-09 trunk/papers/fse2011/sig-alternate.tex

@@
 To start debugging, the developer sets a breakpoint
-on line 22. Once the button is clicked, execution is paused at line
+on line 22. Once the button is clicked, the execution is paused at line
 22. Figure~\ref{fig:example1} shows the Firebug debugger while the
@@
  Now it is clear that the bug occurs because \texttt{oldValue} is
-\texttt{undefined} once execution reaches line 25 (Figure~\ref{fig:example4}).
+\texttt{undefined} once the execution reaches line 25 (Figure~\ref{fig:example4}).
 
@@
 frame locations, and other state values in scope at the call point. 
-Then the callback returns to continue execution. Thus the query is not 
+Then the callback returns to continue the execution. Thus the query is not 
 a breakpoint in the sense of pausing for user interaction, but breakpoint 
@@
 \texttt{for(property in object)} loops. 
-The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty} provides an alternative via \texttt{defineProperty} a standard JavaScript
+The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference\\/Global\_Objects/Object/defineProperty} provides an alternative via \texttt{defineProperty} a standard JavaScript
 function which receives 

### 2011-03-10 papers/fse2011/sig-alternate.tex
cut back to almost 10 pages

@@
 \begin{abstract}
-Developers often seek the origins of wrong values they see in their
-debugger. Their search must be backwards in time: the code causing the
-wrong value executed before the wrong value appeared. Searching with
-breakpoint- or log- based debuggers demands persistence and
-significant experience with the application being debugged. 
+%Developers often seek the origins of wrong values they see in their
+%debugger. Their search must be backwards in time: the code causing the
+%wrong value executed before the wrong value appeared. Searching with
+%breakpoint- or log- based debuggers demands persistence and
+%significant experience with the application being debugged. 
 We introduce a new, practical feature for debuggers called \textit{lastChange}, 
@@
 Enhanced debugging operations save  
-time, reducing development costs  and improve software quality.
+time, reduce development costs and improve software quality.
 
@@
 dealing with long log files and analyzing huge amounts of collected data. 
-Niether approach assists the developer in finding origins to a wrong
+Neither approach efficiently assists the developer in finding origins to a wrong
 value.
@@
 
+By browsing through the code or other means\cite{Barton},
+ the developer determines that the value displayed on the 
+button is set at line 22. Since the displayed value is incorrect we know 
+the bug occured before we hit this line.
+To start debugging, the developer sets a breakpoint
+on line 22. Once the button is clicked, the execution is paused at line
+22. Figure~\ref{fig:example1} shows the Firebug debugger while the
+execution is paused. Firebug has several panels (e.g., HTML, CSS,
+Script, DOM, etc.) that each demonstrate one aspect of the Web page.
+The Script panel contains the list of all loaded source
+files and regular debugging facilities such as setting breakpoints and
+stepping. To the right of the script panel, the Watch panel shows the program state
+where the developer can examine object and variable values. In our case, the
+\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
+
 To apply backward search strategy for locating defects, the developer
@@
 on \texttt{myCondition.value} at this point. The debugger re-executes the
-program and break again on line 22, analyzes it queries and shows the developer line 25-the
+program and breaks again on line 22, analyzes its queries and shows the developer line 25-the
 place \texttt{oldValue} is assigned to
@@
 variable. These scopes are not necessarily regular JavaScript
-objects. Scope object is usually a transient copy of a native object. 
+objects.  
 Therefore, to track changes to a variable in these scopes we
 employ a different approach.
-
-Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
-a code block, enclosed the executing code. In
-JavaScript, a code block can be identified by the file url and  
-the block's first instruction program counter. Given this information, the debugger is
-able to recognize the code block in loaded scripts or once it is loaded.
-Similar to \textit{lastChange} on object property, we define two basic operations: 
-\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one, 
-given a scope returns an integer as the scope's identifier. The second one, 
-given a callback function, a code block and a variable name-which is defined inside the block, the function is called
-whenever the variable is changed.
 
@@
 
-Figure~\ref{fig:recursive} illustrates how the \texttt{ScopeId()} operation separates instances 
+Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
+a code block, enclosed the executing code. In
+JavaScript, a code block can be identified by the file url and  
+the block's first instruction program counter. Given this information, the debugger is
+able to recognize the code block in loaded scripts or once it is loaded.
+Similar to \textit{lastChange} on object property, we define two basic operations: 
+\texttt{scopeId()} -- which returns an integer given a scope -- and \texttt{setVariableChangeHook()} -- which calls its first parameter, a callback function, when a 
+variable in its second parameter, a code block, mathes the name given in the third parameter.
+
+Figure~\ref{fig:recursive} illustrates how the \texttt{scopeId()} operation separates instances 
 of a variable in different scopes having the same name.
@@
 \centering 
-\includegraphics[width=.48\textwidth]{7-foo-changes2.jpg}
+\includegraphics[width=.40\textwidth]{7-foo-changes2.png}
 \caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
-change event the scope id returns by \texttt{ScopeId()} is recorded along with call stack and program state information. 
+change event the scope id returns by \texttt{scopeId()} is recorded along with call stack and program state information. 
    The last column having the scope id \texttt{foo} at the reproduction point indicates 
@@
 arrive at the reproduction point and discover the id of the requested value.
-When we perform \textit{lastChange} based on a previous \textit{lastChange} the query algorithm 
+When we perform \textit{lastChange} based on a previous \textit{lastChange}, the query algorithm 
 must retain additional information. Consider the following example:
@@
 asks for the last change of \texttt{baz.y}, we need to track objects named \texttt{baz}
-at changes of \texttt{bar.x} and changes to objects named \texttt{y}. Then at the reproduction point
+at changes of \texttt{bar.x} and changes to objects named \texttt{y}. Then, at the reproduction point,
 we need to work out which \texttt{baz} the developer wanted, then select the last change of that \texttt{baz.y}.
-Figure~\ref{fig:lastchange-lastchange} illustrates the extra row of data tracking of \texttt{baz} objects 
-at \texttt{x} change events 
+Figure~\ref{fig:lastchange-lastchange} illustrates the extra row of data (tracking of \texttt{baz} objects 
+at \texttt{x} change events) 
 and how the id values allow the last change of \texttt{baz.y} to be worked out.
@@
 The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and 
-\textit{Querypoint} is developed over this interface.
-Our prototype implementation defines our four primitive operations in JavaScript code and using techniques which are cumbersome and comparatively slow to execute.
-However the JavaScript prototype is
+\textit{Querypoint} is developed over this interface. Our prototype implements the four primitive operations in JavaScript 
+using techniques which are cumbersome and comparatively slow to execute. However the JavaScript prototype is
 easy to explore, change, and share with others for feedback.
@@
 otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. This use of a regular object property  might change
-the program behaviour. For example it will apear as an extra property in 
-\texttt{for(property in object)} loops. 
-The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference/Global\_Objects\\/Object/defineProperty} provides an alternative via \texttt{defineProperty} a standard JavaScript
-function which receives 
-an argument specifying whether the property is enumerable or not. By setting the enumerable
-field \texttt{false} for \texttt{\_objectId}, this property will not
-apear in \texttt{for(property in object)} loops and therefore has no
-effect on the program execution. Note that \texttt{\_objectId} is
-not set for all objects but only those objects that need an id.
-
-\subsection{{\large\bf\texttt{setPropertyChangeHook()}} operation}
+for each new \texttt{\_objectId} needed. 
+%\footnote[3]{This use of a regular object property  might change
+%the program behaviour. For example it will appear as an extra property in 
+%\texttt{for(property in object)} loops. 
+%The next version of Firefox (https://developer.mozilla.org/en/JavaScript/Reference\\/Global\_Objects/Object/defineProperty) provides \texttt{defineProperty}, 
+%allowing a property to be added which is invisible to enumeration.} Note that \texttt{\_objectId} is
+%not set for all objects but only those objects that need an id.
+
+\subsection{{\normalsize\bf\texttt{setPropertyChangeHook()}} operation}
 The Firefox JavaScript engine supports watching property changes in an
@@
 excepting the global object and its predefined properties is available.  For 
-our \textit{lastChange} prototype we created a version of
+our \textit{lastChange} prototype, we created a version of
 \texttt{setPropertyChangeHook()}.  The basic strategy is to get a reference to the object just
@@
 JavaScript engine, we can get file URL and line number for each object
-creation (e.g., myFile.js, line 24). We set a hook on this line
+creation (e.g., myFile.js, line 24). We set a breakpoint on this line
 and parse the source code to determine which object was created.
@@
 
-\subsection{{\large\bf\texttt{scopeId()}} operation}
-The prototype sets a hook at the beginning of all code blocks needing
+\subsection{{\normalsize\bf\texttt{scopeId()}} operation}
+The prototype sets a breakpoint at the beginning of all code blocks needing
 a scope id. The scope id is kept as a variable with name 
@@
 will be set, but if the execution is paused at line 20 , four hooks on
-lines 11, 12, 14, 20 will be set. These two cases are different due
-the fact that \texttt{myVar} in \texttt{firstChild} is a local variable
-but in \texttt{secondChild} is a closure variable.
+lines 11, 12, 14, 20 will be set. These two cases are different: \texttt{myVar} in 
+\texttt{firstChild} is a local variable
+but in \texttt{secondChild} it is a closure variable.
 
@@
 
-To build a test case from one execution, two elements should be carefully 
-considered. First, the initial state should be the same as the initial state
-of execution. Second, similar actions and events should be applied to
-the program during the execution. \textit{Querypoint} supports two mechanism
+The \textit{Querypoint} prototype supports two mechanism
 for automatic re-execution: callstack-reproduction and record-replay. In callstack reproduction the function from
@@
 \section{Reproducible Non-deterministic Execution}
-We claimed that the only prerequisite for \textit{lastChange} function is bug
-reproducibility. A bug is \textit{reproducible} for a developer when the developer can
+We claim that the only prerequisite for \textit{lastChange}  is bug-reproducibility. 
+A bug is \textit{reproducible} for a developer when the developer can
 start from a determined initial state, operate on the program with a
@@
 events during the execution. Conversely, if the defect depends on the order of execution, 
-it will likely fail to reproduce on every execution. By relying on reproducibility but 
+it will likely fail to reproduce on some executions. By relying on reproducibility but 
 not requiring deterministic execution, \textit{lastChange} covers the common case 
@@
 
-There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
-to formulate a conditional breakpoint.
-Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
-array. The array contains numbers except one item which is
-\texttt{undefined} and it causes a bug in line 30. There is a call to
-\texttt{randomPermutation} function in line 11 which randomly
-permutes the array item. So at every execution the
-\texttt{undefined} item will be in a new place. Calling
-\textit{lastChange} on \texttt{x} at the place the bug happens, gives a
-point which shows line 14. Although this point exists at every
-re-execution but it can not be identified by an event index. A conditional breakpoint on 
-the value of the item would succeed and the developer can reason from the 
-\textit{lastChange} results to create the condition.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[language=myLang, framerule=0pt]
-10 function randomProcess(array){
-11   randomPermutation(array);
-12   var x, y;
-13   for (var i=0 ; i<array.length ; i++){
-14      x = array[i]
-...
-30      y = x+1;
-31   }
-32 }
-\end{lstlisting}
-%\end{verbatim}
-\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
-\label{fig:counter-example}
-\end{figure}
+% Cut to reduce size
+%There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
+%to formulate a conditional breakpoint.
+%Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
+%array. The array contains numbers except one item which is
+%\texttt{undefined} and it causes a bug in line 30. There is a call to
+%\texttt{randomPermutation} function in line 11 which randomly
+%permutes the array item. So at every execution the
+%\texttt{undefined} item will be in a new place. Calling
+%\textit{lastChange} on \texttt{x} at the place the bug happens, gives a
+%point which shows line 14. Although this point exists at every
+%re-execution but it can not be identified by an event index. A conditional breakpoint on 
+%the value of the item would succeed and the developer can reason from the 
+\%textit{lastChange} results to create the condition.
+
+%\begin{figure}[htp]
+%\lstset{basicstyle=\scriptsize}
+%\begin{lstlisting}[language=myLang, framerule=0pt]
+%10 function randomProcess(array){
+%11   randomPermutation(array);
+%12   var x, y;
+%13   for (var i=0 ; i<array.length ; i++){
+%14      x = array[i]
+%...
+%30      y = x+1;
+%31   }
+%32 }
+%\end{lstlisting}
+%\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
+%\label{fig:counter-example}
+%\end{figure}
 
 \section{User Study}
-We supplied four experienced Javascript developers with our prototype lastChange in an 
+We supplied four experienced Javascript developers with our prototype in an 
 extended Firebug debugger\footnote[5]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
@@
 Based on our own experience we expect these strategies represent the kinds of approaches 
-developers have available. These operations are time consuming and tedious: all four users 
-found the defect location with just two \textit{lastChange} operations. Based on our measurements,
-this makes \textit{lastChange} about three times faster than breakpoints for the navigation from 
-the reproduction point to the defect
-(We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
-issues have been hidden by the design of our tests). Our results show that, when a defect 
+developers have available. These operations are time consuming and tedious. In contrast, all four users 
+found the defect location with just two \textit{lastChange} operations.
+% Based on our measurements,
+%this makes \textit{lastChange} about three times faster than breakpoints for the navigation from 
+%the reproduction point to the defect
+We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
+issues have been hidden by the design of our tests. Nevertheless our results show that, when a defect 
 relates to incorrect values and a developer recognizes this, then the operational 
@@
 
-The key ingredients in our argument are: 
-\begin{enumerate}
-   \item developers need an operation like \textit{lastChange}, 
-   \item developers can learn to use \textit{lastChange}, 
-   \item practical implementations are feasible with modest
-invested development time,
-   \item in most cases \textit{lastChange} will be much faster than current alternatives,
-   \item the worst cases are not more common or more painful than
-alternatives.
-	 \item the \textit{lastChange} approach can be generalized to other queries.
-\end{enumerate}
+%The key ingredients in our argument are: 
+%\begin{enumerate}
+%   \item developers need an operation like \textit{lastChange}, 
+%   \item developers can learn to use \textit{lastChange}, 
+%   \item practical implementations are feasible with modest
+%invested development time,
+%   \item in most cases \textit{lastChange} will be much faster than current alternatives,
+%   \item the worst cases are not more common or more painful than
+%alternatives.
+%	 \item the \textit{lastChange} approach can be generalized to other queries.
+%\end{enumerate}
 
@@
 
-We have shown how \textit{lastChange} identifies the prior point in
-program execution where a program state value changes. Is it something
-the developer needs to do?  Since ultimately programs are just
+%We have shown how \textit{lastChange} identifies the prior point in
+%program execution where a program state value changes. Is it something
+%the developer needs to do?
+
+Since ultimately programs are just
 transformation of state values, debugging is ultimately backtracking
 to find defects in program state change\cite{Weiser,Zeller}.  When a developer halts a
-program on a breakpoint they have three kinds of information: a model
-of the program in their mind, a call stack showing what part of the
-program is halted, and the state at that point (a combination of the
-debugger's view of the program internal state and the output of the
-program up to this point of execution). If the model does not match
-the call stack or if no value in the viewable program state aligns
-with the developers model for this point in execution, the developer
-will seek another view by changing the breakpoint or the input
-data. If a value appears incorrect, they may have a flash of insight
-and know the defect. Otherwise they need to figure out what operation
+program on a breakpoint they compare the call stack and program state to their model of the program.
+If any value seems to be incorrect,  they need to figure out what operation
 causes the incorrect value. Here \textit{lastChange} takes over and addresses a key
 part of the debugging process.
+%have three kinds of information: a model
+%of the program in their mind, a call stack showing what part of the
+%program is halted, and the state at that point (a combination of the
+%debugger's view of the program internal state and the output of the
+%program up to this point of execution). If the model does not match
+%the call stack or if no value in the viewable program state aligns
+%with the developers model for this point in execution, the developer
+%will seek another view by changing the breakpoint or the input
+%data. If a value appears incorrect, they may have a flash of insight
+%and know the defect. Otherwise they need to figure out what operation
+%causes the incorrect value. Here \textit{lastChange} takes over and addresses a key
+%part of the debugging process.
 
@@
 
-If \texttt{lastChange} could be useful, can developers figure out how
-to use it? While our user study was small, our prototype demonstrates that
+%If \texttt{lastChange} could be useful, can developers figure out how
+%to use it? 
+While our user study was small, our prototype demonstrates that
 \textit{lastChange} can be easily activated by operations on the
 graphical representation of erroneous data in a debugger and the 
-results can be interpreted by users. We designed the
-user interface for the results from \textit{lastChange} to resemble
-the results from a breakpoint, with the source code of the change
-point highlighted and the state of the program presented the way state
-is presented from a breakpoint. Based on this user interface, we
-believe developers can start to use \textit{lastChange} with minimal
-training. Our users may not be representative, but the key point here
-is that the learning curve is small compared with the challenge of learning 
-breakpoint debugging in the first place.
-
+results can be interpreted by users. 
 While \textit{lastChange} is not a breakpoint, 
@@
 same operation developers use to debug with breakpoints.
-In our own experience, \textit{lastChange} dramatically reduces the work in
-setting and removing breakpoints, so work to cause re-execution  become noticable.
-Therefore automatic mechanisms
-for re-execution will be corresponding more valuable for debugging
-with \textit{lastChange} (Our \textit{Querypoint} prototype  
-implements a simple form of automatic 
-re-execution for both breakpoint and \textit{lastChange}).
+
+%We designed the
+%user interface for the results from \textit{lastChange} to resemble
+%the results from a breakpoint, with the source code of the change
+%point highlighted and the state of the program presented the way state
+%is presented from a breakpoint. Based on this user interface, we
+%believe developers can start to use \textit{lastChange} with minimal
+%training. Our users may not be representative, but the key point here
+%is that the learning curve is small compared with the challenge of learning 
+%breakpoint debugging in the first place.
+
+%In our own experience, \textit{lastChange} dramatically reduces the work in
+%setting and removing breakpoints, so work to cause re-execution  become noticable.
+%Therefore automatic mechanisms
+%for re-execution will be corresponding more valuable for debugging
+%with \textit{lastChange} (Our \textit{Querypoint} prototype  
+%implements a simple form of automatic 
+%re-execution for both breakpoint and \textit{lastChange}).
 
@@
 implementation would require access to the object id at the point of
-object creation and \texttt{setPropertyChan geHook()}. Many
+object creation and \texttt{setPropertyChangeHook()}. Many
 object-oriented runtimes provide object identifiers and 
 provide access to object creation directly or by bytecode instrumentation\cite{JPDA}. 
-In the particular case of the Firefox Web browser we used for our prototype, the primary barrier
-to practical implementation would likely be integration with the
-increasingly sophisticated just in time compilers. In the case of
-tracking variable changes, \texttt{setVariableChangeHook()} can be implemented
-similar to \texttt{setPropertyChangeHook()} if JavaScript scopes-like regular 
-JavaScript objects-support \texttt{watch()} function.
+%In the particular case of the Firefox Web browser we used for our prototype, the primary barrier
+%to practical implementation would likely be integration with the
+%increasingly sophisticated just in time compilers. In the case of
+%tracking variable changes, \texttt{setVariableChangeHook()} can be implemented
+%similar to \texttt{setPropertyChangeHook()} if JavaScript scopes-like regular 
+%JavaScript objects-support \texttt{watch()} function.
 
@@
 
-When developers try \textit{lastChange}, will they get results fast
-enough to benefit? While we only used our prototype on toy programs,
-\textit{lastChange} seemed as fast as breakpoint re-execution.
-But what can we say about realistic programs?
+%When developers try \textit{lastChange}, will they get results fast
+%enough to benefit? While we only used our prototype on toy programs,
+%\textit{lastChange} seemed as fast as breakpoint re-execution.
+%But what can we say about realistic programs?
 
@@
 
-We implemented a
-simple and effective mechanism allowing developers to control 
-overhead: we stored data to a depth of two property accesses 
-(e.g. foo.bar.x), then placed a \textit{re-run} button 
-in the user interface at the third level. If developers reached the 
-third level they can see more data at the cost of one more replay.
-
-For comparison we should use the practical alternative: developers
+%We implemented a
+%simple and effective mechanism allowing developers to control 
+%overhead: we stored data to a depth of two property accesses 
+%(e.g. foo.bar.x), then placed a \textit{re-run} button 
+%in the user interface at the third level. If developers reached the 
+%third level they can see more data at the cost of one more replay.
+
+For comparison consider today's practical alternative: developers
 setting breakpoints. For the vast majority of programs, a developer
 will take much more time to set one breakpoint than
-\textit{lastChange} would add. But typically the developer may not
+\textit{lastChange} would add. Moreover, typically the developer may not
 guess the point of last change. They must then ponder another
-breakpoint and re-execute. Unlike the re-execution we use to 
-optimize performance in \textit{lastChange}, 
-developers still will not know if the breakpoint they hit is the point of last change
- or even if it is related to the change at all.
+breakpoint and re-execute.
+
+%Unlike the re-execution we use to 
+%optimize performance in \textit{lastChange}, 
+%developers still will not know if the breakpoint they hit is the point of last change
+ %or even if it is related to the change at all.
 
@@
 
-Finally we consider the worst cases: what about code that changes
-objects in long running loops? Every time through the loop we incur
+%Finally we consider the worst cases: what about code that changes
+%objects in long running loops? 
+Every time through the loop we incur
 the call back overhead; if the loop itself has relatively little code
@@
 enormous. 
-
-These are difficult issues for other techniques as well:  breakpoints are not feasible in these cases and logging
-becomes unwieldy. Since automatic logging solutions are highly tuned,
-their overhead in this case will likely be much less than
-\textit{lastChange}. On the other hand, \textit{lastChange} integrates
-with an interactive debugger and detecting that we are in a high
-overhead loop is simply a matter of checking our internal counter. In
-such unusual cases we may simply offer the developer the option of
-studying the loop code then omitting it from \textit{lastChange}
-operations. Developers face this issue with any debugger today: occasionally a
+Other techniques also struggle with this case:  breakpoints in highly repeating loops are not feasible and logging
+becomes unwieldy. 
+Developers face this issue with any debugger today: occasionally a
 debugger causes too much overhead to be useful for debugging. 
-The users of \textit{lastChange} may encounter these kinds of cases, but 
-that is the nature of debugging: you need different tools for 
-different kinds of problems.
+%Since automatic logging solutions are highly tuned,
+%their overhead in this case will likely be much less than
+%\textit{lastChange}. On the other hand, \textit{lastChange} integrates
+%with an interactive debugger and detecting that we are in a high
+%overhead loop is simply a matter of checking our internal counter. %
+%In
+%such unusual cases we may simply offer the developer the option of
+%studying the loop code then omitting it from \textit{lastChange}
+%operations. 
+%
+%The users of \textit{lastChange} may encounter these kinds of cases, but 
+%that is the nature of debugging: you need different tools for 
+%different kinds of problems.
 
@@
 Our \textit{lastChange} algorithm can be viewed as a particular interface to a general facility. 
-The general facility replays execution, querys the runtime at points of interest during execution,
+The general facility replays execution, queries the runtime at points of interest during execution,
 and analyzes the result at the reproduction point. We have selected one kind of query and analysis
@@
 kinds of queries and analysis can be invented and integrated to automate other aspects of debugging.
-Moreover, the query history analysis used to test for non-determinism here may also be the basis for
-more effective user interfaces to debugging sessions. The series of cascaded \textit{lastChange} queries becomes 
-logical path followed by the developer seeking the defect and this path may be useful if presented in effective user interfaces.
+%Moreover, the query history analysis used to test for non-determinism here may also be the basis for
+%more effective user interfaces to debugging sessions. The series of cascaded \textit{lastChange} queries becomes 
+%logical path followed by the developer seeking the defect and this path may be useful if presented in effective user interfaces.
 

### 2011-03-10 papers/fse2011/sig-alternate.tex

@@
 \usepackage{graphicx}
+\usepackage{xcolor}
 \usepackage{subfigure} %[tight,normalsize]
@@
 works backwards, moving from a point in the program execution where a
-value appears to be incorrect back to the point were that value was
+value appears to be incorrect back to the point where that value was
 set.  Two conventional approaches, breakpoint-based and
@@
 summarizes investigated execution points and collected results.
-The \textit{lastChange} algorigthm provides information on important program
+The \textit{lastChange} algorithm provides information on important program
 values during the program execution without voluminous logs and without tedious
@@
 button is set at line 22. Since the displayed value is incorrect we know 
-the bug occured before we hit this line.
+the bug occurred before we hit this line.
 To start debugging, the developer sets a breakpoint
@@
 where the developer can examine object and variable values. In our case, the
-\texttt{myObject.myProperty} value at the paused point is zero. We expected this value to be \texttt{2}.
+\texttt{myObject.myProperty} value at the paused point is \texttt{0}. We expected this value to be \texttt{2}.
 
@@
 
-\includegraphics[width=.48\textwidth]{5-example-points.png}
+\includegraphics [width=.48\textwidth]{5-example-points.pdf} 
 \caption{The examined points before locating the defect.
@@
 place \texttt{oldValue} is assigned to
-\texttt{myCondition.value}. (If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
-the debugger can notify the developer that this variable is never assigned a value).
+\texttt{myCondition.value}. If the developer asks for \textit{lastChange} on \texttt{oldValue}, 
+the debugger can notify the developer that this variable is never assigned a value.
  Now it is clear that the bug occurs because \texttt{oldValue} is
@@
 Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, height=.17\textheight
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
   ]{1-bp22.jpg}}
@@
 one until we return to the original breakpoint. In section 5 we
-discuss cases were it is possible to pause at lines of \textit{lastChange}.
+discuss cases where it is possible to pause at lines of \textit{lastChange}.
 
@@
 \centering 
-\includegraphics [width=.48\textwidth] {6-foo-changes1.png} %[width=.48\textwidth][scale=0.75]
+\includegraphics [width=.48\textwidth] {6-foo-changes1.pdf} %[width=.48\textwidth][scale=0.75]
 \caption{A hypothetical list of  change events for a property \texttt{foo}. 
@@
 \centering 
-\includegraphics[width=.40\textwidth]{7-foo-changes2.png}
+\includegraphics[width=.40\textwidth]{7-foo-changes2.pdf}
 \caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
@@
 \centering 
-\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.png}
+\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.pdf}
 \caption{The list of change events stored for locating point B, the
@@
 %the value of the item would succeed and the developer can reason from the 
-\%textit{lastChange} results to create the condition.
+%textit{lastChange} results to create the condition.
 

### 2011-03-10 trunk/papers/fse2011/sig-alternate.tex

@@
 chain and the first scope which has a variable with the same name is
-the variable's scope. There are five different scope types: local,
-global, \texttt{with}, closure and \texttt{catch}. We explain these
+the variable's scope. There are five different scope types: global, local,
+closure, \texttt{with} and \texttt{catch}. We explain these
 cases in two groups.
@@
 variable. These scopes are not necessarily regular JavaScript
-objects. Scope object is usually a transient copy of a native object. 
+objects.  
 Therefore, to track changes to a variable in these scopes we
@@
 %\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[language=myLang, framerule=0pt]
-  function f(){
-    var x = 0;
-    x++;
-    if (!stop) f();
-  }
-
-Sample Trace:
-
-   f()
-A  |  x changes, scope 1 
-   |  f()
-   |  |  x changes, scope 2
-   |  |  f()
-B  |  |  |  x changes, scope 3 
-C  |  ... , scope 1
-\end{lstlisting}
+\includegraphics [width=.48\textwidth] {9-scopes.pdf} %[width=.48\textwidth][scale=0.75]
+
+%\lstset{basicstyle=\scriptsize}
+%\begin{lstlisting}[language=myLang, framerule=0pt]
+%  function f(){
+%    var x = 0;	
+%    x++;
+%    ...
+%    if (!stop) f();
+%  }
+
+%Sample Trace:
+
+%   f()
+%A  |  x changes, scope 1 
+%   |  f()
+%   |  |  x changes, scope 2
+%   |  |  f()
+%B  |  |  |  x changes, scope 3 
+%C  |  ... , scope 1
+%\end{lstlisting}
 %\end{verbatim}
@@
 Similar to \textit{lastChange} on object property, we define two basic operations: 
-\texttt{scopeId()} and \texttt{setVariableChangeHook()}. The first one, 
-given a scope returns an integer as the scope's identifier. The second one, 
-given a callback function, a code block and a variable name-which is defined inside the block, the function is called
-whenever the variable is changed.
+\texttt{scopeId()} -- which returns an integer given a scope -- and \texttt{setVariableChangeHook()} -- which calls its first parameter, a callback function, when a 
+variable in its second parameter, a code block, matches the name given in the third parameter.
 
@@
 otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. This use of a regular object property  might change
-the program behaviour. For example it will apear as an extra property in 
-\texttt{for(property in object)} loops. 
-The next version of Firefox\footnote[3]{https://developer.mozilla.org/en/JavaScript/Reference\\/Global\_Objects/Object/defineProperty} provides an alternative via \texttt{defineProperty} a standard JavaScript
-function which receives 
-an argument specifying whether the property is enumerable or not. By setting the enumerable
-field \texttt{false} for \texttt{\_objectId}, this property will not
-apear in \texttt{for(property in object)} loops and therefore has no
-effect on the program execution. Note that \texttt{\_objectId} is
-not set for all objects but only those objects that need an id.
+for each new \texttt{\_objectId} needed. 
+%\footnote[3]{This use of a regular object property  might change
+%the program behaviour. For example it will appear as an extra property in 
+%\texttt{for(property in object)} loops. 
+%The next version of Firefox (https://developer.mozilla.org/en/JavaScript/Reference\\/Global\_Objects/Object/defineProperty) provides \texttt{defineProperty}, 
+%allowing a property to be added which is invisible to enumeration.} Note that \texttt{\_objectId} is
+%not set for all objects but only those objects that need an id.
 
@@
 \subsection{{\normalsize\bf\texttt{scopeId()}} operation}
-The prototype sets a hook at the beginning of all code blocks needing
+The prototype sets a breakpoint at the beginning of all code blocks needing
 a scope id. The scope id is kept as a variable with name 
@@
 
-There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
-to formulate a conditional breakpoint.
-Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
-array. The array contains numbers except one item which is
-\texttt{undefined} and it causes a bug in line 30. There is a call to
-\texttt{randomPermutation} function in line 11 which randomly
-permutes the array item. So at every execution the
-\texttt{undefined} item will be in a new place. Calling
-\textit{lastChange} on \texttt{x} at the place the bug happens, gives a
-point which shows line 14. Although this point exists at every
-re-execution but it can not be identified by an event index. A conditional breakpoint on 
-the value of the item would succeed and the developer can reason from the 
-\textit{lastChange} results to create the condition.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[language=myLang, framerule=0pt]
-10 function randomProcess(array){
-11   randomPermutation(array);
-12   var x, y;
-13   for (var i=0 ; i<array.length ; i++){
-14      x = array[i]
-...
-30      y = x+1;
-31   }
-32 }
-\end{lstlisting}
-%\end{verbatim}
-\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
-\label{fig:counter-example}
-\end{figure}
+% Cut to reduce size
+%There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
+%to formulate a conditional breakpoint.
+%Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
+%array. The array contains numbers except one item which is
+%\texttt{undefined} and it causes a bug in line 30. There is a call to
+%\texttt{randomPermutation} function in line 11 which randomly
+%permutes the array item. So at every execution the
+%\texttt{undefined} item will be in a new place. Calling
+%\textit{lastChange} on \texttt{x} at the place the bug happens, gives a
+%point which shows line 14. Although this point exists at every
+%re-execution but it can not be identified by an event index. A conditional breakpoint on 
+%the value of the item would succeed and the developer can reason from the 
+%textit{lastChange} results to create the condition.
+
+%\begin{figure}[htp]
+%\lstset{basicstyle=\scriptsize}
+%\begin{lstlisting}[language=myLang, framerule=0pt]
+%10 function randomProcess(array){
+%11   randomPermutation(array);
+%12   var x, y;
+%13   for (var i=0 ; i<array.length ; i++){
+%14      x = array[i]
+%...
+%30      y = x+1;
+%31   }
+%32 }
+%\end{lstlisting}
+%\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
+%\label{fig:counter-example}
+%\end{figure}
 
 \section{User Study}
-We supplied four experienced Javascript developers with our prototype lastChange in an 
+We supplied four experienced Javascript developers with our prototype in an 
 extended Firebug debugger\footnote[5]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 

### 2011-03-10 papers/fse2011/sig-alternate.tex

@@
 \textit{lastChange} can be called on object property, on a variable value, 
-or on the results of a \textit{lastChange}. We explain each case in the following subsections.
+or on the results of a \textit{lastChange}. Moroever, common data structures such as
+arrays and hashmaps are also supported as special cases of \textit{lastChange} on object property.
+We explain each case in the following subsections.
 
@@
 \texttt{scopeId()} -- which returns an integer given a scope -- and \texttt{setVariableChangeHook()} -- which calls its first parameter, a callback function, when a 
-variable in its second parameter, a code block, mathes the name given in the third parameter.
+variable in its second parameter, a code block, matches the name given in the third parameter.
 
@@
  \FOR {$p$ is defined at the $q$ result}
-   \IF {$p$ is a lastChange on object property} 
-     \STATE the property owner id should be stored at $q$ change events. 
-   \ELSIF {$p$ is a lastChange on variable} 
-     \STATE the variable scope id should be stored at $q$ change events.
+   \IF {$p$ is a $lastChange$ on object property} 
+     \STATE the property {\bf owner id} must be stored at $q$ change events. 
+   \ELSIF {$p$ is a $lastChange$ on variable} 
+     \STATE the variable {\bf scope id} must be stored at $q$ change events.
 	 \ENDIF 
@@
 In the case that the execution is deterministic, the \textit{lastChange}
-event index can be used as an index for a conditional breakpoint. 
+event index can be used as an index for a conditional breakpoint \cite{Boothe, Maruyama}. 
 Moreover, this works in a non-deterministic execution if non-determinism

### 2011-03-10 trunk/papers/fse2011/sig-alternate.tex

@@
 
-\begin{lstlisting}[language=myLang, framerule=0pt]
+\begin{lstlisting}[frame=single, language=myLang] %, framerule=0pt]
+
 1 <html>
@@
 \lstset{basicstyle=\small}
-\begin{lstlisting}[language=myLang2, framerule=0pt]
+\begin{lstlisting}[frame=single, language=myLang2] %, framerule=0pt]
+
  point A : the reproduction point 
@@
 \centering 
+\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.pdf}
+\caption{The list of change events stored for locating point B, the
+  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
+  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
+\label{fig:lastchange-lastchange}
+\end{figure}
+
+\begin{figure}[htp]
+\centering 
 %\begin{algorithm}
+\begin{frame}
 \begin{algorithmic}
@@
 \end{algorithmic}
+\end{frame}
 %\end{algorithm}
@@
 \end{figure}
-
 %---------------------------------------------------------------------------------------------------
@@
 
-\begin{figure}[htp]
-\centering 
-\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.pdf}
-\caption{The list of change events stored for locating point B, the
-  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
-  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
-\label{fig:lastchange-lastchange}
-\end{figure}
-
 \subsection{{\normalsize\bf\texttt{objectId()}} operation}
@@
 \lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[language=myLang, framerule=0pt]
+\begin{lstlisting}[frame=single, language=myLang]% framerule=0pt]
+
 (a) Case 1:
@@
 \lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[language=myLang, framerule=0pt]
+\begin{lstlisting}[frame=single, language=myLang]%, framerule=0pt]
+
 10  function parent(){
@@
 \lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[language=myLang, framerule=0pt]
+\begin{lstlisting}[frame=single, language=myLang]%, framerule=0pt]
+
 10 a = false;
@@
 \lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[language=myLang, framerule=0pt]
+\begin{lstlisting}[frame=single, language=myLang] % framerule=0pt]
+
 44 vector.r = Math.floor(Math.random()*5)*6;

### 2011-03-10 papers/fse2011/sig-alternate.tex
final cuts to 10 pages

@@
 A bug is \textit{reproducible} for a developer when the developer can
-start from a determined initial state, operate on the program with a
+start from a given initial state, operate on the program with a
 list of actions, and reproduce the symptoms of the bug. The details of
@@
 are not deterministic.  
-
- In this section we discuss non-determinism and \textit{lastChange}. However we want 
-to emphasize that when developers have to think about non-determistic execution 
-it usually means that bugs are not reproducible. 
-The reproducibility of the bug
-means that the defect is very unlikely to depend on the order of
-events during the execution. Conversely, if the defect depends on the order of execution, 
-it will likely fail to reproduce on some executions. By relying on reproducibility but 
-not requiring deterministic execution, \textit{lastChange} covers the common case 
-developers focus on while not adding addition complexity to the implementation.
+% In this section we discuss non-determinism and \textit{lastChange}. However we want 
+%to emphasize that when developers have to think about non-determistic execution 
+%it usually means that bugs are not reproducible. 
+%The reproducibility of the bug
+%means that the defect is very unlikely to depend on the order of
+%events during the execution. Conversely, if the defect depends on the order of execution, 
+%it will likely fail to reproduce on some executions. 
+By relying on reproducibility but 
+not requiring deterministic execution, \textit{lastChange} works on the same range of cases.
 
@@
 a conventional watchpoint hits, the record may differ each time we
-re-execute. But \textit{lastChange} does not ask the developer to
-consider these single points. Rather it analyzes all of the
-change events in an entire execution at the reproduction point where the bug
-has already occurred and shows the final result to the developer. 
+re-execute. But \textit{lastChange} does not compare values across 
+executions. Rather it analyzes all of the
+change events in a single execution. 
 Neither the data gathering nor the analysis require deterministic execution.
 
-When the developer selects a value and
-asks for \textit{lastChange}, the developer is expressing the hypothesis that
-the value is related to the defect. Since the defect does not depend on
- exeuction order, the reproducibility of
-the bug makes it very unlikely that the \textit{lastChange} will
-depend upon order of events during execution.
-There can be rare cases where the bug is reproducible but the
-value from \textit{lastChange} is not. As in conventional breakpoint
-debugging, we can only determine this empirically, by observing
-multiple executions with different values. Unlike conventional
-breakpoint debugging, implementations of \textit{lastChange} readily
-help in detecting such cases: as we work back through a series of
-\textit{lastChange} requests we can compare values with previous
-executions. Different values on different executions will signal that
-the execution is not deterministic.
-
+Since we don't need to compare values across executions to implement \textit{lastChange}, we can get more information if we do compare:
+ different points of last change on different executions will signal that the execution is not deterministic. (Note the converse is not true, many non-deterministic 
+programs will give identical results for \textit{lastChange}.)
 Consider the example in Figure~\ref{fig:nondeterministic-values}. 
-Assume that at the first exeuction, developers sees that \texttt{a} is \texttt{true} and asks
+Assume that at the first execution, developers sees that \texttt{a} is \texttt{true} and asks
 for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
@@
 it to the \texttt{a} value in the next executions. So if this value is different, debugger informs the developer
-that the \textit{lastChange} query is made on a different value. In cases that the value is not a primitive but an object,
-the primitive properties of the object examined by the developer are stored and compared.
+that the \textit{lastChange} query is made on a different value.
+% In cases that the value is not a primitive but an object,
+%the primitive properties of the object examined by the developer are stored and compared.
 

### 2011-03-11 papers/fse2011/sig-alternate.tex

@@
 
-\subsection{{\large\bf\textit{lastChange}} on object property}
+\subsection{{\large\bf\textit{lastChange}} on Object Property}
 To simplify the algorithm explanation and defer technical details, we
@@
 
-\subsection{{\large\bf\textit{lastChange}} on variable} 
+\subsection{{\large\bf\textit{lastChange}} on Variable} 
 In JavaScript, every frame has a scope chain and every available
@@
 \begin{figure}[htp]
-\centering 
+%\centering 
 %\begin{algorithm}
-\begin{frame}
-\begin{algorithmic}
-
+\line(1,0){240}
+\begin{algorithmic}%[frame=single]
 \FOR{$q$ in $lastChange$ queries} 
@@
 \end{algorithmic}
-\end{frame}
+\line(1,0){240}
 %\end{algorithm}
@@
 using techniques which are cumbersome and comparatively slow to execute. However the JavaScript prototype is
-easy to explore, change, and share with others for feedback.
-  A professionally useful debugger would implement these primitive operations within the JavaScript engine.
-
-\subsection{{\normalsize\bf\texttt{objectId()}} operation}
-\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
+easy to explore, change, and share with others for feedback. A professionally useful debugger 
+would implement these primitive operations within the JavaScript engine.
+
+\subsection{{\normalsize\bf\texttt{objectId()}} Operation}
+\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}
+\footnote[1]{The property name we used in the prototype is longer and more specific to reduce the chance of name conflicts.} .
 It returns the value if this property is already defined,
@@
 
-\subsection{{\normalsize\bf\texttt{setPropertyChangeHook()}} operation}
+\subsection{{\normalsize\bf\texttt{setPropertyChangeHook()}} Operation}
 The Firefox JavaScript engine supports watching property changes in an
 object. Every object has a function \texttt{watch(propName, callback)}
-which receives two parameters, a property name and function.  Whenever
+which receives two parameters, a property name and a function.  Whenever
 the property with the given name changes, the \texttt{callback} function is
@@
 this object. Although in most regular cases we have only one
-statement and one object creation in a line, there are cases that more
-than one object might be created in a line. There is no simple way to
+statement and one object creation, there are cases where more
+objects are created in the line. There is no simple way to
 recognize the interesting object among these new objects. So instead
@@
 An object might be created by one of these statements: object
-initializer (\texttt{\{...\}}), \textit{new} operator (\texttt{new 
-constructor()}) or function definition statment (\texttt{function()}). 
+literal(\texttt{\{...\}}), \textit{new} operator (\texttt{new 
+constructor()}) or function definition statement (\texttt{function()}). 
 By parsing the source code we can recognize the statements that
@@
 
-The new object can also be set as the property of a parent object by a
-colon (\texttt{:}). This case is also treated similar to previous case. The
-only difference is that the full path of property from the root parent
-in the local scope should be considered as the assignee statement. For
+The new object can also be set as the property of a parent object 
+(or array) inside an object (or array) literal. This case is also treated 
+similar to previous case. The only difference is that the full path of property 
+from the root parent in the local scope must be considered as the assignee statement. For
 example in Figure~\ref{fig:objectCreation}(b), if the creation line
-is 20, we keep \texttt{parentObject.newObject}. In this case stepping
-should be continued until the end of line 22 for getting a reference
+is 20, we keep \texttt{parent.child}. In this case stepping
+must be continued until the end of the object literal (line 22) for getting a reference
 to the created new object.
 
-There is another case for new objects where they are passed as
-arguments to other functions (Figure~\ref{fig:objectCreation}(c)). In these
-cases instead of step-over we use step-in and we get the corresponding
-argument as a new object.
-
-Although this approach is successful in many ordinary cases, there are some 
-cases that a more comprehensive analysis needed for correct behaviour. For example in a case
-where the new object is assigned to \texttt{a[++i]} where i is a variable
-(Figure~\ref{fig:objectCreation}(d)), \texttt{a[++i]} is kept in the list
-of assignee statements. Obviously, evaluating this statement doesn't return
+In cases where the new object is passed as an 
+argument to a function (Figure~\ref{fig:objectCreation}(c)), we use step-in instead of step-over. 
+To get a reference to the new object
+it is enough to evaluate the corresponding argument inside the function. The other cases
+where the program does not keep a reference to the created object (e.g., when a function object is
+just called after its creation), are not in our interest.
+
+%(or \texttt{this} if the object is being constructed by \texttt{new} statement)
+
+Although this approach is successful in many ordinary cases, we can imagine 
+cases where a more comprehensive analysis needed for the correct behaviour.
+Consider the case where the new object is assigned to an expression like \texttt{a[++i]}. 
+% (where i is a variable). 
+%This expression is kept in the list                      %(Figure~\ref{fig:objectCreation}(d))
+%of assignee statements to be evaluated later for getting a reference to the new object. 
+Obviously, evaluating this statement doesn't return
 a reference to the new object. Our prototype implementation does not handle these kinds of unusual cases yet.
@@
 Throughout this section we implicitly assumed that the object will be created at 
-the same location in the next execution. So, what happens if it
-is not true? Once the execution reaches the reproduction point, it
-reveals that the object has been created in different location. This time,
+the same location in the next execution. If the assumption is
+not true, once the execution reaches the reproduction point, it
+reveals that the object has been created in a different location. This time,
 prototype re-executes the program considering both locations as possible 
@@
 (a) Case 1:
- 20 x.y = new myConstructor();
+ 20  x.y = new MyClass();
 
 (b) Case 2:
- 19  parentObject = {
- 20   newObject : {
+ 19  parent = {
+ 20    child : {
  21      x : 5
@@
 
-(d) Case 4:
- 20 a[++i] = new myConstructor();
 \end{lstlisting}
+
+%(d) Case 4:
+% 20 a[++i] = new myConstructor();
+
 %\end{verbatim}
@@
 
-\subsection{{\normalsize\bf\texttt{scopeId()}} operation}
+\subsection{{\normalsize\bf\texttt{scopeId()}} Operation}
 The prototype sets a breakpoint at the beginning of all code blocks needing
@@
 
-\subsection{{\normalsize\bf\texttt{setVariableChangeHook()}} operation}
+\subsection{{\normalsize\bf\texttt{setVariableChangeHook()}} Operation}
 Variables defined in local, closure, and catch scopes are only changed in
 their scope; that includes the defining scope and scopes nested whithin them.
-For example in Figure~\ref{fig:js-closure}, variable \texttt{myVar} in line 11 can only be
+For example in Figure~\ref{fig:js-closure}, variable \texttt{foo} in line 11 can only be
 changed in lines 10 to 23. Therefore, after locating the function in
@@
 We also set a hook at the first line of the function which is
-corresponding to the line where the variable is defined. In Figure
-~\ref{fig:js-closure}, if the execution is paused at line 17 and the
-last change of \texttt{myVar} is queried, two hooks on lines 16 and 17
+corresponding to the line where the variable is defined. In Figure~\ref{fig:js-closure}, 
+if the execution is paused at line 17 and the
+last change of \texttt{foo} is queried, two hooks on lines 16 and 17
 will be set, but if the execution is paused at line 20 , four hooks on
-lines 11, 12, 14, 20 will be set. These two cases are different: \texttt{myVar} in 
-\texttt{firstChild} is a local variable
-but in \texttt{secondChild} it is a closure variable.
+lines 11, 12, 14, 20 will be set. These two cases are different: \texttt{foo} in 
+\texttt{childOne} is a local variable
+but in \texttt{childTwo} it is a closure variable.
 
@@
 
-10  function parent(){
-11    var myVar;
-12    myVar = ...;
-13    function myfun(){
-14      myVar = ...;
-15      function firstChild(){
-16        var myVar;
-17        myVar = ...;
+10  function main(){
+11    var foo;
+12    foo = ...;
+13    function parent(){
+14      foo = ...;
+15      function childOne(){
+16        var foo;
+17        foo = ...;
 18      }  
-19      function secondChild(){
-20        myVar = ...;			      
+19      function childTwo(){
+20        foo = ...;			      
 21      }
@@
 %\end{verbatim}
-\caption{Sample JavaScript code demonstrating local and clousure variables.}
+\caption{Sample JavaScript code demonstrating local and closure variables.}
 \label{fig:js-closure}
@@
 
-\subsection{Re-Execution, reproduction point and data collection}
+\subsection{Re-Execution, Reproduction Point and Data Collection}
 \textit{Querypoint} needs a test case to reproduce the
@@
 Since we don't need to compare values across executions to implement \textit{lastChange}, we can get more information if we do compare:
- different points of last change on different executions will signal that the execution is not deterministic. (Note the converse is not true, many non-deterministic 
-programs will give identical results for \textit{lastChange}.)
+ different points of last change on different executions will signal that the execution is not deterministic. Note the converse is not true, many non-deterministic 
+programs will give identical results for \textit{lastChange}.
 Consider the example in Figure~\ref{fig:nondeterministic-values}. 
-Assume that at the first execution, developers sees that \texttt{a} is \texttt{true} and asks
-for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
+Assume that at the first execution, the developer sees that the \texttt{a} value is \texttt{true} and asks
+for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-execution, \texttt{a} is \texttt{false},
 and \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
@@
 
-10 a = false;
-11 b = false;
-...
-20 if ( random() ) { a = true; } else { b = true; }
-...
-30 if (a || b) { bug();  /* breakpoint */ }
+10 a = b = false;
+20 if (random()) {a = true;} else {b = true;}
+30 if (a || b) {bug(); /* breakpoint */}
 \end{lstlisting}
@@
 
-\subsection{Combination of {\large\bf\textit{lastChange}} and breakpoint debugging}
+\subsection{Combination of {\large\bf\textit{lastChange}} and Breakpoint Debugging}
 \label{sec:pausing}
@@
 
-In the case that the execution is deterministic, the \textit{lastChange}
+In the case that the execution is deterministic, the \textit{last-\ Change}
 event index can be used as an index for a conditional breakpoint \cite{Boothe, Maruyama}. 
@@
 conditional breakpoint matches the last 
-change, this fact  can only verify  at the reproduction point. These theoretical concerns are not
-likely to cause significant practical problems: if the value at the conditional breakpoint is not suspcious, 
+change, this fact can only be verified at the reproduction point. These theoretical concerns are not
+likely to cause significant practical problems: if the value at the conditional breakpoint is not suspicious, 
 then the developer will know to simply return to \textit{lastChange} or move on to another tactic to find the bug.
@@
 We designed the example programs to require two steps of \textit{lastChange}; 
-all four users took more steps (9, 13, 12, and more than 30) to find the defect location with breakpoints.  
+all four users took more steps (9, 13, 12, and more than 30) to find the defect location with breakpoints (Figure~\ref{fig:userstudy}).  
 To find locations for breakpoints two users scrolled through the source, 
@@
 plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
+
+\begin{figure}[htp]
+\centering 
+\includegraphics[width=.48\textwidth]{10-userstudy.pdf}
+\caption{The number of steps and time (in seconds) every developer spent on each program
+before locating the defect. The highlighted numbers show cases where the developer was
+permitted to use \textit{lastChange}.}
+\label{fig:userstudy}
+\end{figure}
 
@@
 %In our own experience, \textit{lastChange} dramatically reduces the work in
-%setting and removing breakpoints, so work to cause re-execution  become noticable.
+%setting and removing breakpoints, so work to cause re-execution  become noticeable.
 %Therefore automatic mechanisms

### 2011-03-11 trunk/papers/fse2011/sig-alternate.tex

@@
 using techniques which are cumbersome and comparatively slow to execute. However the JavaScript prototype is
-easy to explore, change, and share with others for feedback.
-  A professionally useful debugger would implement these primitive operations within the JavaScript engine.
-
-\subsection{{\normalsize\bf\texttt{objectId()}} operation}
+easy to explore, change, and share with others for feedback. A professionally useful debugger 
+would implement these primitive operations within the JavaScript engine.
+
+\subsection{{\normalsize\bf\texttt{objectId()}} Operation}
 \texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
+%\footnote[3]{The property name we used in the prototype is longer and more specific to reduce the chance of name conflicts.} .
 It returns the value if this property is already defined,
@@
 after its creation, then use \texttt{watch()} function to monitor
-property changes in the object. Setting a flag\footnote[4]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
-JavaScript engine, we can get file URL and line number for each object
+property changes in the object. Setting a flag\footnote[3]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
+JavaScript engine, we can get the file URL and the line number for each object
 creation (e.g., myFile.js, line 24). We set a breakpoint on this line
@@
 that the new objects are assigned to. We set a hook on the creation
-line. Once the hook hits, we evaluate all assignee statements. Then 
+line. Once the hook hits, we evaluate the assignee statements. Then 
 we do stepping(step-over) and after each step we evaluate the
@@
 
-The new object can also be set as the property of a parent object by a
-colon (\texttt{:}). This case is also treated similar to previous case. The
-only difference is that the full path of property from the root parent
-in the local scope should be considered as the assignee statement. For
+The new object can also be set as the property of a parent object 
+(or array) inside an object (or array) literal. This case is also treated 
+similar to previous case. The only difference is that the full path of property 
+from the root parent in the local scope must be considered as the assignee statement. For
 example in Figure~\ref{fig:objectCreation}(b), if the creation line
-is 20, we keep \texttt{parentObject.newObject}. In this case stepping
-should be continued until the end of line 22 for getting a reference
+is 20, we keep \texttt{parent.child}. In this case stepping
+must be continued until the end of the object literal (line 22) for getting a reference
 to the created new object.
 
-There is another case for new objects where they are passed as
-arguments to other functions (Figure~\ref{fig:objectCreation}(c)). In these
-cases instead of step-over we use step-in and we get the corresponding
-argument as a new object.
-
-Although this approach is successful in many ordinary cases, there are some 
-cases that a more comprehensive analysis needed for correct behaviour. For example in a case
-where the new object is assigned to \texttt{a[++i]} where i is a variable
-(Figure~\ref{fig:objectCreation}(d)), \texttt{a[++i]} is kept in the list
-of assignee statements. Obviously, evaluating this statement doesn't return
+In cases where the new object is passed as an 
+argument to a function (Figure~\ref{fig:objectCreation}(c)), we use step-in instead of step-over. 
+To get a reference to the new object
+it is enough to evaluate the corresponding argument inside the function. The other cases
+where the program does not keep a reference to the created object (e.g., when a function object is
+just called after its creation), are not in our interest.
+
+%(or \texttt{this} if the object is being constructed by \texttt{new} statement)
+
+Although this approach is successful in many ordinary cases, we can imagine 
+cases where a more comprehensive analysis needed for the correct behaviour. 
+Consider the case where the new object is assigned to an expression like \texttt{a[++i]}. 
+% (where i is a variable). 
+%This expression is kept in the list                      %(Figure~\ref{fig:objectCreation}(d))
+%of assignee statements to be evaluated later for getting a reference to the new object. 
+Obviously, evaluating this statement doesn't return
 a reference to the new object. Our prototype implementation does not handle these kinds of unusual cases yet.
@@
 
-\section{Reproducible Non-deterministic Execution}
+\section{Reproducible Non-Deterministic Execution}
 We claim that the only prerequisite for \textit{lastChange}  is bug-reproducibility. 
 A bug is \textit{reproducible} for a developer when the developer can
-start from a determined initial state, operate on the program with a
+start from a given initial state, operate on the program with a
 list of actions, and reproduce the symptoms of the bug. The details of
@@
 a conventional watchpoint hits, the record may differ each time we
-re-execute. But \textit{lastChange} does not ask the developer to
-consider these single points. Rather it analyzes all of the
-change events in an entire execution at the reproduction point where the bug
-has already occurred and shows the final result to the developer. 
+re-execute. But \textit{lastChange} does not compare values across 
+executions. Rather it analyzes all of the
+change events in a single execution. 
 Neither the data gathering nor the analysis require deterministic execution.
 
-When the developer selects a value and
-asks for \textit{lastChange}, the developer is expressing the hypothesis that
-the value is related to the defect. Since the defect does not depend on
- exeuction order, the reproducibility of
-the bug makes it very unlikely that the \textit{lastChange} will
-depend upon order of events during execution.
-There can be rare cases where the bug is reproducible but the
-value from \textit{lastChange} is not. As in conventional breakpoint
-debugging, we can only determine this empirically, by observing
-multiple executions with different values. Unlike conventional
-breakpoint debugging, implementations of \textit{lastChange} readily
-help in detecting such cases: as we work back through a series of
-\textit{lastChange} requests we can compare values with previous
-executions. Different values on different executions will signal that
-the execution is not deterministic.
-
+Since we don't need to compare values across executions to implement \textit{lastChange}, we can get more information if we do compare:
+ different points of last change on different executions will signal that the execution is not deterministic. Note the converse is not true, many non-deterministic 
+programs will give identical results for \textit{lastChange}.
 Consider the example in Figure~\ref{fig:nondeterministic-values}. 
-Assume that at the first exeuction, developers sees that \texttt{a} is \texttt{true} and asks
-for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-exeuction, \texttt{a} is \texttt{false},
+Assume that at the first execution, the developer sees that the \texttt{a} value is \texttt{true} and asks
+for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-execution, \texttt{a} is \texttt{false},
 and \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
@@
 provided (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
+The first program, Shapes, calculates the area and perimeter values for a list of shapes.
+The bug happens when one of the calculated numbers is zero.
+The second program, Moving Circle, randomely scales and moves a circle in the page.
+The bug happens once the circle becomes invisible after an exception
+occurs.
+This case represent a reproducible non-deterministic execution.
+The developers are asked to located the defects cause these bugs.
 All four developers successfully applied \textit{lastChange} to the test programs
@@
 plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
+
+\begin{figure}[htp]
+\centering 
+\includegraphics[width=.48\textwidth]{10-userstudy.pdf}
+\caption{The number of steps and time (in seconds) every developer spent on each program
+before locating the defect. Cells with a white background report values with conventional debugging; Cells with a colored background use \textit{lastChange}.}
+
+\label{fig:userstudy}
+\end{figure}
 

### 2011-03-11 trunk/papers/fse2011/sig-alternate.tex

@@
 The bug happens when one of the calculated numbers is zero.
-The second program, Moving Circle, randomely scales and moves a circle in the page.
+The second program, Moving Circle, randomly scales and moves a circle in the page.
 The bug happens once the circle becomes invisible after an exception
@@
 This case represent a reproducible non-deterministic execution.
-The developers are asked to located the defects cause these bugs.
+The developers were asked to locate the defects that caused these bugs.
 All four developers successfully applied \textit{lastChange} to the test programs
@@
 
-We designed the example programs to require two steps of \textit{lastChange}; 
-all four users took more steps (9, 13, 12, and more than 30) to find the defect location with breakpoints (Figure~\ref{fig:userstudy}).  
-To find locations for breakpoints two users scrolled through the source, 
-another searched the text, a third set a lot of breakpoints to get an understand of the control flow. 
+To find the defect location with breakpoints, all four users took more steps and more time (Figure~\ref{fig:userstudy}).  
+Two users scrolled through the source, 
+another searched the text, a third set a lot of breakpoints to understand the control flow. 
 Based on our own experience we expect these strategies represent the kinds of approaches 
@@
 \includegraphics[width=.48\textwidth]{10-userstudy.pdf}
-\caption{The number of steps and time (in seconds) every developer spent on each program
-before locating the defect. Cells with a white background report values with conventional debugging; Cells with a colored background use \textit{lastChange}.}
+\caption{The number of steps (and time in seconds) required before locating a defect, for each test subject and test program. 
+Cells with a white background report values with conventional debugging; Cells with a colored background use \textit{lastChange}.}
 

### 2011-03-12 papers/fse2011/sig-alternate.tex

@@
 \subsection{{\normalsize\bf\texttt{objectId()}} Operation}
-\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}
-\footnote[1]{The property name we used in the prototype is longer and more specific to reduce the chance of name conflicts.} .
+\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
+%\footnote[3]{The property name we used in the prototype is longer and more specific to reduce the chance of name conflicts.} .
 It returns the value if this property is already defined,
@@
 
-\section{Reproducible Non-deterministic Execution}
+\section{Reproducible Non-Deterministic Execution}
 We claim that the only prerequisite for \textit{lastChange}  is bug-reproducibility. 
@@
 We supplied four experienced Javascript developers with our prototype in an 
-extended Firebug debugger\footnote[5]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
+extended Firebug debugger\footnote[4]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
 applied both conventional breakpoint and \textit{lastChange} on two small programs we 
 provided (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
+The first program, Shapes, calculates the area and perimeter values for a list of shapes.
+The bug happens when one of the calculated numbers is zero.
+The second program, Moving Circle, randomly scales and moves a circle in the page.
+The bug happens once the circle becomes invisible after an exception
+occurs.
+This case represent a reproducible non-deterministic execution.
+The developers were asked to locate the defects that caused these bugs.
 All four developers successfully applied \textit{lastChange} to the test programs
@@
 \includegraphics[width=.48\textwidth]{10-userstudy.pdf}
-\caption{The number of steps and time (in seconds) every developer spent on each program
-before locating the defect. The highlighted numbers show cases where the developer was
-permitted to use \textit{lastChange}.}
+\caption{The number of steps (and time in seconds) required before locating a defect, for each test subject and test program. 
+Cells with a white background report values with conventional debugging; Cells with a colored background use \textit{lastChange}.}
+
 \label{fig:userstudy}
@@
 \label{sec:relatedWork}
-
-The algorithm we presented in this paper obtain information about
-the execution state logically earlier in the control flow by querying 
-the executioin state during replay using the technology of 
-conventional breakpoint debuggers.  This
-approach resembles the operational model of replay-based debugging 
+%The algorithm we presented in this paper obtain information about
+%the execution state logically earlier in the control flow by querying 
+%the executioin state during replay using the technology of 
+%conventional breakpoint debuggers.  
+The \textit{lastChange} approach resembles the operational model of replay-based debugging 
 and the query approach of logging-based
@@
 times. \textit{lastChange} collects data on re-execution by queries
-selected by developer interaction with the debugger. Therefore we have 
+selected by developer interaction with the debugger. Therefore it has 
 the selectivity of the replay-based approaches that improves performance, 
-but we have the flexibilty of the queries so we do not require deterministic replay.
+% but we have 
+and the flexibilty of the queries so it does not require deterministic replay.
 
@@
 beginning of execution. It relies on deterministic execution replay
-(i.e., the same sequence of instructions in re-execution) and records
-the results of non-deterministic system calls and re-injects them into
+%(i.e., the same sequence of instructions in re-execution) 
+and records the results of non-deterministic system calls and re-injects them into
 the program when it is replayed. It makes use of checkpoints to reduce
-the time needed for re-execution.  Reverse watchpoint, is proposed by
-Maruyama et al., analyses the execution and moves the debugger to the
-last write access of a selected variable by re-executing the program
-from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
-replay and uses a counter to correctly locate a point in the next
-execution. The main disadvantage of these approaches is that they require 
-exactly the same executions. Even one instruction difference between
+the time needed for re-execution. Reverse watchpoint, similar to bdb, uses
+a counter to correctly locate the last write access of a selected variable in the
+next execution \cite{Maruyama}.
+% Reverse watchpoint is proposed by Maruyama et al., analyses the execution and moves the debugger to the
+% last write access of a selected variable by re-executing the program
+%from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
+%replay and uses a counter to correctly locate a point in the next
+%execution. 
+The main disadvantage of these approaches is that they require 
+identical, instruction by instruction, re-executions. % exactly the same executions. 
+Even one instruction difference between
 two executions leads to wrong results. On the other hand,
@@
 and later let the developer to navigate through the obtained execution
-log. In this approach there is no execution to resume: moving
-backwards in the log can be similar to moving forwards. Omniscient
-debuggers suffer from a different set of issues. First, the recording
+log. In these approaches there is no execution to resume: moving
+backwards in the log can be similar to moving forwards. A more scalable 
+approach to omniscient debugging has been proposed by Pothier et al. \cite{Pothier}. 
+Their back-in-time debugger, TOD, addresses the space problem by storing 
+execution events in a distributed database. Bhansali et al. \cite{Bhansali} attempted to address the performance overhead 
+and large trace size of logging-based debugging in their time-travelling debugger, Nirvana. 
+Nirvana first collects a full compressed trace of program execution and then 
+re-simulate the execution. Their results are quite similar to omniscient 
+debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
+re-simulation.
+
+Logging-based debuggers suffer from a different set of issues. First, the recording
 step is time expensive and it should be repeated in case of changes in
@@
 the program state at a certain point) may not be efficient enough for
-debugging of realistic programs.
-
-A more scalable approach has been proposed by Pothier et
-al. \cite{Pothier}. Their back-in-time debugger, TOD, addresses the
-space problem by storing execution events in a distributed
-database. Comparing to Omniscient debuggers our approach is
+debugging of realistic programs. Comparing to logging-based debuggers our approach is
 lightweight and more flexible. Developer can start debugging just
@@
 in conventional breakpoint debuggers.
-
-Bhansali et al. \cite{Bhansali} attempted to attack performance overhead 
-and large trace size in their time-travelling debugger, Nirvana. Nirvana 
-first collects a full compressed trace of program execution and then 
-re-simulate the execution. Their results are quite similar to omniscient 
-debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
-re-simulation.
-
-A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
-machine level support for keeping the object flow. It replaces every
-object reference with an alias object which keeps the history of
-changes to the object reference. In this way, when an object is
-collected by garbage collector, its track of changes (if it is not
-referenced by other aliases) will be also collected. Though this
-approach incurs less runtime overhead in
-comparison to omniscient debuggers (7 times to 115 times), it adds memory
-overhead.
-
-Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
-Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
-First, it is limited to \texttt{undefined} and \texttt{null} values. Second, this approach dose not return the last change
-of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
-
-Two new directions in logging debuggers explore more detailed use of
-the log and more effective logging approaches. WhyLine\cite{Ko}
-provides visual interface to collected runtime information and lets
-developer moves on execution log using queries expressed in terms of
-the programming objects. WhyLine stores the program user interface in
-addition to program trace and provides answers to why and why not
-questions to the user. Jive\cite{Czyz} depicts the history of
-execution by a sequence diagram and lets user to query on events
-database. Both tools suffer from the requirement of gathering tracing information before their unique capabilities can be used.
-We imagine that the runtime queries we use in \textit{lastChange}  may be used to gather data incrementally for these kinds of debugging approaches.
 
@@
 
+A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
+machine level support for keeping the object flow. It replaces every
+object reference with an alias object which keeps the history of
+changes to the object reference. 
+%In this way, when an object is
+%collected by garbage collector, its track of changes (if it is not
+%referenced by other aliases) will be also collected. 
+Although this approach incurs less runtime overhead (7 times) in
+comparison to omniscient debuggers, it adds memory
+overhead.
+
+Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
+Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
+First, it is limited to \texttt{undefined} and \texttt{null} values. Second, this approach dose not return the last change
+of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
+
+%Two new directions in logging debuggers explore more detailed use of
+%the log and more effective user interface to the collected data. %logging approaches. 
+%WhyLine\cite{Ko} provides visual interface to collected runtime information and lets
+%developer moves on execution log using queries expressed in terms of
+%the programming objects.
+
+WhyLine\cite{Ko} stores the program user interface in
+addition to the program trace and provides answers to why and why not
+questions to the user. 
+%Jive\cite{Czyz} depicts the history of
+%execution by a sequence diagram and lets the user to query on the events
+%database. 
+WhyLine suffers from the requirement of gathering tracing information before its unique capabilities can be used.
+We imagine that the runtime queries we use in \textit{lastChange} may be used to gather data incrementally for this kind of debugging approaches.
+
 %Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
@@
 
-\bibitem{Czyz}%[Czyz(2007)]
-J.K. Czyz, and B. Jayaraman. \newblock Declarative and visual debugging in Eclipse.
-\newblock In \emph{OOPSLA workshop on eclipse technology eXchange},
-October, 2007.
+%\bibitem{Czyz}%[Czyz(2007)]
+%J.K. Czyz, and B. Jayaraman. \newblock Declarative and visual debugging in Eclipse.
+%\newblock In \emph{OOPSLA workshop on eclipse technology eXchange},
+%October, 2007.
 

### 2011-03-12 trunk/papers/fse2011/sig-alternate.tex

@@
 We supplied four experienced Javascript developers with our prototype in an 
-extended Firebug debugger\footnote[5]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
+extended Firebug debugger\footnote[4]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
 applied both conventional breakpoint and \textit{lastChange} on two small programs we 
@@
 beginning of execution. It relies on deterministic execution replay
-(i.e., the same sequence of instructions in re-execution) and records
-the results of non-deterministic system calls and re-injects them into
+%(i.e., the same sequence of instructions in re-execution) 
+and records the results of non-deterministic system calls and re-injects them into
 the program when it is replayed. It makes use of checkpoints to reduce
-the time needed for re-execution.  Reverse watchpoint, is proposed by
-Maruyama et al., analyses the execution and moves the debugger to the
-last write access of a selected variable by re-executing the program
-from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
-replay and uses a counter to correctly locate a point in the next
-execution. The main disadvantage of these approaches is that they require 
-exactly the same executions. Even one instruction difference between
+the time needed for re-execution. Reverse watchpoint, similar to bdb, uses
+a counter to correctly locate the last write access of a selected variable in the
+next execution \cite{Maruyama}.
+% Reverse watchpoint is proposed by Maruyama et al., analyses the execution and moves the debugger to the
+% last write access of a selected variable by re-executing the program
+%from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
+%replay and uses a counter to correctly locate a point in the next
+%execution. 
+The main disadvantage of these approaches is that they require 
+identical, instruction by instruction, re-executions. % exactly the same executions. 
+Even one instruction difference between
 two executions leads to wrong results. On the other hand,
 \textit{lastChange} doesn't require any special feature in the
-re-execution and it is fit to  developers' everyday debugging
-practice.
+re-execution and fits into existing debugging practice
 
@@
 and later let the developer to navigate through the obtained execution
-log. In this approach there is no execution to resume: moving
-backwards in the log can be similar to moving forwards. Omniscient
-debuggers suffer from a different set of issues. First, the recording
+log. In these approaches there is no execution to resume: moving
+backwards in the log can be similar to moving forwards. A more scalable 
+approach to omniscient debugging has been proposed by Pothier et al. \cite{Pothier}. 
+Their back-in-time debugger, TOD, addresses the space problem by storing 
+execution events in a distributed database. Bhansali et al. \cite{Bhansali} attempted to address the performance overhead 
+and large trace size of logging-based debugging in their time-travelling debugger, Nirvana. 
+Nirvana first collects a full compressed trace of program execution and then 
+simulates re-execution. Their results are quite similar to omniscient 
+debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
+re-simulation.
+
+Logging-based debuggers suffer from different issues. First, the recording
 step is time expensive and it should be repeated in case of changes in
@@
 the program state at a certain point) may not be efficient enough for
-debugging of realistic programs.
-
-A more scalable approach has been proposed by Pothier et
-al. \cite{Pothier}. Their back-in-time debugger, TOD, addresses the
-space problem by storing execution events in a distributed
-database. Comparing to Omniscient debuggers our approach is
-lightweight and more flexible. Developer can start debugging just
+debugging realistic programs. Comparing to logging-based debuggers our approach is 
+has little upfront cost and more flexibility. The developer can start debugging just 
 after reproducing bug without a capturing step.  Changing inputs or
@@
 
-Bhansali et al. \cite{Bhansali} attempted to attack performance overhead 
-and large trace size in their time-travelling debugger, Nirvana. Nirvana 
-first collects a full compressed trace of program execution and then 
-re-simulate the execution. Their results are quite similar to omniscient 
-debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
-re-simulation.
+Program slicing\cite{Weiser} approaches debugging from a completely different perspective.
+Given a point of interest {\bf S} in a program, a \textit{slice} is an executable subset of the program affecting {\bf S}.
+Many studies have shown ways to compute the slice more quickly or to constrain the slice to a smaller subset of the program \cite{Horwitz, Sridharan}.
+Dynamic slicing \cite{Korel} applies slicing analysis at run time and thus most closely resembles \textit{lastChange} from among the slicing approaches.
+Our \textit{lastChange} approach can be related this way: first, allow the developer to select from {\bf S} a key critical value {\bf V}.
+Then compute a slice affecting {\bf V}.
+Show the developer only the most relevant part of that slice (the \textit{lastChange}).
+Finally iterate towards the fault by chaining new slice-selection criteria.
+
+Both approaches rely on selecting {\bf S}.
+Both approaches differ from breakpoint debugging in analyzing a program from a known good point (e.g.
+start of the program) to {\bf S}.
+Slicing reduces the space the developer needs to search, but provides no guidance within the slice; \textit{lastChange} explores the slice using developer-selected search criteria, but does not help the developer recognize code that cannot impact {\bf S}.
+Slicing requires a sophisticated compiler-like technology while \textit{lastChange} builds on familiar run-time debugger technology.
 
@@
 object reference with an alias object which keeps the history of
-changes to the object reference. In this way, when an object is
-collected by garbage collector, its track of changes (if it is not
-referenced by other aliases) will be also collected. Though this
-approach incurs less runtime overhead in
-comparison to omniscient debuggers (7 times to 115 times), it adds memory
+changes to the object reference. 
+%In this way, when an object is
+%collected by garbage collector, its track of changes (if it is not
+%referenced by other aliases) will be also collected. 
+Although this approach incurs less runtime overhead (7 times) in
+comparison to omniscient debuggers, it adds memory
 overhead.
@@
 
-Two new directions in logging debuggers explore more detailed use of
-the log and more effective logging approaches. WhyLine\cite{Ko}
-provides visual interface to collected runtime information and lets
-developer moves on execution log using queries expressed in terms of
-the programming objects. WhyLine stores the program user interface in
-addition to program trace and provides answers to why and why not
-questions to the user. Jive\cite{Czyz} depicts the history of
-execution by a sequence diagram and lets user to query on events
-database. Both tools suffer from the requirement of gathering tracing information before their unique capabilities can be used.
-We imagine that the runtime queries we use in \textit{lastChange}  may be used to gather data incrementally for these kinds of debugging approaches.
-
-Program slicing\cite{Weiser} approaches debugging from a completely different perspective.
-Given a point of interest {\bf S} in a program, a \textit{slice} is an executable subset of the program affecting {\bf S}.
-Many studies have shown ways to compute the slice more quickly or to constrain the slice to a smaller subset of the program \cite{Horwitz, Sridharan}.
-Dynamic slicing \cite{Korel} applies slicing analysis at run time and thus most closely resembles lastChange from among the slicing approaches.
-Our lastChange approach can be related this way: first, allow the developer to select from {\bf S} a key critical value {\bf V}.
-Then compute a slice affecting {\bf V}.
-Show the developer only the most relevant part of that slice (the lastChange).
-Finally iterate towards the fault by chaining new slice-selection criteria.
-
-Both approaches rely on selecting {\bf S}.
-Both approaches differ from breakpoint debugging in analyzing a program from a known good point (e.g.
-start of the program) to {\bf S}.
-Slicing reduces the space the developer needs to search, but provides no guidance within the slice; lastChange explores the slice using developer-selected search criteria, but does not help the developer recognize code that cannot impact {\bf S}.
-Slicing requires a sophisticated compiler-like technology while lastChange builds on familiar run-time debugger technology.
+%Two new directions in logging debuggers explore more detailed use of
+%the log and more effective user interface to the collected data. %logging approaches. 
+%WhyLine\cite{Ko} provides visual interface to collected runtime information and lets
+%developer moves on execution log using queries expressed in terms of
+%the programming objects.
+
+WhyLine\cite{Ko} stores the program user interface in
+addition to the program trace and provides answers to why and why not
+questions to the user. 
+%Jive\cite{Czyz} depicts the history of
+%execution by a sequence diagram and lets the user to query on the events
+%database. 
+WhyLine suffers from the requirement of gathering tracing information before its unique capabilities can be used.
+We imagine that the runtime queries we use in \textit{lastChange} may be used to gather data incrementally for this kind of debugging approach.
 

### 2011-03-12 trunk/papers/fse2011/sig-alternate.tex

@@
 A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
-machine level support for keeping the object flow. It replaces every
+machine level support for keeping the history of events. It replaces every
 object reference with an alias object which keeps the history of
@@
 Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
-First, it is limited to \texttt{undefined} and \texttt{null} values. Second, this approach dose not return the last change
+First, it is limited to \texttt{undefined} and \texttt{null} values. Second, it does not return the last change
 of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
@@
 \bibitem{Zeller}
-A. Zeller. \newblock Why programs fail: A gauide to systematic debugging.
+A. Zeller. \newblock Why programs fail: A guide to systematic debugging.
 Morgan Kaufmann (2005)

### 2011-03-17 trunk/papers/splash-wavefront2011/sigplanconf-template.tex

--- 2011-02-02 trunk/papers/issta2011/sigproc-sp.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
+%-----------------------------------------------------------------------------
 %
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
+%               Template for sigplanconf LaTeX Class
 %
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
+% Name:         sigplanconf-template.tex
 %
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
+% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
+%               file for SIGPLAN conference proceedings.
 %
-% For tracking purposes - this is V3.1SP - APRIL 2009
+% Author:       Paul C. Anagnostopoulos
+%               Windfall Software
+%               978 371-2316
+%               paul@windfall.com
+%
+% Created:      15 February 2005
+%
+%-----------------------------------------------------------------------------
 
-\documentclass{acm_proc_article-sp}
+\documentclass[10pt, preprint]{sigplanconf}
 
+% The following \documentclass options may be useful:
+%
+% 10pt          To set in 10-point type instead of 9-point.
+% 11pt          To set in 11-point type instead of 9-point.
+% authoryear    To obtain author/year citation style instead of numeric.
+
+\usepackage{amsmath}
 \usepackage{graphicx}
@@
 
-\title{Better JavaScript Runtime Understanding by Automated Function Name Extraction}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
+\conferenceinfo{WXYZ '05}{date, City.} 
+\copyrightyear{2005} 
+\copyrightdata{[to be supplied]}
 
-\numberofauthors{3} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Salman Mirghasemi\\
-       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne}\\
-       \affaddr{Lausanne, Switzerland}\\
-       \email{salman.mirghasemi@epfl.ch}
-% 2nd. author
-\alignauthor
-John J. Barton\\
-       \affaddr{IBM Research - Almaden}\\
-       \affaddr{San Jose, USA}\\
-       \email{johnjbarton@johnjbarton.com}
-% 3rd. author
-\alignauthor Claude Petitpierre\\
-       \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne}\\
-       \affaddr{Lausanne, Switzerland}\\
-       \email{claude.petitpierre@epfl.ch}
-}
+\titlebanner{preprint}        % These are ignored unless
+\preprintfooter{Fixing JavaScript Function Names}   % 'preprint' option specified.
+
+%\title{Better JavaScript Runtime Understanding by Automated Function Name Extraction}
+%\title{JavaScript Lost Names, Is There Any Solution?}
+%\title{JavaScript Lost Names, Any Amendment?}
+\title{Fixing Lost JavaScript Function Names in Debuggers}
+%\subtitle{Subtitle Text, if any}
+
+\authorinfo{Salman Mirghasemi}
+           {\'Ecole Polytechnique F\'ed\'erale de Lausanne(EPFL)}
+           {salman.mirghasemi@epfl.ch}
+\authorinfo{John J. Barton}
+           {IBM Research - Almaden}
+           {bartonjj@us.ibm.com}
+\authorinfo{Claude Petitpierre}
+           {\'Ecole Polytechnique F\'ed\'erale de Lausanne(EPFL)}
+           {claude.petitpierre@epfl.ch}
 
 \maketitle
+
 \begin{abstract}
 Understanding JavaScript code due to its dynamic, weakly-typed nature is complicated.
-Developers usually understand JavaScript programs by running them and examining their elements at runtime.
+Developers usually comprehend JavaScript programs by running them and examining their elements at runtime.
 However, understanding concrete values, particularly user-defined and function objects, is not always straightforward.
-Function names can aid in this regard; they can appear as the constructor name in object representation or as the functions identifier in callstack.
-Unfortunately, only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
-As a solution to this issue, we propose an approach for automated JavaScript function naming based on source code analysis.
+Function names can aid in this regard; they can appear as the constructor name in object representation or as the function identifier in callstack.
+Unfortunately, based on our analysis over ten famous JavaScrip projects, only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
+As a solution to this problem, we propose an automated approach based on source code analysis for naming nameless JavaScript functions.
 We applied our approach on several JavaScript projects and the resutls are very promising.
-
 \end{abstract}
@@
 
-\terms{Algorithms, Human Factors, Languages}
+\terms
+Algorithms, Human Factors, Languages
 
-\keywords{Debugging, JavaScript, Function Name} % NOT required for Proceedings
+\keywords
+JavaScript, Function Name, Debugging
 
@@
 Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
-This language is used by 97 out of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
-It is very likely that JavaScript keeps this crucial role at least for the next few years.
+This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
+It is very likely that JavaScript keeps this crucial role at least for the next few years or decade.
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
@@
 
-To cope with the pace of changes, JavaScript developers need to improve their develoment processes and practices.
+To cope with the pace of changes, JavaScript developers need improved develoment processes, practices and tools.
 They need modern editors for writing and editing larger programs and effective tools for understanding complicated JavaScript runtime.
@@
 The value of a variable can be a primitive value, an object with any structure or even a function.
-One callsite may invoke different function bodies with different number of arities that none of them can be understood from the code.
+One callsite may invoke different function bodies with various number of arities that none of them can be understood from the code.
 Therefore, the lack of descriptive data in JavaScript code is the most fundumental issue in enhancing JavaScript tool support.
@@
 Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
-It can save developers' time, prevent bugs and improve the program reliability.
+It can save developers' time, prevent bugs and improve the program quality.
 However, many errors can not be recognized without a strong typing stystem.
@@
 Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
+This leads us to another hidden issue for improving JavaScript development tools; Due to highly dynamism in JavaScript many elements are remained nameless.
+Therefore there is no common language between the tool and developer for referring to elements.
 
@@
 To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
-For example, in case of user-defined objects, the name of object's constructor can be very helpful in the object summary.
-It can work like a class name and summarizes the object structure.
+For example, in case of user-defined objects, the name of object's constructor in the object summary can be very helpful.
+It works like a class name in class-based languages and suggests the object structure.
 
-Functions are central to program comprehension in JavaScript. They are first-class objects that are used for different purposes by developers; 
-they may be used as an object  constructor, a clousure scope(module) or even  passed as an argument in a function call.
-However, there is a subtle issue with JavaScript functions that makes working with them quite difficult: functions can be defined and created with no name or identifier.
+Functions are central to program comprehension in JavaScript.
+They are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a clousure scope(module) or even  passed as an argument in a function call.
+However, there is a subtle issue with JavaScript functions that makes working with them quite difficult: functions can be defined and created without a name or identifier.
 This problem particularly shows up in debuggers \cite{Zaytsev}.
-The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.
 
-In this paper, we propose automated JavaScript function naming based on extracted data from the source code.
-The candidate function names can be used in debuggers for more descriptive object summaries and callstack view.
-Moreover, these function names can be used in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+In this paper, we analyze function creation and consumption in ten famous project.
+We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
+The candidate function names can be used in debuggers for more descriptive object summaries and callstack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+
+%The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.
 
@@
 
-\section{The Function Naming Problem}
+\section{The Nameless Function Problem}
 
 A JavaScript function can be defined in different ways: by the {\small\texttt{function}} operator (i.e., function decleration or expression) or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
-Once a statement which defines a function is evaluated, a {\small\texttt{Function}} object is created.
-Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects can be created from that definition.
+Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} object is created.
+Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects can be created from the same definition.
 To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
@@
 According to ECMA specification, a function name (identifier) can be specified after the {\small\texttt{function}} operator (It is mandatory for function declerations but optional for function expressions) \cite{ECMA}.
-However, the usage of function identifiers is limited.
-The reason is that, function names, in addition to naming the function, has an effect on available variables in the scopes.
+However, developers usually hesitate in specifying the function name and therfore the usage of function identifiers is very limited.
+The main cause of this hesitation is that function names, in addition to naming the function, has another effect on the available variables in the scopes.
 In the case of function declearations, the function object is assigned to a variable in the function scope, but in the case of function expressions, the function object is available only inside the function.
-The confusing behavior of function identifiers get worse by function statements introduced by some browsers such as Firfox.
+The confusing behavior of function identifiers get worse by function statements introduced by some browsers such as Firefox.
 Function statements are like function expressions, but the function object is available in the entire function scope like function declarations \cite{Zaytsev}.
-Therefore, developers often prefer to omit the function identifier in the function statement to avoid its confusing impact.
+As a consequence, developers often prefer to omit the function identifier in the function statement to avoid its confusing impact.
 
@@
 For every project, the total number of functions and the number of functions with name are collected (Table~\ref{functions}).
-The ratio of the number of functions with names to the total number of functions is less than 13 percent in all projects excepting Prototype and the average ratio is less than 7 percent.
+In all projects excepting one (Prototype), the ratio of the number of functions with names to the total number of functions is less than 13 percent and the average ratio is less than 7 percent.
 Our analysis does not include the functions defined by dynamically created scripts evaluated by {\small\texttt{eval}} function.
@@
 Developers have usually the option to look at the function code, but it is tedious and time-consuming.
-Two main issues apears in debuggers due to the lack of function name.
+Two main issues apear in debuggers due to the lack of function name.
 First, object constructor name which can faciliate understanding the object value, is not available in the object summary.
@@
 We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
-A better name would be the the argument name in the called function (here {\small\texttt{callback}}).
+A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
 However the latter requires knowning the function body of the called function which is not always possible.
@@
 %the function name not very long like google chrome  xxxx.yyy.zzz
+\subsection{Limitations}
+%some long names
+%"this" in names
 
@@
 
-%ACKNOWLEDGMENTS are optional
-%\section{Acknowledgments}
+\appendix
+\section{Appendix Title}
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+This is the text of the appendix, if you need one.
 
-%\bibliographystyle{abbrv}
-%\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
+\acks
 
-\begin{thebibliography}{10}
+Acknowledgments, if needed.
+
+% We recommend abbrvnat bibliography style.
+
+%\bibliographystyle{abbrvnat}
+
+% The bibliography should be embedded for final submission.
+
+%\begin{thebibliography}{10}
+
+\begin{thebibliography}{}
+\softraggedright
+
+%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
+%P. Q. Smith, and X. Y. Jones. ...reference text...
 

### 2011-03-24 papers/splash-wavefront2011/sigplanconf-template.tex

--- 2011-03-17 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
@@
 \usepackage{array}
+\usepackage{algorithmic}
+\usepackage{algorithm}
+\usepackage{textcomp}
+\usepackage{listings}
+\usepackage{hyperref}
+%\usepackage{cite} %after hyperref
 
@@
 Function names can aid in this regard; they can appear as the constructor name in object representation or as the function identifier in callstack.
-Unfortunately, based on our analysis over ten famous JavaScrip projects, only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
-As a solution to this problem, we propose an automated approach based on source code analysis for naming nameless JavaScript functions.
+Based on our analysis over ten famous JavaScrip projects, unfortunately only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
+As a solution to this problem, we propose an automated approach based on local source code analysis for naming nameless JavaScript functions.
 We applied our approach on several JavaScript projects and the resutls are very promising.
@@
 \keywords
-JavaScript, Function Name, Debugging
+JavaScript, Function Name, Debugger
 
@@
 This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
-It is very likely that JavaScript keeps this crucial role at least for the next few years or decade.
+It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade.
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
@@
 As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
-The value of a variable can be a primitive value, an object with any structure or even a function.
+For example, the value of a variable can be a primitive value, an object with any structure or even a function.
 One callsite may invoke different function bodies with various number of arities that none of them can be understood from the code.
@@
 These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
-These discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
-Moreover, these infered data can help in code coprehension if they are properly presented.
+The discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
+Moreover, the infered data can help in code comprehension if they are properly presented.
 Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
@@
 To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
-For example, in case of user-defined objects, the name of object's constructor in the object summary can be very helpful.
+For example, in the case of user-defined objects, the name of object's constructor in the object summary can be very helpful.
 It works like a class name in class-based languages and suggests the object structure.
 
-Functions are central to program comprehension in JavaScript.
-They are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a clousure scope(module) or even  passed as an argument in a function call.
+Functions are central to program comprehension in Java-Script.
+They are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
 However, there is a subtle issue with JavaScript functions that makes working with them quite difficult: functions can be defined and created without a name or identifier.
@@
 
+%\section{The Nameless Function Problem}
+\section{The Anonymous Functions Problem}
+
+A JavaScript function can be defined in different ways: by the {\small\texttt{function}} operator (i.e., function decleration or expression) or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
+Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} object is created.
+Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects can be created from the same definition.
+To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
+
 \begin{table}
 \centering
-\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
 \scalebox{0.9}{
@@
   }
- \label{functions} 
+\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
+\label{js-functions} 
 \end{table}
@@
 
-\section{The Nameless Function Problem}
-
-A JavaScript function can be defined in different ways: by the {\small\texttt{function}} operator (i.e., function decleration or expression) or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
-Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} object is created.
-Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects can be created from the same definition.
-To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
-
 {\small\texttt{Function}} objects have no name by default; as the {\small\texttt{Function}} constructor doesn't receive any name.
-According to ECMA specification, a function name (identifier) can be specified after the {\small\texttt{function}} operator (It is mandatory for function declerations but optional for function expressions) \cite{ECMA}.
-However, developers usually hesitate in specifying the function name and therfore the usage of function identifiers is very limited.
-The main cause of this hesitation is that function names, in addition to naming the function, has another effect on the available variables in the scopes.
-In the case of function declearations, the function object is assigned to a variable in the function scope, but in the case of function expressions, the function object is available only inside the function.
+According to ECMA specification, an identifier (function name) can be specified after the {\small\texttt{function}} operator (It is mandatory for function declerations but optional for function expressions) \cite{ECMA}.
+However, developers usually hesitate to specify the function name and therefore the usage of function identifiers is very limited.
+The main cause of this hesitation is that function identifiers, in addition to naming the function, has another effect on the available variables in the current or inner scopes.
+In the case of function declearations, the function object is assigned to a variable in the function scope, but in the case of function expressions, the function object is available only inside the function body.
 The confusing behavior of function identifiers get worse by function statements introduced by some browsers such as Firefox.
@@
 
-To support the above argument, we analyzed the source code of ten famous JavaScript projects.
-For every project, the total number of functions and the number of functions with name are collected (Table~\ref{functions}).
-In all projects excepting one (Prototype), the ratio of the number of functions with names to the total number of functions is less than 13 percent and the average ratio is less than 7 percent.
-Our analysis does not include the functions defined by dynamically created scripts evaluated by {\small\texttt{eval}} function.
-Among all functions defined in these ten projects, only 116 functions (less than 0.12 percent) are defined by the {\small\texttt{Function}} constructor.
+To investigate the correctness of above argument, we analyzed the source code of ten famous JavaScript projects.
+For every project, the total number of functions and the number of functions with an identifier are collected (Table~\ref{js-functions}).
+The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent.
+Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function.
+Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
+Therefore, the results support the fact that a large proportion of JavaScript functions are remained nameless by developers.
 
@@
 Therefore, it is usually very difficult to recall the function operation from its local name.
-Developers have usually the option to look at the function code, but it is tedious and time-consuming.
+Developers have usually the option to look at the function code, but it becomes tedious and time-consuming when developer has to do it over and over again.
 Two main issues apear in debuggers due to the lack of function name.
@@
 
-\subsection{Constructor Name}
+\subsection{Missed Constructor Name in Object Summary}
 JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new Constructor()}}).
@@
 \begin{figure}[htp]
-{\small 
-\begin{verbatim}
-9  var main = function(){
-10   return function(){
+%{\small 
+%\begin{verbatim}
+
+\lstset{basicstyle=\scriptsize}
+\lstset{emph={FOO,BAR},emphstyle=\textit}
+%\lstset{backgroundcolor=\color{yellow}}
+\lstdefinelanguage{myLang}
+{morekeywords={if, function, var, return, new}}
+
+\begin{lstlisting}[frame=single, language=myLang]
+9  var main = function() {
+10   return function() {
 11     var foo = new FOO("a");
@@
 18 }();
-19 var FOO = function(a){
+19 var FOO = function(a) {
 20   this.a = a;
 21 }
-22 var BAR = function(b){
+22 var BAR = function(b) {
 23   this.b = b;
 24 }
-25 var op = function(){
+25 var op = function() {
 26   var local;
-27   return function(callBack){
+27   return function(callBack) {
 28     local++;
@@
 31 }();
-\end{verbatim}}
+\end{lstlisting}
+%\end{verbatim}}
 \caption{An excerpt of a JavaScript code.}
@@
 
-\subsection{Callstack View}
+\subsection{Anonymous Function Names in Callstack View}
 To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
@@
 The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows {\small\texttt{anonymouse}} as the name of all functions excepting the first one.
+Google chrome shows \textit{anonymous} as the name of all functions excepting the first one.
 Firebug performs better by guessing three function names but it still fails in one case.
 In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
-
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
-
-A function name must help the developer to
-distinguish the function from other functions with different behaviours.
-The behaviour of a function is dependent to its source code, enclosing scopes (e.g., global and closure variables), the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
-The first two parameters can be almost known from the source code, while the two last parameters are usually not known until the function call at runtime.
-Therefore, to name a function object, it is enough to name its \textit{function body}.
-
-A function body can be uniquly identified by its location in the source file.
-A naive proposal for the function name for a function body is a combination of the function file name and line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
-Morover, A proposed function name should be close to the name a developer would choose for the function.
-
-JavaScript does not support a packageing mechanism to be used for modular programming.
-Scripts are loaded from different files and executed within the same or different global objects.
-Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
-The same mechanism can be used to define nested subpackages.
-As the project size and the number of functions increases, the function name may not be enough to recognize the function.
-The developer also wants to know the function's library or package name.
 
@@
 
+The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
+The {\small\texttt{this}} value is missed in both views.
+The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+
 \section{Automated Funcation Naming}
+  The problem is discussed in several locations on the web \cite{DisplayName, Zaytsev} and various solutions have been proposed by developers.
+A simple solution would be annotating the function by its name or adding a property (e.g., \textit{displayName}) with the function name as its value.
+Although these solutions may help, they cause developers extra work.
+	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code.
+Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
 
-    To tackle the aforementioned issues caused due to the lack of function names, we propose automated function naming by anlyzing the source code and extracting the initial name used for the function object after its creation.
-To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
+\subsection{The Rationale}
+\subsubsection{Function Object vs. Function Body}%What Should be Named?}
+The first question arises is that which one should be named?
+the function body or the function object.
+A function name must help the developer to distinguish the function from other functions with different behaviours.
+The behaviour of a function object, in addition to its body (the source code), is dependent to the enclosing scopes (e.g., global and closure variables).
+Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code.
+Therefore, to name a function object, it is fair enough to name its \textit{function body}.
 
-    We can recognize seven function bodies in the code, none of them has a name.
-The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
-The result is assigned to variable {\small\texttt{main}}.
-Therefore the internal function body is named {\small\texttt{main}} as its corresponding function object is assinged to a variable with this name.
-What about the outer function itself?
-We name that
- {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+%\subsubsection{Static vs. Dynamic}
+%Can we improve the names at runtime?
+% function object path in dom model is good candidate for the name but only for persistent objects ?
+
+%\subsubsection{Local vs. Global}
+
+%It is conceivable that two function objects which are created from the same function body have different enclosing scopes and therefore different behaviours.
+
+%, the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
+The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.
+
+%\subsubsection{Is it possible to automatically name all functions?}
+\subsubsection{What Makes a Good Function Name?}
+A function name should be useful for both the developer who are familar with the code and the developer who is not.
+It should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used (e.g., to create object \textit{foo}), or at least works as an identifier.
+
+A function body can be uniquely identified by its location in the source file.
+A naive proposal for the function name for a function body is a combination of the function file name and line number.
+Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+On the other extreme extend, the function body itself can be used as the function identifier.
+This identifier it too long to be displayed and read by the developer.
+
+JavaScript does not support a packageing mechanism to be used for modular programming.
+Scripts are loaded from different files and executed within the same or different global objects.
+Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
+The same mechanism can be used to define nested subpackages.
+As the project size and the number of functions increases, the function name may not be enough to recognize the function.
+The developer also wants to know the function's library or package name.
+
+%\subsubsection{Other Challenges}%
+% functions pass the name as string, different types of class definitions
 
@@
 \centering
-\caption{Different cases of function object creation and usage in JavaScript.}
 \scalebox{0.8}{
@@
   }
- \label{function-types} 
+\caption{Different cases of function object creation and usage in JavaScript.}
+\label{table:function-types} 
 \end{table}
-
- The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
-We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
-A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
-However the latter requires knowning the function body of the called function which is not always possible.
-
-    As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are assigned to variable with the same names.
-Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}}, the functions in lines 25 and 27 can be named {\small\texttt{opClosure}} and {\small\texttt{op}} respectively.
 
@@
 \centering
-\caption{The number of nameless functions in each category defined in table~\ref{function-types}.}
   \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
@@
   \end{tabular}
- \label{function-types-count} 
+\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
+\label{function-type-count} 
 \end{table*}
+
+\subsection{The basic idea}
+   We employ the fact that developers know many function objects (particularly those which are reused) by the names they can access and call them. 
+   On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
+Therefore, we analyze the code to find all names that the function object is assigned to them.
+For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep trakc of the function effect on other identifiers.
+
+   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
+We can recognize seven function bodies in the code, none of them has a name.
+For every function we first build a summary.
+The summary explains how the function object is used in relation to other identifiers.
+The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
+The result is assigned to variable {\small\texttt{main}}.
+In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
+The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
+
+%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
+What about the outer function itself?
+We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+
+The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
+This function contributes in producing the {\small\texttt{result}} value.
+Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
+%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
+A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
+However the latter requires knowning the function body of the called function which is not always possible.
+
+As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
+The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
+
+%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
+
+\subsection{Function Object Creation and Consumption}
+%     and extracting the initial name used for the function object after its creation. 
+%In the third subsection we discuss qualities we expect from an automatically created function name.
 
@@
 We can generalize the approach used for naming functions in the example by studying differnt cases that a function object can be created and used.
-Once a function object is created, one of the cases presented in Table~\ref{function-types} can happen.
+Once a function object is created, one of the cases presented in Table~\ref{table:function-types} can happen.
 One common case of function object creation is by top script named function bodies.
@@
 We discuss this reduction in ~\ref{sec:general-element-naming}.
-Table~\ref{function-types-count} shows the number of nameless functions in each category in the studied projects.
+Table~\ref{function-type-count} shows the number of nameless functions in each category in the studied projects.
 These numbers shows how frequent and important a category of functions is in these projects.
@@
 Calling functions objects just after their creations is a common pattern in JavaScript.
-This pattern is usually used for building modules employing the clousure feature in JavaScript.
+This pattern is usually used for building modules employing the closure feature in JavaScript.
 Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
@@
 Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
-Many constructors are build by this form and therfore the name of thes functions appear in object summaries.
+Many constructors are build by this form and therefore the name of thes functions appear in object summaries.
 
@@
 \centering
-\caption{JavaScript Expression Reduction to Name.}
 \scalebox{0.9}{
@@
   }
+\caption{JavaScript Expression Reduction to Name.}
 \label{expression-reduction} 
@@
 \centering
-\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
 \scalebox{0.9}{
@@
  \label{firebug} 
+\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
 \end{table}
@@
 
+% open problems: naming scripts loaded and evaluated by eval,
 \section{Related Work}
+% ecoop 2009 paper
+% typing system papers
 
 \section{Conclusion}
-In this paper we presented an approach for naming JavaScript functions both
-as individual objects and in call stack.
+We highlighted the problem of nameless functions in JavaScript. We studied 10 famous JavaScript projects source code. From
+our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
+values and functions in callstack.
 
-\appendix
-\section{Appendix Title}
+%\appendix
+%\section{Appendix Title}
 
-This is the text of the appendix, if you need one.
+%This is the text of the appendix, if you need one.
 
-\acks
+%\acks
 
-Acknowledgments, if needed.
+%Acknowledgments, if needed.
 
@@
 \newblock http://www.commonjs.org/
+
+\bibitem{DisplayName}
+Add prettyName/displayName support to Profiler output and Stacks.
+\newblock \emph{Firebug Bug Repository},
+\newblock http://code.google.com/p/fbug/issues/detail?id=1811
 

### 2011-03-28 trunk/papers/splash-wavefront2011/sigplanconf-template.tex

@@
 
+%\section{The Nameless Function Problem}
+\section{Anonymous Functions Problem}
+
+A JavaScript function can be defined in different ways: by the {\small\texttt{function}} operator (i.e., function decleration or expression) or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
+Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} object is created.
+Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects can be created from the same definition.
+To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
+
 \begin{table}
 \centering
-\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
 \scalebox{0.9}{
@@
 
+The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
+The {\small\texttt{this}} value is missed in both views.
+The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+
+\section{Discussion}
+The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}.
+Different solutions have been proposed and discussed by practitioners.
+A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes.
+For example, a new property (e.g., \textit{displayName}) in function object can be used for storing the function name, or the function name can be defined by annotation.
+Although these solutions may help, they cause developers extra work.
+
+%Morover, these solutions do not work for lagacy code.
+We instead propose an automated approach for naming all functions by anlyzing the source code.
+Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.
+
+%\subsection{Rationale}
+\subsection{Function Object vs. Function Body}%What Should be Named?}
+The first question arises is that which one should be named?
+the function body or the function object.
+A function name must help the developer to distinguish the function from other functions with different behaviours.
+The behaviour of a function object, in addition to its body (the source code), is dependent to the enclosing scopes (e.g., global and closure variables).
+Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code.
+Therefore, to name a function object, it is fair enough to name its \textit{function body}.
+
+%\subsubsection{Static vs. Dynamic}
+%Can we improve the names at runtime?
+% function object path in dom model is good candidate for the name but only for persistent objects ?
+
+%\subsubsection{Local vs. Global}
+
+%It is conceivable that two function objects which are created from the same function body have different enclosing scopes and therefore different behaviours.
+
+%, the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
+The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.
+
+%\subsubsection{Is it possible to automatically name all functions?}
+\subsection{What Makes a Good Function Name?}
+A function name should be useful for both the developer who are familar with the code and the developer who is not.
+It should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used (e.g., to create object \textit{foo}), or at least works as an identifier.
+
+A function body can be uniquely identified by its location in the source file.
+A naive proposal for the function name for a function body is a combination of the function file name and line number.
+Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+On the other extreme extend, the function body itself can be used as the function identifier.
+This identifier it too long to be displayed and read by the developer.
+
+JavaScript does not support a packageing mechanism to be used for modular programming.
+Scripts are loaded from different files and executed within the same or different global objects.
+Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
+The same mechanism can be used to define nested subpackages.
+As the project size and the number of functions increases, the function name may not be enough to recognize the function.
+The developer also wants to know the function's library or package name.
+
+%\subsubsection{Other Challenges}%
+% functions pass the name as string, different types of class definitions
+
 \section{Automated Funcation Naming}
-
-    To tackle the aforementioned issues caused due to the lack of function names, we propose automated function naming by anlyzing the source code and extracting the initial name used for the function object after its creation.
-To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
-
-    We can recognize seven function bodies in the code, none of them has a name.
-The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
-The result is assigned to variable {\small\texttt{main}}.
-Therefore the internal function body is named {\small\texttt{main}} as its corresponding function object is assinged to a variable with this name.
-What about the outer function itself?
-We name that
- {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code.
+Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
 
@@
   \end{tabular}
- \label{function-types-count} 
+\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
+\label{function-type-count} 
 \end{table*}
+
+\subsection{basic idea}
+   Developers refer to function objects in JavaScript in different ways.
+For permanet global functions (e.g., classes, utility functions) the alias used to access the function object is the natural way of refereing.
+Other function objects which have shorter life time and are not assigned to an alias, are usually refered by their role or the way they affect other objects.
+We employ this fact and name function objects using their aliases or the aliases of objects they affect.
+
+      On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
+Therefore, we analyze the code to find all names that the function object is assigned to them.
+For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.
+
+   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
+We can recognize seven function bodies in the code, none of them has a name.
+For every function we first build a summary.
+The summary explains how the function object is used in relation to other identifiers.
+The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
+The result is assigned to variable {\small\texttt{main}}.
+In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
+The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
+
+%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
+What about the outer function itself?
+We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+
+The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
+This function contributes in producing the {\small\texttt{result}} value.
+Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
+%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
+A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
+However the latter requires knowning the function body of the called function which is not always possible.
+
+As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
+The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
+
+%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
+
+\subsection{Function Object Creation and Consumption}
+%     and extracting the initial name used for the function object after its creation. 
+%In the third subsection we discuss qualities we expect from an automatically created function name.
 

### 2011-03-29 trunk/papers/splash-wavefront2011/sigplanconf-template.tex

@@
 
-The other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
 In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
@@
 A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes.
-For example, a new property (e.g., \textit{displayName}) in function object can be used for storing the function name, or the function name can be defined by annotation.
+For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation.
 Although these solutions may help, they cause developers extra work.
 
-%Morover, these solutions do not work for lagacy code.
-We instead propose an automated approach for naming all functions by anlyzing the source code.
+We instead propose an almost automated approach for naming all functions by anlyzing the source code.
 Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.
 
-%\subsection{Rationale}
-\subsection{Function Object vs. Function Body}%What Should be Named?}
-The first question arises is that which one should be named?
-the function body or the function object.
-A function name must help the developer to distinguish the function from other functions with different behaviours.
-The behaviour of a function object, in addition to its body (the source code), is dependent to the enclosing scopes (e.g., global and closure variables).
+\subsection{What Makes a Good Function Name?}
+A function name is basicly used to assist the developer to recall or understand the function behaviour.
+For a dveloper who is already familiar with the function, it works more like an identifier.
+However, this identifier should be easily recognized by the developer.
+For example, a naive proposal for the function name is a combination of the function file name and its first line number.
+Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+
+ On the other hand, for a devloper who does not know the function, a function name should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
+A function name must not be too long that can not be displayed or read by the developer.
+For example, the function body explains the function behaviour well however it is not an appropriate function name.
+
+\subsection{What should be named?} %// Function Object or Function Body}%What Should be Named?}
+In JavaScript, functions can be accessed and changed like a regular object.
+Two function objects which are created from the same function body may have different properties.
+They also may have different enclosing scopes and therefore different behaviours.
+The question arises here is which one should be named, the function body or the function object?
 Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code.
-Therefore, to name a function object, it is fair enough to name its \textit{function body}.
+Therfore the general function behaviour is mainly dependent to its function body and the enclosed function bodies.
+
+\subsection{Context, Package and Function Names}
+JavaScript does not support a standard packageing mechanism to be used for modular programming.
+Scripts are loaded from different files and executed within the same or different global objects.
+Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
+The same mechanism is reused for defining subpackages.
+As the project size and the number of functions increases, the short function name will not be enough for recognizing the function.
+The developer also wants the class or the module contains the function.
+In addition to the package name, knowning the context (the enclosing function body) that contains the function can help in better understanding the function behaviour.
 
 %\subsubsection{Static vs. Dynamic}
-%Can we improve the names at runtime?
+% Can we improve the names at runtime?
 % function object path in dom model is good candidate for the name but only for persistent objects ?
@@
 %\subsubsection{Local vs. Global}
-
-%It is conceivable that two function objects which are created from the same function body have different enclosing scopes and therefore different behaviours.
-
-%, the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
+%the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
 The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.
@@
 %\subsubsection{Is it possible to automatically name all functions?}
-\subsection{What Makes a Good Function Name?}
-A function name should be useful for both the developer who are familar with the code and the developer who is not.
-It should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used (e.g., to create object \textit{foo}), or at least works as an identifier.
-
-A function body can be uniquely identified by its location in the source file.
-A naive proposal for the function name for a function body is a combination of the function file name and line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
-On the other extreme extend, the function body itself can be used as the function identifier.
-This identifier it too long to be displayed and read by the developer.
-
-JavaScript does not support a packageing mechanism to be used for modular programming.
-Scripts are loaded from different files and executed within the same or different global objects.
-Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
-The same mechanism can be used to define nested subpackages.
-As the project size and the number of functions increases, the function name may not be enough to recognize the function.
-The developer also wants to know the function's library or package name.
 
@@
 Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
+
+\subsection{basic idea}
+   Developers refer to function objects in JavaScript in different ways.
+For permanet global functions (e.g., classes, utility functions) the alias used to access the function object is the natural way of refereing.
+Other function objects which have shorter life time and are not assigned to an alias, are usually refered by their role or the way they affect other objects.
+We employ this fact and name function objects using their aliases or the aliases of objects they affect.
+
+      On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
+Therefore, we analyze the code to find all names that the function object is assigned to them.
+For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.
+
+   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
+We can recognize seven function bodies in the code, none of them has a name.
+For every function we first build a summary.
+The summary explains how the function object is used in relation to other identifiers.
+The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
+The result is assigned to variable {\small\texttt{main}}.
+In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
+The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
+
+%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
+What about the outer function itself?
+We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+
+The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
+This function contributes in producing the {\small\texttt{result}} value.
+Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
+%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
+A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
+However the latter requires knowning the function body of the called function which is not always possible.
+
+As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
+The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
+
+%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
 
@@
 \end{table*}
-
-\subsection{basic idea}
-   Developers refer to function objects in JavaScript in different ways.
-For permanet global functions (e.g., classes, utility functions) the alias used to access the function object is the natural way of refereing.
-Other function objects which have shorter life time and are not assigned to an alias, are usually refered by their role or the way they affect other objects.
-We employ this fact and name function objects using their aliases or the aliases of objects they affect.
-
-      On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
-Therefore, we analyze the code to find all names that the function object is assigned to them.
-For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.
-
-   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
-We can recognize seven function bodies in the code, none of them has a name.
-For every function we first build a summary.
-The summary explains how the function object is used in relation to other identifiers.
-The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
-The result is assigned to variable {\small\texttt{main}}.
-In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
-The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
-
-%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
-What about the outer function itself?
-We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
-
-The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
-This function contributes in producing the {\small\texttt{result}} value.
-Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
-%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
-A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
-However the latter requires knowning the function body of the called function which is not always possible.
-
-As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
-The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
-%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
 

### 2011-03-29 trunk/papers/splash-wavefront2011/sigplanconf-template.tex

@@
 
-\subsection{What should be named?} %// Function Object or Function Body}%What Should be Named?}
+\subsection{What Should be Named?} %// Function Object or Function Body}%What Should be Named?}
 In JavaScript, functions can be accessed and changed like a regular object.
@@
 
+%\subsection{Is it possible to automatically name functions?}
 %\subsubsection{Static vs. Dynamic}
@@
 
-\subsection{basic idea}
    Developers refer to function objects in JavaScript in different ways.
@@
 For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.
+
+\subsection{basic idea}
 
@@
   \hline 
+   1 &
+   & 
+   &  
+   & direct access.
+   & bar\textsuperscript{*}.foo = function()\{...\}\\
+   \cline{0-0}\cline{5-6}
 
-   1 &
+   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+   & 
+   & 
+   & \raggedright hashmap access by a string. 
+   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   3 &
+   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
+   & \raggedright hashmap access by a variable name.
+   & bar\textsuperscript{*}[foo] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   4 &
+   & 
+   & 
+   & \raggedright hashmap access by a JavaScript expression.
+   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   5 &
+   &
+   &
+   & \raggedright  array index.
+   & foo\textsuperscript{*}[0] = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   6 &
+   & 
+   & \multicolumn{2}{|l|}{
+      variable.}
+   & foo = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   7 &
    &  
@@
 
-	 2 &
-	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+	 8 &
+	 & 
 	 & \multicolumn{2}{|m{2.8cm}|}{
@@
    & [..., function()\{...\}, ...] \\ 
-   \cline{0-0}\cline{4-6}
-
-   3 &
-   & 
-   &  
-   & direct access.
-   & bar\textsuperscript{*}.foo = function()\{...\}\\
-   \cline{0-0}\cline{5-6}
-
-   4 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
-   & 
-   & 
-   & \raggedright hashmap access by a string. 
-   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   5 &
-   & 
-   & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
-   & \raggedright hashmap access by a variable name.
-   & bar\textsuperscript{*}[foo] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   6 &
-   & 
-   & 
-   & \raggedright hashmap access by a JavaScript expression.
-   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   7 &
-   &
-   & \multicolumn{2}{|l|}{
-      array index.}
-   & foo\textsuperscript{*}[0] = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   8 &
-   & 
-   & \multicolumn{2}{|l|}{
-      variable.}
-   & foo = function()\{...\} \\
    \cline{0-0}\cline{3-6}

### 2011-03-30 papers/splash-wavefront2011/sigplanconf-template.tex

@@
 %\section{The Nameless Function Problem}
-\section{The Anonymous Functions Problem}
+\section{Anonymous Functions Problem}
 
@@
 
-\section{Automated Funcation Naming}
-  The problem is discussed in several locations on the web \cite{DisplayName, Zaytsev} and various solutions have been proposed by developers.
-A simple solution would be annotating the function by its name or adding a property (e.g., \textit{displayName}) with the function name as its value.
+\section{Discussion}
+The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}.
+Different solutions have been proposed and discussed by practitioners.
+A basic solution is a mechanism for naming functions by developers without affecting the variables in scopes.
+For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation.
 Although these solutions may help, they cause developers extra work.
-	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code.
-Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
 
-\subsection{The Rationale}
-\subsubsection{Function Object vs. Function Body}%What Should be Named?}
-The first question arises is that which one should be named?
-the function body or the function object.
-A function name must help the developer to distinguish the function from other functions with different behaviours.
-The behaviour of a function object, in addition to its body (the source code), is dependent to the enclosing scopes (e.g., global and closure variables).
+We instead propose an almost automated approach for naming all functions by anlyzing the source code.
+Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.
+
+\subsection{What Makes a Good Function Name?}
+A function name is basicly used to assist the developer to recall or understand the function behaviour.
+For a dveloper who is already familiar with the function, it works more like an identifier.
+However, this identifier should be easily recognized by the developer.
+For example, a naive proposal for the function name is a combination of the function file name and its first line number.
+Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+
+ On the other hand, for a devloper who does not know the function, a function name should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
+A function name must not be too long that can not be displayed or read by the developer.
+For example, the function body explains the function behaviour well however it is not an appropriate function name.
+
+\subsection{What Should be Named?} %// Function Object or Function Body}%What Should be Named?}
+In JavaScript, functions can be accessed and changed like a regular object.
+Two function objects which are created from the same function body may have different properties.
+They also may have different enclosing scopes and therefore different behaviours.
+The question arises here is which one should be named, the function body or the function object?
 Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code.
-Therefore, to name a function object, it is fair enough to name its \textit{function body}.
+Therfore the general function behaviour is mainly dependent to its function body and the enclosed function bodies.
 
+\subsection{Context, Package and Function Names}
+JavaScript does not support a standard packageing mechanism to be used for modular programming.
+Scripts are loaded from different files and executed within the same or different global objects.
+Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
+The same mechanism is reused for defining subpackages.
+As the project size and the number of functions increases, the short function name will not be enough for recognizing the function.
+The developer also wants the class or the module contains the function.
+In addition to the package name, knowning the context (the enclosing function body) that contains the function can help in better understanding the function behaviour.
+
+%\subsection{Is it possible to automatically name functions?}
 %\subsubsection{Static vs. Dynamic}
-%Can we improve the names at runtime?
+% Can we improve the names at runtime?
 % function object path in dom model is good candidate for the name but only for persistent objects ?
@@
 %\subsubsection{Is it possible to automatically name all functions?}
-\subsubsection{What Makes a Good Function Name?}
-A function name should be useful for both the developer who are familar with the code and the developer who is not.
-It should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used (e.g., to create object \textit{foo}), or at least works as an identifier.
-
-A function body can be uniquely identified by its location in the source file.
-A naive proposal for the function name for a function body is a combination of the function file name and line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
-On the other extreme extend, the function body itself can be used as the function identifier.
-This identifier it too long to be displayed and read by the developer.
-
-JavaScript does not support a packageing mechanism to be used for modular programming.
-Scripts are loaded from different files and executed within the same or different global objects.
-Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
-The same mechanism can be used to define nested subpackages.
-As the project size and the number of functions increases, the function name may not be enough to recognize the function.
-The developer also wants to know the function's library or package name.
 
@@
 % functions pass the name as string, different types of class definitions
+
+\section{Automated Funcation Naming}
+%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code.
+Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
+  Developers usually understand and refer to function objects by aliases they use to access them.
+This fact particularly holds for permanent function objects such as classes and utility functions.
+However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program.
+We employ these facts to construct an identifier for a function.
+We analyse the source code to locate alias(es) which the function object is assigned to.
+If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name.
+Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values.
+If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure.
+If the case of function calls chain we use the most nested called function name for constructing the identifier.
+In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.
+
+    %  On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
+Therefore, we analyze the code to find all names that the function object is assigned to them.
+For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep track of the function effect on other identifiers.
+
+\subsection{Examples}
+
+   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
+We can recognize seven function bodies in the code, none of them has a name.
+For every function we first build a summary.
+The summary explains how the function object is used in relation to other identifiers.
+The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
+The result is assigned to variable {\small\texttt{main}}.
+In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
+The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
+
+%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
+What about the outer function itself?
+We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+
+The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
+This function contributes in producing the {\small\texttt{result}} value.
+Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
+%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
+A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
+However the latter requires knowning the function body of the called function which is not always possible.
+
+As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
+The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
+
+%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
 
@@
 \end{table*}
-
-\subsection{The basic idea}
-   We employ the fact that developers know many function objects (particularly those which are reused) by the names they can access and call them. 
-   On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
-Therefore, we analyze the code to find all names that the function object is assigned to them.
-For cases where the function object is not assigned to a variable or object property but is used to produce other values we keep trakc of the function effect on other identifiers.
-
-   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
-We can recognize seven function bodies in the code, none of them has a name.
-For every function we first build a summary.
-The summary explains how the function object is used in relation to other identifiers.
-The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
-The result is assigned to variable {\small\texttt{main}}.
-In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
-The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
-
-%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
-What about the outer function itself?
-We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
-
-The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
-This function contributes in producing the {\small\texttt{result}} value.
-Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
-%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
-A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
-However the latter requires knowning the function body of the called function which is not always possible.
-
-As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
-The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
-%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
 

### 2011-03-30 papers/splash-wavefront2011/sigplanconf-template.tex

@@
 If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure.
-If the case of function calls chain we use the most nested called function name for constructing the identifier.
+In the case of function calls chain we use the most nested called function name for constructing the identifier.
 In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.
@@
 We can recognize seven function bodies in the code, none of them has a name.
-For every function we first build a summary.
+The first function in line 9 is called just after its creation and sets the {\small\texttt{main<}} value.
+We name this function {\small\texttt{main<}}.
+The symbol {\small\texttt{<}} shows that the function object contributes to the {\small\texttt{main}} value.
+To name the function object defined in line 10, we analyze the code to get the aliases used for the function object after its creation.
+Once the function object is created it is returned.
+As the enclosed function is just called after its creation we can continue our search for more aliases in the outer scope.
+The function object is assigned to {\small\texttt{main}}.
+Therfore we name it {\small\texttt{main}}.
+
+   %For every function we first build a summary.
 The summary explains how the function object is used in relation to other identifiers.
@@
 The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
-
 %    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
@@
 This function contributes in producing the {\small\texttt{result}} value.
-Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
+Moreover, it is located inside another function which is named {\small\texttt{main<}}.
+Therefore, its full name will be {\small\texttt{main</result<}}.
+The symbol {\small\texttt{/}} is used to separate the context name from the function name.
+
+%Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
 %We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
@@
 
-As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
+The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
+Therefore, the same names will be used for the functions.
+The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
+
+%As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
 The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

### 2011-03-31 papers/splash-wavefront2011/sigplanconf-template.tex

@@
 %\title{JavaScript Lost Names, Any Amendment?}
-\title{Fixing Lost JavaScript Function Names in Debuggers}
+%\title{Fixing Lost JavaScript Function Names in Debuggers}
+\title{Naming Anonymous JavaScript Functions}
 %\subtitle{Subtitle Text, if any}
@@
 \begin{lstlisting}[frame=single, language=myLang]
-9  var main = function() {
-10   return function() {
+9  var main = function() {         // main<
+10   return function() {           // main
 11     var foo = new FOO("a");
@@
 13     var result = op(
-14       function(value){
+14       function(value){          // main</result<
 15         return value;
@@
 18 }();
-19 var FOO = function(a) {
+19 var FOO = function(a) {         // FOO
 20   this.a = a;
 21 }
-22 var BAR = function(b) {
+22 var BAR = function(b) {         // BAR
 23   this.b = b;
 24 }
-25 var op = function() {
+25 var op = function() {           // op<
 26   var local;
-27   return function(callBack) {
+27   return function(callBack) {   // op
 28     local++;
@@
 In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.
+  Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+These functions usually receive a string as the class name or function name.
+In our approach we need to get hint about these functions declarations.
+These hints can be usually described in simple regular expressions.
 
@@
 The symbol {\small\texttt{/}} is used to separate the context name from the function name.
+The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
+Therefore, the same names will be used for the functions.
+The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
 
@@
 However the latter requires knowning the function body of the called function which is not always possible.
-
-The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
-Therefore, the same names will be used for the functions.
-The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
 %As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.

### 2011-04-01 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
sections 1 and 2.0, but did not re-read it yet

@@
 \conferenceinfo{WXYZ '05}{date, City.} 
-\copyrightyear{2005} 
+\copyrightyear{2011} 
 \copyrightdata{[to be supplied]}
@@
 \titlebanner{preprint}        % These are ignored unless
-\preprintfooter{Fixing JavaScript Function Names}   % 'preprint' option specified.
+\preprintfooter{Naming Anonymous JavaScript Functions}   % 'preprint' option specified.
 
@@
 
-To cope with the pace of changes, JavaScript developers need improved develoment processes, practices and tools.
-They need modern editors for writing and editing larger programs and effective tools for understanding complicated JavaScript runtime.
-However, there has been severe inherent barriers for improving JavaScript tool support.
-JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
-JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
-As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
-For example, the value of a variable can be a primitive value, an object with any structure or even a function.
-One callsite may invoke different function bodies with various number of arities that none of them can be understood from the code.
-Therefore, the lack of descriptive data in JavaScript code is the most fundumental issue in enhancing JavaScript tool support.
+To cope with these large and sophisticated systems, JavaScript developers turn to better development tools.
+These tools analyze then represent the program in ways that the developer might only be able to imagine through substaintial time-consuming reading of source code.
+One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.
+All of these tools need to express program artifacts in a compact way the developer can understand.
+For example, the debugger needs to present the execution call stack so the developer can understand which functions are currently active.
+Obviously a particularly good compact representation would be a name given by the developer in the source code.
+However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones.
+Anonymous artifacts prevent tools from communcating effectively with developers.
 
-Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
-It can save developers' time, prevent bugs and improve the program quality.
-However, many errors can not be recognized without a strong typing stystem.
-To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
-These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
-The discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
-Moreover, the infered data can help in code comprehension if they are properly presented.
-Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
-This leads us to another hidden issue for improving JavaScript development tools; Due to highly dynamism in JavaScript many elements are remained nameless.
-Therefore there is no common language between the tool and developer for referring to elements.
+Among program artifacts, functions are central to program comprehension in JavaScript.
+In addition to the their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
+However, functions can be defined and created without a name or identifier.
 
-Developers usually understand JavaScript code by examining the running program in debuggers.
-At runtime, concrete values are available and the developer can directly check and understand object structures and control flows.
-Understanding a concrete value, particulary for non-primitive values such as objects and functions, is not always straightforward.
-To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
-For example, in the case of user-defined objects, the name of object's constructor in the object summary can be very helpful.
-It works like a class name in class-based languages and suggests the object structure.
-
-Functions are central to program comprehension in Java-Script.
-They are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
-However, there is a subtle issue with JavaScript functions that makes working with them quite difficult: functions can be defined and created without a name or identifier.
-This problem particularly shows up in debuggers \cite{Zaytsev}.
-
-In this paper, we analyze function creation and consumption in ten famous project.
+In this paper, we analyze function creation and consumption in ten large, well-known projects.
+We show that within these projects less than 7\% of the function objects are named.
 We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
@@
 
-%The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.
+%\section{The Nameless Function Problem}
+\section{The Anonymous Function Problem}
 
-%\section{The Nameless Function Problem}
-\section{Anonymous Functions Problem}
+A JavaScript function can be defined with the {\small\texttt{function}} operator or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
+The {\small\texttt{function}} operator can appear in a function declaration, function expression, or function statement (the latter form is available in Firefox but not part of a standard).
+Of these forms, only the function declaration requires a function name and the {\small\texttt{Function}} constructor has no mechanism to name the function.
+In other words, JavaScript developers can define functions with or without function names.
 
-A JavaScript function can be defined in different ways: by the {\small\texttt{function}} operator (i.e., function decleration or expression) or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
-Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} object is created.
-Notice that, depending on the times a function definition is evaluated, zero to many {\small\texttt{Function}} objects can be created from the same definition.
-To classify {\small\texttt{Function}} objects created by the same code, we call every script defines a function as a \textit{function body}.
+If you are unfamilar with JavaScript or other functional programming languages, you might imagine that developers would naturally select the form with names, simply as an organizational tool.
+However this is not the case.
+Functions in JavaScript are first-class objects.
+They can be assigned to any variable or object property, or passed as an argument to a function.
+Consequently JavaScript programmers can use this constructs to organize their thinking about the program, without the use of function names.
+
+So what do JavaScript developers do in practice?
+To get empirical evidence we analyzed the source code of ten well-known JavaScript projects.
+For every project, the total number of functions and the number of functions with an identifier are collected (Table~\ref{js-functions}).
+The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent.
+)Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function).
+Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
+Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
 
@@
 
-{\small\texttt{Function}} objects have no name by default; as the {\small\texttt{Function}} constructor doesn't receive any name.
-According to ECMA specification, an identifier (function name) can be specified after the {\small\texttt{function}} operator (It is mandatory for function declerations but optional for function expressions) \cite{ECMA}.
-However, developers usually hesitate to specify the function name and therefore the usage of function identifiers is very limited.
-The main cause of this hesitation is that function identifiers, in addition to naming the function, has another effect on the available variables in the current or inner scopes.
-In the case of function declearations, the function object is assigned to a variable in the function scope, but in the case of function expressions, the function object is available only inside the function body.
-The confusing behavior of function identifiers get worse by function statements introduced by some browsers such as Firefox.
-Function statements are like function expressions, but the function object is available in the entire function scope like function declarations \cite{Zaytsev}.
-As a consequence, developers often prefer to omit the function identifier in the function statement to avoid its confusing impact.
+% JJB TODO
+% It is common that the same function is called by various names in different contexts. 
+%Therefore, it is usually very difficult to recall the function operation from its local name. 
+%Developers have usually the option to look at the function code, but it becomes tedious
+% and time-consuming when developer has to do it over and over again.
 
-To investigate the correctness of above argument, we analyzed the source code of ten famous JavaScript projects.
-For every project, the total number of functions and the number of functions with an identifier are collected (Table~\ref{js-functions}).
-The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent.
-Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function.
-Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
-Therefore, the results support the fact that a large proportion of JavaScript functions are remained nameless by developers.
+%Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
+%object is created. Notice that, depending on the times a function definition is evaluated, 
+%zero to many {\small\texttt{Function}} objects can be created from the same definition. 
+%To classify {\small\texttt{Function}} objects created by the same code, we call every 
+%script defines a function as a \textit{function body}.
 
-Functions in JavaScript are first-class objects.
-They can be assigned to any variable or object proeprty, or passed as an argument to a function.
-It is common that the same function is called by various names in different contexts.
-Therefore, it is usually very difficult to recall the function operation from its local name.
-Developers have usually the option to look at the function code, but it becomes tedious and time-consuming when developer has to do it over and over again.
+To understand the consequences of anonymous funcitons on development tools we will focus on one example, the impact on debuggers.
 Two main issues apear in debuggers due to the lack of function name.
-First, object constructor name which can faciliate understanding the object value, is not available in the object summary.
-Second, the callstack view is usually full of \textit{anonymous} functions and therefore less informative.
+First, object constructor name, which can faciliate understanding the object value, is not available in the object summary.
+Second, the callstack view is usually full of \textit{anonymous} functions and therefore much less informative.
 We disscuss these issues in the next two subsections.
@@
 Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
+  Developers usually understand and refer to function objects by aliases they use to access them.
+This fact particularly holds for permanent function objects such as classes and utility functions.
+However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program.
+We employ these facts to construct an identifier for a function.
+We analyse the source code to locate alias(es) which the function object is assigned to.
+If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name.
+Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values.
+If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure.
+In the case of function calls chain we use the most nested called function name for constructing the identifier.
+In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.
+  Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+These functions usually receive a string as the class name or function name.
+In our approach we need to get hint about these functions declarations.
+These hints can be usually described in simple regular expressions.
 
-   Developers refer to function objects in JavaScript in different ways.
-For permanet global functions (e.g., classes, utility functions) the alias used to access the function object is the natural way of refereing.
-Other function objects which have shorter life time and are not assigned to an alias, are usually refered by their role or the way they affect other objects.
-We employ this fact and name function objects using their aliases or the aliases of objects they affect.
-
-      On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
+    %  On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
 Therefore, we analyze the code to find all names that the function object is assigned to them.
@@
 
-\subsection{basic idea}
+\subsection{Examples}
 
@@
 This function contributes in producing the {\small\texttt{result}} value.
-Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
+Moreover, it is located inside another function which is named {\small\texttt{main<}}.
+Therefore, its full name will be {\small\texttt{main</result<}}.
+The symbol {\small\texttt{/}} is used to separate the context name from the function name.
+The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
+Therefore, the same names will be used for the functions.
+The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
+
+%Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
 %We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
@@
 However the latter requires knowning the function body of the called function which is not always possible.
-
-As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
+%As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
 The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

### 2011-04-01 papers/splash-wavefront2011/sigplanconf-template.tex
add appendix 1 for citations to projects

@@
   }
-\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
+\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.}
 \label{js-functions} 
@@
 
-%\appendix
-%\section{Appendix Title}
-
-%This is the text of the appendix, if you need one.
+\appendix
+\section{JavaScript Projects Analyzed for Function Names}
+\begin{description}
+\item[Closure] Google Web Library, ...
+\item[Dojo] JavaScript Toolkit
+\item[ExtJS] JavaScript Framework
+\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
+\item[jQuery]
+\item[MochiKit]
+\item[MooTools]
+\item[Prototype]
+\item[Scriptaculous]
+\item[YUI]
+\end{description}
 

### 2011-04-01 papers/splash-wavefront2011/sigplanconf-template.tex
edits section 3, but could not check with latex

@@
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
-Morover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}.
+Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}.
 There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.
@@
 To cope with these large and sophisticated systems, JavaScript developers turn to better development tools.
-These tools analyze then represent the program in ways that the developer might only be able to imagine through substaintial time-consuming reading of source code.
+These tools analyze then represent the program in ways that the developer might only be able to imagine through substantial time-consuming reading of source code.
 One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.
@@
 However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones.
-Anonymous artifacts prevent tools from communcating effectively with developers.
+Anonymous artifacts prevent tools from communicating effectively with developers.
 
@@
 We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
-The candidate function names can be used in debuggers for more descriptive object summaries and callstack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
 
@@
 
-If you are unfamilar with JavaScript or other functional programming languages, you might imagine that developers would naturally select the form with names, simply as an organizational tool.
+If you are unfamiliar with JavaScript or other functional programming languages, you might imagine that developers would naturally select the form with names, simply as an organizational tool.
 However this is not the case.
@@
 \subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
-\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
+\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
 \label{debuggers-objects}
@@
 
-% JJB TODO
-% It is common that the same function is called by various names in different contexts. 
-%Therefore, it is usually very difficult to recall the function operation from its local name. 
-%Developers have usually the option to look at the function code, but it becomes tedious
-% and time-consuming when developer has to do it over and over again.
-
-%Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
-%object is created. Notice that, depending on the times a function definition is evaluated, 
-%zero to many {\small\texttt{Function}} objects can be created from the same definition. 
-%To classify {\small\texttt{Function}} objects created by the same code, we call every 
-%script defines a function as a \textit{function body}.
-
-To understand the consequences of anonymous funcitons on development tools we will focus on one example, the impact on debuggers.
-Two main issues apear in debuggers due to the lack of function name.
-First, object constructor name, which can faciliate understanding the object value, is not available in the object summary.
-Second, the callstack view is usually full of \textit{anonymous} functions and therefore much less informative.
-We disscuss these issues in the next two subsections.
+To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
+Two main issues appear in debuggers due to the lack of function name.
+First, object constructor name, which can facilitate understanding the object value, is not available in the object summary.
+Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative.
+We discuss these issues in the next two subsections.
 
@@
 Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code.
-We set a breakpoint on line 13 and examin the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
+We set a breakpoint on line 13 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
 Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}.
@@
 These additional properties may hint developer about the object structures.
-{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
+{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
 
@@
 To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debugger and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
+Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug.
+The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms.
 Google chrome shows \textit{anonymous} as the name of all functions excepting the first one.
 Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.
 
@@
 \subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
-\caption{The screenshot of callstack view of Google Chrome and Firebug JavaScript debuggers paused at the same breakpoint.}
+\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
 \label{debuggers-callstack}
@@
 The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+The \small\texttt{arguments} values is shown in Firebug, but it still suffers from the same issues as object summaries.
 
-\section{Discussion}
+\section{Goals}
 The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}.
@@
 For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation.
-Although these solutions may help, they cause developers extra work.
+Although these solutions may help, they cause developers extra work, the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.
 
-We instead propose an almost automated approach for naming all functions by anlyzing the source code.
+We instead propose an almost automated approach for naming all functions by analyzing the source code.
 Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.
 
+\subsection{What Should Be Named?}
+
+Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
+object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
+zero to many {\small\texttt{Function}} objects can be created from the same definition. 
+Two function objects which are created from the same function body may have different object properties added at runtime.
+They also may have different enclosing scopes and therefore different behaviors.
+Thus our first
+decision: do we try to name the {\small\texttt{Function}} objects or the source that defines them?
+
+For the common use cases, the different {\small\texttt{Function}} objects are bound to one or more properties of objects.
+The  names of these properties inform the developer about the role of the function in the actions of the object.
+To determine the actions of the functions in turn, the developer must read the function source (or perhaps its documentation).
+Our function names serve to recall or summarize that source or documentation for the developer.
+Therefore we seek to name the source, the content between the curly braces known as the \textit{FunctionBody} in the standard\cite{ECMA}.
+
+After reflection the reader may be puzzled by the preceding claim.
+On the one hand we claim that the function object instance may be bound to properties in multiple objects and those property names are not helpful for naming.
+On the other hand we will shortly introduce an algorithm that uses a property name (in part) to name a \textit{FunctionBody}.
+Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a \small\textit{Function}  to an object property differs from all other bindings because it is located in text near the \textit{FunctionBody} and thus developers associate this first binding with the meaning of the \small\textit{FunctionBody}.
+
 \subsection{What Makes a Good Function Name?}
-A function name is basicly used to assist the developer to recall or understand the function behaviour.
-For a dveloper who is already familiar with the function, it works more like an identifier.
+A function name is basically used to assist the developer to recall or understand the function behavior.
+For a developer who is already familiar with the function, it works more like an identifier.
 However, this identifier should be easily recognized by the developer.
 For example, a naive proposal for the function name is a combination of the function file name and its first line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+Although it may work as an identifier, but it does not assist the developer to recall or understand the function behavior.
 
- On the other hand, for a devloper who does not know the function, a function name should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
+ On the other hand, for a developer who does not know the function, a function name should explains the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
 A function name must not be too long that can not be displayed or read by the developer.
-For example, the function body explains the function behaviour well however it is not an appropriate function name.
-
-\subsection{What Should be Named?} %// Function Object or Function Body}%What Should be Named?}
-In JavaScript, functions can be accessed and changed like a regular object.
-Two function objects which are created from the same function body may have different properties.
-They also may have different enclosing scopes and therefore different behaviours.
-The question arises here is which one should be named, the function body or the function object?
-Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code.
-Therfore the general function behaviour is mainly dependent to its function body and the enclosed function bodies.
+For example, the function body explains the function behavior well however it is not an appropriate function name.
 
 \subsection{Context, Package and Function Names}
-JavaScript does not support a standard packageing mechanism to be used for modular programming.
+JavaScript does not support a standard packaging mechanism to be used for modular programming.
 Scripts are loaded from different files and executed within the same or different global objects.
@@
 The developer also wants the class or the module contains the function.
-In addition to the package name, knowning the context (the enclosing function body) that contains the function can help in better understanding the function behaviour.
+In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.
 
@@
 
-\section{Automated Funcation Naming}
+\section{Automated Function Naming}
 %	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code.

### 2011-04-05 papers/splash-wavefront2011/sigplanconf-template.tex

@@
 Among program artifacts, functions are central to program comprehension in JavaScript.
-In addition to the their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
+In addition to their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
 However, functions can be defined and created without a name or identifier.
@@
 The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+
+%In this paper, we analyze function creation and consumption in ten famous project.
+We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
+The candidate function names can be used in debuggers for more descriptive object summaries and callstack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+
+%The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.
 
@@
 The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent.
-)Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function).
+Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function).
 Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
@@
 
+\begin{figure}[htp]
+%{\small 
+%\begin{verbatim}
+
+\lstset{basicstyle=\scriptsize}
+\lstset{emph={FOO,BAR},emphstyle=\textit}
+%\lstset{backgroundcolor=\color{yellow}}
+\lstdefinelanguage{myLang}
+{morekeywords={if, function, var, return, new}}
+
+\begin{lstlisting}[frame=single, language=myLang]
+9  var main = function() {         // main<
+10   return function() {           // main
+11     var foo = new FOO("a");
+12     var bar = new BAR("b");
+13     var result = op(
+14       function(value){          // main/result<
+15         return value;
+16        });
+17   }
+18 }();
+19 var FOO = function(a) {         // FOO
+20   this.a = a;
+21 }
+22 var BAR = function(b) {         // BAR
+23   this.b = b;
+24 }
+25 var op = function() {           // op<
+26   var local;
+27   return function(callBack) {   // op
+28     local++;
+29     return callBack(local);
+30   }
+31 }();
+\end{lstlisting}
+%\end{verbatim}}
+\caption{An excerpt of a JavaScript code.}
+\label{js-code}
+\end{figure}
+
 \begin{figure*}[htp]
@@
 Firebug classify objects in the same general class, but includes some of the object properties in the summary.
-These additional properties may hint developer about the object structures.
+These additional properties may hint the developer about the object structures.
 {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
-
-\begin{figure}[htp]
-%{\small 
-%\begin{verbatim}
-
-\lstset{basicstyle=\scriptsize}
-\lstset{emph={FOO,BAR},emphstyle=\textit}
-%\lstset{backgroundcolor=\color{yellow}}
-\lstdefinelanguage{myLang}
-{morekeywords={if, function, var, return, new}}
-
-\begin{lstlisting}[frame=single, language=myLang]
-9  var main = function() {         // main<
-10   return function() {           // main
-11     var foo = new FOO("a");
-12     var bar = new BAR("b");
-13     var result = op(
-14       function(value){          // main</result<
-15         return value;
-16        });
-17   }
-18 }();
-19 var FOO = function(a) {         // FOO
-20   this.a = a;
-21 }
-22 var BAR = function(b) {         // BAR
-23   this.b = b;
-24 }
-25 var op = function() {           // op<
-26   var local;
-27   return function(callBack) {   // op
-28     local++;
-29     return callBack(local);
-30   }
-31 }();
-\end{lstlisting}
-%\end{verbatim}}
-\caption{An excerpt of a JavaScript code.}
-\label{js-code}
-\end{figure}
 
@@
 The {\small\texttt{this}} value is missed in both views.
-The \small\texttt{arguments} values is shown in Firebug, but it still suffers from the same issues as object summaries.
+The {\small\texttt{arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.
 
@@
 On the other hand we will shortly introduce an algorithm that uses a property name (in part) to name a \textit{FunctionBody}.
-Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a \small\textit{Function}  to an object property differs from all other bindings because it is located in text near the \textit{FunctionBody} and thus developers associate this first binding with the meaning of the \small\textit{FunctionBody}.
+Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a {\small\textit{Function}}  to an object property differs from all other bindings because it is located in text near the \textit{FunctionBody} and thus developers associate this first binding with the meaning of the {\small\textit{FunctionBody}}.
 
@@
 We employ these facts to construct an identifier for a function.
-We analyse the source code to locate alias(es) which the function object is assigned to.
+We analyze the source code and build a summary that explains the function object creation, consumption and assignment.
+This summary which only contains identifiers (i.e., variable and property names) and strings available in the source code gives us the ingeredients for function identifier construction.
+
+  %We analyse the source code to obtain the alias(es) that used for the function object or  is assigned to.
 If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name.
@@
 In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.
-  Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
-These functions usually receive a string as the class name or function name.
-In our approach we need to get hint about these functions declarations.
-These hints can be usually described in simple regular expressions.
 
@@
 
-\subsection{Examples}
+\subsection{Example}
 
@@
 We can recognize seven function bodies in the code, none of them has a name.
-The first function in line 9 is called just after its creation and sets the {\small\texttt{main<}} value.
-We name this function {\small\texttt{main<}}.
-The symbol {\small\texttt{<}} shows that the function object contributes to the {\small\texttt{main}} value.
-To name the function object defined in line 10, we analyze the code to get the aliases used for the function object after its creation.
-Once the function object is created it is returned.
-As the enclosed function is just called after its creation we can continue our search for more aliases in the outer scope.
-The function object is assigned to {\small\texttt{main}}.
-Therfore we name it {\small\texttt{main}}.
+The first function in line 9 is called just after its creation and sets the {\small\texttt{main}} value.
+We can explain the function object consumption after its creation in two steps: 1)The function object is called.
+2)The result is assigned to {\small\texttt{main}}.
+We use this summary to name the function.
+Although the result object is different from the function object, the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value.
+Based on this analysis, we name the function object {\small\texttt{main<}}.
+The symbol {\small\texttt{<}} shows the contribution part.
 
-   %For every function we first build a summary.
-The summary explains how the function object is used in relation to other identifiers.
-The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
-The result is assigned to variable {\small\texttt{main}}.
-In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
-The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
-%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
-What about the outer function itself?
-We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+The function in line 10 is returned just after its creation.
+However, as the enclosing function is just called after its creation we can follow the function object flow in the enclosing scope and see that the function object is assigned to {\small\texttt{main}}.
+The summary of the function object consumption will be: 1)The function object is returned.
+2)The function object is assigned to {\small\texttt{main}}.
+As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
 
-The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
-This function contributes in producing the {\small\texttt{result}} value.
-Moreover, it is located inside another function which is named {\small\texttt{main<}}.
-Therefore, its full name will be {\small\texttt{main</result<}}.
-The symbol {\small\texttt{/}} is used to separate the context name from the function name.
-The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
+We can write the consumption summary for the third function (defined in line 14), in this form: 1)The function object is passed as an argument to function {\small\texttt{op}}.
+2) The call result is assigned to {\small\texttt{result}}.
+If we simply put of identifiers in this summary together we get {\small\texttt{result<op()}}.
+However, the function names (here {\small\texttt{op}}) usually give an indirect information (e.g., role) about the function object.
+Therefore, as we explain in the next subsection, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
+After ignoring {\small\texttt{op}}, we will have {\small\texttt{result<}}.
+Therefore the full name of the function will be {\small\texttt{main/result<}}.
+The first part before slash  shows the context name (the enclosing function name) for this function.
+We can similarly name other functions in Figure~\ref{js-code}.
+
+%The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
 Therefore, the same names will be used for the functions.
 The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
-%Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
-%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
-A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
-However the latter requires knowning the function body of the called function which is not always possible.
-%As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
-The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
-%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
 
@@
 
+\subsection{Function Object Consumption Summary}
+We can generalize the approach used for naming functions in the example by studying differnt cases of function object creation and consumption.
+Once a function object is created, one of the cases presented in Table~\ref{table:function-types} can happen.
+Note that two cases where the funcation is a top script element and the function is created by {\small\texttt{Function}} constructor do not appear in the table.
+The top script functions can not be anonymous and the functions defined by the constructor can be consdiered as a regular function body.
+Names which are specified with a star in the table are expressions reduced to a name.
+We explain this reduction in ~\ref{sec:general-element-naming}.
+
+To obtain the function object consumption summary for a function body, we process the abstract syntax tree from the function definition node recursively back to the root node in the enclosed function.
+Nodes which are not one of the type specfied in Table~\ref{table:function-types} are ignored.
+As we go upward in the tree, we keep identifiers and whether the object consumed is the same, part of or contributed to the result object.
+Once the summary is ready we construct the identifier.
+The identifiers come from function calls (case 11) are ignored if there is any other type of identifier.
+Otherwise, only the closest function call identifier will be used.
+
+\subsection{Reducing a JavaScript Expression to a Name}
+\label{sec:general-element-naming}
+
+\begin{table}
+\centering
+\scalebox{0.9}{
+  \begin{tabular}{ | l | l | l |}
+  \hline
+   Description & Total & Named \\ 
+  \hline 
+   Primitive Value & value & value.toString() \\ 
+  \hline 
+   Variable & foo & foo \\ 
+  \hline 
+   GetProp & bar.foo & Name(bar).foo \\ 
+  \hline 
+   GetElem & bar[foo] & Name(bar)+[Name(foo)] \\ 
+  \hline 
+   Add & bar op foo & Name(bar)+op+Name(foo) \\ 
+  \hline 
+   Condition & cond?bar:foo & Name(bar)+":"+Name(foo) \\ 
+  \hline 
+  \end{tabular}
+  }
+\caption{JavaScript Expression Reduction to Name.}
+\label{expression-reduction} 
+\end{table}
+
+\subsection{Building a String from Arguments}
+
+\subsection{Building a String from An Expression}
+
+\subsection{Namer Functions}
+Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+These functions usually receive a string as the class name or function name.
+The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
+A namer function works like an assignment in the summary.
+
+% to register a function with a name
+% to wrap the function
+% as a callback
+
+\subsection{Similar Function Names in a File}
+It is conceivable, that function bodies are named with the same names in a file.
+It can happen in different situations.
+One of the common cases is the two different function bodies may assing to a property based on a condition (e.g., the browser).
+For these cases we add a dollar sign and an index to the similar function names.
+For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+
+%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
+% more than one return
+
+\subsection{Temporary Variables} %aliases for the same object
+
+\subsection{Context Name}
+
+\subsection{Functions created by {\large \texttt{eval()}}}
+The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is avaialble.
+However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
+
+%\section{Improved by Runtime Data}
+%\subsection{Naming Functions in Call Stack}
+
+\begin{figure}[htp]
+\begin{verbatim}
+(a)
+ foo();
+(b)
+ foo.bar();
+(c)
+ foo.apply(bar, args);
+(d)
+ foo.call();
+\end{verbatim}
+\caption{Different cases of function object creation.}
+\label{fig:functionCall}
+\end{figure}
+
+\section{evaluation}
+
+\subsection{Object Creation}
+
 \begin{table*}
@@
 
-\subsection{Function Object Creation and Consumption}
 %     and extracting the initial name used for the function object after its creation. 
@@
 
-% to register a function with a name
-% to wrap the function
-% as a callback
-
-\subsection{Reducing a JavaScript Expression to a Name}
-\label{sec:general-element-naming}
-
-\begin{table}
-\centering
-\scalebox{0.9}{
-  \begin{tabular}{ | l | l | l |}
-  \hline
-   Description & Total & Named \\ 
-  \hline 
-   Primitive Value & value & value.toString() \\ 
-  \hline 
-   Variable & foo & foo \\ 
-  \hline 
-   GetProp & bar.foo & Name(bar).foo \\ 
-  \hline 
-   GetElem & bar[foo] & Name(bar)+[Name(foo)] \\ 
-  \hline 
-   Add & bar op foo & Name(bar)+op+Name(foo) \\ 
-  \hline 
-   Condition & cond?bar:foo & Name(bar)+":"+Name(foo) \\ 
-  \hline 
-  \end{tabular}
-  }
-\caption{JavaScript Expression Reduction to Name.}
-\label{expression-reduction} 
-\end{table}
-
-\subsection{Similar Function Names in a File}
-It is conceivable, that function bodies are named with the same names in a file.
-It can happen in different situations.
-One of the common cases is the two different function bodies may assing to a property based on a condition (e.g., the browser).
-For these cases we add a dollar sign and an index to the similar function names.
-For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
-
-%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
-% more than one return
-
-\subsection{Package Name}
-
-\subsection{Functions created by {\large \texttt{eval()}}}}
-The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is avaialble.
-However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
-
-\section{Improved by Runtime Data}
-\subsection{Naming Functions in Call Stack}
-
-\begin{figure}[htp]
-\begin{verbatim}
-(a)
- foo();
-(b)
- foo.bar();
-(c)
- foo.apply(bar, args);
-(d)
- foo.call();
-\end{verbatim}
-\caption{Different cases of function object creation.}
-\label{fig:functionCall}
-\end{figure}
-
-\section{evaluation}
-
 \subsection{Developers' vs. Automated Names}
@@
 
+%JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
+JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
+As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
+For example, the value of a variable can be a primitive value, an object with any structure or even a function.
+One callsite may invoke different function bodies with various number of arities that none of them can be understood from the code.
+Therefore, the lack of descriptive data in JavaScript code is the most fundumental issue in enhancing JavaScript tool support.
+
+Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
+It can save developers' time, prevent bugs and improve the program quality.
+However, many errors can not be recognized without a strong typing stystem.
+To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
+These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
+The discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
+Moreover, the infered data can help in code comprehension if they are properly presented.
+Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
+This leads us to another hidden issue for improving JavaScript development tools; Due to highly dynamism in JavaScript many elements are remained nameless.
+Therefore there is no common language between the tool and developer for referring to elements.
+
+%Developers usually understand JavaScript code by examining the running program in debuggers.
+At runtime, concrete values are available and the developer can directly check and understand object structures and control flows.
+Understanding a concrete value, particulary for non-primitive values such as objects and functions, is not always straightforward.
+To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
+For example, in the case of user-defined objects, the name of object's constructor in the object summary can be very helpful.
+It works like a class name in class-based languages and suggests the object structure.
 \section{Conclusion}

### 2011-04-06 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
first pass on sections 4.0, 4.1 and 4.2

@@
 However, the JavaScript language itself does not require names for many program artifacts and -- as we shall see -- nameless or anonymous artifacts are more common than named ones.
-Anonymous artifacts prevent tools from communcating effectively with developers.
+Anonymous artifacts prevent tools from communicating effectively with developers.
 
 Among program artifacts, functions are central to program comprehension in JavaScript.
-In addition to the their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
+In addition to their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
 However, functions can be defined and created without a name or identifier.
@@
 We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
+The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+
+%In this paper, we analyze function creation and consumption in ten famous project.
+We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
 The candidate function names can be used in debuggers for more descriptive object summaries and callstack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+
+%The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.
 
@@
   }
-\caption{The total number of functions and the number of named functions in ten famous JavaScript projects.}
+\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.}
 \label{js-functions} 
 \end{table}
-
-\begin{figure*}[htp]
-\centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
-\hfil
-\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
-\caption{The screenshot of veriables view of Google Chrome and Firebug JavaScript debuggers displaying the same program state.}
-\label{debuggers-objects}
-\end{figure*}
-
-% JJB TODO
-% It is common that the same function is called by various names in different contexts. 
-%Therefore, it is usually very difficult to recall the function operation from its local name. 
-%Developers have usually the option to look at the function code, but it becomes tedious
-% and time-consuming when developer has to do it over and over again.
-
-%Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
-%object is created. Notice that, depending on the times a function definition is evaluated, 
-%zero to many {\small\texttt{Function}} objects can be created from the same definition. 
-%To classify {\small\texttt{Function}} objects created by the same code, we call every 
-%script defines a function as a \textit{function body}.
-
-To understand the consequences of anonymous funcitons on development tools we will focus on one example, the impact on debuggers.
-Two main issues apear in debuggers due to the lack of function name.
-First, object constructor name, which can faciliate understanding the object value, is not available in the object summary.
-Second, the callstack view is usually full of \textit{anonymous} functions and therefore much less informative.
-We disscuss these issues in the next two subsections.
-
-\subsection{Missed Constructor Name in Object Summary}
-JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new Constructor()}}).
-A constructor is a regular JavaScript function.
-Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called.
-The role of constructor is to initialize the empty object.
-Although the structure of object imposed by the constructor, unlike class-based object-oriented languages, may not remain intact during the object's lifetime \cite{Richards}, the constructor can still be used to classify the object.
-Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.
-
-Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code.
-We set a breakpoint on line 13 and examin the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
-Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}.
-However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects.
-The developer has to expand the object nodes to recognize their similarities and differences.
-Firebug classify objects in the same general class, but includes some of the object properties in the summary.
-These additional properties may hint developer about the object structures.
-{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behaviour; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
 
@@
 13     var result = op(
-14       function(value){          // main</result<
+14       function(value){          // main/result<
 15         return value;
@@
 
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
+\hfil
+\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
+\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
+\label{debuggers-objects}
+\end{figure*}
+
+To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
+Two main issues appear in debuggers due to the lack of function name.
+First, object constructor name, which can facilitate understanding the object value, is not available in the object summary.
+Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative.
+We discuss these issues in the next two subsections.
+
+\subsection{Missed Constructor Name in Object Summary}
+JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new Constructor()}}).
+A constructor is a regular JavaScript function.
+Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called.
+The role of constructor is to initialize the empty object.
+Although the structure of object imposed by the constructor, unlike class-based object-oriented languages, may not remain intact during the object's lifetime \cite{Richards}, the constructor can still be used to classify the object.
+Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.
+
+Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code.
+We set a breakpoint on line 13 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
+Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}.
+However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects.
+The developer has to expand the object nodes to recognize their similarities and differences.
+Firebug classify objects in the same general class, but includes some of the object properties in the summary.
+These additional properties may hint the developer about the object structures.
+{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
+
 \subsection{Anonymous Function Names in Callstack View}
 To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
-Figure~\ref{debuggers-callstack} shows how the program callstack is displayed in Google Chrome debugger and Firebug.
-The differences in the number of frames and line numbers between two callstacks are due to dissimilar event handling implementations in the underlying platforms.
+Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug.
+The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms.
 Google chrome shows \textit{anonymous} as the name of all functions excepting the first one.
 Firebug performs better by guessing three function names but it still fails in one case.
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behaviour.
+In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.
 
@@
 The {\small\texttt{this}} value is missed in both views.
-The arguments values is shown in Firebug, but it still sufferes from similar issues explained for displaying object summaries.
+The {\small\texttt{arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.
 
-\section{Discussion}
+\section{Automated Function Naming}
 The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}.
@@
 For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation.
-Although these solutions may help, they cause developers extra work.
+Although these solutions may help, they cause developers extra work, the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.
 
-We instead propose an almost automated approach for naming all functions by anlyzing the source code.
+We instead propose an almost automated approach for naming all functions by analyzing the source code.
 Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.
 
+\subsection{What Should Be Named?}
+
+Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
+object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
+zero to many {\small\texttt{Function}} objects can be created from the same definition. 
+Two function objects which are created from the same function body may have different object properties added at runtime.
+They also may have different enclosing scopes and therefore different behaviors.
+Thus our first
+decision: do we try to name the {\small\texttt{Function}} objects or the source that defines them?
+
+For the common use cases, the different {\small\texttt{Function}} objects are bound to one or more properties of objects.
+The  names of these properties inform the developer about the role of the function in the actions of the object.
+To determine the actions of the functions in turn, the developer must read the function source (or perhaps its documentation).
+Our function names serve to recall or summarize that source or documentation for the developer.
+Therefore we seek to name the source, the content between the curly braces known as the \textit{FunctionBody} in the standard\cite{ECMA}.
+
+After reflection the reader may be puzzled by the preceding claim.
+On the one hand we claim that the function object instance may be bound to properties in multiple objects and those property names are not helpful for naming.
+On the other hand we will shortly introduce an algorithm that uses a property name (in part) to name a \textit{FunctionBody}.
+Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a {\small\textit{Function}}  to an object property differs from all other bindings because it is located in text near the \textit{FunctionBody} and thus developers associate this first binding with the meaning of the {\small\textit{FunctionBody}}.
+
 \subsection{What Makes a Good Function Name?}
-A function name is basicly used to assist the developer to recall or understand the function behaviour.
-For a dveloper who is already familiar with the function, it works more like an identifier.
+A function name is basically used to assist the developer to recall or understand the function behavior.
+For a developer who is already familiar with the function, it works more like an identifier.
 However, this identifier should be easily recognized by the developer.
 For example, a naive proposal for the function name is a combination of the function file name and its first line number.
-Although it may work as an identifier, but it does not assist the develper to recall or understand the function behaviour.
+Although it may work as an identifier, but it does not assist the developer to recall or understand the function behavior.
 
- On the other hand, for a devloper who does not know the function, a function name should explains the function behaviour, or an abstraction of the function behaviour, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
+ On the other hand, for a developer who does not know the function, a function name should explains the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
 A function name must not be too long that can not be displayed or read by the developer.
-For example, the function body explains the function behaviour well however it is not an appropriate function name.
-
-\subsection{What Should be Named?} %// Function Object or Function Body}%What Should be Named?}
-In JavaScript, functions can be accessed and changed like a regular object.
-Two function objects which are created from the same function body may have different properties.
-They also may have different enclosing scopes and therefore different behaviours.
-The question arises here is which one should be named, the function body or the function object?
-Although the actual enclosing scopes are not known until the function object creation, their structure can be almost known from the enclosing source code.
-Therfore the general function behaviour is mainly dependent to its function body and the enclosed function bodies.
+For example, the function body explains the function behavior well however it is not an appropriate function name.
 
 \subsection{Context, Package and Function Names}
-JavaScript does not support a standard packageing mechanism to be used for modular programming.
+JavaScript does not support a standard packaging mechanism to be used for modular programming.
 Scripts are loaded from different files and executed within the same or different global objects.
@@
 
-\section{Automated Funcation Naming}
+\section{Static  Function Object Consumption}
+
+We call our automated naming solution "Static Function Object Consumption", since it relies only a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by binding to an object property, variable reference, or function argument.
+Static Function Object Consumption generalizes the built-in JavaScript naming and common, simple coding patterns like object property initializers and variable assignments typically recognized by developers as naming functions.
+The built-in naming, a function declaration, binds a name in a scope to a function object created from the adjacent function body.
+For example, in  {\small\texttt{function foo() \{return 1;\}}}, the name  {\small\texttt{foo}} is bound the the function body in curly braces.
+Object property initializers bind a object property name to a function created from an adjacent function body.
+For example,  {\small\texttt{var bar = \{foo: function()\{return 2; \}\}}}, sets {\small\texttt{bar.foo}} to a function object created from the body {\small\texttt{\{return 2;\}}}.
+While the language does not associate the function body with the property  {\small\texttt{bar.foo}}, a JavaScript developer would because the created function body initializes the property.
+Similarly, a varible name bound to a function object, such as {\small\texttt{var baz = function()\{return 3; \}}}, is naturally associated with the function body.
+All three of these simple cases share the character that a function body creates a function object which is then bound to an identifier.
+
+Our algorithm applies the same logic: we follow the function object backwards through the code to create a name in cases where an identifier is not directly given in the code.
+By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree.
+For each function body, we walk up the tree looking for the constructs in table 2.
+As we describe in section XX, for every matching construct we record identifiers or expressions to use in constructing a name.
+Then we assemble a name using the expression-reduction rules outlined in section YY and the context naming rules in section ZZ.
+The result is a summary that contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanitory tokens.
+It compactly explains the function object creation, consumption and assignment.
+For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.
+
 %	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code.
 Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
-  Developers usually understand and refer to function objects by aliases they use to access them.
+%  Developers usually understand and refer to function objects by aliases they use to access them.
 This fact particularly holds for permanent function objects such as classes and utility functions.
@@
 
-\subsection{Examples}
+\subsection{Example}
 
-   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
-We can recognize seven function bodies in the code, none of them has a name.
-The first function in line 9 is called just after its creation and sets the {\small\texttt{main<}} value.
-We name this function {\small\texttt{main<}}.
-The symbol {\small\texttt{<}} shows that the function object contributes to the {\small\texttt{main}} value.
-To name the function object defined in line 10, we analyze the code to get the aliases used for the function object after its creation.
-Once the function object is created it is returned.
-As the enclosed function is just called after its creation we can continue our search for more aliases in the outer scope.
-The function object is assigned to {\small\texttt{main}}.
-Therfore we name it {\small\texttt{main}}.
+To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
 
-   %For every function we first build a summary.
-The summary explains how the function object is used in relation to other identifiers.
-The first function defined in line 9 is called just after its creation and returns another function defined in line 10.
-The result is assigned to variable {\small\texttt{main}}.
-In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object.
-The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
-%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name.
-What about the outer function itself?
-We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.
+The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
+We can explain the function object consumption after its creation in two steps: 1) the function object is called (case 9 in table 2).
+2) the result is assigned to {\small\texttt{main}} (case 6 in table 2).
+This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
+We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".
 
-The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}.
-This function contributes in producing the {\small\texttt{result}} value.
-Moreover, it is located inside another function which is named {\small\texttt{main<}}.
-Therefore, its full name will be {\small\texttt{main</result<}}.
-The symbol {\small\texttt{/}} is used to separate the context name from the function name.
-The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
-Therefore, the same names will be used for the functions.
+The function in line 10 is returned just after its creation.
+However, as the enclosing function is just called after its creation we can follow the function object flow in the enclosing scope and see that the function object is assigned to {\small\texttt{main}}.
+The summary of the function object consumption will be: 1) the function object is returned (case 10, table 2), 2) the function object is assigned to {\small\texttt{main}} (case 6 table 2).
+As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
+BUT I DON"T GET IT.
+
+The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
+Here 1) the function object is passed as an argument to function {\small\texttt{op}} (case 11), 2) The call result is assigned to {\small\texttt{result}} (case 6).
+If we simply put of identifiers in this summary together we get {\small\texttt{main/result<op()}}.
+The first part before slash  shows the context name (the enclosing function name) for this function.
+However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
+Therefore, as we explain in the next subsection, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
+After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
+Eliding identifiers is important to avoid creating long, unweildy names.
+
+The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.
 The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
-%Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
-%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}).
-A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}).
-However the latter requires knowning the function body of the called function which is not always possible.
-%As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names.
-The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
-%Similar to the first two functions which are named {\small\texttt{mainClosure}} and {\small\texttt{main}},
 
@@
 
+\subsection{Overview of the Function Object Consumption Algorithm}
+The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
+For each function body look for the path of the function object from creation to consumption.
+We process the abstract syntax tree from the function definition node recursively back to the root node in the enclosed function.
+On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}.
+As we go upward in the tree, we keep identifiers and whether the object consumed is the same, part of, or contributed to the result object.
+Once the summary is ready we construct the identifier.
+The identifiers come from function calls (case 11) are ignored if there is any other type of identifier.
+Otherwise, only the closest function call identifier will be used.
+Nodes which are not one of the type specfied in Table~\ref{table:function-types} are ignored.
+
+Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table.
+The top script functions can not be anonymous and the functions defined by the constructor can be considered as a regular function body.
+Names which are specified with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifer in ~\ref{sec:general-element-naming}.
+
+\subsection{Reducing a JavaScript Expression to a Name}
+\label{sec:general-element-naming}
+
+\begin{table}
+\centering
+\scalebox{0.9}{
+  \begin{tabular}{ | l | l | l |}
+  \hline
+   Description & Total & Named \\ 
+  \hline 
+   Primitive Value & value & value.toString() \\ 
+  \hline 
+   Variable & foo & foo \\ 
+  \hline 
+   GetProp & bar.foo & Name(bar).foo \\ 
+  \hline 
+   GetElem & bar[foo] & Name(bar)+[Name(foo)] \\ 
+  \hline 
+   Add & bar op foo & Name(bar)+op+Name(foo) \\ 
+  \hline 
+   Condition & cond?bar:foo & Name(bar)+":"+Name(foo) \\ 
+  \hline 
+  \end{tabular}
+  }
+\caption{JavaScript Expression Reduction to Name.}
+\label{expression-reduction} 
+\end{table}
+
+\subsection{Building a String from Arguments}
+
+\subsection{Building a String from An Expression}
+
+\subsection{Namer Functions}
+Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+These functions usually receive a string as the class name or function name.
+The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
+A namer function works like an assignment in the summary.
+
+% to register a function with a name
+% to wrap the function
+% as a callback
+
+\subsection{Similar Function Names in a File}
+It is conceivable, that function bodies are named with the same names in a file.
+It can happen in different situations.
+One of the common cases is the two different function bodies may assing to a property based on a condition (e.g., the browser).
+For these cases we add a dollar sign and an index to the similar function names.
+For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+
+%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
+% more than one return
+
+\subsection{Temporary Variables} %aliases for the same object
+
+\subsection{Context Name}
+
+\subsection{Functions created by {\large \texttt{eval()}}}
+The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is avaialble.
+However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
+
+%\section{Improved by Runtime Data}
+%\subsection{Naming Functions in Call Stack}
+
+\begin{figure}[htp]
+\begin{verbatim}
+(a)
+ foo();
+(b)
+ foo.bar();
+(c)
+ foo.apply(bar, args);
+(d)
+ foo.call();
+\end{verbatim}
+\caption{Different cases of function object creation.}
+\label{fig:functionCall}
+\end{figure}
+
+\section{evaluation}
+
+\subsection{Object Creation}
+
 \begin{table*}

### 2011-04-06 papers/splash-wavefront2011/sigplanconf-template.tex
just spellcheck

@@
 However, understanding concrete values, particularly user-defined and function objects, is not always straightforward.
-Function names can aid in this regard; they can appear as the constructor name in object representation or as the function identifier in callstack.
-Based on our analysis over ten famous JavaScrip projects, unfortunately only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
+Function names can aid in this regard; they can appear as the constructor name in object representation or as the function identifier in call-stack.
+Based on our analysis over ten famous JavaScript projects, unfortunately only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
 As a solution to this problem, we propose an automated approach based on local source code analysis for naming nameless JavaScript functions.
-We applied our approach on several JavaScript projects and the resutls are very promising.
+We applied our approach on several JavaScript projects and the results are very promising.
 \end{abstract}
@@
 
-\section{Goals}
+\section{Automated Function Naming}
 The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}.
@@
 
-\section{Automated Function Naming}
+\section{Static  Function Object Consumption}
+
+We call our automated naming solution "Static Function Object Consumption", since it relies only a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by binding to an object property, variable reference, or function argument.
+Static Function Object Consumption generalizes the built-in JavaScript naming and common, simple coding patterns like object property initializers and variable assignments typically recognized by developers as naming functions.
+The built-in naming, a function declaration, binds a name in a scope to a function object created from the adjacent function body.
+For example, in  {\small\texttt{function foo() \{return 1;\}}}, the name  {\small\texttt{foo}} is bound the the function body in curly braces.
+Object property initializers bind a object property name to a function created from an adjacent function body.
+For example,  {\small\texttt{var bar = \{foo: function()\{return 2; \}\}}}, sets {\small\texttt{bar.foo}} to a function object created from the body {\small\texttt{\{return 2;\}}}.
+While the language does not associate the function body with the property  {\small\texttt{bar.foo}}, a JavaScript developer would because the created function body initializes the property.
+Similarly, a varible name bound to a function object, such as {\small\texttt{var baz = function()\{return 3; \}}}, is naturally associated with the function body.
+All three of these simple cases share the character that a function body creates a function object which is then bound to an identifier.
+
+Our algorithm applies the same logic: we follow the function object backwards through the code to create a name in cases where an identifier is not directly given in the code.
+By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree.
+For each function body, we walk up the tree looking for the constructs in table 2.
+As we describe in section XX, for every matching construct we record identifiers or expressions to use in constructing a name.
+Then we assemble a name using the expression-reduction rules outlined in section YY and the context naming rules in section ZZ.
+The result is a summary that contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
+It compactly explains the function object creation, consumption and assignment.
+For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.
+
 %	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code.
 Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
-  Developers usually understand and refer to function objects by aliases they use to access them.
+%  Developers usually understand and refer to function objects by aliases they use to access them.
 This fact particularly holds for permanent function objects such as classes and utility functions.
@@
 
-  %We analyse the source code to obtain the alias(es) that used for the function object or  is assigned to.
+  %We analyze the source code to obtain the alias(es) that used for the function object or  is assigned to.
 If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name.
@@
 
-To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}.
-We can recognize seven function bodies in the code, none of them has a name.
-The first function in line 9 is called just after its creation and sets the {\small\texttt{main}} value.
-We can explain the function object consumption after its creation in two steps: 1)The function object is called.
-2)The result is assigned to {\small\texttt{main}}.
-We use this summary to name the function.
-Although the result object is different from the function object, the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value.
-Based on this analysis, we name the function object {\small\texttt{main<}}.
-The symbol {\small\texttt{<}} shows the contribution part.
+To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
+
+The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
+We can explain the function object consumption after its creation in two steps: 1) the function object is called (case 9 in table 2).
+2) the result is assigned to {\small\texttt{main}} (case 6 in table 2).
+This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
+We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".
 
@@
 However, as the enclosing function is just called after its creation we can follow the function object flow in the enclosing scope and see that the function object is assigned to {\small\texttt{main}}.
-The summary of the function object consumption will be: 1)The function object is returned.
-2)The function object is assigned to {\small\texttt{main}}.
+The summary of the function object consumption will be: 1) the function object is returned (case 10, table 2), 2) the function object is assigned to {\small\texttt{main}} (case 6 table 2).
 As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
+BUT I DON"T GET IT.
 
-We can write the consumption summary for the third function (defined in line 14), in this form: 1)The function object is passed as an argument to function {\small\texttt{op}}.
-2) The call result is assigned to {\small\texttt{result}}.
-If we simply put of identifiers in this summary together we get {\small\texttt{result<op()}}.
-However, the function names (here {\small\texttt{op}}) usually give an indirect information (e.g., role) about the function object.
+The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
+Here 1) the function object is passed as an argument to function {\small\texttt{op}} (case 11), 2) The call result is assigned to {\small\texttt{result}} (case 6).
+If we simply put of identifiers in this summary together we get {\small\texttt{main/result<op()}}.
+The first part before slash  shows the context name (the enclosing function name) for this function.
+However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
 Therefore, as we explain in the next subsection, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
-After ignoring {\small\texttt{op}}, we will have {\small\texttt{result<}}.
-Therefore the full name of the function will be {\small\texttt{main/result<}}.
-The first part before slash  shows the context name (the enclosing function name) for this function.
-We can similarly name other functions in Figure~\ref{js-code}.
+After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
+Eliding identifiers is important to avoid creating long, unwieldy names.
 
-%The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}.
-Therefore, the same names will be used for the functions.
+The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.
 The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
@@
 
-\subsection{Function Object Consumption Summary}
-We can generalize the approach used for naming functions in the example by studying differnt cases of function object creation and consumption.
-Once a function object is created, one of the cases presented in Table~\ref{table:function-types} can happen.
-Note that two cases where the funcation is a top script element and the function is created by {\small\texttt{Function}} constructor do not appear in the table.
-The top script functions can not be anonymous and the functions defined by the constructor can be consdiered as a regular function body.
-Names which are specified with a star in the table are expressions reduced to a name.
-We explain this reduction in ~\ref{sec:general-element-naming}.
-
-To obtain the function object consumption summary for a function body, we process the abstract syntax tree from the function definition node recursively back to the root node in the enclosed function.
-Nodes which are not one of the type specfied in Table~\ref{table:function-types} are ignored.
-As we go upward in the tree, we keep identifiers and whether the object consumed is the same, part of or contributed to the result object.
+\subsection{Overview of the Function Object Consumption Algorithm}
+The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
+For each function body look for the path of the function object from creation to consumption.
+We process the abstract syntax tree from the function definition node recursively back to the root node in the enclosed function.
+On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}.
+As we go upward in the tree, we keep identifiers and whether the object consumed is the same, part of, or contributed to the result object.
 Once the summary is ready we construct the identifier.
@@
 Otherwise, only the closest function call identifier will be used.
+Nodes which are not one of the type specified in Table~\ref{table:function-types} are ignored.
+
+Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table.
+The top script functions can not be anonymous and the functions defined by the constructor can be considered as a regular function body.
+Names which are specified with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.
 
@@
 It can happen in different situations.
-One of the common cases is the two different function bodies may assing to a property based on a condition (e.g., the browser).
+One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser).
 For these cases we add a dollar sign and an index to the similar function names.
@@
 \subsection{Functions created by {\large \texttt{eval()}}}
-The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is avaialble.
+The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is available.
 However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
@@
 \subsection{Naming Scheme}
-We can generalize the approach used for naming functions in the example by studying differnt cases that a function object can be created and used.
+We can generalize the approach used for naming functions in the example by studying different cases that a function object can be created and used.
 Once a function object is created, one of the cases presented in Table~\ref{table:function-types} can happen.
@@
 Moreover, Note that functions are created by {\small\texttt{Function}} constructor can be replace by a function body and named in the same way.
-For every case, we will explain how a name can be assinged to the function.
+For every case, we will explain how a name can be assigned to the function.
 
@@
 \subsubsection{Case 1: in Object Literal}
- This case usually apears when developers try to group a set of functions in a new object.
+ This case usually appears when developers try to group a set of functions in a new object.
 A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
@@
 Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
-This case usually happens when the functinos are assinged to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
+This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
 
@@
 \subsubsection{Case 5: setProperty by variable}
-The usage of this case is also limited. This form usually apears when the same function body is assigned to different properties in a loop. Therefore, the variable
+The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. Therefore, the variable
  name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
-Morover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
+Moreover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
 To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
@@
 \subsubsection{Case 6: setProperty by Expression}
- A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condtion?"prop1":"prop2"}}.
+ A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}.
 To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
@@
 The function is usually registered with a name which is also passed as string argument.
-Therefore, to imporove our naming approach, we include the first string argument (if there is any) in the name.
+Therefore, to improve our naming approach, we include the first string argument (if there is any) in the name.
 For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
@@
 For example, the value of a variable can be a primitive value, an object with any structure or even a function.
-One callsite may invoke different function bodies with various number of arities that none of them can be understood from the code.
-Therefore, the lack of descriptive data in JavaScript code is the most fundumental issue in enhancing JavaScript tool support.
+One call-site may invoke different function bodies with various number of arities that none of them can be understood from the code.
+Therefore, the lack of descriptive data in JavaScript code is the most fundamental issue in enhancing JavaScript tool support.
 
@@
 It can save developers' time, prevent bugs and improve the program quality.
-However, many errors can not be recognized without a strong typing stystem.
+However, many errors can not be recognized without a strong typing system.
 To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
@@
 The discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
-Moreover, the infered data can help in code comprehension if they are properly presented.
+Moreover, the inferred data can help in code comprehension if they are properly presented.
 Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
@@
 At runtime, concrete values are available and the developer can directly check and understand object structures and control flows.
-Understanding a concrete value, particulary for non-primitive values such as objects and functions, is not always straightforward.
+Understanding a concrete value, particularly for non-primitive values such as objects and functions, is not always straightforward.
 To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
@@
 our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
-values and functions in callstack.
+values and functions in the call-stack.
 

### 2011-04-06 papers/splash-wavefront2011/sigplanconf-template.tex
style correction.

@@
 Our function names serve to recall or summarize that source or documentation for the developer.
-Therefore we seek to name the source, the content between the curly braces known as the \textit{FunctionBody} in the standard\cite{ECMA}.
+Therefore we seek to name the source, the content between the curly braces known as the {\textit{FunctionBody}} in the standard\cite{ECMA}.
 
@@
 On the one hand we claim that the function object instance may be bound to properties in multiple objects and those property names are not helpful for naming.
-On the other hand we will shortly introduce an algorithm that uses a property name (in part) to name a \textit{FunctionBody}.
-Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a {\small\textit{Function}}  to an object property differs from all other bindings because it is located in text near the \textit{FunctionBody} and thus developers associate this first binding with the meaning of the {\small\textit{FunctionBody}}.
+On the other hand we will shortly introduce an algorithm that uses a property name (in part) to name a {\textit{FunctionBody}}.
+Ultimately we are relying on a subtle characteristic of JavaScript programming: the first binding of a {\textit{Function}}  to an object property differs from all other bindings because it is located in text near the {\textit{FunctionBody}} and thus developers associate this first binding with the meaning of the {\textit{FunctionBody}}.
 
@@
 
-We call our automated naming solution "Static Function Object Consumption", since it relies only a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by binding to an object property, variable reference, or function argument.
+We call our automated naming solution "Static Function Object Consumption", since it relies only on a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by binding to an object property, variable reference, or function argument.
 Static Function Object Consumption generalizes the built-in JavaScript naming and common, simple coding patterns like object property initializers and variable assignments typically recognized by developers as naming functions.

### 2011-04-06 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
progress on the algorithm description

@@
 Then we assemble a name using the expression-reduction rules outlined in section YY and the context naming rules in section ZZ.
-The result is a summary that contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanitory tokens.
+The result is a summary that contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
 It compactly explains the function object creation, consumption and assignment.
@@
 After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
-Eliding identifiers is important to avoid creating long, unweildy names.
+Eliding identifiers is important to avoid creating long, unwieldy names.
 
@@
   }
-\caption{Different cases of function object creation and usage in JavaScript.}
+\caption{Different cases of function object creation and usage in JavaScript.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
 \label{table:function-types} 
@@
 \subsection{Overview of the Function Object Consumption Algorithm}
+Our function naming algorithm parses the JavaScript and builds a name based on the parse tree.
+Each function body results in a list of identifers and expressions marked with the kind of parse node that contributed them (\ref{sec:nodewalk}).
+Some of the items on the list are dropped if their neighboring items already give better information for the name.
+Then the expressions are converted to pseudo-identifiers (\ref{sec:general-element-naming}).
+Finally the attributes are converted to augmenting symbols on the identifiers while  the list is collapsed to a name\ref{sec:concatenate}.
+
+\subsection{Full Function Object Consumption Name}
+\label{sec:nodewalk}
+The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
 The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
-For each function body look for the path of the function object from creation to consumption.
-We process the abstract syntax tree from the function definition node recursively back to the root node in the enclosed function.
+For each function body we look for the path of the function object from creation to consumption.
+We process the abstract syntax tree from the function body node back to the root node in the enclosed function.
 On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}.
-As we go upward in the tree, we keep identifiers and whether the object consumed is the same, part of, or contributed to the result object.
+As we go upward in the tree, we keep identifiers and whether the object consumed is the result object (rows 1-6), part of the result object (rows 7-8), or contribute to the result object (rows 9-11).
 Once the summary is ready we construct the identifier.
@@
 Otherwise, only the closest function call identifier will be used.
-Nodes which are not one of the type specfied in Table~\ref{table:function-types} are ignored.
+Nodes which are not one of the type specified in Table~\ref{table:function-types} are ignored.
 
@@
 The top script functions can not be anonymous and the functions defined by the constructor can be considered as a regular function body.
-Names which are specified with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifer in ~\ref{sec:general-element-naming}.
+
+\subsection{Culling Less Informative Items}
+Since ultimately our aim is an understandable name, we next process our list of identifiers to remove items likely to be uninformative.
+Of course this is a heuristic process and ultimately we expect it to be tuned with user testing or future insights.
+For now we remove XXX from our list because YYY.
 
@@
 \label{sec:general-element-naming}
+In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
+The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not neccessarily
+ a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT.
 
@@
 \subsection{Building a String from Arguments}
+WHAT?
 
-\subsection{Building a String from An Expression}
+\subsection{Conversion to an Name}
+At this stage of the algorithm we have a list of identifiers with attributes (which row contributed the identifier).
+Next we join the list items using special characters to signal the attributes.
+For identifers from rows 1-6 of Table~\ref{table:function-types} we put out the identifier followed by a WHAT.
+For rows 7 and 8 we put out the identifier followed by a slash (/), the traditional separator in a containment heirarchy.
+For rows 9-11 the identifier is followed by a left angle bracket (<) indicating 'contributes to'.
+
+The particular symbols we use may be refined with more experience in how developers respond to them.
+Our intution is that these extra symbols need to be visually compact because their purpose is to adjust the developers expectation for the identifier.
+For example, the function on line 9 of Fig.~\ref{fig:js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.
+
+\section{Special Cases}
+Given that our goals trade precision for rapid recogition, our names are not unique or perfectly tuned to every developer's need.
+We also leave some cases anonymous.
+We add  few special cases to our algorithm to patch over these issues.
+
+\subsection{Similar Function Names in a File}
+It is conceivable, that function bodies are named with the same names in a file.
+It can happen in different situations.
+One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser).
+For these cases we add a dollar sign and an index to the similar function names.
+For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
 
@@
 A namer function works like an assignment in the summary.
+MORE
 
@@
 
-\subsection{Similar Function Names in a File}
-It is conceivable, that function bodies are named with the same names in a file.
-It can happen in different situations.
-One of the common cases is the two different function bodies may assing to a property based on a condition (e.g., the browser).
-For these cases we add a dollar sign and an index to the similar function names.
-For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+\subsection{ {\texttt .displayName} }
+The ultimate fallback for function names is to allow the developer to specify them manually.
+For applicaiton developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.
 

### 2011-04-07 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
section 4 reorganized. tree walk algorithm pseudo code is added.

@@
 The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
-
 %The function name is necessary for referring and recalling the function's functionality, but only a small proportion (less than 7\%) of JavaScript functions are named.
@@
 \begin{figure}[htp]
-%{\small 
-%\begin{verbatim}
 
@@
 \lstset{emph={FOO,BAR},emphstyle=\textit}
-%\lstset{backgroundcolor=\color{yellow}}
 \lstdefinelanguage{myLang}
@@
 \end{lstlisting}
-%\end{verbatim}}
 \caption{An excerpt of a JavaScript code.}
@@
 % function object path in dom model is good candidate for the name but only for persistent objects ?
-
 %\subsubsection{Local vs. Global}
@@
 The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.
-
 %\subsubsection{Is it possible to automatically name all functions?}
-
 %\subsubsection{Other Challenges}%
@@
 By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree.
-For each function body, we walk up the tree looking for the constructs in table 2.
+For each function body, we walk up the tree recording identifiers or expressions explains the function object consumption.
+The result is, \textit{object consumption summary}, a list of collected data at every visited node in the tree.
+%Then, to refine the summary from temporary variable, we look for assignments from and to the variables appear in the summary.
+Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings.
+After the refinment step,
+Then, we rank collected identifiers and strings and elide less relevant data from the summary.
+At the end we construct a string from the consumption summary.
+The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
+It compactly explains the function object creation, consumption and assignment.
+For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.
+
+The name is built by the above process does not contain any information about enclosing scopes.
+We call it \textit{local name}.
+We get the function \textit{full name} by adding the enclosing function full name with a slash before the local name.
+
+%To name a expression, we walk up the tree looking for the constructs in table 2.
 As we describe in section XX, for every matching construct we record identifiers or expressions to use in constructing a name.
@@
 We analyze the source code and build a summary that explains the function object creation, consumption and assignment.
-This summary which only contains identifiers (i.e., variable and property names) and strings available in the source code gives us the ingeredients for function identifier construction.
-
+%This summary which only contains identifiers (i.e., variable and property names) and strings available in the source code gives us the ingeredients for function identifier construction.
  %We analyze the source code to obtain the alias(es) that used for the function object or  is assigned to.
@@
 In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.
-
  %  On the other hand, it is very likely that the function object is assigned to this name in a place very close to the place the function object is created.
@@
 The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
-We can explain the function object consumption after its creation in two steps: 1) the function object is called (case 9 in table 2).
-2) the result is assigned to {\small\texttt{main}} (case 6 in table 2).
+We can explain the function object consumption after its creation in two steps: 1) the function object is called.
+2) the result is assigned to {\small\texttt{main}}.
 This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
@@
 The function in line 10 is returned just after its creation.
-However, as the enclosing function is just called after its creation we can follow the function object flow in the enclosing scope and see that the function object is assigned to {\small\texttt{main}}.
-The summary of the function object consumption will be: 1) the function object is returned (case 10, table 2), 2) the function object is assigned to {\small\texttt{main}} (case 6 table 2).
+This function is located inside a closure function (i.e., a function which is called directly after its creation).
+This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the clousre call result ({\small\texttt{main}}).
+The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}.
 As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
-BUT I DON"T GET IT.
 
 The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
-Here 1) the function object is passed as an argument to function {\small\texttt{op}} (case 11), 2) The call result is assigned to {\small\texttt{result}} (case 6).
-If we simply put of identifiers in this summary together we get {\small\texttt{main/result<op()}}.
+Here 1) the function object is passed as an argument to function {\small\texttt{op}}, 2) The call result is assigned to {\small\texttt{result}}.
+If we simply put the identifiers in the summary together we get {\small\texttt{main/result<op()}}.
 The first part before slash  shows the context name (the enclosing function name) for this function.
 However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
-Therefore, as we explain in the next subsection, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
+Therefore, as we explain in 4.5, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
 After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
@@
 \centering
-\scalebox{0.8}{
+%\scalebox{0.8}{
 \renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
+\begin{tabular}{ | c | l | m{2.5cm} | l|}
   \hline
-   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
   \hline
+
    1 & 
-   & 
-   &  
-   & direct access.
-   & bar\textsuperscript{*}.foo = function()\{...\}\\
-   \cline{0-0}\cline{5-6}
+   & \raggedright property of a new object in an object literal.
+   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
+   \cline{0-0}\cline{3-4}
 
-   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
-   & 
-   & 
-   & \raggedright hashmap access by a string. 
-   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
+	 2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+	 & \raggedright 
+	   new array index in an array literal.
+   & [..., function()\{...\}, ...] \\ 
+   \cline{0-0}\cline{3-4}
 
    3 &
-   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
-   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
-   & \raggedright hashmap access by a variable name.
-   & bar\textsuperscript{*}[foo] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
+   & 
+     \raggedright passed as an argument to a function.
+   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
+   \cline{0-0}\cline{3-4}
 
    4 &
-   & 
-   & 
-   & \raggedright hashmap access by a JavaScript expression.
-   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   5 &
-   &
-   &
-   & \raggedright  array index.
-   & foo\textsuperscript{*}[0] = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   6 &
-   & 
-   & \multicolumn{2}{|l|}{
-      variable.}
-   & foo = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   7 &
-   &  
-   & \multicolumn{2}{|m{2.8cm}|}{
-     \raggedright property of a new object in an object literal.}
-   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
-   \cline{0-0}\cline{4-6}
-
-	 8 &
-	 & 
-	 & \multicolumn{2}{|m{2.8cm}|}{
-	   new array index in an array literal.} 
-   & [..., function()\{...\}, ...] \\ 
-   \cline{0-0}\cline{3-6}
-
-   9 &
-   & \multicolumn{3}{|m{3.8cm}|}{
-     \raggedright directly called.}
-   & function()\{...\}() \\
-   \cline{0-0}\cline{3-6}
-
-   10 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright returned from a function call.}
-   & \{... return function()\{...\}\} \\
-   \cline{0-0}\cline{3-6}
-
-   11 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright passed as an argument to a function.}
-   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
-   \hline
+   & \raggedright assigned to a variable or write pointer.
+   & foo\textsuperscript{*} = function()\{...\} \\
+   \cline{0-0}\cline{2-4}
 
   \end{tabular}
-  }
+%  }
 \caption{Different cases of function object creation and usage in JavaScript.
@@
 
-\subsection{Overview of the Function Object Consumption Algorithm}
-Our function naming algorithm parses the JavaScript and builds a name based on the parse tree.
+%\subsection{Full Function Object Consumption Name}
+\subsection{Expression Value Consumption Summary}
+\label{sec:nodewalk}
+The algorithm builds a consumption summary for an expression, starting from the expression node walking up in the absstract syntax tree.
+In the particular case when we start from an expression wich defines a function ( a function body or {\small\texttt{new Function()}}), it calculates the consumption summary for the function.
+The first node is an expression and returns a value.
+The algorithm ends when we reach a node which is an assignment or a statmement which does not return any value.
+When we move from a node to its parent, the value of the node expression can be the same, part of or different from its parent expression value.
+For every visited node we keep this information.
+
+\floatname{algorithm}{Procedure}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+
+\begin{algorithm}                      % enter the algorithm environment
+\caption{Compute Object Consumption Summary for Node $n$}          % give the algorithm a caption
+\label{alg1}                           % and a label for \ref{} commands later in the document
+\begin{algorithmic}                    % enter the algorithmic environment
+\REQUIRE Node $n$ in Abstract Syntax Tree
+\ENSURE Object Consumption Summary 
+\STATE $List$ $summary$ = $new$ $List$()
+
+\WHILE {$n.parent$ is an expression}  
+	\STATE $dataItem$ = $new$ $DataItem$()
+    \IF {$n$ value is the same as $n.parent$ value}
+    	 \STATE $dataItem.isTheSame$ = $true$
+    \ELSIF {$n$ value is a property of $n.parent$ value}
+    		\STATE $dataItem.isPartOf$ = $true$
+    \ELSE	
+	   		\STATE $dataItem.isContributedTo$ = $true$
+    \ENDIF
+    \IF {$n.parent$ is a function call and $n$ is an argument}
+   	    \STATE $dataItem.isFunctionCall$ = $true$
+   	    \STATE $dataItem.id$ = $idForFC(n.parent)$
+   	    \STATE $dataItem.hint$ = $hintForFC(n.parent)$
+   	\ELSIF {$n.parent$ is an object literal and $n$ is assigned to $foo$}
+   	    \STATE $dataItem.isObjLiteral$ = $true$
+   	    \STATE $dataItem.id$ = $foo$
+    \ENDIF     
+   \STATE $summary.add(dataItem)$
+   \STATE $n$ = $n.parent$
+\ENDWHILE
+
+  \IF {$n.parent$ is an assignment} 
+  	\STATE $dataItem$ = $new$ $DataItem$()
+		\STATE $dataItem.isAssignment$ = $true$
+    \STATE $dataItem.id$ = $idForAssignment(n.parent)$
+    \STATE $summary.add(dataItem)$
+  \ENDIF	
+  \RETURN $summary$
+\end{algorithmic}
+\end{algorithm}
+
+Once we move from a node to its parent, we keep the
+
+%The algorithm build a consumption summary for an expression which returns a value.
+A consumption summary is a list of collected information at every not in the tree traversal.
+At every node two items are stored.
+First the relation of the consumed value and the result value.
+The consumed expressions can be part of the result expression like first two cases in table 2.
+The result value might be different from the consumed value like case 3 in table 2.
+Morover we keep identifiers at every node is one of the constructs in table 2.
+
+%Our function naming algorithm parses the JavaScript and builds a name based on the parse tree.
 Each function body results in a list of identifers and expressions marked with the kind of parse node that contributed them (\ref{sec:nodewalk}).
@@
 
-\subsection{Full Function Object Consumption Name}
-\label{sec:nodewalk}
 The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
@@
 
+%\subsection{Variable Refinement}\subsubsection{Read Variable}\subsubsection{Write Variable}
+
+%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
+% more than one return
+
+%\subsection{Temporary Variables} %aliases for the same object
+
+\subsection{Expression Reductions}
+\subsubsection{to a Name}
+\label{sec:general-element-naming}
+In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
+The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not neccessarily
+ a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT. 
+\subsubsection{to a Hashmap Key}
+
+\subsubsection{Building a String from Arguments}
+WHAT?
+
 \subsection{Culling Less Informative Items}
@@
 For now we remove XXX from our list because YYY.
-
-\subsection{Reducing a JavaScript Expression to a Name}
-\label{sec:general-element-naming}
-In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
-The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not neccessarily
- a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT.
 
@@
 
-\subsection{Building a String from Arguments}
-WHAT?
+\subsection{Enclosed By a Closure Function}
+A closure function is called directly after its creation. Therefore a closure function is like a simple block and any static analysis like
+for buiilding object consumption summary and variable refinement can be continued outside a closure function. Every expression which its value
+is returned in the closure function is assigned to the expression that closure function call result is assigned to. Morover, in cases where the
+function call defines "this" (by apply()) or arguments these variables can be replaced in the function body.
 
@@
 
-\subsection{ {\texttt .displayName} }
-The ultimate fallback for function names is to allow the developer to specify them manually.
-For applicaiton developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.
-
-%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
-% more than one return
-
-\subsection{Temporary Variables} %aliases for the same object
-
 \subsection{Context Name}
@@
 
-\begin{figure}[htp]
-\begin{verbatim}
-(a)
- foo();
-(b)
- foo.bar();
-(c)
- foo.apply(bar, args);
-(d)
- foo.call();
-\end{verbatim}
-\caption{Different cases of function object creation.}
-\label{fig:functionCall}
-\end{figure}
-
 \section{evaluation}
 
-\subsection{Object Creation}
+\subsection{Developers' vs. Automated Names}
+
+\subsection{Compared to Firebug {\large \texttt{guessFunctionName()}}}
+Firebug uses a utility function called {\small \texttt{guessFunctionName()}} to name nameless functions.
+This algorithm used in the function searches lines around the line the function definition line for specific patterns by regular expressions. The
+  first string matches one of the patterns becomes the name of the function. We compared the results of our algorithm to Firebug's in table~\ref{firebug}.
+
+The first column shows, how many functions get similar names by both algorithm. In average, for 60\% of functions both algorithms produce the same names.
+Firebug is not able to name about 15\% of functions. In 35\% of functions the results are different. In most cases, the proposed name by Firebug is the name of another function and is wrong.
+
+\begin{table}
+\centering
+\scalebox{0.9}{
+  \begin{tabular}{ | l | l | l | l | l |}
+  \hline
+   Project & Similar & Different & UnNamed \\ 
+  \hline 
+   Closure & 8524(1\%) & 9195 & 516(2\%) \\ 
+  \hline 
+   DoJo & 12180(1\%) & 9195 & 5780(2\%) \\ 
+  \hline 
+   ExtJS & 100(1\%) & 9195 & 208(2\%) \\ 
+  \hline 
+   Firebug & 2901(1\%) & 9195 & 494(0\%) \\ 
+  \hline 
+   jQuery & 283(1\%) & 9195 & 117(0\%) \\ 
+  \hline 
+   MochiKit &  1568(1\%) & 9195 & 234(2\%) \\ 
+  \hline 
+   MooTools & 440(1\%) & 9195 & 128(2\%) \\ 
+  \hline 
+   Prototype & 292(1\%) & 9195 & 326(0\%) \\ 
+  \hline 
+   Scriptaculous &  100(1\%) & 9195 & 397(2\%) \\ 
+  \hline 
+   YUI &  11248(1\%) & 9195 & 3702(2\%) \\ 
+  \hline 
+   All & 100(1\%) & 9195 & 208(2\%) \\ 
+  \hline 
+  \end{tabular}
+  }
+ \label{firebug} 
+\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
+\end{table}
+
+\subsection{Manual Check}
+%Firebug, JQuery,
+
+%JQuery
+% core.js
+
+%namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
+%commonjs requriejs, ...
+%the function name not very long like google chrome  xxxx.yyy.zzz
+
+\section{Disucussion}
+
+\subsection{ {\texttt .displayName} }
+The ultimate fallback for function names is to allow the developer to specify them manually.
+For applicaiton developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.
+
+\subsection{Limitations}
+%some long names
+%"this" in names
+
+% open problems: naming scripts loaded and evaluated by eval,
+\section{Related Work}
+% Andrew Ko paper about errors by names
+% ecoop 2009 paper
+% typing system papers
+
+%JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
+JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
+As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
+For example, the value of a variable can be a primitive value, an object with any structure or even a function.
+One call-site may invoke different function bodies with various number of arities that none of them can be understood from the code.
+Therefore, the lack of descriptive data in JavaScript code is the most fundamental issue in enhancing JavaScript tool support.
+
+Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
+It can save developers' time, prevent bugs and improve the program quality.
+However, many errors can not be recognized without a strong typing system.
+To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
+These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
+The discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
+Moreover, the inferred data can help in code comprehension if they are properly presented.
+Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
+This leads us to another hidden issue for improving JavaScript development tools; Due to highly dynamism in JavaScript many elements are remained nameless.
+Therefore there is no common language between the tool and developer for referring to elements.
+
+%Developers usually understand JavaScript code by examining the running program in debuggers.
+At runtime, concrete values are available and the developer can directly check and understand object structures and control flows.
+Understanding a concrete value, particularly for non-primitive values such as objects and functions, is not always straightforward.
+To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
+For example, in the case of user-defined objects, the name of object's constructor in the object summary can be very helpful.
+It works like a class name in class-based languages and suggests the object structure.
+
+\section{Conclusion}
+We highlighted the problem of anonymous functions in JavaScript. We studied 10 famous JavaScript projects source code. From
+our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
+values and functions in the call-stack.
+
+\appendix
+\section{JavaScript Projects Analyzed for Function Names}
+\begin{description}
+\item[Closure] Google Web Library, ...
+\item[Dojo] JavaScript Toolkit
+\item[ExtJS] JavaScript Framework
+\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
+\item[jQuery]
+\item[MochiKit]
+\item[MooTools]
+\item[Prototype]
+\item[Scriptaculous]
+\item[YUI]
+\end{description}
+
+%\acks
+
+%Acknowledgments, if needed.
+
+% We recommend abbrvnat bibliography style.
+
+%\bibliographystyle{abbrvnat}
+
+% The bibliography should be embedded for final submission.
+
+%\begin{thebibliography}{10}
+
+\begin{thebibliography}{}
+\softraggedright
+
+%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
+%P. Q. Smith, and X. Y. Jones. ...reference text...
+
+\bibitem{Anderson}
+C. Anderson, P. Giannini, and S. Drossopoulou. \newblock Towards Type Inference for JavaScript.
+\newblock In \emph{Proceedings of the 19th European conference on Object-Oriented Programming(ECOOP)},
+July, 2005.
+
+\bibitem{Anderson2}
+C. Anderson and P. Giannini. \newblock Type checking for javascript.
+\newblock \emph{Electr. Notes Theor. Comput. Sci.}, 138(2), 2005.
+
+\bibitem{CJS}
+Common JS.
+\newblock http://www.commonjs.org/
+
+\bibitem{DisplayName}
+Add prettyName/displayName support to Profiler output and Stacks.
+\newblock \emph{Firebug Bug Repository},
+\newblock http://code.google.com/p/fbug/issues/detail?id=1811
+
+\bibitem{ECMA}
+ECMA International.
+\newblock \emph{ECMA-262: ECMAScript Language Specification},
+ECMA (European Association for Standardizing Information
+and Communication Systems), Geneva, Switzerland, third edition,
+December 1999.
+
+\bibitem{FAO}
+Firefox Add-ons.
+\newblock https://addons.mozilla.org/en-US/developers/docs/gett ing-started.
+
+\bibitem{GCE}
+Google Chrome Extensions.
+\newblock http://code.google.com/chrome/extensions.
+
+\bibitem{Heidegger}
+P. Heidegger and P. Thiemann.\newblock Recency types for dynamically-typed, object-based languages.
+\newblock In \emph{Proceedings of Foundations of Object Oriented Languages (FOOL)},
+2009.
+
+\bibitem{Ingalls}
+D. Ingalls, K. Palacz, S. Uhler and A. Taivalsaari.\newblock The lively kernel a self-supporting system on
+a web page.
+\newblock In \emph{Self-Sustaining Systems},
+2008.
+
+\bibitem{JSOffice}
+JScript development in Microsoft Office 11.
+\newblock http://msdn.microsoft.com/ en-us/library/aa202668(office.11).aspx
+
+\bibitem{JSOffice2}
+JavaScript development in OpenOffice.
+\newblock http://framework.openoffice.org/ scripting/release-0.2/javascript-devguide.html
+
+\bibitem{Richards}
+G. Richards, S. Lebresne, B. Burg and J. Vitek.\newblock An analysis of the dynamic behavior of JavaScript programs.
+\newblock In \emph{Proceedings of the 2010 ACM SIGPLAN conference on Programming language design and implementation(PLDI)},
+June, 2010.
+
+\bibitem{SSJSR}
+Server-Side JavaScript Reference v1.2.
+\newblock http://research.nihonsoft.org/ javascript/ServerReferenceJS12.
+
+\bibitem{Thiemann}
+P. Thiemann.\newblock Towards a type system for analyzing JavaScript programs.
+\newblock In \emph{Proceedings of European Symposium on Programming (ESOP)},
+2005.
+
+\bibitem{Zaytsev}
+J. Zaytsev.\newblock Named function expressions demystified.
+\newblock http://kangax.github.com/nfe,
+June, 2010.
+
+\end{thebibliography}
+
+\section{To Be Removed}
 
@@
 
-\subsection{Developers' vs. Automated Names}
-
-\subsection{Compared to Firebug {\large \texttt{guessFunctionName()}}}
-Firebug uses a utility function called {\small \texttt{guessFunctionName()}} to name nameless functions.
-This algorithm used in the function searches lines around the line the function definition line for specific patterns by regular expressions. The
-  first string matches one of the patterns becomes the name of the function. We compared the results of our algorithm to Firebug's in table~\ref{firebug}.
-
-The first column shows, how many functions get similar names by both algorithm. In average, for 60\% of functions both algorithms produce the same names.
-Firebug is not able to name about 15\% of functions. In 35\% of functions the results are different. In most cases, the proposed name by Firebug is the name of another function and is wrong.
-
-\begin{table}
-\centering
-\scalebox{0.9}{
-  \begin{tabular}{ | l | l | l | l | l |}
-  \hline
-   Project & Similar & Different & UnNamed \\ 
-  \hline 
-   Closure & 8524(1\%) & 9195 & 516(2\%) \\ 
-  \hline 
-   DoJo & 12180(1\%) & 9195 & 5780(2\%) \\ 
-  \hline 
-   ExtJS & 100(1\%) & 9195 & 208(2\%) \\ 
-  \hline 
-   Firebug & 2901(1\%) & 9195 & 494(0\%) \\ 
-  \hline 
-   jQuery & 283(1\%) & 9195 & 117(0\%) \\ 
-  \hline 
-   MochiKit &  1568(1\%) & 9195 & 234(2\%) \\ 
-  \hline 
-   MooTools & 440(1\%) & 9195 & 128(2\%) \\ 
-  \hline 
-   Prototype & 292(1\%) & 9195 & 326(0\%) \\ 
-  \hline 
-   Scriptaculous &  100(1\%) & 9195 & 397(2\%) \\ 
-  \hline 
-   YUI &  11248(1\%) & 9195 & 3702(2\%) \\ 
-  \hline 
-   All & 100(1\%) & 9195 & 208(2\%) \\ 
-  \hline 
-  \end{tabular}
-  }
- \label{firebug} 
-\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
-\end{table}
-
-\subsection{Manual Check}
-%Firebug, JQuery,
-
-%JQuery
-% core.js
-
-%namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
-%commonjs requriejs, ...
-%the function name not very long like google chrome  xxxx.yyy.zzz
-\subsection{Limitations}
-%some long names
-%"this" in names
-
-% open problems: naming scripts loaded and evaluated by eval,
-\section{Related Work}
-% ecoop 2009 paper
-% typing system papers
-
-%JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
-JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
-As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
-For example, the value of a variable can be a primitive value, an object with any structure or even a function.
-One call-site may invoke different function bodies with various number of arities that none of them can be understood from the code.
-Therefore, the lack of descriptive data in JavaScript code is the most fundamental issue in enhancing JavaScript tool support.
-
-Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
-It can save developers' time, prevent bugs and improve the program quality.
-However, many errors can not be recognized without a strong typing system.
-To attack this issue a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
-These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
-The discovered facts about variable types are not only useful for catching errors but to provide modern editing features such as auto-complete and refactoring in development environments.
-Moreover, the inferred data can help in code comprehension if they are properly presented.
-Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
-This leads us to another hidden issue for improving JavaScript development tools; Due to highly dynamism in JavaScript many elements are remained nameless.
-Therefore there is no common language between the tool and developer for referring to elements.
-
-%Developers usually understand JavaScript code by examining the running program in debuggers.
-At runtime, concrete values are available and the developer can directly check and understand object structures and control flows.
-Understanding a concrete value, particularly for non-primitive values such as objects and functions, is not always straightforward.
-To facilitate understanding these complex values in the first place, debuggers show a summary of these objects.
-For example, in the case of user-defined objects, the name of object's constructor in the object summary can be very helpful.
-It works like a class name in class-based languages and suggests the object structure.
-\section{Conclusion}
-We highlighted the problem of nameless functions in JavaScript. We studied 10 famous JavaScript projects source code. From
-our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
-values and functions in the call-stack.
-
-\appendix
-\section{JavaScript Projects Analyzed for Function Names}
-\begin{description}
-\item[Closure] Google Web Library, ...
-\item[Dojo] JavaScript Toolkit
-\item[ExtJS] JavaScript Framework
-\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
-\item[jQuery]
-\item[MochiKit]
-\item[MooTools]
-\item[Prototype]
-\item[Scriptaculous]
-\item[YUI]
-\end{description}
-
-%\acks
-
-%Acknowledgments, if needed.
-
-% We recommend abbrvnat bibliography style.
-
-%\bibliographystyle{abbrvnat}
-
-% The bibliography should be embedded for final submission.
-
-%\begin{thebibliography}{10}
-
-\begin{thebibliography}{}
-\softraggedright
-
-%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-%P. Q. Smith, and X. Y. Jones. ...reference text...
-
-\bibitem{Anderson}
-C. Anderson, P. Giannini, and S. Drossopoulou. \newblock Towards Type Inference for JavaScript.
-\newblock In \emph{Proceedings of the 19th European conference on Object-Oriented Programming(ECOOP)},
-July, 2005.
-
-\bibitem{Anderson2}
-C. Anderson and P. Giannini. \newblock Type checking for javascript.
-\newblock \emph{Electr. Notes Theor. Comput. Sci.}, 138(2), 2005.
-
-\bibitem{CJS}
-Common JS.
-\newblock http://www.commonjs.org/
-
-\bibitem{DisplayName}
-Add prettyName/displayName support to Profiler output and Stacks.
-\newblock \emph{Firebug Bug Repository},
-\newblock http://code.google.com/p/fbug/issues/detail?id=1811
-
-\bibitem{ECMA}
-ECMA International.
-\newblock \emph{ECMA-262: ECMAScript Language Specification},
-ECMA (European Association for Standardizing Information
-and Communication Systems), Geneva, Switzerland, third edition,
-December 1999.
-
-\bibitem{FAO}
-Firefox Add-ons.
-\newblock https://addons.mozilla.org/en-US/developers/docs/gett ing-started.
-
-\bibitem{GCE}
-Google Chrome Extensions.
-\newblock http://code.google.com/chrome/extensions.
-
-\bibitem{Heidegger}
-P. Heidegger and P. Thiemann.\newblock Recency types for dynamically-typed, object-based languages.
-\newblock In \emph{Proceedings of Foundations of Object Oriented Languages (FOOL)},
-2009.
-
-\bibitem{Ingalls}
-D. Ingalls, K. Palacz, S. Uhler and A. Taivalsaari.\newblock The lively kernel a self-supporting system on
-a web page.
-\newblock In \emph{Self-Sustaining Systems},
-2008.
-
-\bibitem{JSOffice}
-JScript development in Microsoft Office 11.
-\newblock http://msdn.microsoft.com/ en-us/library/aa202668(office.11).aspx
-
-\bibitem{JSOffice2}
-JavaScript development in OpenOffice.
-\newblock http://framework.openoffice.org/ scripting/release-0.2/javascript-devguide.html
-
-\bibitem{Richards}
-G. Richards, S. Lebresne, B. Burg and J. Vitek.\newblock An analysis of the dynamic behavior of JavaScript programs.
-\newblock In \emph{Proceedings of the 2010 ACM SIGPLAN conference on Programming language design and implementation(PLDI)},
-June, 2010.
-
-\bibitem{SSJSR}
-Server-Side JavaScript Reference v1.2.
-\newblock http://research.nihonsoft.org/ javascript/ServerReferenceJS12.
-
-\bibitem{Thiemann}
-P. Thiemann.\newblock Towards a type system for analyzing JavaScript programs.
-\newblock In \emph{Proceedings of European Symposium on Programming (ESOP)},
-2005.
-
-\bibitem{Zaytsev}
-J. Zaytsev.\newblock Named function expressions demystified.
-\newblock http://kangax.github.com/nfe,
-June, 2010.
-
-\end{thebibliography}
-
 \end{document}

### 2011-04-07 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
the function creation/consumption table is removed.

@@
 
-\begin{table}
-\centering
-%\scalebox{0.8}{
-\renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | m{2.5cm} | l|}
-  \hline
-   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
-  \hline
-
-   1 & 
-   & \raggedright property of a new object in an object literal.
-   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
-   \cline{0-0}\cline{3-4}
-
-	 2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
-	 & \raggedright 
-	   new array index in an array literal.
-   & [..., function()\{...\}, ...] \\ 
-   \cline{0-0}\cline{3-4}
-
-   3 &
-   & 
-     \raggedright passed as an argument to a function.
-   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
-   \cline{0-0}\cline{3-4}
-
-   4 &
-   & \raggedright assigned to a variable or write pointer.
-   & foo\textsuperscript{*} = function()\{...\} \\
-   \cline{0-0}\cline{2-4}
-
-  \end{tabular}
-%  }
-\caption{Different cases of function object creation and usage in JavaScript.
-Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
-\label{table:function-types} 
-\end{table}
-
 %\subsection{Full Function Object Consumption Name}
-\subsection{Expression Value Consumption Summary}
+\subsection{Consumption Summary Algorithm}
 \label{sec:nodewalk}
@@
 
-\floatname{algorithm}{Procedure}
+%\floatname{algorithm}{Procedure}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}

### 2011-04-07 papers/splash-wavefront2011/sigplanconf-template.tex
4.2 is complete.

@@
 
+%\subsection{Full Function Object Consumption Name}
+\subsection{Consumption Summary Algorithm}
+\label{sec:nodewalk}
+
+The algrithm builds a consumption summary for an expression which returns a value.
+It starts from the the expression node in the abstract syntax tree produced from parsing the source code and walks up  collecting data.
+In the particular case when we start from an expression wich defines a function ( a function body or {\small\texttt{new Function()}} ), it computess the consumption summary for the function.
+The first node is an expression and returns a value.
+At every step, it stores how the value of the current node is related to the value of the parent node.
+If the parent expression is an array or object literal then the curerent node value is \textit{partOf} the parent node value.
+Otherwise the node expression value is \textit{theSame} as or different \textit{contributesTo} parent value.
+
+%~\ref{alg1})
+
 \begin{table}
 \centering
-\scalebox{0.8}{
+%\scalebox{0.8}{
 \renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
+\begin{tabular}{ | c | l | m{2.5cm} | l|}
   \hline
-   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
   \hline
+
    1 & 
+   & \raggedright an object literal.
+   & \{ ..., foo: expr \}\\ 
+   \cline{0-0}\cline{3-4}
+
+   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node is\end{rotate}} 
    & 
-   &  
-   & direct access.
-   & bar\textsuperscript{*}.foo = function()\{...\}\\
-   \cline{0-0}\cline{5-6}
-
-   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
-   & 
-   & 
-   & \raggedright hashmap access by a string. 
-   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
+     \raggedright a function call.
+   & foo\textsuperscript{*}(..., expr, ...) \\
+   \cline{0-0}\cline{3-4}
 
    3 &
-   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
-   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
-   & \raggedright hashmap access by a variable name.
-   & bar\textsuperscript{*}[foo] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   4 &
-   & 
-   & 
-   & \raggedright hashmap access by a JavaScript expression.
-   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   5 &
-   &
-   &
-   & \raggedright  array index.
-   & foo\textsuperscript{*}[0] = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   6 &
-   & 
-   & \multicolumn{2}{|l|}{
-      variable.}
-   & foo = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   7 &
-   &  
-   & \multicolumn{2}{|m{2.8cm}|}{
-     \raggedright property of a new object in an object literal.}
-   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
-   \cline{0-0}\cline{4-6}
-
-	 8 &
-	 & 
-	 & \multicolumn{2}{|m{2.8cm}|}{
-	   new array index in an array literal.} 
-   & [..., function()\{...\}, ...] \\ 
-   \cline{0-0}\cline{3-6}
-
-   9 &
-   & \multicolumn{3}{|m{3.8cm}|}{
-     \raggedright directly called.}
-   & function()\{...\}() \\
-   \cline{0-0}\cline{3-6}
-
-   10 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright returned from a function call.}
-   & \{... return function()\{...\}\} \\
-   \cline{0-0}\cline{3-6}
-
-   11 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright passed as an argument to a function.}
-   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
-   \hline
+   & \raggedright an assignment.
+   & foo\textsuperscript{*} = expr\\
+   \cline{0-0}\cline{2-4}
 
   \end{tabular}
-  }
-\caption{Different cases of function object creation and usage in JavaScript.}
-\label{table:function-types} 
+%  }
+\caption{Nodes produce identifiers in the function object consumption summary.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
+\label{table:node-types} 
 \end{table}
 
-\subsection{Overview of the Function Object Consumption Algorithm}
-The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
-For each function body look for the path of the function object from creation to consumption.
-We process the abstract syntax tree from the function definition node recursively back to the root node in the enclosed function.
+Morover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
+If the parent node is an object literal, then the node value is assigned to a named property like {\small\texttt{foo}}.
+In this case we keep {\small\texttt{foo}} as the \textit{id}.
+If the parent node is a function call that the expression value is passed as one of its argument, we reduce the function expression to a name and we keep that as \textit{id}.
+In the case of function call, another value, \textit{hint}, will also be computed and saved.
+In the case where the parent node is an assignment we reduce the left side expression to a name and we keep that as \textit{id}.
+The algorithm ends when we reach a node which an assignment or a statmement which does not return any value (i.e., the node is not an expression).
+
+%\floatname{algorithm}{Procedure}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+
+\begin{algorithm}                      % enter the algorithm environment
+\caption{Compute Object Consumption Summary for Node $n$}          % give the algorithm a caption
+\label{alg1}                           % and a label for \ref{} commands later in the document
+\begin{algorithmic}                    % enter the algorithmic environment
+\REQUIRE Node $n$ in Abstract Syntax Tree
+\ENSURE Object Consumption Summary 
+\STATE $List$ $summary$ = $new$ $List$()
+
+\WHILE {$n.parent$ is an expression}  
+	\STATE $dataItem$ = $new$ $DataItem$()
+    \IF {$n$ value is the same as $n.parent$ value}
+    	 \STATE $dataItem.isTheSame$ = $true$
+    \ELSIF {$n$ value is a property of $n.parent$ value}
+    		\STATE $dataItem.isPartOf$ = $true$
+    \ELSE	
+	   		\STATE $dataItem.isContributesTo$ = $true$
+    \ENDIF
+    \IF {$n.parent$ is a function call and $n$ is an argument}
+   	    \STATE $dataItem.isFunctionCall$ = $true$
+   	    \STATE $dataItem.id$ = $idForFC(n.parent)$
+   	    \STATE $dataItem.hint$ = $hintForFC(n.parent)$
+   	\ELSIF {$n.parent$ is an object literal and $n$ is assigned to $foo$}
+   	    \STATE $dataItem.isObjLiteral$ = $true$
+   	    \STATE $dataItem.id$ = $foo$
+    \ENDIF     
+   \STATE $summary.add(dataItem)$
+   \STATE $n$ = $n.parent$
+\ENDWHILE
+
+  \IF {$n.parent$ is an assignment} 
+  	\STATE $dataItem$ = $new$ $DataItem$()
+		\STATE $dataItem.isAssignment$ = $true$
+    \STATE $dataItem.id$ = $idForAssignment(n.parent)$
+    \STATE $summary.add(dataItem)$
+  \ENDIF	
+  \RETURN $summary$
+\end{algorithmic}
+\end{algorithm}
+
+%The algorithm build a consumption summary for an expression which returns a value.
+A consumption summary is a list of collected information at every not in the tree traversal.
+At every node two items are stored.
+First the relation of the consumed value and the result value.
+The consumed expressions can be part of the result expression like first two cases in table 2.
+The result value might be different from the consumed value like case 3 in table 2.
+Morover we keep identifiers at every node is one of the constructs in table 2.
+
+%Our function naming algorithm parses the JavaScript and builds a name based on the parse tree.
+Each function body results in a list of identifers and expressions marked with the kind of parse node that contributed them (\ref{sec:nodewalk}).
+Some of the items on the list are dropped if their neighboring items already give better information for the name.
+Then the expressions are converted to pseudo-identifiers (\ref{sec:general-element-naming}).
+Finally the attributes are converted to augmenting symbols on the identifiers while  the list is collapsed to a name\ref{sec:concatenate}.
+
+%The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
+%The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
+For each function body we look for the path of the function object from creation to consumption.
+We process the abstract syntax tree from the function body node back to the root node in the enclosed function.
 On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}.
-As we go upward in the tree, we keep identifiers and whether the object consumed is the same, part of, or contributed to the result object.
+As we go upward in the tree, we keep identifiers and whether the object consumed is the result object (rows 1-6), part of the result object (rows 7-8), or contribute to the result object (rows 9-11).
 Once the summary is ready we construct the identifier.
@@
 
-Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table.
+%Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table.
 The top script functions can not be anonymous and the functions defined by the constructor can be considered as a regular function body.
-Names which are specified with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.
 
-\subsection{Reducing a JavaScript Expression to a Name}
+%\subsection{Variable Refinement}\subsubsection{Read Variable}\subsubsection{Write Variable}
+
+%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
+% more than one return
+
+%\subsection{Temporary Variables} %aliases for the same object
+
+\subsection{Expression Reductions}
 \label{sec:general-element-naming}
+
+\subsubsection{to a Name}
+In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
+The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not neccessarily
+ a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT. 
+\subsubsection{to a Hashmap Key}
+
+\subsubsection{Building a String from Arguments}
+WHAT?
+
+\subsection{Culling Less Informative Items}
+Since ultimately our aim is an understandable name, we next process our list of identifiers to remove items likely to be uninformative.
+Of course this is a heuristic process and ultimately we expect it to be tuned with user testing or future insights.
+For now we remove XXX from our list because YYY.
 
@@
 
-\subsection{Building a String from Arguments}
+\subsection{Enclosed By a Closure Function}
+A closure function is called directly after its creation. Therefore a closure function is like a simple block and any static analysis like
+for buiilding object consumption summary and variable refinement can be continued outside a closure function. Every expression which its value
+is returned in the closure function is assigned to the expression that closure function call result is assigned to. Morover, in cases where the
+function call defines "this" (by apply()) or arguments these variables can be replaced in the function body.
 
-\subsection{Building a String from An Expression}
+\subsection{Conversion to an Name}
+At this stage of the algorithm we have a list of identifiers with attributes (which row contributed the identifier).
+Next we join the list items using special characters to signal the attributes.
+For identifers from rows 1-6 of Table~\ref{table:function-types} we put out the identifier followed by a WHAT.
+For rows 7 and 8 we put out the identifier followed by a slash (/), the traditional separator in a containment heirarchy.
+For rows 9-11 the identifier is followed by a left angle bracket (<) indicating 'contributes to'.
 
-\subsection{Namer Functions}
-Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
-These functions usually receive a string as the class name or function name.
-The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
-A namer function works like an assignment in the summary.
+The particular symbols we use may be refined with more experience in how developers respond to them.
+Our intution is that these extra symbols need to be visually compact because their purpose is to adjust the developers expectation for the identifier.
+For example, the function on line 9 of Fig.~\ref{fig:js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.
 
-% to register a function with a name
-% to wrap the function
-% as a callback
+\section{Special Cases}
+Given that our goals trade precision for rapid recogition, our names are not unique or perfectly tuned to every developer's need.
+We also leave some cases anonymous.
+We add  few special cases to our algorithm to patch over these issues.
 
@@
 
-%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
-% more than one return
+\subsection{Namer Functions}
+Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+These functions usually receive a string as the class name or function name.
+The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
+A namer function works like an assignment in the summary.
+MORE
 
-\subsection{Temporary Variables} %aliases for the same object
+% to register a function with a name
+% to wrap the function
+% as a callback
 

### 2011-04-07 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
to make sure all changes are applied.

@@
 \label{sec:nodewalk}
-The algorithm builds a consumption summary for an expression, starting from the expression node walking up in the absstract syntax tree.
-In the particular case when we start from an expression wich defines a function ( a function body or {\small\texttt{new Function()}}), it calculates the consumption summary for the function.
+
+The algrithm builds a consumption summary for an expression which returns a value.
+It starts from the the expression node in the abstract syntax tree produced from parsing the source code and walks up  collecting data.
+In the particular case when we start from an expression wich defines a function ( a function body or {\small\texttt{new Function()}} ), it computess the consumption summary for the function.
 The first node is an expression and returns a value.
-The algorithm ends when we reach a node which is an assignment or a statmement which does not return any value.
-When we move from a node to its parent, the value of the node expression can be the same, part of or different from its parent expression value.
-For every visited node we keep this information.
+At every step, it stores how the value of the current node is related to the value of the parent node.
+If the parent expression is an array or object literal then the curerent node value is \textit{partOf} the parent node value.
+Otherwise the node expression value is \textit{theSame} as or different \textit{contributesTo} parent value.
+
+%~\ref{alg1})
+
+\begin{table}
+\centering
+%\scalebox{0.8}{
+\renewcommand\arraystretch{2.0}
+\begin{tabular}{ | c | l | m{2.5cm} | l|}
+  \hline
+   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+  \hline
+
+   1 & 
+   & \raggedright an object literal.
+   & \{ ..., foo: expr \}\\ 
+   \cline{0-0}\cline{3-4}
+
+   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node is\end{rotate}} 
+   & 
+     \raggedright a function call.
+   & foo\textsuperscript{*}(..., expr, ...) \\
+   \cline{0-0}\cline{3-4}
+
+   3 &
+   & \raggedright an assignment.
+   & foo\textsuperscript{*} = expr\\
+   \cline{0-0}\cline{2-4}
+
+  \end{tabular}
+%  }
+\caption{Nodes produce identifiers in the function object consumption summary.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
+\label{table:node-types} 
+\end{table}
 
@@
     \ELSE	
-	   		\STATE $dataItem.isContributedTo$ = $true$
+	   		\STATE $dataItem.isContributesTo$ = $true$
     \ENDIF
@@
 
-Once we move from a node to its parent, we keep the
+Morover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
+If the parent node is an object literal, then the node value is assigned to a named property like {\small\texttt{foo}}.
+In this case we keep {\small\texttt{foo}} as the \textit{id}.
+If the parent node is a function call that the expression value is passed as one of its argument, we reduce the function expression to a name and we keep that as \textit{id}.
+In the case of function call, another value, \textit{hint}, will also be computed from other arguments and stored.
+In the case where the parent node is an assignment we reduce the left side expression to a name and we keep that as \textit{id}.
+The algorithm ends when we reach a node which is an assignment or a statmement which does not return any value (i.e., the node is not an expression).
 
@@
 
-The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
-The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
+%The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
+%The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
 For each function body we look for the path of the function object from creation to consumption.
@@
 
-Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table.
+%Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table.
 The top script functions can not be anonymous and the functions defined by the constructor can be considered as a regular function body.
@@
 \subsection{Expression Reductions}
+\label{sec:general-element-naming}
+
 \subsubsection{to a Name}
-\label{sec:general-element-naming}
 In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
@@
 
+\begin{table}
+\centering
+\scalebox{0.8}{
+\renewcommand\arraystretch{2.0}
+\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
+  \hline
+   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+  \hline 
+   1 &
+   & 
+   &  
+   & direct access.
+   & bar\textsuperscript{*}.foo = function()\{...\}\\
+   \cline{0-0}\cline{5-6}
+
+   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+   & 
+   & 
+   & \raggedright hashmap access by a string. 
+   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   3 &
+   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
+   & \raggedright hashmap access by a variable name.
+   & bar\textsuperscript{*}[foo] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   4 &
+   & 
+   & 
+   & \raggedright hashmap access by a JavaScript expression.
+   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   5 &
+   &
+   &
+   & \raggedright  array index.
+   & foo\textsuperscript{*}[0] = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   6 &
+   & 
+   & \multicolumn{2}{|l|}{
+      variable.}
+   & foo = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   7 &
+   &  
+   & \multicolumn{2}{|m{2.8cm}|}{
+     \raggedright property of a new object in an object literal.}
+   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
+   \cline{0-0}\cline{4-6}
+
+	 8 &
+	 & 
+	 & \multicolumn{2}{|m{2.8cm}|}{
+	   new array index in an array literal.} 
+   & [..., function()\{...\}, ...] \\ 
+   \cline{0-0}\cline{3-6}
+
+   9 &
+   & \multicolumn{3}{|m{3.8cm}|}{
+     \raggedright directly called.}
+   & function()\{...\}() \\
+   \cline{0-0}\cline{3-6}
+
+   10 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright returned from a function call.}
+   & \{... return function()\{...\}\} \\
+   \cline{0-0}\cline{3-6}
+
+   11 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright passed as an argument to a function.}
+   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
+   \hline
+
+  \end{tabular}
+  }
+\caption{Different cases of function object creation and usage in JavaScript.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
+\label{table:function-types} 
+\end{table}
+
 \begin{table*}

### 2011-04-07 papers/splash-wavefront2011/sigplanconf-template.tex
minor edits near the front

@@
 One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.
+
 All of these tools need to express program artifacts in a compact way the developer can understand.
@@
 
-In this paper, we analyze function creation and consumption in ten large, well-known projects.
-We show that within these projects less than 7\% of the function objects are named.
+In this paper, we analyze ten large, well-known projects. We show that within these projects less than 7\% of the function bodies are named. 
+We analyze the syntactic constructs that function bodies appear in and rationalize how developers think about the bodies in relation to the structure of the code.
 We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
@@
 They can be assigned to any variable or object property, or passed as an argument to a function.
-Consequently JavaScript programmers can use this constructs to organize their thinking about the program, without the use of function names.
+Consequently JavaScript programmers can use these other constructs to organize their thinking about the program, without the use of function names.
 
@@
 To get empirical evidence we analyzed the source code of ten well-known JavaScript projects.
-For every project, the total number of functions and the number of functions with an identifier are collected (Table~\ref{js-functions}).
-The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent.
-Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function).
+For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}.
+The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent.
 Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
+Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}; these cases would only make the ratio even smaller.
 Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
@@
 \subsection{Missed Constructor Name in Object Summary}
-JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new Constructor()}}).
+JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call).
 A constructor is a regular JavaScript function.
@@
 The role of constructor is to initialize the empty object.
-Although the structure of object imposed by the constructor, unlike class-based object-oriented languages, may not remain intact during the object's lifetime \cite{Richards}, the constructor can still be used to classify the object.
+Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards}, the constructor can still be useful in classify the object.
 Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.
 
-Figure~\ref{js-code} demonstrates an excerpt of a JavaScript code.
+Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue.
 We set a breakpoint on line 13 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
@@
 
-\subsection{Anonymous Function Names in Callstack View}
-To illustrate the second issue, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
+\subsection{Anonymous Function Names in Call-stack View}
+The second problem is the call-stack.
+To illustrate this, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
 Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug.
@@
 
-Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
+%Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
 In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
@@
 \section{Automated Function Naming}
-The anonymous functions problem is discussed in several articles and forums on the web \cite{DisplayName, Zaytsev}.
+The anonymous functions problem is discussed in several articles and forums on the Web \cite{DisplayName, Zaytsev}.
 Different solutions have been proposed and discussed by practitioners.
@@
 For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation.
-Although these solutions may help, they cause developers extra work, the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.
+Although these solutions may help, they cause developers extra work, the displayName value can become out of sync with the meaning of the code over time,  the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.
 
@@
 Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings.
-After the refinment step,
+After the refinement step,
 Then, we rank collected identifiers and strings and elide less relevant data from the summary.
@@
 This function is located inside a closure function (i.e., a function which is called directly after its creation).
-This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the clousre call result ({\small\texttt{main}}).
+This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the closure call result ({\small\texttt{main}}).
 The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}.
@@
 
-The algrithm builds a consumption summary for an expression which returns a value.
+The algorithm builds a consumption summary for an expression which returns a value.
 It starts from the the expression node in the abstract syntax tree produced from parsing the source code and walks up  collecting data.
-In the particular case when we start from an expression wich defines a function ( a function body or {\small\texttt{new Function()}} ), it computess the consumption summary for the function.
+In the particular case when we start from an expression which defines a function ( a function body or {\small\texttt{new Function()}} ), it computes the consumption summary for the function.
 The first node is an expression and returns a value.
 At every step, it stores how the value of the current node is related to the value of the parent node.
-If the parent expression is an array or object literal then the curerent node value is \textit{partOf} the parent node value.
+If the parent expression is an array or object literal then the current node value is \textit{partOf} the parent node value.
 Otherwise the node expression value is \textit{theSame} as or different \textit{contributesTo} parent value.
@@
 \end{table}
-
-Morover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
-If the parent node is an object literal, then the node value is assigned to a named property like {\small\texttt{foo}}.
-In this case we keep {\small\texttt{foo}} as the \textit{id}.
-If the parent node is a function call that the expression value is passed as one of its argument, we reduce the function expression to a name and we keep that as \textit{id}.
-In the case of function call, another value, \textit{hint}, will also be computed and saved.
-In the case where the parent node is an assignment we reduce the left side expression to a name and we keep that as \textit{id}.
-The algorithm ends when we reach a node which an assignment or a statmement which does not return any value (i.e., the node is not an expression).
 
@@
 
+Moreover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
+If the parent node is an object literal, then the node value is assigned to a named property like {\small\texttt{foo}}.
+In this case we keep {\small\texttt{foo}} as the \textit{id}.
+If the parent node is a function call that the expression value is passed as one of its argument, we reduce the function expression to a name and we keep that as \textit{id}.
+In the case of function call, another value, \textit{hint}, will also be computed from other arguments and stored.
+In the case where the parent node is an assignment we reduce the left side expression to a name and we keep that as \textit{id}.
+The algorithm ends when we reach a node which is an assignment or a statement which does not return any value (i.e., the node is not an expression).
+
 %The algorithm build a consumption summary for an expression which returns a value.
@@
 The result value might be different from the consumed value like case 3 in table 2.
-Morover we keep identifiers at every node is one of the constructs in table 2.
+Moreover we keep identifiers at every node is one of the constructs in table 2.
 
@@
 In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
-The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not neccessarily
+The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not necessarily
  a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT. 
@@
 A closure function is called directly after its creation. Therefore a closure function is like a simple block and any static analysis like
-for buiilding object consumption summary and variable refinement can be continued outside a closure function. Every expression which its value
-is returned in the closure function is assigned to the expression that closure function call result is assigned to. Morover, in cases where the
+for building object consumption summary and variable refinement can be continued outside a closure function. Every expression which its value
+is returned in the closure function is assigned to the expression that closure function call result is assigned to. Moreover, in cases where the
 function call defines "this" (by apply()) or arguments these variables can be replaced in the function body.
@@
 Next we join the list items using special characters to signal the attributes.
-For identifers from rows 1-6 of Table~\ref{table:function-types} we put out the identifier followed by a WHAT.
-For rows 7 and 8 we put out the identifier followed by a slash (/), the traditional separator in a containment heirarchy.
+For identifiers from rows 1-6 of Table~\ref{table:function-types} we put out the identifier followed by a WHAT.
+For rows 7 and 8 we put out the identifier followed by a slash (/), the traditional separator in a containment hierarchy.
 For rows 9-11 the identifier is followed by a left angle bracket (<) indicating 'contributes to'.
@@
 The particular symbols we use may be refined with more experience in how developers respond to them.
-Our intution is that these extra symbols need to be visually compact because their purpose is to adjust the developers expectation for the identifier.
+Our intuition is that these extra symbols need to be visually compact because their purpose is to adjust the developers expectation for the identifier.
 For example, the function on line 9 of Fig.~\ref{fig:js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.
@@
 \section{Special Cases}
-Given that our goals trade precision for rapid recogition, our names are not unique or perfectly tuned to every developer's need.
+Given that our goals trade precision for rapid recognition, our names are not unique or perfectly tuned to every developer's need.
 We also leave some cases anonymous.

### 2011-04-07 papers/splash-wavefront2011/sigplanconf-template.tex
moved some stuff around and begin work on algorithm

@@
 Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
-Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}; these cases would only make the ratio even smaller.
+Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.
 Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
@@
 Static Function Object Consumption generalizes the built-in JavaScript naming and common, simple coding patterns like object property initializers and variable assignments typically recognized by developers as naming functions.
+
 The built-in naming, a function declaration, binds a name in a scope to a function object created from the adjacent function body.
@@
 
-Our algorithm applies the same logic: we follow the function object backwards through the code to create a name in cases where an identifier is not directly given in the code.
-By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree.
-For each function body, we walk up the tree recording identifiers or expressions explains the function object consumption.
-The result is, \textit{object consumption summary}, a list of collected data at every visited node in the tree.
-%Then, to refine the summary from temporary variable, we look for assignments from and to the variables appear in the summary.
-Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings.
-After the refinement step,
-Then, we rank collected identifiers and strings and elide less relevant data from the summary.
-At the end we construct a string from the consumption summary.
-The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
-It compactly explains the function object creation, consumption and assignment.
+Our algorithm applies the same logic: we look at the code preceding the function body to see where the resulting function object will end up, or
+where the object will be \textit{consumed}.
+Along that path we collect or construct identifiers from the developers source code.
+We add some symbols to guide the developer to the function body in complex cases, and we prefix deeply nested function bodies with context names to disambiguate the result.
 For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.
-
-The name is built by the above process does not contain any information about enclosing scopes.
-We call it \textit{local name}.
-We get the function \textit{full name} by adding the enclosing function full name with a slash before the local name.
 
@@
 
-\subsection{Example}
-
-To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
-
-The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
-We can explain the function object consumption after its creation in two steps: 1) the function object is called.
-2) the result is assigned to {\small\texttt{main}}.
-This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
-We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".
-
-The function in line 10 is returned just after its creation.
-This function is located inside a closure function (i.e., a function which is called directly after its creation).
-This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the closure call result ({\small\texttt{main}}).
-The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}.
-As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
-
-The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
-Here 1) the function object is passed as an argument to function {\small\texttt{op}}, 2) The call result is assigned to {\small\texttt{result}}.
-If we simply put the identifiers in the summary together we get {\small\texttt{main/result<op()}}.
-The first part before slash  shows the context name (the enclosing function name) for this function.
-However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
-Therefore, as we explain in 4.5, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
-After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
-Eliding identifiers is important to avoid creating long, unwieldy names.
-
-The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.
-The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
 %\subsection{Full Function Object Consumption Name}
@@
 \label{sec:nodewalk}
+
+We parse the JavaScript and search the resulting syntax tree for function body nodes.
+For each function body, we apply the algorithm outlined in Algorithm~\ref{alg1}).
+The basic idea is to look for parent nodes with helpful identifiers and to keep track of how the parent and child are related.
+to determine they match one of the rows in Table~\ref{table:node-types}. Any matching no
+
+walk up the tree recording identifiers or expressions explains the function object consumption.
+The result is, \textit{object consumption summary}, a list of collected data at every visited node in the tree.
+%Then, to refine the summary from temporary variable, we look for assignments from and to the variables appear in the summary.
+Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings.
+After the refinement step,
+Then, we rank collected identifiers and strings and elide less relevant data from the summary.
+At the end we construct a string from the consumption summary.
+The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
+It compactly explains the function object creation, consumption and assignment.
+The name is built by the above process does not contain any information about enclosing scopes.
+We call it \textit{local name}.
+We get the function \textit{full name} by adding the enclosing function full name with a slash before the local name.
 
@@
 
-\begin{table}
-\centering
-%\scalebox{0.8}{
-\renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | m{2.5cm} | l|}
-  \hline
-   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
-  \hline
-
-   1 & 
-   & \raggedright an object literal.
-   & \{ ..., foo: expr \}\\ 
-   \cline{0-0}\cline{3-4}
-
-   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node is\end{rotate}} 
-   & 
-     \raggedright a function call.
-   & foo\textsuperscript{*}(..., expr, ...) \\
-   \cline{0-0}\cline{3-4}
-
-   3 &
-   & \raggedright an assignment.
-   & foo\textsuperscript{*} = expr\\
-   \cline{0-0}\cline{2-4}
-
-  \end{tabular}
-%  }
-\caption{Nodes produce identifiers in the function object consumption summary.
-Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
-\label{table:node-types} 
-\end{table}
-
 %\floatname{algorithm}{Procedure}
@@
 \begin{algorithm}                      % enter the algorithm environment
-\caption{Compute Object Consumption Summary for Node $n$}          % give the algorithm a caption
+\caption{Compute Object Consumption Summary for Function Body Nodes}          % give the algorithm a caption
 \label{alg1}                           % and a label for \ref{} commands later in the document
 \begin{algorithmic}                    % enter the algorithmic environment
-\REQUIRE Node $n$ in Abstract Syntax Tree
+\REQUIRE Function Body Node $n$ in Abstract Syntax Tree
 \ENSURE Object Consumption Summary 
@@
 
+\begin{table}
+\centering
+%\scalebox{0.8}{
+\renewcommand\arraystretch{2.0}
+\begin{tabular}{ | c | l | m{2.5cm} | l|}
+  \hline
+   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+  \hline
+
+   1 & 
+   & \raggedright an object literal.
+   & \{ ..., foo: expr \}\\ 
+   \cline{0-0}\cline{3-4}
+
+   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node is\end{rotate}} 
+   & 
+     \raggedright a function call.
+   & foo\textsuperscript{*}(..., expr, ...) \\
+   \cline{0-0}\cline{3-4}
+
+   3 &
+   & \raggedright an assignment.
+   & foo\textsuperscript{*} = expr\\
+   \cline{0-0}\cline{2-4}
+
+  \end{tabular}
+%  }
+\caption{Nodes produce identifiers in the function object consumption summary.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
+\label{table:node-types} 
+\end{table}
+
 Moreover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
@@
 %\subsection{Naming Functions in Call Stack}
+
+\subsection{Example}
+
+To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
+
+The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
+We can explain the function object consumption after its creation in two steps: 1) the function object is called.
+2) the result is assigned to {\small\texttt{main}}.
+This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
+We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".
+
+The function in line 10 is returned just after its creation.
+This function is located inside a closure function (i.e., a function which is called directly after its creation).
+This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the closure call result ({\small\texttt{main}}).
+The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}.
+As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
+
+The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
+Here 1) the function object is passed as an argument to function {\small\texttt{op}}, 2) The call result is assigned to {\small\texttt{result}}.
+If we simply put the identifiers in the summary together we get {\small\texttt{main/result<op()}}.
+The first part before slash  shows the context name (the enclosing function name) for this function.
+However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
+Therefore, as we explain in 4.5, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
+After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
+Eliding identifiers is important to avoid creating long, unwieldy names.
+
+The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.
+The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
 

### 2011-04-07 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
11-row table re-ordered to match the text.

@@
 To get empirical evidence we analyzed the source code of ten well-known JavaScript projects.
-For every project, the total number of functions and the number of functions with an identifier are collected (Table~\ref{js-functions}).
-The average ratio of named functions to all functions is less then 7 percent and excepting one project (Prototype), the ratio does not exceed 13 percent.
-Our analysis does not include the functions defined by dynamically created evaluated scripts created by {\small\texttt{eval}} function).
+For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}.
+The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent.
 Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
+Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.
 Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
@@
 
-Our algorithm applies the same logic: we follow the function object backwards through the code to create a name in cases where an identifier is not directly given in the code.
-By 'backwards through the code' we mean that we parse the JavaScript and analyze the resulting syntax tree.
-For each function body, we walk up the tree recording identifiers or expressions explains the function object consumption.
-The result is, \textit{object consumption summary}, a list of collected data at every visited node in the tree.
-%Then, to refine the summary from temporary variable, we look for assignments from and to the variables appear in the summary.
-Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings.
-After the refinment step,
-Then, we rank collected identifiers and strings and elide less relevant data from the summary.
-At the end we construct a string from the consumption summary.
-The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
-It compactly explains the function object creation, consumption and assignment.
+Our algorithm applies the same logic: we look at the code preceding the function body to see where the resulting function object will end up, or
+where the object will be \textit{consumed}.
+Along that path we collect or construct identifiers from the developers source code.
+We add some symbols to guide the developer to the function body in complex cases, and we prefix deeply nested function bodies with context names to disambiguate the result.
 For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.
-
-The name is built by the above process does not contain any information about enclosing scopes.
-We call it \textit{local name}.
-We get the function \textit{full name} by adding the enclosing function full name with a slash before the local name.
 
@@
 
-\subsection{Example}
-
-To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
-
-The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
-We can explain the function object consumption after its creation in two steps: 1) the function object is called.
-2) the result is assigned to {\small\texttt{main}}.
-This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
-We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".
-
-The function in line 10 is returned just after its creation.
-This function is located inside a closure function (i.e., a function which is called directly after its creation).
-This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the clousre call result ({\small\texttt{main}}).
-The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}.
-As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
-
-The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
-Here 1) the function object is passed as an argument to function {\small\texttt{op}}, 2) The call result is assigned to {\small\texttt{result}}.
-If we simply put the identifiers in the summary together we get {\small\texttt{main/result<op()}}.
-The first part before slash  shows the context name (the enclosing function name) for this function.
-However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
-Therefore, as we explain in 4.5, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
-After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
-Eliding identifiers is important to avoid creating long, unwieldy names.
-
-The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.
-The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
 %\subsection{Full Function Object Consumption Name}
@@
 
-The algrithm builds a consumption summary for an expression which returns a value.
+We parse the JavaScript and search the resulting syntax tree for function body nodes.
+For each function body, we apply the algorithm outlined in Algorithm~\ref{alg1}).
+The basic idea is to look for parent nodes with helpful identifiers and to keep track of how the parent and child are related.
+to determine they match one of the rows in Table~\ref{table:node-types}. Any matching no
+
+walk up the tree recording identifiers or expressions explains the function object consumption.
+The result is, \textit{object consumption summary}, a list of collected data at every visited node in the tree.
+%Then, to refine the summary from temporary variable, we look for assignments from and to the variables appear in the summary.
+Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings.
+After the refinement step,
+Then, we rank collected identifiers and strings and elide less relevant data from the summary.
+At the end we construct a string from the consumption summary.
+The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
+It compactly explains the function object creation, consumption and assignment.
+The name is built by the above process does not contain any information about enclosing scopes.
+We call it \textit{local name}.
+We get the function \textit{full name} by adding the enclosing function full name with a slash before the local name.
+
+The algorithm builds a consumption summary for an expression which returns a value.
 It starts from the the expression node in the abstract syntax tree produced from parsing the source code and walks up  collecting data.
-In the particular case when we start from an expression wich defines a function ( a function body or {\small\texttt{new Function()}} ), it computess the consumption summary for the function.
+In the particular case when we start from an expression which defines a function ( a function body or {\small\texttt{new Function()}} ), it computes the consumption summary for the function.
 The first node is an expression and returns a value.
 At every step, it stores how the value of the current node is related to the value of the parent node.
-If the parent expression is an array or object literal then the curerent node value is \textit{partOf} the parent node value.
+If the parent expression is an array or object literal then the current node value is \textit{partOf} the parent node value.
 Otherwise the node expression value is \textit{theSame} as or different \textit{contributesTo} parent value.
@@
 %~\ref{alg1})
-
-\begin{table}
-\centering
-%\scalebox{0.8}{
-\renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | m{2.5cm} | l|}
-  \hline
-   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
-  \hline
-
-   1 & 
-   & \raggedright an object literal.
-   & \{ ..., foo: expr \}\\ 
-   \cline{0-0}\cline{3-4}
-
-   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node is\end{rotate}} 
-   & 
-     \raggedright a function call.
-   & foo\textsuperscript{*}(..., expr, ...) \\
-   \cline{0-0}\cline{3-4}
-
-   3 &
-   & \raggedright an assignment.
-   & foo\textsuperscript{*} = expr\\
-   \cline{0-0}\cline{2-4}
-
-  \end{tabular}
-%  }
-\caption{Nodes produce identifiers in the function object consumption summary.
-Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
-\label{table:node-types} 
-\end{table}
 
@@
 \begin{algorithm}                      % enter the algorithm environment
-\caption{Compute Object Consumption Summary for Node $n$}          % give the algorithm a caption
+\caption{Compute Object Consumption Summary for Function Body Nodes}          % give the algorithm a caption
 \label{alg1}                           % and a label for \ref{} commands later in the document
 \begin{algorithmic}                    % enter the algorithmic environment
-\REQUIRE Node $n$ in Abstract Syntax Tree
+\REQUIRE Function Body Node $n$ in Abstract Syntax Tree
 \ENSURE Object Consumption Summary 
 \STATE $List$ $summary$ = $new$ $List$()
-
 \WHILE {$n.parent$ is an expression}  
@@
 
-Morover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
+\begin{table}
+\centering
+%\scalebox{0.8}{
+\renewcommand\arraystretch{2.0}
+\begin{tabular}{ | c | l | m{2.5cm} | l|}
+  \hline
+   & \multicolumn{2} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+  \hline
+
+   1 & 
+   & \raggedright an object literal.
+   & \{ ..., foo: expr \}\\ 
+   \cline{0-0}\cline{3-4}
+
+   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node is\end{rotate}} 
+   & 
+     \raggedright a function call.
+   & foo\textsuperscript{*}(..., expr, ...) \\
+   \cline{0-0}\cline{3-4}
+
+   3 &
+   & \raggedright an assignment.
+   & foo\textsuperscript{*} = expr\\
+   \cline{0-0}\cline{2-4}
+
+  \end{tabular}
+%  }
+\caption{Nodes produce identifiers in the function object consumption summary.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
+\label{table:node-types} 
+\end{table}
+
+Moreover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
 If the parent node is an object literal, then the node value is assigned to a named property like {\small\texttt{foo}}.
@@
 In the case where the parent node is an assignment we reduce the left side expression to a name and we keep that as \textit{id}.
-The algorithm ends when we reach a node which is an assignment or a statmement which does not return any value (i.e., the node is not an expression).
+The algorithm ends when we reach a node which is an assignment or a statement which does not return any value (i.e., the node is not an expression).
 
@@
   \hline
+
    1 &
+   &  
+   & \multicolumn{2}{|m{2.8cm}|}{
+     \raggedright property of a new object in an object literal.}
+   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
+   \cline{0-0}\cline{4-6}
+
+	 2 &
+	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+	 & \multicolumn{2}{|m{2.8cm}|}{
+	   new array index in an array literal.} 
+   & [..., function()\{...\}, ...] \\ 
+   \cline{0-0}\cline{4-6}
+
+   3 &
    & 
@@
 
-   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+   4 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
    & 
@@
 
-   3 &
-   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
-   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
+   5 &
+   & 
+   & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
    & \raggedright hashmap access by a variable name.
@@
 
-   4 &
+   6 &
    & 
@@
    & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   5 &
+   \cline{0-0}\cline{4-6}
+
+   7 &
    &
-   &
-   & \raggedright  array index.
+   & \multicolumn{2}{|l|}{
+      array index.}
    & foo\textsuperscript{*}[0] = function()\{...\} \\
@@
 
-   6 &
+   8 &
    & 
@@
    & foo = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   7 &
-   &  
-   & \multicolumn{2}{|m{2.8cm}|}{
-     \raggedright property of a new object in an object literal.}
-   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
-   \cline{0-0}\cline{4-6}
-
-	 8 &
-	 & 
-	 & \multicolumn{2}{|m{2.8cm}|}{
-	   new array index in an array literal.} 
-   & [..., function()\{...\}, ...] \\ 
    \cline{0-0}\cline{3-6}

### 2011-04-08 papers/splash-wavefront2011/sigplanconf-template.tex
edit on algorithm and nameExpression; move cases up rename to intuition

@@
 
+\section{To Be Removed}
+
+\begin{table}
+\centering
+\scalebox{0.8}{
+\renewcommand\arraystretch{2.0}
+\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
+  \hline
+   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+  \hline 
+   1 &
+   & 
+   &  
+   & direct access.
+   & bar\textsuperscript{*}.foo = function()\{...\}\\
+   \cline{0-0}\cline{5-6}
+
+   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+   & 
+   & 
+   & \raggedright hashmap access by a string. 
+   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   3 &
+   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
+   & \raggedright hashmap access by a variable name.
+   & bar\textsuperscript{*}[foo] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   4 &
+   & 
+   & 
+   & \raggedright hashmap access by a JavaScript expression.
+   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   5 &
+   &
+   &
+   & \raggedright  array index.
+   & foo\textsuperscript{*}[0] = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   6 &
+   & 
+   & \multicolumn{2}{|l|}{
+      variable.}
+   & foo = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   7 &
+   &  
+   & \multicolumn{2}{|m{2.8cm}|}{
+     \raggedright property of a new object in an object literal.}
+   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
+   \cline{0-0}\cline{4-6}
+
+	 8 &
+	 & 
+	 & \multicolumn{2}{|m{2.8cm}|}{
+	   new array index in an array literal.} 
+   & [..., function()\{...\}, ...] \\ 
+   \cline{0-0}\cline{3-6}
+
+   9 &
+   & \multicolumn{3}{|m{3.8cm}|}{
+     \raggedright directly called.}
+   & function()\{...\}() \\
+   \cline{0-0}\cline{3-6}
+
+   10 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright returned from a function call.}
+   & \{... return function()\{...\}\} \\
+   \cline{0-0}\cline{3-6}
+
+   11 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright passed as an argument to a function.}
+   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
+   \hline
+
+  \end{tabular}
+  }
+\caption{Different cases of function object creation and usage in JavaScript.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
+\label{table:function-types} 
+\end{table}
+
+\begin{table*}
+\centering
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+  \hline 
+   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
+  \hline 
+   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
+  \hline 
+   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
+  \hline 
+   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
+  \hline 
+   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
+  \hline 
+   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
+  \hline 
+   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
+  \hline 
+   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
+  \hline 
+   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
+  \hline 
+   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
+  \hline 
+   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
+  \hline 
+  \end{tabular}
+\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
+\label{function-type-count} 
+\end{table*}
+
+%     and extracting the initial name used for the function object after its creation. 
+%In the third subsection we discuss qualities we expect from an automatically created function name.
+
+\subsection{Building Up Intuition by Example}
+We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
+We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.
+To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
+We want to see what kinds of cases are important and what aspects of these cases help us identify functions.
+
+For this purpose we created 11 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 11 cases, giving the numerical results in Table~\ref{function-type-count}.
+Then we examine each of these cases to think about how we want the functions named.
+
+\subsubsection{Case 1: in Object Literal}
+ This case usually appears when developers try to group a set of functions in a new object.
+A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
+This structure resembles the class structure in traditional object-oriented languages.
+When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
+This structure is also used  when the owner object is a shared object with a set of utility functions.
+
+ The majority of nameless functions (more than 65\%) in almost all studied projects (except Closure), are defined in object literals.
+This case seems particularly simple: the property name makes a good name for the function body.
+But why?
+Our reasoning; the developer-invented property name has high information content, it is textually close to the function body, and the function object created by the function body initializes to the property.
+In some sense the property 'consumes' the function object.
+
+\subsubsection{Case 2: in Array Literal}
+Contrary to the previous case the appearance of this case is very limited.
+It usually appears in initializations or when an array of functions are passed as an argument.
+Among all projects only two projects have instances of nameless functions defined in this way.
+To name the function body defined in an array literal, first we must name the array literal.
+To name the array literal, we consider it as a function body and we employ the same algorithm we use for naming a function body.
+If the array literal receives a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
+
+\subsubsection{Case3: setProperty by Direct Access }
+This case is the second most common case in the studied projects.
+Here, we can see why the Closure project is different from other projects in the first case.
+About 94\% of nameless functions in this project are defined in this way.
+It seems that the Closure developers follow an internal standard for function objects creation and usage.
+Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
+This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
+
+\subsubsection{Case 4: setProperty by String}
+In JavaScript, objects are like hashmaps and their properties can also be accessed by strings.
+In general an expression can be specified in the brackets after the object.
+The expression is evaluated at runtime and the result which should be a string is used to access the property.
+In the simplest form, the expression can be a string.
+As this form can be completely replaced by the direct access, we see few instances of this form for function object assignment.
+The string inside the brackets become the function name in this case.
+
+\subsubsection{Case 5: setProperty by variable}
+The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. Therefore, the variable
+ name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
+Moreover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
+To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
+
+\subsubsection{Case 6: setProperty by Expression}
+ A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}.
+To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
+
+%jQuery.fn["inner" + name] = function() {
+%dojo[dojo._defaultXhr ? "_defaultXhr" : "xhr"] = function
+%scope[this.triggerEvent]
+
+\subsubsection{Case 7: setArray}
+We only observed one instance of this form in the studied projects. The function name consists of the array name with the index like {\small\texttt{foo[0]}}.
+
+\subsubsection{Case 8: setVariable }
+As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
+and its internal scopes.
+Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name is the local function name.
+Therefore, for this group of functions the variable name is used as the function name.
+
+\subsubsection{Case 9: Called}
+Calling functions objects just after their creations is a common pattern in JavaScript.
+This pattern is usually used for building modules employing the closure feature in JavaScript.
+Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
+
+If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
+In this case, we name the function {\small\texttt{Closure}}.
+If the function returns a value and it is assinged to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
+
+\subsubsection{Case 10: Returned}
+Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
+Many constructors are build by this form and therefore the name of thes functions appear in object summaries.
+
+If the function is returned from a function which is just called after its creation(case 9), and the result is assigned to {\small\texttt{foo}}, we name the function {\small\texttt{foo}}.
+Otherwise, if the name of outer function is {\small\texttt{foo}}, we name the function {\small\texttt{fooResult}}.
+
+% this is also important as many constructor/classes are made in this way
+
+\subsubsection{Case 11: as an Argument}
+Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
+{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
+functions as arguments is to register function in a global shared object.
+The function is usually registered with a name which is also passed as string argument.
+Therefore, to improve our naming approach, we include the first string argument (if there is any) in the name.
+For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
+
 %\subsection{Is it possible to automatically name functions?}
@@
 For each function body, we apply the algorithm outlined in Algorithm~\ref{alg1}).
-The basic idea is to look for parent nodes with helpful identifiers and to keep track of how the parent and child are related.
-to determine they match one of the rows in Table~\ref{table:node-types}. Any matching no
-
-walk up the tree recording identifiers or expressions explains the function object consumption.
-The result is, \textit{object consumption summary}, a list of collected data at every visited node in the tree.
-%Then, to refine the summary from temporary variable, we look for assignments from and to the variables appear in the summary.
-Then we replace the temporary variables more expressive identifiers (e.g., property names) or strings.
-After the refinement step,
-Then, we rank collected identifiers and strings and elide less relevant data from the summary.
-At the end we construct a string from the consumption summary.
+The basic idea is to look for parent nodes with helpful identifiers as outlined in  Table~\ref{table:node-types}.
+In simple cases the parent node will have a simple identifier; otherwise we construct an identifier from the expression as described in \ref{sec:general-element-naming}.
+At each step we track how the parent and child are related.
+If the parent expression is an array or object literal then the current node value is \textit{partOf} the parent node value.
+Otherwise the node expression value is \textit{theSame} as or different \textit{contributesTo} parent value.
+The algorithm ends when we reach a node which is an assignment or a statement which does not return any value (i.e., the node is not an expression).
+The algorithm result is an \textit{object consumption summary}, a list of collected data at every visited parent node of the function body.
+
+Next we rank the collected identifiers and strings to elide less relevant data from the summary.
+Finally we concatenate the items with marker symbols to construct a string from the consumption summary.
 The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
 It compactly explains the function object creation, consumption and assignment.
+
 The name is built by the above process does not contain any information about enclosing scopes.
 We call it \textit{local name}.
-We get the function \textit{full name} by adding the enclosing function full name with a slash before the local name.
-
-The algorithm builds a consumption summary for an expression which returns a value.
-It starts from the the expression node in the abstract syntax tree produced from parsing the source code and walks up  collecting data.
-In the particular case when we start from an expression which defines a function ( a function body or {\small\texttt{new Function()}} ), it computes the consumption summary for the function.
-The first node is an expression and returns a value.
-At every step, it stores how the value of the current node is related to the value of the parent node.
-If the parent expression is an array or object literal then the current node value is \textit{partOf} the parent node value.
-Otherwise the node expression value is \textit{theSame} as or different \textit{contributesTo} parent value.
-
-%~\ref{alg1})
-
-%\floatname{algorithm}{Procedure}
+We get the function \textit{full name} by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
+This full-name is our function body name.
+
+%\floatname{algorithm}{Procedure}b
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
    	    \STATE $dataItem.isFunctionCall$ = $true$
-   	    \STATE $dataItem.id$ = $idForFC(n.parent)$
-   	    \STATE $dataItem.hint$ = $hintForFC(n.parent)$
+   	    \STATE $dataItem.id$ = $nameExpression(n.parent)$
+   	    \STATE $dataItem.hint$ = $argSummary(n.parent)$
    	\ELSIF {$n.parent$ is an object literal and $n$ is assigned to $foo$}
@@
 		\STATE $dataItem.isAssignment$ = $true$
-    \STATE $dataItem.id$ = $idForAssignment(n.parent)$
+    \STATE $dataItem.id$ = $nameExpression(n.parent)$
     \STATE $summary.add(dataItem)$
@@
 
-Moreover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
+%Moreover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
 If the parent node is an object literal, then the node value is assigned to a named property like {\small\texttt{foo}}.
@@
 In the case where the parent node is an assignment we reduce the left side expression to a name and we keep that as \textit{id}.
-The algorithm ends when we reach a node which is an assignment or a statement which does not return any value (i.e., the node is not an expression).
 
@@
 
-\subsubsection{to a Name}
-In simple cases the syntax tree node will have an identifier we can use as part of our name. In more complex cases an expression will written in place of an identifier. 
-The expression can be long and complex. Again, to make our names more compact and readable we convert expression into a pseudo-identifier (i.e. not necessarily
- a valid JavaScript identifier) that resembles the expression. We do this by retaining any simple identifiers -- the developer will recognize these -- but we drop WHAT. 
-\subsubsection{to a Hashmap Key}
-
-\subsubsection{Building a String from Arguments}
-WHAT?
-
-\subsection{Culling Less Informative Items}
-Since ultimately our aim is an understandable name, we next process our list of identifiers to remove items likely to be uninformative.
-Of course this is a heuristic process and ultimately we expect it to be tuned with user testing or future insights.
-For now we remove XXX from our list because YYY.
+In simple cases the syntax tree node will have an identifier we can use as part of our name.
+In more complex cases an expression will written in place of an identifier.
+We reduce these expressions to pseudo-identifiers (i.e.
+not necessarily a valid JavaScript identifier) that resembles the expression.
+This work is done during the Object Consumption Summary algorithm in the functions described here:
+\paragraph{Identifiers for Function Arguments (argSummary)} Search for all string nodes in other arguments and concatenated them by ``-'', dropping  characters over 10. 
+\paragraph{Identifiers for Assignments and Function calls (nameExpressions)} This function gets called for nodes resulting from the first 6 rows of Table~{table:function-types}.
+The expressions here will evaluate to a writable address, so we want to extract the most specific developer-invented identifiers from the expression.
+Thus we apply the rules from Table~{expression-reduction}, which starts from the right hand side of the expression;  we skip any JavaScript keywords like \texttt{this} or \text{prototype}.
+If we encounter any pattern which does not match, for example a function call, we stop.
+
+Obviously these rules are heuristic and can be improved through experience and interaction with developers.
+We are attempting to balance information content with length.
+Large complex expressions will give pseudo-identifiers which are complex, but with some identifiable parts.
 
@@
   \hline
-   Description & Total & Named \\ 
+   Description &Pattern &  Name \\ 
   \hline 
@@
   \hline 
-   Variable & foo & foo \\ 
-  \hline 
-   GetProp & bar.foo & Name(bar).foo \\ 
-  \hline 
-   GetElem & bar[foo] & Name(bar)+[Name(foo)] \\ 
-  \hline 
-   Add & bar op foo & Name(bar)+op+Name(foo) \\ 
-  \hline 
-   Condition & cond?bar:foo & Name(bar)+":"+Name(foo) \\ 
+   Variable & id & id \\ 
+  \hline 
+   GetProp & e.id & Name(e).id \\ 
+  \hline 
+   GetElem & e1[e2] & Name(e1)+``['+'Name(e2)+``]'' \\ 
+  \hline 
+   Add & e1 op e2 & Name(e1)+op+Name(e2) \\ 
+  \hline 
+   Condition & cond?e1:e2 & Name(e1)+":"+Name(e2) \\ 
   \hline 
@@
   }
-\caption{JavaScript Expression Reduction to Name.}
+\caption{JavaScript Expression Reduction to a Name.
+Expressions which match an entry in the pattern column are converted as shown in the Name column.
+Here \texttt{e} indicates an expression, \texttt{id} indicates an identifier, \texttt{+} means string concatenation and \texttt{Name()} means we apply the pattern matching recursively.}
 \label{expression-reduction} 
@@
 
-To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
+To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
 
 The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
-We can explain the function object consumption after its creation in two steps: 1) the function object is called.
+We can explain the function object consumption after its creation in two steps.
+First the parent node is a function call (row 2 in Table~\ref{table:node-types}.
 2) the result is assigned to {\small\texttt{main}}.
@@
 
-\section{To Be Removed}
-
-\begin{table}
-\centering
-\scalebox{0.8}{
-\renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
-  \hline
-   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
-  \hline 
-   1 &
-   & 
-   &  
-   & direct access.
-   & bar\textsuperscript{*}.foo = function()\{...\}\\
-   \cline{0-0}\cline{5-6}
-
-   2 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
-   & 
-   & 
-   & \raggedright hashmap access by a string. 
-   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   3 &
-   & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
-   & \multirow{5}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
-   & \raggedright hashmap access by a variable name.
-   & bar\textsuperscript{*}[foo] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   4 &
-   & 
-   & 
-   & \raggedright hashmap access by a JavaScript expression.
-   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   5 &
-   &
-   &
-   & \raggedright  array index.
-   & foo\textsuperscript{*}[0] = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   6 &
-   & 
-   & \multicolumn{2}{|l|}{
-      variable.}
-   & foo = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   7 &
-   &  
-   & \multicolumn{2}{|m{2.8cm}|}{
-     \raggedright property of a new object in an object literal.}
-   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
-   \cline{0-0}\cline{4-6}
-
-	 8 &
-	 & 
-	 & \multicolumn{2}{|m{2.8cm}|}{
-	   new array index in an array literal.} 
-   & [..., function()\{...\}, ...] \\ 
-   \cline{0-0}\cline{3-6}
-
-   9 &
-   & \multicolumn{3}{|m{3.8cm}|}{
-     \raggedright directly called.}
-   & function()\{...\}() \\
-   \cline{0-0}\cline{3-6}
-
-   10 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright returned from a function call.}
-   & \{... return function()\{...\}\} \\
-   \cline{0-0}\cline{3-6}
-
-   11 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright passed as an argument to a function.}
-   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
-   \hline
-
-  \end{tabular}
-  }
-\caption{Different cases of function object creation and usage in JavaScript.
-Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
-\label{table:function-types} 
-\end{table}
-
-\begin{table*}
-\centering
-  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
-  \hline
-     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
-  \hline 
-   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
-  \hline 
-   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
-  \hline 
-   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
-  \hline 
-   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
-  \hline 
-   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
-  \hline 
-   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
-  \hline 
-   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
-  \hline 
-   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
-  \hline 
-   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
-  \hline 
-   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
-  \hline 
-   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
-  \hline 
-  \end{tabular}
-\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
-\label{function-type-count} 
-\end{table*}
-
-%     and extracting the initial name used for the function object after its creation. 
-%In the third subsection we discuss qualities we expect from an automatically created function name.
-
-\subsection{Naming Scheme}
-We can generalize the approach used for naming functions in the example by studying different cases that a function object can be created and used.
-Once a function object is created, one of the cases presented in Table~\ref{table:function-types} can happen.
-One common case of function object creation is by top script named function bodies.
-We did not considered this case as a separate case as it can be transformed to case 8 where a function body is assigned to a variable.
-Moreover, Note that functions are created by {\small\texttt{Function}} constructor can be replace by a function body and named in the same way.
-For every case, we will explain how a name can be assigned to the function.
-
-Names which are specified with a star are reduced from a JavaScript expression.
-We discuss this reduction in ~\ref{sec:general-element-naming}.
-Table~\ref{function-type-count} shows the number of nameless functions in each category in the studied projects.
-These numbers shows how frequent and important a category of functions is in these projects.
-%they have similar pattern
-
-\subsubsection{Case 1: in Object Literal}
- This case usually appears when developers try to group a set of functions in a new object.
-A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
-This structure resembles the class structure in traditional object-oriented languages.
-When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
-This structure is also used  when the owner object is a shared object with a set of utility functions.
-
- The majority of nameless functions (more than 65\%) in almost all studied projects (except Closure), are defined in object literals.
-For this group of functions we assign the property name used to keep a reference to the function object as the function name.
-
-\subsubsection{Case 2: in Array Literal}
-Contrary to the previous case the appearance of this case is very limited.
-It usually appears in initializations or when an array of functions are passed as an argument.
-Among all projects only two projects have instances of nameless functions defined in this way.
-To name the function body defined in an array literal, first we must name the array literal.
-To name the array literal, we consider it as a function body and we employ the same algorithm we use for naming a function body.
-If the array literal receives a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
-
-\subsubsection{Case3: setProperty by Direct Access }
-This case is the second most common case in the studied projects.
-Here, we can see why the Closure project is different from other projects in the first case.
-About 94\% of nameless functions in this project are defined in this way.
-It seems that the Closure developers follow an internal standard for function objects creation and usage.
-Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
-This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
-
-\subsubsection{Case 4: setProperty by String}
-In JavaScript, objects are like hashmaps and their properties can also be accessed by strings.
-In general an expression can be specified in the brackets after the object.
-The expression is evaluated at runtime and the result which should be a string is used to access the property.
-In the simplest form, the expression can be a string.
-As this form can be completely replaced by the direct access, we see few instances of this form for function object assignment.
-The string inside the brackets become the function name in this case.
-
-\subsubsection{Case 5: setProperty by variable}
-The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. Therefore, the variable
- name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
-Moreover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
-To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
-
-\subsubsection{Case 6: setProperty by Expression}
- A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}.
-To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
-
-%jQuery.fn["inner" + name] = function() {
-%dojo[dojo._defaultXhr ? "_defaultXhr" : "xhr"] = function
-%scope[this.triggerEvent]
-
-\subsubsection{Case 7: setArray}
-We only observed one instance of this form in the studied projects. The function name consists of the array name with the index like {\small\texttt{foo[0]}}.
-
-\subsubsection{Case 8: setVariable }
-As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
-and its internal scopes.
-Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name is the local function name.
-Therefore, for this group of functions the variable name is used as the function name.
-
-\subsubsection{Case 9: Called}
-Calling functions objects just after their creations is a common pattern in JavaScript.
-This pattern is usually used for building modules employing the closure feature in JavaScript.
-Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
-
-If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
-In this case, we name the function {\small\texttt{Closure}}.
-If the function returns a value and it is assinged to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
-
-\subsubsection{Case 10: Returned}
-Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
-Many constructors are build by this form and therefore the name of thes functions appear in object summaries.
-
-If the function is returned from a function which is just called after its creation(case 9), and the result is assigned to {\small\texttt{foo}}, we name the function {\small\texttt{foo}}.
-Otherwise, if the name of outer function is {\small\texttt{foo}}, we name the function {\small\texttt{fooResult}}.
-
-% this is also important as many constructor/classes are made in this way
-
-\subsubsection{Case 11: as an Argument}
-Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
-{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
-functions as arguments is to register function in a global shared object.
-The function is usually registered with a name which is also passed as string argument.
-Therefore, to improve our naming approach, we include the first string argument (if there is any) in the name.
-For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
-
 \end{document}

### 2011-04-08 trunk/papers/splash-wavefront2011/sigplanconf-template.tex

@@
 
+\section{To Be Removed}
+
+\begin{table}
+\centering
+\scalebox{0.8}{
+\renewcommand\arraystretch{2.0}
+\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
+  \hline
+   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
+  \hline
+
+   1 &
+   &  
+   & \multicolumn{2}{|m{2.8cm}|}{
+     \raggedright property of a new object in an object literal.}
+   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
+   \cline{0-0}\cline{4-6}
+
+	 2 &
+	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+	 & \multicolumn{2}{|m{2.8cm}|}{
+	   new array index in an array literal.} 
+   & [..., function()\{...\}, ...] \\ 
+   \cline{0-0}\cline{4-6}
+
+   3 &
+   & 
+   &  
+   & direct access.
+   & bar\textsuperscript{*}.foo = function()\{...\}\\
+   \cline{0-0}\cline{5-6}
+
+   4 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+   & 
+   & 
+   & \raggedright hashmap access by a string. 
+   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   5 &
+   & 
+   & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
+   & \raggedright hashmap access by a variable name.
+   & bar\textsuperscript{*}[foo] = function()\{...\} \\
+   \cline{0-0}\cline{5-6}
+
+   6 &
+   & 
+   & 
+   & \raggedright hashmap access by a JavaScript expression.
+   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   7 &
+   &
+   & \multicolumn{2}{|l|}{
+      array index.}
+   & foo\textsuperscript{*}[0] = function()\{...\} \\
+   \cline{0-0}\cline{4-6}
+
+   8 &
+   & 
+   & \multicolumn{2}{|l|}{
+      variable.}
+   & foo = function()\{...\} \\
+   \cline{0-0}\cline{3-6}
+
+   9 &
+   & \multicolumn{3}{|m{3.8cm}|}{
+     \raggedright directly called.}
+   & function()\{...\}() \\
+   \cline{0-0}\cline{3-6}
+
+   10 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright returned from a function call.}
+   & \{... return function()\{...\}\} \\
+   \cline{0-0}\cline{3-6}
+
+   11 &
+   & \multicolumn{3}{|m{3.5cm}|}{
+     \raggedright passed as an argument to a function.}
+   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
+   \hline
+
+  \end{tabular}
+    }
+\caption{Different cases of function object creation and usage in JavaScript.
+Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
+\label{table:function-types} 
+\end{table}
+
+\begin{table*}
+\centering
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
+  \hline 
+   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
+  \hline 
+   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
+  \hline 
+   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
+  \hline 
+   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
+  \hline 
+   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
+  \hline 
+   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
+  \hline 
+   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
+  \hline 
+   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
+  \hline 
+   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
+  \hline 
+   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
+  \hline 
+   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
+  \hline 
+  \end{tabular}
+\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
+\label{function-type-count} 
+\end{table*}
+
+%     and extracting the initial name used for the function object after its creation. 
+%In the third subsection we discuss qualities we expect from an automatically created function name.
+
+\subsection{Building Up Intuition by Example}
+We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
+We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.
+To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
+We want to see what kinds of cases are important and what aspects of these cases help us identify functions.
+
+For this purpose we created 11 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 11 cases, giving the numerical results in Table~\ref{function-type-count}.
+Then we examine each of these cases to think about how we want the functions named.
+
+\subsubsection{Case 1: in Object Literal}
+ This case usually appears when developers try to group a set of functions in a new object.
+A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
+This structure resembles the class structure in traditional object-oriented languages.
+When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
+This structure is also used  when the owner object is a shared object with a set of utility functions.
+
+ The majority of nameless functions (more than 65\%) in almost all studied projects (except Closure), are defined in object literals.
+This case seems particularly simple: the property name makes a good name for the function body.
+But why?
+Our reasoning; the developer-invented property name has high information content, it is textually close to the function body, and the function object created by the function body initializes to the property.
+In some sense the property 'consumes' the function object.
+
+\subsubsection{Case 2: in Array Literal}
+Contrary to the previous case the appearance of this case is very limited.
+It usually appears in initializations or when an array of functions are passed as an argument.
+Among all projects only two projects have instances of nameless functions defined in this way.
+To name the function body defined in an array literal, first we must name the array literal.
+To name the array literal, we consider it as a function body and we employ the same algorithm we use for naming a function body.
+If the array literal receives a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
+
+\subsubsection{Case3: setProperty by Direct Access }
+This case is the second most common case in the studied projects.
+Here, we can see why the Closure project is different from other projects in the first case.
+About 94\% of nameless functions in this project are defined in this way.
+It seems that the Closure developers follow an internal standard for function objects creation and usage.
+Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
+This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
+
+\subsubsection{Case 4: setProperty by String}
+In JavaScript, objects are like hashmaps and their properties can also be accessed by strings.
+In general an expression can be specified in the brackets after the object.
+The expression is evaluated at runtime and the result which should be a string is used to access the property.
+In the simplest form, the expression can be a string.
+As this form can be completely replaced by the direct access, we see few instances of this form for function object assignment.
+The string inside the brackets become the function name in this case.
+
+\subsubsection{Case 5: setProperty by variable}
+The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. Therefore, the variable
+ name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
+Moreover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
+To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
+
+\subsubsection{Case 6: setProperty by Expression}
+ A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}.
+To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
+
+%jQuery.fn["inner" + name] = function() {
+%dojo[dojo._defaultXhr ? "_defaultXhr" : "xhr"] = function
+%scope[this.triggerEvent]
+
+\subsubsection{Case 7: setArray}
+We only observed one instance of this form in the studied projects. The function name consists of the array name with the index like {\small\texttt{foo[0]}}.
+
+\subsubsection{Case 8: setVariable }
+As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
+and its internal scopes.
+Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name is the local function name.
+Therefore, for this group of functions the variable name is used as the function name.
+
+\subsubsection{Case 9: Called}
+Calling functions objects just after their creations is a common pattern in JavaScript.
+This pattern is usually used for building modules employing the closure feature in JavaScript.
+Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
+
+If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
+In this case, we name the function {\small\texttt{Closure}}.
+If the function returns a value and it is assinged to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
+
+\subsubsection{Case 10: Returned}
+Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
+Many constructors are build by this form and therefore the name of thes functions appear in object summaries.
+
+If the function is returned from a function which is just called after its creation(case 9), and the result is assigned to {\small\texttt{foo}}, we name the function {\small\texttt{foo}}.
+Otherwise, if the name of outer function is {\small\texttt{foo}}, we name the function {\small\texttt{fooResult}}.
+
+% this is also important as many constructor/classes are made in this way
+
+\subsubsection{Case 11: as an Argument}
+Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
+{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
+functions as arguments is to register function in a global shared object.
+The function is usually registered with a name which is also passed as string argument.
+Therefore, to improve our naming approach, we include the first string argument (if there is any) in the name.
+For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
+
 %\subsection{Is it possible to automatically name functions?}
@@
 \STATE $List$ $summary$ = $new$ $List$()
+
 \WHILE {$n.parent$ is an expression}  
@@
 
-\section{To Be Removed}
-
-\begin{table}
-\centering
-\scalebox{0.8}{
-\renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | l | l | m{2.5cm} | l|}
-  \hline
-   & \multicolumn{4} {| c |}{Description} & \multicolumn{1} {| c |}{Code} \\ 
-  \hline
-
-   1 &
-   &  
-   & \multicolumn{2}{|m{2.8cm}|}{
-     \raggedright property of a new object in an object literal.}
-   & \{ ..., foo: function()\{...\}, ...\}\\ %{\small\begin{verbatim}{ ..., foo: function(){...}, ...}\end{verbatim}} \\ %
-   \cline{0-0}\cline{4-6}
-
-	 2 &
-	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
-	 & \multicolumn{2}{|m{2.8cm}|}{
-	   new array index in an array literal.} 
-   & [..., function()\{...\}, ...] \\ 
-   \cline{0-0}\cline{4-6}
-
-   3 &
-   & 
-   &  
-   & direct access.
-   & bar\textsuperscript{*}.foo = function()\{...\}\\
-   \cline{0-0}\cline{5-6}
-
-   4 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
-   & 
-   & 
-   & \raggedright hashmap access by a string. 
-   & bar\textsuperscript{*}["foo"] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   5 &
-   & 
-   & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}object property through\end{rotate}}
-   & \raggedright hashmap access by a variable name.
-   & bar\textsuperscript{*}[foo] = function()\{...\} \\
-   \cline{0-0}\cline{5-6}
-
-   6 &
-   & 
-   & 
-   & \raggedright hashmap access by a JavaScript expression.
-   & bar\textsuperscript{*}[foo\textsuperscript{*}] = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   7 &
-   &
-   & \multicolumn{2}{|l|}{
-      array index.}
-   & foo\textsuperscript{*}[0] = function()\{...\} \\
-   \cline{0-0}\cline{4-6}
-
-   8 &
-   & 
-   & \multicolumn{2}{|l|}{
-      variable.}
-   & foo = function()\{...\} \\
-   \cline{0-0}\cline{3-6}
-
-   9 &
-   & \multicolumn{3}{|m{3.8cm}|}{
-     \raggedright directly called.}
-   & function()\{...\}() \\
-   \cline{0-0}\cline{3-6}
-
-   10 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright returned from a function call.}
-   & \{... return function()\{...\}\} \\
-   \cline{0-0}\cline{3-6}
-
-   11 &
-   & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright passed as an argument to a function.}
-   & foo\textsuperscript{*}(..., function()\{\}, ...) \\
-   \hline
-
-  \end{tabular}
- }
-\caption{Different cases of function object creation and usage in JavaScript.
-Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
-\label{table:function-types} 
-\end{table}
-
-\begin{table*}
-\centering
-  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
-  \hline
-     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
-  \hline 
-   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
-  \hline 
-   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
-  \hline 
-   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
-  \hline 
-   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
-  \hline 
-   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
-  \hline 
-   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
-  \hline 
-   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
-  \hline 
-   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
-  \hline 
-   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
-  \hline 
-   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
-  \hline 
-   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
-  \hline 
-\end{tabular}
-\caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
-\label{function-type-count} 
-\end{table*}
-
-%     and extracting the initial name used for the function object after its creation. 
-%In the third subsection we discuss qualities we expect from an automatically created function name.
-
-\subsection{Naming Scheme}
-We can generalize the approach used for naming functions in the example by studying different cases that a function object can be created and used.
-Once a function object is created, one of the cases presented in Table~\ref{table:function-types} can happen.
-One common case of function object creation is by top script named function bodies.
-We did not considered this case as a separate case as it can be transformed to case 8 where a function body is assigned to a variable.
-Moreover, Note that functions are created by {\small\texttt{Function}} constructor can be replace by a function body and named in the same way.
-For every case, we will explain how a name can be assigned to the function.
-
-Names which are specified with a star are reduced from a JavaScript expression.
-We discuss this reduction in ~\ref{sec:general-element-naming}.
-Table~\ref{function-type-count} shows the number of nameless functions in each category in the studied projects.
-These numbers shows how frequent and important a category of functions is in these projects.
-%they have similar pattern
-
-\subsubsection{Case 1: in Object Literal}
- This case usually appears when developers try to group a set of functions in a new object.
-A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
-This structure resembles the class structure in traditional object-oriented languages.
-When a new object is created by the constructor, the new object also inherits all functions defined in the constructor's prototype.
-This structure is also used  when the owner object is a shared object with a set of utility functions.
-
- The majority of nameless functions (more than 65\%) in almost all studied projects (except Closure), are defined in object literals.
-For this group of functions we assign the property name used to keep a reference to the function object as the function name.
-
-\subsubsection{Case 2: in Array Literal}
-Contrary to the previous case the appearance of this case is very limited.
-It usually appears in initializations or when an array of functions are passed as an argument.
-Among all projects only two projects have instances of nameless functions defined in this way.
-To name the function body defined in an array literal, first we must name the array literal.
-To name the array literal, we consider it as a function body and we employ the same algorithm we use for naming a function body.
-If the array literal receives a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
-
-\subsubsection{Case3: setProperty by Direct Access }
-This case is the second most common case in the studied projects.
-Here, we can see why the Closure project is different from other projects in the first case.
-About 94\% of nameless functions in this project are defined in this way.
-It seems that the Closure developers follow an internal standard for function objects creation and usage.
-Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
-This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
-
-\subsubsection{Case 4: setProperty by String}
-In JavaScript, objects are like hashmaps and their properties can also be accessed by strings.
-In general an expression can be specified in the brackets after the object.
-The expression is evaluated at runtime and the result which should be a string is used to access the property.
-In the simplest form, the expression can be a string.
-As this form can be completely replaced by the direct access, we see few instances of this form for function object assignment.
-The string inside the brackets become the function name in this case.
-
-\subsubsection{Case 5: setProperty by variable}
-The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. Therefore, the variable
- name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
-Moreover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
-To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
-
-\subsubsection{Case 6: setProperty by Expression}
- A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}.
-To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
-
-%jQuery.fn["inner" + name] = function() {
-%dojo[dojo._defaultXhr ? "_defaultXhr" : "xhr"] = function
-%scope[this.triggerEvent]
-
-\subsubsection{Case 7: setArray}
-We only observed one instance of this form in the studied projects. The function name consists of the array name with the index like {\small\texttt{foo[0]}}.
-
-\subsubsection{Case 8: setVariable }
-As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
-and its internal scopes.
-Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name is the local function name.
-Therefore, for this group of functions the variable name is used as the function name.
-
-\subsubsection{Case 9: Called}
-Calling functions objects just after their creations is a common pattern in JavaScript.
-This pattern is usually used for building modules employing the closure feature in JavaScript.
-Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
-
-If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
-In this case, we name the function {\small\texttt{Closure}}.
-If the function returns a value and it is assinged to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
-
-\subsubsection{Case 10: Returned}
-Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
-Many constructors are build by this form and therefore the name of thes functions appear in object summaries.
-
-If the function is returned from a function which is just called after its creation(case 9), and the result is assigned to {\small\texttt{foo}}, we name the function {\small\texttt{foo}}.
-Otherwise, if the name of outer function is {\small\texttt{foo}}, we name the function {\small\texttt{fooResult}}.
-
-% this is also important as many constructor/classes are made in this way
-
-\subsubsection{Case 11: as an Argument}
-Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
-{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
-functions as arguments is to register function in a global shared object.
-The function is usually registered with a name which is also passed as string argument.
-Therefore, to improve our naming approach, we include the first string argument (if there is any) in the name.
-For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
-
 \end{document}

### 2011-04-08 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
add examples for cases 5, 11

@@
 
-\section{To Be Removed}
+\section{Building Up Intuition by Example}
+We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
+We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.
+To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
+We want to see what kinds of cases are important and what aspects of these cases help us identify functions.
+
+For this purpose we created 11 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 11 cases, giving the numerical results in Table~\ref{function-type-count}.
+Then we examine each of these cases to think about how we want the functions named.
 
@@
 
-\subsection{Building Up Intuition by Example}
-We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
-We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.
-To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
-We want to see what kinds of cases are important and what aspects of these cases help us identify functions.
-
-For this purpose we created 11 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 11 cases, giving the numerical results in Table~\ref{function-type-count}.
-Then we examine each of these cases to think about how we want the functions named.
-
 \subsubsection{Case 1: in Object Literal}
@@
 It usually appears in initializations or when an array of functions are passed as an argument.
-Among all projects only two projects have instances of nameless functions defined in this way.
+Among all projects only two have instances of nameless functions defined in this way.
+
 To name the function body defined in an array literal, first we must name the array literal.
@@
 Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
-This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assinged to the function body as its name.
+This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assigned to the function body as its name.
 
@@
 \subsubsection{Case 5: setProperty by variable}
-The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. Therefore, the variable
- name is a general name like {\small\texttt{fname}} or {\small\texttt{item}}.
-Moreover, based on the variable value-which is not known until runtime-the owner can be a    regular object or an array.
-To name a function in this case we use the owner object name with the variable inside brackets like {\small\texttt{bar[foo]}}.
+The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
+For example see the inner function in Fig.~\ref{fig:jQueryEach}. The variable
+ name in the cases we examined was generic name like {\small\texttt{o}} or {\small\texttt{item}}.
+Nevertheless identifying the function body using the assignment target seems natural and clear in these cases.
+\begin{figure*}[htp]
+\begin{verbatim}
+jQuery.each( "ajaxStart ajaxStop ajaxComplete ajaxError".split(" "), function( i, o ) {
+    jQuery.fn[o] = function( f ) {
+        return this.bind(o, f);
+    };
+});
+\end{verbatim}
+\caption{An example of functions passed as arguments to a function (row 11 in Table~\ref{table:function-types} and (the inner definition) an example of a 
+function assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}. The function is from the jQuery library but simplified to fit on the page. }
+\label{fig:jQueryEach}
+\end{figure*}
 
@@
  A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}.
-To name this functions, similar to previous case we use the owner object and a sbustring of expression inside the brackets.
+To name this functions, similar to previous case we use the owner object and a substring of expression inside the brackets.
 
@@
 Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
-Many constructors are build by this form and therefore the name of thes functions appear in object summaries.
+Many constructors are build by this form and therefore the name of these functions appear in object summaries.
 
@@
 \subsubsection{Case 11: as an Argument}
-Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
-{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
-functions as arguments is to register function in a global shared object.
-The function is usually registered with a name which is also passed as string argument.
-Therefore, to improve our naming approach, we include the first string argument (if there is any) in the name.
-For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
+Numbers in table~\ref{function-type-count} show that creating and passing functions as arguments is very common in JavaScript.
+For example, see Fig.~\ref{fig:jQueryEach}.
+The calling function and the other arguments look helpful, to the extent that they have identifiers invented by the developer.
+As in the the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in the example are highly specific to the function body.
 

### 2011-04-08 papers/splash-wavefront2011/sigplanconf-template.tex
a wrong number correction in table 3.

@@
   \hline 
-   ExtJS         & 30221(83\%)& 0  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
+   ExtJS         & 30221(83\%)& 10  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
   \hline 
@@
 %In the third subsection we discuss qualities we expect from an automatically created function name.
-
-\subsection{Building Up Intuition by Example}
-We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
-We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.
-To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
-We want to see what kinds of cases are important and what aspects of these cases help us identify functions.
-
-For this purpose we created 11 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 11 cases, giving the numerical results in Table~\ref{function-type-count}.
-Then we examine each of these cases to think about how we want the functions named.
 
@@
 \subsubsection{Case 11: as an Argument}
-Numbers in table~\ref{function-types-count} show that creating and passing functions as arguments is very common in JavaScript. If the calling function name is 
-{\small\texttt{foo}} and the function is passed as the {\small\texttt{ith}} argument, we name the function {\small\texttt{foo(i)}}. One of the common cases of passing
-functions as arguments is to register function in a global shared object.
-The function is usually registered with a name which is also passed as string argument.
-Therefore, to improve our naming approach, we include the first string argument (if there is any) in the name.
-For example if the string argument is {\small\texttt{myFunction}} the assigned name will be {\small\texttt{foo(i)(myFunction)}}.
+Numbers in table~\ref{function-type-count} show that creating and passing functions as arguments is very common in JavaScript.
+For example, see Fig.~\ref{fig:jQueryEach}.
+The calling function and the other arguments look helpful, to the extent that they have identifiers invented by the developer.
+As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in the example are highly specific to the function body.
 

### 2011-04-09 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
progress on the intuition section

@@
 Then we examine each of these cases to think about how we want the functions named.
+We'll ignore nesting of function scopes in the analysis to avoid taking on too much at one time.
 
@@
 
-\subsubsection{Case 1: in Object Literal}
+\subsection{Case 1: Object Property Initializer}
  This case usually appears when developers try to group a set of functions in a new object.
@@
 This case seems particularly simple: the property name makes a good name for the function body.
-But why?
-Our reasoning; the developer-invented property name has high information content, it is textually close to the function body, and the function object created by the function body initializes to the property.
-In some sense the property 'consumes' the function object.
-
-\subsubsection{Case 2: in Array Literal}
+But what logic are we implicitly applying here?
+Our reasoning: the developer-invented property name has high information content, it is textually close to the function body, and the function object created by the function body initializes to the property.
+These observations guide us in more complex cases.
+
+\subsection{Case 2: in Array Literal}
 Contrary to the previous case the appearance of this case is very limited.
@@
 
-\subsubsection{Case3: setProperty by Direct Access }
+\subsection{Case 3: Property Assignment With  Property Identifier }
 This case is the second most common case in the studied projects.
@@
 It seems that the Closure developers follow an internal standard for function objects creation and usage.
-Although most functions are assigned to objects in the initialization phase, there are still cases where functions assigned through direct access.
-This case usually happens when the functions are assigned to object properties after its initialization. Similar to the first case the property name is assigned to the function body as its name.
-
-\subsubsection{Case 4: setProperty by String}
-In JavaScript, objects are like hashmaps and their properties can also be accessed by strings.
-In general an expression can be specified in the brackets after the object.
-The expression is evaluated at runtime and the result which should be a string is used to access the property.
-In the simplest form, the expression can be a string.
-As this form can be completely replaced by the direct access, we see few instances of this form for function object assignment.
-The string inside the brackets become the function name in this case.
-
-\subsubsection{Case 5: setProperty by variable}
+
+Following the model from Case 1, we expect a good name would combine the object name with the property identifier.
+The complication in this case comes from the object name: in general the object reference can be a computed expression.
+These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small.
+This comment apply to all of the cases in table~\ref{table:function-types} marked with an asterix on the expression identifier.
+
+\subsection{Case 4: Property Assignment With  Property Name String}
+In JavaScript, objects are like hashmaps and their properties can also be accessed by a string can be specified in the brackets after the object.
+Semantically this is the same as the previous case and we see few instances of this form for function object assignment.
+The string inside the brackets can be considered a property identifier for naming.
+
+\subsection{Case 5: Property Assignment With  Property Name Variable}
+Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we can't statically compute the string to use as a property identifier.
 The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
 For example see the inner function in Fig.~\ref{fig:jQueryEach}. The variable
- name in the cases we examined was generic name like {\small\texttt{o}} or {\small\texttt{item}}.
-Nevertheless identifying the function body using the assignment target seems natural and clear in these cases.
+ name in the cases we examined was generic name like {\small\texttt{o}} or {\small\texttt{item}}. Unlike the previous two cases, we
+don't have a specific property name.
+Nevertheless identifying the function body using the assignment target with the variable name as the property name follows the reasoning used for the simple cases.
 \begin{figure*}[htp]
@@
 
-\subsubsection{Case 6: setProperty by Expression}
- A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}.
-To name this functions, similar to previous case we use the owner object and a substring of expression inside the brackets.
-
-%jQuery.fn["inner" + name] = function() {
-%dojo[dojo._defaultXhr ? "_defaultXhr" : "xhr"] = function
-%scope[this.triggerEvent]
-
-\subsubsection{Case 7: setArray}
-We only observed one instance of this form in the studied projects. The function name consists of the array name with the index like {\small\texttt{foo[0]}}.
-
-\subsubsection{Case 8: setVariable }
+\subsection{Case 6:  Property Assignment With  Property Name Expressions}
+Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
+ A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values.
+Unlike Case 5, the property name expression need not be a simple developer-invented identifier.
+We will need to process the expression to balance length with information.
+
+Notice that from the programming language point of view, Cases 3 through 6 are all special cases of Case 6.
+After all we are just selecting an object property in all of these cases.
+But from a naming point of view these cases present different challenges and the more complex cases will make our necessary tradeoffs more costly.
+
+\subsection{Case 7: Assignment to an Element of an Array}
+We only observed one instance of this form in the studied projects. The numerical index should clearly be part of the name; the array name may be an expression that we have to analyze to create name.
+
+\subsection{Case 8: Assignment to a Variable }
 As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
 and its internal scopes.
-Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name is the local function name.
-Therefore, for this group of functions the variable name is used as the function name.
-
-\subsubsection{Case 9: Called}
-Calling functions objects just after their creations is a common pattern in JavaScript.
-This pattern is usually used for building modules employing the closure feature in JavaScript.
-Although the function object usage is only limited to this call, functions inside the closure function(The function is being called) has access to the properties in the closure scope in the future calls.
+Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name works will as the function name.
+
+\subsection{Case 9: Anonymous Functions Immediately Called}
+Calling functions objects just after their creations is a common pattern in JavaScript. This pattern is usually used for building modules employing the closure feature in JavaScript.
+In this pattern, the called or outer function provides a scope for function and object definition; functions defined inside of the called-function  have access to the properties in the closure scope in the future calls.
+The outer function is often not explicitly named and in some cases the return value is not assigned.
+
+If the called-function is assigned to a variable or object property, then we have a version of one of the other cases in Table~\ref{function-types}.
+The difference here is that we can tell from static analysis that the assignment will use the return value of the function, not the function object itself.
+But for naming purposes the key information will be the assignment target.
 
 If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
-In this case, we name the function {\small\texttt{Closure}}.
-If the function returns a value and it is assinged to {\small\texttt{foo}}, we name the function {\small\texttt{fooClosure}}.
-
-\subsubsection{Case 10: Returned}
+In this case we can't use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name.
+To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.
+
+\subsection{Case 10: Returned From a Function Call}
 Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
-Many constructors are build by this form and therefore the name of these functions appear in object summaries.
-
-If the function is returned from a function which is just called after its creation(case 9), and the result is assigned to {\small\texttt{foo}}, we name the function {\small\texttt{foo}}.
-Otherwise, if the name of outer function is {\small\texttt{foo}}, we name the function {\small\texttt{fooResult}}.
+Many constructors are built using this form and therefore the names of these functions appear in object summaries.
+
+One important special case are functions returned from functions which are immediately called (Case 9).  For example, XXX.
 
@@
 
-\subsubsection{Case 11: as an Argument}
+\subsection{Case 11: Function passed as an Argument}
 Numbers in table~\ref{function-type-count} show that creating and passing functions as arguments is very common in JavaScript.
@@
 The calling function and the other arguments look helpful, to the extent that they have identifiers invented by the developer.
-As in the the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in the example are highly specific to the function body.
+As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.
+This important case will stress any naming algorithm: we somehow have to summarize the function call -- which itself may be an expression -- and the other arguments -- any or all of which may be expressions.
+
+\subsection{Results of studying examples}
+We reached two main conclusions from studying the way anonymous functions are used in the source of the 10 projects we examined.
+First, we want to try to find the name of the initializer or assignment target that will receive the function object created from a function body.
+JavaScript programmers are creating anonymous functions but they are loading them into object references and the expressions that result in those references have informative identifiers inside.
+Second, these expressions that we focus on may often be simple identifiers, but if they don't we will need to analyze the source of these expressions to extract meaningful summaries.
+This summary has to balance information against length.
+
+Overlaying our analysis above is hierarchy: any of the cases can be nested in function scopes.
+Obviously this hierarchy must be represented in our names.
+Algorithmically this is straight forward recursion.
+But from the name usability point of view, deep hierarchy means long names, exactly the problem we want to avoid.
+Fortunately developers are well trained in dealing with this kind of problem and we anticipate  that hierarchical names can be shown to users in progressive depth depending on the particular needs in the user interface.
 
@@
 \section{Static  Function Object Consumption}
-
-We call our automated naming solution "Static Function Object Consumption", since it relies only on a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by binding to an object property, variable reference, or function argument.
+Using our analysis we have created a preliminary automatic naming solution.  
+We call our automated naming solution "Static Function Object Consumption", since it relies only on a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by assignment to or initialization of  an object property, variable reference, or function argument.
 Static Function Object Consumption generalizes the built-in JavaScript naming and common, simple coding patterns like object property initializers and variable assignments typically recognized by developers as naming functions.

### 2011-04-10 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
A new category of function objects is added to section 4.

@@
 \keywords
-JavaScript, Function Name, Debugger
+JavaScript, Anonymous Function Name, Debugger
 
@@
 \centering
-\scalebox{0.9}{
+\scalebox{0.8}{
   \begin{tabular}{ | l | l | l | l | l |}
@@
 
-For this purpose we created 11 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 11 cases, giving the numerical results in Table~\ref{function-type-count}.
+For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.
 Then we examine each of these cases to think about how we want the functions named.
@@
 	 2 &
-	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}assigned to a(n)\end{rotate}}
+	 & \multirow{8}{*}{\hspace{.2cm}\begin{rotate}{90}is assigned to a(n)\end{rotate}}
 	 & \multicolumn{2}{|m{2.8cm}|}{
@@
 
-   3 &
+   3 & \multirow{12}{*}{\hspace{.2cm}\begin{rotate}{90}The function object\end{rotate}} 
    & 
    &  
-   & direct access.
+   & direct access by a property identifier.
    & bar\textsuperscript{*}.foo = function()\{...\}\\
@@
 
-   4 & \multirow{11}{*}{\hspace{.2cm}\begin{rotate}{90}The function object is\end{rotate}} 
+   4 & 
    & 
@@
    & \multicolumn{3}{|m{3.8cm}|}{
-     \raggedright directly called.}
+     \raggedright is directly called.}
    & function()\{...\}() \\
@@
    10 &
+   & \multicolumn{3}{|m{3.8cm}|}{
+     \raggedright property is accessed.}
+   & function()\{...\}.foo \\
+   \cline{0-0}\cline{3-6}
+
+   11 &
    & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright returned from a function call.}
+     \raggedright is returned from a function call.}
    & \{... return function()\{...\}\} \\
@@
 
-   11 &
+   12 &
    & \multicolumn{3}{|m{3.5cm}|}{
-     \raggedright passed as an argument to a function.}
+     \raggedright is passed as an argument to a function.}
    & foo\textsuperscript{*}(..., function()\{\}, ...) \\
@@
     }
-\caption{Different cases of function object creation and usage in JavaScript.
+\caption{Different cases of anonymous function object creation and usage in JavaScript.
 Identifiers with a star in the table can be expressions as well as simple identifiers; we explain how we reduce expressions to pseudo-identifier in ~\ref{sec:general-element-naming}.}
@@
 \centering
-  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l |}
-  \hline
-     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 \\ 
-  \hline 
-   Closure       & 23(0.3\%)  & 0  & 8465(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%)& 16(0.2\%)& 43(0.5\%)& 365(4\%)\\ 
-  \hline 
-   DOJO          & 9599(61\%) & 6  & 1762(11\%) & 21 & 22 & 2  & 1 & 1143(7\%)& 471(3\%) & 169(1\%) & 2644(17\%) \\ 
-  \hline 
-   ExtJS         & 30221(83\%)& 10  & 1476(4\%)  & 3  & 16 & 9  & 0 & 820(2\%) & 788(2\%) & 509(1\%) & 2617(7\%) \\ 
-  \hline 
-   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 0  & 0  & 0 & 14(0.4\%)& 7(0.2\%) & 6(0.2\%) & 149(5\%) \\ 
-  \hline 
-   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 9(2\%)   & 0        & 86(21\%)  \\ 
-  \hline 
-   MochiKit      & 1080(59\%) & 0  & 383(21\%)  & 0  & 2  & 0  & 0 & 106(6\%) & 18(1\%)  & 41(2\%)  & 181(10\%) \\ 
-  \hline 
-   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 14(2\%)  & 105(17\%) \\ 
-  \hline 
-   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 8(2\%)   & 71(16\%) \\ 
-  \hline 
-   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 9(1\%)   & 160(18\%) \\ 
-  \hline 
-   YUI           & 14154(66\%)& 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%)& 172(1\%) & 95(0.5\%)& 4004(19\%)\\ 
-  \hline 
-   All           & 58774(65\%)& 23 & 14562(16\%)& 28 & 150& 19 & 1 & 3460(4\%)& 1591(2\%)& 894(1\%) & 10382(12\%) \\ 
+\scalebox{0.9}{
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+     & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12\\ 
+  \hline 
+   Closure       & 23(0.3\%)  & 0  & 8466(94\%) & 3  & 4  & 0  & 0 & 67(0.7\%) & 16(0.2\%) & 0  & 43(0.5\%) & 365(4\%)\\ 
+  \hline 
+   DOJO          & 9601(61\%) & 7  & 1765(11\%) & 21 & 24 & 2  & 1 & 1151(7\%) & 476(3\%) & 2  & 175(1\%) & 2641(17\%) \\ 
+  \hline 
+   ExtJS         & 30221(83\%) & 0  & 1476(4\%)  & 3  & 40 & 9  & 0 & 859(2\%) & 788(2\%) & 180  & 517(1\%) & 2439(7\%) \\ 
+  \hline 
+   Firebug       & 2296(76\%) & 0  & 539(18\%)  & 1  & 2  & 0  & 0 & 17(0.4\%) & 7(0.2\%) & 2  & 6(0.2\%) & 148(5\%) \\ 
+  \hline 
+   jQuery        & 233(58\%)  & 0  & 34(9\%)    & 0  & 10 & 2  & 0 & 24(6\%)  & 10(2\%)   & 0  & 0        & 86(21\%)  \\ 
+  \hline 
+   MochiKit      & 1080(59\%) & 10  & 385(21\%)  & 0  & 4  & 0  & 0 & 110(6\%) & 18(1\%)  & 0  & 41(2\%)  & 181(10\%) \\ 
+  \hline 
+   MooTools      & 339(55\%)  & 0  & 79(13\%)   & 0  & 4  & 3  & 0 & 53(9\%)  & 21(3\%)  & 20  & 14(2\%)  & 85(13\%) \\ 
+  \hline 
+   Prototype     & 265(60\%)  & 0  & 28(6\%)    & 0  & 0  & 1  & 0 & 25(6\%)  & 44(10\%) & 1  & 8(2\%)   & 70(16\%) \\ 
+  \hline 
+   Scriptaculous & 564(64\%)  & 0  & 75(8\%)    & 0  & 2  & 2  & 0 & 27(3\%)  & 45(5\%)  & 21  & 9(1\%)   & 139(15\%) \\ 
+  \hline 
+   YUI           & 14154(66\%) & 7  & 1721(8\%)  & 0  & 90 & 0  & 0 & 1181(6\%) & 172(1\%) & 0  & 95(0.5\%) & 4004(19\%)\\ 
+  \hline 
+   All           & 58776(65\%)& 24 & 14568(16\%)& 28 & 180& 19 & 1 & 3514(4\%)& 1597(2\%)& 226  & 908(1\%) & 10072(11\%) \\ 
   \hline 
   \end{tabular}
+}
 \caption{The number of nameless functions in each category defined in table~\ref{table:function-types}.}
@@
 
-\subsection{Case 11: Function passed as an Argument}
+\subsection{Case 11: Function Property is Accessd}
+This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or an agumented function to {\small\texttt{Function}} object prototype is called.
+
+\subsection{Case 12: Function Passed as an Argument}
 Numbers in table~\ref{function-type-count} show that creating and passing functions as arguments is very common in JavaScript.
@@
 Once the summary is ready we construct the identifier.
-The identifiers come from function calls (case 11) are ignored if there is any other type of identifier.
+The identifiers come from function calls (case 12) are ignored if there is any other type of identifier.
 Otherwise, only the closest function call identifier will be used.
@@
 For rows 7 and 8 we put out the identifier followed by a slash (/), the traditional separator in a containment hierarchy.
-For rows 9-11 the identifier is followed by a left angle bracket (<) indicating 'contributes to'.
+For rows 9-12 the identifier is followed by a left angle bracket (<) indicating 'contributes to'.
 

### 2011-04-11 papers/splash-wavefront2011/sigplanconf-template.tex
evaluation tables are updated.

@@
 
+\begin{table}
+
+\centering
+\scalebox{0.8}{
+  \begin{tabular}{ | l | l | l | l | l |}
+  \hline
+   Project & Description & Total & Named \\ 
+  \hline 
+   Closure & Google Web Library & 9195 & 208(2\%) \\ 
+  \hline 
+   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
+  \hline 
+   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
+  \hline 
+   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
+  \hline 
+   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
+  \hline 
+   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
+  \hline 
+   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
+  \hline 
+   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
+  \hline 
+   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
+  \hline 
+   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
+  \hline 
+   All &  & 96008 & 6008(6.3\%) \\ 
+  \hline 
+  \end{tabular}
+  }
+\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.} 
+\label{js-functions} 
+\end{table}
+
 %\section{The Nameless Function Problem}
@@
 So what do JavaScript developers do in practice?
-To get empirical evidence we analyzed the source code of ten well-known JavaScript projects.
+To get empirical evidence we analyzed the source code of ten well-known JavaScript projects \footnote[1]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}.
 For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}.
@@
 Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
-
-\begin{table}
-\centering
-\scalebox{0.9}{
-  \begin{tabular}{ | l | l | l | l | l |}
-  \hline
-   Project & Description & Total & Named \\ 
-  \hline 
-   Closure & Google Web Library & 9195 & 208(2\%) \\ 
-  \hline 
-   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
-  \hline 
-   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
-  \hline 
-   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
-  \hline 
-   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
-  \hline 
-   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
-  \hline 
-   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
-  \hline 
-   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
-  \hline 
-   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
-  \hline 
-   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
-  \hline 
-   All &  & 96008 & 6008(6.3\%) \\ 
-  \hline 
-  \end{tabular}
-  }
-\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.}
-\label{js-functions} 
-\end{table}
 
@@
 
-For this purpose we created 11 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 11 cases, giving the numerical results in Table~\ref{function-type-count}.
+For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.
 Then we examine each of these cases to think about how we want the functions named.
+We'll ignore nesting of function scopes in the analysis to avoid taking on too much at one time.
 
@@
 
-\subsubsection{Case3: setProperty by Direct Access }
+\subsection{Case 3: Property Assignment With Property Identifier }
 This case is the second most common case in the studied projects.
@@
 
-\subsubsection{Case 11: as an Argument}
+\subsection{Case 11: Function Property is Accessd}
+This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or an agumented function to {\small\texttt{Function}} object prototype is called.
+
+\subsection{Case 12: Function Passed as an Argument}
 Numbers in table~\ref{function-type-count} show that creating and passing functions as arguments is very common in JavaScript.
@@
 The calling function and the other arguments look helpful, to the extent that they have identifiers invented by the developer.
-As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in the example are highly specific to the function body.
+As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.
+This important case will stress any naming algorithm: we somehow have to summarize the function call -- which itself may be an expression -- and the other arguments -- any or all of which may be expressions.
+
+\subsection{Results of studying examples}
+We reached two main conclusions from studying the way anonymous functions are used in the source of the 10 projects we examined.
+First, we want to try to find the name of the initializer or assignment target that will receive the function object created from a function body.
+JavaScript programmers are creating anonymous functions but they are loading them into object references and the expressions that result in those references have informative identifiers inside.
+Second, these expressions that we focus on may often be simple identifiers, but if they don't we will need to analyze the source of these expressions to extract meaningful summaries.
+This summary has to balance information against length.
+
+Overlaying our analysis above is hierarchy: any of the cases can be nested in function scopes.
+Obviously this hierarchy must be represented in our names.
+Algorithmically this is straight forward recursion.
+But from the name usability point of view, deep hierarchy means long names, exactly the problem we want to avoid.
+Fortunately developers are well trained in dealing with this kind of problem and we anticipate  that hierarchical names can be shown to users in progressive depth depending on the particular needs in the user interface.
 
@@
 We parse the JavaScript and search the resulting syntax tree for function body nodes.
-For each function body, we apply the algorithm outlined in Algorithm~\ref{alg1}).
+For each function body, we apply the algorithm outlined in Algorithm ~\ref{alg1}.
 The basic idea is to look for parent nodes with helpful identifiers as outlined in  Table~\ref{table:node-types}.
@@
 
+\begin{table}
+\centering
+\scalebox{0.8}{
+  \begin{tabular}{ | l | l | l | l | l |}
+  \hline
+   Project & NoName & Freq=1 & Freq\textless=2 & Avg/lng Len  \\ 
+  \hline 
+   Closure & 10 & 8874(99\%) & 8960(99.7\%) & 35/101 \\ 
+  \hline 
+   DoJo & 390 & 13189(83\%) & 13761(87\%) & 36/162 \\ 
+  \hline 
+   ExtJS & 231 & 33960(93\%) & 35240(96\%)  & 25/91\\ 
+  \hline 
+   Firebug & 10 & 2976(99\%) & 3002(99.5\%) & 36/140 \\ 
+  \hline 
+   jQuery & 8  & 335(84\%) & 381(95\%) & 18/65 \\ 
+  \hline 
+   MochiKit &  16 & 1622(89\%) & 1714(84\%) & 22/80 \\ 
+  \hline 
+   MooTools & 18  & 462(75\%) & 546(88\%) & 14/73 \\ 
+  \hline 
+   Prototype & 19  & 353(80\%) & 383(87\%) & 25/88 \\ 
+  \hline 
+   Scriptaculous &  19 & 779(88\%) & 819(93\%) & 27/132 \\ 
+  \hline 
+   YUI & 15 & 19204(90\%) & 20298(95\%)  & 37/145 \\ 
+  \hline 
+   All & 736(1\%) & 81754(91\%) & 85104(95\%) &  \\ 
+  \hline 
+  \end{tabular}
+  }
+ \label{firebug} 
+\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longes length of produced names for each project.}
+\end{table}    
+\subsection{Produced Names Characteristics}
+
 \subsection{Developers' vs. Automated Names}
@@
 \centering
-\scalebox{0.9}{
-  \begin{tabular}{ | l | l | l | l | l |}
-  \hline
-   Project & Similar & Different & UnNamed \\ 
-  \hline 
-   Closure & 8524(1\%) & 9195 & 516(2\%) \\ 
-  \hline 
-   DoJo & 12180(1\%) & 9195 & 5780(2\%) \\ 
-  \hline 
-   ExtJS & 100(1\%) & 9195 & 208(2\%) \\ 
-  \hline 
-   Firebug & 2901(1\%) & 9195 & 494(0\%) \\ 
-  \hline 
-   jQuery & 283(1\%) & 9195 & 117(0\%) \\ 
-  \hline 
-   MochiKit &  1568(1\%) & 9195 & 234(2\%) \\ 
-  \hline 
-   MooTools & 440(1\%) & 9195 & 128(2\%) \\ 
-  \hline 
-   Prototype & 292(1\%) & 9195 & 326(0\%) \\ 
-  \hline 
-   Scriptaculous &  100(1\%) & 9195 & 397(2\%) \\ 
-  \hline 
-   YUI &  11248(1\%) & 9195 & 3702(2\%) \\ 
-  \hline 
-   All & 100(1\%) & 9195 & 208(2\%) \\ 
+\scalebox{0.8}{
+  \begin{tabular}{ | l | l | l | l |}
+  \hline
+   Project & Equal & Similar & Fbug NoName  \\ 
+  \hline 
+   Closure & 5 & 8528(95\%) & 312(3\%) \\ 
+  \hline 
+   DoJo & 1853(12\%) & 12182(77\%) & 3362(2\%)  \\ 
+  \hline 
+   ExtJS & 3376(9\%) & 17579(48\%) & 1543(4\%)  \\ 
+  \hline 
+   Firebug & 271(9\%) & 2839(94\%) & 167(5\%)  \\ 
+  \hline 
+   jQuery & 119(30\%) & 282(70\%) & 95(24\%) \\ 
+  \hline 
+   MochiKit & 609(33\%) &  1568(86\%) & 202(11\%) \\ 
+  \hline 
+   MooTools & 250(40\%) & 446(72\%) & 121(19\%)  \\ 
+  \hline 
+   Prototype & 33(7\%) & 310(70\%) & 125(28\%)  \\ 
+  \hline 
+   Scriptaculous & 36(4\%) &  652(74\%) & 195(22\%)  \\ 
+  \hline 
+   YUI & 51 &  11808(55\%) & 3317(15\%) \\ 
+  \hline 
+   All & 6603(7\%) & 56194(62\%) & 9439(10\%) \\ 
   \hline 
@@
  \label{firebug} 
-\caption{Number of similar, and different function names in comparison to Firebug {\small \texttt{guessFunctionName()}}.}
+\caption{Number of functions received the same or similar names to FOC approach and no name by Firebug {\small \texttt{guessFunctionName()}}.}
 \end{table}

### 2011-04-11 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
notes from our IRC verbatim

@@
 Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
-
-\begin{table}
-\centering
-\scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l |}
-  \hline
-   Project & Description & Total & Named \\ 
-  \hline 
-   Closure & Google Web Library & 9195 & 208(2\%) \\ 
-  \hline 
-   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
-  \hline 
-   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
-  \hline 
-   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
-  \hline 
-   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
-  \hline 
-   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
-  \hline 
-   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
-  \hline 
-   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
-  \hline 
-   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
-  \hline 
-   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
-  \hline 
-   All &  & 96008 & 6008(6.3\%) \\ 
-  \hline 
-  \end{tabular}
-  }
-\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.}
-\label{js-functions} 
-\end{table}
 
@@
 Next we rank the collected identifiers and strings to elide less relevant data from the summary. 
+\begin{verbatim}
+	salmir	if during the walking up we reach a "return" node and the outer function is a "closure function" we jump to the parent node of "closure function"
+	johnjbarton	inside the while correct?
+	salmir	right.
+	salmir	there is also another effect, but not in the algorithm. The parent context name will become the closure functions parent context name.
+johnjbarton	can we handle this case with the end of the while loop:
+	johnjbarton	n = n.parent
+	salmir	yes.
+	johnjbarton	to
+	johnjbarton	n = getNextNode(n)
+	salmir	getParentNode();
+	johnjbarton	then explain getNextNode is either n.parent or the funky other thing
+
+		so now we are done with the summary and we process it with another algorithm
+	salmir	yes.drop case 2 unless we have at least one of 1 or 3?
+	salmir	yes.
+	johnjbarton	why?because the name from the function call is less valuable than the target
+	salmir	because those identifiers give some information about the function object directly, but the function calls are indirect.
+johnjbarton	ok we need an example for both paths
+salmir	line 13
+	salmir	we drop op()
+	salmir	for the other case when we keep function call, you can use figure 4.
+	salmir	jquery example.
+	johnjbarton	which one, inner or outer
+	salmir	inner
+	johnjbarton	I don't see it
+	salmir	right, outer.
+
+salmir	if there are more than on function call we just use the closes one to the function defintion.
+	salmir	foo(bar(baz("MyFun", function(){})) -> baz[MyFun]()
+	johnjbarton	so if we have two case 2 and zero 1 or 3, then pick the early case 2?
+	salmir	yes.
+
+johnjbarton	so the next step is to concatenate
+	johnjbarton	and you just remove dups or?
+	salmir	just that.
+	johnjbarton	and the reason for << is no identifier is found
+	salmir	yes, or internal nodes.
+	johnjbarton	what is an internal node?>
+	salmir	foo(bar(baz((function(){})))
+	salmir	<<<
+	salmir	myObject = foo(bar(baz((function(){})))
+        salmir	here foo, bar baz all are internal nodes.
+	salmir	so we just get myObject< as name
+\end{verbatim}
 Finally we concatenate the items with marker symbols to construct a string from the consumption summary.

### 2011-04-11 papers/splash-wavefront2011/sigplanconf-template.tex
evaluation table is updated.

@@
 
-\begin{table}
+\begin{table*}
 \centering
 \scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l |}
-  \hline
-   Project & NoName & Freq=1 & Freq\textless=2 & Avg/lng Len  \\ 
-  \hline 
-   Closure & 10 & 8874(99\%) & 8960(99.7\%) & 35/101 \\ 
-  \hline 
-   DoJo & 390 & 13189(83\%) & 13761(87\%) & 36/162 \\ 
-  \hline 
-   ExtJS & 231 & 33960(93\%) & 35240(96\%)  & 25/91\\ 
-  \hline 
-   Firebug & 10 & 2976(99\%) & 3002(99.5\%) & 36/140 \\ 
-  \hline 
-   jQuery & 8  & 335(84\%) & 381(95\%) & 18/65 \\ 
-  \hline 
-   MochiKit &  16 & 1622(89\%) & 1714(84\%) & 22/80 \\ 
-  \hline 
-   MooTools & 18  & 462(75\%) & 546(88\%) & 14/73 \\ 
-  \hline 
-   Prototype & 19  & 353(80\%) & 383(87\%) & 25/88 \\ 
-  \hline 
-   Scriptaculous &  19 & 779(88\%) & 819(93\%) & 27/132 \\ 
-  \hline 
-   YUI & 15 & 19204(90\%) & 20298(95\%)  & 37/145 \\ 
-  \hline 
-   All & 736(1\%) & 81754(91\%) & 85104(95\%) &  \\ 
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+   Project       & Anonymous &  FBUG NoName   & NoName   & NoShortName &    = FBUG Name       &    ~ FBUG Name        & Duplicates  & Avg/lng       & Avg/lng  \\ 
+  \hline 
+   Closure       & 8987      &   312(3\%)     & 10       &  51         &    66(0.7\%)         &    8528(95\%)         & 113(1\%)    & 33/76         & 35/101 \\ 
+  \hline 
+   DoJo          & 15866     &   3362(2\%)    & 390      &  528        &    3067(19\%)        &    12182(77\%)        & 2677(17\%)  & 35/81         & 36/162 \\ 
+  \hline 
+   ExtJS         & 36533     &   1543(4\%)    & 231      &  631        &    4007(11\%)        &    17579(48\%)        & 2573(7\%)   & 22/65         & 25/91  \\ 
+  \hline 
+   Firebug       & 3018      &   167(5\%)     & 10       &  14         &    397(13\%)         &    2839(94\%)         & 2976(1\%)   & 27/70         & 36/140 \\ 
+  \hline 
+   jQuery        & 399       &   95(24\%)     & 8        &  9          &    151(38\%)         &    282(70\%)          & 64(16\%)    & 14/50         & 18/65  \\ 
+  \hline 
+   MochiKit      & 1829      &   202(11\%)    & 16       &  59         &    779(43\%)         &    1568(86\%)         & 207(11\%)   & 17/49         & 22/80   \\ 
+  \hline 
+   MooTools      & 618       &   121(19\%)    & 18       &  30         &    266(43\%)         &    446(72\%)          & 156(25\%)   & 12/36         & 14/73   \\ 
+  \hline 
+   Prototype     & 442       &   125(28\%)    & 19       &  24         &    38(0.8\%)         &    310(70\%)          & 89(20\%)    & 23/55         & 25/88    \\ 
+  \hline  
+   Scriptaculous & 884       &   195(22\%)    & 19       &  25         &    79(0.8\%)         &    652(74\%)          & 105(12\%)   & 22/55         & 27/132   \\ 
+  \hline    
+   YUI           & 21424     &   3317(15\%)   & 15       &  212        &    4846(23\%)        &    11808(55\%)        & 2220(10\%)  & 16/114         & 37/145  \\ 
+  \hline 
+   All           & 90000     &   9439(10\%)   & 736(1\%) &  1583(2\%)  &    13696(15\%)       &    56194(62\%)        & 8264(9\%)   &                &          \\ 
   \hline       
@@
  \label{firebug} 
-\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longes length of produced names for each project.}
-\end{table}    
+\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longest length of produced names for each project.}
+\end{table*}    
 \subsection{Produced Names Characteristics}
@@
 Firebug is not able to name about 15\% of functions. In 35\% of functions the results are different. In most cases, the proposed name by Firebug is the name of another function and is wrong.
-
-\begin{table}
-\centering
-\scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l |}
-  \hline
-   Project & Equal & Similar & Fbug NoName  \\ 
-  \hline 
-   Closure & 5 & 8528(95\%) & 312(3\%) \\ 
-  \hline 
-   DoJo & 1853(12\%) & 12182(77\%) & 3362(2\%)  \\ 
-  \hline 
-   ExtJS & 3376(9\%) & 17579(48\%) & 1543(4\%)  \\ 
-  \hline 
-   Firebug & 271(9\%) & 2839(94\%) & 167(5\%)  \\ 
-  \hline 
-   jQuery & 119(30\%) & 282(70\%) & 95(24\%) \\ 
-  \hline 
-   MochiKit & 609(33\%) &  1568(86\%) & 202(11\%) \\ 
-  \hline 
-   MooTools & 250(40\%) & 446(72\%) & 121(19\%)  \\ 
-  \hline 
-   Prototype & 33(7\%) & 310(70\%) & 125(28\%)  \\ 
-  \hline 
-   Scriptaculous & 36(4\%) &  652(74\%) & 195(22\%)  \\ 
-  \hline 
-   YUI & 51 &  11808(55\%) & 3317(15\%) \\ 
-  \hline 
-   All & 6603(7\%) & 56194(62\%) & 9439(10\%) \\ 
-  \hline 
-  \end{tabular}
-  }
- \label{firebug} 
-\caption{Number of functions received the same or similar names to FOC approach and no name by Firebug {\small \texttt{guessFunctionName()}}.}
-\end{table}
 

### 2011-04-11 trunk/papers/splash-wavefront2011/sigplanconf-template.tex

@@
 \centering
-\scalebox{0.9}{
+\scalebox{0.8}{
   \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l | l | l |}
@@
 
-\section{evaluation}
-
-\begin{table}
+\begin{table*}
 \centering
 \scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l |}
-  \hline
-   Project & NoName & Freq=1 & Freq\textless=2 & Avg/lng Len  \\ 
-  \hline 
-   Closure & 10 & 8874(99\%) & 8960(99.7\%) & 35/101 \\ 
-  \hline 
-   DoJo & 390 & 13189(83\%) & 13761(87\%) & 36/162 \\ 
-  \hline 
-   ExtJS & 231 & 33960(93\%) & 35240(96\%)  & 25/91\\ 
-  \hline 
-   Firebug & 10 & 2976(99\%) & 3002(99.5\%) & 36/140 \\ 
-  \hline 
-   jQuery & 8  & 335(84\%) & 381(95\%) & 18/65 \\ 
-  \hline 
-   MochiKit &  16 & 1622(89\%) & 1714(84\%) & 22/80 \\ 
-  \hline 
-   MooTools & 18  & 462(75\%) & 546(88\%) & 14/73 \\ 
-  \hline 
-   Prototype & 19  & 353(80\%) & 383(87\%) & 25/88 \\ 
-  \hline 
-   Scriptaculous &  19 & 779(88\%) & 819(93\%) & 27/132 \\ 
-  \hline 
-   YUI & 15 & 19204(90\%) & 20298(95\%)  & 37/145 \\ 
-  \hline 
-   All & 736(1\%) & 81754(91\%) & 85104(95\%) &  \\ 
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+   Project       & Anonymous &  FBUG NoName   & NoName   & NoShortName &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
+  \hline 
+   Closure       & 8987      &   312(3\%)     & 10       &  51         &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
+  \hline 
+   DoJo          & 15866     &   3362(2\%)    & 390      &  528        &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
+  \hline 
+   ExtJS         & 36533     &   1543(4\%)    & 231      &  631        &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
+  \hline 
+   Firebug       & 3018      &   167(5\%)     & 10       &  14         &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
+  \hline 
+   jQuery        & 399       &   95(24\%)     & 8        &  9          &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
+  \hline 
+   MochiKit      & 1829      &   202(11\%)    & 16       &  59         &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
+  \hline 
+   MooTools      & 618       &   121(19\%)    & 18       &  30         &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
+  \hline 
+   Prototype     & 442       &   125(28\%)    & 19       &  24         &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
+  \hline  
+   Scriptaculous & 884       &   195(22\%)    & 19       &  25         &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
+  \hline    
+   YUI           & 21424     &   3317(15\%)   & 15       &  212        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
+  \hline 
+   All           & 90000     &   9439(10\%)   & 736(1\%) &  1583(2\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   &                &          \\ 
   \hline       
@@
   }
- \label{firebug} 
-\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longes length of produced names for each project.}
-\end{table}    
-\subsection{Produced Names Characteristics}
-
-\subsection{Developers' vs. Automated Names}
-
-\subsection{Compared to Firebug {\large \texttt{guessFunctionName()}}}
-Firebug uses a utility function called {\small \texttt{guessFunctionName()}} to name nameless functions.
-This algorithm used in the function searches lines around the line the function definition line for specific patterns by regular expressions. The
-  first string matches one of the patterns becomes the name of the function. We compared the results of our algorithm to Firebug's in table~\ref{firebug}.
-
-The first column shows, how many functions get similar names by both algorithm. In average, for 60\% of functions both algorithms produce the same names.
-Firebug is not able to name about 15\% of functions. In 35\% of functions the results are different. In most cases, the proposed name by Firebug is the name of another function and is wrong.
-
-\begin{table}
-\centering
-\scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l |}
-  \hline
-   Project & Equal & Similar & Fbug NoName  \\ 
-  \hline 
-   Closure & 5 & 8528(95\%) & 312(3\%) \\ 
-  \hline 
-   DoJo & 1853(12\%) & 12182(77\%) & 3362(2\%)  \\ 
-  \hline 
-   ExtJS & 3376(9\%) & 17579(48\%) & 1543(4\%)  \\ 
-  \hline 
-   Firebug & 271(9\%) & 2839(94\%) & 167(5\%)  \\ 
-  \hline 
-   jQuery & 119(30\%) & 282(70\%) & 95(24\%) \\ 
-  \hline 
-   MochiKit & 609(33\%) &  1568(86\%) & 202(11\%) \\ 
-  \hline 
-   MooTools & 250(40\%) & 446(72\%) & 121(19\%)  \\ 
-  \hline 
-   Prototype & 33(7\%) & 310(70\%) & 125(28\%)  \\ 
-  \hline 
-   Scriptaculous & 36(4\%) &  652(74\%) & 195(22\%)  \\ 
-  \hline 
-   YUI & 51 &  11808(55\%) & 3317(15\%) \\ 
-  \hline 
-   All & 6603(7\%) & 56194(62\%) & 9439(10\%) \\ 
-  \hline 
-  \end{tabular}
-  }
- \label{firebug} 
-\caption{Number of functions received the same or similar names to FOC approach and no name by Firebug {\small \texttt{guessFunctionName()}}.}
-\end{table}
+ \label{evaluation} 
+\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longest length of produced names for each project.}
+\end{table*}
+
+\section{evaluation}
+The purpose of our evaluation is to answer the follwing questions: 1) How effective is the approach in naming anonymous functions?
+2)How the algorithm  improves the current approaches used in available debuggers for inferring anonymous function names?
+3) Are the proposed names are unique to be used as identifiers or conversely what portion of proposed names are duplicated?
+4) Are the proposed names appropriate for user interface presentation?
+
+We compared our results to Firebug naming output.
+Firebug does not use a parser for naming functions, it instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name.
+Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases.
+First column in Table~\ref{evaluation} contains the number of anonymous functions in each project.
+The second column shows the number of functions remained anonymous in Firebug.
+About 10 percent of anonymous functions still remained nameless in Firebug.
+The third column contains the number of functions which remained nameless after applying the static function object consumption algorithm.
+The numbers show that the algorihtm names more than 99 percent of anonymous functions.
+The next column shows how many of functions are named by do not have a short name (i.e., they are named only by their context names).
+
+The fifth and sixth columns compare Firebug names to short names.
+In 15 percent of cases the short name is the same as firbug name.
+The next column shows the number of functions which their short name does not equals to Firebug name but ends with it.
+It means that short names contain more information (e.g., the function class name or parent object name) than Firebug names in 47 percent of cases.
+
+The duplicates column show the number of duplicated function names.
+About 9 percent of inferred names used for more than one function in a file.
+The main source of duplicated names are test cases particularly in DOJO, ExtJS and YUI.
+%the other sources :1) function calls with no hint  2) conditional functions (e.g., based on browser)
+
+The last two columns show the average and longest function name lengths (in characters) for both short and full names. The average length is at most 37 characters.
+
+%\subsection{Produced Names Characteristics}
+%\subsection{Developers' vs. Automated Names}
+%\subsection{Compared to Firebug {\large \texttt{guessFunctionName()}}}
 
 \subsection{Manual Check}
-%Firebug, JQuery,
-
-%JQuery
-% core.js
-
 %namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
@@
 %the function name not very long like google chrome  xxxx.yyy.zzz
+
+%Firebug uses a utility function called {\small \texttt{guessFunctionName()}} to name nameless functions.This algorithm used in the function searches lines around the line the function definition line for specific patterns by regular expressions.
+The  first string matches one of the patterns becomes the name of the function.
+We compared the results of our algorithm to Firebug's in table~\ref{firebug}.
+%The first column shows, how many functions get similar names by both algorithm.
+In average, for 60\% of functions both algorithms produce the same names.
+Firebug is not able to name about 15\% of functions.
+In 35\% of functions the results are different.
+In most cases, the proposed name by Firebug is the name of another function and is wrong.
 

### 2011-04-11 papers/splash-wavefront2011/sigplanconf-template.tex
re-word the algorithm section

--- 2011-04-11 papers/splash-wavefront2011/sigplanconf-template.tex
@@
 \section{Static  Function Object Consumption}
-Using our analysis we have created a preliminary automatic naming solution.  
-We call our automated naming solution "Static Function Object Consumption", since it relies only on a parser (static) and it attempts to name function bodies by tracking the function object created from the body to where the object is 'consumed', for example by assignment to or initialization of  an object property, variable reference, or function argument.
-Static Function Object Consumption generalizes the built-in JavaScript naming and common, simple coding patterns like object property initializers and variable assignments typically recognized by developers as naming functions.
-
-The built-in naming, a function declaration, binds a name in a scope to a function object created from the adjacent function body.
-For example, in  {\small\texttt{function foo() \{return 1;\}}}, the name  {\small\texttt{foo}} is bound the the function body in curly braces.
-Object property initializers bind a object property name to a function created from an adjacent function body.
-For example,  {\small\texttt{var bar = \{foo: function()\{return 2; \}\}}}, sets {\small\texttt{bar.foo}} to a function object created from the body {\small\texttt{\{return 2;\}}}.
-While the language does not associate the function body with the property  {\small\texttt{bar.foo}}, a JavaScript developer would because the created function body initializes the property.
-Similarly, a varible name bound to a function object, such as {\small\texttt{var baz = function()\{return 3; \}}}, is naturally associated with the function body.
-All three of these simple cases share the character that a function body creates a function object which is then bound to an identifier.
-
-Our algorithm applies the same logic: we look at the code preceding the function body to see where the resulting function object will end up, or
-where the object will be \textit{consumed}.
-Along that path we collect or construct identifiers from the developers source code.
-We add some symbols to guide the developer to the function body in complex cases, and we prefix deeply nested function bodies with context names to disambiguate the result.
-For the simple cases of function declaration, object property initialization, and variable initialization the algorithm gives the same results we described above.
+Using our analysis we have created a preliminary automatic naming solution.  The three parts of our solution match three observations for our study. First we apply 
+ \textit{(Static) Function Object Consumption}, which tracks the function object created from a function body to where the object is 'consumed', for example by assignment to or initialization of  an object property, variable reference, or function argument.
+The "static" qualifier just indicates that we will only use a parser.
+Second, we reduce complex expressions to pseudo-identifiers focusing on developer-invented names.
+Third we apply our approach hierarchically to  deal with nested function bodies.
+
+We will describe the details in the next sections.
+In constructing names we realized one additional aspect: as we move from simple object property names to more complex examples, the path of the object consumption is an added bit of information helpful in naming.
+Thus we add some symbols to guide the developer to the function body in complex cases: this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance.
 
@@
 We parse the JavaScript and search the resulting syntax tree for function body nodes.
-For each function body, we apply the algorithm outlined in Algorithm ~\ref{alg1}.
-The basic idea is to look for parent nodes with helpful identifiers as outlined in  Table~\ref{table:node-types}.
-In simple cases the parent node will have a simple identifier; otherwise we construct an identifier from the expression as described in \ref{sec:general-element-naming}.
-At each step we track how the parent and child are related.
-If the parent expression is an array or object literal then the current node value is \textit{partOf} the parent node value.
-Otherwise the node expression value is \textit{theSame} as or different \textit{contributesTo} parent value.
+For each function body, we apply the algorithm outlined in Algorithm~\ref{alg1}.
+The basic idea (the \verb|while| loop) is to walk the syntax tree from the body up through parent nodes until we hit a node that is not a JavaScript expression.
+For each node we create an entry in a list and record in it information about the relationship between the node and its parent.
+We'll use this relationship information in Sec.~\ref{sec:concatenation}.Then for each node  we record developer-invented identifiers related to the destiny of the function object created from the body as outlined in  Table~\ref{table:node-types}.
+For the first and third rows of the table we record the information recursively; for the second row,  assignment node, we record the information after the loop terminates.
 The algorithm ends when we reach a node which is an assignment or a statement which does not return any value (i.e., the node is not an expression).
@@
 
-Next we rank the collected identifiers and strings to elide less relevant data from the summary.
-Finally we concatenate the items with marker symbols to construct a string from the consumption summary.
-The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
-It compactly explains the function object creation, consumption and assignment.
-
-The name is built by the above process does not contain any information about enclosing scopes.
-We call it \textit{local name}.
-We get the function \textit{full name} by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
-This full-name is our function body name.
+The algorithm uses three subroutines: \verb|getNextNode|,  \verb|nameExpression|, and \verb|argSummary|.
+The \verb|getNextNode| routine normally returns \verb|n.parent|, but we also use this point in the algorithm to handle an important special case, function bodies inside of \textit{immediate functions} typically used for modularity or scoping in JavaScript.
+We discuss this case in Sec.~\ref{sec:immediate}.
+The remaining two subroutines construct a pseudo-identifier from the expression as described in \ref{sec:general-element-naming}; they return their argument if it is simply an identifier.
 
@@
    \STATE $summary.add(dataItem)$
-   \STATE $n$ = $n.parent$
+   \STATE $n$ = getNextNode($n$)
 \ENDWHILE
@@
 
-%Moreover, we compute an \textit{id} value for node types appear in table~\ref{table:node-types}.
-If the parent node is an object literal, then the node value is assigned to a named property like {\small\texttt{foo}}.
-In this case we keep {\small\texttt{foo}} as the \textit{id}.
-If the parent node is a function call that the expression value is passed as one of its argument, we reduce the function expression to a name and we keep that as \textit{id}.
-In the case of function call, another value, \textit{hint}, will also be computed from other arguments and stored.
-In the case where the parent node is an assignment we reduce the left side expression to a name and we keep that as \textit{id}.
-
-%The algorithm build a consumption summary for an expression which returns a value.
-A consumption summary is a list of collected information at every not in the tree traversal.
-At every node two items are stored.
-First the relation of the consumed value and the result value.
-The consumed expressions can be part of the result expression like first two cases in table 2.
-The result value might be different from the consumed value like case 3 in table 2.
-Moreover we keep identifiers at every node is one of the constructs in table 2.
-
-%Our function naming algorithm parses the JavaScript and builds a name based on the parse tree.
-Each function body results in a list of identifers and expressions marked with the kind of parse node that contributed them (\ref{sec:nodewalk}).
-Some of the items on the list are dropped if their neighboring items already give better information for the name.
-Then the expressions are converted to pseudo-identifiers (\ref{sec:general-element-naming}).
-Finally the attributes are converted to augmenting symbols on the identifiers while  the list is collapsed to a name\ref{sec:concatenate}.
-
-%The first stage of the algorithm builds a list of identifiers we call the \textit{full-name}, short for \textit{Full Function Object Consumption Name}.
-%The algorithm starts by parsing the JavaScript code in to a syntax tree\cite{XX}, then iterating over each function body in the tree.
-For each function body we look for the path of the function object from creation to consumption.
-We process the abstract syntax tree from the function body node back to the root node in the enclosed function.
-On each step we determine if the next node represents one of the cases presented in Table~\ref{table:function-types}.
-As we go upward in the tree, we keep identifiers and whether the object consumed is the result object (rows 1-6), part of the result object (rows 7-8), or contribute to the result object (rows 9-11).
-Once the summary is ready we construct the identifier.
-The identifiers come from function calls (case 12) are ignored if there is any other type of identifier.
-Otherwise, only the closest function call identifier will be used.
-Nodes which are not one of the type specified in Table~\ref{table:function-types} are ignored.
-
-%Note that two cases, one where the function is a top script element and the second where function is created by {\small\texttt{Function}} constructor do not appear in the table.
-The top script functions can not be anonymous and the functions defined by the constructor can be considered as a regular function body.
-
-%\subsection{Variable Refinement}\subsubsection{Read Variable}\subsubsection{Write Variable}
-
-%examples: toString functions in different classes, myFunction = cond? function(){..} : function(){..} 
-% more than one return
-
-%\subsection{Temporary Variables} %aliases for the same object
+\subsection{Consumption by Immediate Functions}
+\label{sec:immediate}
+JavaScript developers use function scope to dynamically create functions with shared but private state.
+In this pattern, an enclosing function contains a number of function and object definitions and it is called immediately after it is defined.
+We call these functions \textit{immediate functions}.
+For an example, see line 10 of the Listing~\ref{js-code} which is enclosed in the function on line 9.
+If the developer returns a function from this outer, immediate function we want to follow the returned object to where it is consumed.
+
+To keep our core algorithm simple we handle these returns from immediate functions as a special case.
+At the end of each loop in Algorithm~\ref{alg1} at the point marked \verb|getNextNode()| we check to see if our parent is a \verb|return| node.
+If not we return the parent node and the loop continues.
+If we have a \verb|return| node, we look to the parent of the \verb|return| node to see if it is a call (either directly with \verb|()| or via \verb|apply()| or \verb|call()|.
+If so, we know we are returning a function object from an immediate function.
+We return the parent of the immediate function, effectively skipping the intermediate nodes so that the name will reflect the consumption of the return value into the destination of the immediate function.
 
@@
 This work is done during the Object Consumption Summary algorithm in the functions described here:
-\paragraph{Identifiers for Function Arguments (argSummary)} Search for all string nodes in other arguments and concatenated them by ``-'', dropping  characters over 10. 
-\paragraph{Identifiers for Assignments and Function calls (nameExpressions)} This function gets called for nodes resulting from the first 6 rows of Table~{table:function-types}.
+\paragraph{Identifiers for Function Arguments} Search for all string nodes in other arguments and concatenated them by ``-'', dropping  characters over 10.  
+ (This work is on in Algorithm~\ref{alg1} in \verb|argSummary|).
+\paragraph{Identifiers for Assignments and Function calls} This function gets called for nodes resulting from the first 6 rows of Table~\ref{table:function-types}.
 The expressions here will evaluate to a writable address, so we want to extract the most specific developer-invented identifiers from the expression.
-Thus we apply the rules from Table~{expression-reduction}, which starts from the right hand side of the expression;  we skip any JavaScript keywords like \texttt{this} or \text{prototype}.
+Thus we apply the rules from Table~\ref{expression-reduction}, which starts from the right hand side of the expression;  we skip any JavaScript keywords like \texttt{this} or \texttt{prototype}.
 If we encounter any pattern which does not match, for example a function call, we stop.
+(This work is on in Algorithm~\ref{alg1} in \verb|nameExpressions|.)
 
@@
   \hline 
-   Primitive Value & value & value.toString() \\ 
+   Primitive & value & value.toString() \\ 
   \hline 
@@
 
-\subsection{Enclosed By a Closure Function}
-A closure function is called directly after its creation. Therefore a closure function is like a simple block and any static analysis like
-for building object consumption summary and variable refinement can be continued outside a closure function. Every expression which its value
-is returned in the closure function is assigned to the expression that closure function call result is assigned to. Moreover, in cases where the
-function call defines "this" (by apply()) or arguments these variables can be replaced in the function body.
-
 \subsection{Conversion to an Name}
-At this stage of the algorithm we have a list of identifiers with attributes (which row contributed the identifier).
-Next we join the list items using special characters to signal the attributes.
-For identifiers from rows 1-6 of Table~\ref{table:function-types} we put out the identifier followed by a WHAT.
-For rows 7 and 8 we put out the identifier followed by a slash (/), the traditional separator in a containment hierarchy.
-For rows 9-12 the identifier is followed by a left angle bracket (<) indicating 'contributes to'.
+\label{sec:concatenation}
+At this stage of the algorithm we have a list of identifiers with attributes which we want to concatenate to create a name.
+
+First we drop function-call identifiers if we have anything else to use for a name.
+The function-call identifiers typically tell us about a transformation of the function body before it is assigned to an object property or variable.
+The transformation may be used many places in the code, while the assignment target is typically an identifier defined by the developer.
+See for example function on line 14 and the function call on line 13 in the Listing~\ref{js-code}.
+Specifically we drop identifiers from row 2 of table~\ref{table:node-types} in any case where have identifiers from rows 1 or 3.
+The outer function in Fig.~\ref{fig:jQueryEach} illustrates the opposite case, where we don't drop function-call identifier.
+
+Second we concatenate the identifiers with a symbol between each parent and child showing the relationship.  As shown in Algorithm~\ref{alg1},  
+if the parent expression is an array or object literal then the identifier will be marked  as \textit{isPartOf} and we insert a dot character.
+If the identifier was marked as  \textit{isContributesTo} we insert a left angle bracket.
+An identifier marked \textit{isSameAs} is skipped over because we already have identifier information for it.
+Because some entries on the object consumption list are empty strings we may have duplicate symbols.
+Any duplicates are replaced a single symbol.
+The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
+It compactly explains the function object creation, consumption and assignment.
 
@@
 For example, the function on line 9 of Fig.~\ref{fig:js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.
+
+The name is built by the above process does not contain any information about enclosing scopes.
+We call it \textit{local name}.
+We get the function \textit{full name} by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
+This full-name is our function body name.
 
@@
 A namer function works like an assignment in the summary.
-MORE
 
@@
 % as a callback
-
-\subsection{Context Name}
 

### 2011-04-12 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
evaluation and sec 4

@@
 
-\subsection{Case 2: in Array Literal}
+\subsection{Case 2: Entry in an Array Literal}
 Contrary to the previous case the appearance of this case is very limited.
@@
 Among all projects only two have instances of nameless functions defined in this way.
-
-To name the function body defined in an array literal, first we must name the array literal.
-To name the array literal, we consider it as a function body and we employ the same algorithm we use for naming a function body.
-If the array literal receives a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
-
-\subsection{Case 3: Property Assignment With Property Identifier }
+For example array argument to \verb|Event._attach| in this example from YUI:
+\begin{verbatim}
+        _attach: function (el, notifier, delegate) {
+            if (Y.DOM.isWindow(el)) {
+                return Event._attach([type, function (e) {
+                    notifier.fire(e);
+                }, el]);
+            }
+       }
+\end{verbatim}
+(The example is nested in more function definitions we do not show here).
+The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|.
+In general we shall want to name these kinds of functions by the destiny of the containing array.
+
+\subsection{Case 3: Property Assignment With Property Identifier}
 This case is the second most common case in the studied projects.
@@
 The complication in this case comes from the object name: in general the object reference can be a computed expression.
+(This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier).
+Here is a simple example from the Closure project:
+\begin{verbatim}
+  this.eventPool_.createObject = function() {
+    return new goog.debug.Trace_.Event_();
+  };
+\end{verbatim}
  These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small.
-This comment apply to all of the cases in table~\ref{table:function-types} marked with an asterix on the expression identifier.
+For example, \verb|this.| add no information to the name since we can't know the value of \verb|this| while parsing.
 
@@
 \subsection{Case 5: Property Assignment With  Property Name Variable}
-Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we can't statically compute the string to use as a property identifier.
+Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we can't (usually) statically compute the string to use as a property identifier.
 The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
@@
  A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values.
+Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
+\begin{verbatim}
+  function define(D) {
+    if (!element) element = getRootElement();
+    property[D] = 'client' + D;
+    viewport['get' + D] = function() { 
+      return element[property[D]] 
+    };
+    return viewport['get' + D]();
+  }
+\end{verbatim}
+The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.
 Unlike Case 5, the property name expression need not be a simple developer-invented identifier.
-We will need to process the expression to balance length with information.
+In this example, \verb|viewport[getD]| could be a good name, but in general we will need to process the expression to balance length with information.
 
@@
 \subsection{Case 9: Anonymous Functions Immediately Called}
-Calling functions objects just after their creations is a common pattern in JavaScript. This pattern is usually used for building modules employing the closure feature in JavaScript.
-In this pattern, the called or outer function provides a scope for function and object definition; functions defined inside of the called-function  have access to the properties in the closure scope in the future calls.
-The outer function is often not explicitly named and in some cases the return value is not assigned.
+Calling functions objects just after their creations is a common pattern in JavaScript.
+For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example.
+\begin{figure}[htp]
+\begin{verbatim}
+Y.ClassNameManager = function () {
+
+ var sPrefix    = CONFIG[CLASS_NAME_PREFIX],
+   sDelimiter = CONFIG[CLASS_NAME_DELIMITER];
+
+    return {
+       getClassName: Y.cached(function () {
+          var args = Y.Array(arguments);
+          if (args[args.length-1] !== true) {
+              args.unshift(sPrefix);
+          } else {
+              args.pop();
+          }
+          return args.join(sDelimiter);
+      })
+    };
+}();
+\end{verbatim}
+\label{fig:classnamemanager}
+\caption{An example the YUI project of function bodies from cases 9 (the outer function)  and 12  (the argument to Y.cached) from Table~\ref{table:function-types}  }
+\end{figure}
 
@@
 
-\subsection{Case 10: Returned From a Function Call}
+\subsection{Case 10: Function Property is Accessed}
+This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or an argument function to {\small\texttt{Function}} object prototype is called.
+
+\subsection{Case 11:  Returned From a Function Call}
+
 Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
 Many constructors are built using this form and therefore the names of these functions appear in object summaries.
-
-One important special case are functions returned from functions which are immediately called (Case 9).  For example, XXX.
-
-% this is also important as many constructor/classes are made in this way
-
-\subsection{Case 11: Function Property is Accessd}
-This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or an agumented function to {\small\texttt{Function}} object prototype is called.
 
@@
 As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.
+Fig.~\ref{fig:classnamemanager} shows different example, where the function called (\verb|Y.Cached()| seems much less important for naming the function than the property that we initialize with the result of calling the function.
 This important case will stress any naming algorithm: we somehow have to summarize the function call -- which itself may be an expression -- and the other arguments -- any or all of which may be expressions.
@@
 
-Next we rank the collected identifiers and strings to elide less relevant data from the summary. 
-\begin{verbatim}
-	salmir	if during the walking up we reach a "return" node and the outer function is a "closure function" we jump to the parent node of "closure function"
-	johnjbarton	inside the while correct?
-	salmir	right.
-	salmir	there is also another effect, but not in the algorithm. The parent context name will become the closure functions parent context name.
-johnjbarton	can we handle this case with the end of the while loop:
-	johnjbarton	n = n.parent
-	salmir	yes.
-	johnjbarton	to
-	johnjbarton	n = getNextNode(n)
-	salmir	getParentNode();
-	johnjbarton	then explain getNextNode is either n.parent or the funky other thing
-
-		so now we are done with the summary and we process it with another algorithm
-	salmir	yes.drop case 2 unless we have at least one of 1 or 3?
-	salmir	yes.
-	johnjbarton	why?because the name from the function call is less valuable than the target
-	salmir	because those identifiers give some information about the function object directly, but the function calls are indirect.
-johnjbarton	ok we need an example for both paths
-salmir	line 13
-	salmir	we drop op()
-	salmir	for the other case when we keep function call, you can use figure 4.
-	salmir	jquery example.
-	johnjbarton	which one, inner or outer
-	salmir	inner
-	johnjbarton	I don't see it
-	salmir	right, outer.
-
-salmir	if there are more than on function call we just use the closes one to the function defintion.
-	salmir	foo(bar(baz("MyFun", function(){})) -> baz[MyFun]()
-	johnjbarton	so if we have two case 2 and zero 1 or 3, then pick the early case 2?
-	salmir	yes.
-
-johnjbarton	so the next step is to concatenate
-	johnjbarton	and you just remove dups or?
-	salmir	just that.
-	johnjbarton	and the reason for << is no identifier is found
-	salmir	yes, or internal nodes.
-	johnjbarton	what is an internal node?>
-	salmir	foo(bar(baz((function(){})))
-	salmir	<<<
-	salmir	myObject = foo(bar(baz((function(){})))
-        salmir	here foo, bar baz all are internal nodes.
-	salmir	so we just get myObject< as name
-\end{verbatim}
-Finally we concatenate the items with marker symbols to construct a string from the consumption summary.
-The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
-It compactly explains the function object creation, consumption and assignment.
-
-The name is built by the above process does not contain any information about enclosing scopes.
-We call it \textit{local name}.
-We get the function \textit{full name} by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
-This full-name is our function body name.
+The algorithm uses three subroutines: \verb|getNextNode|,  \verb|nameExpression|, and \verb|argSummary|.
+The \verb|getNextNode| routine normally returns \verb|n.parent|, but we also use this point in the algorithm to handle an important special case, function bodies inside of \textit{immediate functions} typically used for modularity or scoping in JavaScript.
+We discuss this case in Sec.~\ref{sec:immediate}.
+The remaining two subroutines construct a pseudo-identifier from the expression as described in \ref{sec:general-element-naming}; they return their argument if it is simply an identifier.
 
@@
 
-\section{Special Cases}
-Given that our goals trade precision for rapid recognition, our names are not unique or perfectly tuned to every developer's need.
-We also leave some cases anonymous.
-We add  few special cases to our algorithm to patch over these issues.
-
-\subsection{Similar Function Names in a File}
-It is conceivable, that function bodies are named with the same names in a file.
-It can happen in different situations.
-One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser).
-For these cases we add a dollar sign and an index to the similar function names.
-For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
-
-\subsection{Namer Functions}
-Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
-These functions usually receive a string as the class name or function name.
-The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
-A namer function works like an assignment in the summary.
-MORE
-
-% to register a function with a name
-% to wrap the function
-% as a callback
-
-\subsection{Context Name}
-
-\subsection{Functions created by {\large \texttt{eval()}}}
-The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is available.
-However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
+The name is built by the above process does not contain any information about enclosing scopes.
+We call it \textit{local name}.
+We get the function \textit{full name} by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
+This full-name is our function body name.
 
@@
  \label{evaluation} 
-\caption{Number of functions remaind anonymous, the number of produced unique function names, the number of produced function names used for at most two functions and the average and longest length of produced names for each project.}
+\caption{Results of Function Object Consumption.
+The rows are the projects listed in Appendix 1.
+First column in  contains the number of anonymous functions in each project.
+The second column shows the number of functions Firebug could not name.
+The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm;  and the fourth column is the number with only a name for enclosing scopes.
+The fifth column give the number of times a FOC function name appears twice in a file and sixth and seventh columns give the average and longest name character counts respectively.
+The last columns have two entries divided by a slash, the first is the local name and the second is the full name.}
 \end{table*}
 
-\section{evaluation}
-The purpose of our evaluation is to answer the follwing questions: 1) How effective is the approach in naming anonymous functions?
-2)How the algorithm  improves the current approaches used in available debuggers for inferring anonymous function names?
+\section{Evaluation}
+The purpose of our evaluation is to answer the following questions: 1) How effective is the approach in naming anonymous functions?
+2) How the algorithm  improves the current approaches used in available debuggers for inferring anonymous function names?
 3) Are the proposed names are unique to be used as identifiers or conversely what portion of proposed names are duplicated?
@@
 
-We compared our results to Firebug naming output.
-Firebug does not use a parser for naming functions, it instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name.
+In Table~\ref{evaluation} We compared our results to Firebug's naming output for each of the 10 projects used previously and listed in Appendix 1.
+Firebug does not use a parser for naming functions.
+It instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name.
 Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases.
-First column in Table~\ref{evaluation} contains the number of anonymous functions in each project.
-The second column shows the number of functions remained anonymous in Firebug.
-About 10 percent of anonymous functions still remained nameless in Firebug.
-The third column contains the number of functions which remained nameless after applying the static function object consumption algorithm.
-The numbers show that the algorihtm names more than 99 percent of anonymous functions.
-The next column shows how many of functions are named by do not have a short name (i.e., they are named only by their context names).
-
-The fifth and sixth columns compare Firebug names to short names.
-In 15 percent of cases the short name is the same as firbug name.
-The next column shows the number of functions which their short name does not equals to Firebug name but ends with it.
-It means that short names contain more information (e.g., the function class name or parent object name) than Firebug names in 47 percent of cases.
+About 10 percent of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).The numbers show that the algorithm names more than 99 percent of the anonymous functions.
 
@@
 
-The last two columns show the average and longest function name lengths (in characters) for both short and full names. The average length is at most 37 characters.
+The last two columns show the average and longest function name lengths (in characters) for both short and full names.
+The average length is at most 37 characters.
+The longest  names are typically long because of a long local name.
 
@@
 
-\section{Disucussion}
+\section{Discussion}
+
+Given that our goals trade precision for rapid recognition, our names are not unique or perfectly tuned to every developer's need.
+We also leave some cases anonymous.
+We add  few special cases to our algorithm to patch over these issues.
+
+\subsection{Similar Function Names in a File}
+It is conceivable, that function bodies are named with the same names in a file.
+It can happen in different situations.
+One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser).
+For these cases we add a dollar sign and an index to the similar function names.
+For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+
+\subsection{Namer Functions}
+Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+These functions usually receive a string as the class name or function name.
+The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
+A namer function works like an assignment in the summary.
+
+% to register a function with a name
+% to wrap the function
+% as a callback
+
+\subsection{Functions created by {\large \texttt{eval()}}}
+The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is available.
+However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
 

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
abstract/conclusion discussion

@@
 \begin{abstract}
-Understanding JavaScript code due to its dynamic, weakly-typed nature is complicated.
-Developers usually comprehend JavaScript programs by running them and examining their elements at runtime.
-However, understanding concrete values, particularly user-defined and function objects, is not always straightforward.
-Function names can aid in this regard; they can appear as the constructor name in object representation or as the function identifier in call-stack.
-Based on our analysis over ten famous JavaScript projects, unfortunately only a very low proportion (less than 7\%) of JavaScript functions are named by developers in the first place.
-As a solution to this problem, we propose an automated approach based on local source code analysis for naming nameless JavaScript functions.
-We applied our approach on several JavaScript projects and the results are very promising.
+JavaScript developers create and call functions; they use functions to construct objects.
+JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations.
+However, developers need not specify names for functions.
+ Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
+By studying examples from these JavaScript projects, we propose Static Function-Object Consumption, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions.
+We applied our approach to these same JavaScript projects and the results are very promising.
 \end{abstract}
@@
 Among all projects only two have instances of nameless functions defined in this way.
-
-To name the function body defined in an array literal, first we must name the array literal.
-To name the array literal, we consider it as a function body and we employ the same algorithm we use for naming a function body.
-If the array literal receives a name like {\small\texttt{foo}}, and the function is defined at index ({\small\texttt{i}}), {{\small\texttt{foo[i]}} is assigned as the function body name.
-
-\subsection{Case 3: Property Assignment With Property Identifier }
+For example array argument to \verb|Event._attach| in this example from YUI:
+\begin{verbatim}
+_attach: function (el, notifier, delegate) {
+  if (Y.DOM.isWindow(el)) {
+    return Event._attach([type, function (e) {
+         notifier.fire(e);
+    }, el]);
+  }
+}
+\end{verbatim}
+(The example is nested in more function definitions we do not show here).
+The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|.
+In general we shall want to name these kinds of functions by the destiny of the containing array.
+
+\subsection{Case 3: Property Assignment With Property Identifier}
 This case is the second most common case in the studied projects.
@@
 
-\section{Special Cases}
-Given that our goals trade precision for rapid recognition, our names are not unique or perfectly tuned to every developer's need.
-We also leave some cases anonymous.
-We add  few special cases to our algorithm to patch over these issues.
-
-\subsection{Similar Function Names in a File}
-It is conceivable, that function bodies are named with the same names in a file.
-It can happen in different situations.
-One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser).
-For these cases we add a dollar sign and an index to the similar function names.
-For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
-
-\subsection{Namer Functions}
-Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
-These functions usually receive a string as the class name or function name.
-The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
-A namer function works like an assignment in the summary.
-
-% to register a function with a name
-% to wrap the function
-% as a callback
-
-\subsection{Functions created by {\large \texttt{eval()}}}
-The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is available.
-However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
-
 %\section{Improved by Runtime Data}
@@
 
-We compared our results to Firebug naming output.
-Firebug does not use a parser for naming functions, it instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name.
+In Table~\ref{evaluation} We compared our results to Firebug's naming output for each of the 10 projects used previously and listed in Appendix 1.
+Firebug does not use a parser for naming functions.
+It instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name  (a function called {\small \texttt{guessFunctionName()}}).
 Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases.
-First column in Table~\ref{evaluation} contains the number of anonymous functions in each project.
-The second column shows the number of functions remained anonymous in Firebug.
-About 10 percent of anonymous functions still remained nameless in Firebug.
-The third column contains the number of functions which remained nameless after applying the static function object consumption algorithm.
-The numbers show that the algorihtm names more than 99 percent of anonymous functions.
-The next column shows how many of functions are named by do not have a short name (i.e., they are named only by their context names).
-
-The fifth and sixth columns compare Firebug names to short names.
-In 15 percent of cases the short name is the same as firbug name.
-The next column shows the number of functions which their short name does not equals to Firebug name but ends with it.
-It means that short names contain more information (e.g., the function class name or parent object name) than Firebug names in 47 percent of cases.
+About 10 percent of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).The numbers show that the algorithm names more than 99 percent of the anonymous functions.
 
@@
 
-\subsection{Manual Check}
+%\subsection{Manual Check}
 %namespaces in JS:http://javascriptweblog.wordpress.com/2010/12/07/namespacing-in-javascript/
@@
 
-\section{Disucussion}
+\section{Discussion}
+Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.
+By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results.
+In other cases FOC will give a more useful name including many cases where the current Firebug approach fails.
+
+There is room for improvements.
+The heuristic elements of the naming solution need to be tuned based on more experience.
+Given that our goals trade precision for rapid recognition, our names are not unique.
+We also leave some cases anonymous which need further investigation.
+
+\subsection{Similar Function Names in a File}
+In some cases function bodies are named with the same names in a file.
+It can happen in different situations.
+One of the common cases is the two different function bodies may assign to a property based on a condition (e.g., the browser).
+For these cases we add a dollar sign and an index to the similar function names.
+For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+
+\subsection{Namer Functions}
+Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+These functions usually receive a string as the class name or function name.
+The number of namer functions is usually very limited for a specific project and can be provided to debugger by the developer.
+A namer function works like an assignment in the summary.
+
+% to register a function with a name
+% to wrap the function
+% as a callback
+
+\subsection{Functions created by {\large \texttt{eval()}}}
+The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is available.
+However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
 
@@
 The ultimate fallback for function names is to allow the developer to specify them manually.
-For applicaiton developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.
-
-\subsection{Limitations}
+For application developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.
+
+%\subsection{Limitations}
 %some long names
@@
 \section{Conclusion}
-We highlighted the problem of anonymous functions in JavaScript. We studied 10 famous JavaScript projects source code. From
-our study we suggested an automatic approach for naming nameless functions that can be used in debuggers for better representation of concrete
-values and functions in the call-stack.
+Our contributions in this paper include an empirical study of the extent of anonymous functions in JavaScript libraries, categorization of those functions to understand the potential for automatic naming, an practical algorithm based on the empirical study, and its evaluation.
+We believe our results can be applied directly in existing JavaScript development tools to give immediate benefit to developers and they provide a basis for future improvements.
 

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
table 6 is updated. section 2 example and figures are updated.

@@
 So what do JavaScript developers do in practice?
-To get empirical evidence we analyzed the source code of ten well-known JavaScript projects \footnote[1]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}.
+To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}.
 For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}.
@@
 \lstset{basicstyle=\scriptsize}
-\lstset{emph={FOO,BAR},emphstyle=\textit}
+\lstset{emph={FOO,BAR}} %,emphstyle=\bf}
 \lstdefinelanguage{myLang}
-{morekeywords={if, function, var, return, new}}
+{morekeywords={if, function, var, return, new, this}}
 
 \begin{lstlisting}[frame=single, language=myLang]
-9  var main = function() {         // main<
-10   return function() {           // main
-11     var foo = new FOO("a");
-12     var bar = new BAR("b");
-13     var result = op(
-14       function(value){          // main/result<
-15         return value;
-16        });
-17   }
-18 }();
-19 var FOO = function(a) {         // FOO
-20   this.a = a;
-21 }
-22 var BAR = function(b) {         // BAR
-23   this.b = b;
-24 }
-25 var op = function() {           // op<
-26   var local;
-27   return function(callBack) {   // op
-28     local++;
-29     return callBack(local);
-30   }
-31 }();
+9  var main = function() {          // main
+10   var foo = new FOO(            
+11      function(){                 // main/foo<
+12        this.welcome = "Hi!";
+13      });
+14   var bar = new BAR("GoodBye.");
+15   alert(foo.welcome);
+16   alert(bar.message);
+17 };
+18 var FOO = function(){            // FOO<    
+19   var instances;
+20   return function(initializer){  // FOO
+21       instances++;         
+22       initializer.apply(this);
+23     }
+24 }();
+25 var BAZ = BAR = function(msg){   // BAR
+26   this.message = msg;
+27 }
 \end{lstlisting}
@@
 \centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.jpg}}
 \hfil
-\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
+\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.jpg}}}
 \caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
@@
 \subsection{Missed Constructor Name in Object Summary}
-JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call).
+JavaScript does not support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call).
 A constructor is a regular JavaScript function.
@@
 Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue.
-We set a breakpoint on line 13 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
+We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
 Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}.
-However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects.
+However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{BAZ.BAR}} class for {\small\texttt{bar}} as their summaries.
+The first class is very general and the second one is misleading.
 The developer has to expand the object nodes to recognize their similarities and differences.
-Firebug classify objects in the same general class, but includes some of the object properties in the summary.
+Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary.
 These additional properties may hint the developer about the object structures.
-{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
+{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
 
@@
 The second problem is the call-stack.
-To illustrate this, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint.
+To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint.
 Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug.
 The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms.
-Google chrome shows \textit{anonymous} as the name of all functions excepting the first one.
-Firebug performs better by guessing three function names but it still fails in one case.
+Among three last functions in the call stack, Google Chrome only shows the name of one of them({\small\texttt{main}}) correctly.
+For the second function (line 22), it shows \textit{anonymous}, and for the third function (line 12), it gives a wrong name, {\small\texttt{foo}}.
+Firebug performs better by guessing two function names correctly, but it still fails in one case.
+It shows {\small\texttt{main}} as the name of last function(line 12) which is the name of its enclosing function.
 In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.
@@
 \centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
+\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.jpg}}
 \hfil
-\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
+\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.jpg}}}
 \caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
@@
   \hline
-   Project       & Anonymous &  FBUG NoName   & NoName   & NoShortName &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
-  \hline 
-   Closure       & 8987      &   312(3\%)     & 10       &  51         &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
-  \hline 
-   DoJo          & 15866     &   3362(2\%)    & 390      &  528        &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
-  \hline 
-   ExtJS         & 36533     &   1543(4\%)    & 231      &  631        &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
-  \hline 
-   Firebug       & 3018      &   167(5\%)     & 10       &  14         &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
-  \hline 
-   jQuery        & 399       &   95(24\%)     & 8        &  9          &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
-  \hline 
-   MochiKit      & 1829      &   202(11\%)    & 16       &  59         &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
-  \hline 
-   MooTools      & 618       &   121(19\%)    & 18       &  30         &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
-  \hline 
-   Prototype     & 442       &   125(28\%)    & 19       &  24         &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
-  \hline  
-   Scriptaculous & 884       &   195(22\%)    & 19       &  25         &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
-  \hline    
-   YUI           & 21424     &   3317(15\%)   & 15       &  212        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
-  \hline 
-   All           & 90000     &   9439(10\%)   & 736(1\%) &  1583(2\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   &                &          \\ 
+\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Quality}               & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
+  \cline{2-10}
+                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
+  \hline 
+   Closure       & 8987      &   312(3\%)     & 51        & 10        &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
+  \hline 
+   DoJo          & 15866     &   3362(21\%)    & 528       & 390       &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
+  \hline 
+   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
+  \hline 
+   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
+  \hline  
+   jQuery        & 399       &   95(24\%)     & 9         & 8         &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
+  \hline  
+   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
+  \hline 
+   MooTools      & 618       &   121(19\%)    & 30        & 18        &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
+  \hline 
+   Prototype     & 442       &   125(28\%)    & 24        & 19        &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
+  \hline  
+   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
+  \hline    
+   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
+  \hline 
+   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   & N/A            & N/A         \\ 
   \hline       

### 2011-04-12 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
table 1 is updated.

@@
 \scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l |}
-  \hline
-   Project & Description & Total & Named \\ 
-  \hline 
-   Closure & Google Web Library & 9195 & 208(2\%) \\ 
-  \hline 
-   DoJo & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
-  \hline 
-   ExtJS & JavaScript Framework & 37717 & 1184(3\%) \\ 
-  \hline 
-   Firebug & Web Development Tool & 3424 & 406(11\%) \\ 
-  \hline 
-   jQuery & JavaScript Library & 422 & 23(5\%) \\ 
-  \hline 
-   MochiKit &  JavaScript Library & 1866 & 37(1\%) \\ 
-  \hline 
-   MooTools & JavaScript Framework & 625 & 7(1\%) \\ 
-  \hline 
-   Prototype & JavaScript Framework & 645 & 203(31\%) \\ 
-  \hline 
-   Scriptaculous &  JavaScript Library & 1092 & 208(19\%) \\ 
-  \hline 
-   YUI &  Yahoo UI Library & 22346 & 922(4\%) \\ 
-  \hline 
-   All &  & 96008 & 6008(6.3\%) \\ 
+  \begin{tabular}{ | l | l | l | l | l | l |}
+  \hline
+   Project & Ver. & Description & Total & Named \\ 
+  \hline 
+   Closure &  & Google Web Library & 9195 & 208(2\%) \\ 
+  \hline 
+   DoJo & 1.5 & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
+  \hline 
+   ExtJS & 3.3.1 & JavaScript Framework & 37717 & 1184(3\%) \\ 
+  \hline 
+   Firebug & 1.7 & Web Development Tool & 3424 & 406(11\%) \\ 
+  \hline 
+   jQuery & 1.4.4 & JavaScript Library & 422 & 23(5\%) \\ 
+  \hline 
+   MochiKit & 1.4.2 &  JavaScript Library & 1866 & 37(1\%) \\ 
+  \hline 
+   MooTools & 1.3 & JavaScript Framework & 625 & 7(1\%) \\ 
+  \hline 
+   Prototype & 1.7 & JavaScript Framework & 645 & 203(31\%) \\ 
+  \hline 
+   Scriptaculous & 1.9 &  JavaScript Library & 1092 & 208(19\%) \\ 
+  \hline 
+   YUI & 3.3 &  Yahoo UI Library & 22346 & 922(4\%) \\ 
+  \hline 
+   All & N/A & N/A & 96008 & 6008(6.3\%) \\ 
   \hline 
@@
 Firebug does not use a parser for naming functions.
-It instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name.
+It instead employs a number of regular expressions and apply them on a few lines around the function definition to obtain a name  (a function called {\small \texttt{guessFunctionName()}}).
 Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases.
@@
 \section{Discussion}
-
-Given that our goals trade precision for rapid recognition, our names are not unique or perfectly tuned to every developer's need.
-We also leave some cases anonymous.
-We add  few special cases to our algorithm to patch over these issues.
+Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.
+By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results.
+In other cases FOC will give a more useful name including many cases where the current Firebug approach fails.
+
+There is room for improvements.
+The heuristic elements of the naming solution need to be tuned based on more experience.
+Given that our goals trade precision for rapid recognition, our names are not unique.
+We also leave some cases anonymous which need further investigation.
 
 \subsection{Similar Function Names in a File}
-It is conceivable, that function bodies are named with the same names in a file.
+In some cases function bodies are named with the same names in a file.
 It can happen in different situations.

### 2011-04-12 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
add examples for cases 10 11

@@
 
-If the called-function is assigned to a variable or object property, then we have a version of one of the other cases in Table~\ref{function-types}.
+If the called-function is assigned to a variable or object property, then we have a version of one of the other cases in Table~\ref{table:function-types}.
 The difference here is that we can tell from static analysis that the assignment will use the return value of the function, not the function object itself.
@@
 \subsection{Case 10: Function Property is Accessed}
-This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or an argument function to {\small\texttt{Function}} object prototype is called.
+In this unusual case a property of the function is accessed directly from the function body.
+This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or when the predefined functions are augmented by adding to {\small\texttt{Function}} prototype.
+Here is an example, from ExtJS, reformatted for display here:
+\begin{verbatim}
+setVisible : function(v, a, d, c, e){
+    if(v){
+        this.showAction();
+    }
+    if(a && v){
+        var cb = function(){
+            this.sync(true);
+            if(c){
+                c();
+            }
+        }.createDelegate(this);
+   }
+   // .....
+}
+\end{verbatim}
+The inner function body is not used directly, but the result of \verb|createDelegate| is assigned to \verb|cb|.
+The most valuable information here is the variable name \verb|cb|, followed by the \verb|createDelegate| function name.
+This example also illustrates that automatic naming could have an effect on developers coding style:  giving a longer name for \verb|cb| would give better names in development tools but currently developers have limited expectations that tools will show such information.
 
@@
 
+In this case the function body appears in a return statement of another function body.
 Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
 Many constructors are built using this form and therefore the names of these functions appear in object summaries.
+Clearly the name of these returned functions is almost the same as the name of the functions that define them.
+For example, in Fig.~\ref{fig:registerWin} a developer might pick names like \verb|registerWinOnIE| and \verb|registerWinNotOnIE| for the functions returned by the Dojo function \verb|registerWin|.
+\begin{figure*}[htbp]
+\begin{verbatim}
+registerWin: function(targetWindow, effectiveNode){
+  // ...
+  if(doc){
+    if(dojo.isIE){
+      ....
+      return function(){
+        doc.detachEvent('onmousedown', mousedownListener);
+        doc.detachEvent('onactivate', activateListener);
+        doc.detachEvent('ondeactivate', deactivateListener);
+        doc = null;    // prevent memory leak (apparent circular reference via closure)
+      };
+    }else{
+      ....
+      return function(){
+        doc.removeEventListener('mousedown', mousedownListener, true);
+        doc.removeEventListener('focus', focusListener, true);
+        doc.removeEventListener('blur', blurListener, true);
+        doc = null;    // prevent memory leak (apparent circular reference via closure)
+      };
+    }
+  }
+},
+\end{verbatim}
+\label{fig:registerWin}
+\caption{An example of a function body in a return statement, case 11 of Table~\ref{table:function-types}  adapted from the Dojo project code}
+\end{figure*}
 
@@
 Our intuition is that these extra symbols need to be visually compact because their purpose is to adjust the developers expectation for the identifier.
-For example, the function on line 9 of Fig.~\ref{fig:js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.
+For example, the function on line 9 of Fig.~\ref{js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.
 

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
section 2 is updated.

@@
 \lstset{basicstyle=\scriptsize}
-\lstset{emph={FOO,BAR}} %,emphstyle=\bf}
+\lstset{emph={Foo,Bar}} %,emphstyle=\bf}
 \lstdefinelanguage{myLang}
@@
 9  var main = function() {          // main
-10   var foo = new FOO(            
+10   var foo = new Foo(            
 11      function(){                 // main/foo<
@@
 13      });
-14   var bar = new BAR("GoodBye.");
+14   var bar = new Bar("GoodBye.");
 15   alert(foo.welcome);
@@
 17 };
-18 var FOO = function(){            // FOO<    
+18 var Foo = function(){            // Foo<    
 19   var instances;
-20   return function(initializer){  // FOO
+20   return function(initializer){  // Foo
 21       instances++;         
@@
 24 }();
-25 var BAZ = BAR = function(msg){   // BAR
+25 var Baz = Bar = function(msg){   // Bar
 26   this.message = msg;
@@
 \centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.jpg}}
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.png}}
 \hfil
-\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.jpg}}}
+\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.png}}}
 \caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
@@
 We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
-Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}.
-However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{BAZ.BAR}} class for {\small\texttt{bar}} as their summaries.
+Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{Foo}} and {\small\texttt{Bar}}.
+However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{Baz.Bar}} class for {\small\texttt{bar}} as their summaries.
 The first class is very general and the second one is misleading.
@@
 These additional properties may hint the developer about the object structures.
-{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
+{\small\texttt{Foo}} and {\small\texttt{Bar}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
 
@@
 \centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.jpg}}
+\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.png}}
 \hfil
-\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.jpg}}}
+\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.png}}}
 \caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
@@
 
-The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.
+The next two functions, {\small\texttt{Foo}} on line 19 and {\small\texttt{Bar}} on line 22 are simple examples of case 6.
 The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
fixed Examples section

@@
 \end{lstlisting}
-\caption{An excerpt of a JavaScript code.}
+\caption{An excerpt of a JavaScript code illustrating anonymous functions. The comments give the results from Sec.~\ref{sec:foc} and these are discussed in Sec.~\ref{sec:examples}}
 \label{js-code}
@@
 \section{Static  Function Object Consumption}
+\label{sec:foc}
 Using our analysis we have created a preliminary automatic naming solution.  The three parts of our solution match three observations for our study. First we apply 
@@
 
-\subsection{Example}
-
-To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
-
-The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
-We can explain the function object consumption after its creation in two steps.
-First the parent node is a function call (row 2 in Table~\ref{table:node-types}.
-2) the result is assigned to {\small\texttt{main}}.
-This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
-We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".
-
-The function in line 10 is returned just after its creation.
-This function is located inside a closure function (i.e., a function which is called directly after its creation).
-This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the closure call result ({\small\texttt{main}}).
-The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}.
-As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
-
-The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
-Here 1) the function object is passed as an argument to function {\small\texttt{op}}, 2) The call result is assigned to {\small\texttt{result}}.
-If we simply put the identifiers in the summary together we get {\small\texttt{main/result<op()}}.
-The first part before slash  shows the context name (the enclosing function name) for this function.
-However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
-Therefore, as we explain in 4.5, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
-After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
-Eliding identifiers is important to avoid creating long, unwieldy names.
-
-The next two functions, {\small\texttt{Foo}} on line 19 and {\small\texttt{Bar}} on line 22 are simple examples of case 6.
-The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
+\subsection{Examples}
+\label{sec:examples}
+To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize five function bodies in the code, none of them has a name.
+
+The first function on line 9 is assigned to the variable \verb|main|.
+The parent node for the function body in the syntax tree will be an assignment, so in Algorithm~\ref{alg1} we skip the \verb|while| loop and compute the \verb|nameExpression| as \verb|main|.
+Ultimately this becomes the name of the function.
+
+The second function on line 11 is nested in the first one.
+It is passed as an argument to a constructor call on line 10 and the resulting object is assigned to \verb|foo|.
+In Algorithm~\ref{alg1} we create two entries in the consumption summary, one for the function call with identifier \verb|FOO| and one for the assignment with identifier \verb|foo|.
+The first one gets marked with \verb|isContributesTo|.
+Following the logic in Sec.~\ref{sec:concatenation}, we drop the function call identifier but mark the name with \verb|<| for contributes-to.
+The resulting local name is \verb|foo<| and the full name includes the enclosing function name: \verb|main/foo<|.
+
+The third function on line 18 is called immediately after definition, on line 24.
+This means the function body in the syntax tree will have a parent from the immediate call then the assignment; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|.
+The name becomes \verb|FOO<|.
+
+The fourth function on line 20 is returned by \verb|FOO<|.
+After the first pass through the \verb|while| loop in Algorithm~\ref{alg1} we enter \verb|getNextNode| and trigger the code described in Sec.~\ref{sec:immediate}.
+This will cause us to walk up the syntax tree to find the assignment target for the outer function.
+We end up with name \verb|FOO|.
+Because do not process the intermediate nodes in the \verb|while| loop we don't mark the name with contributes-to and we don't record that the function is nested.
+Of course the function body is nested, but it is bound to an un-nested variable.
+To keep the name compact we choose not to encode this complex information.
+Rather we stick to the simple picture that the function 'is' \verb|FOO|.
+If the developer wants to know more they can look up \verb|FOO| to see the construction and nesting.
+
+The fifth function on line 25 is assigned to two variables.
+This example illustrates that we stop processing in Algorithm~\ref{alg1} as soon as we hit the first assignment, giving the name \verb|BAR|.
+This aligns with our observation that the visually closest identifier is the best choice.
+
+\section{Evaluation}
 
@@
 \end{table*}
-
-\section{Evaluation}
-The purpose of our evaluation is to answer the following questions: 1) How effective is the approach in naming anonymous functions?
-2) How the algorithm  improves the current approaches used in available debuggers for inferring anonymous function names?
-3) Are the proposed names are unique to be used as identifiers or conversely what portion of proposed names are duplicated?
-4) Are the proposed names appropriate for user interface presentation?
 

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
updates to "related work" section.

@@
 % open problems: naming scripts loaded and evaluated by eval,
+
 \section{Related Work}
@@
 % typing system papers
-
+% readability parameter paper
+
+To best of our knowledge, this paper is the first study in naming anonymous functions in JavaScript.
+H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs.
+Their approach employ rules extracted from a big corpus of Java projects to recognize buggy names.
+To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.
+This approach assumes that the function is already named and constructs the names based on the function internal structure.
+In contrast, our approach construct the function name by analysing the function context.
+
+Caprile and Tonella \cite{Caprile}, analyse the structure of function identifiers in C programs.
+The identifiers are decomposed into fragments that are then classified into seven lexical categories.
+The structure of the function identifiers are futher described by a hand-crafted grammar.
 %JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
@@
 
-\appendix
-\section{JavaScript Projects Analyzed for Function Names}
-\begin{description}
-\item[Closure] Google Web Library, ...
-\item[Dojo] JavaScript Toolkit
-\item[ExtJS] JavaScript Framework
-\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
-\item[jQuery]
-\item[MochiKit]
-\item[MooTools]
-\item[Prototype]
-\item[Scriptaculous]
-\item[YUI]
-\end{description}
+%\appendix
+%\section{JavaScript Projects Analyzed for Function Names}
+%\begin{description}
+%\item[Closure] Google Web Library, ...
+%\item[Dojo] JavaScript Toolkit
+%\item[ExtJS] JavaScript Framework
+%\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
+%\item[jQuery]
+%\item[MochiKit]
+%\item[MooTools]
+%\item[Prototype]
+%\item[Scriptaculous]
+%\item[YUI]
+%\end{description}
 
@@
 \newblock \emph{Electr. Notes Theor. Comput. Sci.}, 138(2), 2005.
+
+\bibitem{Caprile}
+B. Caprile and P. Tonella. \newblock Nomen est omen: Analyzing the language of function identifiers.
+\newblock In \emph{Proceedings of the 6th working conference on Reverse Engineering(WCRE)},
+October, 1999.
 
@@
 
+\bibitem{Host}
+E. W. H{\o}st and  B. M. {\O}stvold.\newblock Debugging Method Names.
+\newblock In \emph{Proceedings of the 23rd European conference on Object-Oriented Programming(ECOOP)},
+July, 2009.
+
 \bibitem{Ingalls}

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
add examples table

@@
 \section{Building Up Intuition by Example}
+\label{sec:intuition}
 We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
@@
 \subsection{Case 2: Entry in an Array Literal}
+\label{sec:arrayLiteral}
 Contrary to the previous case the appearance of this case is very limited.
@@
 \subsection{Case 3: Property Assignment With Property Identifier}
+\label{sec:propid}
 This case is the second most common case in the studied projects.
@@
 \subsection{Case 6:  Property Assignment With  Property Name Expressions}
+\label{sec:propexpressions}
 Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
@@
 \subsection{Case 8: Assignment to a Variable }
+This case is widely used and we expect  developers would expect the function body to get the name of the variable.
 As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
 and its internal scopes.
-Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name works will as the function name.
+There are cases in which a variable name is used temporarily, as the function is passed to another function or assigned to an object property.
+However, in most cases the variable name works well as the function name.
 
@@
 \subsection{Case 10: Function Property is Accessed}
+\label{sec:funcprop}
 In this unusual case a property of the function is accessed directly from the function body.
@@
 \label{sec:examples}
+
+\begin{table*}[tb]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+Example Code & Static Function-Object Consumption Name \\
+\hline
+Sec.~\ref{sec:arrayLiteral} & YUI.add[event-focus]()/\_attach/Event.\_attach() \\
+\hline
+Sec.~\ref{sec:propid} & eventPool\_createObject \\
+\hline
+Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
+\hline
+Fig.~\ref{fig:jQueryEach} inner & jQuery.fn[o] \\
+\hline
+Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
+\hline
+Fig.~\ref{fig:classnamemanager} outer & YUI.add[classnamemanager]()/Y.ClassNameManage\verb|<| \\
+\hline
+Fig.~\ref{fig:classnamemanager} inner & YUI.add[classnamemanager]()/Y.ClassNameManager/getClassName \\
+\hline
+Sec.~\ref{sec:funcprop} inner & ?????????????\\
+\hline
+Fig.~\ref{fig:registerWin} inner & registerWin\verb|<| \\
+\end{tabular}
+\label{table:examples}
+\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
+Full names are listed, even in cases where our example code omitted the enclosing function scope.}
+\end{table*}
+
 To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize five function bodies in the code, none of them has a name.
@@
 
+Finally, Table~\ref{table:examples} gives the names of functions from examples discussed in \ref{sec:intuition}.
+
 \section{Evaluation}
@@
 H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs.
-Their approach employ rules extracted from a big corpus of Java projects to recognize buggy names.
+Their approach employs rules extracted from a big corpus of Java projects to recognize buggy names.
 To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.
 This approach assumes that the function is already named and constructs the names based on the function internal structure.
-In contrast, our approach construct the function name by analysing the function context.
+In contrast, our approach construct the function name by analyzing the function context.
 
@@
 The identifiers are decomposed into fragments that are then classified into seven lexical categories.
-The structure of the function identifiers are futher described by a hand-crafted grammar.
+The structure of the function identifiers are further described by a hand-crafted grammar.
 %JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
table 6 was updated.

@@
 \centering
-\scalebox{0.9}{
+\scalebox{0.8}{
   \begin{tabular}{ | l | l | l |}
@@
 \centering
+\scalebox{1}{
 \begin{tabular}{|l|l|}
@@
 \hline
-Sec.~\ref{sec:arrayLiteral} & YUI.add[event-focus]()/\_attach/Event.\_attach() \\
-\hline
-Sec.~\ref{sec:propid} & eventPool\_createObject \\
+Sec.~\ref{sec:arrayLiteral} outer & YUI.add(event-focus)/\_attach \\
+\hline
+Sec.~\ref{sec:arrayLiteral} inner & YUI.add(event-focus)/\_attach/Event.\_attach() \\
+\hline
+Sec.~\ref{sec:propid} & eventPool.\_createObject \\
 \hline
@@
 \hline
-Fig.~\ref{fig:classnamemanager} outer & YUI.add[classnamemanager]()/Y.ClassNameManage\verb|<| \\
-\hline
-Fig.~\ref{fig:classnamemanager} inner & YUI.add[classnamemanager]()/Y.ClassNameManager/getClassName \\
-\hline
-Sec.~\ref{sec:funcprop} inner & ?????????????\\
-\hline
-Fig.~\ref{fig:registerWin} inner & registerWin\verb|<| \\
+Fig.~\ref{fig:classnamemanager} outer & YUI.add(classnamemanager)/Y.ClassNameManager\textless \\
+\hline
+Fig.~\ref{fig:classnamemanager} inner & YUI.add(classnamemanager)/Y.ClassNameManager/getClassName \\
+\hline
+Sec.~\ref{sec:funcprop} inner & setVisible/cb\textless\\
+\hline
+Fig.~\ref{fig:registerWin} inner & registerWin/ \\
+\hline
 \end{tabular}
+}
 \label{table:examples}

### 2011-04-13 papers/splash-wavefront2011/sigplanconf-template.tex
first 5 sections + table 7 were updated.

@@
 
-\conferenceinfo{WXYZ '05}{date, City.} 
+\conferenceinfo{SPLASH Wavefront '11}{22-27 October, Portlant, Oregon, USA.} 
 \copyrightyear{2011} 
@@
 JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations.
-However, developers need not specify names for functions.
+However, developers need not to specify names for functions.
  Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
-By studying examples from these JavaScript projects, we propose Static Function-Object Consumption, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions.
-We applied our approach to these same JavaScript projects and the results are very promising.
+By studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions.
+We applied our approach to 90000 anonymous functions appeared in the analyzed JavaScript project.
+The approach is successful in naming more than 99\% (91\% are unique in file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.
+
 \end{abstract}
@@
 Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
-This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}.
+This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}.
 It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade.
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
-Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards}.
+Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards2}.
 There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.
@@
 
-\begin{table}
-
-\centering
-\scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l | l |}
-  \hline
-   Project & Ver. & Description & Total & Named \\ 
-  \hline 
-   Closure &  & Google Web Library & 9195 & 208(2\%) \\ 
-  \hline 
-   DoJo & 1.5 & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
-  \hline 
-   ExtJS & 3.3.1 & JavaScript Framework & 37717 & 1184(3\%) \\ 
-  \hline 
-   Firebug & 1.7 & Web Development Tool & 3424 & 406(11\%) \\ 
-  \hline 
-   jQuery & 1.4.4 & JavaScript Library & 422 & 23(5\%) \\ 
-  \hline 
-   MochiKit & 1.4.2 &  JavaScript Library & 1866 & 37(1\%) \\ 
-  \hline 
-   MooTools & 1.3 & JavaScript Framework & 625 & 7(1\%) \\ 
-  \hline 
-   Prototype & 1.7 & JavaScript Framework & 645 & 203(31\%) \\ 
-  \hline 
-   Scriptaculous & 1.9 &  JavaScript Library & 1092 & 208(19\%) \\ 
-  \hline 
-   YUI & 3.3 &  Yahoo UI Library & 22346 & 922(4\%) \\ 
-  \hline 
-   All & N/A & N/A & 96008 & 6008(6.3\%) \\ 
-  \hline 
-  \end{tabular}
-  }
-\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.} 
-\label{js-functions} 
-\end{table}
-
 %\section{The Nameless Function Problem}
@@
 
-A JavaScript function can be defined with the {\small\texttt{function}} operator or the {\small\texttt{Function}} constructor (i.e., {\small\texttt{new Function(args, source)}}) \cite{ECMA}.
-The {\small\texttt{function}} operator can appear in a function declaration, function expression, or function statement (the latter form is available in Firefox but not part of a standard).
-Of these forms, only the function declaration requires a function name and the {\small\texttt{Function}} constructor has no mechanism to name the function.
+A JavaScript function can be defined with the \verb|function| operator or the \verb|Function| constructor (i.e., \verb|new Function(| \verb|args, source)|) \cite{ECMA}.
+The \verb|function| operator can appear in a function declaration, function expression, or function statement (the latter form is available in Firefox but not part of a standard).
+Of these forms, only the function declaration requires a function name and the \verb|Function| constructor has no mechanism to name the function.
 In other words, JavaScript developers can define functions with or without function names.
@@
 
+\begin{table}%[htp]
+
+\centering
+\scalebox{0.8}{
+  \begin{tabular}{ | l | l | l | l | l | l |}
+  \hline
+   Project & Ver. & Description & Total & Named \\ 
+  \hline 
+   Closure & r683 & Google Web Library & 9195 & 208(2\%) \\ 
+  \hline 
+   DoJo & 1.5 & JavaScript Toolkit & 18676 & 2810(15\%) \\ 
+  \hline 
+   ExtJS & 3.3.1 & JavaScript Framework & 37717 & 1184(3\%) \\ 
+  \hline 
+   Firebug & 1.7 & Web Development Tool & 3424 & 406(11\%) \\ 
+  \hline 
+   jQuery & 1.4.4 & JavaScript Library & 422 & 23(5\%) \\ 
+  \hline 
+   MochiKit & 1.4.2 &  JavaScript Library & 1866 & 37(1\%) \\ 
+  \hline 
+   MooTools & 1.3 & JavaScript Framework & 625 & 7(1\%) \\ 
+  \hline 
+   Prototype & 1.7 & JavaScript Framework & 645 & 203(31\%) \\ 
+  \hline 
+   Scriptaculous & 1.9 &  JavaScript Library & 1092 & 208(19\%) \\ 
+  \hline 
+   YUI & 3.3 &  Yahoo UI Library & 22346 & 922(4\%) \\ 
+  \hline 
+   All &  & All Projects & 96008 & 6008(6.3\%) \\ 
+  \hline 
+  \end{tabular}
+  }
+\caption{The total number of functions and the number of named functions (and percent named)  in ten large JavaScript projects. See appendix 1 for the project citations.} 
+\label{js-functions} 
+\end{table}
+
 So what do JavaScript developers do in practice?
@@
 The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent.
-Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
-Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.
+Among all functions only a very limited number of them (116 functions) are defined by the \verb|Function| constructor.
+Our analysis does not include the functions defined dynamically by \verb|eval| function or \verb|new Function()|; these cases would only make the ratio even smaller.
 Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
 
-\begin{figure}[htp]
+To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
+Two main issues appear in debuggers due to the lack of function name.
+First, object constructor name, which can facilitate understanding the object value, is not available in the object summary.
+Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative.
+We discuss these issues in the next two subsections.
+
+\subsection{Missed Constructor Name in Object Summary}
+JavaScript does not support classes, but objects can be created by constructors (\verb|new| followed by a function call).
+A constructor is a regular JavaScript function.
+Once the \verb|new| keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to \verb|this| and the constructor is called.
+The role of constructor is to initialize the empty object.
+Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards2}, the constructor can still be useful in classifying the object.
+Debuggers employ this fact and display the constructor name in the object summary to facilitate the developer's understanding.
+
+\begin{figure}%[htp]
 
@@
 
-To understand the consequences of anonymous functions on development tools we will focus on one example, the impact on debuggers.
-Two main issues appear in debuggers due to the lack of function name.
-First, object constructor name, which can facilitate understanding the object value, is not available in the object summary.
-Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative.
-We discuss these issues in the next two subsections.
-
-\subsection{Missed Constructor Name in Object Summary}
-JavaScript does not support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call).
-A constructor is a regular JavaScript function.
-Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called.
-The role of constructor is to initialize the empty object.
-Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards}, the constructor can still be useful in classify the object.
-Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.
-
 Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue.
 We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
-Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{Foo}} and {\small\texttt{Bar}}.
-However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{Baz.Bar}} class for {\small\texttt{bar}} as their summaries.
+Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|.
+However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| as their summaries.
 The first class is very general and the second one is misleading.
 The developer has to expand the object nodes to recognize their similarities and differences.
-Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary.
+Firebug classify both objects in the general \verb|Object| class, but includes some of the object properties in the summary.
 These additional properties may hint the developer about the object structures.
-{\small\texttt{Foo}} and {\small\texttt{Bar}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
+\verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or in some cases infer misleading names.
 
@@
 The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms.
-Among three last functions in the call stack, Google Chrome only shows the name of one of them({\small\texttt{main}}) correctly.
-For the second function (line 22), it shows \textit{anonymous}, and for the third function (line 12), it gives a wrong name, {\small\texttt{foo}}.
+Among three last functions in the call stack, Google Chrome only shows the name of first function (\verb|main|) correctly.
+For the second function (line 22), it shows \verb|anonymous|, and for the last function (line 12), it gives a wrong name, \verb|foo|.
 Firebug performs better by guessing two function names correctly, but it still fails in one case.
-It shows {\small\texttt{main}} as the name of last function(line 12) which is the name of its enclosing function.
+It shows \verb|main| as the name of last function(line 12) which is the name of another function (the enclosing function at line 9).
 In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.
@@
 
-%Two other pieces of information which are important at function calls are {\small\texttt{this}} and argument values.
-In JavaScript, {\small\texttt{this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
-The {\small\texttt{this}} value is missed in both views.
-The {\small\texttt{arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.
+%Two other pieces of information which are important at function calls are \verb|this}} and argument values.
+In JavaScript, \verb|this}} like arguments is not defined by lexical scopes but it is bound once the function is called.
+The \verb|this}} value is missed in both views.
+The \verb|arguments}} values is shown in Firebug, but it still suffers from the same issues as object summaries.
 
@@
 
-We instead propose an almost automated approach for naming all functions by analyzing the source code.
+We instead propose an automated approach for naming anonymous functions by analyzing the source code.
 Before getting into explaining the algorithm details we discuss the rationale behind some of decisions we made in this approach.
@@
 
-Once a statement which defines a function is evaluated, a new {\small\texttt{Function}} 
+Once a statement which defines a function is evaluated, a new \verb|Function| 
 object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
-zero to many {\small\texttt{Function}} objects can be created from the same definition. 
+zero to many \verb|Function| objects can be created from the same definition. 
 Two function objects which are created from the same function body may have different object properties added at runtime.
@@
 Thus our first
-decision: do we try to name the {\small\texttt{Function}} objects or the source that defines them?
-
-For the common use cases, the different {\small\texttt{Function}} objects are bound to one or more properties of objects.
+decision: do we try to name the \verb|Function| objects or the source that defines them?
+
+For the common use cases, the different \verb|Function| objects are bound to one or more properties of objects.
 The  names of these properties inform the developer about the role of the function in the actions of the object.
@@
 Scripts are loaded from different files and executed within the same or different global objects.
-Developers usually use objects at the top level to encapsulate properties, objects and functions from a framework or library.
+Developers usually use objects at the top level to encapsulate objects, properties and functions from a framework or library.
 The same mechanism is reused for defining subpackages.
@@
 
-For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 libraries into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.
+For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.
 Then we examine each of these cases to think about how we want the functions named.
-We'll ignore nesting of function scopes in the analysis to avoid taking on too much at one time.
-
-\begin{table}
+We will ignore nesting of function scopes in the analysis to avoid taking on too much at one time.
+
+\begin{table}[htp]
 \centering
@@
 
-\begin{table*}
+\begin{table*}[htp]
 \centering
@@
 %In the third subsection we discuss qualities we expect from an automatically created function name.
-
 \subsection{Case 1: Object Property Initializer}
  This case usually appears when developers try to group a set of functions in a new object.
-A common case is grouping a set of functions in the {\small\texttt{prototype}} property of the constructor.
+A common case is grouping a set of functions in the \verb|prototype| property of the constructor.
 This structure resembles the class structure in traditional object-oriented languages.
@@
 It usually appears in initializations or when an array of functions are passed as an argument.
-Among all projects only two have instances of nameless functions defined in this way.
-For example array argument to \verb|Event._attach| in this example from YUI:
-\begin{verbatim}
+Among all projects only three have instances of nameless functions defined in this way.
+For example array argument to \verb|Event._attach| in this example from YUI \footnote[3]{The example is nested in more function definitions we do not show here.}:
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   _attach: function (el, notifier, delegate) {
@@
   }
-\end{verbatim}
-(The example is nested in more function definitions we do not show here).
+\end{lstlisting}
+%\end{verbatim}
 The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|.
@@
 Following the model from Case 1, we expect a good name would combine the object name with the property identifier.
-The complication in this case comes from the object name: in general the object reference can be a computed expression.
-(This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier).
+The complication in this case comes from the object name: in general the object reference can be a computed expression \footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}.
 Here is a simple example from the Closure project:
-\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   this.eventPool_.createObject = function() {
@@
   };
-\end{verbatim}
+\end{lstlisting}
+
  These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small.
-For example, \verb|this.| add no information to the name since we can't know the value of \verb|this| while parsing.
+For example, \verb|this.| add no information to the name since we cannot know the value of \verb|this| while parsing.
 
@@
 \subsection{Case 5: Property Assignment With  Property Name Variable}
-Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we can't (usually) statically compute the string to use as a property identifier.
+Object member names can be variable references that get converted to strings at runtime: this is syntactically similar to Case 4, but we cannot (usually) statically compute the string to use as a property identifier.
 The usage of this case is also limited. This form usually appears when the same function body is assigned to different properties in a loop. 
 For example see the inner function in Fig.~\ref{fig:jQueryEach}. The variable
- name in the cases we examined was generic name like {\small\texttt{o}} or {\small\texttt{item}}. Unlike the previous two cases, we
-don't have a specific property name.
+ name in the cases we examined was generic name like \verb|o| or \verb|item|. Unlike the previous two cases, we
+do not have a specific property name.
 Nevertheless identifying the function body using the assignment target with the variable name as the property name follows the reasoning used for the simple cases.
-\begin{figure*}[htp]
-\begin{verbatim}
-jQuery.each( "ajaxStart ajaxStop ajaxComplete ajaxError".split(" "), function( i, o ) {
+\begin{figure}[htp]
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
+  jQuery.each("ajaxStart ajaxStop ajaxComplete ajaxError"
+    .split(" "), function( i, o ) {
        jQuery.fn[o] = function( f ) {
@@
   });
-\end{verbatim}
-\caption{An example of functions passed as arguments to a function (row 11 in Table~\ref{table:function-types} and (the inner definition) an example of a 
-function assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}. The function is from the jQuery library but simplified to fit on the page. }
+\end{lstlisting}
+\caption{An example of a function (the inner definition) assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}) and an example of 
+functions passed as arguments to a function (row 11 in Table~\ref{table:function-types}). The function is from the jQuery library but simplified to fit on the page. }
 \label{fig:jQueryEach}
-\end{figure*}
+\end{figure}
 
@@
 Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
- A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values.
+ A common case of expression in this case is a conditional expression, e.g., \verb|condition?"prop1":"prop2"|, where the property that we assign the function to depends upon runtime values.
 Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
-\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   function define(D) {
@@
   }
-\end{verbatim}
+\end{lstlisting}
 The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.
@@
 \subsection{Case 9: Anonymous Functions Immediately Called}
-Calling functions objects just after their creations is a common pattern in JavaScript.
+Calling function objects just after their creations is a common pattern in JavaScript.
 For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example.
 \begin{figure}[htp]
-\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   Y.ClassNameManager = function () {
-
     var sPrefix = CONFIG[CLASS_NAME_PREFIX],
     sDelimiter = CONFIG[CLASS_NAME_DELIMITER];
-
     return {
@@
   }();
-\end{verbatim}
+\end{lstlisting}
+\caption{An example the YUI project of function bodies from cases 9 (the outer function)  and 12  (the argument to Y.cached) from Table~\ref{table:function-types}  }
 \label{fig:classnamemanager}
-\caption{An example the YUI project of function bodies from cases 9 (the outer function)  and 12  (the argument to Y.cached) from Table~\ref{table:function-types}  }
 \end{figure}
@@
 If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
-In this case we can't use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name.
+In this case we cannot use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name.
 To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.
@@
 In this unusual case a property of the function is accessed directly from the function body.
-This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or when the predefined functions are augmented by adding to {\small\texttt{Function}} prototype.
+This case usually happens when one of the predefined functions (i.e., \verb|call, apply,| \verb|bind|) or added functions to the \verb|Function| prototype is called.
 Here is an example, from ExtJS, reformatted for display here:
-\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   setVisible : function(v, a, d, c, e){
@@
   }
-\end{verbatim}
+\end{lstlisting}
 The inner function body is not used directly, but the result of \verb|createDelegate| is assigned to \verb|cb|.
@@
 In this case the function body appears in a return statement of another function body.
-Although this category only includes 2\% of nameless function, proper naming of functions in this class is important.
+Although this category only includes 2\% of nameless functions, proper naming of functions in this class is important.
 Many constructors are built using this form and therefore the names of these functions appear in object summaries.
@@
 For example, in Fig.~\ref{fig:registerWin} a developer might pick names like \verb|registerWinOnIE| and \verb|registerWinNotOnIE| for the functions returned by the Dojo function \verb|registerWin|.
-\begin{figure*}[htbp]
-\begin{verbatim}
+\begin{figure}[htbp]
+
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
 registerWin: function(targetWindow, effectiveNode){
-  // ...
+ ...
  if(doc){
@@
     doc.detachEvent('ondeactivate', deactivateListener);
-        doc = null;    // prevent memory leak (apparent circular reference via closure)
+    doc = null;    
    };
@@
    return function(){
-        doc.removeEventListener('mousedown', mousedownListener, true);
+    doc.removeEventListener(
+                    'mousedown', mousedownListener, true);
     doc.removeEventListener('focus', focusListener, true);
     doc.removeEventListener('blur', blurListener, true);
-        doc = null;    // prevent memory leak (apparent circular reference via closure)
+    doc = null;   
    };
-    }
-  }
-},
-\end{verbatim}
+}}},
+\end{lstlisting}
+\caption{An example of a function body in a return statement, case 11 of Table~\ref{table:function-types}  adapted from the Dojo project code}
 \label{fig:registerWin}
-\caption{An example of a function body in a return statement, case 11 of Table~\ref{table:function-types}  adapted from the Dojo project code}
-\end{figure*}
+\end{figure}
 
@@
 As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.
-Fig.~\ref{fig:classnamemanager} shows different example, where the function called (\verb|Y.Cached()| seems much less important for naming the function than the property that we initialize with the result of calling the function.
+Fig.~\ref{fig:classnamemanager} shows different example, where the function called (\verb|Y.Cached()|) seems much less important for naming the function than the property that we initialize with the result of calling the function.
 This important case will stress any naming algorithm: we somehow have to summarize the function call -- which itself may be an expression -- and the other arguments -- any or all of which may be expressions.
 
-\subsection{Results of studying examples}
+\subsection{Results of Studying Examples}
 We reached two main conclusions from studying the way anonymous functions are used in the source of the 10 projects we examined.
@@
 JavaScript programmers are creating anonymous functions but they are loading them into object references and the expressions that result in those references have informative identifiers inside.
-Second, these expressions that we focus on may often be simple identifiers, but if they don't we will need to analyze the source of these expressions to extract meaningful summaries.
+Second, these expressions that we focus on may often be simple identifiers, but if they do not we will need to analyze the source of these expressions to extract meaningful summaries.
 This summary has to balance information against length.
@@
 %\subsubsection{Local vs. Global}
-%the object bound to {\small\texttt{this}}-depending on the way the function is called-and passed arguments.
+%the object bound to \verb|this}}-depending on the way the function is called-and passed arguments.
 The first two parameters can be almost known from the source code and are less dependent to the runtime while the last two parameters are usually not known until the function call at runtime.
@@
 For each node we create an entry in a list and record in it information about the relationship between the node and its parent.
-We'll use this relationship information in Sec.~\ref{sec:concatenation}.Then for each node  we record developer-invented identifiers related to the destiny of the function object created from the body as outlined in  Table~\ref{table:node-types}.
+We'll use this relationship information in Sec.~\ref{sec:concatenation}.
+Then for each node  we record developer-invented identifiers related to the destiny of the function object created from the body as outlined in  Table~\ref{table:node-types}.
 For the first and third rows of the table we record the information recursively; for the second row,  assignment node, we record the information after the loop terminates.
@@
    \STATE $summary.add(dataItem)$
-   \STATE $n$ = getNextNode($n$)
+   \STATE $n$ = $getNextNode(n)$
 \ENDWHILE
@@
 \centering
-%\scalebox{0.8}{
+\scalebox{0.8}{
 \renewcommand\arraystretch{2.0}
-\begin{tabular}{ | c | l | m{2.5cm} | l|}
+\begin{tabular}{ | c | l | m{3cm} | l|}
   \hline
@@
    1 & 
-   & \raggedright an object literal.
+   & \raggedright is an object literal.
    & \{ ..., foo: expr \}\\ 
@@
 
-   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node is\end{rotate}} 
+   2 & \multirow{4}{*}{\hspace{.2cm}\begin{rotate}{90}The parent node\end{rotate}} 
    & 
-     \raggedright a function call.
+     \raggedright is a function call.
    & foo\textsuperscript{*}(..., expr, ...) \\
@@
    3 &
-   & \raggedright an assignment.
+   & \raggedright is an assignment.
    & foo\textsuperscript{*} = expr\\
@@
   \end{tabular}
-%  }
+  }
 \caption{Nodes produce identifiers in the function object consumption summary.
@@
 We call these functions \textit{immediate functions}.
-For an example, see line 10 of the Listing~\ref{js-code} which is enclosed in the function on line 9.
+For an example, see line 10 of the Figure~\ref{js-code} which is enclosed in the function on line 9.
 If the developer returns a function from this outer, immediate function we want to follow the returned object to where it is consumed.
@@
 To keep our core algorithm simple we handle these returns from immediate functions as a special case.
-At the end of each loop in Algorithm~\ref{alg1} at the point marked \verb|getNextNode()| we check to see if our parent is a \verb|return| node.
+At the end of each loop in Algorithm~\ref{alg1} at the point marked \verb|getNextNode()| we check to see if the parent is a \verb|return| node.
 If not we return the parent node and the loop continues.
@@
 This work is done during the Object Consumption Summary algorithm in the functions described here:
-\paragraph{Identifiers for Function Arguments} Search for all string nodes in other arguments and concatenated them by ``-'', dropping  characters over 10.  
+\paragraph{Identifiers for Function Arguments} Search for all literal string nodes in other arguments and concatenated them by ``-'', dropping  characters over 10.  
  (This work is on in Algorithm~\ref{alg1} in \verb|argSummary|).
-\paragraph{Identifiers for Assignments and Function calls} This function gets called for nodes resulting from the first 6 rows of Table~\ref{table:function-types}.
-The expressions here will evaluate to a writable address, so we want to extract the most specific developer-invented identifiers from the expression.
+\paragraph{Identifiers for Assignments and Function calls} This function gets called for nodes resulting from the last 2 rows of Table~\ref{table:node-types}.
+The expressions here will evaluate to a writable or readable address, so we want to extract the most specific developer-invented identifiers from the expression.
 Thus we apply the rules from Table~\ref{expression-reduction}, which starts from the right hand side of the expression; we skip any JavaScript keywords like \texttt{this} or \texttt{prototype}.
-If we encounter any pattern which does not match, for example a function call, we stop.
+We also skip any pattern which does not match (e.g., a function call).
 (This work is on in Algorithm~\ref{alg1} in \verb|nameExpressions|.)
@@
   \hline 
-   GetElem & e1[e2] & Name(e1)+``['+'Name(e2)+``]'' \\ 
-  \hline 
-   Add & e1 op e2 & Name(e1)+op+Name(e2) \\ 
-  \hline 
-   Condition & cond?e1:e2 & Name(e1)+":"+Name(e2) \\ 
+   GetElem & e1[e2] & Name(e1)+[+Name(e2)+] \\ 
+  \hline 
+   Operation & e1 op e2 & Name(e1)+op+Name(e2) \\ 
+  \hline 
+   Condition & cond?e1:e2 & Name(e1)+:+Name(e2) \\ 
   \hline 
@@
 The transformation may be used many places in the code, while the assignment target is typically an identifier defined by the developer.
-See for example function on line 14 and the function call on line 13 in the Listing~\ref{js-code}.
-Specifically we drop identifiers from row 2 of table~\ref{table:node-types} in any case where have identifiers from rows 1 or 3.
-The outer function in Fig.~\ref{fig:jQueryEach} illustrates the opposite case, where we don't drop function-call identifier.
+See for example function on line 14 and the function call on line 13 in the Figure~\ref{js-code}.
+Specifically we drop identifiers from row 2 of table~\ref{table:node-types} in any case where we have identifiers from rows 1 or 3.
+The outer function in Fig.~\ref{fig:jQueryEach} illustrates the opposite case, where we do not drop function-call identifier.
 
@@
 Because some entries on the object consumption list are empty strings we may have duplicate symbols.
-Any duplicates are replaced a single symbol.
+Any duplicates are replaced by a single symbol.
 The result contains identifiers (i.e., variable and property names) and strings available in the source code plus some explanatory tokens.
@@
 We get the function \textit{full name} by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
-This full-name is our function body name.
+This full-name is the function body name.
 
@@
 \hline
-Example Code & Static Function-Object Consumption Name \\
+Example Code & Static Function-Object Consumption Full Name \\
 \hline
@@
 \hline
-Sec.~\ref{sec:propid} & eventPool.\_createObject \\
+Sec.~\ref{sec:propid} & eventPool\_.createObject \\
 \hline
@@
 \hline
-Fig.~\ref{fig:jQueryEach} inner & jQuery.fn[o] \\
+Fig.~\ref{fig:jQueryEach} inner & jQuery.each(ajaxStart)/jQuery.fn[o] \\
 \hline
@@
 \hline
-Fig.~\ref{fig:classnamemanager} inner & YUI.add(classnamemanager)/Y.ClassNameManager/getClassName \\
+Fig.~\ref{fig:classnamemanager} inner & YUI.add(classnamemanager)/Y.ClassNameManager.getClassName\textless \\
 \hline
@@
 It is passed as an argument to a constructor call on line 10 and the resulting object is assigned to \verb|foo|.
-In Algorithm~\ref{alg1} we create two entries in the consumption summary, one for the function call with identifier \verb|FOO| and one for the assignment with identifier \verb|foo|.
+In Algorithm~\ref{alg1} we create two entries in the consumption summary, one for the function call with identifier \verb|Foo| and one for the assignment with identifier \verb|foo|.
 The first one gets marked with \verb|isContributesTo|.
@@
 
-The fourth function on line 20 is returned by \verb|FOO<|.
+The fourth function on line 20 is returned by \verb|Foo<|.
 After the first pass through the \verb|while| loop in Algorithm~\ref{alg1} we enter \verb|getNextNode| and trigger the code described in Sec.~\ref{sec:immediate}.
 This will cause us to walk up the syntax tree to find the assignment target for the outer function.
-We end up with name \verb|FOO|.
-Because do not process the intermediate nodes in the \verb|while| loop we don't mark the name with contributes-to and we don't record that the function is nested.
+We end up with name \verb|Foo|.
+Because do not process the intermediate nodes in the \verb|while| loop we do not mark the name with contributes-to and we do not record that the function is nested.
 Of course the function body is nested, but it is bound to an un-nested variable.
 To keep the name compact we choose not to encode this complex information.
-Rather we stick to the simple picture that the function 'is' \verb|FOO|.
-If the developer wants to know more they can look up \verb|FOO| to see the construction and nesting.
+Rather we stick to the simple picture that the function 'is' \verb|Foo|.
+If the developer wants to know more they can look up \verb|Foo| to see the construction and nesting.
 
 The fifth function on line 25 is assigned to two variables.
-This example illustrates that we stop processing in Algorithm~\ref{alg1} as soon as we hit the first assignment, giving the name \verb|BAR|.
+This example illustrates that we stop processing in Algorithm~\ref{alg1} as soon as we hit the first assignment, giving the name \verb|Bar|.
 This aligns with our observation that the visually closest identifier is the best choice.
@@
   \hline
-\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Quality}               & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
+\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
   \cline{2-10}
-                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
-  \hline 
-   Closure       & 8987      &   312(3\%)     & 51        & 10        &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
-  \hline 
-   DoJo          & 15866     &   3362(21\%)    & 528       & 390       &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
-  \hline 
-   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
-  \hline 
-   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
-  \hline  
-   jQuery        & 399       &   95(24\%)     & 9         & 8         &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
-  \hline  
-   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
-  \hline 
-   MooTools      & 618       &   121(19\%)    & 30        & 18        &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
-  \hline 
-   Prototype     & 442       &   125(28\%)    & 24        & 19        &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
-  \hline  
-   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
-  \hline    
-   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
-  \hline 
-   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   & N/A            & N/A         \\ 
+                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Avgerage   & Longest  \\ 
+  \hline 
+   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 \\ 
+  \hline 
+   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 35/36      & 81/162 \\ 
+  \hline 
+   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  \\ 
+  \hline 
+   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 \\ 
+  \hline  
+   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  \\ 
+  \hline  
+   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80   \\ 
+  \hline 
+   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73   \\ 
+  \hline 
+   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 23/25      & 55/88    \\ 
+  \hline  
+   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 22/27      & 55/132   \\ 
+  \hline    
+   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145  \\ 
+  \hline 
+   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)  & N/A       & N/A         \\ 
   \hline       
@@
 For these cases we add a dollar sign and an index to the similar function names.
-For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
+For example, if there are two function bodies with names \verb|myFunction|, the functions are named as \verb|myFunction\$0| and \verb|myFunction\$1|.
 
@@
 \subsection{Functions created by {\large \texttt{eval()}}}
-The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is available.
+The function bodies in \verb|eval| statements can be named similar to other objects as the source code is available.
 However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
@@
 %JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
-JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
+JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards2}.
 As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
@@
 
-\bibitem{Richards}
+\bibitem{Richards1}
+G. Richards, C. Hammer, B. Burg and J. Vitek. \newblock The Eval that Men Do.
+\newblock In \emph{Proceedings of the 25th European conference on Object-Oriented Programming(ECOOP)},
+July, 2011.
+
+\bibitem{Richards2}
 G. Richards, S. Lebresne, B. Burg and J. Vitek.\newblock An analysis of the dynamic behavior of JavaScript programs.

### 2011-04-13 papers/splash-wavefront2011/sigplanconf-template.tex
table 6 is updated.

@@
 
-\begin{table*}[tb]
-\centering
-\scalebox{1}{
-\begin{tabular}{|l|l|}
-\hline
-Example Code & Static Function-Object Consumption Full Name \\
-\hline
-Sec.~\ref{sec:arrayLiteral} outer & YUI.add(event-focus)/\_attach \\
-\hline
-Sec.~\ref{sec:arrayLiteral} inner & YUI.add(event-focus)/\_attach/Event.\_attach() \\
-\hline
-Sec.~\ref{sec:propid} & eventPool\_.createObject \\
-\hline
-Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
-\hline
-Fig.~\ref{fig:jQueryEach} inner & jQuery.each(ajaxStart)/jQuery.fn[o] \\
-\hline
-Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
-\hline
-Fig.~\ref{fig:classnamemanager} outer & YUI.add(classnamemanager)/Y.ClassNameManager\textless \\
-\hline
-Fig.~\ref{fig:classnamemanager} inner & YUI.add(classnamemanager)/Y.ClassNameManager.getClassName\textless \\
-\hline
-Sec.~\ref{sec:funcprop} inner & setVisible/cb\textless\\
-\hline
-Fig.~\ref{fig:registerWin} inner & registerWin/ \\
-\hline
-\end{tabular}
-}
-\label{table:examples}
-\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
-Full names are listed, even in cases where our example code omitted the enclosing function scope.}
-\end{table*}
-
 To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize five function bodies in the code, none of them has a name.
@@
 Finally, Table~\ref{table:examples} gives the names of functions from examples discussed in \ref{sec:intuition}.
+
+\begin{table}[htb]
+\centering
+\scalebox{.8}{
+{\small
+\begin{tabular}{|l|l|}
+\hline
+Example Code & Static Function-Object Consumption Full Name \\
+\hline
+Sec.~\ref{sec:arrayLiteral} outer & YUI.add(event-focus)/\_attach \\
+\hline
+Sec.~\ref{sec:arrayLiteral}  inner & YUI.add(event-focus)/\_attach/Event.\_attach() \\
+\hline
+Sec.~\ref{sec:propid} & eventPool\_.createObject \\
+\hline
+Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
+\hline
+Fig.~\ref{fig:jQueryEach} inner & jQuery.each(ajaxStart)/jQuery.fn[o] \\
+\hline
+Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
+\hline
+Fig.~\ref{fig:classnamemanager}  outer & YUI.add(classnamem)/Y.ClassNameManager\textless \\
+\hline
+Fig.~\ref{fig:classnamemanager}  inner &  YUI.add(classnamem)/Y.ClassNameManager.getClassName\textless \\
+\hline
+Sec.~\ref{sec:funcprop}  inner & setVisible/cb\textless\\
+\hline
+Fig.~\ref{fig:registerWin}  inner & registerWin/ \\
+\hline
+\end{tabular}
+}
+}
+\label{table:examples}
+\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
+Full names are listed, even in cases where our example code omitted the enclosing function scope.}
+\end{table}
 
@@
 Firefox Add-ons.
-\newblock https://addons.mozilla.org/en-US/developers/docs/gett ing-started.
+\newblock https://addons.mozilla.org/en-US/developers/docs/getting-started.
 

### 2011-04-13 papers/splash-wavefront2011/sigplanconf-template.tex

@@
 }
-\label{table:examples}
 \caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
 Full names are listed, even in cases where our example code omitted the enclosing function scope.}
+\label{table:examples}
 \end{table}
@@
 \section{Evaluation}
-
-\begin{table*}
-\centering
-\scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
-  \hline
-\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
-  \cline{2-10}
-                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Avgerage   & Longest  \\ 
-  \hline 
-   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 \\ 
-  \hline 
-   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 35/36      & 81/162 \\ 
-  \hline 
-   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  \\ 
-  \hline 
-   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 \\ 
-  \hline  
-   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  \\ 
-  \hline  
-   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80   \\ 
-  \hline 
-   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73   \\ 
-  \hline 
-   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 23/25      & 55/88    \\ 
-  \hline  
-   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 22/27      & 55/132   \\ 
-  \hline    
-   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145  \\ 
-  \hline 
-   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)  & N/A       & N/A         \\ 
-  \hline       
-  \end{tabular}
-  }
- \label{evaluation} 
-\caption{Results of Function Object Consumption.
-The rows are the projects listed in Appendix 1.
-First column in  contains the number of anonymous functions in each project.
-The second column shows the number of functions Firebug could not name.
-The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm;  and the fourth column is the number with only a name for enclosing scopes.
-The fifth column give the number of times a FOC function name appears twice in a file and sixth and seventh columns give the average and longest name character counts respectively.
-The last columns have two entries divided by a slash, the first is the local name and the second is the full name.}
-\end{table*}
 
@@
 Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases.
-About 10 percent of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).The numbers show that the algorithm names more than 99 percent of the anonymous functions.
-
-The duplicates column show the number of duplicated function names.
-About 9 percent of inferred names used for more than one function in a file.
-The main source of duplicated names are test cases particularly in DOJO, ExtJS and YUI.
-%the other sources :1) function calls with no hint  2) conditional functions (e.g., based on browser)
+About 10 percent (the second column) of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).
+The third column shows that only FOC-Locall name more than 98 percent of anonymous functions.
+By adding the enclosing function names, this number increases to more than 99 percent for FOC-Full(the fourth column).
+Based on our observations, most functions remain anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.
+
+The duplicates columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-FULL.
+The number shows that Firebug assignes duplicate names to about 47 percent of anonymous functions.
+The first reason behind this huge number is that Firebug relies on regular expressions instead of abastract syntax tree for locating names.
+The second reason is that Firebug does not analyze the function object flow but tries to construct the name from the identifiers close to function definition.
+The second column shows that FOC-Local gives much less duplicates (13\%) comparing to Firebug.
+It means that local names with are sufficient for recognizing function while they have shorter length than full names.
+The third column says that less than 9 percent of anonymous functions get duplicated names by full names.
+Based on our observations, many of duplicates in projects such as DOJO, ExtJS and YUI come from test files.
+In a test file the same use case is repeated with different data and therefore the same function names appear several times.
+In projects like JQuery, Prototype, MooTools the conditional statements are the main source of duplicates.
+These libraries usually check against different environment properties (e.g., browser) to load the appropriate function.
 
@@
 The longest names are typically long because of a long local name.
+Again in most cases long names apear in test files due to deep nested functions.
+
+\begin{table*}[htp]
+\centering
+\scalebox{0.8}{
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
+  \cline{2-10}
+                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Avgerage   & Longest  \\ 
+  \hline 
+   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 \\ 
+  \hline 
+   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 35/36      & 81/162 \\ 
+  \hline 
+   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  \\ 
+  \hline 
+   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 \\ 
+  \hline  
+   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  \\ 
+  \hline  
+   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80   \\ 
+  \hline 
+   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73   \\ 
+  \hline 
+   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 23/25      & 55/88    \\ 
+  \hline  
+   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 22/27      & 55/132   \\ 
+  \hline    
+   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145  \\ 
+  \hline 
+   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)  & N/A       & N/A         \\ 
+  \hline       
+  \end{tabular}
+  }
+\caption{Results of Function Object Consumption.
+The rows are the projects listed in Appendix 1.
+First column contains the number of anonymous functions in each project.
+The second column shows the number of functions Firebug could not name.
+The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number with only a name for enclosing scopes.
+The next three column gives the number of times a Firebug, FOC-Local and FOC-Full function name appears twice in a file and eighth and nineth columns give the average and longest name character counts respectively.
+The last columns have two entries divided by a slash, the first is the local name and the second is the full name.}
+ \label{evaluation} 
+\end{table*}
 

### 2011-04-13 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
evaluation and related work sections were updated.

@@
 
-\conferenceinfo{WXYZ '05}{date, City.} 
+\conferenceinfo{SPLASH Wavefront '11}{22-27 October, Portland, Oregon, USA.} 
 \copyrightyear{2011} 
@@
 The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent.
-Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor.
-Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.
+Among all functions only a very limited number of them (116 functions) are defined by the \verb|Function| constructor.
+Our analysis does not include the functions defined dynamically by \verb|eval| function or \verb|new Function()|; these cases would only make the ratio even smaller.
 Therefore, we conclude that a large proportion of JavaScript functions are anonymous.
-
-\begin{figure}[htp]
-
-\lstset{basicstyle=\scriptsize}
-\lstset{emph={FOO,BAR}} %,emphstyle=\bf}
-\lstdefinelanguage{myLang}
-{morekeywords={if, function, var, return, new, this}}
-
-\begin{lstlisting}[frame=single, language=myLang]
-9  var main = function() {          // main
-10   var foo = new FOO(            
-11      function(){                 // main/foo<
-12        this.welcome = "Hi!";
-13      });
-14   var bar = new BAR("GoodBye.");
-15   alert(foo.welcome);
-16   alert(bar.message);
-17 };
-18 var FOO = function(){            // FOO<    
-19   var instances;
-20   return function(initializer){  // FOO
-21       instances++;         
-22       initializer.apply(this);
-23     }
-24 }();
-25 var BAZ = BAR = function(msg){   // BAR
-26   this.message = msg;
-27 }
-\end{lstlisting}
-\caption{An excerpt of a JavaScript code.}
-\label{js-code}
-\end{figure}
-
-\begin{figure*}[htp]
-\centerline{
-\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.jpg}}
-\hfil
-\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.jpg}}}
-\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
-\label{debuggers-objects}
-\end{figure*}
 
@@
 \subsection{Missed Constructor Name in Object Summary}
-JavaScript does not support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call).
+JavaScript does not support classes, but objects can be created by constructors (\verb|new| followed by a function call).
 A constructor is a regular JavaScript function.
-Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called.
+Once the \verb|new| keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to \verb|this| and the constructor is called.
 The role of constructor is to initialize the empty object.
-Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards}, the constructor can still be useful in classify the object.
-Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.
+Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards2}, the constructor can still be useful in classifying the object.
+Debuggers employ this fact and display the constructor name in the object summary to facilitate the developer's understanding.
+
+\begin{figure}%[htp]
+
+\lstset{basicstyle=\scriptsize}
+\lstset{emph={Foo,Bar}} %,emphstyle=\bf}
+\lstdefinelanguage{myLang}
+{morekeywords={if, function, var, return, new, this}}
+
+\begin{lstlisting}[frame=single, language=myLang]
+9  var main = function() {          // main
+10   var foo = new Foo(            
+11      function(){                 // main/foo<
+12        this.welcome = "Hi!";
+13      });
+14   var bar = new Bar("GoodBye.");
+15   alert(foo.welcome);
+16   alert(bar.message);
+17 };
+18 var Foo = function(){            // Foo<    
+19   var instances;
+20   return function(initializer){  // Foo
+21     instances++;         
+22     initializer.apply(this);
+23   }
+24 }();
+25 var Baz = Bar = function(msg){   // Bar
+26   this.message = msg;
+27 }
+\end{lstlisting}
+\caption{An excerpt of a JavaScript code illustrating anonymous functions. The comments give the results from Sec.~\ref{sec:foc} and these are discussed in Sec.~\ref{sec:examples}}
+\label{js-code}
+\end{figure}
+
+\begin{figure*}[htp]
+\centerline{
+\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.png}}
+\hfil
+\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.png}}}
+\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
+\label{debuggers-objects}
+\end{figure*}
 
@@
 We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}).
-Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}.
-However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{BAZ.BAR}} class for {\small\texttt{bar}} as their summaries.
+Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|.
+However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| as their summaries.
 The first class is very general and the second one is misleading.
 The developer has to expand the object nodes to recognize their similarities and differences.
-Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary.
+Firebug classify both objects in the general \verb|Object| class, but includes some of the object properties in the summary.
 These additional properties may hint the developer about the object structures.
-{\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.
+\verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or in some cases infer misleading names.
 
@@
 \subsection{Case 2: Entry in an Array Literal}
+\label{sec:arrayLiteral}
 Contrary to the previous case the appearance of this case is very limited.
 It usually appears in initializations or when an array of functions are passed as an argument.
-Among all projects only two have instances of nameless functions defined in this way.
-For example array argument to \verb|Event._attach| in this example from YUI:
-\begin{verbatim}
+Among all projects only three have instances of nameless functions defined in this way.
+For example array argument to \verb|Event._attach| in this example from YUI \footnote[3]{The example is nested in more function definitions we do not show here.}:
+%\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   _attach: function (el, notifier, delegate) {
@@
   });
-\end{verbatim}
-\caption{An example of functions passed as arguments to a function (row 11 in Table~\ref{table:function-types} and (the inner definition) an example of a 
-function assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}. The function is from the jQuery library but simplified to fit on the page. }
+\end{lstlisting}
+\caption{An example of a function (the inner definition) assigned to a hashmap using a variable name (row 5 in Table~\ref{table:function-types}) and an example of 
+functions passed as arguments to a function (row 11 in Table~\ref{table:function-types}). The function is from the jQuery library but simplified to fit on the page. }
 \label{fig:jQueryEach}
-\end{figure*}
+\end{figure}
 
 \subsection{Case 6:  Property Assignment With  Property Name Expressions}
+\label{sec:propexpressions}
 Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
- A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values.
-Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
-\begin{verbatim}
+ A common case of expression in this case is a conditional expression, e.g., \verb|condition?"prop1":"prop2"|, where the property that we assign the function to depends upon runtime values.
+Another kind of example of computed names comes from the Prototype project (reformatted to fit in the page):
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   function define(D) {
@@
 \subsection{Case 8: Assignment to a Variable }
+This case is widely used and we expect  developers would expect the function body to get the name of the variable.
 As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
 and its internal scopes.
-Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name works will as the function name.
+There are cases in which a variable name is used temporarily, as the function is passed to another function or assigned to an object property.
+However, in most cases the variable name works well as the function name.
 
 \subsection{Case 9: Anonymous Functions Immediately Called}
-Calling functions objects just after their creations is a common pattern in JavaScript.
+Calling function objects just after their creations is a common pattern in JavaScript.
 For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example.
 \begin{figure}[htp]
-\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   Y.ClassNameManager = function () {
-
     var sPrefix = CONFIG[CLASS_NAME_PREFIX],
     sDelimiter = CONFIG[CLASS_NAME_DELIMITER];
-
     return {
@@
 \subsection{Case 10: Function Property is Accessed}
+\label{sec:funcprop}
 In this unusual case a property of the function is accessed directly from the function body.
-This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or when the predefined functions are augmented by adding to {\small\texttt{Function}} prototype.
+This case usually happens when one of the predefined functions (i.e., \verb|call, apply,| \verb|bind|) or added functions to the \verb|Function| prototype is called.
 Here is an example, from ExtJS, reformatted for display here:
-\begin{verbatim}
+\lstset{basicstyle=\scriptsize}
+\begin{lstlisting}[frame=single, language=myLang]
   setVisible : function(v, a, d, c, e){
@@
 
-\subsection{Example}
-
-To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name.
-
-The first function on line 9 is called just after its creation (see line 18) and the return sets the {\small\texttt{main}} value.
-We can explain the function object consumption after its creation in two steps.
-First the parent node is a function call (row 2 in Table~\ref{table:node-types}.
-2) the result is assigned to {\small\texttt{main}}.
-This differs from the simple variable assignment case: the value of {\small\texttt{main}} is not a function object but rather the return value of a function object.
-We summarize this by saying that the result object is produced by the function object or the function object contributed to the {\small\texttt{main}} value and we write it {\small\texttt{main<}}, where the symbol {\small\texttt{<}} indicates "contributes to".
-
-The function in line 10 is returned just after its creation.
-This function is located inside a closure function (i.e., a function which is called directly after its creation).
-This structure lets us to continue the static function object consumption analysis by assigning the return expression (the function body in line 10) to the alias set by the closure call result ({\small\texttt{main}}).
-The summary of the function object consumption will be: 1) the function object is returned , 2) the function object is assigned to {\small\texttt{main}}.
-As the function object is directly assigned to this variable we name the function {\small\texttt{main}}.
-
-The third function, line 14, is passed to a function {\small\texttt{op}} on line 13, within the body of the function we named {\small\texttt{main}} .
-Here 1) the function object is passed as an argument to function {\small\texttt{op}}, 2) The call result is assigned to {\small\texttt{result}}.
-If we simply put the identifiers in the summary together we get {\small\texttt{main/result<op()}}.
-The first part before slash  shows the context name (the enclosing function name) for this function.
-However, the function names (here {\small\texttt{op()}}) usually give an indirect information (e.g., role) about the function object.
-Therefore, as we explain in 4.5, we ignore them if other kind of identifiers (e.g., variable and property name) are available in the summary.
-After dropping {\small\texttt{op}}, we will have {\small\texttt{main/result<}}.
-Eliding identifiers is important to avoid creating long, unwieldy names.
-
-The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.
-The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
-
-\begin{table*}
+\subsection{Examples}
+\label{sec:examples}
+
+To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize five function bodies in the code, none of them has a name.
+
+The first function on line 9 is assigned to the variable \verb|main|.
+The parent node for the function body in the syntax tree will be an assignment, so in Algorithm~\ref{alg1} we skip the \verb|while| loop and compute the \verb|nameExpression| as \verb|main|.
+Ultimately this becomes the name of the function.
+
+The second function on line 11 is nested in the first one.
+It is passed as an argument to a constructor call on line 10 and the resulting object is assigned to \verb|foo|.
+In Algorithm~\ref{alg1} we create two entries in the consumption summary, one for the function call with identifier \verb|Foo| and one for the assignment with identifier \verb|foo|.
+The first one gets marked with \verb|isContributesTo|.
+Following the logic in Sec.~\ref{sec:concatenation}, we drop the function call identifier but mark the name with \verb|<| for contributes-to.
+The resulting local name is \verb|foo<| and the full name includes the enclosing function name: \verb|main/foo<|.
+
+The third function on line 18 is called immediately after definition, on line 24.
+This means the function body in the syntax tree will have a parent from the immediate call then the assignment; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|.
+The name becomes \verb|FOO<|.
+
+The fourth function on line 20 is returned by \verb|Foo<|.
+After the first pass through the \verb|while| loop in Algorithm~\ref{alg1} we enter \verb|getNextNode| and trigger the code described in Sec.~\ref{sec:immediate}.
+This will cause us to walk up the syntax tree to find the assignment target for the outer function.
+We end up with name \verb|Foo|.
+Because do not process the intermediate nodes in the \verb|while| loop we do not mark the name with contributes-to and we do not record that the function is nested.
+Of course the function body is nested, but it is bound to an un-nested variable.
+To keep the name compact we choose not to encode this complex information.
+Rather we stick to the simple picture that the function 'is' \verb|Foo|.
+If the developer wants to know more they can look up \verb|Foo| to see the construction and nesting.
+
+The fifth function on line 25 is assigned to two variables.
+This example illustrates that we stop processing in Algorithm~\ref{alg1} as soon as we hit the first assignment, giving the name \verb|Bar|.
+This aligns with our observation that the visually closest identifier is the best choice.
+
+Finally, Table~\ref{table:examples} gives the names of functions from examples discussed in \ref{sec:intuition}.
+
+\begin{table}[htb]
 \centering
-\scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
-  \hline
-\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Quality}               & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
-  \cline{2-10}
-                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
-  \hline 
-   Closure       & 8987      &   312(3\%)     & 51        & 10        &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
-  \hline 
-   DoJo          & 15866     &   3362(21\%)    & 528       & 390       &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
-  \hline 
-   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
-  \hline 
-   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
-  \hline  
-   jQuery        & 399       &   95(24\%)     & 9         & 8         &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
-  \hline  
-   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
-  \hline 
-   MooTools      & 618       &   121(19\%)    & 30        & 18        &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
-  \hline 
-   Prototype     & 442       &   125(28\%)    & 24        & 19        &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
-  \hline  
-   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
-  \hline    
-   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
-  \hline 
-   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   & N/A            & N/A         \\ 
+\scalebox{.8}{
+{\small
+\begin{tabular}{|l|l|}
+\hline
+Example Code & Static Function-Object Consumption Full Name \\
+\hline
+Sec.~\ref{sec:arrayLiteral} outer & YUI.add(event-focus)/\_attach \\
+\hline
+Sec.~\ref{sec:arrayLiteral}  inner & YUI.add(event-focus)/\_attach/Event.\_attach() \\
+\hline
+Sec.~\ref{sec:propid} & eventPool\_.createObject \\
+\hline
+Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
+\hline
+Fig.~\ref{fig:jQueryEach} inner & jQuery.each(ajaxStart)/jQuery.fn[o] \\
+\hline
+Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
+\hline
+Fig.~\ref{fig:classnamemanager}  outer & YUI.add(classnamem)/Y.ClassNameManager\textless \\
+\hline
+Fig.~\ref{fig:classnamemanager}  inner &  YUI.add(classnamem)/Y.ClassNameManager.getClassName\textless \\
+\hline
+Sec.~\ref{sec:funcprop}  inner & setVisible/cb\textless\\
+\hline
+Fig.~\ref{fig:registerWin}  inner & registerWin/ \\
 \hline
@@
 }
- \label{evaluation} 
-\caption{Results of Function Object Consumption.
-The rows are the projects listed in Appendix 1.
-First column in  contains the number of anonymous functions in each project.
-The second column shows the number of functions Firebug could not name.
-The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm;  and the fourth column is the number with only a name for enclosing scopes.
-The fifth column give the number of times a FOC function name appears twice in a file and sixth and seventh columns give the average and longest name character counts respectively.
-The last columns have two entries divided by a slash, the first is the local name and the second is the full name.}
-\end{table*}
+}
+\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
+Full names are listed, even in cases where our example code omitted the enclosing function scope.}
+\label{table:examples}
+\end{table}
 
 \section{Evaluation}
-The purpose of our evaluation is to answer the following questions: 1) How effective is the approach in naming anonymous functions?
-2) How the algorithm  improves the current approaches used in available debuggers for inferring anonymous function names?
-3) Are the proposed names are unique to be used as identifiers or conversely what portion of proposed names are duplicated?
-4) Are the proposed names appropriate for user interface presentation?
 
@@
 Although this approach is not reliable and may provide wrong names for some functions, it infers acceptable names in many simple cases.
-About 10 percent of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).The numbers show that the algorithm names more than 99 percent of the anonymous functions.
-
-The duplicates column show the number of duplicated function names.
-About 9 percent of inferred names used for more than one function in a file.
-The main source of duplicated names are test cases particularly in DOJO, ExtJS and YUI.
-%the other sources :1) function calls with no hint  2) conditional functions (e.g., based on browser)
+About 10 percent (the second column) of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).
+The third column shows that only FOC-Locall name more than 98 percent of anonymous functions.
+By adding the enclosing function names, this number increases to more than 99 percent for FOC-Full(the fourth column).
+Based on our observations, most functions remain anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.
+
+The duplicates columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-FULL.
+The number shows that Firebug assigns duplicate names to about 47 percent of anonymous functions.
+The first reason behind this huge number is that Firebug relies on regular expressions instead of abstract syntax tree for locating names.
+The second reason is that Firebug does not analyze the function object flow but tries to construct the name from the identifiers close to function definition.
+The second column shows that FOC-Local gives much less duplicates (13\%) comparing to Firebug.
+It means that local names with are sufficient for recognizing function while they have shorter length than full names.
+The third column says that less than 9 percent of anonymous functions get duplicated names by full names.
+Based on our observations, many of duplicates in projects such as DOJO, ExtJS and YUI come from test files.
+In a test file the same use case is repeated with different data and therefore the same function names appear several times.
+In projects like JQuery, Prototype, MooTools the conditional statements are the main source of duplicates.
+These libraries usually check against different environment properties (e.g., browser) to load the appropriate function.
 
@@
 The average length is at most 37 characters.
-The longest  names are typically long because of a long local name.
+The last column shows that only 3 percent of functions get local names longer than 50 characters or full names longer than 80 characters.
+Again, based on our observations a main source of long names are deep nested functions which mostly appear in test files.
+
+\begin{table*}[htp]
+\centering
+\scalebox{0.8}{
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{3}{|c|}{Local/Full Length}  \\ 
+  \cline{2-11}
+                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Average   & Longest & \textgreater50/\textgreater80 \\ 
+  \hline 
+   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 & 471/30  \\ 
+  \hline 
+   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 24/36      & 81/162 & 680/765 \\ 
+  \hline 
+   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  & 177/2 \\ 
+  \hline 
+   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 & 76/18 \\ 
+  \hline  
+   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  & 0/0 \\ 
+  \hline  
+   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80  & 0/0 \\ 
+  \hline 
+   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73  & 0/0 \\ 
+  \hline 
+   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 21/25      & 55/88  & 5/1 \\ 
+  \hline  
+   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 21/27      & 55/132 & 7/5  \\ 
+  \hline    
+   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145 & 223/292 \\ 
+  \hline 
+   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)   & N/A       & N/A      & 1639/1113 (3\%)  \\ 
+  \hline       
+  \end{tabular}
+  }
+\caption{Results of Function Object Consumption.
+The rows are the projects listed in Appendix 1.
+First column contains the number of anonymous functions in each project.
+The second column shows the number of functions Firebug could not name.
+The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number with only a name for enclosing scopes.
+The next three column gives the number of times a Firebug, FOC-Local and FOC-Full function name appears twice in a file.
+The last three columns contain the length information.
+Every cell has two entries divided by a slash, the first is the local name and the second is the full name.
+The eighth and ninth columns give the average and longest name character counts respectively.
+The last columns shows the number of functions get local names/full names with length greater than 50/80 characters.}
+ \label{evaluation} 
+\end{table*}
 
@@
 
-\section{Discussion}
-Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.
+%\section{Discussion}
+%Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.
 By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results.
@@
 
-There is room for improvements.
+%There is room for improvements.
 The heuristic elements of the naming solution need to be tuned based on more experience.
@@
 
-\subsection{Similar Function Names in a File}
-In some cases function bodies are named with the same names in a file.
+%Java Inner classes have the same problem in a smaller scale
+
+%\subsection{Similar Function Names in a File}
+%In some cases function bodies are named with the same names in a file.
 It can happen in different situations.
@@
 For these cases we add a dollar sign and an index to the similar function names.
-For example, if there are two function bodies with names {\small\texttt{myFunction}}, the functions are named as {\small\texttt{myFunction\$0}} and {\small\texttt{myFunction\$1}}.
-
-\subsection{Namer Functions}
-Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+For example, if there are two function bodies with names \verb|myFunction|, the functions are named as \verb|myFunction\$0| and \verb|myFunction\$1|.
+
+%\subsection{Namer Functions}
+%Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
 These functions usually receive a string as the class name or function name.
@@
 
-\subsection{Functions created by {\large \texttt{eval()}}}
-The function bodies in {\small\texttt{eval}} statements can be named similar to other objects as the source code is available.
+%\subsection{Functions created by {\large \texttt{eval()}}}
+%The function bodies in \verb|eval| statements can be named similar to other objects as the source code is available.
 However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
 
-\subsection{ {\texttt .displayName} }
-The ultimate fallback for function names is to allow the developer to specify them manually.
+%\subsection{ {\texttt .displayName} }
+%The ultimate fallback for function names is to allow the developer to specify them manually.
 For application developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.
@@
 % typing system papers
-
+% readability parameter paper
+
+To best of our knowledge, this paper is the first study in naming anonymous functions in JavaScript.
+However, there have been a few studies on the JavaScript programs behavior.
+In a recent work, Richards et al.
+conducted a study on dynamic behavior of JavaScript programs \cite{Richard2}.
+Although thier study contains some aspects of JavaScript function objects creation and usage, such as the number of different call sites and arities in function calls, it does not provide any data about anonymous functions.
+
+H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs.
+Their approach employs rules extracted from a big corpus of Java projects to recognize buggy names.
+To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.
+This approach assumes that the function is already named and constructs the names based on the function internal structure.
+In contrast, our approach construct the function name by analyzing the function context.
+
+Caprile and Tonella \cite{Caprile}, analyze the structure of function identifiers in C programs.
+The identifiers are decomposed into fragments that are then classified into seven lexical categories.
+The structure of the function identifiers are further described by a hand-crafted grammar.
 %JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming.
-JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}.
+JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards2}.
 As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations.
@@
 
-Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
+The result of our work can be improved and impact other aspects of JavaScript programming if a stronger typing system is employed.
+a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
+These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
+The discovered facts about variable types are not only useful for catching errors but to assist developers in code comprehension.
+Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
+Our approach can help in this regard by assigning names to nameless elements.
+
+%Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
 It can save developers' time, prevent bugs and improve the program quality.
@@
 2009.
+
+\bibitem{Host}
+E. W. H{\o}st and  B. M. {\O}stvold.\newblock Debugging Method Names.
+\newblock In \emph{Proceedings of the 23rd European conference on Object-Oriented Programming(ECOOP)},
+July, 2009.
 
@@
 JScript development in Microsoft Office 11.
-\newblock http://msdn.microsoft.com/ en-us/library/aa202668(office.11).aspx
+\newblock http://msdn.microsoft.com/en-us/library/aa202668(office.11).aspx
 
@@
 JavaScript development in OpenOffice.
-\newblock http://framework.openoffice.org/ scripting/release-0.2/javascript-devguide.html
-
-\bibitem{Richards}
+\newblock http://framework.openoffice.org/scripting/release-0.2/javascript-devguide.html
+
+\bibitem{Richards1}
+G. Richards, C. Hammer, B. Burg and J. Vitek. \newblock The Eval that Men Do.
+\newblock In \emph{Proceedings of the 25th European conference on Object-Oriented Programming(ECOOP)},
+July, 2011.
+
+\bibitem{Richards2}
 G. Richards, S. Lebresne, B. Burg and J. Vitek.\newblock An analysis of the dynamic behavior of JavaScript programs.
@@
 Server-Side JavaScript Reference v1.2.
-\newblock http://research.nihonsoft.org/ javascript/ServerReferenceJS12.
+\newblock http://research.nihonsoft.org/javascript/ServerReferenceJS12.
 

### 2011-04-14 papers/splash-wavefront2011/sigplanconf-template.tex
final pass, add discussion

@@
 
-\conferenceinfo{SPLASH Wavefront '11}{22-27 October, Portlant, Oregon, USA.} 
+\conferenceinfo{SPLASH Wavefront '11}{22-27 October, Portland, Oregon, USA.} 
 \copyrightyear{2011} 
@@
 To cope with these large and sophisticated systems, JavaScript developers turn to better development tools.
-These tools analyze then represent the program in ways that the developer might only be able to imagine through substantial time-consuming reading of source code.
+These tools analyze and represent the program in ways that the developer might only be able to imagine through substantial, time-consuming reading of source code.
 One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.
@@
 For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}.
-The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent.
+The average ratio of named functions to all functions is less then 7 percent and, excepting one project, \textit{Prototype}, the ratio does not exceed 13 percent.
 Among all functions only a very limited number of them (116 functions) are defined by the \verb|Function| constructor.
@@
 \subsection{Missed Constructor Name in Object Summary}
+\label{sec:missedctor}
 JavaScript does not support classes, but objects can be created by constructors (\verb|new| followed by a function call).
@@
 The role of constructor is to initialize the empty object.
-Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards2}, the constructor can still be useful in classifying the object.
+Unlike class-based object-oriented languages, the structure of the object  may change during the object's lifetime \cite{Richards2}.
+Nevertheless, the constructor can still be useful in classifying the object most of the time.
 Debuggers employ this fact and display the constructor name in the object summary to facilitate the developer's understanding.
@@
 \subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.png}}}
-\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
+\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.
+The content of these views is discussed in Sec.~\ref{sec:missedctor} }
 \label{debuggers-objects}
@@
 Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|.
-However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| as their summaries.
+However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| in their summaries.
 The first class is very general and the second one is misleading.
@@
 These additional properties may hint the developer about the object structures.
-\verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or in some cases infer misleading names.
+\verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior: the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or they infer a misleading name.
 
 \subsection{Anonymous Function Names in Call-stack View}
+\label{sec:callstack}
 The second problem is the call-stack.
@@
 \subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.png}}}
-\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
+\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.
+The contents of these views are discussed in Sec.~\ref{sec:callstack} }
 \label{debuggers-callstack}
@@
 
- On the other hand, for a developer who does not know the function, a function name should explains the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
+ On the other hand, for a developer who does not know the function, a function name should explain the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
 A function name must not be too long that can not be displayed or read by the developer.
-For example, the function body explains the function behavior well however it is not an appropriate function name.
+For example, the entire function body source code explains the function behavior well, however it is not an appropriate function name.
 
@@
 Then we examine each of these cases to think about how we want the functions named.
-We will ignore nesting of function scopes in the analysis to avoid taking on too much at one time.
+We will skip over the nesting of function scopes in the analysis to avoid taking on too much at one time; we return to this aspect at the end of this section.
 
@@
 %\end{verbatim}
-The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|.
+The developer will probably think of the array entry as one item in a collection passed to \verb|Event._attach|.
 In general we shall want to name these kinds of functions by the destiny of the containing array.
@@
 Following the model from Case 1, we expect a good name would combine the object name with the property identifier.
-The complication in this case comes from the object name: in general the object reference can be a computed expression \footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}.
+The complication in this case comes from the object name: in general the object reference can be a computed expression\footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}.
 Here is a simple example from the Closure project:
@@
 
- These expressions can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small.
+In general, the expression can be long and complex: to create a useful name we need to focus on developer-invented identifiers in the expression and work to keep the total number of characters small.
 For example, \verb|this.| add no information to the name since we cannot know the value of \verb|this| while parsing.
@@
 \subsection{Case 4: Property Assignment With  Property Name String}
-In JavaScript, objects are like hashmaps and their properties can also be accessed by a string can be specified in the brackets after the object.
-Semantically this is the same as the previous case and we see few instances of this form for function object assignment.
+In JavaScript, objects are like hashmaps and their properties can also be accessed by a string  specified in the brackets after the object.
+Semantically this is the same as the previous case and we see few instances of this form of function object assignment.
 The string inside the brackets can be considered a property identifier for naming.
@@
  A common case of expression in this case is a conditional expression, e.g., \verb|condition?"prop1":"prop2"|, where the property that we assign the function to depends upon runtime values.
-Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
+Another kind of example of computed names comes from the Prototype project (reformatted to fit in the page):
 \lstset{basicstyle=\scriptsize}
@@
 Calling function objects just after their creations is a common pattern in JavaScript.
-For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager}; the function is called at the bottom of the example.
+For example see the assignment to \verb|Y.ClassNameManager| in Fig.~\ref{fig:classnamemanager} (the function is called at the bottom of the example).
 \begin{figure}[htp]
@@
 If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
-In this case we cannot use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name.
+In this case we cannot use the assignment target idea from Case 1, but the source proximity and the developer-invented names concepts point to using interior identifiers in a name.
 To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.
@@
 The calling function and the other arguments look helpful, to the extent that they have identifiers invented by the developer.
-As in the example we see that the calling function, \verb|jQuery.each()| can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.
+As in this example, we see that the calling function, \verb|jQuery.each()|, can be generic so it provides less valuable information, but the arguments in that example are highly specific to the function body.
 Fig.~\ref{fig:classnamemanager} shows different example, where the function called (\verb|Y.Cached()|) seems much less important for naming the function than the property that we initialize with the result of calling the function.
@@
 JavaScript programmers are creating anonymous functions but they are loading them into object references and the expressions that result in those references have informative identifiers inside.
-Second, these expressions that we focus on may often be simple identifiers, but if they do not we will need to analyze the source of these expressions to extract meaningful summaries.
+Second, these expressions that we focus on may often be simple identifiers, but if they are not we will need to analyze the source code of these expressions to extract meaningful summaries.
 This summary has to balance information against length.
@@
 Thus we add some symbols to guide the developer to the function body in complex cases: this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance.
+We describe these symbols in Sec.~\ref{sec:concatenation}.
 
@@
 We are attempting to balance information content with length.
-Large complex expressions will give pseudo-identifiers which are complex, but with some identifiable parts.
+Large complex expressions will give pseudo-identifiers which are complex, but with some identifiable parts adequate for developer recognition and search.
 
@@
 The function-call identifiers typically tell us about a transformation of the function body before it is assigned to an object property or variable.
-The transformation may be used many places in the code, while the assignment target is typically an identifier defined by the developer.
-See for example function on line 14 and the function call on line 13 in the Figure~\ref{js-code}.
+The transformation may be used many places in the code, while the assignment target is typically an identifier defined by the developer for a specific section of source code.
+See, for example, function on line 14 and the function call on line 13 in the Figure~\ref{js-code}.
 Specifically we drop identifiers from row 2 of table~\ref{table:node-types} in any case where we have identifiers from rows 1 or 3.
@@
 This means the function body in the syntax tree will have a parent from the immediate call then the assignment; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|.
-The name becomes \verb|FOO<|.
+The name becomes \verb|Foo<|.
 
@@
 
-In Table~\ref{evaluation} We compared our results to Firebug's naming output for each of the 10 projects used previously and listed in Appendix 1.
+In Table~\ref{evaluation} we compared our results to Firebug's naming output for each of the 10 projects used previously and listed in Appendix 1.
 Firebug does not use a parser for naming functions.
@@
 About 10 percent (the second column) of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).
-The third column shows that only FOC-Locall name more than 98 percent of anonymous functions.
+The third column shows that more than 98 percent of anonymous functions have a FOC-defined local name.
 By adding the enclosing function names, this number increases to more than 99 percent for FOC-Full(the fourth column).
-Based on our observations, most functions remain anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.
-
-The duplicates columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-FULL.
-The number shows that Firebug assignes duplicate names to about 47 percent of anonymous functions.
-The first reason behind this huge number is that Firebug relies on regular expressions instead of abastract syntax tree for locating names.
+Based on our observations, most functions remaining anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.
+
+The "Duplicates By" columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-Full.
+The number shows that Firebug assigns duplicate names to about 47 percent of anonymous functions.
+The first reason behind this huge number is that Firebug relies on regular expressions instead of abstract syntax tree for locating names.
 The second reason is that Firebug does not analyze the function object flow but tries to construct the name from the identifiers close to function definition.
 The second column shows that FOC-Local gives much less duplicates (13\%) comparing to Firebug.
-It means that local names with are sufficient for recognizing function while they have shorter length than full names.
+This means that local names are sufficient for recognizing functions within a file, which is helpful because they have shorter length than full names.
 The third column says that less than 9 percent of anonymous functions get duplicated names by full names.
@@
 The average length is at most 37 characters.
-The longest names are typically long because of a long local name.
-Again in most cases long names apear in test files due to deep nested functions.
+The last column shows that only 3 percent of functions get local names longer than 50 characters or full names longer than 80 characters.
+Again, based on our observations a main source of long names are deep nested functions which mostly appear in test files.
 
@@
 \scalebox{0.8}{
-  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
-  \hline
-\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
-  \cline{2-10}
-                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Avgerage   & Longest  \\ 
-  \hline 
-   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 \\ 
-  \hline 
-   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 35/36      & 81/162 \\ 
-  \hline 
-   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  \\ 
-  \hline 
-   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 \\ 
-  \hline  
-   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  \\ 
-  \hline  
-   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80   \\ 
-  \hline 
-   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73   \\ 
-  \hline 
-   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 23/25      & 55/88    \\ 
-  \hline  
-   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 22/27      & 55/132   \\ 
-  \hline    
-   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145  \\ 
-  \hline 
-   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)  & N/A       & N/A         \\ 
+  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l | l |}
+  \hline
+\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Duplicates by}              & \multicolumn{3}{|c|}{Local/Full Length}  \\ 
+  \cline{2-11}
+                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    Firebug          &    FOC-Local   & FOC-Full    & Average   & Longest & \textgreater50/\textgreater80 \\ 
+  \hline 
+   Closure       & 8987      &   312(3\%)     & 51        & 10        &    662(7\%)         &    211(2\%)    & 103(1\%)    & 33/35      & 76/101 & 471/30  \\ 
+  \hline 
+   DoJo          & 15866     &   3362(21\%)   & 528       & 390       &    3325(21\%)       &    2993(19\%)  & 2287(14\%)  & 24/36      & 81/162 & 680/765 \\ 
+  \hline 
+   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    23777(65\%)      &    3737(10\%   & 2342(7\%)   & 22/25      & 65/91  & 177/2 \\ 
+  \hline 
+   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    481(16\%)        &    85(3\%)     & 32(1\%)     & 27/36      & 70/140 & 76/18 \\ 
+  \hline  
+   jQuery        & 399       &   95(24\%)     & 9         & 8         &    162(40\%)        &    97(24\%)    & 56(14\%)    & 14/18      & 50/65  & 0/0 \\ 
+  \hline  
+   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    491(27\%)        &    314(17\%)   & 191(10\%)   & 17/22      & 49/80  & 0/0 \\ 
+  \hline 
+   MooTools      & 618       &   121(19\%)    & 30        & 18        &    272(44\%)        &    158(26\%)   & 138(22\%)   & 12/14      & 36/73  & 0/0 \\ 
+  \hline 
+   Prototype     & 442       &   125(28\%)    & 24        & 19        &    154(35\%)        &    70(16\%)    & 70(16\%)    & 21/25      & 55/88  & 5/1 \\ 
+  \hline  
+   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    306(36\%)        &    131(19\%)   & 86(9\%)     & 21/27      & 55/132 & 7/5  \\ 
+  \hline    
+   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    10073(47\%)      &    3558(17\%)  & 2205(10\%)  & 16/37      & 114/145 & 223/292 \\ 
+  \hline 
+   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    39703(44\%)      &    11354(13\%) & 7510(8\%)   & N/A       & N/A      & 1639/1113 (3\%)  \\ 
   \hline       
@@
 The second column shows the number of functions Firebug could not name.
-The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number with only a name for enclosing scopes.
-The next three column gives the number of times a Firebug, FOC-Local and FOC-Full function name appears twice in a file and eighth and nineth columns give the average and longest name character counts respectively.
-The last columns have two entries divided by a slash, the first is the local name and the second is the full name.}
+The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number of functions the FOC leaves without a name even from enclosing scopes.
+The next three columns give the number of times a Firebug, FOC-Local, and FOC-Full function name appears twice in a file, respectively.
+The last three columns contain the length information.
+Every cell has two entries divided by a slash, the first is the local name and the second is the full name.
+The eighth and ninth columns give the average and longest name character counts respectively.
+The last columns shows the number of functions with local names greater then 50 characters in length separated by a slash from the number of functions wit full names with length greater than 80 characters.}
  \label{evaluation} 
@@
 
-\subsection{Similar Function Names in a File}
-In some cases function bodies are named with the same names in a file.
+A complete naming solution will need to consider some addition issues.
+The user interface that shows names typically has limited space and even our efforts to create short names may be adequate.
+Often the hierarchy can help: we can show the trailing entry in a slash delimited list and the trailing entry in a dot delimited list with mouse-over expansion to bring up an overlay line with more of the full name displayed.
+Some JavaScript libraries have a regular pattern or specific re-naming registration system (see for example the ExtJS ClassManager\cite{ExtJSClassManager}).
+A naming solution should recognize these patterns or systems.
+Similarly JavaScript libraries might support the \verb|.displayName| to provide custom names where the developer overhead to introduce and maintain the extra field is justified by the wide spread use of the library.
+
+%Java Inner classes have the same problem in a smaller scale
+
+%\subsection{Similar Function Names in a File}
+%In some cases function bodies are named with the same names in a file.
 It can happen in different situations.
@@
 
-\subsection{Namer Functions}
-Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
+%\subsection{Namer Functions}
+%Many JavaScript projects have one or a few functions which are used for defining classes or registering function objects.
 These functions usually receive a string as the class name or function name.
@@
 
-\subsection{Functions created by {\large \texttt{eval()}}}
-The function bodies in \verb|eval| statements can be named similar to other objects as the source code is available.
+%\subsection{Functions created by {\large \texttt{eval()}}}
+%The function bodies in \verb|eval| statements can be named similar to other objects as the source code is available.
 However, eval scripts have no file name and therefore, it causes issues for assigning appropriate packages name to these functions.
 
-\subsection{ {\texttt .displayName} }
-The ultimate fallback for function names is to allow the developer to specify them manually.
+%\subsection{ {\texttt .displayName} }
+%The ultimate fallback for function names is to allow the developer to specify them manually.
 For application developers this is tedious path, but for library developers the cost may be justified by the many potential developers who will see the custom name.
@@
 To best of our knowledge, this paper is the first study in naming anonymous functions in JavaScript.
+However, there have been a few studies on the JavaScript programs behavior.
+In a recent work, Richards et al.
+conducted a study on dynamic behavior of JavaScript programs \cite{Richards2}.
+Although thier study contains some aspects of JavaScript function objects creation and usage, such as the number of different call sites and arities in function calls, it does not provide any data about anonymous functions.
+
+We previously mentioned four JavaScript naming approaches: Zaytsev advocates expanded use of names in function expressions\cite{Zaytsev}, support for \verb|displayName| in debuggers has been requested\cite{DisplayName}, the Firebug Regular expressions, and the Google Chrome debugger's function name 'inference'\cite{ChromeInfer}.
+The last one appears to be a parser based approach with goals similar to the ad-hoc Firebug regular expressions: look for identifiers preceding anonymous function bodies.
+
 H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs.
@@
 
-Caprile and Tonella \cite{Caprile}, analyse the structure of function identifiers in C programs.
+Caprile and Tonella \cite{Caprile}, analyze the structure of function identifiers in C programs.
 The identifiers are decomposed into fragments that are then classified into seven lexical categories.
@@
 
-Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
+The result of our work can be improved and impact other aspects of JavaScript programming if a stronger typing system is employed.
+A few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
+These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
+The discovered facts about variable types are not only useful for catching errors but to assist developers in code comprehension.
+Nevertheless, none of the mentioned approaches provided effective means for sharing this information with the developer.
+Our approach can help in this regard by assigning names to nameless elements.
+
+%Catching errors early (i.e., before or at the compilation time) is an important feature for development environments.
 It can save developers' time, prevent bugs and improve the program quality.
@@
 
+\bibitem{ChromeInfer}
+V8 Google FuncNameInferrer 
+\newblock http://v8.googlecode.com/svn/trunk/src/func-name-inferrer.h
+
 \bibitem{CJS}
@@
 
+\bibitem{ExtJSClassManager}
+Jacky Nguyen
+\newblock \emph{Ext.ClassManager}
+\newblock http://dev.sencha.com/deploy/ext-4.0-beta2/docs/source/ClassManager.html
+
 \bibitem{FAO}
@@
 JavaScript development in OpenOffice.
-\newblock http://framework.openoffice.org/ scripting/release-0.2/javascript-devguide.html
+\newblock http://framework.openoffice.org/scripting/release-0.2/javascript-devguide.html
 

### 2011-04-14 papers/splash-wavefront2011/sigplanconf-template.tex
two correction from salman

@@
 \section{Discussion}
-Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.
+Overall the Function-Object Consumption approach dramatically reduces the number of functions that a development tool cannot name for a developer.
 By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results.
@@
 H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs.
-Their approach employs rules extracted from a big corpus of Java projects to recognize buggy names.
+Their approach employs rules extracted from a large corpus of Java projects to recognize buggy names.
 To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.

### 2011-04-14 papers/splash-wavefront2011/sigplanconf-template.tex
complete appendix 1

@@
 
-%\appendix
-%\section{JavaScript Projects Analyzed for Function Names}
-%\begin{description}
-%\item[Closure] Google Web Library, ...
-%\item[Dojo] JavaScript Toolkit
-%\item[ExtJS] JavaScript Framework
-%\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
-%\item[jQuery]
-%\item[MochiKit]
-%\item[MooTools]
-%\item[Prototype]
-%\item[Scriptaculous]
-%\item[YUI]
-%\end{description}
+\appendix
+\section{JavaScript Projects Analyzed for Function Names}
+\begin{description}
+\item[Closure] Closure Library, r683, Google Code, \\
+http://code.google.com/p/closure-library/
+\item[Dojo] Dojo JavaScript Toolkit, version 1.5, \\
+http://dojotoolkit.org/
+\item[ExtJS] JavaScript Framework, version 3.3.1 \\
+http://www.sencha.com/products/extjs/
+\item[Firebug] Web Page Debugger, version 1.7 \\
+ http://code.google.com/p/fbug/.
+\item[jQuery] JavaScript Library, version 1.4.4\\
+http://jquery.com/
+\item[MochiKit] version 1.4.2 \\
+http://mochi.github.com/mochikit/
+\item[MooTools] JavaScript Framework, version 1.3 \\
+http://mootools.net/
+\item[Prototype] JavaScript Framework, version 1.7 \\
+http://www.prototypejs.org/
+\item[Scriptaculous] JavaScript Library, version 1.9 \\
+http://script.aculo.us/
+\item[YUI] Library, Yahoo, Inc., version 3.3 \\
+http://developer.yahoo.com/yui/
+\end{description}
 

### 2011-04-14 papers/splash-wavefront2011/sigplanconf-template.tex
include Claude's corrections

@@
 JavaScript developers create and call functions; they use functions to construct objects.
-JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations.
-However, developers need not to specify names for functions.
+JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and in object representations.
+However, most functions are anonymous: developers need not to specify names for functions.
  Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
-By studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions.
-We applied our approach to 90000 anonymous functions appeared in the analyzed JavaScript project.
-The approach is successful in naming more than 99\% (91\% are unique in file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.
+After studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for providing names to nameless JavaScript functions.
+We applied our approach to 90000 anonymous functions that appeared in the analyzed JavaScript project.
+The approach is successful in naming more than 99\% (91\% are unique within their file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.
 
@@
 Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
-This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}.
+This language is used by the Web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}.
 It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade.
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
-Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards2}.
+Moreover, JavaScript is also becoming a general purpose computing platform\cite{Richards2} for office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and even program development environments \cite{Ingalls}.
 There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.
 
-To cope with these large and sophisticated systems, JavaScript developers turn to better development tools.
-These tools analyze and represent the program in ways that the developer might only be able to imagine through substantial, time-consuming reading of source code.
+To cope with these large and sophisticated systems, JavaScript developers turn to development tools.
 One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.
@@
 All of these tools need to express program artifacts in a compact way the developer can understand.
-For example, the debugger needs to present the execution call stack so the developer can understand which functions are currently active.
+For example, the debugger must present the execution call stack so the developer can understand which functions are currently active.
 Obviously a particularly good compact representation would be a name given by the developer in the source code.
@@
 
-Among program artifacts, functions are central to program comprehension in JavaScript.
+Among program artifacts, functions are central to understanding a JavaScript program.
 In addition to their role in the execution stack, they are first-class objects that are used for different purposes by developers; they may be used as an object constructor, a closure scope (module) or even  passed as an argument in a function call.
-However, functions can be defined and created without a name or identifier.
+These functions can be defined and created without a name or identifier.
 
 In this paper, we analyze ten large, well-known projects. We show that within these projects less than 7\% of the function bodies are named. 
-We analyze the syntactic constructs that function bodies appear in and rationalize how developers think about the bodies in relation to the structure of the code.
+We analyze the syntactic constructs surrounding these function bodies and rationalize how developers think about the bodies in relation to the structure of the code.
+
 We propose an automated approach based on extracted data from the source code for naming JavaScript functions.
-The candidate function names can be used in debuggers for more descriptive object summaries and call-stack view, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
+The candidate function names can be used in debuggers for more descriptive object summaries and call-stack views, or in integration with proposed JavaScript typing systems for providing modern editing features in development environments.
 
@@
 Two main issues appear in debuggers due to the lack of function name.
-First, object constructor name, which can facilitate understanding the object value, is not available in the object summary.
+First, the object constructor name, which can facilitate understanding the object value, is not available in the object summary.
 Second, the call-stack view is usually full of \textit{anonymous} functions and therefore much less informative.
@@
 Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|.
-However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| in their summaries.
+
+The Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| in their summaries.
 The first class is very general and the second one is misleading.
 The developer has to expand the object nodes to recognize their similarities and differences.
-Firebug classify both objects in the general \verb|Object| class, but includes some of the object properties in the summary.
-These additional properties may hint the developer about the object structures.
+
+Firebug classifies both objects in the general \verb|Object| class, but includes some of the object properties in the summary.
+These additional properties may give a hint to the developer about the object structures.
 \verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior: the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or they infer a misleading name.
@@
 The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms.
-Among three last functions in the call stack, Google Chrome only shows the name of first function (\verb|main|) correctly.
-For the second function (line 22), it shows \verb|anonymous|, and for the last function (line 12), it gives a wrong name, \verb|foo|.
+Among the three top functions in the call stack, Google Chrome shows only the name of the third one down, function (\verb|main|), correctly.
+For the second frame from the top (marked as line 22), it shows \verb|anonymous|, and for the top frame (marked at line 12), it gives a wrong name, \verb|foo|.
 Firebug performs better by guessing two function names correctly, but it still fails in one case.
-It shows \verb|main| as the name of last function(line 12) which is the name of another function (the enclosing function at line 9).
-In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.
+It shows \verb|main| as the name of the function on the top frame (marked at line 12) but this is the name of another function (the enclosing function at line 9).
+In these cases, the information provided by the debugger is useless and the developer has to locate the function source to understand or recall the function behavior.
 
@@
 For example, a new property (e.g., \textit{displayName}) in the function object can be used for storing the function name, or the function name can be defined by an annotation.
-Although these solutions may help, they cause developers extra work, the displayName value can become out of sync with the meaning of the code over time,  the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.
+Although these solutions may help, they require extra work from developers, the displayName value can become out of sync with the meaning of the code over time,  the annotation may be incorrectly recognized in programs that use the same property name for another purpose, and maintenance of the debugger becomes more difficult once the call-stack names can be overridden by user code.
 
@@
 
-Once a statement which defines a function is evaluated, a new \verb|Function| 
-object is created.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
+A statement defining a function creates new \verb|Function| 
+object.  The definition may be evaluated multiple times, and depending on the times a function definition is evaluated, 
 zero to many \verb|Function| objects can be created from the same definition. 
 Two function objects which are created from the same function body may have different object properties added at runtime.
-They also may have different enclosing scopes and therefore different behaviors.
+They may also have different enclosing scopes and therefore different behaviors.
 Thus our first
-decision: do we try to name the \verb|Function| objects or the source that defines them?
-
-For the common use cases, the different \verb|Function| objects are bound to one or more properties of objects.
+question: do we try to name the \verb|Function| objects or the source that defines them?
+
+For the common cases, the different \verb|Function| objects are bound to one or more properties of objects.
 The  names of these properties inform the developer about the role of the function in the actions of the object.
@@
 For example, a naive proposal for the function name is a combination of the function file name and its first line number.
-Although it may work as an identifier, but it does not assist the developer to recall or understand the function behavior.
+Although it may work as an identifier, it does not assist the developer to recall or understand the function behavior.
 
  On the other hand, for a developer who does not know the function, a function name should explain the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
-A function name must not be too long that can not be displayed or read by the developer.
+A function name must not be so long that it can not be displayed or read by the developer.
 For example, the entire function body source code explains the function behavior well, however it is not an appropriate function name.
@@
 As the project size and the number of functions increases, the short function name will not be enough for recognizing the function.
-The developer also wants the class or the module contains the function.
+The developer also wants the class or the module that contains the function.
 In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.
@@
 We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
-We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.
+We have to create salient information from source code: we anticipate that removing characters will be our biggest challenge.
 To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
@@
 
-For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.
+For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of these 12 cases, giving the numerical results in Table~\ref{function-type-count}.
 Then we examine each of these cases to think about how we want the functions named.
@@
 \subsection{Case 1: Object Property Initializer}
- This case usually appears when developers try to group a set of functions in a new object.
+ This case usually appears when developers tries to group a set of functions in a new object.
 A common case is grouping a set of functions in the \verb|prototype| property of the constructor.
@@
 
-Following the model from Case 1, we expect a good name would combine the object name with the property identifier.
+Following the model from Case 1, we think a good name would combine the object name with the property identifier.
 The complication in this case comes from the object name: in general the object reference can be a computed expression\footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}.
@@
 In this case we cannot use the assignment target idea from Case 1, but the source proximity and the developer-invented names concepts point to using interior identifiers in a name.
-To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.
+To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create in this way is for an immediately called function.
 
@@
 In constructing names we realized one additional aspect: as we move from simple object property names to more complex examples, the path of the object consumption is an added bit of information helpful in naming.
-Thus we add some symbols to guide the developer to the function body in complex cases: this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance.
+Thus we add some symbols to guide the developer to the function body in complex cases: in this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance.
 We describe these symbols in Sec.~\ref{sec:concatenation}.
@@
 For an example, see line 10 of the Figure~\ref{js-code} which is enclosed in the function on line 9.
-If the developer returns a function from this outer, immediate function we want to follow the returned object to where it is consumed.
+If the developer returns a function from this outer, immediate function, we want to follow the returned object to where it is consumed.
 
@@
 In simple cases the syntax tree node will have an identifier we can use as part of our name.
-In more complex cases an expression will written in place of an identifier.
+In more complex cases an expression will be written in place of an identifier.
 We reduce these expressions to pseudo-identifiers (i.e.
@@
 This work is done during the Object Consumption Summary algorithm in the functions described here:
-\paragraph{Identifiers for Function Arguments} Search for all literal string nodes in other arguments and concatenated them by ``-'', dropping  characters over 10.  
+\paragraph{Identifiers for Function Arguments} Search for all literal string nodes in other arguments and concatenated them by ``-'', dropping  characters beyond 10.  
  (This work is on in Algorithm~\ref{alg1} in \verb|argSummary|).
@@
 
-The name is built by the above process does not contain any information about enclosing scopes.
+The name built by the above process does not contain any information about enclosing scopes.
 We call it \textit{local name}.
-We get the function \textit{full name} by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
+We get the function \textit{full name} (that is a local name qualified by its position in the scope hierarchy) by adding the enclosing function full-name with a slash before the local-name, recursing through enclosing scopes.
 This full-name is the function body name.
@@
 The third function on line 18 is called immediately after definition, on line 24.
-This means the function body in the syntax tree will have a parent from the immediate call then the assignment; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|.
+This means the function body in the syntax tree will have a parent from the immediate call and then the assignment parent node; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|.
 The name becomes \verb|Foo<|.
@@
 The rows are the projects listed in Appendix 1.
-First column contains the number of anonymous functions in each project.
+The first column contains the number of anonymous functions in each project.
 The second column shows the number of functions Firebug could not name.
@@
 conducted a study on dynamic behavior of JavaScript programs \cite{Richards2}.
-Although thier study contains some aspects of JavaScript function objects creation and usage, such as the number of different call sites and arities in function calls, it does not provide any data about anonymous functions.
+Although their study contains some aspects of JavaScript function objects creation and usage, such as the number of different call sites and arities in function calls, it does not provide any data about anonymous functions.
 
@@
 Their approach employs rules extracted from a large corpus of Java projects to recognize buggy names.
-To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.
+To fix a name, a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.
 This approach assumes that the function is already named and constructs the names based on the function internal structure.
@@
 Our contributions in this paper include an empirical study of the extent of anonymous functions in JavaScript libraries, categorization of those functions to understand the potential for automatic naming, an practical algorithm based on the empirical study, and its evaluation.
-We believe our results can be applied directly in existing JavaScript development tools to give immediate benefit to developers and they provide a basis for future improvements.
+We believe our result can be applied directly in existing JavaScript development tools to give immediate benefit to developers and provides a basis for future improvements.
 

### 2011-04-14 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
final changes to avoid splitting code

@@
 \begin{abstract}
-JavaScript developers create and call functions; they use functions to construct objects.
-JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and object representations.
-However, developers need not to specify names for functions.
+JavaScript developers create programs by calling functions and they use functions to construct objects.
+JavaScript development tools need to report to developers about those functions and constructors, for example in debugger call-stacks and in object representations.
+However, most functions are anonymous: developers need not to specify names for functions.
  Based on our analysis of ten large, widely used JavaScript projects, less than 7\% of JavaScript functions are named by developers. 
-By studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for naming nameless JavaScript functions.
-We applied our approach to 90000 anonymous functions appeared in the analyzed JavaScript project.
-The approach is successful in naming more than 99\% (91\% are unique in file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.
+After studying examples from these JavaScript projects, we propose \textit{Static Function-Object Consumption}, a principled, automated approach based on local source code analysis for providing names to nameless JavaScript functions.
+We applied our approach to 90000 anonymous functions that appeared in the analyzed JavaScript project.
+The approach is successful in naming more than 99\% (91\% are unique within their file) of anonymous functions while the average length of function names is kept less than 37 characters.% which is appropriate for presentation.
 
@@
 Along with the wave of ``Web 2.0", JavaScript has become the inevitable part of almost every modern web site.
-This language is used by all of the web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}.
+This language is used by the Web's 100 most popular sites\footnote[1]{http://www.alexa.com}\cite{Richards1}.
 It is very likely that JavaScript keeps this crucial role for the next few years or even the next decade.
 Along with the growth of demands for more comprehensive user interfaces, the size and the complexity of web applications is increasing.
-Moreover, JavaScript is also becoming a general purpose computing platform with office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and development environments \cite{Ingalls} being developed in JavaScript \cite{Richards2}.
+Moreover, JavaScript is also becoming a general purpose computing platform\cite{Richards2} for office applications \cite{JSOffice, JSOffice2}, browsers \cite{FAO, GCE} and even program development environments \cite{Ingalls}.
 There are also proposals for employing JavaScript in server-side applications \cite{SSJSR, CJS}.
 
-To cope with these large and sophisticated systems, JavaScript developers turn to better development tools.
-These tools analyze then represent the program in ways that the developer might only be able to imagine through substantial time-consuming reading of source code.
+To cope with these large and sophisticated systems, JavaScript developers turn to development tools.
 One prime example is a runtime debugger: the developer can halt a running program and examine the program state and execution call stack.
@@
 Two objects assigned to variables \verb|foo| and \verb|bar| are constructed by two different constructors: \verb|Foo| and \verb|Bar|.
-However, Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| as their summaries.
+
+The Google Chrome debugger shows the general class of \verb|Object| for \verb|foo| and the \verb|Baz.Bar| class for \verb|bar| in their summaries.
 The first class is very general and the second one is misleading.
 The developer has to expand the object nodes to recognize their similarities and differences.
-Firebug classify both objects in the general \verb|Object| class, but includes some of the object properties in the summary.
-These additional properties may hint the developer about the object structures.
-\verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or in some cases infer misleading names.
+
+Firebug classifies both objects in the general \verb|Object| class, but includes some of the object properties in the summary.
+These additional properties may give a hint to the developer about the object structures.
+\verb|Foo| and \verb|Bar| definitions at lines 20 and 25 explain the debuggers' behavior: the function statements has no explicit name (identifier), therefore debuggers considered them as anonymous functions or they infer a misleading name.
 
 \subsection{Anonymous Function Names in Call-stack View}
+\label{sec:callstack}
 The second problem is the call-stack.
@@
 For example, a naive proposal for the function name is a combination of the function file name and its first line number.
-Although it may work as an identifier, but it does not assist the developer to recall or understand the function behavior.
-
- On the other hand, for a developer who does not know the function, a function name should explains the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
-A function name must not be too long that can not be displayed or read by the developer.
-For example, the function body explains the function behavior well however it is not an appropriate function name.
+Although it may work as an identifier, it does not assist the developer to recall or understand the function behavior.
+
+ On the other hand, for a developer who does not know the function, a function name should explain the function behavior, or an abstraction of the function behavior, or why/where the function is used/defined (e.g., to create the object \textit{foo}).
+A function name must not be so long that it can not be displayed or read by the developer.
+For example, the entire function body source code explains the function behavior well, however it is not an appropriate function name.
 
@@
 As the project size and the number of functions increases, the short function name will not be enough for recognizing the function.
-The developer also wants the class or the module contains the function.
+The developer also wants the class or the module that contains the function.
 In addition to the package name, knowing the context (the enclosing function body) that contains the function can help in better understanding the function behavior.
-
-\section{Building Up Intuition by Example}
-\label{sec:intuition}
-We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
-We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.
-To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
-We want to see what kinds of cases are important and what aspects of these cases help us identify functions.
-
-For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of 12 cases, giving the numerical results in Table~\ref{function-type-count}.
-Then we examine each of these cases to think about how we want the functions named.
-We will ignore nesting of function scopes in the analysis to avoid taking on too much at one time.
 
@@
 
+\section{Building Up Intuition by Example}
+\label{sec:intuition}
+We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions.
+We have to create salient information from source code: we anticipate that removing characters will be our biggest challenge.
+To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions.
+We want to see what kinds of cases are important and what aspects of these cases help us identify functions.
+
+For this purpose we created 12 categories of function body expressions shown in Table~\ref{table:function-types} and we categorized all of the nameless functions from the 10 JavaScript projects into one of these 12 cases, giving the numerical results in Table~\ref{function-type-count}.
+Then we examine each of these cases to think about how we want the functions named.
+We will skip over the nesting of function scopes in the analysis to avoid taking on too much at one time; we return to this aspect at the end of this section.
+
 \begin{table*}[htp]
@@
 
-Following the model from Case 1, we expect a good name would combine the object name with the property identifier.
-The complication in this case comes from the object name: in general the object reference can be a computed expression \footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}.
+Following the model from Case 1, we think a good name would combine the object name with the property identifier.
+The complication in this case comes from the object name: in general the object reference can be a computed expression\footnote[4]{This comment applies to all of the cases in table~\ref{table:function-types} marked with an asterisk on the expression identifier}.
 Here is a simple example from the Closure project:
@@
 If the function call has no result, it means that the function performs one task (e.g., initialization of some values in the outer scope for later use).
-In this case we cannot use the assignment target idea from Case 1, but source proximity and developer-invented names point to using interior identifiers in a name.
-To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create this way is for an immediately called function.
+In this case we cannot use the assignment target idea from Case 1, but the source proximity and the developer-invented names concepts point to using interior identifiers in a name.
+To avoid confusing the developer by using the same name for the outer and interior functions, we will need some way to signify that the name we create in this way is for an immediately called function.
 
@@
 In constructing names we realized one additional aspect: as we move from simple object property names to more complex examples, the path of the object consumption is an added bit of information helpful in naming.
-Thus we add some symbols to guide the developer to the function body in complex cases: this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance.
+Thus we add some symbols to guide the developer to the function body in complex cases: in this way the extra information does not take a lot of space and it can be ignored by developers who have not yet learned about its significance.
+We describe these symbols in Sec.~\ref{sec:concatenation}.
 
@@
 \label{sec:nodewalk}
-
-We parse the JavaScript and search the resulting syntax tree for function body nodes.
-For each function body, we apply the algorithm outlined in Algorithm~\ref{alg1}.
-The basic idea (the \verb|while| loop) is to walk the syntax tree from the body up through parent nodes until we hit a node that is not a JavaScript expression.
-For each node we create an entry in a list and record in it information about the relationship between the node and its parent.
-We'll use this relationship information in Sec.~\ref{sec:concatenation}.
-Then for each node  we record developer-invented identifiers related to the destiny of the function object created from the body as outlined in  Table~\ref{table:node-types}.
-For the first and third rows of the table we record the information recursively; for the second row,  assignment node, we record the information after the loop terminates.
-The algorithm ends when we reach a node which is an assignment or a statement which does not return any value (i.e., the node is not an expression).
-The algorithm result is an \textit{object consumption summary}, a list of collected data at every visited parent node of the function body.
-
-The algorithm uses three subroutines: \verb|getNextNode|,  \verb|nameExpression|, and \verb|argSummary|.
-The \verb|getNextNode| routine normally returns \verb|n.parent|, but we also use this point in the algorithm to handle an important special case, function bodies inside of \textit{immediate functions} typically used for modularity or scoping in JavaScript.
-We discuss this case in Sec.~\ref{sec:immediate}.
-The remaining two subroutines construct a pseudo-identifier from the expression as described in \ref{sec:general-element-naming}; they return their argument if it is simply an identifier.
 
@@
 
+We parse the JavaScript and search the resulting syntax tree for function body nodes.
+For each function body, we apply the algorithm outlined in Algorithm~\ref{alg1}.
+The basic idea (the \verb|while| loop) is to walk the syntax tree from the body up through parent nodes until we hit a node that is not a JavaScript expression.
+For each node we create an entry in a list and record in it information about the relationship between the node and its parent.
+We'll use this relationship information in Sec.~\ref{sec:concatenation}.
+Then for each node  we record developer-invented identifiers related to the destiny of the function object created from the body as outlined in  Table~\ref{table:node-types}.
+For the first and third rows of the table we record the information recursively; for the second row,  assignment node, we record the information after the loop terminates.
+The algorithm ends when we reach a node which is an assignment or a statement which does not return any value (i.e., the node is not an expression).
+The algorithm result is an \textit{object consumption summary}, a list of collected data at every visited parent node of the function body.
+
+The algorithm uses three subroutines: \verb|getNextNode|,  \verb|nameExpression|, and \verb|argSummary|.
+The \verb|getNextNode| routine normally returns \verb|n.parent|, but we also use this point in the algorithm to handle an important special case, function bodies inside of \textit{immediate functions} typically used for modularity or scoping in JavaScript.
+We discuss this case in Sec.~\ref{sec:immediate}.
+The remaining two subroutines construct a pseudo-identifier from the expression as described in \ref{sec:general-element-naming}; they return their argument if it is simply an identifier.
+
 \begin{table}
@@
 The third function on line 18 is called immediately after definition, on line 24.
-This means the function body in the syntax tree will have a parent from the immediate call then the assignment; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|.
-The name becomes \verb|FOO<|.
+This means the function body in the syntax tree will have a parent from the immediate call and then the assignment parent node; the call does not give us an identifier but it does give a consumption summary entry with \verb|isContributesTo|.
+The name becomes \verb|Foo<|.
 
@@
 About 10 percent (the second column) of anonymous functions still remained nameless in Firebug (in addition, some named functions may be quite incorrect because of the simple algorithm).
-The third column shows that only FOC-Locall name more than 98 percent of anonymous functions.
+The third column shows that more than 98 percent of anonymous functions have a FOC-defined local name.
 By adding the enclosing function names, this number increases to more than 99 percent for FOC-Full(the fourth column).
-Based on our observations, most functions remain anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.
-
-The duplicates columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-FULL.
+Based on our observations, most functions remaining anonymous in FOC-Full are top level \textit{immediate} functions which are usually used for creating a local scope for a set of variables.
+
+The "Duplicates By" columns show the number of functions which get a name which is also assigned to another function(s) for Firebug, FOC-Local and FOC-Full.
 The number shows that Firebug assigns duplicate names to about 47 percent of anonymous functions.
@@
 The second column shows that FOC-Local gives much less duplicates (13\%) comparing to Firebug.
-It means that local names with are sufficient for recognizing function while they have shorter length than full names.
+This means that local names are sufficient for recognizing functions within a file, which is helpful because they have shorter length than full names.
 The third column says that less than 9 percent of anonymous functions get duplicated names by full names.
@@
 The rows are the projects listed in Appendix 1.
-First column contains the number of anonymous functions in each project.
+The first column contains the number of anonymous functions in each project.
 The second column shows the number of functions Firebug could not name.
-The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number with only a name for enclosing scopes.
-The next three column gives the number of times a Firebug, FOC-Local and FOC-Full function name appears twice in a file.
+The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm; and the fourth column is the number of functions the FOC leaves without a name even from enclosing scopes.
+The next three columns give the number of times a Firebug, FOC-Local, and FOC-Full function name appears twice in a file, respectively.
 The last three columns contain the length information.
@@
 The eighth and ninth columns give the average and longest name character counts respectively.
-The last columns shows the number of functions get local names/full names with length greater than 50/80 characters.}
+The last columns shows the number of functions with local names greater then 50 characters in length separated by a slash from the number of functions wit full names with length greater than 80 characters.}
  \label{evaluation} 
@@
 
-%\section{Discussion}
-%Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.
+\section{Discussion}
+Overall the Function-Object Consumption approach dramatically reduces the number of functions that a development tool cannot name for a developer.
 By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results.
@@
 
-%There is room for improvements.
+There is room for improvements.
 The heuristic elements of the naming solution need to be tuned based on more experience.
@@
 We also leave some cases anonymous which need further investigation.
+
+A complete naming solution will need to consider some addition issues.
+The user interface that shows names typically has limited space and even our efforts to create short names may be adequate.
+Often the hierarchy can help: we can show the trailing entry in a slash delimited list and the trailing entry in a dot delimited list with mouse-over expansion to bring up an overlay line with more of the full name displayed.
+Some JavaScript libraries have a regular pattern or specific re-naming registration system (see for example the ExtJS ClassManager\cite{ExtJSClassManager}).
+A naming solution should recognize these patterns or systems.
+Similarly JavaScript libraries might support the \verb|.displayName| to provide custom names where the developer overhead to introduce and maintain the extra field is justified by the wide spread use of the library.
 
@@
 In a recent work, Richards et al.
-conducted a study on dynamic behavior of JavaScript programs \cite{Richard2}.
-Although thier study contains some aspects of JavaScript function objects creation and usage, such as the number of different call sites and arities in function calls, it does not provide any data about anonymous functions.
+conducted a study on dynamic behavior of JavaScript programs \cite{Richards2}.
+Although their study contains some aspects of JavaScript function objects creation and usage, such as the number of different call sites and arities in function calls, it does not provide any data about anonymous functions.
+
+We previously mentioned four JavaScript naming approaches: Zaytsev advocates expanded use of names in function expressions\cite{Zaytsev}, support for \verb|displayName| in debuggers has been requested\cite{DisplayName}, the Firebug Regular expressions, and the Google Chrome debugger's function name 'inference'\cite{ChromeInfer}.
+The last one appears to be a parser based approach with goals similar to the ad-hoc Firebug regular expressions: look for identifiers preceding anonymous function bodies.
 
 H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs.
-Their approach employs rules extracted from a big corpus of Java projects to recognize buggy names.
-To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.
+Their approach employs rules extracted from a large corpus of Java projects to recognize buggy names.
+To fix a name, a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement.
 This approach assumes that the function is already named and constructs the names based on the function internal structure.
@@
 The result of our work can be improved and impact other aspects of JavaScript programming if a stronger typing system is employed.
-a few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
+A few static typing systems have been proposed for JavaScript \cite{Anderson, Anderson2, Heidegger, Thiemann}.
 These approaches discover the type of values and object structures for a variable by statically analyzing the source code and possible program control flows lead to the variable assignment.
@@
 Our contributions in this paper include an empirical study of the extent of anonymous functions in JavaScript libraries, categorization of those functions to understand the potential for automatic naming, an practical algorithm based on the empirical study, and its evaluation.
-We believe our results can be applied directly in existing JavaScript development tools to give immediate benefit to developers and they provide a basis for future improvements.
-
-%\appendix
-%\section{JavaScript Projects Analyzed for Function Names}
-%\begin{description}
-%\item[Closure] Google Web Library, ...
-%\item[Dojo] JavaScript Toolkit
-%\item[ExtJS] JavaScript Framework
-%\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
-%\item[jQuery]
-%\item[MochiKit]
-%\item[MooTools]
-%\item[Prototype]
-%\item[Scriptaculous]
-%\item[YUI]
-%\end{description}
+We believe our result can be applied directly in existing JavaScript development tools to give immediate benefit to developers and provides a basis for future improvements.
+
+\appendix
+\section{JavaScript Projects Analyzed for Function Names}
+\begin{description}
+\item[Closure] Closure Library, r683, Google Code, \\
+http://code.google.com/p/closure-library/
+\item[Dojo] Dojo JavaScript Toolkit, version 1.5, \\
+http://dojotoolkit.org/
+\item[ExtJS] JavaScript Framework, version 3.3.1 \\
+http://www.sencha.com/products/extjs/
+\item[Firebug] Web Page Debugger, version 1.7 \\
+ http://code.google.com/p/fbug/.
+\item[jQuery] JavaScript Library, version 1.4.4\\
+http://jquery.com/
+\item[MochiKit] version 1.4.2 \\
+http://mochi.github.com/mochikit/
+\item[MooTools] JavaScript Framework, version 1.3 \\
+http://mootools.net/
+\item[Prototype] JavaScript Framework, version 1.7 \\
+http://www.prototypejs.org/
+\item[Scriptaculous] JavaScript Library, version 1.9 \\
+http://script.aculo.us/
+\item[YUI] Library, Yahoo, Inc., version 3.3 \\
+http://developer.yahoo.com/yui/
+\end{description}
 
@@
 October, 1999.
+
+\bibitem{ChromeInfer}
+V8 Google FuncNameInferrer 
+\newblock http://v8.googlecode.com/svn/trunk/src/func-name-inferrer.h
 

### 2011-04-26 papers/fse2011/reviewResponse.txt
edited version of Salman's response

Thank you for reviewing our paper on 'lastChange'. We respond to the
questions raised by the reviewers and then request that the first
reviewer reconsider part of their analysis.

The first reviewer asks:

Q: "The paper presents the work as a general debugging approach. ... how
much of it is made possible through the unique characteristics of
Firefox and Javascript programming? How closely similar could it be
possible to support this idea for a compiled language?"

A: Section 3 of our paper presents a general algorithm and in that
section we give the four prerequisite operations, 1) objectId(), 2)
setPropertyChangeHook(), 3) scopeId(), and 4)
setVariableChangeHook(). A runtime which can support these operations
can run the algorithm; other runtimes cannot. No special feature of
Firefox or of JavaScript is used in this section. Whether a language
is compiled or not does not relate to our technique. We have
implemented this technique for Java as shown in an unreviewed
technical report: http://infoscience.epfl.ch/record/164417. This
technique should apply to C, C++, C#, Pascal, PHP, Ruby, and so on.

The second reviewer asked many important questions about our small user study:

Q: "Who were the developers?"

A: Unfortunately it would not be practical to give the names of our study
particiapants. We assume the reviewer is asking for more information
about the skill of the developers, which we addresss in the remaining
answers.

Q: "How much experience did they have?"

A: These were all skilled developers with several years of experience in
debugging complex programs.

Q: "Are they researchers?"

A: Yes of course. Practically speaking, we cannot hire 'average'
developers to engage in a lengthy study of such a complex subject as
debugging code. A small study with "folks down the hall" is what is
practical.

Q: "Do they know the concept of a data dependency?"

A: Yes. However, our prototype does not require users to know this concept.

Q: "Do they work on programming tools?"

A: No.

Q: "How complex were the test applications?"

A: These were simple applications and they are available on the Web site
we listed in footnote 4,
http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy.

Q: "We're they already familiar with Firebug and its debugging tools?"

A: Of course, most JavaScript developers use Firebug.

Q: "How was the task explained to them?"

A: The instructions were provided on the Web pages listed in footnote 4,
http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy/group1.html.

Q: "We're they given time limits?"

A: As described in the Web pages listed in footnote 4, the introduction
and practice sessions where not timed, then two time trials were
performed. That is how we arrived that the numbers in Figure 12.

Q: "How were they recruited?"

A: We asked for volunteers from among people in our building who we
knew wrote JavaScript.

Q: "What counted as a "step" in Figure 12)."

A: Oops we should have explained that a step in Figure 12 means a button
push, either single stepping the debugger or running a querypoint.

Q: "The sample size of 4 was extremely small, preventing the authors from
really avoiding learning effects (they did counterbalance exposure to
each program)."

A: We did counterbalance amoung users but as you say the small sample
makes this ineffective. We would like to point out that learning
effects stongly bias against our technique. As the reviewers surely
experience, debugging takes a long time to master. New debugging
techniques take a long time to learn. That our test subjects were able
to succeed in less than an hour is itself the most important result of
our small study.

Finally we ask reviewer #1 to reconsider section 4 of our paper and
the related work section discussing reverse watchpoints.

We are very surprised at the claim of reviewer #1 that we don't build
on top of existing debug technology. Section 4 of our paper details
how we built lastChange on top of the Firebug debugger. Perhaps we
should have been clearer: by "breakpoint technology" we mean all the
different ways debuggers pause execution when a special event
occurs. It includes line step, function enter/exit, variable/property
access/change (watchpoint), error/exception, conditional breakpionts,
and changes on graphical changes. (see for example our ref. 1). Our
ability to build upon existing debugger technology is essential to the
practicality of our approach.

We do not believe the claim of the first reviewer that a developer can
"manually perform a lastChange query in relatively few steps." In fact
our user study, as small and limited as it may be, provides direct
evidence against this claim. Moreover our approach can be applied
recursively, to obtain the lastChange to a value found on a
lastChange.

Reviewer #1 points to a combination of watchpoints and the "drop in
frame" feature in Eclipse. Watchpoints trigger on data value changes;
"Drop in frame" allows for shorter re-execution cycles like the local
replay we explained in section 4.5. The fundamental problem with these
techniques is that they only work in the 'forward' direction. If we
land on a watchpoint after a 'drop in frame' operation, then is this
the last change or just one of a hundred changes? This fundamental
problem is why papers cited as our references 4, 5, 6, 8, 11, 12, 13,
and 15 exist: developers want to go backwards. That is why we called
our paper "lastChange". As cited in our related work section, our
approach is superior to even reverse watchpoints, a technology created
to go beyond normal watchpoints. We could of course include a
discussion of normal watchpoints.

Again we thank the reviewers. We believe small changes to the text
based on this feedback would clarify and improve the paper.

### 2011-04-27 papers/fse2011/reviewResponse.txt

@@
 
-Q: "The paper presents the work as a general debugging approach. ... how
-much of it is made possible through the unique characteristics of
-Firefox and Javascript programming? How closely similar could it be
-possible to support this idea for a compiled language?"
+Q: "The paper presents the work as a general debugging approach. ...  
+How closely similar could it be possible to support this idea for a compiled language?"
 
-A: Section 3 of our paper presents a general algorithm and in that
-section we give the four prerequisite operations, 1) objectId(), 2)
-setPropertyChangeHook(), 3) scopeId(), and 4)
-setVariableChangeHook(). A runtime which can support these operations
-can run the algorithm; other runtimes cannot. No special feature of
-Firefox or of JavaScript is used in this section. Whether a language
-is compiled or not does not relate to our technique. We have
+A: Section 3 of our paper presents a general algorithm and we have
 implemented this technique for Java as shown in an unreviewed
-technical report: http://infoscience.epfl.ch/record/164417. This
-technique should apply to C, C++, C#, Pascal, PHP, Ruby, and so on.
+technical report: http://infoscience.epfl.ch/record/164417.
 
-The second reviewer asked many important questions about our small user study:
+The second reviewer asked many important questions about our small user study, we summarized them in 3 main qeustions:
 
-Q: "Who were the developers?"
+Q: Who were the developers?
 
-A: Unfortunately it would not be practical to give the names of our study
-particiapants. We assume the reviewer is asking for more information
-about the skill of the developers, which we addresss in the remaining
-answers.
-
-Q: "How much experience did they have?"
-
-A: These were all skilled developers with several years of experience in
-debugging complex programs.
-
-Q: "Are they researchers?"
-
-A: Yes of course. Practically speaking, we cannot hire 'average'
-developers to engage in a lengthy study of such a complex subject as
-debugging code. A small study with "folks down the hall" is what is
-practical.
-
-Q: "Do they know the concept of a data dependency?"
-
-A: Yes. However, our prototype does not require users to know this concept.
-
-Q: "Do they work on programming tools?"
-
-A: No.
-
-Q: "How complex were the test applications?"
-
-A: These were simple applications and they are available on the Web site
-we listed in footnote 4,
-http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy.
-
-Q: "We're they already familiar with Firebug and its debugging tools?"
-
-A: Of course, most JavaScript developers use Firebug.
-
-Q: "How was the task explained to them?"
-
-A: The instructions were provided on the Web pages listed in footnote 4,
-http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy/group1.html.
-
-Q: "We're they given time limits?"
-
-A: As described in the Web pages listed in footnote 4, the introduction
-and practice sessions where not timed, then two time trials were
-performed. That is how we arrived that the numbers in Figure 12.
-
-Q: "How were they recruited?"
-
-A: We asked for volunteers from among people in our building who we
+A: The developers were all skilled developers with several years of experience in
+debugging complex programs and familiar with Firebug. They knew the concept of 
+data dependency, however our prototype does not require users to know this concept. 
+We recruited them by asking for volunteers from among people in our building who we 
 knew wrote JavaScript.
 
-Q: "What counted as a "step" in Figure 12)."
+Q: How the user study is conducted?
 
-A: Oops we should have explained that a step in Figure 12 means a button
-push, either single stepping the debugger or running a querypoint.
+A: The instructions of user study and programs code were provided on the Web site we listed in footnote 4,
+http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy .
 
-Q: "The sample size of 4 was extremely small, preventing the authors from
-really avoiding learning effects (they did counterbalance exposure to
-each program)."
+Q: What counted as a "step" in Figure 12?
 
-A: We did counterbalance amoung users but as you say the small sample
-makes this ineffective. We would like to point out that learning
-effects stongly bias against our technique. As the reviewers surely
-experience, debugging takes a long time to master. New debugging
-techniques take a long time to learn. That our test subjects were able
-to succeed in less than an hour is itself the most important result of
-our small study.
-
-Finally we ask reviewer #1 to reconsider section 4 of our paper and
-the related work section discussing reverse watchpoints.
+A: We should have explained that a step in Figure 12 means a button
+push, either single stepping the debugger or running a lastChange query.
 
@@
 occurs. It includes line step, function enter/exit, variable/property
-access/change (watchpoint), error/exception, conditional breakpionts,
-and changes on graphical changes. (see for example our ref. 1). Our
-ability to build upon existing debugger technology is essential to the
+access/change (watchpoint), error/exception, conditional breakpionts, etc.
+Our ability to build upon existing debugger technology is essential to the 
 practicality of our approach.
-
-We do not believe the claim of the first reviewer that a developer can
-"manually perform a lastChange query in relatively few steps." In fact
-our user study, as small and limited as it may be, provides direct
-evidence against this claim. Moreover our approach can be applied
-recursively, to obtain the lastChange to a value found on a
-lastChange.
 
@@
 and 15 exist: developers want to go backwards. That is why we called
-our paper "lastChange". As cited in our related work section, our
+our paper "lastChange". As cited in section 8, our
 approach is superior to even reverse watchpoints, a technology created
@@
 based on this feedback would clarify and improve the paper.
+
+--------------------------------------------------------------------------------
+Removed
+--------------------------------------------------------------------------------
+We do not believe the claim of the first reviewer that "a developer can 
+manually perform a lastChange query in relatively few steps". In fact
+our user study, as small and limited as it may be, provides direct
+evidence against this claim. Moreover our approach can be applied
+recursively, to obtain the lastChange to a value found on a
+lastChange.

### 2011-04-27 papers/fse2011/reviewResponse.txt
last edits.

@@
-Thank you for reviewing our paper on 'lastChange'. We respond to the
-questions raised by the reviewers and then request that the first
-reviewer reconsider part of their analysis.
+Thank you for reviewing our paper on 'lastChange'. We respond to the questions raised by the reviewers and then request that the first reviewer reconsider part of their analysis.
 
-The first reviewer asks:
+1) The first reviewer asked:
 
-Q: "The paper presents the work as a general debugging approach. ...  
-How closely similar could it be possible to support this idea for a compiled language?"
+Q: "The paper presents the work as a general debugging approach. ... How closely similar could it be possible to support this idea for a compiled language?"
 
-A: Section 3 of our paper presents a general algorithm and we have
-implemented this technique for Java as shown in an unreviewed
-technical report: http://infoscience.epfl.ch/record/164417.
+A: Section 3 of our paper presents a general algorithm and we have implemented this technique for Java as shown in this technical report: http://infoscience.epfl.ch/record/164417.
 
-The second reviewer asked many important questions about our small user study, we summarized them in 3 main qeustions:
+2) The second reviewer asked a few questions about our user study, we summarized them in 3 main qeustions:
 
@@
 
-A: The developers were all skilled developers with several years of experience in
-debugging complex programs and familiar with Firebug. They knew the concept of 
-data dependency, however our prototype does not require users to know this concept. 
-We recruited them by asking for volunteers from among people in our building who we 
-knew wrote JavaScript.
+A: The developers were all skilled developers with several years of experience in debugging complex programs and familiar with Firebug.
+They knew the concept of data dependency, however our prototype does not require users to know this concept.
+We recruited them by asking for volunteers from among people in our department who we knew wrote JavaScript.
 
@@
 
-A: The instructions of user study and programs code were provided on the Web site we listed in footnote 4,
-http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy .
+A: The instructions of user study and programs code were provided on the Web site we listed in footnote 4, http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy .
 
-Q: What counted as a "step" in Figure 12?
+Q: What counted as a 'step' in Figure 12?
 
-A: We should have explained that a step in Figure 12 means a button
-push, either single stepping the debugger or running a lastChange query.
+A: We should have explained that a step in Figure 12 means a button push, either single stepping the debugger or running a lastChange query.
 
-We are very surprised at the claim of reviewer #1 that we don't build
-on top of existing debug technology. Section 4 of our paper details
-how we built lastChange on top of the Firebug debugger. Perhaps we
-should have been clearer: by "breakpoint technology" we mean all the
-different ways debuggers pause execution when a special event
-occurs. It includes line step, function enter/exit, variable/property
-access/change (watchpoint), error/exception, conditional breakpionts, etc.
-Our ability to build upon existing debugger technology is essential to the 
-practicality of our approach.
+3) We are very surprised at the claim of reviewer #1 that we don't build on top of existing debug technology.
+Section 4 of our paper details how we built lastChange on top of the Firebug debugger.
+Perhaps we should have been clearer: by "breakpoint technology" we mean all the different ways debuggers pause execution when a special event occurs.
+It includes line step, function enter/exit, variable/property access/change (watchpoint), error/exception, conditional breakpionts, etc.
+Our ability to build upon existing debugger technology is essential to the practicality of our approach.
 
-Reviewer #1 points to a combination of watchpoints and the "drop in
-frame" feature in Eclipse. Watchpoints trigger on data value changes;
-"Drop in frame" allows for shorter re-execution cycles like the local
-replay we explained in section 4.5. The fundamental problem with these
-techniques is that they only work in the 'forward' direction. If we
-land on a watchpoint after a 'drop in frame' operation, then is this
-the last change or just one of a hundred changes? This fundamental
-problem is why papers cited as our references 4, 5, 6, 8, 11, 12, 13,
-and 15 exist: developers want to go backwards. That is why we called
-our paper "lastChange". As cited in section 8, our
-approach is superior to even reverse watchpoints, a technology created
-to go beyond normal watchpoints. We could of course include a
-discussion of normal watchpoints.
-
-Again we thank the reviewers. We believe small changes to the text
-based on this feedback would clarify and improve the paper.
+Reviewer #1 points to a combination of watchpoints and the 'drop in frame' feature in Eclipse.
+We do not believe the claim of the first reviewer that "a developer can manually perform a lastChange query in relatively few steps".
+In fact our user study, as small and limited as it may be, provides direct evidence against this claim.
+Watchpoints trigger on data value changes; 'Drop in frame' allows for shorter re-execution cycles like the local replay we explained in section 4.5.
+The fundamental problem with these techniques is that they only work in the 'forward' direction.
+If we land on a watchpoint after a 'drop in frame' operation, then is this the last change or just one of a hundred changes?
+This fundamental problem is why papers cited as our references 4, 5, 6, 8, 11, 12, 13, and 15 exist: developers want to go backwards.
+That is why we called our paper 'lastChange'.
+As cited in section 8, our approach is superior to even reverse watchpoints, a technology created to go beyond normal watchpoints.
 
@@
 --------------------------------------------------------------------------------
-We do not believe the claim of the first reviewer that "a developer can 
-manually perform a lastChange query in relatively few steps". In fact
-our user study, as small and limited as it may be, provides direct
-evidence against this claim. Moreover our approach can be applied
-recursively, to obtain the lastChange to a value found on a
-lastChange.
+Moreover our approach can be applied recursively, to obtain the lastChange to a value found on a lastChange.
+
+Again we thank the reviewers. We believe small changes to the text based on this feedback would clarify and improve the paper.

### 2011-06-07 trunk/papers/fse-tool2011/reviewResponse.txt

--- 2011-04-27 papers/fse2011/reviewResponse.txt
@@
 Q: "The paper presents the work as a general debugging approach. ... How closely similar could it be possible to support this idea for a compiled language?"
-
 A: Section 3 of our paper presents a general algorithm and we have implemented this technique for Java as shown in this technical report: http://infoscience.epfl.ch/record/164417.
 
-2) The second reviewer asked a few questions about our user study, we summarized them in 3 main qeustions:
+2) The second reviewer asked a few questions about our user study, we summarized them in 3 main questions:
 
 Q: Who were the developers?
-
 A: The developers were all skilled developers with several years of experience in debugging complex programs and familiar with Firebug.
@@
 Q: How the user study is conducted?
-
 A: The instructions of user study and programs code were provided on the Web site we listed in footnote 4, http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy .
@@
 Q: What counted as a 'step' in Figure 12?
-
 A: We should have explained that a step in Figure 12 means a button push, either single stepping the debugger or running a lastChange query.

### 2011-06-07 trunk/papers/fse-tool2011/sig-alternate.tex

--- 2011-03-12 trunk/papers/fse2011/sig-alternate.tex
@@
 
-\title{Debugging by {\huge\bf\textit{lastChange}}}
+%\title{Debugging by {\huge\bf\textit{lastChange}}}
+\title{\huge\bf{Querypoint} : Moving Backwards on Wrong Values in the Buggy Execution}
 
@@
 John J. Barton\\
-       \affaddr{IBM Research - Almadan}\\
+       \affaddr{IBM Research - Almaden}\\
        \email{bartonjj@us.ibm.com}
@@
 \begin{abstract}
-%Developers often seek the origins of wrong values they see in their
-%debugger. Their search must be backwards in time: the code causing the
-%wrong value executed before the wrong value appeared. Searching with
-%breakpoint- or log- based debuggers demands persistence and
-%significant experience with the application being debugged. 
-We introduce a new, practical feature for debuggers called \textit{lastChange}, 
-which automatically locates the last point that a variable or an object property 
-has been changed. Starting from a 
-program halted on a breakpoint, the \textit{lastChange} solution
-applies queries to the live program during re-execution, recording the call stack 
-and limited program state each time the property value changes.
-When the program halts again on the breakpoint, the recorded information 
-can be shown to the developer.
-As a proof of this concept, we developed \textit{Querypoint}, a prototype
-which enhances the popular Firebug JavaScript debugger with
- the \textit{lastChange} feature and studied users applying the prototype to 
-some test cases.
- The approach used in implementing 
-\textit{lastChange} combines the flexibility of breakpoint debugging
-with the expressive power of log-based query debugging.  Contrary to
-other replay-based approaches, which require exactly the same
-re-executions (deterministic executions), our new approach only requires \textit{bug 
-reproducibility}, meaning a test case is available which reproduces the bug and a 
-way to halt execution reliably after the reproduction.
 
 \end{abstract}
+Developers often seek the origins of wrong values they see in their
+debugger. Their search must be backwards in time: the code causing the
+wrong value executed before the wrong value appeared. Searching with
+breakpoint- or log- based debuggers demands persistence and significant experience with the application being debugged.
+
+\textit{Querypoint}, is a Firefox plugin which enhances the popular Firebug JavaScript debugger with
+ a new, practical feature called \textit{lastChange}, which automatically locates the last point that a variable 
+or an object property has been changed. Starting from a program halted on a breakpoint, the \textit{lastChange} solution
+applies queries to the live program during re-execution, recording the call stack and limited program state each time 
+the property value changes. When the program halts again on the breakpoint, the recorded information can be shown to the developer.
 
@@
 \category{D.2.6}{Programming Environments}{Integrated environments}
-
-% A category with the (minimum) three required fields
-%\category{H.4}{Information Systems Applications}{Miscellaneous}
-%A category including the fourth, optional field follows...
-%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
@@
 dealing with long log files and analyzing huge amounts of collected data. 
-Neither approach efficiently assists the developer in finding origins to a wrong
+Neither approach effectively assists the developer in finding origins to a wrong
 value.
@@
 
-The rest of the paper is organized as follows. First, we demonstrate
-the \textit{lastChange} usage on a simple example with the comparison
-to breakpoint debugging. Section 3 presents \textit{lastChange}
-algorithm. In section 4, we explain the details of the JavaScript
-prototype implementation. We discuss the effect of non-determinism on
-the \textit{lastChange} results in section 5. The user study results 
-are presented in section 6. %TODO update it according to new Section 6 contains an evaluation of\text{lastChange} functionality.
+\section{Related Work}
+\label{sec:relatedWork}
+%whyline, firecrystal
+
+Tools developed to enhance developers' movement on the buggy execution can be classifed in two groups: replay-based and logging-based.
+
+%The algorithm we presented in this paper obtain information about
+%the execution state logically earlier in the control flow by querying 
+%the executioin state during replay using the technology of 
+%conventional breakpoint debuggers.  
+The \textit{lastChange} approach resembles the operational model of replay-based debugging 
+and the query approach of logging-based
+debugging.  Replay-based approaches capture limited data during
+execution and replay the buggy execution to reach past points. In
+contrast, logging-based approaches collect enough data during
+execution to relieve developer from re-execution, then query the data to 
+inform the developer. Replay-based
+approaches impose much less runtime overhead (about two orders of
+magnitudes) comparing to logging-based approaches. However, developer
+has to re-execute the buggy execution several
+times. \textit{lastChange} collects data on re-execution by queries
+selected by developer interaction with the debugger. Therefore it has 
+the selectivity of the replay-based approaches that improves performance, 
+% but we have 
+and the flexibilty of the queries so it does not require deterministic replay.
+
+Among replay-based debuggers we compare to bdb \cite{Boothe} and
+reverse watchpoint \cite{Maruyama}.  A bidirectional C debugger, bdb
+employs a step counter to locate the requested point from the
+beginning of execution. It relies on deterministic execution replay
+%(i.e., the same sequence of instructions in re-execution) 
+and records the results of non-deterministic system calls and re-injects them into
+the program when it is replayed. It makes use of checkpoints to reduce
+the time needed for re-execution. Reverse watchpoint, similar to bdb, uses
+a counter to correctly locate the last write access of a selected variable in the
+next execution \cite{Maruyama}.
+% Reverse watchpoint is proposed by Maruyama et al., analyses the execution and moves the debugger to the
+% last write access of a selected variable by re-executing the program
+%from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
+%replay and uses a counter to correctly locate a point in the next
+%execution. 
+The main disadvantage of these approaches is that they require 
+identical, instruction by instruction, re-executions. % exactly the same executions. 
+Even one instruction difference between
+two executions leads to wrong results. On the other hand,
+\textit{lastChange} doesn't require any special feature in the
+re-execution and fits into existing debugging practice
+
+Among logging-based approaches are \textit{omniscient} debuggers
+ODB\cite{Lewis} and Unstuck\cite{Hofer}. Both
+approaches keep the log history in memory and hence can only record
+and store the complete history for a short period of time. These
+debuggers record all the events that occur during the buggy execution
+and later let the developer to navigate through the obtained execution
+log. In these approaches there is no execution to resume: moving
+backwards in the log can be similar to moving forwards. A more scalable 
+approach to omniscient debugging has been proposed by Pothier et al. \cite{Pothier}. 
+Their back-in-time debugger, TOD, addresses the space problem by storing 
+execution events in a distributed database. Bhansali et al. \cite{Bhansali} attempted to address the performance overhead 
+and large trace size of logging-based debugging in their time-travelling debugger, Nirvana. 
+Nirvana first collects a full compressed trace of program execution and then 
+simulates re-execution. Their results are quite similar to omniscient 
+debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
+re-simulation.
+
+Logging-based debuggers suffer from different issues. First, the recording
+step is time expensive and it should be repeated in case of changes in
+program. Second, the execution log cannot fully replace the live
+execution. There are other aspects of execution (e.g., program user
+interface, file system, database tables, etc.) which are also
+important in debugging and are not available to the developer in 
+logging-based debuggers. Third, querying collected data (e.g., to restore
+the program state at a certain point) may not be efficient enough for
+debugging realistic programs. Comparing to logging-based debuggers our approach 
+has little upfront cost and more flexibility. The developer can start debugging just 
+after reproducing the bug without a capturing step.  Changing inputs or
+environment settings and re-executing to investigate the bug works as
+in conventional breakpoint debuggers.
+
+A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
+machine level support for keeping the history of events. It replaces every
+object reference with an alias object which keeps the history of
+changes to the object reference. 
+%In this way, when an object is
+%collected by garbage collector, its track of changes (if it is not
+%referenced by other aliases) will be also collected. 
+Although this approach incurs less runtime overhead (7 times) in
+comparison to omniscient debuggers, it adds memory
+overhead.
+
+Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
+Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
+First, it is limited to \texttt{undefined} and \texttt{null} values. Second, it does not return the last change
+of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
+
+%Two new directions in logging debuggers explore more detailed use of
+%the log and more effective user interface to the collected data. %logging approaches. 
+%WhyLine\cite{Ko} provides visual interface to collected runtime information and lets
+%developer moves on execution log using queries expressed in terms of
+%the programming objects.
+
+WhyLine\cite{Ko} stores the program user interface in
+addition to the program trace and provides answers to why and why not
+questions to the user. 
+%Jive\cite{Czyz} depicts the history of
+%execution by a sequence diagram and lets the user to query on the events
+%database. 
+WhyLine suffers from the requirement of gathering tracing information before its unique capabilities can be used.
+We imagine that the runtime queries we use in \textit{lastChange} may be used to gather data incrementally for this kind of debugging approach.
+
+%Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
+Moreover, the Lienhard et al.
+debugger significantly changes the virtual machine, while our approach is a generalization to conditional breakpoints and available debugger infrastructure can be adapted to support it.
+
+%\textit{lastChange} functionality does rely on a conventional breakpoint to begin queries, a requirement not shared by full logging solutions.
+Here we leverage past experience of developers, but there are also new tools [] to help with this problem in the case of graphical and event based systems.
 
@@
 
-\begin{figure}[htp]
-\centering
-
-\includegraphics [width=.48\textwidth]{5-example-points.pdf} 
-\caption{The examined points before locating the defect.
-The arrow represents the logical forward progress of the program.
-Three actual executions are superimposed on this arrow.
-All three stop at the reproduction point indicated by circle 1.
-After the first execution, the developer asks for lastChange as described in section \ref{sec:introExample}, yielding information  indicated by circle 2.
-After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
-\label{fig:example-points}
-\end{figure}
+\begin{figure*}[htp]
+
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel on the right shows the program state at
+  the paused
+  point.
+Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
+  ]{1-bp22.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
+  ]{3-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
+  enter the expression in the watch box and after re-execution the result is available.
+  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
+    ]{4-lastChange2.jpg}}
+
+\caption{The stages of locating the defect using \textit{lastChange} feature.}
+\label{fig:lastChange}
+\end{figure*}
 
@@
 
-\begin{figure*}[htp]
-
-\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
-  panel is selected; it gives access to
-  all loaded source files and allows breakpoints to be set on lines. In this
-  figure, the execution is paused at line 22 by a regular
-  breakpoint. The Watch panel on the right shows the program state at
-  the paused
-  point.
-Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
-  ]{1-bp22.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myObject.myProperty}. The left panel, QP, shows the source
-  code at the point of \textit{lastChange}; The right panel,
-  TraceData, shows the collected data at the
-  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
-  ]{3-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
-  enter the expression in the watch box and after re-execution the result is available.
-  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
-  the list shows the corresponding code and
-  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
-    ]{4-lastChange2.jpg}}
-
-\caption{The stages of locating the defect using \textit{lastChange} feature.}
-\label{fig:lastChange}
-\end{figure*}
-
 Notice that in our example, \textit{lastChange} combines some aspects
@@
 
-\section{lastChange Algorithm}
-
-The \textit{lastChange} algorithm is based on program re-execution of
-a program halted on a breakpoint. The algorithm starts when developer
-examines the program state at a breakpoint hit and asks for the
-\textit{lastChange} of a value. The breakpoint hit becomes the
-\textit{reproduction point}. Debugger sets hooks (a callback
-function dependent upon the underlying runtime) on all instructions
-that might be the result of \textit{lastChange} query. Then the
-debugger re-executes the program and every time a hook hits it
-checks for a \textit{change event}. In the case of a change, it stores
-part of the program state values.  Once the execution reaches the
-reproduction point, it analyzes the collected data and shows the
-result.  The program state at the execution point of the last change
-event is the \textit{lastChange}.
-
-As we described in the preceding section, a \textit{lastChange} query can
-be performed on the result of another \textit{lastChange} query. If we
-name the reproduction point \textit{R}, we can write the first
-\textit{lastChange} in the introductory example in this form:
-\textit{lastChange(R, myObject.myProperty)}. It means that this query
-is defined at \textit{R}. If we name the result of this query
-\textit{L}, we can write the second \textit{lastChange} in this form:
-\textit{lastChange(L, myCondition.value)}. In this way, a sequence of
-\textit{lastChange} queries with any length can be defined.
-
-\textit{lastChange} can be called on object property, on a variable value, 
-or on the results of a \textit{lastChange}. Moroever, common data structures such as
-arrays and hashmaps are also supported as special cases of \textit{lastChange} on object property.
-We explain each case in the following subsections.
-
-\subsection{{\large\bf\textit{lastChange}} on Object Property}
-To simplify the algorithm explanation and defer technical details, we
-define two basic operations and later we explain the details of these
-two operations. The first operation is \texttt{objectId()}: given a
-JavaScript object it returns an integer as its identifier. This
-identifier is unique to the object during one execution.  By using an
-object id instead of an object reference we allow the garbage
-collector to reclaim the space for dead objects just as it would in the
-absence of the debugger. The second
-operation is \texttt{setPropertyChangeHook()}: given a function and a
-string, the function is called whenever a property changes and its
-name matches the string. For example, if the string is 
-\texttt{foo}, changes to \texttt{bar.foo} or \texttt{baz.foo} would
-call the function.  The callback function receives a reference to the
-owner of \texttt{foo}.
-
-To see how these functions work, suppose the developer asks for the
-last change of \texttt{bar.foo} at the reproduction point in a
-program. The debugger calls \texttt{setPropertyChangeHook()} with
-\texttt{foo} as the property name and re-executes the
-program. Whenever \texttt{foo} changes and the callback function is to
-be called, debugger first calls \texttt{objectId()} on the
-\texttt{foo} owner object. Then it stores this owner id, the stack
-frame locations, and other state values in scope at the call point. 
-Then the callback returns to continue the execution. Thus the query is not 
-a breakpoint in the sense of pausing for user interaction, but breakpoint 
-technology can be used to implement the query.
-Whenever the execution reaches the reproduction point the debugger
-looks at the history of \texttt{foo} changes and finds the last
-\texttt{foo} change with the same object id as \texttt{bar} id at the
-reproduction point. Figure~\ref{fig:foo-changes1} shows the list of
-property \texttt{foo} change events in a hypothetical
-execution. \texttt{bar} id at the reproduction point is 1010, so the
-last change of \texttt{bar.foo} is the fourth column.
-
-\begin{figure}[htp]
-\centering 
-\includegraphics [width=.48\textwidth] {6-foo-changes1.pdf} %[width=.48\textwidth][scale=0.75]
-\caption{A hypothetical list of  change events for a property \texttt{foo}. 
-Each change event adds a column with the id of the object changed, the call stack,
-and some program state such as local variable values. 
-At the reproduction point  we determine which id  corresponds to 
-object \texttt{bar} and read out column 4,  the last
-  change of \texttt{bar.foo}. Column 3 is also a change of
-  the object we want to study, id 1010, but it is not the last change;
-  Column 5 is also a change of a property \texttt{foo} but it is not for
-  the object we are interested in.}
-\label{fig:foo-changes1}
-\end{figure}
-
-\subsection{{\large\bf\textit{lastChange}} on Variable} 
-In JavaScript, every frame has a scope chain and every available
-variable in the frame comes from one of the scopes in the frame's
-scope chain. Once the developer asks for the last change of a variable with name 
-\texttt{foo} at the reproduction point, the debugger first determines the
-variable's scope as follows: it iterates over the scopes in the scope
-chain and the first scope which has a variable with the same name is
-the variable's scope. There are five different scope types: global, local,
-closure, \texttt{with} and \texttt{catch}. We explain these
-cases in two groups.
-
-\subsubsection{global and \texttt{with} scopes}
-Global scope is the most outer scope in the scope chain and it is
-also referred to as the global object (the \texttt{window}
-object in Web pages). This scope is a regular JavaScript object and therefore every
-global variable is a property of global object. Similarly,
- \texttt{with} scopes are also regular JavaScript objects. A \texttt{with}
-scope is created by a \texttt{with()} block with an object as the
-parameter. Every property of this parameter object is available inside the
-block as a variable. \textit{lastChange} treats the case where variable's scope
-is global or \texttt{with}, like it does on an object
-property.
-
-\subsubsection{local, closure and \texttt{catch} scopes}
-Local scope refers to the most nested scope in the scope
-chain which contains the local variables. Closure scope refers to the 
-scope which is created for a nested function and contains variables 
-defined in the outer block. Catch scope is the scope created in the catch
-block of try-catch statements and contains the exception
-variable. These scopes are not necessarily regular JavaScript
-objects.  
-Therefore, to track changes to a variable in these scopes we
-employ a different approach.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\includegraphics [width=.48\textwidth] {9-scopes.pdf} %[width=.48\textwidth][scale=0.75]
-
-%\lstset{basicstyle=\scriptsize}
-%\begin{lstlisting}[language=myLang, framerule=0pt]
-%  function f(){
-%    var x = 0;	
-%    x++;
-%    ...
-%    if (!stop) f();
-%  }
-
-%Sample Trace:
-
-%   f()
-%A  |  x changes, scope 1 
-%   |  f()
-%   |  |  x changes, scope 2
-%   |  |  f()
-%B  |  |  |  x changes, scope 3 
-%C  |  ... , scope 1
-%\end{lstlisting}
-%\end{verbatim}
-\caption{A recursive call trace illustrating the scope
-  id.
-The lines in the bottom half of the diagram simulate a trace of the change events for the variable \texttt{x} as the function \texttt{f()} calls itself.
-Each call creates a scope; eventually when the variable \texttt{stop} is changed by an external process we return from the recursion.
-The lines marked A, B, and C are discussed in the text.}
-\label{fig:recursive}
-\end{figure}
-
-Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
-a code block, enclosed the executing code. In
-JavaScript, a code block can be identified by the file url and  
-the block's first instruction program counter. Given this information, the debugger is
-able to recognize the code block in loaded scripts or once it is loaded.
-Similar to \textit{lastChange} on object property, we define two basic operations: 
-\texttt{scopeId()} -- which returns an integer given a scope -- and \texttt{setVariableChangeHook()} -- which calls its first parameter, a callback function, when a 
-variable in its second parameter, a code block, matches the name given in the third parameter.
-
-Figure~\ref{fig:recursive} illustrates how the \texttt{scopeId()} operation separates instances 
-of a variable in different scopes having the same name.
-If we ask for the last change on \texttt{x} at point labeled \texttt{C} in scope with id 1, we want the change at line \texttt{A} in scope 1, not 
-the change at the line marked \texttt{B}, where a variable named \texttt{x} in scope 3 is changed.
-
-If the developer asks for the last change of variable \texttt{foo} at the 
-reproduction point in a program, debugger calls 
-\texttt{setVari- ableChangeHook()} with the variable's defining
-block and name as parameters and re-executes the
-program. Whenever \texttt{foo} changes and the callback function is to
-be called, debugger first calls \texttt{scopeId()} on the
-variable's scope. Then it stores this scope id, the stack
-frame locations, and other state values in scope at the call point.
-Whenever the execution reaches the reproduction point the debugger
-looks at the history of \texttt{foo} changes and finds the last
-\texttt{foo} change with the same scope id as the variable's scope id
-at the reproduction point (Figure~\ref{fig:foo-changes2}).
-
-\begin{figure}[htp]
-\centering 
-\includegraphics[width=.40\textwidth]{7-foo-changes2.pdf}
-\caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
-change event the scope id returns by \texttt{scopeId()} is recorded along with call stack and program state information. 
-   The last column having the scope id \texttt{foo} at the reproduction point indicates 
-  the last change.}
-\label{fig:foo-changes2}
-\end{figure}
-
-\subsection{{\large\bf\textit{lastChange}} on {\large\bf\textit{lastChange}}}
-The \textit{lastChange} algorithm records changes by id (either object or scope id), then reads out the last change when we
-arrive at the reproduction point and discover the id of the requested value.
-When we perform \textit{lastChange} based on a previous \textit{lastChange}, the query algorithm 
-must retain additional information. Consider the following example:
-
-\lstdefinelanguage{myLang2}
-{morekeywords={point, lastChange}}
-
-\lstset{basicstyle=\small}
-\begin{lstlisting}[frame=single, language=myLang2] %, framerule=0pt]
-
- point A : the reproduction point 
- point B : lastChange(A, bar.x) 
- point C : lastChange(B, baz.y) 
-\end{lstlisting}
-
-%\begin{center}
-%\textit{
-% }
-% \end{center}
-
-where point A is a breakpoint, point B is the last change of the object property \texttt{bar.x} at point A, and
-point C is the last change of the object property \texttt{baz.y} at point B. 
-The object referenced by \texttt{baz} changes upon re-execution. Therefore when the developer
-asks for the last change of \texttt{baz.y}, we need to track objects named \texttt{baz}
-at changes of \texttt{bar.x} and changes to objects named \texttt{y}. Then, at the reproduction point,
-we need to work out which \texttt{baz} the developer wanted, then select the last change of that \texttt{baz.y}.
-Figure~\ref{fig:lastchange-lastchange} illustrates the extra row of data (tracking of \texttt{baz} objects 
-at \texttt{x} change events) 
-and how the id values allow the last change of \texttt{baz.y} to be worked out.
-
-In the general case we perform dependency analysis as outlined in 
-Figure~\ref{fig:dependency-analysis} to
-create the list of additional data (object id or scope id) to be collected at a change
-event. The process can be repeated to cascade \textit{lastChange} arbitrarily deep.
-
-\begin{figure}[htp]
-\centering 
-\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.pdf}
-\caption{The list of change events stored for locating point B, the
-  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
-  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
-\label{fig:lastchange-lastchange}
-\end{figure}
-
-\begin{figure}[htp]
-%\centering 
-%\begin{algorithm}
-\line(1,0){240}
-\begin{algorithmic}%[frame=single]
-\FOR{$q$ in $lastChange$ queries} 
- \FOR {$p$ is defined at the $q$ result}
-   \IF {$p$ is a $lastChange$ on object property} 
-     \STATE the property {\bf owner id} must be stored at $q$ change events. 
-   \ELSIF {$p$ is a $lastChange$ on variable} 
-     \STATE the variable {\bf scope id} must be stored at $q$ change events.
-	 \ENDIF 
- \ENDFOR 
-\ENDFOR
-
-\end{algorithmic}
-\line(1,0){240}
-%\end{algorithm}
-\caption{\textit{lastChange} queries dependency analysis.}
-\label{fig:dependency-analysis}
-\end{figure}
-%---------------------------------------------------------------------------------------------------
-\section{JavaScript implementation}
-To verify the \textit{lastChange} algorithm we
-implemented\footnote[1]{http://code.google.com/p/querypoint-debugging} it in an extension to the Firebug
-JavaScript debugger\footnote[2]{http://getfirebug.com}. %\cite{Firebug}. %\cite{firebug-version-1.6}. 
-Firebug itself is an extension of the Firefox browser. %\cite{Firefox}. %\cite{firefox-version-3.6}
-The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and 
-\textit{Querypoint} is developed over this interface. Our prototype implements the four primitive operations in JavaScript 
-using techniques which are cumbersome and comparatively slow to execute. However the JavaScript prototype is
-easy to explore, change, and share with others for feedback. A professionally useful debugger 
-would implement these primitive operations within the JavaScript engine.
-
-\subsection{{\normalsize\bf\texttt{objectId()}} Operation}
-\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
-%\footnote[3]{The property name we used in the prototype is longer and more specific to reduce the chance of name conflicts.} .
-It returns the value if this property is already defined,
-otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. 
-%\footnote[3]{This use of a regular object property  might change
-%the program behaviour. For example it will appear as an extra property in 
-%\texttt{for(property in object)} loops. 
-%The next version of Firefox (https://developer.mozilla.org/en/JavaScript/Reference\\/Global\_Objects/Object/defineProperty) provides \texttt{defineProperty}, 
-%allowing a property to be added which is invisible to enumeration.} Note that \texttt{\_objectId} is
-%not set for all objects but only those objects that need an id.
-
-\subsection{{\normalsize\bf\texttt{setPropertyChangeHook()}} Operation}
-The Firefox JavaScript engine supports watching property changes in an
-object. Every object has a function \texttt{watch(propName, callback)}
-which receives two parameters, a property name and a function.  Whenever
-the property with the given name changes, the \texttt{callback} function is
-called. The hook set by this function remains enabled even if the
-property is deleted and defined again.
-
-For our purposes, the \texttt{watch()} function only covers the case
-of global object properties. At the beginning of execution, no object
-excepting the global object and its predefined properties is available.  For 
-our \textit{lastChange} prototype, we created a version of
-\texttt{setPropertyChangeHook()}.  The basic strategy is to get a reference to the object just
-after its creation, then use \texttt{watch()} function to monitor
-property changes in the object. Setting a flag\footnote[3]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
-JavaScript engine, we can get the file URL and the line number for each object
-creation (e.g., myFile.js, line 24). We set a breakpoint on this line
-and parse the source code to determine which object was created.
-
-The only data we have is the object creation location including the
-file url and the line number and the goal is to get a reference to
-this object. Although in most regular cases we have only one
-statement and one object creation, there are cases where more
-objects are created in the line. There is no simple way to
-recognize the interesting object among these new objects. So instead
-of one object, we monitor all new objects created in the line.
-
-An object might be created by one of these statements: object
-literal(\texttt{\{...\}}), \textit{new} operator (\texttt{new 
-constructor()}) or function definition statement (\texttt{function()}). 
-By parsing the source code we can recognize the statements that
-create an object. The next step is getting a reference to the new object.
-
-The new object can be assigned to an object property or a variable by
-an assignment (\texttt{=}). In these cases we keep the assignee statement 
-at the left side. The idea is that we create a list of assignee statements 
-that the new objects are assigned to. We set a hook on the creation
-line. Once the hook hits, we evaluate the assignee statements. Then 
-we do stepping(step-over) and after each step we evaluate the
-statements. Every statement which has a new value, we consider the new
-value (if it is an object) as a new object. For example in Figure
-~\ref{fig:objectCreation}(a), if the creation line number is 20, we
-have only one statement which creates a new object and it is assigned
-to \texttt{x.y}.
-
-The new object can also be set as the property of a parent object 
-(or array) inside an object (or array) literal. This case is also treated 
-similar to previous case. The only difference is that the full path of property 
-from the root parent in the local scope must be considered as the assignee statement. For
-example in Figure~\ref{fig:objectCreation}(b), if the creation line
-is 20, we keep \texttt{parent.child}. In this case stepping
-must be continued until the end of the object literal (line 22) for getting a reference
-to the created new object.
-
-In cases where the new object is passed as an 
-argument to a function (Figure~\ref{fig:objectCreation}(c)), we use step-in instead of step-over. 
-To get a reference to the new object
-it is enough to evaluate the corresponding argument inside the function. The other cases
-where the program does not keep a reference to the created object (e.g., when a function object is
-just called after its creation), are not in our interest.
-
-%(or \texttt{this} if the object is being constructed by \texttt{new} statement)
-
-Although this approach is successful in many ordinary cases, we can imagine 
-cases where a more comprehensive analysis needed for the correct behaviour. 
-Consider the case where the new object is assigned to an expression like \texttt{a[++i]}. 
-% (where i is a variable). 
-%This expression is kept in the list                      %(Figure~\ref{fig:objectCreation}(d))
-%of assignee statements to be evaluated later for getting a reference to the new object. 
-Obviously, evaluating this statement doesn't return
-a reference to the new object. Our prototype implementation does not handle these kinds of unusual cases yet.
-
-Throughout this section we implicitly assumed that the object will be created at 
-the same location in the next execution. If the assumption is
-not true, once the execution reaches the reproduction point, it
-reveals that the object has been created in a different location. This time,
-prototype re-executes the program considering both locations as possible 
-object creation locations.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang]% framerule=0pt]
-
-(a) Case 1:
- 20  x.y = new MyClass();
-
-(b) Case 2:
- 19  parent = {
- 20    child : {
- 21      x : 5
- 22  }}
-
-(c) Case 3:
- 20  myFunction({myProperty:5});
-
-\end{lstlisting}
-
-%(d) Case 4:
-% 20 a[++i] = new myConstructor();
-
-%\end{verbatim}
-\caption{Examples of different cases in getting references to created JavaScript objects.}
-\label{fig:objectCreation}
-\end{figure}
-
-\subsection{{\normalsize\bf\texttt{scopeId()}} Operation}
-The prototype sets a breakpoint at the beginning of all code blocks needing
-a scope id. The scope id is kept as a variable with name 
-\texttt{\_scopeId} in the scope. Whenever the hook is hit,  meaning a new scope
-is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
-function \texttt{eval()}. For example, executing \texttt{eval("var \_scopeId = 10")} creates a
-variable with name \texttt{\_scopeId} and value \texttt{10} in the
-scope of the \texttt{eval()} call, which is our interesting scope. \texttt{scopeId()}
-operation returns the value of \texttt{\_scopeId} in the scope.
-
-\subsection{{\normalsize\bf\texttt{setVariableChangeHook()}} Operation}
-Variables defined in local, closure, and catch scopes are only changed in
-their scope; that includes the defining scope and scopes nested whithin them.
-For example in Figure~\ref{fig:js-closure}, variable \texttt{foo} in line 11 can only be
-changed in lines 10 to 23. Therefore, after locating the function in
-which the variable is defined, it is enough to parse the code inside
-the function block and set a hook on all lines where the variable is
-assigned a new value. 
-We also set a hook at the first line of the function which is
-corresponding to the line where the variable is defined. In Figure~\ref{fig:js-closure}, 
-if the execution is paused at line 17 and the
-last change of \texttt{foo} is queried, two hooks on lines 16 and 17
-will be set, but if the execution is paused at line 20 , four hooks on
-lines 11, 12, 14, 20 will be set. These two cases are different: \texttt{foo} in 
-\texttt{childOne} is a local variable
-but in \texttt{childTwo} it is a closure variable.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang]%, framerule=0pt]
-
-10  function main(){
-11    var foo;
-12    foo = ...;
-13    function parent(){
-14      foo = ...;
-15      function childOne(){
-16        var foo;
-17        foo = ...;
-18      }  
-19      function childTwo(){
-20        foo = ...;			      
-21      }
-22    }  
-23  }    
-\end{lstlisting}
-%\end{verbatim}
-\caption{Sample JavaScript code demonstrating local and closure variables.}
-\label{fig:js-closure}
-\end{figure}
-
 \subsection{Re-Execution, Reproduction Point and Data Collection}
-\textit{Querypoint} needs a test case to reproduce the
-execution and conditions to correctly recognize the reproduction point. 
-Although both elements can be directly provided by developer, \textit{Querypoint}
-is also able to automatically create them from the first execution.
-
-To replay execution, \textit{Querypoint} keeps track of breakpoint hits and single steps. For example, 
-if the developer queries \textit{lastChange} at the third hit of breakpoint \textit{b}, in
-re-execution, the third hit is recognized as the reproduction point.
-
-The \textit{Querypoint} prototype supports two mechanism
-for automatic re-execution: callstack-reproduction and record-replay. In callstack reproduction the function from
-the earliest frame of the call stack is called with the same parameters. The idea
-behind this mechanism is that many bugs in web pages can be reproduced by re-firing
-an event like clicking on a button. The record-replay execution uses two phases. In the record phase, it 
-stores the initial page url and the events and parameters corresponding to user actions. In the replay phase, it opens
-the same url and simulates events as if they were user actions. The callstack reproduction mechanism provides
-shorter re-execution cycles while the record-replay is more accurate about the
-initial state.
-
-In addition to the data collected at every change event for identifying the \textit{lastChange}
-result, \textit{Querypoint} partially stores values in program state.
-There is a trade-off between the amount of data collected at every change event and the number of re-executions.
-If developer asks for
-some values which have not been stored, \textit{Querypoint} re-executes and collects the requested data.
-
-% Discuss what happens when assumptions changes, like object creation location.
+
+\section{Limitations and Future Work}
 
 \section{Reproducible Non-Deterministic Execution}
-We claim that the only prerequisite for \textit{lastChange}  is bug-reproducibility. 
-A bug is \textit{reproducible} for a developer when the developer can
-start from a given initial state, operate on the program with a
-list of actions, and reproduce the symptoms of the bug. The details of
-the execution can change each time we re-execute the buggy program,
-but the buggy result is the same.  All modern debuggers in wide use that we know 
-about rely on reproducible but non-deterministic execution for simple practical reasons: 
-developers must reproduce a bug to study it and modern execution environments 
-are not deterministic.  
-% In this section we discuss non-determinism and \textit{lastChange}. However we want 
-%to emphasize that when developers have to think about non-determistic execution 
-%it usually means that bugs are not reproducible. 
-%The reproducibility of the bug
-%means that the defect is very unlikely to depend on the order of
-%events during the execution. Conversely, if the defect depends on the order of execution, 
-%it will likely fail to reproduce on some executions. 
-By relying on reproducibility but 
-not requiring deterministic execution, \textit{lastChange} works on the same range of cases.
-
-\subsection{{\large\bf\textit{lastChange}} Result Consistency}
-\label{sec:resultConsistency}
-
-Each time we re-execute a non-deterministic program, 
-the details of execution instruction order may change. 
-For example, if we record the source code lines every time
-a conventional watchpoint hits, the record may differ each time we
-re-execute. But \textit{lastChange} does not compare values across 
-executions. Rather it analyzes all of the
-change events in a single execution. 
-Neither the data gathering nor the analysis require deterministic execution.
-
-Since we don't need to compare values across executions to implement \textit{lastChange}, we can get more information if we do compare:
- different points of last change on different executions will signal that the execution is not deterministic. Note the converse is not true, many non-deterministic 
-programs will give identical results for \textit{lastChange}.
-Consider the example in Figure~\ref{fig:nondeterministic-values}. 
-Assume that at the first execution, the developer sees that the \texttt{a} value is \texttt{true} and asks
-for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-execution, \texttt{a} is \texttt{false},
-and \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
-result shows line 10, which is a correct answer for this execution but not for the previous one.
-When user asks for the \textit{lastChange} on variable \texttt{a}, debugger stores \texttt{a} value and compares
-it to the \texttt{a} value in the next executions. So if this value is different, debugger informs the developer
-that the \textit{lastChange} query is made on a different value.
-% In cases that the value is not a primitive but an object,
-%the primitive properties of the object examined by the developer are stored and compared.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang]%, framerule=0pt]
-
-10 a = b = false;
-20 if (random()) {a = true;} else {b = true;}
-30 if (a || b) {bug(); /* breakpoint */}
-\end{lstlisting}
-%\end{verbatim}
-\caption{\textit{lastChange} on non-deterministic values.}
-\label{fig:nondeterministic-values}
-\end{figure}
 
 \subsection{Combination of {\large\bf\textit{lastChange}} and Breakpoint Debugging}
-\label{sec:pausing}
-Using \textit{lastChange} a developer can work backwards on the flow of data, but sometimes bugs are more obvious when
-we watch control flow forwards. Consider for example,
-
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang] % framerule=0pt]
-
-44 vector.r = Math.floor(Math.random()*5)*6;
-45 if (vector.r !== 0 && vector.r < 30);
-46   return vector;
-\end{lstlisting}
-%\end{verbatim}
-where \textit{lastChange} shows us that \texttt{vector.r} is zero at line 44. In our user studies, developers
-wanted to single step forward from line 44. If they could do this, they may be surprised to see line 46 execute 
-even if \texttt{vector.r} is zero, directing their attention to line 45 where they can discover the errant semicolon.
-However, a \textit{lastChange} is just a query result, not a breakpoint. Under what conditions can we 
-cause the debugger to stop at the \textit{lastChange} point?
-
-In the case that the execution is deterministic, the \textit{last-\ Change}
-event index can be used as an index for a conditional breakpoint \cite{Boothe, Maruyama}. 
-Moreover, this works in a non-deterministic execution if non-determinism
-has no effect on the event index.  The debugger can easily set this conditional breakpoint
-and reexecute the program. If the stream of change events differs in this re-execution the
-developer can be warned that the conditional breakpoint may not be the \textit{lastChange} point.
-However, if the stream of events is the same, we do not know that the 
-conditional breakpoint matches the last 
-change, this fact can only be verified at the reproduction point. These theoretical concerns are not
-likely to cause significant practical problems: if the value at the conditional breakpoint is not suspicious, 
-then the developer will know to simply return to \textit{lastChange} or move on to another tactic to find the bug.
-
-% Cut to reduce size
-%There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
-%to formulate a conditional breakpoint.
-%Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
-%array. The array contains numbers except one item which is
-%\texttt{undefined} and it causes a bug in line 30. There is a call to
-%\texttt{randomPermutation} function in line 11 which randomly
-%permutes the array item. So at every execution the
-%\texttt{undefined} item will be in a new place. Calling
-%\textit{lastChange} on \texttt{x} at the place the bug happens, gives a
-%point which shows line 14. Although this point exists at every
-%re-execution but it can not be identified by an event index. A conditional breakpoint on 
-%the value of the item would succeed and the developer can reason from the 
-%textit{lastChange} results to create the condition.
-
-%\begin{figure}[htp]
-%\lstset{basicstyle=\scriptsize}
-%\begin{lstlisting}[language=myLang, framerule=0pt]
-%10 function randomProcess(array){
-%11   randomPermutation(array);
-%12   var x, y;
-%13   for (var i=0 ; i<array.length ; i++){
-%14      x = array[i]
-%...
-%30      y = x+1;
-%31   }
-%32 }
-%\end{lstlisting}
-%\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
-%\label{fig:counter-example}
-%\end{figure}
-
-\section{User Study}
-We supplied four experienced Javascript developers with our prototype in an 
-extended Firebug debugger\footnote[4]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
-applied both conventional breakpoint and \textit{lastChange} on two small programs we 
-provided (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
-The first program, Shapes, calculates the area and perimeter values for a list of shapes.
-The bug happens when one of the calculated numbers is zero.
-The second program, Moving Circle, randomly scales and moves a circle in the page.
-The bug happens once the circle becomes invisible after an exception
-occurs.
-This case represent a reproducible non-deterministic execution.
-The developers were asked to locate the defects that caused these bugs.
-All four developers successfully applied \textit{lastChange} to the test programs
-and understood how it could help debugging.
-
-To find the defect location with breakpoints, all four users took more steps and more time (Figure~\ref{fig:userstudy}).  
-Two users scrolled through the source, 
-another searched the text, a third set a lot of breakpoints to understand the control flow. 
-Based on our own experience we expect these strategies represent the kinds of approaches 
-developers have available. These operations are time consuming and tedious. In contrast, all four users 
-found the defect location with just two \textit{lastChange} operations.
-% Based on our measurements,
-%this makes \textit{lastChange} about three times faster than breakpoints for the navigation from 
-%the reproduction point to the defect
-We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
-issues have been hidden by the design of our tests. Nevertheless our results show that, when a defect 
-relates to incorrect values and a developer recognizes this, then the operational 
-mechanics of lastChange lead to the defect much more quickly than breakpoints.
-
-Our observation and discussions with users also brought out several important issues and improvements
-for our user interface. Perhaps the most important and challenging improvement would be better integration 
-with breakpoint debugging. Our implementation put the results of \textit{lastChange} in a similar but different
-view from breakpoint debugging. This focuses attention on value changes, but it makes studying control 
-flow more difficult: we don't support single stepping from a \textit{lastChange} result in our user interface. In our next iteration we 
-plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
-
-\begin{figure}[htp]
-\centering 
-\includegraphics[width=.48\textwidth]{10-userstudy.pdf}
-\caption{The number of steps (and time in seconds) required before locating a defect, for each test subject and test program. 
-Cells with a white background report values with conventional debugging; Cells with a colored background use \textit{lastChange}.}
-
-\label{fig:userstudy}
-\end{figure}
-
-\section{Discussion}
-
-We have presented the \textit{lastChange} algorithm and described our
-prototype implementation. Our goal is practical improvements in debugging. To achieve our goal we need practical JavaScript engines
-to add new debug primitives so that developers in the field can use our new technique. This paper is
-one step to convince implementers to enable \textit{lastChange}.
-Thus we summarize here our arguments that \textit{lastChange} should be supported.
-
-%The key ingredients in our argument are: 
-%\begin{enumerate}
-%   \item developers need an operation like \textit{lastChange}, 
-%   \item developers can learn to use \textit{lastChange}, 
-%   \item practical implementations are feasible with modest
-%invested development time,
-%   \item in most cases \textit{lastChange} will be much faster than current alternatives,
-%   \item the worst cases are not more common or more painful than
-%alternatives.
-%	 \item the \textit{lastChange} approach can be generalized to other queries.
-%\end{enumerate}
-
-%TODOWe have also developed a prototype implementation of the debugger control part of lastChange for Java.
-The main differences (one or two sentences).
-We will report on this implementation in a later publication
-\subsection{Developers need an operation like \protect{\large\bf\textit{last- Change}} }
-
-%We have shown how \textit{lastChange} identifies the prior point in
-%program execution where a program state value changes. Is it something
-%the developer needs to do?
-
-Since ultimately programs are just
-transformation of state values, debugging is ultimately backtracking
-to find defects in program state change\cite{Weiser,Zeller}.  When a developer halts a
-program on a breakpoint they compare the call stack and program state to their model of the program.
-If any value seems to be incorrect,  they need to figure out what operation
-causes the incorrect value. Here \textit{lastChange} takes over and addresses a key
-part of the debugging process.
-%have three kinds of information: a model
-%of the program in their mind, a call stack showing what part of the
-%program is halted, and the state at that point (a combination of the
-%debugger's view of the program internal state and the output of the
-%program up to this point of execution). If the model does not match
-%the call stack or if no value in the viewable program state aligns
-%with the developers model for this point in execution, the developer
-%will seek another view by changing the breakpoint or the input
-%data. If a value appears incorrect, they may have a flash of insight
-%and know the defect. Otherwise they need to figure out what operation
-%causes the incorrect value. Here \textit{lastChange} takes over and addresses a key
-%part of the debugging process.
-
-\subsection{Developers can learn to use \protect{\large\bf\textit{lastChange}}}
-
-%If \texttt{lastChange} could be useful, can developers figure out how
-%to use it? 
-While our user study was small, our prototype demonstrates that
-\textit{lastChange} can be easily activated by operations on the
-graphical representation of erroneous data in a debugger and the 
-results can be interpreted by users. 
-While \textit{lastChange} is not a breakpoint, 
-all of the assumptions developers already have for breakpoints hold
-for \textit{lastChange}. In particular the re-execution is just the
-same operation developers use to debug with breakpoints.
-
-%We designed the
-%user interface for the results from \textit{lastChange} to resemble
-%the results from a breakpoint, with the source code of the change
-%point highlighted and the state of the program presented the way state
-%is presented from a breakpoint. Based on this user interface, we
-%believe developers can start to use \textit{lastChange} with minimal
-%training. Our users may not be representative, but the key point here
-%is that the learning curve is small compared with the challenge of learning 
-%breakpoint debugging in the first place.
-
-%In our own experience, \textit{lastChange} dramatically reduces the work in
-%setting and removing breakpoints, so work to cause re-execution  become noticeable.
-%Therefore automatic mechanisms
-%for re-execution will be corresponding more valuable for debugging
-%with \textit{lastChange} (Our \textit{Querypoint} prototype  
-%implements a simple form of automatic 
-%re-execution for both breakpoint and \textit{lastChange}).
-
-\subsection{Practical implementations are feasible}
-
-We have described our prototype all-JavaScript implementation in Sec. 4. It is adequate for 
-exploring the ideas and may even be usable in production. However significant 
-improvments can be made. A fully usable
-implementation would require access to the object id at the point of
-object creation and \texttt{setPropertyChangeHook()}. Many
-object-oriented runtimes provide object identifiers and 
-provide access to object creation directly or by bytecode instrumentation\cite{JPDA}. 
-%In the particular case of the Firefox Web browser we used for our prototype, the primary barrier
-%to practical implementation would likely be integration with the
-%increasingly sophisticated just in time compilers. In the case of
-%tracking variable changes, \texttt{setVariableChangeHook()} can be implemented
-%similar to \texttt{setPropertyChangeHook()} if JavaScript scopes-like regular 
-%JavaScript objects-support \texttt{watch()} function.
-
-\subsection{In most cases \protect{\large\bf\textit{lastChange}} will be much faster than current alternatives}
-
-%When developers try \textit{lastChange}, will they get results fast
-%enough to benefit? While we only used our prototype on toy programs,
-%\textit{lastChange} seemed as fast as breakpoint re-execution.
-%But what can we say about realistic programs?
-
-Recall that we
-insert additional code through debugger callbacks, then re-execute the
-program. The additional code we insert is proportional (in our
-JavaScript algorithm) to 1) the number of places a property or
-variable with a given name is changed, 2) the number of places objects
-are created. The overhead for each execution at a change event
- depends upon the amount of data we store for each change event; 
-the overhead for object creation could be small since we only need to 
-determine if the object is one we need to watch.
-
-%We implemented a
-%simple and effective mechanism allowing developers to control 
-%overhead: we stored data to a depth of two property accesses 
-%(e.g. foo.bar.x), then placed a \textit{re-run} button 
-%in the user interface at the third level. If developers reached the 
-%third level they can see more data at the cost of one more replay.
-
-For comparison consider today's practical alternative: developers
-setting breakpoints. For the vast majority of programs, a developer
-will take much more time to set one breakpoint than
-\textit{lastChange} would add. Moreover, typically the developer may not
-guess the point of last change. They must then ponder another
-breakpoint and re-execute.
-
-%Unlike the re-execution we use to 
-%optimize performance in \textit{lastChange}, 
-%developers still will not know if the breakpoint they hit is the point of last change
- %or even if it is related to the change at all.
-
-We could also compare to solutions based on logging or tracing. Manual
-logging has very high overhead: the developer must add code, debug
-that added code, then analyze the log (To be fair, the log can become
-a permanent debugging aid). Automatic logging as we discuss in 
-section \ref{sec:relatedWork} causes about one or two orders of magnitude slow down as well
-as requiring a completely different set of development tools.
-
-\subsection{The worst cases are not more common or more painful than alternatives}
-
-%Finally we consider the worst cases: what about code that changes
-%objects in long running loops? 
-Every time through the loop we incur
-the call back overhead; if the loop itself has relatively little code
-the overhead could be very large; if the loop computation is a
-significant fraction of the full program, the slowdown would be
-enormous. 
-Other techniques also struggle with this case:  breakpoints in highly repeating loops are not feasible and logging
-becomes unwieldy. 
-Developers face this issue with any debugger today: occasionally a
-debugger causes too much overhead to be useful for debugging. 
-%Since automatic logging solutions are highly tuned,
-%their overhead in this case will likely be much less than
-%\textit{lastChange}. On the other hand, \textit{lastChange} integrates
-%with an interactive debugger and detecting that we are in a high
-%overhead loop is simply a matter of checking our internal counter. %
-%In
-%such unusual cases we may simply offer the developer the option of
-%studying the loop code then omitting it from \textit{lastChange}
-%operations. 
-%
-%The users of \textit{lastChange} may encounter these kinds of cases, but 
-%that is the nature of debugging: you need different tools for 
-%different kinds of problems.
-
-\subsection{Generalizations}
-Our \textit{lastChange} algorithm can be viewed as a particular interface to a general facility. 
-The general facility replays execution, queries the runtime at points of interest during execution,
-and analyzes the result at the reproduction point. We have selected one kind of query and analysis
-that can be easily integrated in existing debuggers and explained to developers, providing automation of 
-the problem of finding the point of last change. We believe other
-kinds of queries and analysis can be invented and integrated to automate other aspects of debugging.
-%Moreover, the query history analysis used to test for non-determinism here may also be the basis for
-%more effective user interfaces to debugging sessions. The series of cascaded \textit{lastChange} queries becomes 
-%logical path followed by the developer seeking the defect and this path may be useful if presented in effective user interfaces.
-
-\section{Related Work}
-\label{sec:relatedWork}
-%The algorithm we presented in this paper obtain information about
-%the execution state logically earlier in the control flow by querying 
-%the executioin state during replay using the technology of 
-%conventional breakpoint debuggers.  
-The \textit{lastChange} approach resembles the operational model of replay-based debugging 
-and the query approach of logging-based
-debugging.  Replay-based approaches capture limited data during
-execution and replay the buggy execution to reach past points. In
-contrast, logging-based approaches collect enough data during
-execution to relieve developer from re-execution, then query the data to 
-inform the developer. Replay-based
-approaches impose much less runtime overhead (about two orders of
-magnitudes) comparing to logging-based approaches. However, developer
-has to re-execute the buggy execution several
-times. \textit{lastChange} collects data on re-execution by queries
-selected by developer interaction with the debugger. Therefore it has 
-the selectivity of the replay-based approaches that improves performance, 
-% but we have 
-and the flexibilty of the queries so it does not require deterministic replay.
-
-Among replay-based debuggers we compare to bdb \cite{Boothe} and
-reverse watchpoint \cite{Maruyama}.  A bidirectional C debugger, bdb
-employs a step counter to locate the requested point from the
-beginning of execution. It relies on deterministic execution replay
-%(i.e., the same sequence of instructions in re-execution) 
-and records the results of non-deterministic system calls and re-injects them into
-the program when it is replayed. It makes use of checkpoints to reduce
-the time needed for re-execution. Reverse watchpoint, similar to bdb, uses
-a counter to correctly locate the last write access of a selected variable in the
-next execution \cite{Maruyama}.
-% Reverse watchpoint is proposed by Maruyama et al., analyses the execution and moves the debugger to the
-% last write access of a selected variable by re-executing the program
-%from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
-%replay and uses a counter to correctly locate a point in the next
-%execution. 
-The main disadvantage of these approaches is that they require 
-identical, instruction by instruction, re-executions. % exactly the same executions. 
-Even one instruction difference between
-two executions leads to wrong results. On the other hand,
-\textit{lastChange} doesn't require any special feature in the
-re-execution and fits into existing debugging practice
-
-Among logging-based approaches are \textit{omniscient} debuggers
-ODB\cite{Lewis} and Unstuck\cite{Hofer}. Both
-approaches keep the log history in memory and hence can only record
-and store the complete history for a short period of time. These
-debuggers record all the events that occur during the buggy execution
-and later let the developer to navigate through the obtained execution
-log. In these approaches there is no execution to resume: moving
-backwards in the log can be similar to moving forwards. A more scalable 
-approach to omniscient debugging has been proposed by Pothier et al. \cite{Pothier}. 
-Their back-in-time debugger, TOD, addresses the space problem by storing 
-execution events in a distributed database. Bhansali et al. \cite{Bhansali} attempted to address the performance overhead 
-and large trace size of logging-based debugging in their time-travelling debugger, Nirvana. 
-Nirvana first collects a full compressed trace of program execution and then 
-simulates re-execution. Their results are quite similar to omniscient 
-debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
-re-simulation.
-
-Logging-based debuggers suffer from different issues. First, the recording
-step is time expensive and it should be repeated in case of changes in
-program. Second, the execution log cannot fully replace the live
-execution. There are other aspects of execution (e.g., program user
-interface, file system, database tables, etc.) which are also
-important in debugging and are not available to the developer in
-omniscient debuggers. Third, querying collected data (e.g., to restore
-the program state at a certain point) may not be efficient enough for
-debugging realistic programs. Comparing to logging-based debuggers our approach is 
-has little upfront cost and more flexibility. The developer can start debugging just 
-after reproducing bug without a capturing step.  Changing inputs or
-environment settings and re-executing to investigate the bug works as
-in conventional breakpoint debuggers.
-
-Program slicing\cite{Weiser} approaches debugging from a completely different perspective.
-Given a point of interest {\bf S} in a program, a \textit{slice} is an executable subset of the program affecting {\bf S}.
-Many studies have shown ways to compute the slice more quickly or to constrain the slice to a smaller subset of the program \cite{Horwitz, Sridharan}.
-Dynamic slicing \cite{Korel} applies slicing analysis at run time and thus most closely resembles \textit{lastChange} from among the slicing approaches.
-Our \textit{lastChange} approach can be related this way: first, allow the developer to select from {\bf S} a key critical value {\bf V}.
-Then compute a slice affecting {\bf V}.
-Show the developer only the most relevant part of that slice (the \textit{lastChange}).
-Finally iterate towards the fault by chaining new slice-selection criteria.
-
-Both approaches rely on selecting {\bf S}.
-Both approaches differ from breakpoint debugging in analyzing a program from a known good point (e.g.
-start of the program) to {\bf S}.
-Slicing reduces the space the developer needs to search, but provides no guidance within the slice; \textit{lastChange} explores the slice using developer-selected search criteria, but does not help the developer recognize code that cannot impact {\bf S}.
-Slicing requires a sophisticated compiler-like technology while \textit{lastChange} builds on familiar run-time debugger technology.
-
-A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
-machine level support for keeping the history of events. It replaces every
-object reference with an alias object which keeps the history of
-changes to the object reference. 
-%In this way, when an object is
-%collected by garbage collector, its track of changes (if it is not
-%referenced by other aliases) will be also collected. 
-Although this approach incurs less runtime overhead (7 times) in
-comparison to omniscient debuggers, it adds memory
-overhead.
-
-Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
-Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
-First, it is limited to \texttt{undefined} and \texttt{null} values. Second, it does not return the last change
-of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
-
-%Two new directions in logging debuggers explore more detailed use of
-%the log and more effective user interface to the collected data. %logging approaches. 
-%WhyLine\cite{Ko} provides visual interface to collected runtime information and lets
-%developer moves on execution log using queries expressed in terms of
-%the programming objects.
-
-WhyLine\cite{Ko} stores the program user interface in
-addition to the program trace and provides answers to why and why not
-questions to the user. 
-%Jive\cite{Czyz} depicts the history of
-%execution by a sequence diagram and lets the user to query on the events
-%database. 
-WhyLine suffers from the requirement of gathering tracing information before its unique capabilities can be used.
-We imagine that the runtime queries we use in \textit{lastChange} may be used to gather data incrementally for this kind of debugging approach.
-
-%Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
-Moreover, the Lienhard et al.
-debugger significantly changes the virtual machine, while our approach is a generalization to conditional breakpoints and available debugger infrastructure can be adapted to support it.
-
-%\textit{lastChange} functionality does rely on a conventional breakpoint to begin queries, a requirement not shared by full logging solutions.
-Here we leverage past experience of developers, but there are also new tools [] to help with this problem in the case of graphical and event based systems.
 
 \section{Conclusion}
-\textit{lastChange} provides critical information for debugging programs: the location and state at the point where a questionable value was assigned.
-It builds upon existing technology and developer experience making it a practical solution for implementers.
-Our prototype demonstrates the feasibility of \textit{lastChange} and its user interface hints at the potential this approach can have in organizing the debugging experience.
-
-%ACKNOWLEDGMENTS are optional
+
 \section{Acknowledgments}
-The authors thank Leo Meyerovich for reading a draft of this paper and suggesting the example in section \ref{sec:resultConsistency} and
-Jan Odvarko and Mike Collins for testing the prototype before our user study and providing helpful suggestions.
 

### 2011-06-08 papers/fse-tool2011/sig-alternate.tex

--- 2011-03-12 trunk/papers/fse2011/sig-alternate.tex
@@
 \begin{abstract}
-%Developers often seek the origins of wrong values they see in their
-%debugger. Their search must be backwards in time: the code causing the
-%wrong value executed before the wrong value appeared. Searching with
-%breakpoint- or log- based debuggers demands persistence and
-%significant experience with the application being debugged. 
-We introduce a new, practical feature for debuggers called \textit{lastChange}, 
-which automatically locates the last point that a variable or an object property 
-has been changed. Starting from a 
-program halted on a breakpoint, the \textit{lastChange} solution
-applies queries to the live program during re-execution, recording the call stack 
-and limited program state each time the property value changes.
-When the program halts again on the breakpoint, the recorded information 
-can be shown to the developer.
-As a proof of this concept, we developed \textit{Querypoint}, a prototype
-which enhances the popular Firebug JavaScript debugger with
- the \textit{lastChange} feature and studied users applying the prototype to 
-some test cases.
- The approach used in implementing 
-\textit{lastChange} combines the flexibility of breakpoint debugging
-with the expressive power of log-based query debugging.  Contrary to
-other replay-based approaches, which require exactly the same
-re-executions (deterministic executions), our new approach only requires \textit{bug 
-reproducibility}, meaning a test case is available which reproduces the bug and a 
-way to halt execution reliably after the reproduction.
 
 \end{abstract}
+Developers often seek the origins of wrong values they see in their
+debugger. Their search must be backwards in time: the code causing the
+wrong value executed before the wrong value appeared. Searching with
+breakpoint- or log- based debuggers demands persistence and significant 
+experience with the application being debugged.
+
+\textit{Querypoint}, is a Firefox plugin which enhances the popular 
+Firebug JavaScript debugger with a new, practical feature called 
+\textit{lastChange}. \textit{lastChange} automatically locates the last point that 
+a variable or an object property has been changed. Starting from a 
+program halted on a breakpoint, the \textit{lastChange} algorithm 
+applies queries to the live program during re-execution, recording 
+the call stack and limited program state each time 
+the property value changes. When the program halts again on the breakpoint, 
+it shows the program state at the last change point. To evaluate the usability and effectivness 
+of \textit{Querypoint} we studied four experienced JavaScript developers applying the tool to two test cases.
 
@@
 
-In breakpoint debugging, developers select data to be collected by
-searching through source files and setting breakpoints. To determine
-where a value was set incorrectly, a developer must set
-breakpoints at all possible points where the value changes. At
-every breakpoint, the developer must determine if the location is in
-fact related to the questionable value change then study the complex
-debugger user interface and memorize values or manually collect
-data. As the number of breakpoint hits increases, the process of
-checking the program state, collecting data and resuming the execution
-becomes cumbersome.
-
-In log-based debugging, developers select data to be collected by
-inserting statements for all points of possible change.  While in
-breakpoint-based debugging, the whole program state is available to
-developer, in log-based debugging, developer has to decide what data
-should be collected when inserts the log statement. It is very common
-that the developer has to repeat this step several times due to
-insufficient collected data, or to wait a long time because too much
-data is recorded. Once adequate data is collected, it still
-requires analyzing and understanding. Developers usually end up in
-dealing with long log files and analyzing huge amounts of collected data. 
-Neither approach efficiently assists the developer in finding origins to a wrong
-value.
-
-Our new functionality in
-debuggers, \textit{lastChange}, locates the origin of a wrong
-value by queries on the running program.
-Imagine that a program execution is
-paused on a breakpoint and the developer is
-suspicious about the value of a variable or an object property. The
-developer selects \textit{lastChange} on the value. The debugger
-replays the buggy execution and collects data
-when the data field changes. Once the execution reaches the same place 
-(i.e., the same
-breakpoint hit), it pauses the execution, analyzes the collected data
-and shows the location of the last change to the developer. The
-developer can also examine the program state at the located point of
-execution, and continue debugging by more \textit{lastChange} queries
-from that point.
-
-Our contribution in this paper is the technique \textit{lastChange},
-which locates the last place a value has changed, gathers other values
-from that execution point, and allows \textit{lastChange} operations
-from that point. The technique builds on existing breakpoint debugger
-technology  and it does not require a special environment to
-create identical, instruction by instruction, re-executions. We demonstrate the feasibility of the approach with 
-\textit{Querypoint}, an implementation extending Firebug
-JavaScript debugger. \textit{Querypoint} also provides mechanism for
-automated bug reproduction, and a novel user interface which
+%In breakpoint debugging, developers select data to be collected by
+%searching through source files and setting breakpoints. To determine
+%where a value was set incorrectly, a developer must set
+%breakpoints at all possible points where the value changes. At
+%every breakpoint, the developer must determine if the location is in
+%fact related to the questionable value change then study the complex
+%debugger user interface and memorize values or manually collect
+%data. As the number of breakpoint hits increases, the process of
+%checking the program state, collecting data and resuming the execution
+%becomes cumbersome.
+
+%In log-based debugging, developers select data to be collected by
+%inserting statements for all points of possible change.  While in
+%breakpoint-based debugging, the whole program state is available to
+%developer, in log-based debugging, developer has to decide what data
+%should be collected when inserts the log statement. It is very common
+%that the developer has to repeat this step several times due to
+%insufficient collected data, or to wait a long time because too much
+%data is recorded. Once adequate data is collected, it still
+%requires analyzing and understanding. Developers usually end up in
+%dealing with long log files and analyzing huge amounts of collected data. 
+%Neither approach effectively assists the developer in finding origins to a wrong
+%value.
+
+Locating the origin of wrong values becomes even harder when developers 
+deal with weakly-typed dynamic languages such as JavaScript. First, due to weakly-typed
+nature of these languages the search space that the developer should consider is considerably 
+larger than traditional languages such as Java and C{\small\#}. Second, dynamic features make 
+program full static analysis almost impossible.
+
+\textit{Querypoint}, is a Firefox plugin which enhances the popular 
+Firebug JavaScript debugger with a new, practical feature called 
+\textit{lastChange}\cite{Mirghasemi2011}. \textit{lastChange}, locates the origin of a wrong
+value by queries on the running program. This feature enables interactive 
+dynamic data dependency navigation without requiring a full trace, unlike 
+other dynamic slice navigation interfaces. The technique builds on existing 
+breakpoint debugger technology  and it does not require a special environment to
+create identical, instruction by instruction, re-executions. \textit{Querypoint} 
+also provides mechanism for automated bug reproduction, and a novel user interface which
 summarizes investigated execution points and collected results.
-The \textit{lastChange} algorithm provides information on important program
-values during the program execution without voluminous logs and without tedious
- insertion and removal of breakpoints. We believe other queries over the
- running program can be formulated to generalize this technique.
-
-The rest of the paper is organized as follows. First, we demonstrate
-the \textit{lastChange} usage on a simple example with the comparison
-to breakpoint debugging. Section 3 presents \textit{lastChange}
-algorithm. In section 4, we explain the details of the JavaScript
-prototype implementation. We discuss the effect of non-determinism on
-the \textit{lastChange} results in section 5. The user study results 
-are presented in section 6. %TODO update it according to new Section 6 contains an evaluation of\text{lastChange} functionality.
-
-\section{Introductory example}
+
+%Morover, it implements interactive 
+% dynamic data dependency navigation for JavaScript, which poses a unique 
+% challenge with respect to its dynamic nature.
+
+%Imagine that a program execution 
+%is paused on a breakpoint and the developer is
+%suspicious about the value of a variable or an object property. The
+%developer selects \textit{lastChange} on the value. The debugger
+%replays the buggy execution and collects data when the data field changes. 
+%Once the execution reaches the same place (i.e., the same
+%breakpoint hit), it pauses the execution, analyzes the collected data
+%and shows the location of the last change to the developer. The
+%developer can also examine the program state at the located point of
+%execution, and continue debugging by more \textit{lastChange} queries
+%from that point.
+
+\section{Related Work}
+\label{sec:relatedWork}
+%whyline, firecrystal
+Most tools developed to enhance developers' navigation on the buggy execution can 
+be classifed in two main groups: replay-based and logging-based. Replay-based 
+approaches capture limited data during execution and replay the buggy execution 
+to reach past points. In contrast, logging-based approaches collect enough data during
+execution to relieve developer from re-execution, then query the data to 
+inform the developer.
+
+Among replay-based debuggers we can name bdb \cite{Boothe} and
+reverse watchpoint \cite{Maruyama}. Both tools rely on deterministic
+executions and employ a step counter to locate the requested point from the
+beginning of execution. These tools incur two to four times runtime overhead.
+
+Among logging-based debuggers are \textit{omniscient} debuggers (e.g.,
+ODB\cite{Lewis}, TOD \cite{Pothier}, Unstuck\cite{Hofer} and WhyLine\cite{Ko}) and
+time-travelling debuggers (e.g., Nirvana \cite{Bhansali}). Logging-based debuggers 
+suffer from different issues. First, the recording
+step is time expensive (20-120 times) and it should be repeated in case of changes in
+program. Second, the execution log cannot fully replace the live
+execution. There are other aspects of execution (e.g., program user
+interface, file system, database tables, etc.) which are also
+important in debugging and are not available to the developer in 
+logging-based debuggers. Third, querying collected data (e.g., to restore
+the program state at a certain point) may not be efficient enough for
+debugging realistic programs.
+
+\textit{Querypoint} resembles the operational model of replay-based debuggers
+and the query approach of logging-based debuggers. Contrary to
+other replay-based debuggers, which require exactly the same
+re-executions (deterministic executions), \textit{Querypoint} only requires \textit{bug 
+reproducibility}, meaning a test case is available which reproduces the bug and a 
+way to halt execution reliably after the reproduction. Contrary to logging-based
+debuggers \textit{Querypoint} selectively collects data which significantly reduces
+runtime overhead incured by logging.
+
+%A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
+%machine level support for keeping the history of events. It replaces every
+%object reference with an alias object which keeps the history of
+%changes to the object reference. Although this approach incurs less runtime overhead (7 times) in
+%comparison to omniscient debuggers, it adds memory
+%overhead.
+
+% Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
+%Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
+%First, it is limited to \texttt{undefined} and \texttt{null} values. Second, it does not return the last change
+%of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
+
+\section{Querypoint}
 \label{sec:introExample}
 
-We illustrate the \textit{lastChange} functionality by a simple
+We illustrate the \textit{Querypoint} functionality by a simple
 example. The example demonstrates a buggy JavaScript code in a HTML
@@
 \texttt{updateButton} function which updates the button's text to the new
-value (line 22).  Once the page is loaded for the first time the
+value (line 22).  Once the page is loaded for the first time, the
 button shows \texttt{1} as the initial value of
@@
 
-Two other functions are called in \texttt{onClick()}, \texttt{foo()}
-and \texttt{bar()}. As developers we often encounter function calls
-which seem peripheral to our current concern; they may have been added
-by another developer, or we may have forgotten their exact properties
-or those properties may have changed, and so on. The difference
-between what we expect these functions to do, e.g. nothing
-interesting, and what they do in practice may cause bugs.
+%Two other functions are called in \texttt{onClick()}, \texttt{foo()}
+%and \texttt{bar()}. As developers we often encounter function calls
+%which seem peripheral to our current concern; they may have been added
+%by another developer, or we may have forgotten their exact properties
+%or those properties may have changed, and so on. The difference
+%between what we expect these functions to do, e.g. nothing
+%interesting, and what they do in practice may cause bugs.
 
@@
 
-By browsing through the code or other means\cite{Barton},
+By browsing through the code,% or other means\cite{Barton},
  the developer determines that the value displayed on the 
@@
 
+\begin{figure*}[htp]
+
+\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
+  panel is selected; it gives access to
+  all loaded source files and allows breakpoints to be set on lines. In this
+  figure, the execution is paused at line 22 by a regular
+  breakpoint. The Watch panel on the right shows the program state at
+  the paused
+  point.
+Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
+]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
+  ]{1-bp22.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myObject.myProperty}. The left panel, QP, shows the source
+  code at the point of \textit{lastChange}; The right panel,
+  TraceData, shows the collected data at the
+  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
+  ]{3-lastChange.jpg}}
+
+\subfigure[The result of \textit{lastChange} query for
+  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
+  enter the expression in the watch box and after re-execution the result is available.
+  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
+  the list shows the corresponding code and
+  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
+    ]{4-lastChange2.jpg}}
+
+\caption{The stages of locating the defect using \textit{lastChange} feature.}
+\label{fig:lastChange}
+\end{figure*}
+
 To apply backward search strategy for locating defects, the developer
@@
 
-\begin{figure}[htp]
-\centering
-
-\includegraphics [width=.48\textwidth]{5-example-points.pdf} 
-\caption{The examined points before locating the defect.
-The arrow represents the logical forward progress of the program.
-Three actual executions are superimposed on this arrow.
-All three stop at the reproduction point indicated by circle 1.
-After the first execution, the developer asks for lastChange as described in section \ref{sec:introExample}, yielding information  indicated by circle 2.
-After the second execution, another lastChange query causes a third execution, yielding information indicated by circle 3.}
-\label{fig:example-points}
-\end{figure}
-
 Looking at line 29, it seems that something is wrong with
@@
 
-As demonstrated in Figure~\ref{fig:example-points}, the developer has
-examined three points of execution. The first point  was the breakpoint set by the developer. 
+The developer has examined three points of execution. The first point  was the breakpoint set by the developer. 
 We call this special breakpoint the \textit{reproduction point}.
@@
 interface. On the top of the left panel in Figure~\ref{fig:example4}
-there is an opened list which shows all three examined points. The
-first one is the breakpoint on line 22, the second one is the point
-which is when \texttt{myObject.myProperty} changed before
-reaching the breakpoint and finally the last one is the point of
-execution in which \texttt{myCondition.value} gets the
-\texttt{undefined} value. Moreover, the source lines related to these
+there is an opened list which shows all three examined points. Moreover, the source lines related to these
 points are marked with red \textbf{Q} icons.
-
-\begin{figure*}[htp]
-
-\subfigure[A screen shot of the Firebug debugger while running the example code from Fig.~\ref{fig:js-code}. The Script
-  panel is selected; it gives access to
-  all loaded source files and allows breakpoints to be set on lines. In this
-  figure, the execution is paused at line 22 by a regular
-  breakpoint. The Watch panel on the right shows the program state at
-  the paused
-  point.
-Developer can query \textit{lastChange} on \texttt{myObject.myProperty} by right-clicking on the value of \texttt{myProperty}.
-]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
-  ]{1-bp22.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myObject.myProperty}. The left panel, QP, shows the source
-  code at the point of \textit{lastChange}; The right panel,
-  TraceData, shows the collected data at the
-  point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
-  ]{3-lastChange.jpg}}
-
-\subfigure[The result of \textit{lastChange} query for
-  \texttt{myCondition.value}. To evaluate an expression (e.g., oldValue) at this point, developer can %TODO should we remove it?
-  enter the expression in the watch box and after re-execution the result is available.
-  The opened list on the top of the left panel shows the visited execution points. Clicking on each point in
-  the list shows the corresponding code and
-  data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
-    ]{4-lastChange2.jpg}}
-
-\caption{The stages of locating the defect using \textit{lastChange} feature.}
-\label{fig:lastChange}
-\end{figure*}
-
-Notice that in our example, \textit{lastChange} combines some aspects
-of breakpoint and of log-based debugging. Like breakpoint debugging,
-the developer re-executes a live runtime without changing the source
-and without a special execution environment beyond the debugger. The
-state of the program memory and the call stack are available at each
-lastChange point. Like log-based debugging, the program state and the
-call stack are recorded during program execution. We can't halt the
-program at \textit{lastChange} because we don't know which point is the last
-one until we return to the original breakpoint. In section 5 we
-discuss cases where it is possible to pause at lines of \textit{lastChange}.
-
-\section{lastChange Algorithm}
-
-The \textit{lastChange} algorithm is based on program re-execution of
-a program halted on a breakpoint. The algorithm starts when developer
-examines the program state at a breakpoint hit and asks for the
-\textit{lastChange} of a value. The breakpoint hit becomes the
-\textit{reproduction point}. Debugger sets hooks (a callback
-function dependent upon the underlying runtime) on all instructions
-that might be the result of \textit{lastChange} query. Then the
-debugger re-executes the program and every time a hook hits it
-checks for a \textit{change event}. In the case of a change, it stores
-part of the program state values.  Once the execution reaches the
-reproduction point, it analyzes the collected data and shows the
-result.  The program state at the execution point of the last change
-event is the \textit{lastChange}.
-
-As we described in the preceding section, a \textit{lastChange} query can
-be performed on the result of another \textit{lastChange} query. If we
-name the reproduction point \textit{R}, we can write the first
-\textit{lastChange} in the introductory example in this form:
-\textit{lastChange(R, myObject.myProperty)}. It means that this query
-is defined at \textit{R}. If we name the result of this query
-\textit{L}, we can write the second \textit{lastChange} in this form:
-\textit{lastChange(L, myCondition.value)}. In this way, a sequence of
-\textit{lastChange} queries with any length can be defined.
-
-\textit{lastChange} can be called on object property, on a variable value, 
-or on the results of a \textit{lastChange}. Moroever, common data structures such as
-arrays and hashmaps are also supported as special cases of \textit{lastChange} on object property.
-We explain each case in the following subsections.
-
-\subsection{{\large\bf\textit{lastChange}} on Object Property}
-To simplify the algorithm explanation and defer technical details, we
-define two basic operations and later we explain the details of these
-two operations. The first operation is \texttt{objectId()}: given a
-JavaScript object it returns an integer as its identifier. This
-identifier is unique to the object during one execution.  By using an
-object id instead of an object reference we allow the garbage
-collector to reclaim the space for dead objects just as it would in the
-absence of the debugger. The second
-operation is \texttt{setPropertyChangeHook()}: given a function and a
-string, the function is called whenever a property changes and its
-name matches the string. For example, if the string is 
-\texttt{foo}, changes to \texttt{bar.foo} or \texttt{baz.foo} would
-call the function.  The callback function receives a reference to the
-owner of \texttt{foo}.
-
-To see how these functions work, suppose the developer asks for the
-last change of \texttt{bar.foo} at the reproduction point in a
-program. The debugger calls \texttt{setPropertyChangeHook()} with
-\texttt{foo} as the property name and re-executes the
-program. Whenever \texttt{foo} changes and the callback function is to
-be called, debugger first calls \texttt{objectId()} on the
-\texttt{foo} owner object. Then it stores this owner id, the stack
-frame locations, and other state values in scope at the call point. 
-Then the callback returns to continue the execution. Thus the query is not 
-a breakpoint in the sense of pausing for user interaction, but breakpoint 
-technology can be used to implement the query.
-Whenever the execution reaches the reproduction point the debugger
-looks at the history of \texttt{foo} changes and finds the last
-\texttt{foo} change with the same object id as \texttt{bar} id at the
-reproduction point. Figure~\ref{fig:foo-changes1} shows the list of
-property \texttt{foo} change events in a hypothetical
-execution. \texttt{bar} id at the reproduction point is 1010, so the
-last change of \texttt{bar.foo} is the fourth column.
-
-\begin{figure}[htp]
-\centering 
-\includegraphics [width=.48\textwidth] {6-foo-changes1.pdf} %[width=.48\textwidth][scale=0.75]
-\caption{A hypothetical list of  change events for a property \texttt{foo}. 
-Each change event adds a column with the id of the object changed, the call stack,
-and some program state such as local variable values. 
-At the reproduction point  we determine which id  corresponds to 
-object \texttt{bar} and read out column 4,  the last
-  change of \texttt{bar.foo}. Column 3 is also a change of
-  the object we want to study, id 1010, but it is not the last change;
-  Column 5 is also a change of a property \texttt{foo} but it is not for
-  the object we are interested in.}
-\label{fig:foo-changes1}
-\end{figure}
-
-\subsection{{\large\bf\textit{lastChange}} on Variable} 
-In JavaScript, every frame has a scope chain and every available
-variable in the frame comes from one of the scopes in the frame's
-scope chain. Once the developer asks for the last change of a variable with name 
-\texttt{foo} at the reproduction point, the debugger first determines the
-variable's scope as follows: it iterates over the scopes in the scope
-chain and the first scope which has a variable with the same name is
-the variable's scope. There are five different scope types: global, local,
-closure, \texttt{with} and \texttt{catch}. We explain these
-cases in two groups.
-
-\subsubsection{global and \texttt{with} scopes}
-Global scope is the most outer scope in the scope chain and it is
-also referred to as the global object (the \texttt{window}
-object in Web pages). This scope is a regular JavaScript object and therefore every
-global variable is a property of global object. Similarly,
- \texttt{with} scopes are also regular JavaScript objects. A \texttt{with}
-scope is created by a \texttt{with()} block with an object as the
-parameter. Every property of this parameter object is available inside the
-block as a variable. \textit{lastChange} treats the case where variable's scope
-is global or \texttt{with}, like it does on an object
-property.
-
-\subsubsection{local, closure and \texttt{catch} scopes}
-Local scope refers to the most nested scope in the scope
-chain which contains the local variables. Closure scope refers to the 
-scope which is created for a nested function and contains variables 
-defined in the outer block. Catch scope is the scope created in the catch
-block of try-catch statements and contains the exception
-variable. These scopes are not necessarily regular JavaScript
-objects.  
-Therefore, to track changes to a variable in these scopes we
-employ a different approach.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\includegraphics [width=.48\textwidth] {9-scopes.pdf} %[width=.48\textwidth][scale=0.75]
-
-%\lstset{basicstyle=\scriptsize}
-%\begin{lstlisting}[language=myLang, framerule=0pt]
-%  function f(){
-%    var x = 0;	
-%    x++;
-%    ...
-%    if (!stop) f();
-%  }
-
-%Sample Trace:
-
-%   f()
-%A  |  x changes, scope 1 
-%   |  f()
-%   |  |  x changes, scope 2
-%   |  |  f()
-%B  |  |  |  x changes, scope 3 
-%C  |  ... , scope 1
-%\end{lstlisting}
-%\end{verbatim}
-\caption{A recursive call trace illustrating the scope
-  id.
-The lines in the bottom half of the diagram simulate a trace of the change events for the variable \texttt{x} as the function \texttt{f()} calls itself.
-Each call creates a scope; eventually when the variable \texttt{stop} is changed by an external process we return from the recursion.
-The lines marked A, B, and C are discussed in the text.}
-\label{fig:recursive}
-\end{figure}
-
-Having the scope chain and the source code, we can map every scope to % perhaps needs more explanation, how?
-a code block, enclosed the executing code. In
-JavaScript, a code block can be identified by the file url and  
-the block's first instruction program counter. Given this information, the debugger is
-able to recognize the code block in loaded scripts or once it is loaded.
-Similar to \textit{lastChange} on object property, we define two basic operations: 
-\texttt{scopeId()} -- which returns an integer given a scope -- and \texttt{setVariableChangeHook()} -- which calls its first parameter, a callback function, when a 
-variable in its second parameter, a code block, matches the name given in the third parameter.
-
-Figure~\ref{fig:recursive} illustrates how the \texttt{scopeId()} operation separates instances 
-of a variable in different scopes having the same name.
-If we ask for the last change on \texttt{x} at point labeled \texttt{C} in scope with id 1, we want the change at line \texttt{A} in scope 1, not 
-the change at the line marked \texttt{B}, where a variable named \texttt{x} in scope 3 is changed.
-
-If the developer asks for the last change of variable \texttt{foo} at the 
-reproduction point in a program, debugger calls 
-\texttt{setVari- ableChangeHook()} with the variable's defining
-block and name as parameters and re-executes the
-program. Whenever \texttt{foo} changes and the callback function is to
-be called, debugger first calls \texttt{scopeId()} on the
-variable's scope. Then it stores this scope id, the stack
-frame locations, and other state values in scope at the call point.
-Whenever the execution reaches the reproduction point the debugger
-looks at the history of \texttt{foo} changes and finds the last
-\texttt{foo} change with the same scope id as the variable's scope id
-at the reproduction point (Figure~\ref{fig:foo-changes2}).
-
-\begin{figure}[htp]
-\centering 
-\includegraphics[width=.40\textwidth]{7-foo-changes2.pdf}
-\caption{A hypothetical list of variable \texttt{foo} change events. Each column of the list indicates a change event; for each
-change event the scope id returns by \texttt{scopeId()} is recorded along with call stack and program state information. 
-   The last column having the scope id \texttt{foo} at the reproduction point indicates 
-  the last change.}
-\label{fig:foo-changes2}
-\end{figure}
-
-\subsection{{\large\bf\textit{lastChange}} on {\large\bf\textit{lastChange}}}
-The \textit{lastChange} algorithm records changes by id (either object or scope id), then reads out the last change when we
-arrive at the reproduction point and discover the id of the requested value.
-When we perform \textit{lastChange} based on a previous \textit{lastChange}, the query algorithm 
-must retain additional information. Consider the following example:
-
-\lstdefinelanguage{myLang2}
-{morekeywords={point, lastChange}}
-
-\lstset{basicstyle=\small}
-\begin{lstlisting}[frame=single, language=myLang2] %, framerule=0pt]
-
- point A : the reproduction point 
- point B : lastChange(A, bar.x) 
- point C : lastChange(B, baz.y) 
-\end{lstlisting}
-
-%\begin{center}
-%\textit{
-% }
-% \end{center}
-
-where point A is a breakpoint, point B is the last change of the object property \texttt{bar.x} at point A, and
-point C is the last change of the object property \texttt{baz.y} at point B. 
-The object referenced by \texttt{baz} changes upon re-execution. Therefore when the developer
-asks for the last change of \texttt{baz.y}, we need to track objects named \texttt{baz}
-at changes of \texttt{bar.x} and changes to objects named \texttt{y}. Then, at the reproduction point,
-we need to work out which \texttt{baz} the developer wanted, then select the last change of that \texttt{baz.y}.
-Figure~\ref{fig:lastchange-lastchange} illustrates the extra row of data (tracking of \texttt{baz} objects 
-at \texttt{x} change events) 
-and how the id values allow the last change of \texttt{baz.y} to be worked out.
-
-In the general case we perform dependency analysis as outlined in 
-Figure~\ref{fig:dependency-analysis} to
-create the list of additional data (object id or scope id) to be collected at a change
-event. The process can be repeated to cascade \textit{lastChange} arbitrarily deep.
-
-\begin{figure}[htp]
-\centering 
-\includegraphics[width=.48\textwidth]{8-lastchange-lastchange.pdf}
-\caption{The list of change events stored for locating point B, the
-  \textit{lastChange} of \texttt{bar.x} at the reproduction point, and
-  point C, the \textit{lastChange} of \texttt{baz.y} at point B.}
-\label{fig:lastchange-lastchange}
-\end{figure}
-
-\begin{figure}[htp]
-%\centering 
-%\begin{algorithm}
-\line(1,0){240}
-\begin{algorithmic}%[frame=single]
-\FOR{$q$ in $lastChange$ queries} 
- \FOR {$p$ is defined at the $q$ result}
-   \IF {$p$ is a $lastChange$ on object property} 
-     \STATE the property {\bf owner id} must be stored at $q$ change events. 
-   \ELSIF {$p$ is a $lastChange$ on variable} 
-     \STATE the variable {\bf scope id} must be stored at $q$ change events.
-	 \ENDIF 
- \ENDFOR 
-\ENDFOR
-
-\end{algorithmic}
-\line(1,0){240}
-%\end{algorithm}
-\caption{\textit{lastChange} queries dependency analysis.}
-\label{fig:dependency-analysis}
-\end{figure}
-%---------------------------------------------------------------------------------------------------
-\section{JavaScript implementation}
-To verify the \textit{lastChange} algorithm we
-implemented\footnote[1]{http://code.google.com/p/querypoint-debugging} it in an extension to the Firebug
-JavaScript debugger\footnote[2]{http://getfirebug.com}. %\cite{Firebug}. %\cite{firebug-version-1.6}. 
-Firebug itself is an extension of the Firefox browser. %\cite{Firefox}. %\cite{firefox-version-3.6}
-The Firefox JavaScript engine provides a JavaScript debugging interface \cite{JSD} and 
-\textit{Querypoint} is developed over this interface. Our prototype implements the four primitive operations in JavaScript 
-using techniques which are cumbersome and comparatively slow to execute. However the JavaScript prototype is
-easy to explore, change, and share with others for feedback. A professionally useful debugger 
-would implement these primitive operations within the JavaScript engine.
-
-\subsection{{\normalsize\bf\texttt{objectId()}} Operation}
-\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
-%\footnote[3]{The property name we used in the prototype is longer and more specific to reduce the chance of name conflicts.} .
-It returns the value if this property is already defined,
-otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
-for each new \texttt{\_objectId} needed. 
-%\footnote[3]{This use of a regular object property  might change
-%the program behaviour. For example it will appear as an extra property in 
-%\texttt{for(property in object)} loops. 
-%The next version of Firefox (https://developer.mozilla.org/en/JavaScript/Reference\\/Global\_Objects/Object/defineProperty) provides \texttt{defineProperty}, 
-%allowing a property to be added which is invisible to enumeration.} Note that \texttt{\_objectId} is
-%not set for all objects but only those objects that need an id.
-
-\subsection{{\normalsize\bf\texttt{setPropertyChangeHook()}} Operation}
-The Firefox JavaScript engine supports watching property changes in an
-object. Every object has a function \texttt{watch(propName, callback)}
-which receives two parameters, a property name and a function.  Whenever
-the property with the given name changes, the \texttt{callback} function is
-called. The hook set by this function remains enabled even if the
-property is deleted and defined again.
-
-For our purposes, the \texttt{watch()} function only covers the case
-of global object properties. At the beginning of execution, no object
-excepting the global object and its predefined properties is available.  For 
-our \textit{lastChange} prototype, we created a version of
-\texttt{setPropertyChangeHook()}.  The basic strategy is to get a reference to the object just
-after its creation, then use \texttt{watch()} function to monitor
-property changes in the object. Setting a flag\footnote[3]{DISABLE\_OBJECT\_TRACE defined in jsdIDebuggerService.idl} into the Firefox 
-JavaScript engine, we can get the file URL and the line number for each object
-creation (e.g., myFile.js, line 24). We set a breakpoint on this line
-and parse the source code to determine which object was created.
-
-The only data we have is the object creation location including the
-file url and the line number and the goal is to get a reference to
-this object. Although in most regular cases we have only one
-statement and one object creation, there are cases where more
-objects are created in the line. There is no simple way to
-recognize the interesting object among these new objects. So instead
-of one object, we monitor all new objects created in the line.
-
-An object might be created by one of these statements: object
-literal(\texttt{\{...\}}), \textit{new} operator (\texttt{new 
-constructor()}) or function definition statement (\texttt{function()}). 
-By parsing the source code we can recognize the statements that
-create an object. The next step is getting a reference to the new object.
-
-The new object can be assigned to an object property or a variable by
-an assignment (\texttt{=}). In these cases we keep the assignee statement 
-at the left side. The idea is that we create a list of assignee statements 
-that the new objects are assigned to. We set a hook on the creation
-line. Once the hook hits, we evaluate the assignee statements. Then 
-we do stepping(step-over) and after each step we evaluate the
-statements. Every statement which has a new value, we consider the new
-value (if it is an object) as a new object. For example in Figure
-~\ref{fig:objectCreation}(a), if the creation line number is 20, we
-have only one statement which creates a new object and it is assigned
-to \texttt{x.y}.
-
-The new object can also be set as the property of a parent object 
-(or array) inside an object (or array) literal. This case is also treated 
-similar to previous case. The only difference is that the full path of property 
-from the root parent in the local scope must be considered as the assignee statement. For
-example in Figure~\ref{fig:objectCreation}(b), if the creation line
-is 20, we keep \texttt{parent.child}. In this case stepping
-must be continued until the end of the object literal (line 22) for getting a reference
-to the created new object.
-
-In cases where the new object is passed as an 
-argument to a function (Figure~\ref{fig:objectCreation}(c)), we use step-in instead of step-over. 
-To get a reference to the new object
-it is enough to evaluate the corresponding argument inside the function. The other cases
-where the program does not keep a reference to the created object (e.g., when a function object is
-just called after its creation), are not in our interest.
-
-%(or \texttt{this} if the object is being constructed by \texttt{new} statement)
-
-Although this approach is successful in many ordinary cases, we can imagine 
-cases where a more comprehensive analysis needed for the correct behaviour. 
-Consider the case where the new object is assigned to an expression like \texttt{a[++i]}. 
-% (where i is a variable). 
-%This expression is kept in the list                      %(Figure~\ref{fig:objectCreation}(d))
-%of assignee statements to be evaluated later for getting a reference to the new object. 
-Obviously, evaluating this statement doesn't return
-a reference to the new object. Our prototype implementation does not handle these kinds of unusual cases yet.
-
-Throughout this section we implicitly assumed that the object will be created at 
-the same location in the next execution. If the assumption is
-not true, once the execution reaches the reproduction point, it
-reveals that the object has been created in a different location. This time,
-prototype re-executes the program considering both locations as possible 
-object creation locations.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang]% framerule=0pt]
-
-(a) Case 1:
- 20  x.y = new MyClass();
-
-(b) Case 2:
- 19  parent = {
- 20    child : {
- 21      x : 5
- 22  }}
-
-(c) Case 3:
- 20  myFunction({myProperty:5});
-
-\end{lstlisting}
-
-%(d) Case 4:
-% 20 a[++i] = new myConstructor();
-
-%\end{verbatim}
-\caption{Examples of different cases in getting references to created JavaScript objects.}
-\label{fig:objectCreation}
-\end{figure}
-
-\subsection{{\normalsize\bf\texttt{scopeId()}} Operation}
-The prototype sets a breakpoint at the beginning of all code blocks needing
-a scope id. The scope id is kept as a variable with name 
-\texttt{\_scopeId} in the scope. Whenever the hook is hit,  meaning a new scope
-is created, \texttt{\_scopeId} is set by calling JavaScript's dynamic compilation 
-function \texttt{eval()}. For example, executing \texttt{eval("var \_scopeId = 10")} creates a
-variable with name \texttt{\_scopeId} and value \texttt{10} in the
-scope of the \texttt{eval()} call, which is our interesting scope. \texttt{scopeId()}
-operation returns the value of \texttt{\_scopeId} in the scope.
-
-\subsection{{\normalsize\bf\texttt{setVariableChangeHook()}} Operation}
-Variables defined in local, closure, and catch scopes are only changed in
-their scope; that includes the defining scope and scopes nested whithin them.
-For example in Figure~\ref{fig:js-closure}, variable \texttt{foo} in line 11 can only be
-changed in lines 10 to 23. Therefore, after locating the function in
-which the variable is defined, it is enough to parse the code inside
-the function block and set a hook on all lines where the variable is
-assigned a new value. 
-We also set a hook at the first line of the function which is
-corresponding to the line where the variable is defined. In Figure~\ref{fig:js-closure}, 
-if the execution is paused at line 17 and the
-last change of \texttt{foo} is queried, two hooks on lines 16 and 17
-will be set, but if the execution is paused at line 20 , four hooks on
-lines 11, 12, 14, 20 will be set. These two cases are different: \texttt{foo} in 
-\texttt{childOne} is a local variable
-but in \texttt{childTwo} it is a closure variable.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang]%, framerule=0pt]
-
-10  function main(){
-11    var foo;
-12    foo = ...;
-13    function parent(){
-14      foo = ...;
-15      function childOne(){
-16        var foo;
-17        foo = ...;
-18      }  
-19      function childTwo(){
-20        foo = ...;			      
-21      }
-22    }  
-23  }    
-\end{lstlisting}
-%\end{verbatim}
-\caption{Sample JavaScript code demonstrating local and closure variables.}
-\label{fig:js-closure}
-\end{figure}
-
-\subsection{Re-Execution, Reproduction Point and Data Collection}
+%The
+%first one is the breakpoint on line 22, the second one is the point
+%which is when \texttt{myObject.myProperty} changed before
+%reaching the breakpoint and finally the last one is the point of
+%execution in which \texttt{myCondition.value} gets the
+%\texttt{undefined} value.
+
+%Notice that in our example, \textit{lastChange} combines some aspects
+%of breakpoint and of log-based debugging. Like breakpoint debugging,
+%the developer re-executes a live runtime without changing the source
+%and without a special execution environment beyond the debugger. The
+%state of the program memory and the call stack are available at each
+%lastChange point. Like log-based debugging, the program state and the
+%call stack are recorded during program execution. We can't halt the
+%program at \textit{lastChange} because we don't know which point is the last
+%one until we return to the original breakpoint. 
+%In section 5 we discuss cases where it is possible to pause at lines of \textit{lastChange}.
+
 \textit{Querypoint} needs a test case to reproduce the
@@
 if the developer queries \textit{lastChange} at the third hit of breakpoint \textit{b}, in
-re-execution, the third hit is recognized as the reproduction point.
-
-The \textit{Querypoint} prototype supports two mechanism
+re-execution, the third hit is recognized as the reproduction point. \textit{Querypoint} supports two mechanism
 for automatic re-execution: callstack-reproduction and record-replay. In callstack reproduction the function from
-the earliest frame of the call stack is called with the same parameters. The idea
-behind this mechanism is that many bugs in web pages can be reproduced by re-firing
-an event like clicking on a button. The record-replay execution uses two phases. In the record phase, it 
+the earliest frame of the call stack is called with the same parameters. The record-replay execution uses two phases. In the record phase, it 
 stores the initial page url and the events and parameters corresponding to user actions. In the replay phase, it opens
-the same url and simulates events as if they were user actions. The callstack reproduction mechanism provides
-shorter re-execution cycles while the record-replay is more accurate about the
-initial state.
+the same url and simulates events as if they were user actions.
 
@@
 There is a trade-off between the amount of data collected at every change event and the number of re-executions.
-If developer asks for
-some values which have not been stored, \textit{Querypoint} re-executes and collects the requested data.
-
-% Discuss what happens when assumptions changes, like object creation location.
-
-\section{Reproducible Non-Deterministic Execution}
-We claim that the only prerequisite for \textit{lastChange}  is bug-reproducibility. 
-A bug is \textit{reproducible} for a developer when the developer can
-start from a given initial state, operate on the program with a
-list of actions, and reproduce the symptoms of the bug. The details of
-the execution can change each time we re-execute the buggy program,
-but the buggy result is the same.  All modern debuggers in wide use that we know 
-about rely on reproducible but non-deterministic execution for simple practical reasons: 
-developers must reproduce a bug to study it and modern execution environments 
-are not deterministic.  
-% In this section we discuss non-determinism and \textit{lastChange}. However we want 
-%to emphasize that when developers have to think about non-determistic execution 
-%it usually means that bugs are not reproducible. 
-%The reproducibility of the bug
-%means that the defect is very unlikely to depend on the order of
-%events during the execution. Conversely, if the defect depends on the order of execution, 
-%it will likely fail to reproduce on some executions. 
-By relying on reproducibility but 
-not requiring deterministic execution, \textit{lastChange} works on the same range of cases.
-
-\subsection{{\large\bf\textit{lastChange}} Result Consistency}
-\label{sec:resultConsistency}
-
-Each time we re-execute a non-deterministic program, 
-the details of execution instruction order may change. 
-For example, if we record the source code lines every time
-a conventional watchpoint hits, the record may differ each time we
-re-execute. But \textit{lastChange} does not compare values across 
-executions. Rather it analyzes all of the
-change events in a single execution. 
-Neither the data gathering nor the analysis require deterministic execution.
-
-Since we don't need to compare values across executions to implement \textit{lastChange}, we can get more information if we do compare:
- different points of last change on different executions will signal that the execution is not deterministic. Note the converse is not true, many non-deterministic 
-programs will give identical results for \textit{lastChange}.
-Consider the example in Figure~\ref{fig:nondeterministic-values}. 
-Assume that at the first execution, the developer sees that the \texttt{a} value is \texttt{true} and asks
-for the \textit{lastChange} of \texttt{a} at the breakpoint. In the re-execution, \texttt{a} is \texttt{false},
-and \texttt{b} is \texttt{true} at the reproduction point. It means that \texttt{lastChange}
-result shows line 10, which is a correct answer for this execution but not for the previous one.
-When user asks for the \textit{lastChange} on variable \texttt{a}, debugger stores \texttt{a} value and compares
-it to the \texttt{a} value in the next executions. So if this value is different, debugger informs the developer
-that the \textit{lastChange} query is made on a different value.
-% In cases that the value is not a primitive but an object,
-%the primitive properties of the object examined by the developer are stored and compared.
-
-\begin{figure}[htp]
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang]%, framerule=0pt]
-
-10 a = b = false;
-20 if (random()) {a = true;} else {b = true;}
-30 if (a || b) {bug(); /* breakpoint */}
-\end{lstlisting}
-%\end{verbatim}
-\caption{\textit{lastChange} on non-deterministic values.}
-\label{fig:nondeterministic-values}
-\end{figure}
-
-\subsection{Combination of {\large\bf\textit{lastChange}} and Breakpoint Debugging}
-\label{sec:pausing}
-Using \textit{lastChange} a developer can work backwards on the flow of data, but sometimes bugs are more obvious when
-we watch control flow forwards. Consider for example,
-
-%\begin{verbatim}
-\lstset{basicstyle=\scriptsize}
-\begin{lstlisting}[frame=single, language=myLang] % framerule=0pt]
-
-44 vector.r = Math.floor(Math.random()*5)*6;
-45 if (vector.r !== 0 && vector.r < 30);
-46   return vector;
-\end{lstlisting}
-%\end{verbatim}
-where \textit{lastChange} shows us that \texttt{vector.r} is zero at line 44. In our user studies, developers
-wanted to single step forward from line 44. If they could do this, they may be surprised to see line 46 execute 
-even if \texttt{vector.r} is zero, directing their attention to line 45 where they can discover the errant semicolon.
-However, a \textit{lastChange} is just a query result, not a breakpoint. Under what conditions can we 
-cause the debugger to stop at the \textit{lastChange} point?
-
-In the case that the execution is deterministic, the \textit{last-\ Change}
-event index can be used as an index for a conditional breakpoint \cite{Boothe, Maruyama}. 
-Moreover, this works in a non-deterministic execution if non-determinism
-has no effect on the event index.  The debugger can easily set this conditional breakpoint
-and reexecute the program. If the stream of change events differs in this re-execution the
-developer can be warned that the conditional breakpoint may not be the \textit{lastChange} point.
-However, if the stream of events is the same, we do not know that the 
-conditional breakpoint matches the last 
-change, this fact can only be verified at the reproduction point. These theoretical concerns are not
-likely to cause significant practical problems: if the value at the conditional breakpoint is not suspicious, 
-then the developer will know to simply return to \textit{lastChange} or move on to another tactic to find the bug.
-
-% Cut to reduce size
-%There are cases where event indexes fail, but a developer can use knowledge gained from \textit{lastChange}
-%to formulate a conditional breakpoint.
-%Consider the example in Figure~\ref{fig:counter-example}. It shows a function which processes an
-%array. The array contains numbers except one item which is
-%\texttt{undefined} and it causes a bug in line 30. There is a call to
-%\texttt{randomPermutation} function in line 11 which randomly
-%permutes the array item. So at every execution the
-%\texttt{undefined} item will be in a new place. Calling
-%\textit{lastChange} on \texttt{x} at the place the bug happens, gives a
-%point which shows line 14. Although this point exists at every
-%re-execution but it can not be identified by an event index. A conditional breakpoint on 
-%the value of the item would succeed and the developer can reason from the 
-%textit{lastChange} results to create the condition.
-
-%\begin{figure}[htp]
-%\lstset{basicstyle=\scriptsize}
-%\begin{lstlisting}[language=myLang, framerule=0pt]
-%10 function randomProcess(array){
-%11   randomPermutation(array);
-%12   var x, y;
-%13   for (var i=0 ; i<array.length ; i++){
-%14      x = array[i]
-%...
-%30      y = x+1;
-%31   }
-%32 }
-%\end{lstlisting}
-%\caption{A counter-example for transforming \textit{lastChange} to a conditional breakpoint.}
-%\label{fig:counter-example}
-%\end{figure}
+If the developer asks for some values which have not been stored, \textit{Querypoint} re-executes and collects the requested data.
 
 \section{User Study}
-We supplied four experienced Javascript developers with our prototype in an 
-extended Firebug debugger\footnote[4]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
-applied both conventional breakpoint and \textit{lastChange} on two small programs we 
-provided (Our prototype did not have a user interface to support Sec.~\ref{sec:pausing}).
+We supplied four experienced Javascript developers with \textit{Querypoint} in an 
+extended Firebug debugger\footnote[1]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
+applied both conventional breakpoint and \textit{lastChange} on two small programs we provided.
 The first program, Shapes, calculates the area and perimeter values for a list of shapes.
@@
 The second program, Moving Circle, randomly scales and moves a circle in the page.
-The bug happens once the circle becomes invisible after an exception
-occurs.
+The bug happens once the circle becomes invisible after an exception occurs.
 This case represent a reproducible non-deterministic execution.
 The developers were asked to locate the defects that caused these bugs.
-All four developers successfully applied \textit{lastChange} to the test programs
-and understood how it could help debugging.
-
-To find the defect location with breakpoints, all four users took more steps and more time (Figure~\ref{fig:userstudy}).  
-Two users scrolled through the source, 
-another searched the text, a third set a lot of breakpoints to understand the control flow. 
-Based on our own experience we expect these strategies represent the kinds of approaches 
-developers have available. These operations are time consuming and tedious. In contrast, all four users 
-found the defect location with just two \textit{lastChange} operations.
+All four developers successfully applied \textit{lastChange} to the test programs and understood how it could help debugging.
+To find the defect location with breakpoints, all four users took more steps\footnote[2]{A step is a button push, either single stepping the debugger or running a lastChange query} and more time (Figure~\ref{fig:userstudy}).
+
+%another searched the text, a third set a lot of breakpoints to understand the control flow. 
+%Based on our own experience we expect these strategies represent the kinds of approaches 
+%developers have available. These operations are time consuming and tedious. In contrast, all four users 
+%found the defect location with just two \textit{lastChange} operations.
+
 % Based on our measurements,
@@
 %the reproduction point to the defect
-We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
-issues have been hidden by the design of our tests. Nevertheless our results show that, when a defect 
-relates to incorrect values and a developer recognizes this, then the operational 
-mechanics of lastChange lead to the defect much more quickly than breakpoints.
-
-Our observation and discussions with users also brought out several important issues and improvements
-for our user interface. Perhaps the most important and challenging improvement would be better integration 
-with breakpoint debugging. Our implementation put the results of \textit{lastChange} in a similar but different
-view from breakpoint debugging. This focuses attention on value changes, but it makes studying control 
-flow more difficult: we don't support single stepping from a \textit{lastChange} result in our user interface. In our next iteration we 
-plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
+%We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
+%issues have been hidden by the design of our tests. Nevertheless our results show that, when a defect 
+%relates to incorrect values and a developer recognizes this, then the operational 
+%mechanics of lastChange lead to the defect much more quickly than breakpoints.
 
@@
 
-\section{Discussion}
-
-We have presented the \textit{lastChange} algorithm and described our
-prototype implementation. Our goal is practical improvements in debugging. To achieve our goal we need practical JavaScript engines
-to add new debug primitives so that developers in the field can use our new technique. This paper is
-one step to convince implementers to enable \textit{lastChange}.
-Thus we summarize here our arguments that \textit{lastChange} should be supported.
-
-%The key ingredients in our argument are: 
-%\begin{enumerate}
-%   \item developers need an operation like \textit{lastChange}, 
-%   \item developers can learn to use \textit{lastChange}, 
-%   \item practical implementations are feasible with modest
-%invested development time,
-%   \item in most cases \textit{lastChange} will be much faster than current alternatives,
-%   \item the worst cases are not more common or more painful than
-%alternatives.
-%	 \item the \textit{lastChange} approach can be generalized to other queries.
-%\end{enumerate}
-
-%TODOWe have also developed a prototype implementation of the debugger control part of lastChange for Java.
-The main differences (one or two sentences).
-We will report on this implementation in a later publication
-\subsection{Developers need an operation like \protect{\large\bf\textit{last- Change}} }
-
-%We have shown how \textit{lastChange} identifies the prior point in
-%program execution where a program state value changes. Is it something
-%the developer needs to do?
-
-Since ultimately programs are just
-transformation of state values, debugging is ultimately backtracking
-to find defects in program state change\cite{Weiser,Zeller}.  When a developer halts a
-program on a breakpoint they compare the call stack and program state to their model of the program.
-If any value seems to be incorrect,  they need to figure out what operation
-causes the incorrect value. Here \textit{lastChange} takes over and addresses a key
-part of the debugging process.
-%have three kinds of information: a model
-%of the program in their mind, a call stack showing what part of the
-%program is halted, and the state at that point (a combination of the
-%debugger's view of the program internal state and the output of the
-%program up to this point of execution). If the model does not match
-%the call stack or if no value in the viewable program state aligns
-%with the developers model for this point in execution, the developer
-%will seek another view by changing the breakpoint or the input
-%data. If a value appears incorrect, they may have a flash of insight
-%and know the defect. Otherwise they need to figure out what operation
-%causes the incorrect value. Here \textit{lastChange} takes over and addresses a key
-%part of the debugging process.
-
-\subsection{Developers can learn to use \protect{\large\bf\textit{lastChange}}}
-
-%If \texttt{lastChange} could be useful, can developers figure out how
-%to use it? 
-While our user study was small, our prototype demonstrates that
-\textit{lastChange} can be easily activated by operations on the
-graphical representation of erroneous data in a debugger and the 
-results can be interpreted by users. 
-While \textit{lastChange} is not a breakpoint, 
-all of the assumptions developers already have for breakpoints hold
-for \textit{lastChange}. In particular the re-execution is just the
-same operation developers use to debug with breakpoints.
-
-%We designed the
-%user interface for the results from \textit{lastChange} to resemble
-%the results from a breakpoint, with the source code of the change
-%point highlighted and the state of the program presented the way state
-%is presented from a breakpoint. Based on this user interface, we
-%believe developers can start to use \textit{lastChange} with minimal
-%training. Our users may not be representative, but the key point here
-%is that the learning curve is small compared with the challenge of learning 
-%breakpoint debugging in the first place.
-
-%In our own experience, \textit{lastChange} dramatically reduces the work in
-%setting and removing breakpoints, so work to cause re-execution  become noticeable.
-%Therefore automatic mechanisms
-%for re-execution will be corresponding more valuable for debugging
-%with \textit{lastChange} (Our \textit{Querypoint} prototype  
-%implements a simple form of automatic 
-%re-execution for both breakpoint and \textit{lastChange}).
-
-\subsection{Practical implementations are feasible}
-
-We have described our prototype all-JavaScript implementation in Sec. 4. It is adequate for 
-exploring the ideas and may even be usable in production. However significant 
-improvments can be made. A fully usable
-implementation would require access to the object id at the point of
-object creation and \texttt{setPropertyChangeHook()}. Many
-object-oriented runtimes provide object identifiers and 
-provide access to object creation directly or by bytecode instrumentation\cite{JPDA}. 
-%In the particular case of the Firefox Web browser we used for our prototype, the primary barrier
-%to practical implementation would likely be integration with the
-%increasingly sophisticated just in time compilers. In the case of
-%tracking variable changes, \texttt{setVariableChangeHook()} can be implemented
-%similar to \texttt{setPropertyChangeHook()} if JavaScript scopes-like regular 
-%JavaScript objects-support \texttt{watch()} function.
-
-\subsection{In most cases \protect{\large\bf\textit{lastChange}} will be much faster than current alternatives}
-
-%When developers try \textit{lastChange}, will they get results fast
-%enough to benefit? While we only used our prototype on toy programs,
-%\textit{lastChange} seemed as fast as breakpoint re-execution.
-%But what can we say about realistic programs?
-
-Recall that we
-insert additional code through debugger callbacks, then re-execute the
-program. The additional code we insert is proportional (in our
-JavaScript algorithm) to 1) the number of places a property or
-variable with a given name is changed, 2) the number of places objects
-are created. The overhead for each execution at a change event
- depends upon the amount of data we store for each change event; 
-the overhead for object creation could be small since we only need to 
-determine if the object is one we need to watch.
-
-%We implemented a
-%simple and effective mechanism allowing developers to control 
-%overhead: we stored data to a depth of two property accesses 
-%(e.g. foo.bar.x), then placed a \textit{re-run} button 
-%in the user interface at the third level. If developers reached the 
-%third level they can see more data at the cost of one more replay.
-
-For comparison consider today's practical alternative: developers
-setting breakpoints. For the vast majority of programs, a developer
-will take much more time to set one breakpoint than
-\textit{lastChange} would add. Moreover, typically the developer may not
-guess the point of last change. They must then ponder another
-breakpoint and re-execute.
-
-%Unlike the re-execution we use to 
-%optimize performance in \textit{lastChange}, 
-%developers still will not know if the breakpoint they hit is the point of last change
- %or even if it is related to the change at all.
-
-We could also compare to solutions based on logging or tracing. Manual
-logging has very high overhead: the developer must add code, debug
-that added code, then analyze the log (To be fair, the log can become
-a permanent debugging aid). Automatic logging as we discuss in 
-section \ref{sec:relatedWork} causes about one or two orders of magnitude slow down as well
-as requiring a completely different set of development tools.
-
-\subsection{The worst cases are not more common or more painful than alternatives}
-
-%Finally we consider the worst cases: what about code that changes
-%objects in long running loops? 
-Every time through the loop we incur
-the call back overhead; if the loop itself has relatively little code
-the overhead could be very large; if the loop computation is a
-significant fraction of the full program, the slowdown would be
-enormous. 
-Other techniques also struggle with this case:  breakpoints in highly repeating loops are not feasible and logging
-becomes unwieldy. 
-Developers face this issue with any debugger today: occasionally a
-debugger causes too much overhead to be useful for debugging. 
-%Since automatic logging solutions are highly tuned,
-%their overhead in this case will likely be much less than
-%\textit{lastChange}. On the other hand, \textit{lastChange} integrates
-%with an interactive debugger and detecting that we are in a high
-%overhead loop is simply a matter of checking our internal counter. %
-%In
-%such unusual cases we may simply offer the developer the option of
-%studying the loop code then omitting it from \textit{lastChange}
-%operations. 
-%
-%The users of \textit{lastChange} may encounter these kinds of cases, but 
-%that is the nature of debugging: you need different tools for 
-%different kinds of problems.
-
-\subsection{Generalizations}
-Our \textit{lastChange} algorithm can be viewed as a particular interface to a general facility. 
-The general facility replays execution, queries the runtime at points of interest during execution,
-and analyzes the result at the reproduction point. We have selected one kind of query and analysis
-that can be easily integrated in existing debuggers and explained to developers, providing automation of 
-the problem of finding the point of last change. We believe other
-kinds of queries and analysis can be invented and integrated to automate other aspects of debugging.
-%Moreover, the query history analysis used to test for non-determinism here may also be the basis for
-%more effective user interfaces to debugging sessions. The series of cascaded \textit{lastChange} queries becomes 
-%logical path followed by the developer seeking the defect and this path may be useful if presented in effective user interfaces.
-
-\section{Related Work}
-\label{sec:relatedWork}
-%The algorithm we presented in this paper obtain information about
-%the execution state logically earlier in the control flow by querying 
-%the executioin state during replay using the technology of 
-%conventional breakpoint debuggers.  
-The \textit{lastChange} approach resembles the operational model of replay-based debugging 
-and the query approach of logging-based
-debugging.  Replay-based approaches capture limited data during
-execution and replay the buggy execution to reach past points. In
-contrast, logging-based approaches collect enough data during
-execution to relieve developer from re-execution, then query the data to 
-inform the developer. Replay-based
-approaches impose much less runtime overhead (about two orders of
-magnitudes) comparing to logging-based approaches. However, developer
-has to re-execute the buggy execution several
-times. \textit{lastChange} collects data on re-execution by queries
-selected by developer interaction with the debugger. Therefore it has 
-the selectivity of the replay-based approaches that improves performance, 
-% but we have 
-and the flexibilty of the queries so it does not require deterministic replay.
-
-Among replay-based debuggers we compare to bdb \cite{Boothe} and
-reverse watchpoint \cite{Maruyama}.  A bidirectional C debugger, bdb
-employs a step counter to locate the requested point from the
-beginning of execution. It relies on deterministic execution replay
-%(i.e., the same sequence of instructions in re-execution) 
-and records the results of non-deterministic system calls and re-injects them into
-the program when it is replayed. It makes use of checkpoints to reduce
-the time needed for re-execution. Reverse watchpoint, similar to bdb, uses
-a counter to correctly locate the last write access of a selected variable in the
-next execution \cite{Maruyama}.
-% Reverse watchpoint is proposed by Maruyama et al., analyses the execution and moves the debugger to the
-% last write access of a selected variable by re-executing the program
-%from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
-%replay and uses a counter to correctly locate a point in the next
-%execution. 
-The main disadvantage of these approaches is that they require 
-identical, instruction by instruction, re-executions. % exactly the same executions. 
-Even one instruction difference between
-two executions leads to wrong results. On the other hand,
-\textit{lastChange} doesn't require any special feature in the
-re-execution and fits into existing debugging practice
-
-Among logging-based approaches are \textit{omniscient} debuggers
-ODB\cite{Lewis} and Unstuck\cite{Hofer}. Both
-approaches keep the log history in memory and hence can only record
-and store the complete history for a short period of time. These
-debuggers record all the events that occur during the buggy execution
-and later let the developer to navigate through the obtained execution
-log. In these approaches there is no execution to resume: moving
-backwards in the log can be similar to moving forwards. A more scalable 
-approach to omniscient debugging has been proposed by Pothier et al. \cite{Pothier}. 
-Their back-in-time debugger, TOD, addresses the space problem by storing 
-execution events in a distributed database. Bhansali et al. \cite{Bhansali} attempted to address the performance overhead 
-and large trace size of logging-based debugging in their time-travelling debugger, Nirvana. 
-Nirvana first collects a full compressed trace of program execution and then 
-simulates re-execution. Their results are quite similar to omniscient 
-debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
-re-simulation.
-
-Logging-based debuggers suffer from different issues. First, the recording
-step is time expensive and it should be repeated in case of changes in
-program. Second, the execution log cannot fully replace the live
-execution. There are other aspects of execution (e.g., program user
-interface, file system, database tables, etc.) which are also
-important in debugging and are not available to the developer in
-omniscient debuggers. Third, querying collected data (e.g., to restore
-the program state at a certain point) may not be efficient enough for
-debugging realistic programs. Comparing to logging-based debuggers our approach is 
-has little upfront cost and more flexibility. The developer can start debugging just 
-after reproducing bug without a capturing step.  Changing inputs or
-environment settings and re-executing to investigate the bug works as
-in conventional breakpoint debuggers.
-
-Program slicing\cite{Weiser} approaches debugging from a completely different perspective.
-Given a point of interest {\bf S} in a program, a \textit{slice} is an executable subset of the program affecting {\bf S}.
-Many studies have shown ways to compute the slice more quickly or to constrain the slice to a smaller subset of the program \cite{Horwitz, Sridharan}.
-Dynamic slicing \cite{Korel} applies slicing analysis at run time and thus most closely resembles \textit{lastChange} from among the slicing approaches.
-Our \textit{lastChange} approach can be related this way: first, allow the developer to select from {\bf S} a key critical value {\bf V}.
-Then compute a slice affecting {\bf V}.
-Show the developer only the most relevant part of that slice (the \textit{lastChange}).
-Finally iterate towards the fault by chaining new slice-selection criteria.
-
-Both approaches rely on selecting {\bf S}.
-Both approaches differ from breakpoint debugging in analyzing a program from a known good point (e.g.
-start of the program) to {\bf S}.
-Slicing reduces the space the developer needs to search, but provides no guidance within the slice; \textit{lastChange} explores the slice using developer-selected search criteria, but does not help the developer recognize code that cannot impact {\bf S}.
-Slicing requires a sophisticated compiler-like technology while \textit{lastChange} builds on familiar run-time debugger technology.
-
-A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
-machine level support for keeping the history of events. It replaces every
-object reference with an alias object which keeps the history of
-changes to the object reference. 
-%In this way, when an object is
-%collected by garbage collector, its track of changes (if it is not
-%referenced by other aliases) will be also collected. 
-Although this approach incurs less runtime overhead (7 times) in
-comparison to omniscient debuggers, it adds memory
-overhead.
-
-Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
-Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
-First, it is limited to \texttt{undefined} and \texttt{null} values. Second, it does not return the last change
-of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
-
-%Two new directions in logging debuggers explore more detailed use of
-%the log and more effective user interface to the collected data. %logging approaches. 
-%WhyLine\cite{Ko} provides visual interface to collected runtime information and lets
-%developer moves on execution log using queries expressed in terms of
-%the programming objects.
-
-WhyLine\cite{Ko} stores the program user interface in
-addition to the program trace and provides answers to why and why not
-questions to the user. 
-%Jive\cite{Czyz} depicts the history of
-%execution by a sequence diagram and lets the user to query on the events
-%database. 
-WhyLine suffers from the requirement of gathering tracing information before its unique capabilities can be used.
-We imagine that the runtime queries we use in \textit{lastChange} may be used to gather data incrementally for this kind of debugging approach.
-
-%Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
-Moreover, the Lienhard et al.
-debugger significantly changes the virtual machine, while our approach is a generalization to conditional breakpoints and available debugger infrastructure can be adapted to support it.
-
-%\textit{lastChange} functionality does rely on a conventional breakpoint to begin queries, a requirement not shared by full logging solutions.
-Here we leverage past experience of developers, but there are also new tools [] to help with this problem in the case of graphical and event based systems.
-
-\section{Conclusion}
-\textit{lastChange} provides critical information for debugging programs: the location and state at the point where a questionable value was assigned.
-It builds upon existing technology and developer experience making it a practical solution for implementers.
-Our prototype demonstrates the feasibility of \textit{lastChange} and its user interface hints at the potential this approach can have in organizing the debugging experience.
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-The authors thank Leo Meyerovich for reading a draft of this paper and suggesting the example in section \ref{sec:resultConsistency} and
-Jan Odvarko and Mike Collins for testing the prototype before our user study and providing helpful suggestions.
+\section{Conclusion and Future Work}
+\textit{Querypoint} provides critical information for debugging Jav- aScript programs: 
+the location and state at the point where a questionable value was assigned. It only requires 
+bug reproducibility and is built on the existing breakpoint technology.
+
+In our next iteration we plan to merge the query and breakpoint results. \textit{Querypoint} shows the 
+results of \textit{lastChange} in a similar but different view from breakpoint debugging. This focuses attention 
+on value changes, but it makes studying control flow more difficult. %: we don't support single stepping from a \textit{lastChange} result in our user interface.
+
+% In our next iteration we plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
 
@@
 
-\bibitem{Barton}
-J.J. Barton, and J. Odvarko. \newblock Dynamic and graphical web page breakpoints.
-\newblock In \emph{Conference on World Wide Web(WWW)},
-April, 2010.
+%\bibitem{Barton}
+%J.J. Barton, and J. Odvarko. \newblock Dynamic and graphical web page breakpoints.
+%\newblock In \emph{Conference on World Wide Web(WWW)},
+%April, 2010.
 
@@
 
-\bibitem{Horwitz}%[Hofer(2006)]
-S. Horwitz, B. Liblit, and M. Polishchuk. \newblock Better Debugging via Output Tracing and Callstack-Sensitive Slicing.
-\emph{IEEE Transactions on
-Software Engineering}, 36(1):7-19, 2010.
-
-\bibitem{JPDA}%[JSD(2010)]
-Java Platform Debugger Architecture. \newblock http://java.sun.com/javase/technologies/ core/toolsapis/jpda.
+%\bibitem{Horwitz}%[Hofer(2006)]
+%S. Horwitz, B. Liblit, and M. Polishchuk. \newblock Better Debugging via Output Tracing and Callstack-Sensitive Slicing.
+%\emph{IEEE Transactions on
+%Software Engineering}, 36(1):7-19, 2010.
+
+%\bibitem{JPDA}%[JSD(2010)]
+%Java Platform Debugger Architecture. \newblock http://java.sun.com/javase/technologies/ core/toolsapis/jpda.
 
@@
 
-\bibitem{Korel}%[Ko(2008)]
-B. Korel and J. Laski. \newblock Dynamic Program Slicing.
-\newblock \emph{Information Processing Letters},
- 29(3):155-163, 1988.
+%\bibitem{Korel}%[Ko(2008)]
+%B. Korel and J. Laski. \newblock Dynamic Program Slicing.
+%\newblock \emph{Information Processing Letters},
+% 29(3):155-163, 1988.
 
@@
 
-\bibitem{Lienhard}%[Lienhard(2008)]
-A. Lienhard, T. G\^{\i}rba, and O. Nierstrasz. \newblock Practical Object-Oriented Back-in-Time Debugging.
-\newblock In \emph{22nd European conference on Object-Oriented Programming(ECOOP)},
-July, 2008.
+%\bibitem{Lienhard}%[Lienhard(2008)]
+%A. Lienhard, T. G\^{\i}rba, and O. Nierstrasz. \newblock Practical Object-Oriented Back-in-Time Debugging.
+%\newblock In \emph{22nd European conference on Object-Oriented Programming(ECOOP)},
+%July, 2008.
 
@@
 
-\bibitem{JSD}%[JSD(2010)]
-Mozila JavaScript Debugging Interface. \newblock http://www.mozilla.org/js/jsd.
+\bibitem{Mirghasemi2011}
+S. Mirghasemi, J.J. Barton, and C. Petitpierre. \newblock Debugging by lastChange.
+\newblock Technical Report. EPFL-REPORT-164250, 2011. 
+%\bibitem{JSD}%[JSD(2010)]
+%Mozila JavaScript Debugging Interface. \newblock http://www.mozilla.org/js/jsd.
 
@@
 
-\bibitem{Sridharan}%[Boothe(2000)]
-M. Sridharan, S.J. Fink , and R. Bodik. \newblock Thin slicing.
-\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
-June, 2007.
-
-\bibitem{Weiser}
-M. Weiser. \newblock Program slicing.
-\newblock \emph{IEEE Transactions on
-Software Engineering}, vol. SE-10, no. 4, pp. 352-357,
-July 1984.
-
-\bibitem{Zeller}
-A. Zeller. \newblock Why programs fail: A guide to systematic debugging.
-Morgan Kaufmann (2005)
+%\bibitem{Sridharan}%[Boothe(2000)]
+%M. Sridharan, S.J. Fink , and R. Bodik. \newblock Thin slicing.
+%\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
+%June, 2007.
+
+%\bibitem{Weiser}
+%M. Weiser. \newblock Program slicing.
+%\newblock \emph{IEEE Transactions on
+%Software Engineering}, vol. SE-10, no. 4, pp. 352-357,
+%July 1984.
+
+%\bibitem{Zeller}
+%A. Zeller. \newblock Why programs fail: A guide to systematic debugging.
+%Morgan Kaufmann (2005)
 

### 2011-06-08 papers/fse-tool2011/sig-alternate.tex

@@
 %
+
+\appendix
+\section{Presentation}
+The presentation will include the follwing parts:
+\begin{enumerate}
+	\item A short demo, debugging a simple buggy web page by the tool.
+	\item A brief explanation of \textit{lastChange} algorithm.
+	\item A brief explanation on \textit{Querypoint} debugging as a general debugging approach.
+	\item Discussion about non-deterministic reproducible executions.
+	\item A comprehensive demo on the Tool features.
+\end{enumerate}
+
+\section{Tool Maturity}
+The tool is functional, however this is the first version of \textit{Querypoint} and therefore it is 
+not mature enough to be used by developers working in industry.
+
+\section{Resources}
+The tool and its source code are publicly available and can be downloaded 
+from \textit{Querypoint Debugging} web site at this address:
+
+\mbox{\href{http://code.google.com/p/querypoint-debugging}{http://code.google.com/p/querypoint-debugging}}
+
+The details of our user study, including the instructions and test cases source code, are available at this address:
+
+\mbox{\href{http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy}{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}}
+
 \end{document}

### 2011-06-09 trunk/papers/fse-tool2011/sig-alternate.tex

@@
 wrong value executed before the wrong value appeared. Searching with
-breakpoint- or log- based debuggers demands persistence and significant experience with the application being debugged.
+breakpoint- or log- based debuggers demands persistence and significant 
+experience with the application being debugged.
 
-\textit{Querypoint}, is a Firefox plugin which enhances the popular Firebug JavaScript debugger with
- a new, practical feature called \textit{lastChange}, which automatically locates the last point that a variable 
-or an object property has been changed. Starting from a program halted on a breakpoint, the \textit{lastChange} solution
-applies queries to the live program during re-execution, recording the call stack and limited program state each time 
-the property value changes. When the program halts again on the breakpoint, the recorded information can be shown to the developer.
+\textit{Querypoint}, is a Firefox plugin which enhances the popular 
+Firebug JavaScript debugger with a new, practical feature called 
+\textit{lastChange}. \textit{lastChange} automatically locates the last point that 
+a variable or an object property has been changed. Starting from a 
+program halted on a breakpoint, the \textit{lastChange} algorithm 
+applies queries to the live program during re-execution, recording 
+the call stack and limited program state each time 
+the property value changes. When the program halts again on the breakpoint, 
+it shows the program state at the last change point. To evaluate the usability and effectivness 
+of \textit{Querypoint} we studied four experienced JavaScript developers applying the tool to two test cases.
 
@@
 
-In breakpoint debugging, developers select data to be collected by
-searching through source files and setting breakpoints. To determine
-where a value was set incorrectly, a developer must set
-breakpoints at all possible points where the value changes. At
-every breakpoint, the developer must determine if the location is in
-fact related to the questionable value change then study the complex
-debugger user interface and memorize values or manually collect
-data. As the number of breakpoint hits increases, the process of
-checking the program state, collecting data and resuming the execution
-becomes cumbersome.
+%In breakpoint debugging, developers select data to be collected by
+%searching through source files and setting breakpoints. To determine
+%where a value was set incorrectly, a developer must set
+%breakpoints at all possible points where the value changes. At
+%every breakpoint, the developer must determine if the location is in
+%fact related to the questionable value change then study the complex
+%debugger user interface and memorize values or manually collect
+%data. As the number of breakpoint hits increases, the process of
+%checking the program state, collecting data and resuming the execution
+%becomes cumbersome.
 
-In log-based debugging, developers select data to be collected by
-inserting statements for all points of possible change.  While in
-breakpoint-based debugging, the whole program state is available to
-developer, in log-based debugging, developer has to decide what data
-should be collected when inserts the log statement. It is very common
-that the developer has to repeat this step several times due to
-insufficient collected data, or to wait a long time because too much
-data is recorded. Once adequate data is collected, it still
-requires analyzing and understanding. Developers usually end up in
-dealing with long log files and analyzing huge amounts of collected data. 
-Neither approach effectively assists the developer in finding origins to a wrong
-value.
+%In log-based debugging, developers select data to be collected by
+%inserting statements for all points of possible change.  While in
+%breakpoint-based debugging, the whole program state is available to
+%developer, in log-based debugging, developer has to decide what data
+%should be collected when inserts the log statement. It is very common
+%that the developer has to repeat this step several times due to
+%insufficient collected data, or to wait a long time because too much
+%data is recorded. Once adequate data is collected, it still
+%requires analyzing and understanding. Developers usually end up in
+%dealing with long log files and analyzing huge amounts of collected data. 
+%Neither approach effectively assists the developer in finding origins to a wrong
+%value.
 
-Our new functionality in
-debuggers, \textit{lastChange}, locates the origin of a wrong
-value by queries on the running program.
-Imagine that a program execution is
-paused on a breakpoint and the developer is
-suspicious about the value of a variable or an object property. The
-developer selects \textit{lastChange} on the value. The debugger
-replays the buggy execution and collects data
-when the data field changes. Once the execution reaches the same place 
-(i.e., the same
-breakpoint hit), it pauses the execution, analyzes the collected data
-and shows the location of the last change to the developer. The
-developer can also examine the program state at the located point of
-execution, and continue debugging by more \textit{lastChange} queries
-from that point.
+Locating the origin of wrong values becomes even harder when developers 
+deal with weakly-typed dynamic languages such as JavaScript. First, due to weakly-typed
+nature of these languages the search space that the developer should consider is considerably 
+larger than traditional languages such as Java and C{\small\#}. Second, dynamic features make 
+program full static analysis almost impossible.
 
-Our contribution in this paper is the technique \textit{lastChange},
-which locates the last place a value has changed, gathers other values
-from that execution point, and allows \textit{lastChange} operations
-from that point. The technique builds on existing breakpoint debugger
-technology  and it does not require a special environment to
-create identical, instruction by instruction, re-executions. We demonstrate the feasibility of the approach with 
-\textit{Querypoint}, an implementation extending Firebug
-JavaScript debugger. \textit{Querypoint} also provides mechanism for
-automated bug reproduction, and a novel user interface which
+\textit{Querypoint}, is a Firefox plugin which enhances the popular 
+Firebug JavaScript debugger with a new, practical feature called 
+\textit{lastChange}\cite{Mirghasemi2011}. \textit{lastChange}, locates the origin of a wrong
+value by queries on the running program. This feature enables interactive 
+dynamic data dependency navigation without requiring a full trace, unlike 
+other dynamic slice navigation interfaces. The technique builds on existing 
+breakpoint debugger technology  and it does not require a special environment to
+create identical, instruction by instruction, re-executions. \textit{Querypoint} 
+also provides mechanism for automated bug reproduction, and a novel user interface which
 summarizes investigated execution points and collected results.
-The \textit{lastChange} algorithm provides information on important program
-values during the program execution without voluminous logs and without tedious
- insertion and removal of breakpoints. We believe other queries over the
- running program can be formulated to generalize this technique.
+
+%Morover, it implements interactive 
+% dynamic data dependency navigation for JavaScript, which poses a unique 
+% challenge with respect to its dynamic nature.
+
+%Imagine that a program execution 
+%is paused on a breakpoint and the developer is
+%suspicious about the value of a variable or an object property. The
+%developer selects \textit{lastChange} on the value. The debugger
+%replays the buggy execution and collects data when the data field changes. 
+%Once the execution reaches the same place (i.e., the same
+%breakpoint hit), it pauses the execution, analyzes the collected data
+%and shows the location of the last change to the developer. The
+%developer can also examine the program state at the located point of
+%execution, and continue debugging by more \textit{lastChange} queries
+%from that point.
 
@@
 %whyline, firecrystal
+Most tools developed to enhance developers' navigation on the buggy execution can 
+be classifed in two main groups: replay-based and logging-based. Replay-based 
+approaches capture limited data during execution and replay the buggy execution 
+to reach past points. In contrast, logging-based approaches collect enough data during
+execution to relieve developer from re-execution, then query the data to 
+inform the developer.
 
-Tools developed to enhance developers' movement on the buggy execution can be classifed in two groups: replay-based and logging-based.
+Among replay-based debuggers we can name bdb \cite{Boothe} and
+reverse watchpoint \cite{Maruyama}. Both tools rely on deterministic
+executions and employ a step counter to locate the requested point from the
+beginning of execution. These tools incur two to four times runtime overhead.
 
-%The algorithm we presented in this paper obtain information about
-%the execution state logically earlier in the control flow by querying 
-%the executioin state during replay using the technology of 
-%conventional breakpoint debuggers.  
-The \textit{lastChange} approach resembles the operational model of replay-based debugging 
-and the query approach of logging-based
-debugging.  Replay-based approaches capture limited data during
-execution and replay the buggy execution to reach past points. In
-contrast, logging-based approaches collect enough data during
-execution to relieve developer from re-execution, then query the data to 
-inform the developer. Replay-based
-approaches impose much less runtime overhead (about two orders of
-magnitudes) comparing to logging-based approaches. However, developer
-has to re-execute the buggy execution several
-times. \textit{lastChange} collects data on re-execution by queries
-selected by developer interaction with the debugger. Therefore it has 
-the selectivity of the replay-based approaches that improves performance, 
-% but we have 
-and the flexibilty of the queries so it does not require deterministic replay.
-
-Among replay-based debuggers we compare to bdb \cite{Boothe} and
-reverse watchpoint \cite{Maruyama}.  A bidirectional C debugger, bdb
-employs a step counter to locate the requested point from the
-beginning of execution. It relies on deterministic execution replay
-%(i.e., the same sequence of instructions in re-execution) 
-and records the results of non-deterministic system calls and re-injects them into
-the program when it is replayed. It makes use of checkpoints to reduce
-the time needed for re-execution. Reverse watchpoint, similar to bdb, uses
-a counter to correctly locate the last write access of a selected variable in the
-next execution \cite{Maruyama}.
-% Reverse watchpoint is proposed by Maruyama et al., analyses the execution and moves the debugger to the
-% last write access of a selected variable by re-executing the program
-%from the beginning\cite{Maruyama}.  Similar to bdb it relies on deterministic
-%replay and uses a counter to correctly locate a point in the next
-%execution. 
-The main disadvantage of these approaches is that they require 
-identical, instruction by instruction, re-executions. % exactly the same executions. 
-Even one instruction difference between
-two executions leads to wrong results. On the other hand,
-\textit{lastChange} doesn't require any special feature in the
-re-execution and fits into existing debugging practice
-
-Among logging-based approaches are \textit{omniscient} debuggers
-ODB\cite{Lewis} and Unstuck\cite{Hofer}. Both
-approaches keep the log history in memory and hence can only record
-and store the complete history for a short period of time. These
-debuggers record all the events that occur during the buggy execution
-and later let the developer to navigate through the obtained execution
-log. In these approaches there is no execution to resume: moving
-backwards in the log can be similar to moving forwards. A more scalable 
-approach to omniscient debugging has been proposed by Pothier et al. \cite{Pothier}. 
-Their back-in-time debugger, TOD, addresses the space problem by storing 
-execution events in a distributed database. Bhansali et al. \cite{Bhansali} attempted to address the performance overhead 
-and large trace size of logging-based debugging in their time-travelling debugger, Nirvana. 
-Nirvana first collects a full compressed trace of program execution and then 
-simulates re-execution. Their results are quite similar to omniscient 
-debuggers. Nirvana incurs about 15 to 68 times runtime overhead in 
-re-simulation.
-
-Logging-based debuggers suffer from different issues. First, the recording
-step is time expensive and it should be repeated in case of changes in
+Among logging-based debuggers are \textit{omniscient} debuggers (e.g.,
+ODB\cite{Lewis}, TOD \cite{Pothier}, Unstuck\cite{Hofer} and WhyLine\cite{Ko}) and
+time-travelling debuggers (e.g., Nirvana \cite{Bhansali}). Logging-based debuggers 
+suffer from different issues. First, the recording
+step is time expensive (20-120 times) and it should be repeated in case of changes in
 program. Second, the execution log cannot fully replace the live
@@
 the program state at a certain point) may not be efficient enough for
-debugging realistic programs. Comparing to logging-based debuggers our approach 
-has little upfront cost and more flexibility. The developer can start debugging just 
-after reproducing the bug without a capturing step.  Changing inputs or
-environment settings and re-executing to investigate the bug works as
-in conventional breakpoint debuggers.
+debugging realistic programs.
 
-A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
-machine level support for keeping the history of events. It replaces every
-object reference with an alias object which keeps the history of
-changes to the object reference. 
-%In this way, when an object is
-%collected by garbage collector, its track of changes (if it is not
-%referenced by other aliases) will be also collected. 
-Although this approach incurs less runtime overhead (7 times) in
-comparison to omniscient debuggers, it adds memory
-overhead.
+\textit{Querypoint} resembles the operational model of replay-based debuggers
+and the query approach of logging-based debuggers. Contrary to
+other replay-based debuggers, which require exactly the same
+re-executions (deterministic executions), \textit{Querypoint} only requires \textit{bug 
+reproducibility}, meaning a test case is available which reproduces the bug and a 
+way to halt execution reliably after the reproduction. Contrary to logging-based
+debuggers \textit{Querypoint} selectively collects data which significantly reduces
+runtime overhead incured by logging.
 
-Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
-Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
-First, it is limited to \texttt{undefined} and \texttt{null} values. Second, it does not return the last change
-of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
+%A recent work by Lienhard et al.\cite{Lienhard} suggests virtual
+%machine level support for keeping the history of events. It replaces every
+%object reference with an alias object which keeps the history of
+%changes to the object reference. Although this approach incurs less runtime overhead (7 times) in
+%comparison to omniscient debuggers, it adds memory
+%overhead.
 
-%Two new directions in logging debuggers explore more detailed use of
-%the log and more effective user interface to the collected data. %logging approaches. 
-%WhyLine\cite{Ko} provides visual interface to collected runtime information and lets
-%developer moves on execution log using queries expressed in terms of
-%the programming objects.
+% Origin tracking of \texttt{undefined} and \texttt{null} values employing \textit{value piggybacking} technique proposed by
+%Bond et al. \cite{Bond}. This approach has two main limitations comparing to \textit{lastChange}.
+%First, it is limited to \texttt{undefined} and \texttt{null} values. Second, it does not return the last change
+%of a \texttt{null} variable but the first place that the \texttt{null} value is originated.
 
-WhyLine\cite{Ko} stores the program user interface in
-addition to the program trace and provides answers to why and why not
-questions to the user. 
-%Jive\cite{Czyz} depicts the history of
-%execution by a sequence diagram and lets the user to query on the events
-%database. 
-WhyLine suffers from the requirement of gathering tracing information before its unique capabilities can be used.
-We imagine that the runtime queries we use in \textit{lastChange} may be used to gather data incrementally for this kind of debugging approach.
-
-%Querypoint debugging uses re-executions to gather infor-mation requested by the developer: the memory overhead depends on the query not the entire program.
-Moreover, the Lienhard et al.
-debugger significantly changes the virtual machine, while our approach is a generalization to conditional breakpoints and available debugger infrastructure can be adapted to support it.
-
-%\textit{lastChange} functionality does rely on a conventional breakpoint to begin queries, a requirement not shared by full logging solutions.
-Here we leverage past experience of developers, but there are also new tools [] to help with this problem in the case of graphical and event based systems.
-
-\section{Introductory example}
+\section{Querypoint}
 \label{sec:introExample}
 
-We illustrate the \textit{lastChange} functionality by a simple
+We illustrate the \textit{Querypoint} functionality by a simple
 example. The example demonstrates a buggy JavaScript code in a HTML
@@
 \texttt{myObject.myProperty} value at the paused point is \texttt{0}. We expected this value to be \texttt{2}.
-
-To apply backward search strategy for locating defects, the developer
-first needs to know the origin of the wrong value. To achieve this
-goal using breakpoints, the developer should search code to find all possible places that
-\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
-object and property can be accessed and changed through different
-names and methods. There is no simple way to identify these aliases or
-even their total number.  The developer can make a good guess and set
-breakpoints on lines where the property seems to be changed. Then they
-re-execute the program and examine the state looking for values that
-may lead to the incorrect value observed at line 22. All this work
-must be repeated if a new alias is discovered or if some
-information related to the buggy result was missed while stopped on
-one of the breakpoints.
-
-In contrast, we have added a high-level function in the debugger,
-\textit{lastChange}, which provides the answer without tedious manual
-effort from the developer. By right clicking on
-\texttt{myObject.myProperty} in the Watch panel, the developer can run
-\textit{lastChange} command (Figure~\ref{fig:example1}). The debugger
-re-executes the program and halts again at the breakpoint on line 22.
-However, it shows a new panel, called QP, centered on the source at line 29
-(Figure~\ref{fig:example3}), the point of \textit{lastChange}.  To
-the right, the TraceData panel shows values of properties of the
-program state when it passed through line 29.  These two panels
-resemble the Script and Watch panels, but they show data collected by
-the debugger at one execution point which is now past: these are
-\textit{traces} or \textit{logs} of information collected during the re-execution.
 
@@
 
+To apply backward search strategy for locating defects, the developer
+first needs to know the origin of the wrong value. To achieve this
+goal using breakpoints, the developer should search code to find all possible places that
+\texttt{myObject. myProperty} might get a new value and set breakpoint at these locations. However, an
+object and property can be accessed and changed through different
+names and methods. There is no simple way to identify these aliases or
+even their total number.  The developer can make a good guess and set
+breakpoints on lines where the property seems to be changed. Then they
+re-execute the program and examine the state looking for values that
+may lead to the incorrect value observed at line 22. All this work
+must be repeated if a new alias is discovered or if some
+information related to the buggy result was missed while stopped on
+one of the breakpoints.
+
+In contrast, we have added a high-level function in the debugger,
+\textit{lastChange}, which provides the answer without tedious manual
+effort from the developer. By right clicking on
+\texttt{myObject.myProperty} in the Watch panel, the developer can run
+\textit{lastChange} command (Figure~\ref{fig:example1}). The debugger
+re-executes the program and halts again at the breakpoint on line 22.
+However, it shows a new panel, called QP, centered on the source at line 29
+(Figure~\ref{fig:example3}), the point of \textit{lastChange}.  To
+the right, the TraceData panel shows values of properties of the
+program state when it passed through line 29.  These two panels
+resemble the Script and Watch panels, but they show data collected by
+the debugger at one execution point which is now past: these are
+\textit{traces} or \textit{logs} of information collected during the re-execution.
+
 Looking at line 29, it seems that something is wrong with
@@
 interface. On the top of the left panel in Figure~\ref{fig:example4}
-there is an opened list which shows all three examined points. The
-first one is the breakpoint on line 22, the second one is the point
-which is when \texttt{myObject.myProperty} changed before
-reaching the breakpoint and finally the last one is the point of
-execution in which \texttt{myCondition.value} gets the
-\texttt{undefined} value. Moreover, the source lines related to these
+there is an opened list which shows all three examined points. Moreover, the source lines related to these
 points are marked with red \textbf{Q} icons.
+%The
+%first one is the breakpoint on line 22, the second one is the point
+%which is when \texttt{myObject.myProperty} changed before
+%reaching the breakpoint and finally the last one is the point of
+%execution in which \texttt{myCondition.value} gets the
+%\texttt{undefined} value.
 
-Notice that in our example, \textit{lastChange} combines some aspects
-of breakpoint and of log-based debugging. Like breakpoint debugging,
-the developer re-executes a live runtime without changing the source
-and without a special execution environment beyond the debugger. The
-state of the program memory and the call stack are available at each
-lastChange point. Like log-based debugging, the program state and the
-call stack are recorded during program execution. We can't halt the
-program at \textit{lastChange} because we don't know which point is the last
-one until we return to the original breakpoint. In section 5 we
-discuss cases where it is possible to pause at lines of \textit{lastChange}.
+%Notice that in our example, \textit{lastChange} combines some aspects
+%of breakpoint and of log-based debugging. Like breakpoint debugging,
+%the developer re-executes a live runtime without changing the source
+%and without a special execution environment beyond the debugger. The
+%state of the program memory and the call stack are available at each
+%lastChange point. Like log-based debugging, the program state and the
+%call stack are recorded during program execution. We can't halt the
+%program at \textit{lastChange} because we don't know which point is the last
+%one until we return to the original breakpoint. 
+%In section 5 we discuss cases where it is possible to pause at lines of \textit{lastChange}.
 
-\subsection{Re-Execution, Reproduction Point and Data Collection}
+\textit{Querypoint} needs a test case to reproduce the
+execution and conditions to correctly recognize the reproduction point. 
+Although both elements can be directly provided by developer, \textit{Querypoint}
+is also able to automatically create them from the first execution.
 
-\section{Limitations and Future Work}
+To replay execution, \textit{Querypoint} keeps track of breakpoint hits and single steps. For example, 
+if the developer queries \textit{lastChange} at the third hit of breakpoint \textit{b}, in
+re-execution, the third hit is recognized as the reproduction point. \textit{Querypoint} supports two mechanism
+for automatic re-execution: callstack-reproduction and record-replay. In callstack reproduction the function from
+the earliest frame of the call stack is called with the same parameters. The record-replay execution uses two phases. In the record phase, it 
+stores the initial page url and the events and parameters corresponding to user actions. In the replay phase, it opens
+the same url and simulates events as if they were user actions.
 
-\section{Reproducible Non-Deterministic Execution}
+In addition to the data collected at every change event for identifying the \textit{lastChange}
+result, \textit{Querypoint} partially stores values in program state.
+There is a trade-off between the amount of data collected at every change event and the number of re-executions.
+If the developer asks for some values which have not been stored, \textit{Querypoint} re-executes and collects the requested data.
 
-\subsection{Combination of {\large\bf\textit{lastChange}} and Breakpoint Debugging}
+\section{User Study}
+We supplied four experienced Javascript developers with \textit{Querypoint} in an 
+extended Firebug debugger\footnote[1]{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}. Following a tutorial and a practice case, we observed as they 
+applied both conventional breakpoint and \textit{lastChange} on two small programs we provided.
+The first program, Shapes, calculates the area and perimeter values for a list of shapes.
+The bug happens when one of the calculated numbers is zero.
+The second program, Moving Circle, randomly scales and moves a circle in the page.
+The bug happens once the circle becomes invisible after an exception occurs.
+This case represent a reproducible non-deterministic execution.
+The developers were asked to locate the defects that caused these bugs.
+All four developers successfully applied \textit{lastChange} to the test programs and understood how it could help debugging.
+To find the defect location with breakpoints, all four users took more steps\footnote[2]{A step is a button push, either single stepping the debugger or running a \textit{lastChange query}} and more time (Figure~\ref{fig:userstudy}).
 
-\section{Conclusion}
+%another searched the text, a third set a lot of breakpoints to understand the control flow. 
+%Based on our own experience we expect these strategies represent the kinds of approaches 
+%developers have available. These operations are time consuming and tedious. In contrast, all four users 
+%found the defect location with just two \textit{lastChange} operations.
 
-\section{Acknowledgments}
+% Based on our measurements,
+%this makes \textit{lastChange} about three times faster than breakpoints for the navigation from 
+%the reproduction point to the defect
+%We recognize that these programs were designed to highlight lastChange and many kinds of debugging 
+%issues have been hidden by the design of our tests. Nevertheless our results show that, when a defect 
+%relates to incorrect values and a developer recognizes this, then the operational 
+%mechanics of lastChange lead to the defect much more quickly than breakpoints.
+
+\begin{figure}[htp]
+\centering 
+\includegraphics[width=.48\textwidth]{10-userstudy.pdf}
+\caption{The number of steps (and time in seconds) required before locating a defect, for each test subject and test program. 
+Cells with a white background report values with conventional debugging; Cells with a colored background use \textit{lastChange}.}
+
+\label{fig:userstudy}
+\end{figure}
+
+\section{Conclusion and Future Work}
+\textit{Querypoint} provides critical information for debugging Jav- aScript programs: 
+the location and state at the point where a questionable value was assigned. It only requires 
+bug reproducibility and is built on the existing breakpoint technology.
+
+In our next iteration we plan to merge the query and breakpoint results. \textit{Querypoint} shows the 
+results of \textit{lastChange} in a similar but different view from breakpoint debugging. This focuses attention 
+on value changes, but it makes studying control flow more difficult. %: we don't support single stepping from a \textit{lastChange} result in our user interface.
+
+% In our next iteration we plan to merge the query and breakpoint results and support pausing as described in Sec.~\ref{sec:pausing}.
 
@@
 
-\bibitem{Horwitz}%[Hofer(2006)]
-S. Horwitz, B. Liblit, and M. Polishchuk. \newblock Better Debugging via Output Tracing and Callstack-Sensitive Slicing.
-\emph{IEEE Transactions on
-Software Engineering}, 36(1):7-19, 2010.
+%\bibitem{Horwitz}%[Hofer(2006)]
+%S. Horwitz, B. Liblit, and M. Polishchuk. \newblock Better Debugging via Output Tracing and Callstack-Sensitive Slicing.
+%\emph{IEEE Transactions on
+%Software Engineering}, 36(1):7-19, 2010.
 
-\bibitem{JPDA}%[JSD(2010)]
-Java Platform Debugger Architecture. \newblock http://java.sun.com/javase/technologies/ core/toolsapis/jpda.
+%\bibitem{JPDA}%[JSD(2010)]
+%Java Platform Debugger Architecture. \newblock http://java.sun.com/javase/technologies/ core/toolsapis/jpda.
 
@@
 
-\bibitem{Sridharan}%[Boothe(2000)]
-M. Sridharan, S.J. Fink , and R. Bodik. \newblock Thin slicing.
-\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
-June, 2007.
+%\bibitem{Sridharan}%[Boothe(2000)]
+%M. Sridharan, S.J. Fink , and R. Bodik. \newblock Thin slicing.
+%\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
+%June, 2007.
 
-\bibitem{Weiser}
-M. Weiser. \newblock Program slicing.
-\newblock \emph{IEEE Transactions on
-Software Engineering}, vol. SE-10, no. 4, pp. 352-357,
-July 1984.
+%\bibitem{Weiser}
+%M. Weiser. \newblock Program slicing.
+%\newblock \emph{IEEE Transactions on
+%Software Engineering}, vol. SE-10, no. 4, pp. 352-357,
+%July 1984.
 
-\bibitem{Zeller}
-A. Zeller. \newblock Why programs fail: A guide to systematic debugging.
-Morgan Kaufmann (2005)
+%\bibitem{Zeller}
+%A. Zeller. \newblock Why programs fail: A guide to systematic debugging.
+%Morgan Kaufmann (2005)
 
@@
 %
+
+\appendix
+\section{Presentation}
+The presentation will include the following parts:
+\begin{enumerate}
+	\item A short demo, debugging a simple buggy web page by the tool.
+	\item The brief explanation of \textit{lastChange} algorithm.
+	\item The brief explanation of \textit{Querypoint} debugging as a general debugging approach.
+	\item The Discussion about non-deterministic reproducible executions.
+	\item A Comprehensive demo on the Tool features.
+\end{enumerate}
+
+\section{Tool Maturity}
+The tool is functional, however this is the first version of \textit{Querypoint} and therefore it is 
+not mature enough to be used by developers. Moreover, \textit{Querypoint} is built on top of the 
+Firefox 3.6 JavaScript engine. Due to significant changes in Firefox platform, \textit{Querypoint} is 
+not compatible with the newer versions of Firefox.
+
+We requested the mozilla team to support basic operations needed by \textit{lastChange} inside the 
+Firefox JavaScript Engine. Our proposal was accepted and they planned for the implementation of 
+these operations (Feature requests 641234 and 641236 in Mozilla Bugzilla) in the next major Firefox release.
+
+\section{Resources}
+The tool and its source code are publicly available and can be downloaded 
+from \textit{Querypoint Debugging} web site at this address:
+
+\mbox{\href{http://code.google.com/p/querypoint-debugging}{http://code.google.com/p/querypoint-debugging}}
+
+The details of our user study, including the instructions and test cases source code, are available at this address:
+
+\mbox{\href{http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy}{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}}
+
 \end{document}

### 2011-06-10 trunk/papers/fse-tool2011/sig-alternate.tex

@@
 the property value changes. When the program halts again on the breakpoint, 
-it shows the program state at the last change point. To evaluate the usability and effectivness 
+it shows the call stack and program state at the last change point. To evaluate the usability and effectivness 
 of \textit{Querypoint} we studied four experienced JavaScript developers applying the tool to two test cases.
@@
 nature of these languages the search space that the developer should consider is considerably 
-larger than traditional languages such as Java and C{\small\#}. Second, dynamic features make 
-program full static analysis almost impossible.
+larger than traditional languages such as Java and C{\small\#}. Second, dynamics features limit 
+the value of traditional compile-time program analysis.
 
@@
 ]{\label{fig:example1}\includegraphics[width=1.0\textwidth, %height=.17\textheight
-  ]{1-bp22.jpg}}
+  ]{1-bp22.png}}
 
@@
   point.]{\label{fig:example3}\includegraphics[width=1.0\textwidth,% height=.21\textheight
-  ]{3-lastChange.jpg}}
+  ]{3-lastChange.png}}
 
@@
   data.]{\label{fig:example4}\includegraphics[width=1.0\textwidth%,height=.25\textheight
-    ]{4-lastChange2.jpg}}
+    ]{4-lastChange2.png}}
 
@@
 
-\mbox{\href{http://code.google.com/p/querypoint-debugging}{http://code.google.com/p/querypoint-debugging}}
+\mbox{\href{http://sites.google.com/site/querypoint}{http://sites.google.com/site/querypoint}}
 
